### 2012-06-15 3dimpvt/_region_.tex
added michaels draft and new draft also

\message{ !name(paper.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the 3DIMPVT Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

\message{ !name(paper.tex) !offset(139) }
\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove citations to
one's own work---in fact it is often impossible to review a paper
unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that
you are Lucy Smith, it says that you are building on her work.  If you
are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
and Jones show in [7]'' and at the end of the paper, include reference
7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
  \begin{center}
    An analysis of the frobnicatable foo filter.
  \end{center}

  In this paper we present a performance analysis of our previous
  paper [1], and show it to be inferior to all previously known
  methods.  Why the previous paper was accepted without this analysis
  is beyond me.

  [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
  \begin{center}
    An analysis of the frobnicatable foo filter.
  \end{center}

  In this paper we present a performance analysis of the paper of
  Smith \etal [1], and show it to be inferior to all previously known
  methods.  Why the previous paper was accepted without this analysis
  is beyond me.

  [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a
  fundamental contribution to human knowledge''.  Nature 381(12),
  1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to
that submission in order to explain the differences, just as you would
if you had previously published related work.  In such cases, include
the anonymized parallel submission~\cite{Authors12} as additional
material and cite it as
\begin{quote} [1] Authors. ``The frobnicatable foo filter'', F\&G 2012
  Submission ID 324, Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details
can be found elsewhere, and refer them to a technical report.  For
conference submissions, the paper must stand on its own, and not {\em
  require} the reviewer to go to a techreport for further details.
Thus, you may say in the body of the paper ``further details may be
found in~\cite{Authors12b}''.  Then submit the techreport as
additional material.  Again, you may not assume the reviewers will
read this material.

Sometimes your paper is about a problem which you tested using a tool
which is widely known to be restricted to a single institution.  For
example, let's say it's 1969, you have solved a key problem on the
Apollo lander, and you believe that the CVPR70 audience would like to
hear about your solution.  The work is a development of your
celebrated 1968 paper entitled ``Zero-g frobnication: How being the
only people in the world with access to the Apollo lander source code
makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how
to improve our previous work [Anonymous, 1968].  This time we tested
the algorithm on a lunar lander [name of lander removed for blind
review]''.  That would be silly, and would immediately identify the
authors. Instead write the following:
\begin{quotation}
  \noindent
  We describe a system for zero-g frobnication.  This system is new
  because it handles the following cases: A, B.  Previous systems
  [Zeus et al. 1968] didn't handle case B properly.  Ours handles it
  by including a foo term in the bar integral.

  ...

  The proposed system was integrated with the Apollo lunar lander, and
  went all the way to the moon, don't you know.  It displayed the
  following behaviours which show how well we solved cases A and B:
  ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you
as the authors.  A reviewer might think it likely that the new paper
was written by Zeus \etal, but cannot make any decision based on that
guess.  He or she would have to be sure that no other authors could
have been contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
  \begin{center}
    \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
  \end{center}
  \caption{Example of caption.  It is set in Roman so that mathematics
    (always set in Roman: $B \sin A = A \sin B$) may be included
    without an ugly clash.}
  \label{fig:long}
  \label{fig:onecol}
\end{figure}

\message{ !name(paper.tex) !offset(325) }

\end{document}

### 2012-06-15 3dimpvt/paper.tex
added michaels draft and new draft also

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the 3DIMPVT Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for 3DIMPVT Proceedings}

\author{First Author\\
  Institution1\\
  Institution1 address\\
  {\tt\small firstauthor@i1.org}
  % For a paper whose authors are all at the same institution, omit
  % the following lines up until the closing ``}''.  Additional
  % authors and addresses can be added with ``\and'', just like the
  % second author.  To save space, use either the email address or
  % home page, not both
  \and
  Second Author\\
  Institution2\\
  First line of institution2 address\\
  {\small\url{http://www.author.org/~second}} }

\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is used in applications
  such as virtual reality and environment mapping. Texture mapping
  these models accurately is vital towards visualizing the data
  gathered by modeling systems and increases overall usability. The
  localization of cameras in 3D scenes often suffers from
  inaccuracies, resulting in visible discontinuties when different
  images are projected onto a texture. Previous approaches at
  minimizing these discontinuities suffer from error accumulation when
  stitching together multiple images and do not robustly handle wide
  ranges of camera locations and angles. We propose two approaches for
  reducing discontinuities during texture mapping, tailored towards a
  backpack-mounted data acquisition system.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Three-dimensional modeling of indoor environments has a variety of
applications such as training and simulation for disaster management,
virtual heritage conservation, and mapping of hazardous sites. Manual
construction of these digital models can be time consuming, and as
such, automated 3D site modeling has garnered much interest in recent
years.

The first step in automated 3d modeling is the physical scanning of
the environment's geometry. An indoor modeling system must be able to
calculate camera locations within an environment while simulatenously
reconstructing the 3D structure of the environment itself. This
problem is studied by the robotics and computer vision communities as
the simultaneous localization and mapping (SLAM) problem, and is
generally solved using a combination of laser range scanners, cameras,
and inertial measurement units (IMUs).

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with higher localization
errors and greater variance in camera locations. The paper is
organized as follows. Section 2 provides an overview of the backpack
modeling system from which data and examples used throughout this
paper are from. Section 3 describes the general problem of 3D texture
mapping and reviews existing approaches. Section 4 describes
challenges posed by the backpack modeling system and presents our two
approaches tailored for walls and floors/ceilings
respectively. Section 5 compares results and presents conclusions.

\section{Backpack Modeling System}
Human-operated data acquisition systems provide unique advantages in terms of agility and portability over vehicular-mounted systems. Unfortunately, human-operated systems suffer from a lack of automation and stability, resulting in higher localization variance and leading to the problems discussed in Section 4.

\subsection{Data Acquisition Hardware}
The backpack modeling system from which our data was collected contains five 2D laser range scanners, two cameras, an orientation sensor, and an IMU (Should I even mention the IMU at all?). The laser scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter range and a 270$^{\circ}$ field of view. These scanners are mounted orthogonally to one another. The two cameras are Point Grey Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a strap-down navigation-grade sensor which combines three ring laser gyros with bias stability of less than 0.003$^{\circ}$/hour and three precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The HG9900 provides highly accurate measurements of all 6 DOF at 200Hz and thus serves as our ground truth for the experiments in this paper. ]The orientation sensor (OS), an InterSense InertiaCube3, provides orientation parameters at a rate of 180Hz.

\subsection{Environment Reconstruction}
Using a combination of these sensors and multiple localization and loop-closure algorithms, the backpack is localized over its data collection period, and a 3D point cloud of our environment is constructed. Approximate normal vectors for each point in the point cloud are then calculated by gathering neighboring points within a small radius and running a Principal Component Analysis procedure. These normal vectors allow for the classification and grouping of adjacent points into structures such as walls, ceilings, floors, and staircases. A RANSAC algorithm is then employed to fit polygonal planes to these structured groupings of points, resulting in a fully planar model. This planar model, consisting of multiple 2D polygonal planes in 3D space, along with the set of images captured by the backpack's camera, can be considered the input data on which our approach runs.

\subsection{Image Subsampling}
Before beginning the texture mapping process, it is prudent to reduce the amount of potential images being considered for texture mapping each plane. The backpack modeling system takes 5 pictures/second from both cameras, resulting in each plane being present in (and capable of being textured mapped by) thousands of images, at a wide variance of distances and angles. Thus, for the sake of efficiency, it makes sense to associate each plane with a much smaller sample of images. When creating this subset of images for each plane, there are three criteria we keep in mind. First, we want such a subset of images to be capable of texturing the entirety of a plane, so as to ensure there are no holes in our final texture. Second, we want all our images to be taken from a relatively close distance to the plane, and at as much of a direct, head-on angle as possible. This ensures that the image projects squarely onto our desired plane, with minimal inclusion of other planes, and we get a texture with high resolution. Third, we desire an amount of overlap between the images chosen. This overlap helps us with preprocessing as well as postprocessing techniques discussed in Sections x and y.

To meet these three criteria, we tesselate each plane into [X] triangles of [Y] size. For each triangle, we find all images that can be projected upon the entirety of the triangle, accounting for occlusion with other planes as well, using standard ray-polygon intersection tests. Of these images, we then select the best one according to the heuristic in equation X, favoring closer distances and more head-on viewing angles. We also enforce that no two images are chosen such that they were taken within 0.5 meters of eachother. This results in a greatly-reduced set of images such that each one is objectively the "best" location-wise for some number of areas on the plane, addressing the first two criteria. Furthermore, since cameras are only at good angles to triangles near their center of projection, images will be chosen such that there is high overlap between them. This process reduces the amount of candidate images for each plane from many thousands to around 50, at fairly even spacing. With this completed, each of our planes is associated with a sufficiently sized list of candidate images, and we are ready to begin texture mapping.

\section{NOTES}
4 Special Considerations due to BMS blabla sucky title
The backpack modeling system described in Section 2 was designed to prioritize for texturing walls. As mentioned previously, the backpack contains two fisheye cameras, one aimed directly to the left of the backpack operator, and one aimed directly to the right. Thus, in order to texture the ceiling where the operator walked, images from both cameras must be combined. Even more problematic, the floor beneath the backpack is physically obscured by the operator's body, and thus must be textured by images taken from different locations. These problems are compounded by the fact that the operator's data acquisition path attempts to fully scan each wall, but not necessarily the entirety of a floor or ceiling. This means that large swaths of floors and ceilings are never walked directly over or under, and thus must be textured by sidelong images taken from further distances and at oblique angles. We strongly prefer head-on images because when images are projected onto a planar surface at an extreme angle, the resultant texture ends up spanning a large portion of the plane, applying low-resolution textures to areas at a great distance from the camera location.

In short, these factors mean that wall planes are associated with a multitude of upright, uniform images, taken head-on and from a relatively close distance at regular intervals, while floors and ceilings are associated with images of all orientations and distances. This major difference suggests we employ two strategies, one tailored for each scenario.

4.1 Texturing Floors and Ceilings

4.2 Texturing Walls
Since our candidate images for texturing a wall are all taken from similar distances and orientations relative to our wall, their individual "qualities" are all fairly similar. We don't have to worry as much about filtering out bad images; rather we seek to select some subset of our images which together form a good texture.

5 Results and Analysis
but also occlusion projection thing. door projected onto wall is fine, door projected onto floor is bad.

\section{EVERYTHING AFTER HERE IS TEMPLATE STUFF}

\section{Introduction}

Please follow the steps outlined below when submitting your manuscript
to the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against
the use of sticky tape to attach your artwork to the paper), so all
authors should read this new version.

% -------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to 3DIMPVT, the authors assert that it has
not been previously published in substantially similar
form. Furthermore, no paper which contains significant overlap with
the contributions of this paper either has been or will be submitted
during the 3DIMPVT 2012 review period to {\bf either a journal} or any
conference or any workshop.  {\bf Papers violating this condition will
  be rejected}.

If there are papers that may appear to the reviewers to violate this
condition, then it is your responsibility to: (1)~cite these papers
(preserving anonymity as described in Section 1.6 below), (2)~argue in
the body of your paper why your 3DIMPVT paper is non-trivially
different from these concurrent submissions, and (3)~include
anonymized versions of those papers in the supplemental material.

\subsection{Paper length}
3DIMPVT papers may be between 6 pages and 8 pages.  Overlength papers
will simply not be reviewed.  This includes papers where the margins
and formatting are deemed to have been significantly altered from
those laid down by this style guide.  Note that this \LaTeX\ guide
already sets figure captions and references in a smaller font.  The
reason such papers will not be reviewed is that there is no provision
for supervised revisions of manuscripts.  The reviewing process cannot
determine the suitability of the paper for presentation in eight pages
if it is reviewed in eleven.

% -------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in
the version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the
ruler should not change the appearance of any other content on the
page.  The camera ready copy should not contain a ruler. (\LaTeX\
users may uncomment the \verb'\cvprfinalcopy' command in the document
preamble.)  Reviewers: note that the ruler measurements do not align
well with lines in the paper --- this turns out to be very difficult
to do well when the paper contains many figures and equations, and,
when done, looks ugly.  Just use fractional references (e.g.\ this
line is $097.15$), although in most cases one would expect that the
approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.
Just because you didn't refer to it in the text doesn't mean some
future reader might not need to refer to it.  It is cumbersome to have
to use circumlocutions like ``the equation second from the top of page
3 column 1''.  (Note that the ruler will not be present in the final
copy, so is not an alternative to equation numbers).  All authors will
benefit from reading Mermin's description of how to write mathematics:
\url{http://www.cvpr.org/doc/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove citations to
one's own work---in fact it is often impossible to review a paper
unless the previous citations are known and available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say that
you are Lucy Smith, it says that you are building on her work.  If you
are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
and Jones show in [7]'' and at the end of the paper, include reference
7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
  \begin{center}
    An analysis of the frobnicatable foo filter.
  \end{center}

  In this paper we present a performance analysis of our previous
  paper [1], and show it to be inferior to all previously known
  methods.  Why the previous paper was accepted without this analysis
  is beyond me.

  [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
  \begin{center}
    An analysis of the frobnicatable foo filter.
  \end{center}

  In this paper we present a performance analysis of the paper of
  Smith \etal [1], and show it to be inferior to all previously known
  methods.  Why the previous paper was accepted without this analysis
  is beyond me.

  [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a
  fundamental contribution to human knowledge''.  Nature 381(12),
  1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to
that submission in order to explain the differences, just as you would
if you had previously published related work.  In such cases, include
the anonymized parallel submission~\cite{Authors12} as additional
material and cite it as
\begin{quote} [1] Authors. ``The frobnicatable foo filter'', F\&G 2012
  Submission ID 324, Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details
can be found elsewhere, and refer them to a technical report.  For
conference submissions, the paper must stand on its own, and not {\em
  require} the reviewer to go to a techreport for further details.
Thus, you may say in the body of the paper ``further details may be
found in~\cite{Authors12b}''.  Then submit the techreport as
additional material.  Again, you may not assume the reviewers will
read this material.

Sometimes your paper is about a problem which you tested using a tool
which is widely known to be restricted to a single institution.  For
example, let's say it's 1969, you have solved a key problem on the
Apollo lander, and you believe that the CVPR70 audience would like to
hear about your solution.  The work is a development of your
celebrated 1968 paper entitled ``Zero-g frobnication: How being the
only people in the world with access to the Apollo lander source code
makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how
to improve our previous work [Anonymous, 1968].  This time we tested
the algorithm on a lunar lander [name of lander removed for blind
review]''.  That would be silly, and would immediately identify the
authors. Instead write the following:
\begin{quotation}
  \noindent
  We describe a system for zero-g frobnication.  This system is new
  because it handles the following cases: A, B.  Previous systems
  [Zeus et al. 1968] didn't handle case B properly.  Ours handles it
  by including a foo term in the bar integral.

  ...

  The proposed system was integrated with the Apollo lunar lander, and
  went all the way to the moon, don't you know.  It displayed the
  following behaviours which show how well we solved cases A and B:
  ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you
as the authors.  A reviewer might think it likely that the new paper
was written by Zeus \etal, but cannot make any decision based on that
guess.  He or she would have to be sure that no other authors could
have been contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
  \begin{center}
    \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
  \end{center}
  \caption{Example of caption.  It is set in Roman so that mathematics
    (always set in Roman: $B \sin A = A \sin B$) may be included
    without an ugly clash.}
  \label{fig:long}
  \label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
  \verb'$conf_a$' &  $conf_a$ \\
  \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The
provided \verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et
alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}''
is a complete word.)  However, use it only when there are three or
more authors.  Thus, the following is correct: `` Frobnication has
been trendy lately.  It was introduced by Alpher~\cite{Alpher02}, and
subsequently developed by Alpher and
Fotheringham-Smythe~\cite{Alpher03}, and Alpher
\etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher
\etal~\cite{Alpher03} ...''  because reference~\cite{Alpher03} has
just two authors.  If you use the \verb'\etal' macro provided, then
you need not worry about double periods when used at the end of a
sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors12} to
\cite{Alpher02,Alpher03,Authors12}.

\begin{figure*}
  \begin{center}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
  \end{center}
  \caption{Example of a short caption, which should be centered.}
  \label{fig:short}
\end{figure*}

% ------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of
the text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches
(22.54 cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide,
with a $\frac{5}{16}$ inch (0.8 cm) space between them. The main title
(on the first page) should begin 1.0 inch (2.54 cm) from the top edge
of the page. The second and following pages should begin 1.0 inch
(2.54 cm) from the top edge. On all pages, the bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5
\times 11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13
cm) from the bottom edge of the page.

% -------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must
be kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8
inches (22.54 cm) high.

% -------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither
is available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge
of the first page. The title should be in Times 14-point, boldface
type.  Capitalize the first letter of nouns, pronouns, verbs,
adjectives, and adverbs; do not capitalize articles, coordinate
conjunctions, or prepositions (unless the title begins with such a
word). Leave two blank lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is
to be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should
be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a
third-order heading (we discourage it), use 10-point Times, boldface,
initially capitalized, flush left, preceded by one blank line,
followed by a period and your text on the same line.

% -------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
  often distracts the reader from the main flow of the argument.}
sparingly.  Indeed, try to avoid footnotes altogether and include
necessary peripheral observations in the text (within parentheses, if
you prefer, as in this sentence).  If you wish to use a footnote,
place it at the bottom of the column on the page on which it is
referenced. Use Times 8-point type, single-spaced.

% -------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors12}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
  \begin{center}
    \begin{tabular}{|l|c|}
      \hline
      Method & Frobnability \\
      \hline\hline
      Theirs & Frumpy \\
      Yours & Frobbly \\
      Ours & Makes one's heart Frob\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Results.   Ours is better.}
\end{table}

% -------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you
wish to make is resolvable in a printed copy of the paper.  Resize
fonts in figures to match the font in the body text, and choose line
widths which render effectively in print.  Many readers (and
reviewers), even of an electronic copy, will choose to print your
paper in order to read it.  You cannot insist that they do otherwise,
and therefore must not assume that they can zoom in to see tiny
details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the figure width as a multiple
of the line width as in the example below {\small\begin{verbatim}
    \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

% -------------------------------------------------------------------------
\subsection{Color}

Color is valuable, and will be visible to readers of the electronic
copy.  However ensure that, when printed on a monochrome printer, no
important information is lost by the conversion to grayscale.

% ------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you
submit your finished paper. We MUST have this form before your paper
can be published in the proceedings.

% Please direct any questions to the production editor in charge of
% these proceedings at the IEEE Computer Society Press: Phone (714)
% 821-8380, or Fax (714) 761-1784.

{\small \bibliographystyle{ieee} \bibliography{egbib} }

\end{document}

### 2012-06-15 3dimpvt/template/egpaper_final.tex
added michaels draft and new draft also

--- 2012-06-15 3dimpvt/paper.tex
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+%\ifcvprfinal\pagestyle{empty}\fi
+\setcounter{page}{4321}
 \begin{document}
@@
 {\tt\small firstauthor@i1.org}
-  % For a paper whose authors are all at the same institution, omit
-  % the following lines up until the closing ``}''.  Additional
-  % authors and addresses can be added with ``\and'', just like the
-  % second author.  To save space, use either the email address or
-  % home page, not both
+% For a paper whose authors are all at the same institution,
+% omit the following lines up until the closing ``}''.
+% Additional authors and addresses can be added with ``\and'',
+% just like the second author.
+% To save space, use either the email address or home page, not both
 \and
@@
 First line of institution2 address\\
-  {\small\url{http://www.author.org/~second}} }
+{\tt\small secondauthor@i2.org}
+}
 
 \maketitle
-% \thispagestyle{empty}
+%\thispagestyle{empty}
 
@@
 \begin{abstract}
-  Automated 3D modeling of building interiors is used in applications
-  such as virtual reality and environment mapping. Texture mapping
-  these models accurately is vital towards visualizing the data
-  gathered by modeling systems and increases overall usability. The
-  localization of cameras in 3D scenes often suffers from
-  inaccuracies, resulting in visible discontinuties when different
-  images are projected onto a texture. Previous approaches at
-  minimizing these discontinuities suffer from error accumulation when
-  stitching together multiple images and do not robustly handle wide
-  ranges of camera locations and angles. We propose two approaches for
-  reducing discontinuities during texture mapping, tailored towards a
-  backpack-mounted data acquisition system.
+   The ABSTRACT is to be in fully-justified italicized text, at the top
+   of the left-hand column, below the author and affiliation
+   information. Use the word ``Abstract'' as the title, in 12-point
+   Times, boldface type, centered relative to the column, initially
+   capitalized. The abstract is to be in 10-point, single-spaced type.
+   Leave two blank lines after the Abstract, then begin the main text.
+   Look at previous 3DIMPVT/3DIM/3DPVT abstracts to get a feel for style and length.
 \end{abstract}
@@
 \section{Introduction}
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and as
-such, automated 3D site modeling has garnered much interest in recent
-years.
 
-The first step in automated 3d modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-calculate camera locations within an environment while simulatenously
-reconstructing the 3D structure of the environment itself. This
-problem is studied by the robotics and computer vision communities as
-the simultaneous localization and mapping (SLAM) problem, and is
-generally solved using a combination of laser range scanners, cameras,
-and inertial measurement units (IMUs).
+Please follow the steps outlined below when submitting your manuscript to
+the IEEE Computer Society Press.  This style guide now has several
+important modifications (for example, you are no longer warned against the
+use of sticky tape to attach your artwork to the paper), so all authors
+should read this new version.
 
-The aim of this paper is to present a solution for texture mapping the
-3D models generated by indoor modeling systems, with specific
-attention given to a human-operated system with higher localization
-errors and greater variance in camera locations. The paper is
-organized as follows. Section 2 provides an overview of the backpack
-modeling system from which data and examples used throughout this
-paper are from. Section 3 describes the general problem of 3D texture
-mapping and reviews existing approaches. Section 4 describes
-challenges posed by the backpack modeling system and presents our two
-approaches tailored for walls and floors/ceilings
-respectively. Section 5 compares results and presents conclusions.
-
-\section{Backpack Modeling System}
-Human-operated data acquisition systems provide unique advantages in terms of agility and portability over vehicular-mounted systems.
-Unfortunately, human-operated systems suffer from a lack of automation and stability, resulting in higher localization variance and leading to the problems discussed in Section 4.
-
-\subsection{Data Acquisition Hardware}
-The backpack modeling system from which our data was collected contains five 2D laser range scanners, two cameras, an orientation sensor, and an IMU (Should I even mention the IMU at all?).
-The laser scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter range and a 270$^{\circ}$ field of view.
-These scanners are mounted orthogonally to one another.
-The two cameras are Point Grey Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting in a 180$^{\circ}$ field of view.
-The IMU, a Honeywell HG9900, is a strap-down navigation-grade sensor which combines three ring laser gyros with bias stability of less than 0.003$^{\circ}$/hour and three precision accelerometers with bias of less than 0.245mm/sec$^{2}$.
-The HG9900 provides highly accurate measurements of all 6 DOF at 200Hz and thus serves as our ground truth for the experiments in this paper.
-]The orientation sensor (OS), an InterSense InertiaCube3, provides orientation parameters at a rate of 180Hz.
-
-\subsection{Environment Reconstruction}
-Using a combination of these sensors and multiple localization and loop-closure algorithms, the backpack is localized over its data collection period, and a 3D point cloud of our environment is constructed.
-Approximate normal vectors for each point in the point cloud are then calculated by gathering neighboring points within a small radius and running a Principal Component Analysis procedure.
-These normal vectors allow for the classification and grouping of adjacent points into structures such as walls, ceilings, floors, and staircases.
-A RANSAC algorithm is then employed to fit polygonal planes to these structured groupings of points, resulting in a fully planar model.
-This planar model, consisting of multiple 2D polygonal planes in 3D space, along with the set of images captured by the backpack's camera, can be considered the input data on which our approach runs.
-
-\subsection{Image Subsampling}
-Before beginning the texture mapping process, it is prudent to reduce the amount of potential images being considered for texture mapping each plane.
-The backpack modeling system takes 5 pictures/second from both cameras, resulting in each plane being present in (and capable of being textured mapped by) thousands of images, at a wide variance of distances and angles.
-Thus, for the sake of efficiency, it makes sense to associate each plane with a much smaller sample of images.
-When creating this subset of images for each plane, there are three criteria we keep in mind.
-First, we want such a subset of images to be capable of texturing the entirety of a plane, so as to ensure there are no holes in our final texture.
-Second, we want all our images to be taken from a relatively close distance to the plane, and at as much of a direct, head-on angle as possible.
-This ensures that the image projects squarely onto our desired plane, with minimal inclusion of other planes, and we get a texture with high resolution.
-Third, we desire an amount of overlap between the images chosen.
-This overlap helps us with preprocessing as well as postprocessing techniques discussed in Sections x and y.
-
-To meet these three criteria, we tesselate each plane into [X] triangles of [Y] size.
-For each triangle, we find all images that can be projected upon the entirety of the triangle, accounting for occlusion with other planes as well, using standard ray-polygon intersection tests.
-Of these images, we then select the best one according to the heuristic in equation X, favoring closer distances and more head-on viewing angles.
-We also enforce that no two images are chosen such that they were taken within 0.5 meters of eachother.
-This results in a greatly-reduced set of images such that each one is objectively the "best" location-wise for some number of areas on the plane, addressing the first two criteria.
-Furthermore, since cameras are only at good angles to triangles near their center of projection, images will be chosen such that there is high overlap between them.
-This process reduces the amount of candidate images for each plane from many thousands to around 50, at fairly even spacing.
-With this completed, each of our planes is associated with a sufficiently sized list of candidate images, and we are ready to begin texture mapping.
-
-\section{NOTES}
-4 Special Considerations due to BMS blabla sucky title
-The backpack modeling system described in Section 2 was designed to prioritize for texturing walls.
-As mentioned previously, the backpack contains two fisheye cameras, one aimed directly to the left of the backpack operator, and one aimed directly to the right.
-Thus, in order to texture the ceiling where the operator walked, images from both cameras must be combined.
-Even more problematic, the floor beneath the backpack is physically obscured by the operator's body, and thus must be textured by images taken from different locations.
-These problems are compounded by the fact that the operator's data acquisition path attempts to fully scan each wall, but not necessarily the entirety of a floor or ceiling.
-This means that large swaths of floors and ceilings are never walked directly over or under, and thus must be textured by sidelong images taken from further distances and at oblique angles.
-We strongly prefer head-on images because when images are projected onto a planar surface at an extreme angle, the resultant texture ends up spanning a large portion of the plane, applying low-resolution textures to areas at a great distance from the camera location.
-
-In short, these factors mean that wall planes are associated with a multitude of upright, uniform images, taken head-on and from a relatively close distance at regular intervals, while floors and ceilings are associated with images of all orientations and distances.
-This major difference suggests we employ two strategies, one tailored for each scenario.
-
-4.1 Texturing Floors and Ceilings
-
-4.2 Texturing Walls
-Since our candidate images for texturing a wall are all taken from similar distances and orientations relative to our wall, their individual "qualities" are all fairly similar.
-We don't have to worry as much about filtering out bad images; rather we seek to select some subset of our images which together form a good texture.
-
-5 Results and Analysis
-but also occlusion projection thing. door projected onto wall is fine, door projected onto floor is bad.
-
-\section{EVERYTHING AFTER HERE IS TEMPLATE STUFF}
-
-\section{Introduction}
-
-Please follow the steps outlined below when submitting your manuscript
-to the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against
-the use of sticky tape to attach your artwork to the paper), so all
-authors should read this new version.
-
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{Language}
@@
 
-By submitting a manuscript to 3DIMPVT, the authors assert that it has
-not been previously published in substantially similar
-form. Furthermore, no paper which contains significant overlap with
-the contributions of this paper either has been or will be submitted
-during the 3DIMPVT 2012 review period to {\bf either a journal} or any
-conference or any workshop.  {\bf Papers violating this condition will
-  be rejected}.
+By submitting a manuscript to 3DIMPVT, the authors assert that it has not been
+previously published in substantially similar form. Furthermore, no paper
+which contains significant overlap with the contributions of this paper
+either has been or will be submitted during the 3DIMPVT 2012 review period to
+{\bf either a journal} or any conference or any
+workshop.
+ {\bf Papers violating this condition will be rejected and a list of violating authors may be included in the proceedings.}
 
-If there are papers that may appear to the reviewers to violate this
-condition, then it is your responsibility to: (1)~cite these papers
-(preserving anonymity as described in Section 1.6 below), (2)~argue in
-the body of your paper why your 3DIMPVT paper is non-trivially
-different from these concurrent submissions, and (3)~include
-anonymized versions of those papers in the supplemental material.
+If there are papers that may appear to the reviewers
+to violate this condition, then it is your responsibility to: (1)~cite
+these papers (preserving anonymity as described in Section 1.6 below),
+(2)~argue in the body of your paper why your 3DIMPVT paper is non-trivially
+different from these concurrent submissions, and (3)~include anonymized
+versions of those papers in the supplemental material.
 
 \subsection{Paper length}
-3DIMPVT papers may be between 6 pages and 8 pages.  Overlength papers
-will simply not be reviewed.  This includes papers where the margins
-and formatting are deemed to have been significantly altered from
-those laid down by this style guide.  Note that this \LaTeX\ guide
-already sets figure captions and references in a smaller font.  The
-reason such papers will not be reviewed is that there is no provision
-for supervised revisions of manuscripts.  The reviewing process cannot
-determine the suitability of the paper for presentation in eight pages
-if it is reviewed in eleven.
+3DIMPVT papers may be between 6 pages and 8 pages. Overlength papers will simply not be reviewed.  This includes papers
+where the margins and formatting are deemed to have been significantly
+altered from those laid down by this style guide.  Note that this
+\LaTeX\ guide already sets figure captions and references in a smaller font.
+The reason such papers will not be reviewed is that there is no provision for
+supervised revisions of manuscripts.  The reviewing process cannot determine
+the suitability of the paper for presentation in eight pages if it is
+reviewed in eleven.
 
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in
-the version submitted for review.  The ruler is provided in order that
+The \LaTeX\ style defines a printed ruler which should be present in the
+version submitted for review.  The ruler is provided in order that
 reviewers may comment on particular lines in the paper without
@@
 document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the
-ruler should not change the appearance of any other content on the
-page.  The camera ready copy should not contain a ruler. (\LaTeX\
-users may uncomment the \verb'\cvprfinalcopy' command in the document
-preamble.)  Reviewers: note that the ruler measurements do not align
-well with lines in the paper --- this turns out to be very difficult
-to do well when the paper contains many figures and equations, and,
-when done, looks ugly.  Just use fractional references (e.g.\ this
-line is $097.15$), although in most cases one would expect that the
-approximate location will be adequate.
+appear on the final output pages.  The presence or absence of the ruler
+should not change the appearance of any other content on the page.  The
+camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
+the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
+note that the ruler measurements do not align well with lines in the paper
+--- this turns out to be very difficult to do well when the paper contains
+many figures and equations, and, when done, looks ugly.  Just use fractional
+references (e.g.\ this line is $095.5$), although in most cases one would
+expect that the approximate location will be adequate.
 
@@
 Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.
-Just because you didn't refer to it in the text doesn't mean some
-future reader might not need to refer to it.  It is cumbersome to have
-to use circumlocutions like ``the equation second from the top of page
-3 column 1''.  (Note that the ruler will not be present in the final
-copy, so is not an alternative to equation numbers).  All authors will
-benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.cvpr.org/doc/mermin.pdf}.
+important for readers to be able to refer to any particular equation.  Just
+because you didn't refer to it in the text doesn't mean some future reader
+might not need to refer to it.  It is cumbersome to have to use
+circumlocutions like ``the equation second from the top of page 3 column
+1''.  (Note that the ruler will not be present in the final copy, so is not
+an alternative to equation numbers).  All authors will benefit from reading
+Mermin's description of how to write mathematics.%: \url{http://www.cvpr.org/doc/mermin.pdf}.
 
@@
 Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove citations to
-one's own work---in fact it is often impossible to review a paper
-unless the previous citations are known and available.
+review.  Blind review does not mean that one must remove
+citations to one's own work---in fact it is often impossible to
+review a paper unless the previous citations are known and
+available.
 
@@
 
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that
-you are Lucy Smith, it says that you are building on her work.  If you
-are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
-and Jones show in [7]'' and at the end of the paper, include reference
-7 as you would any other cited work.
+Saying ``this builds on the work of Lucy Smith [1]'' does not say
+that you are Lucy Smith, it says that you are building on her
+work.  If you are Smith and Jones, do not say ``as we show in
+[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
+paper, include reference 7 as you would any other cited work.
 
@@
 
-  In this paper we present a performance analysis of our previous
-  paper [1], and show it to be inferior to all previously known
-  methods.  Why the previous paper was accepted without this analysis
-  is beyond me.
+   In this paper we present a performance analysis of our
+   previous paper [1], and show it to be inferior to all
+   previously known methods.  Why the previous paper was
+   accepted without this analysis is beyond me.
 
@@
 
-  In this paper we present a performance analysis of the paper of
-  Smith \etal [1], and show it to be inferior to all previously known
-  methods.  Why the previous paper was accepted without this analysis
-  is beyond me.
+   In this paper we present a performance analysis of the
+   paper of Smith \etal [1], and show it to be inferior to
+   all previously known methods.  Why the previous paper
+   was accepted without this analysis is beyond me.
 
-  [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a
-  fundamental contribution to human knowledge''.  Nature 381(12),
-  1-213.
+   [1] Smith, L and Jones, C. ``The frobnicatable foo
+   filter, a fundamental contribution to human knowledge''.
+   Nature 381(12), 1-213.
 \end{quote}
@@
 If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to
-that submission in order to explain the differences, just as you would
-if you had previously published related work.  In such cases, include
-the anonymized parallel submission~\cite{Authors12} as additional
-material and cite it as
-\begin{quote} [1] Authors. ``The frobnicatable foo filter'', F\&G 2012
-  Submission ID 324, Supplied as additional material {\tt fg324.pdf}.
+which covers similar or overlapping material, you may need to refer to that
+submission in order to explain the differences, just as you would if you
+had previously published related work.  In such cases, include the
+anonymized parallel submission~\cite{Authors12} as additional material and
+cite it as
+\begin{quote}
+[1] Authors. ``The frobnicatable foo filter'', F\&G 2012 Submission ID 324,
+Supplied as additional material {\tt fg324.pdf}.
 \end{quote}
 
-Finally, you may feel you need to tell the reader that more details
-can be found elsewhere, and refer them to a technical report.  For
-conference submissions, the paper must stand on its own, and not {\em
-  require} the reviewer to go to a techreport for further details.
-Thus, you may say in the body of the paper ``further details may be
-found in~\cite{Authors12b}''.  Then submit the techreport as
-additional material.  Again, you may not assume the reviewers will
-read this material.
+Finally, you may feel you need to tell the reader that more details can be
+found elsewhere, and refer them to a technical report.  For conference
+submissions, the paper must stand on its own, and not {\em require} the
+reviewer to go to a techreport for further details.  Thus, you may say in
+the body of the paper ``further details may be found
+in~\cite{Authors12b}''.  Then submit the techreport as additional material.
+Again, you may not assume the reviewers will read this material.
 
-Sometimes your paper is about a problem which you tested using a tool
-which is widely known to be restricted to a single institution.  For
-example, let's say it's 1969, you have solved a key problem on the
-Apollo lander, and you believe that the CVPR70 audience would like to
-hear about your solution.  The work is a development of your
-celebrated 1968 paper entitled ``Zero-g frobnication: How being the
-only people in the world with access to the Apollo lander source code
-makes us a wow at parties'', by Zeus \etal.
+Sometimes your paper is about a problem which you tested using a tool which
+is widely known to be restricted to a single institution.  For example,
+let's say it's 1969, you have solved a key problem on the Apollo lander,
+and you believe that the 3DIMPVT12 audience would like to hear about your
+solution.  The work is a development of your celebrated 1968 paper entitled
+``Zero-g frobnication: How being the only people in the world with access to
+the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
 
-You can handle this paper like any other.  Don't write ``We show how
-to improve our previous work [Anonymous, 1968].  This time we tested
-the algorithm on a lunar lander [name of lander removed for blind
-review]''.  That would be silly, and would immediately identify the
-authors. Instead write the following:
+You can handle this paper like any other.  Don't write ``We show how to
+improve our previous work [Anonymous, 1968].  This time we tested the
+algorithm on a lunar lander [name of lander removed for blind review]''.
+That would be silly, and would immediately identify the authors. Instead
+write the following:
 \begin{quotation}
 \noindent
-  We describe a system for zero-g frobnication.  This system is new
-  because it handles the following cases: A, B.  Previous systems
-  [Zeus et al. 1968] didn't handle case B properly.  Ours handles it
-  by including a foo term in the bar integral.
+   We describe a system for zero-g frobnication.  This
+   system is new because it handles the following cases:
+   A, B.  Previous systems [Zeus et al. 1968] didn't
+   handle case B properly.  Ours handles it by including
+   a foo term in the bar integral.
 
@@
 
-  The proposed system was integrated with the Apollo lunar lander, and
-  went all the way to the moon, don't you know.  It displayed the
-  following behaviours which show how well we solved cases A and B:
-  ...
+   The proposed system was integrated with the Apollo
+   lunar lander, and went all the way to the moon, don't
+   you know.  It displayed the following behaviours
+   which show how well we solved cases A and B: ...
 \end{quotation}
 As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you
-as the authors.  A reviewer might think it likely that the new paper
-was written by Zeus \etal, but cannot make any decision based on that
-guess.  He or she would have to be sure that no other authors could
-have been contracted to solve problem B.
+reads better than the first version, and does not explicitly name you as
+the authors.  A reviewer might think it likely that the new paper was
+written by Zeus \etal, but cannot make any decision based on that guess.
+He or she would have to be sure that no other authors could have been
+contracted to solve problem B.
 
@@
 \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
+   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
 \end{center}
    \caption{Example of caption.  It is set in Roman so that mathematics
-    (always set in Roman: $B \sin A = A \sin B$) may be included
-    without an ugly clash.}
+   (always set in Roman: $B \sin A = A \sin B$) may be included without an
+   ugly clash.}
 \label{fig:long}
@@
 The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The
-provided \verb'\eg' macro takes care of this.
+sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
+\verb'\eg' macro takes care of this.
 
-When citing a multi-author paper, you may save space by using ``et
-alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}''
-is a complete word.)  However, use it only when there are three or
-more authors.  Thus, the following is correct: `` Frobnication has
-been trendy lately.  It was introduced by Alpher~\cite{Alpher02}, and
-subsequently developed by Alpher and
-Fotheringham-Smythe~\cite{Alpher03}, and Alpher
-\etal~\cite{Alpher04}.''
+When citing a multi-author paper, you may save space by using ``et alia'',
+shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
+However, use it only when there are three or more authors.  Thus, the
+following is correct: ``
+   Frobnication has been trendy lately.
+   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
+   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
 
-This is incorrect: ``... subsequently developed by Alpher
-\etal~\cite{Alpher03} ...''  because reference~\cite{Alpher03} has
-just two authors.  If you use the \verb'\etal' macro provided, then
-you need not worry about double periods when used at the end of a
-sentence as in Alpher \etal.
+This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
+because reference~\cite{Alpher03} has just two authors.  If you use the
+\verb'\etal' macro provided, then you need not worry about double periods
+when used at the end of a sentence as in Alpher \etal.
 
@@
 
-% ------------------------------------------------------------------------
+%------------------------------------------------------------------------
 \section{Formatting your paper}
 
-All text must be in a two-column format. The total allowable width of
-the text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches
-(22.54 cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide,
-with a $\frac{5}{16}$ inch (0.8 cm) space between them. The main title
-(on the first page) should begin 1.0 inch (2.54 cm) from the top edge
-of the page. The second and following pages should begin 1.0 inch
-(2.54 cm) from the top edge. On all pages, the bottom margin should be
-1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5
-\times 11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13
-cm) from the bottom edge of the page.
+All text must be in a two-column format. The total allowable width of the
+text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
+cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
+$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
+first page) should begin 1.0 inch (2.54 cm) from the top edge of the
+page. The second and following pages should begin 1.0 inch (2.54 cm) from
+the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
+cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
+paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
+page.
 
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{Margins and page numbering}
 
-All printed material, including text, illustrations, and charts, must
-be kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8
-inches (22.54 cm) high.
+All printed material, including text, illustrations, and charts, must be kept
+within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
+high.  Page numbers should be in footer with page numbers, centered and .75
+inches from the bottom of the page and make it start at the correct page
+number rather than the 4321 in the example.  To do this fine the line (around
+line 23)  
+\begin{verbatim}
+%\ifcvprfinal\pagestyle{empty}\fi
+\setcounter{page}{4321}
+\end{verbatim}
+where the number 4321 is your assigned starting page.
 
-% -------------------------------------------------------------------------
+Make sure the first page is numbered by commenting out the first page being
+empty on line 46
+\begin{verbatim}
+%\thispagestyle{empty}
+\end{verbatim}
+
+%-------------------------------------------------------------------------
 \subsection{Type-style and fonts}
 
-Wherever Times is specified, Times Roman may also be used. If neither
-is available on your word processor, please use the font closest in
+Wherever Times is specified, Times Roman may also be used. If neither is
+available on your word processor, please use the font closest in
 appearance to Times to which you have access.
 
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge
-of the first page. The title should be in Times 14-point, boldface
-type.  Capitalize the first letter of nouns, pronouns, verbs,
-adjectives, and adverbs; do not capitalize articles, coordinate
-conjunctions, or prepositions (unless the title begins with such a
-word). Leave two blank lines after the title.
+MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
+the first page. The title should be in Times 14-point, boldface type.
+Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
+adverbs; do not capitalize articles, coordinate conjunctions, or
+prepositions (unless the title begins with such a word). Leave two blank
+lines after the title.
 
 AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is
-to be followed by two blank lines.
+and printed in Times 12-point, non-boldface type. This information is to
+be followed by two blank lines.
 
@@
 Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should
-be centred.
+Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
 
@@
 should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
+with one blank line before.
 
@@
 should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a
-third-order heading (we discourage it), use 10-point Times, boldface,
-initially capitalized, flush left, preceded by one blank line,
-followed by a period and your text on the same line.
+with one blank line before, and one after. If you require a third-order
+heading (we discourage it), use 10-point Times, boldface, initially
+capitalized, flush left, preceded by one blank line, followed by a period
+and your text on the same line.
 
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{Footnotes}
@@
 Please use footnotes\footnote {This is what a footnote looks like.  It
-  often distracts the reader from the main flow of the argument.}
-sparingly.  Indeed, try to avoid footnotes altogether and include
-necessary peripheral observations in the text (within parentheses, if
-you prefer, as in this sentence).  If you wish to use a footnote,
-place it at the bottom of the column on the page on which it is
-referenced. Use Times 8-point type, single-spaced.
+often distracts the reader from the main flow of the argument.} sparingly.
+Indeed, try to avoid footnotes altogether and include necessary peripheral
+observations in
+the text (within parentheses, if you prefer, as in this sentence).  If you
+wish to use a footnote, place it at the bottom of the column on the page on
+which it is referenced. Use Times 8-point type, single-spaced.
 
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{References}
@@
 
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{Illustrations, graphs, and photographs}
 
-All graphics should be centered.  Please ensure that any point you
-wish to make is resolvable in a printed copy of the paper.  Resize
-fonts in figures to match the font in the body text, and choose line
-widths which render effectively in print.  Many readers (and
-reviewers), even of an electronic copy, will choose to print your
-paper in order to read it.  You cannot insist that they do otherwise,
-and therefore must not assume that they can zoom in to see tiny
-details on a graphic.
+All graphics should be centered.  Please ensure that any point you wish to
+make is resolvable in a printed copy of the paper.  Resize fonts in figures
+to match the font in the body text, and choose line widths which render
+effectively in print.  Many readers (and reviewers), even of an electronic
+copy, will choose to print your paper in order to read it.  You cannot
+insist that they do otherwise, and therefore must not assume that they can
+zoom in to see tiny details on a graphic.
 
 When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the figure width as a multiple
-of the line width as in the example below {\small\begin{verbatim}
+\verb+\includegraphics+, and to specify the  figure width as a multiple of
+the line width as in the example below
+{\small\begin{verbatim}
    \usepackage[dvips]{graphicx} ...
@@
 
-% -------------------------------------------------------------------------
+%-------------------------------------------------------------------------
 \subsection{Color}
 
-Color is valuable, and will be visible to readers of the electronic
-copy.  However ensure that, when printed on a monochrome printer, no
-important information is lost by the conversion to grayscale.
+Color is valuable, and will be visible to readers of the electronic copy.
+However ensure that, when printed on a monochrome printer, no important
+information is lost by the conversion to grayscale.
 
-% ------------------------------------------------------------------------
+%------------------------------------------------------------------------
 \section{Final copy}
 
-You must include your signed IEEE copyright release form when you
-submit your finished paper. We MUST have this form before your paper
-can be published in the proceedings.
+You must include your signed IEEE copyright release form when you submit
+your finished paper. We MUST have this form before your paper can be
+published in the proceedings.
 
-% Please direct any questions to the production editor in charge of
-% these proceedings at the IEEE Computer Society Press: Phone (714)
-% 821-8380, or Fax (714) 761-1784.
-
-{\small \bibliographystyle{ieee} \bibliography{egbib} }
+{\small
+\bibliographystyle{ieee}
+\bibliography{egbib}
+}
 

### 2012-06-15 isvc_submission_latex/_region_.tex
added michaels draft and new draft also

\message{ !name(isvc_submission.tex)}%last updated in April 2002 by Antje Endemann

\documentclass[runningheads]{llncs}
%In order to omit page numbers and running heads
%please use the following line instead of the first command line:
%\documentclass{llncs}.
%Furthermore change the line \pagestyle{headings} to
%\pagestyle{empty}.

\input{psfig.sty}

\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath}

\begin{document}

\message{ !name(isvc_submission.tex) !offset(-3) }

\pagestyle{headings}
%In order to omit page numbers and running heads
%please change this line to
%\pagestyle{empty}
%and change the first command line too, see above.

\mainmatter

\title{Texturing Long Planar Surfaces with Imprecise Camera Poses for Indoor 3D Modeling}

\titlerunning{Lecture Notes in Computer Science}
\maketitle

\begin{abstract}
Automated 3D modeling of building interiors is useful in
applications such as virtual reality and environment mapping.
Texture mapping walls is an important step in visualizing the results of an indoor 3D modeling system. Methods to localize the camera in the 3D scene often are not pixel accurate, meaning that when multiple images are used for texture mapping there are seams and discontinuities between these images. Several approaches to this problem have been proposed but each suffer from a distinct problem of error accumulation for long chains of images, such as those from a long corridor. We propose a new approach to texture mapping planar surfaces that eliminates most discontinuities between images but does not suffer from error accumulation for long chains. We validate this approach using images from several long hallways with data generated by a human operated backpack 3D indoor modeling system.

\end{abstract}

\section{Introduction}
\label{sec:intro}

Three-dimensional modeling of indoor environments has a variety of applications such as training and simulation for disaster management, virtual heritage conservation, and mapping of hazardous sites. Manual construction of these models can be time consuming, and as such, automated 3D site modeling has garnered much interest in recent years.

An indoor modeling system must first be able to simultaneously estimate the camera's location within an environment and the 3D structure of the environment. This problem is studied by the robotics and computer vision communities as the simultaneous localization and mapping (SLAM) problem. It is usually solved with the aid of laser range scanners, cameras, and inertial measurement units (IMUs) that survey the environment in a vehicle or human-operated backpack \cite{liu2010indoor,chen2010indoor}. The devices, along with various localization algorithms, can generate a point cloud which is then processed by a surface reconstruction algorithm to infer structure such as walls and ceilings. Finally, the reconstructed surfaces are textured using captured images and the estimated camera position for each photo.

Though the localization errors resulting from these laser based 
algorithms are quite low even in these complex environments,
when the resulting recovered pose is used to texture
map camera imagery onto the resulting 3D triangular mesh
models, there is significant misalignment between successive
images used to texture map neighboring triangles. This implies
that the scan matching based localization algorithms are not
pixel accurate. The misalignment problem is the focus of this paper.

Previous work on this problem proposed an
image based approach in which the pose from laser scan matching
based localization is refined using camera imagery \cite{liu2010indoor}. Traditional image stitching approaches using image correspondences have also been tried \cite{brown2007automatic}. However both these approaches suffer from error accumulation when used for long chains, for example 20 or 40 images. These long chains of images are common in indoor modeling when buildings have long corridors. Though image stitching can produce excellent results in some cases, it breaks down when there are very few features in the overlapping portions of the images, such as on empty walls. The probability of such a breakdown increases for longer chains of images, as does the error accumulation.

We separate the texture mapping problem into two independent subproblems: camera localization refinement and image selection. To refine the camera localization we use an image-based approach (SIFT matches \cite{lowe1999object}) to shift the cameras right, left, up, or down on the plane. The direction and the amount to shift each image is determined globally within each plane using a linear least squares approach. For image selection, we choose a subset of the available images that covers the plane while minimizing the appearence of seams or discontinuities in the final mosaic. We present two approaches to this. The first is a greedy heuristic that covers the plane by iteratively selecting the image that will cover the largest number of empty pixels on the plane. The second approach specifies a cost function, such as the total image energy in the vicinity of the seams, and chooses images that cover the plane while minimizing this cost. The second approach can be done efficiently using dynamic programming when the images overlap in a directed acyclic graph (DAG) structure from left to right, as they do in long hallways using our system.

The approach presented here gracefully handles long chains of images without error accumulation, which we demonstrate on data from our human operated backpack 3D indoor modeling system \cite{chen2010indoor}. This paper is organized as follows. Section \ref{sec:corridors} outlines the problem of texture mapping for indoor 3D modeling and demonstrate existing approaches. Section \ref{sec:approach} describes our approach. Section \ref{sec:results} shows results using data generated from our backpack system and presents conclusions.

%\section{Indoor 3D Modeling Backpack System}
%\label{sec:backpack}

%Our indoor modeling system consists of a backpack which has been specially equipped with laser scanners and three cameras pointed in orthogonal directions. The setup is shown in Figure 1.

\section{Texture Mapping Planes}
\label{sec:corridors}

%Well really I want to tell it like this. Think naive. This causes seams. Related by homography so we try image stitching. But here's the problem. Breaks in the chain, and error accumulation. So then comes the graph-based optimization. But that is 3D and it has this error accumulation. So we need something that solves the problem globally. And we need something that can handle "breaks in the chain" gracefully. So think back to when we did it do it naively though (triangles and map images to triangles) then there isn't this problem of error accumulation. Everything gets reset at each triangle so there is no error progpogation. But then we're back to the problem that there are seams because we're not aligning images nearby one another. What we're going to try in the next section is similar to the graph-based optimization but we're doing it in 2D. We're also going to add an intellegent image selection.

\begin{figure}
\centering
\includegraphics[height=2in]{Projection.pdf}
\caption{The plane is specified in 3D space by the four corners $C_1$ to $C_4$. Images are related to the plane through the camera matrices $P_{1..M}$. }
%\caption{The plane is specified in 3D space by the four corners $C_1$ to $C_4$. Images are related to the plane through the camera matrices $P_{1..M}$. For example, the 3D point X in the world coordinate system is related to the image point x shown in the figure as $x = P_i X$.}
\label{fig:projection}
\end{figure}

The geometry of the the texture mapping problem for indoor 3D modeling is shown in Figure 1. We are given a set of $M$ images. Each image has a camera matrix $P_i$ for $i=1..M$, which translates a point in the world coordinate system to a point in image $i$'s coordinates. A camera matrix $P_i$ is composed of the camera's intrinsic parameters, such as focal length and image center, as well as the extrinsic parameters which specify the rotation and translation of the camera center's position with respect to the world coordinates at the time that image $i$ was taken. These extrinsic parameters are determined by the localization hardware and algorithms as part of the indoor modeling system. A point $X$ on the plane can be related to its corresponding pixel $x$ in image $i$ through the following equation:

\[
x=project(P_iX)
\]

where 
\[X = \begin{pmatrix} x \\ y \\ z \end{pmatrix} \textrm{ and } project(X) = \begin{pmatrix} x/z \\ y/z \end{pmatrix}
\]

We are also given a plane generated by the surface reconstruction system, which is to be texture mapped by these images. The plane is defined by four corner points $C_1$ to $C_4$ in world coordinates and a normal vector indicating the front facing side of the plane. The challenge is to texture the plane using these images, while eliminating any discontinuities or seams that would suggest that the plane was not composed of a single continuous image.

\subsection{Best-Candidate Mapping}

\begin{figure}
\centering
\includegraphics[height=1.5in]{naive.png}
\caption{The result of naive texture mapping based on the imprecise camera matrices estimated by the localization system.}
\label{fig:naive}
\end{figure}

Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate, one can texture map the plane simply by discretizing the plane into tiles or triangles and texturing each tile or triangle seperately. It makes sense to texture each tile or triangle by selecting a best candidate image. This is usually the nearest and/or most direct facing image to the tile or triangle.

As Figure \ref{fig:naive} demonstrates, the best candidate mapping leads to significant misalignment between successive tiles. This suggests that while the errors in the localization system are quite low, they are not pixel accurate. For photorealistic texture mapping, either the camera matrices need to be refined such that the localization is pixel accurate, or image stitching techniques need to be applied to provide this illusion. The following are two existing techniques to solve this problem.

\subsection{Image Mosaicing}

\begin{figure}
\centering
\includegraphics[width=4in]{panoMy.jpg}
\caption{Image mosaicing. }
\label{fig:mosaic}
\end{figure}

When images are taken of a plane from arbitrary overlapping positions, they are related by homography \cite{hz}. Thus, existing homography-based image mosaicing algorithms are applicable \cite{brown2007automatic}. However, errors can compound when long chains of images are mosaiced together using these approaches. For example, a pixel in the $n$th image in the chain must be translated into the first image's coordinates by multiplying by the $3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these homography matrices is propagated to all further images until the chain is broken. For some chains of images this can happen almost immediately due to erroneous correspondence matches and the resulting image mosaic is grossly misshapen.

Figure \ref{fig:mosaic} shows the output of the AutoStitch software package which does homography-based image mosaicing. This plane is nearly a best-case scenerio with many features spread uniformly across it. Even so, the mosaicing produces errors that causes straight lines to appear as waves on the plane. This image was generated after careful hand tuning. Many planes that had fewer features simply failed. This led us to conclude that image mosaicing alone is not enough to reliably texture map our indoor 3D modeling dataset.

\subsection{Image-Based 3D Localization Refinement}

\begin{figure}
\centering
\includegraphics[width=3in]{Graph_crop.pdf}
\caption{Using the graph-based localization refinement algorithm from [11] suffers from the problem of compounding errors. }
\label{fig:graph}
\end{figure}

Another approach is to refine the camera matrices using image correspondences to guide the process. Each camera matrix has 6 degrees of freedom. Previous work attempted to refine the camera matrix by solving a non-linear optimization problem \cite{liu2010indoor}. This process is carried out at the same time as the laser based backpack localization and is therefore specific to the system in \cite{liu2010indoor,chen2010indoor}. Unfortunately, this approach suffers from a similar error propagation problem shown in Figure \ref{fig:graph}. In this work we also refine the placement of images using image correspondences. However, we do so in two dimensions on the plane where as this previous work did so over all 6 degrees of freedom. Refining in two dimensions on the plane is less flexible in that it cannot fix certain projection errors. Emperically we find that it avoids the error propagation problem.

\section{Our Approach}
\label{sec:approach}

Our approach can be summarized as follows. First we place all the images on the plane using the imprecise camera matrices given to us by the localization algorithm. This is done using the naive approach outlined in Section 2.1. This naive placement looks bad because the camera matrices are not pixel accurate. Our first challenge is to improve the placement of these images either by fixing the camera's localization in 3 dimeensions, or through 2 dimensional image processing techniques. We choose to use image processing techniques. SIFT matches are found between overlapping images. The imprecise localization means that matching SIFT features coming from two different images may not map to the same location on the plane. To fix this, we shift the images left, right, up, or down in such a way to maximize the agreement among images for each SIFT match.

The next problem is image selection. The cameras on the backpack system produce far more images than are necessary to completely cover the plane. For example, a long hallway may have several hundereds of images when just 10 or 20 would suffice. We would prefer to use fewer images because this leads to fewer seams between images. However, we'd also like to make sure we are using good images that were taken perpendicular to the plane, for example, and whose seams fall in unimportant areas such as blank walls. In this section we outline two approaches to solving the image selection problem: a greedy heuristic solution that can work on any plane, and a dynamic programming formulation requires images overlap in a DAG structure.

\subsection{Preprocessing}
As a starting point, we naively texture map the plane using the given imprecise camera matrices for each image in the set. This is done by discretizing the plane into an arbitrary density of pixels and projecting each pixel into the image plane using the estimated camera matrix $P_i$. We later intend to shift some of these projected images around on the plane and remove some others. Therefore, each image is stored intact in its own data structure so that it can later be merged with the other images on the plane. We use a Hough transform to rotate the projected images such that vertical lines are pointing directly upwards. This can be effective for indoor modeling, since many indoor scenes contain strong vertical lines from features such as doors, wall panels, or rectangular frames.

\subsection{Localization Refinement}

The camera matrices generated by the localization algorithm are imprecise so the images are misaligned. To fix this, we choose to fix the locations in 2D. First we find corresponding points between all pairs of overlapping images using SIFT matches \cite{lowe1999object}. An illustration of this is given in Figure \ref{fig:matches}. The SIFT matches allow us to determine the correct $x$ and $y$ distances between two images on the plane. We already have an estimate of the $x$ and $y$ distances between the two images which was given by the localization algorithms. Soon we will compare the original estimates to the SIFT-based distances and use this to improve the quality of the image locations.

\subsubsection{Robust SIFT Distances using RANSAC}

First we need to ensure that the SIFT-based distances are reliable. Since SIFT matches frequently include outliers, the RANSAC framework \cite{fischler1981random} is used for a robust estimate of the $x$ and $y$ distances between the two images. The RANSAC framework will attempt to build a consensus among the SIFT matches about what the true $x$ and $y$ distance is between the two images while ignoring the influence of outliers that may skew the results. The framework handles the consensus-building machinery, and only requires that two functions be specified: the fitting function and the distance function. These functions are called for random subsets of the SIFT matches until the best set of inliers is found. For this application, the fitting function simply finds the average distance between matches. If the matches are exactly correct and the image is frontal and planar then the distances for various SIFT feature matches should be the same. Our distance function for a pair of points is the difference between those points' SIFT match distance and the average distance computed by the fitting function. We specified a 10 pixel outlier threshold to the framework. This means that a SIFT match is labeled as an outlier if its $x$ and $y$ distance is not within 10 pixels of the average distance computed by the fitting function.

\subsubsection{Refining Image Positions using Least Squares}

There are a total of $M^{2}$ possible pairs of images, however we can only measure distances between images that overlap at SIFT feature points. Given these distances and the original image location estimates, we solve a least squares problem ($\textrm{min}_{\beta} ||\beta X - y||_2^2 $) to estimate the correct location of the images on the plane. The vector $\beta$ of unknowns are the correct $x$ and $y$ locations of each image on the plane from $1 \dots M$. Finding the correct $x$ and $y$ locations are independent from one another so we will only consider the $x$ locations:

% Draw least squares problem here.

\[\beta =
 \begin{pmatrix}
  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
 \end{pmatrix}
\]

The matrix $X$ is constructed with one row for each pair of images with measured distances produced by the SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the columns corresponding to the two images in the pair. For example, the matrix below indicates that we generated a SIFT-based distance between images 1 and 2, images 1 and 3, images 2 and 3, etc.

\[
 X =
 \begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
   0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\ 
  0 & 0 & 0 & \cdots & -1 & 1 \\ 
  1 & 0 & 0 & \cdots & 0 & 0 \\ 
 \end{pmatrix}
\]

If only relative distances between images are included then there is no way to determine the absolute location of any of the images and the matrix becomes rank deficient. To fix this we choose the first image to serve as the anchor for the rest, meaning all the absolute distances are based on its original location. This is done by adding a row with a $1$ in the first column and the rest zeros.

Finally, the observation vector $y$ is constructed using the SIFT-based distances generated earlier in the matching stage. The distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based distances. The last element in the observation vector is the original location of the first image determined by the localization algorithm.

\[
y^T = 
 \begin{pmatrix}
  d_{1,2}, & d_{1,3}, & d_{2,3}, & \hdots & d_{N-2,N-1}, & d_{N-1,N}, &  x_1
 \end{pmatrix}
\]

The $\beta$ that minimizes  $||\beta X - y||_2^2$ tells us a set of image locations on the plane that best honors all the SIFT-based distance measurements between images. A similar problem is solved for the $y$ dimension. In practice there are often cases where there is a break in the chain of images, meaning that no SIFT matches were found between one segment of the plane and another. In this case we add rows to the $X$ matrix and observations to the $y$ vector that contain the original $x$ and $y$ distance estimates generated by the localization algorithm. Another way to do this is to add rows for all neighboring pairs of images and solve a weighted least squares problem where the SIFT distances are given a higher weight i.e. 1, and the distances generated by the localization algorithm are given a smaller weight i.e. 0.01.

%Given these corresponding points, we can align the neighboring projected images by setting the pixel location of the right projected image based on the pixel location of the left projected image and the average distance between the SIFT matches. Note that we are solving for two variables: the x and y coordinates of the right projected image's pixel location on the plane.  Intuitively speaking, we are taking pairs of images and sliding the right image horizontally and vertically until the corresponding points overlap. If no matches can be found between neighboring images, they are left in their originally estimated locations. 
%
%\begin{figure}
%\begin{lstlisting}
%% RANSAC fitting function
%function shift = fit_shift(x1, x2)
%    % Average distance between matches
%    shift = mean(x1-x2,2); 	
%
%% RANSAC distance function
%function [inliers, shift] = 
%         shiftdist(shift, x1, x2, t);
%    % Find the shift error for each match
%    shiftmat = repmat(shift,1,size(x2,2));
%    err = sum(abs(x1-(x2+shiftmat)));
%    % Inliers are those with error less than t
%    inliers = find(abs(err) < t);
%
%\end{lstlisting}
%\caption{Fitting function and distance function for RANSAC.}
%\end{figure}

\subsection{Image Selection}

The backpack system produces images at a much faster rate than is necessary to fully texture map all surfaces. Many of these images can be discarded because the range they cover is also covered by other images in the set. In fact, our system discards images as a preprocessing step that are either not directly facing the plane or are beyond a certain threshold distance from each plane. Beyond this, it can be advantageous to throw away redundant images at this stage because fewer images generate fewer seams and therefore fewer potential visual artifacts from misalignment. We describe two methods for image selection. The first is a greedy heuristic that makes no assumption about the plane or the images. The second method assumes that the images overlap in a DAG structure and employs dynamic programming to minimize a specific cost associated with a selection of images.

\subsubsection{Greedy Heuristic}

We begin with an empty plane and a set of $M$ images. The image that covers the largest number of pixels on the plane is chosen and copied to the plane. The pixels covered by that image are then considered to be covered. Next, the image that covers the largest number of uncovered pixels is chosen. It is copied to the plane as well. If it overlaps with any covered pixels then the image is blended according to the process described in Section 4.1.2. This process continues until the plane is completely covered.

\subsubsection{Cost Functions}

The greedy algorithm will cover the plane, if possible, and will tend toward using fewer images. However, the solution is not optimal with respect to any image-based cost. We may be interested in covering the plane while minimizing the sum of squared pixel differences of the blended seam regions. This would encourage seams to be placed either in featureless areas, such as blank walls, or in areas in which the images are very well aligned. Another possible cost function is edge energy, i.e. the sum of the smoothed gradient of the blended seam regions. This would encourage seams to be placed in featureless areas even more than the sum of squared pixel difference cost function.

\subsubsection{Dynamic Programming}

\begin{figure}
\centering
\includegraphics[width=3in]{DynProg.pdf}
\caption{Image Selection is done by constructing a graph of sorted images. Then we solve a shortest path problem where the edge weights represent the cost of a seam between two overlapping images.}
\label{fig:DynProg}
\end{figure}

In the general case, finding the optimal subset of images with regard to the cost functions appears to have exponential complexity in the number of images. For this reason, we did not attempt this approach to image selection. However, if the images overlap only in one direction, as they do in long hallways, we can construct a DAG from the overlapping images and solve a simple shortest path problem to find an optimal subset of images with regard to the cost functions.

Figure \ref{fig:DynProg} demonstrates the construction of a DAG from overlapping images of a long hallway. Images are sorted by location (e.g. left to right) and become nodes in a graph. Edges are placed in the graph between images that overlap. The weights of these edges are determined by a cost function, such as image energy, or the sum of squared pixel differences between the two images in the seam region. Next, we solve a shortest path problem from the first node in the graph to the last node. This provides a set of images that completely covers the plane, but minimizes the cost of the seams produced. Note that this only works when all the images completely cover one dimension. In this case the vertical dimension of the plane is covered by all images.

\subsection{Blending}

The steps above eliminate visual artifacts from misalignment, but there still are obvious discontinuities in brightness between images resulting from differences in lighting. This problem has been successfully addressed in previous work using an alpha blending technique in which the pixel intensities in overlapping images are blended proportional to the pixel's location in the image \cite{liu2010indoor}. We use a similar technique to improve the visual quality of our results. In the small area where images overlap, there is a linear weighting function in the horizontal direction that interpolates between the left image and the right, providing a gradual transition between images. The final location corrected, subsampled, and blended image is shown in Figure \ref{fig:window4}.

\section{Results}
\label{sec:results}

\section{Conclusions and Future Work}
\label{sec:results}

\bibliographystyle{IEEEbib}
\small
\bibliography{strings,refs}

\message{ !name(isvc_submission.tex) !offset(-5) }

\end{document}

### 2012-06-17 3dimpvt/paper.tex
updating

@@
 \begin{abstract}
-  Automated 3D modeling of building interiors is used in applications
-  such as virtual reality and environment mapping. Texture mapping
-  these models accurately is vital towards visualizing the data
+  Automated 3D modeling of building interiors is useful in applications
+  such as virtual reality and environment mapping. Accurate texture
+  mapping of these models is vital towards visualizing the data
   gathered by modeling systems and increases overall usability. The
-  localization of cameras in 3D scenes often suffers from
-  inaccuracies, resulting in visible discontinuties when different
-  images are projected onto a texture. Previous approaches at
-  minimizing these discontinuities suffer from error accumulation when
-  stitching together multiple images and do not robustly handle wide
-  ranges of camera locations and angles. We propose two approaches for
-  reducing discontinuities during texture mapping, tailored towards a
-  backpack-mounted data acquisition system.
+  localization of cameras in 3D scenes with respect to model surfaces
+  often suffers from inaccuracies, resulting in visible discontinuties
+  when different images are directly projected onto a plane for
+  texturing. Previous approaches at minimizing these discontinuities
+  suffer from error accumulation when stitching together multiple
+  images and do not robustly handle a wide range of camera locations
+  and angles. We propose two approaches for reducing discontinuities
+  during texture mapping, tailored towards a backpack-mounted data
+  acquisition system.
 \end{abstract}
@@
 errors and greater variance in camera locations. The paper is
-organized as follows. Section 2 provides an overview of the backpack
-modeling system from which data and examples used throughout this
-paper are from. Section 3 describes the general problem of 3D texture
-mapping and reviews existing approaches. Section 4 describes
-challenges posed by the backpack modeling system and presents our two
-approaches tailored for walls and floors/ceilings
-respectively. Section 5 compares results and presents conclusions.
+organized as follows. Section \ref{sec:backpackSystem} provides an
+overview of the backpack modeling system from which data and examples
+used throughout this paper are from. Section
+\ref{sec:textureMappingOverview} describes the general problem of 3D
+texture mapping and reviews existing approaches. Section
+\ref{sec:textureMappingMethods} describes challenges posed by the
+backpack modeling system and presents our two approaches tailored for
+walls and floors/ceilings respectively. Section \ref{sec:results} compares results and
+presents conclusions.
 
 \section{Backpack Modeling System}
-Human-operated data acquisition systems provide unique advantages in terms of agility and portability over vehicular-mounted systems.
-Unfortunately, human-operated systems suffer from a lack of automation and stability, resulting in higher localization variance and leading to the problems discussed in Section 4.
+\label{sec:backpackSystem}
+Human-operated data acquisition systems provide unique advantages over vehicular-mounted systems in
+terms of agility and portability. Unfortunately, human-operated systems also suffer from a lack of
+automation and stability, resulting in higher localization variance
+and leading to the problems discussed in Section 4.
 
 \subsection{Data Acquisition Hardware}
-The backpack modeling system from which our data was collected contains five 2D laser range scanners, two cameras, an orientation sensor, and an IMU (Should I even mention the IMU at all?).
-The laser scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter range and a 270$^{\circ}$ field of view.
-These scanners are mounted orthogonally to one another.
-The two cameras are Point Grey Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting in a 180$^{\circ}$ field of view.
-The IMU, a Honeywell HG9900, is a strap-down navigation-grade sensor which combines three ring laser gyros with bias stability of less than 0.003$^{\circ}$/hour and three precision accelerometers with bias of less than 0.245mm/sec$^{2}$.
-The HG9900 provides highly accurate measurements of all 6 DOF at 200Hz and thus serves as our ground truth for the experiments in this paper.
-]The orientation sensor (OS), an InterSense InertiaCube3, provides orientation parameters at a rate of 180Hz.
+The backpack modeling system from which our data was collected
+contains five 2D laser range scanners, two cameras, an orientation
+sensor, and an IMU. The laser
+scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter
+range and a 270$^{\circ}$ field of view. These scanners are mounted
+orthogonally to one another. The two cameras are Point Grey
+Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting
+in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a
+strap-down navigation-grade sensor which combines three ring laser
+gyros with bias stability of less than 0.003$^{\circ}$/hour and three
+precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The
+HG9900 provides highly accurate measurements of all 6 DOF at 200Hz, and the orientation sensor (OS), an InterSense InertiaCube3,
+provides orientation parameters at a rate of 180Hz.
+Wearing this backpack, a human operator then takes great care to walk a path such that every wall in the desired indoor environment is passed and scanned lengthwise at least once.
 
 \subsection{Environment Reconstruction}
-Using a combination of these sensors and multiple localization and loop-closure algorithms, the backpack is localized over its data collection period, and a 3D point cloud of our environment is constructed.
-Approximate normal vectors for each point in the point cloud are then calculated by gathering neighboring points within a small radius and running a Principal Component Analysis procedure.
-These normal vectors allow for the classification and grouping of adjacent points into structures such as walls, ceilings, floors, and staircases.
-A RANSAC algorithm is then employed to fit polygonal planes to these structured groupings of points, resulting in a fully planar model.
-This planar model, consisting of multiple 2D polygonal planes in 3D space, along with the set of images captured by the backpack's camera, can be considered the input data on which our approach runs.
+Using data gathered by the onboard sensors and multiple localization and
+loop-closure algorithms, the backpack is localized over its data
+collection period, and a 3D point cloud of the environment is
+constructed. Approximate normal vectors for each point in the point
+cloud are then calculated by gathering neighboring points within a
+small radius and processing them with Principal Component Analysis. These normal vectors allow for the classification and
+grouping of adjacent points into structures such as walls, ceilings,
+floors, and staircases. A RANSAC algorithm is then employed to fit
+polygonal planes to these structured groupings of points, resulting in
+a fully planar model. This planar model, consisting of multiple 2D
+polygonal planes in 3D space, must then be textured by some subset of the images captured by
+the backpack's camera.
 
-\subsection{Image Subsampling}
-Before beginning the texture mapping process, it is prudent to reduce the amount of potential images being considered for texture mapping each plane.
-The backpack modeling system takes 5 pictures/second from both cameras, resulting in each plane being present in (and capable of being textured mapped by) thousands of images, at a wide variance of distances and angles.
-Thus, for the sake of efficiency, it makes sense to associate each plane with a much smaller sample of images.
-When creating this subset of images for each plane, there are three criteria we keep in mind.
-First, we want such a subset of images to be capable of texturing the entirety of a plane, so as to ensure there are no holes in our final texture.
-Second, we want all our images to be taken from a relatively close distance to the plane, and at as much of a direct, head-on angle as possible.
-This ensures that the image projects squarely onto our desired plane, with minimal inclusion of other planes, and we get a texture with high resolution.
-Third, we desire an amount of overlap between the images chosen.
-This overlap helps us with preprocessing as well as postprocessing techniques discussed in Sections x and y.
+\subsection{Plane Generalization}
+The planes we aim to texture are output by the surface reconstruction
+algorithm briefly explained in Section \ref{sec:backpackSystem}.
+These planes have arbitrary orientation and include simple rectangular
+walls as well as complicated floor planes defined by over 100
+vertices. In order to abstract out the difficulties of dealing with
+complex geometry, a minimal bounding box is constructed for each
+plane, and used as the target for texture mapping. Since the final
+texture created will be a standard rectangular image regardless, we
+can simply leave the area between the plane boundary and its bounding
+box untextured, and make sure to store the plane's original vertices
+for future retrieval.
 
-To meet these three criteria, we tesselate each plane into [X] triangles of [Y] size.
-For each triangle, we find all images that can be projected upon the entirety of the triangle, accounting for occlusion with other planes as well, using standard ray-polygon intersection tests.
-Of these images, we then select the best one according to the heuristic in equation X, favoring closer distances and more head-on viewing angles.
-We also enforce that no two images are chosen such that they were taken within 0.5 meters of eachother.
-This results in a greatly-reduced set of images such that each one is objectively the "best" location-wise for some number of areas on the plane, addressing the first two criteria.
-Furthermore, since cameras are only at good angles to triangles near their center of projection, images will be chosen such that there is high overlap between them.
-This process reduces the amount of candidate images for each plane from many thousands to around 50, at fairly even spacing.
-With this completed, each of our planes is associated with a sufficiently sized list of candidate images, and we are ready to begin texture mapping.
+\subsection{Image Association}
+\label{sec:imageAssociation}
+In order to speed up the texture mapping process, it is prudent to
+reduce the amount of potential images being considered for texture
+mapping each plane. The backpack modeling system takes 5
+pictures/second from both cameras, resulting in each plane being
+present in (and capable of being textured mapped by) thousands of
+images, at a wide range of distances and angles. Thus, for the sake
+of efficiency, it makes sense to associate each plane with a much
+smaller list of images. When creating this subset of images to be associated with each
+plane, there are three criteria we keep in mind. First, we want such a
+subset of images to be capable of texturing the entirety of a plane,
+so as to ensure there are no holes in our final texture. Second, we
+want all our images to be taken from a relatively close distance to
+the plane, and at as much of a direct, head-on angle as possible. This
+ensures that the image projects squarely onto our desired plane, with
+minimal inclusion of other planes, and we get a texture with high
+resolution. Third, we desire an amount of overlap between the images
+chosen. This overlap helps us with preprocessing as well as
+postprocessing techniques discussed in Sections x and y.
+
+To meet these three criteria, we divide each plane into [X] triangles
+of [Y] size (our planes often have fairly complex geometry, hence the
+use of triangulation), using an ear-clipping algorithm followed by
+further triangular tesselation. For each triangle, we find all images
+that can be projected upon the entirety of the triangle, accounting
+for occlusion with other planes as well, using the standard
+ray-polygon intersection test shown in figure X. Of these images, we
+then select the best one according to the heuristic in equation X,
+favoring closer distances and more head-on viewing angles. We also
+enforce that no two images are chosen such that they were taken within
+0.5 meters of eachother. This results in a greatly-reduced set of
+images such that each one is objectively the "best" location-wise for
+some number of areas on the plane, addressing the first two
+criteria. Furthermore, since cameras are only at good angles to
+triangles near their center of projection, images will be chosen such
+that there is high overlap between them. With this process completed,
+we have reduced the amount of candidate images for each plane from
+many thousands to around 50, and are ready to begin the texture
+mapping process.
+
+\section{Texture Mapping Overview}
+\label{sec:textureMappingOverview}
+
+\begin{figure}
+  \centering
+  \includegraphics[height=2in]{Projection.pdf}
+  \caption{Planes are specified in 3D space by four corners $C_1$ to
+    $C_4$. Images are related to each plane through the camera
+    matrices $P_{1..M}$. }
+  % \caption{The plane is specified in 3D space by the four corners
+  % $C_1$ to $C_4$. Images are related to the plane through the camera
+  % matrices $P_{1..M}$. For example, the 3D point X in the world
+  % coordinate system is related to the image point x shown in the
+  % figure as $x = P_i X$.}
+  \label{fig:projection}
+\end{figure}
+
+In this section, we will discuss the process of texture mapping a
+single plane, as the texturing of each of our planes is completely
+independent and can even be completed in parallel.
+
+The geometry of the general texture mapping process is shown in Figure 1.
+
+ As
+described in the previous section, we are provided with a set of $M$
+candidate images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
+translates a 3D point in the world coordinate system to a 2D point in
+image $i$'s coordinates. A camera matrix $P_i$ is composed of the
+camera's intrinsic parameters, such as focal length and image center,
+as well as the extrinsic parameters which specify the rotation and
+translation of the camera center's position with respect to the world
+coordinates at the time that image $i$ was taken. These extrinsic
+parameters are determined by the localization hardware and algorithms
+mentioned in Section \ref{sec:backpackSystem}. A point $X$ on the
+plane in 3D space can be related to its corresponding pixel $x$ in image $i$
+through the following equation:
+
+\[
+x=project(P_iX)
+\]
+
+where
+\[X = \begin{pmatrix} x \\ y \\ z \end{pmatrix} \textrm{ and }
+project(X) = \begin{pmatrix} x/z \\ y/z \end{pmatrix}
+\]
+
+A plane to be textured is defined by four corner vertices $C_1$ to $C_4$ in
+world coordinates and a normal vector indicating the front facing side
+of the plane. Our goal is to texture this plane using its associated
+images, while eliminating any visual discontinuities or seams that
+would suggest that the plane's texture was not composed of a single
+continuous image.
+
+\subsection{Naive Mapping}
+\label{sec:naive}
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{naive.png}
+  \caption{The result of naive texture mapping based on the imprecise
+    camera matrices estimated by the localization system.}
+  \label{fig:naive}
+\end{figure}
+
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+one can texture map the plane simply by discretizing the plane into
+sections and texturing each section with one image. It makes sense to
+texture each section by selecting the best image locally, as was done
+in \ref{sec:imageAssociation}.
+
+As Figure \ref{fig:naive} demonstrates, this naive mapping approach
+leads to significant misalignment between successive tiles. This
+suggests that while the errors in the localization system are quite
+low, they are not pixel accurate. For photorealistic texture mapping,
+either the camera matrices need to be refined such that the
+localization is pixel accurate, resulting in a perfect mapping, or
+image stitching techniques need to be applied to provide this
+illusion. A commonly-used technique for each approach is examined
+next.
+
+\subsection{Image Mosaicing}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{panoMy.jpg}
+  \caption{Image mosaicing. }
+  \label{fig:mosaic}
+\end{figure}
+
+When images are taken of a plane from arbitrary overlapping positions,
+they are related by homography \cite{hz}. Thus, existing
+homography-based image mosaicing algorithms are applicable
+\cite{brown2007automatic}. However, errors can compound when long
+chains of images are mosaiced together using these approaches. For
+example, a pixel in the $n$th image in the chain must be translated
+into the first image's coordinates by multiplying by the $3\times3$
+matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these homography
+matrices is propagated to all further images until the chain is
+broken. For some chains of images this can happen almost immediately
+due to erroneous correspondence matches and the resulting image mosaic
+is grossly misshapen.
+
+Figure \ref{fig:mosaic} shows the output of the AutoStitch software
+package which does homography-based image mosaicing. This plane is
+nearly a best-case scenerio with many features spread uniformly across
+it. Even so, the mosaicing produces errors that causes straight lines
+to appear as waves on the plane. This image was generated after
+careful hand tuning. Many planes that had fewer features simply
+failed. This led to the conclusion that image mosaicing is not a
+robust enough solution for reliably texture mapping our dataset.
+
+\subsection{Image-Based 3D Localization Refinement}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{Graph_crop.pdf}
+  \caption{Using the graph-based localization refinement algorithm
+    from [11] suffers from the problem of compounding errors. }
+  \label{fig:graph}
+\end{figure}
+
+Another approach is to refine the camera matrices using image
+correspondences to guide the process. Each image's camera matrix has 6 degrees of freedom. Previous work has attempted to refine
+camera matrices by solving a non-linear optimization problem
+\cite{liu2010indoor}. This process is specific to the backpack system
+which generated our dataset, as it must be run during backpack
+localization\cite{liu2010indoor,chen2010indoor}. Unfortunately, this
+approach suffers from a similar error propagation problem shown in
+Figure \ref{fig:graph}. In our new approach, we also refine the
+placement of images using image correspondences. However, we do so in
+two dimensions on the plane whereas this previous work did so over all
+6 degrees of freedom. Refining in two dimensions on the plane is less
+flexible in that it does not address projection errors, however, it
+provides noticeable benefits while avoiding the error propagation
+problem.
+
+\section{Our Approach}
+Our approach begins with the naive projection of all our images onto separate copies of our plane, such that no projected data is lost.
+We then perform a series of preprocessing steps to rotate and shift each image's projection such that its overlapping regions with other projections are as seamless as possible.
+Following this, we perform a basic intensity-matching algorithm across all images, as images taken from different locations have different levels of overall brightness.
+From here, we assign textures to our planes using one of two methods, dependent on whether they are wall planes or ceiling/floor planes.
+The reasoning for this is explained in section \ref{sec:whydifferent}.
+Lastly, we apply alpha blending to smooth out any remaining seams.
+
+\subsection{Preprocessing}
+As a starting point, we naively texture map the plane using the given imprecise camera matrices for each image in the set.
+This is done by discretizing the plane into an arbitrary density of pixels and projecting each pixel into the image plane using the estimated camera matrix $P_i$.
+We later intend to shift some of these projected images around on the plane and remove some others.
+Therefore, each image is stored intact in its own data structure so that it can later be merged with the other images on the plane.
+We use a Hough transform to rotate the projected images such that vertical lines are pointing directly upwards.
+This can be effective for indoor modeling, since many indoor scenes contain strong vertical lines from features such as doors, wall panels, or rectangular frames.
+
+\subsection{Localization Refinement}
+
+The camera matrices generated by the localization algorithm are imprecise so the images are misaligned.
+To fix this, we choose to fix the locations in 2D.
+First we find corresponding points between all pairs of overlapping images using SIFT matches \cite{lowe1999object}.
+An illustration of this is given in Figure \ref{fig:matches}.
+The SIFT matches allow us to determine the correct $x$ and $y$ distances between two images on the plane.
+We already have an estimate of the $x$ and $y$ distances between the two images which was given by the localization algorithms.
+Soon we will compare the original estimates to the SIFT-based distances and use this to improve the quality of the image locations.
+
+\subsubsection{Robust SIFT Distances using RANSAC}
+
+First we need to ensure that the SIFT-based distances are reliable.
+Since SIFT matches frequently include outliers, the RANSAC framework \cite{fischler1981random} is used for a robust estimate of the $x$ and $y$ distances between the two images.
+The RANSAC framework will attempt to build a consensus among the SIFT matches about what the true $x$ and $y$ distance is between the two images while ignoring the influence of outliers that may skew the results.
+The framework handles the consensus-building machinery, and only requires that two functions be specified: the fitting function and the distance function.
+These functions are called for random subsets of the SIFT matches until the best set of inliers is found.
+For this application, the fitting function simply finds the average distance between matches.
+If the matches are exactly correct and the image is frontal and planar then the distances for various SIFT feature matches should be the same.
+Our distance function for a pair of points is the difference between those points' SIFT match distance and the average distance computed by the fitting function.
+We specified a 10 pixel outlier threshold to the framework.
+This means that a SIFT match is labeled as an outlier if its $x$ and $y$ distance is not within 10 pixels of the average distance computed by the fitting function.
+
+\subsubsection{Refining Image Positions using Least Squares}
+
+There are a total of $M^{2}$ possible pairs of images, however we can only measure distances between images that overlap at SIFT feature points.
+Given these distances and the original image location estimates, we solve a least squares problem ($\textrm{min}_{\beta} ||\beta X - y||_2^2 $) to estimate the correct location of the images on the plane.
+The vector $\beta$ of unknowns are the correct $x$ and $y$ locations of each image on the plane from $1 \dots M$.
+Finding the correct $x$ and $y$ locations are independent from one another so we will only consider the $x$ locations:
+
+% Draw least squares problem here.
+
+\[\beta =
+ \begin{pmatrix}
+  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
+ \end{pmatrix}
+\]
+
+The matrix $X$ is constructed with one row for each pair of images with measured distances produced by the SIFT matching stage.
+A row in the matrix has a $-1$ and $1$ in the columns corresponding to the two images in the pair.
+For example, the matrix below indicates that we generated a SIFT-based distance between images 1 and 2, images 1 and 3, images 2 and 3, etc.
+
+\[
+ X =
+ \begin{pmatrix}
+  -1 & 1 & 0 & \cdots & 0 & 0\\
+  -1 & 0 & 1 & \cdots & 0 & 0\\
+   0 & -1 & 1 & \cdots & 0 & 0\\
+  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
+  0 & 0 & 0 & \cdots & 1 & 0 \\ 
+  0 & 0 & 0 & \cdots & -1 & 1 \\ 
+  1 & 0 & 0 & \cdots & 0 & 0 \\ 
+ \end{pmatrix}
+\]
+
+If only relative distances between images are included then there is no way to determine the absolute location of any of the images and the matrix becomes rank deficient.
+To fix this we choose the first image to serve as the anchor for the rest, meaning all the absolute distances are based on its original location.
+This is done by adding a row with a $1$ in the first column and the rest zeros.
+
+Finally, the observation vector $y$ is constructed using the SIFT-based distances generated earlier in the matching stage.
+The distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based distances.
+The last element in the observation vector is the original location of the first image determined by the localization algorithm.
+
+\[
+y^T = 
+ \begin{pmatrix}
+  d_{1,2}, & d_{1,3}, & d_{2,3}, & \hdots & d_{N-2,N-1}, & d_{N-1,N}, &  x_1
+ \end{pmatrix}
+\]
+
+The $\beta$ that minimizes  $||\beta X - y||_2^2$ tells us a set of image locations on the plane that best honors all the SIFT-based distance measurements between images.
+A similar problem is solved for the $y$ dimension.
+In practice there are often cases where there is a break in the chain of images, meaning that no SIFT matches were found between one segment of the plane and another.
+In this case we add rows to the $X$ matrix and observations to the $y$ vector that contain the original $x$ and $y$ distance estimates generated by the localization algorithm.
+Another way to do this is to add rows for all neighboring pairs of images and solve a weighted least squares problem where the SIFT distances are given a higher weight i.e.
+1, and the distances generated by the localization algorithm are given a smaller weight i.e.
+0.01.
+
+At this point we now have our target plane associated with a list of images as well as their rotated and shifted projections upon the plane.
+We are ready to begin assigning these projections to areas of our plane for texturing.
+
+\subsection{Ceiling/Floor Texturing vs. Wall Texturing}
+\label{sec:whydifferent}
+The backpack
+modeling system described in Section \ref{sec:backpackHardware} was designed to prioritize for
+texturing walls. As mentioned previously, the backpack contains two
+fisheye cameras, one aimed directly to the left of the backpack
+operator, and one aimed directly to the right. Thus, in order to
+texture the ceiling above where the operator walked, images from both
+cameras must be combined, with their boundaries meeting overhead. Even more problematic, the floor beneath the
+backpack is physically obscured by the operator's body, and thus must
+be textured by images taken from behind the operator or from the side. This problem of distant cameras at poor angles
+is compounded by the fact that the operator's data acquisition path
+attempts to fully scan each wall, but not necessarily the entirety of
+a floor or ceiling. This means that large swaths of floors and
+ceilings are never walked directly over or under, and thus must be
+textured by sidelong images taken from further distances and at
+oblique angles.
+Images taken from closer distances are much preferred, as the effects of imprecise localization and camera matrices become multiplied over greater distances.
+We also strongly prefer head-on images because when images
+are projected onto a planar surface at an extreme angle, the resultant
+texture ends up spanning a large portion of the plane, applying
+low-resolution textures to areas at greater distances from the camera
+location.
+
+In short, these factors mean that wall planes are generally associated with a
+multitude of upright, uniform images, from a relatively close distance and originally taken head-on at regular intervals, while floors and
+ceilings are associated with images taken from all manner of orientations and
+distances. This major difference suggests we employ two strategies,
+one tailored for each scenario.
+
+\subsection{Texturing Walls}
+Because wall images in general are all good candidates for texturing due to their orientation and location, our goal is less about selecting good images for individual texturing, and more about selecting a set of images that together form a good texture.
+
+\subsection{Texturing Ceilings and Floors}
+
+Because the images associated with ceilings and floors are often captured by cameras at sidelong angles, we must be conservative when texture mapping such planes.
+Since localization errors compound over distance, we often have candidate images that project well on areas near the camera itself, but much more poorly at greater distances.
+
+Furthermore, as a result of the projection process and cropping due to occlusion, The geometry of the usable texture projected onto the plane for each image is generally complex and difficult to work with.
+
+These problems suggest that we must segment our images to some extent, as many of our images have desired as well as undesired portions.
+Such segmentation undoubtedly leads to more discontinuities, but floors and ceilings have lame textures
+
+\subsection{Evaluation of Methods}
+methods can be used on eachother
 
 \section{NOTES}
-4 Special Considerations due to BMS blabla sucky title
-The backpack modeling system described in Section 2 was designed to prioritize for texturing walls.
-As mentioned previously, the backpack contains two fisheye cameras, one aimed directly to the left of the backpack operator, and one aimed directly to the right.
-Thus, in order to texture the ceiling where the operator walked, images from both cameras must be combined.
-Even more problematic, the floor beneath the backpack is physically obscured by the operator's body, and thus must be textured by images taken from different locations.
-These problems are compounded by the fact that the operator's data acquisition path attempts to fully scan each wall, but not necessarily the entirety of a floor or ceiling.
-This means that large swaths of floors and ceilings are never walked directly over or under, and thus must be textured by sidelong images taken from further distances and at oblique angles.
-We strongly prefer head-on images because when images are projected onto a planar surface at an extreme angle, the resultant texture ends up spanning a large portion of the plane, applying low-resolution textures to areas at a great distance from the camera location.
 
-In short, these factors mean that wall planes are associated with a multitude of upright, uniform images, taken head-on and from a relatively close distance at regular intervals, while floors and ceilings are associated with images of all orientations and distances.
-This major difference suggests we employ two strategies, one tailored for each scenario.
+\subsection{Occlusion Masking}
+not sure where this section should go. it happens after projections,
+discussed in texture mapping overview, but it's definitely more of a
+preprocessing step.  Before we proceed with texturing our planes, we
+need to ensure that each plane's associated images contain only
+content that should be mapped onto the target plane in question. From
+the above process, images were chosen such that they had an unoccluded
+view of one or more trianglular sections upon a plane. This may not
+necessarily hold true however for all areas of the plane, as
+demonstrated in figure SOMETHING. If images are not modified to mask
+out occluded areas, different images could attempt to cover the same
+location on a plane with drastically different textures, inevitably
+leading to undesireable discontinuities in our final texture.
+
+Fortunately, by virtue of our indoor environments, the vast majority
+of surface geometry is either horizontal or vertical, with high
+amounts of right angles. This means that the areas we wish to mask out
+of our images due to occlusion are nearly always rectangular
+areas. Similar to the triangular tesselation performed for image
+association above, we split our image into
+
+With the steps in this section completed, we have generalized the
+input of our texture mapping problem into rectangular planes that are
+associated with a list of good candidate images, and we are ready to
+begin the texture mapping process.
 
@@
 
-4.2 Texturing Walls
-Since our candidate images for texturing a wall are all taken from similar distances and orientations relative to our wall, their individual "qualities" are all fairly similar.
-We don't have to worry as much about filtering out bad images; rather we seek to select some subset of our images which together form a good texture.
+4.2 Texturing Walls Since our candidate images for texturing a wall
+are all taken from similar distances and orientations relative to our
+wall, their individual "qualities" are all fairly similar. We don't
+have to worry as much about filtering out bad images; rather we seek
+to select some subset of our images which together form a good
+texture.
 
-5 Results and Analysis
-but also occlusion projection thing. door projected onto wall is fine, door projected onto floor is bad.
+5 Results and Analysis but also occlusion projection thing. door
+projected onto wall is fine, door projected onto floor is bad.
 

### 2012-06-17 3dimpvt/paper.tex
added more

@@
 
-\section{Our Approach}
+\section{Our Approach Overview}
 Our approach begins with the naive projection of all our images onto separate copies of our plane, such that no projected data is lost.
@@
 
-\subsection{Texturing Walls}
-Because wall images in general are all good candidates for texturing due to their orientation and location, our goal is less about selecting good images for individual texturing, and more about selecting a set of images that together form a good texture.
+\section{Texturing Walls}
+Because wall images in general are all fairly good candidates for texturing due to their orientation and location, our goal is less about determining the best images to texture with individually, and more about selecting a set of images that together form the most seamless texture.
+
+In order to objectively decide which sets of images form the most seamless textures, we need to decide on a cost function.
+We may be interested in covering the plane while minimizing the sum of squared pixel differences of the blended seam regions.
+This would encourage seams to be placed either in featureless areas, such as blank walls, or in areas in which the images are very well aligned.
+Another possible cost function is edge energy, i.e.
+the sum of the smoothed gradient of the blended seam regions.
+This would encourage seams to be placed in featureless areas even more than the sum of squared pixel difference cost function.
+For the dataset whose results are used in this paper, the first cost function is used, as the regular occurrence of featureless areas is not guaranteed.
+
+\subsection{Image Selection}
+
+Now that we have a cost function defined, we need to mechanically select the set of images for which the overall cost function is minimized.
+By adding the constraint that we aim to cover the entirety of our plane, one could see how our problem generalizes to a graph coverage problem, as depicted in figure X.
+Returning again to the optimality of our situation when texturing walls however, we can make a quick simplification for the sake of efficiency.
+Given that our wall-texture candidate images were all taken from a head-on angle, we can reason that their projections onto the plane are approximately rectangular.
+By simply discarding any excess texture and cropping them all to be rectangular, our problem becomes the conceptually simpler problem of filling a polygon with rectangles, such that the sum of all edge costs between each pair of rectangles is minimal.
+
+maybe i dunno
+
+Following the general scheme of Prim's algorithm for a minimum spanning tree, we can greedily add the minimal-cost image to our set until we have reached the desired coverage of our plane.
+This method can be applied on all manner of planes and images, howev this could be used for floors ceilings who knows
+
+\begin{figure}
+\centering
+\includegraphics[width=3in]{DynProg.pdf}
+\caption{Image Selection is done by constructing a graph of sorted images. Then we solve a shortest path problem where the edge weights represent the cost of a seam between two overlapping images.}
+\label{fig:DynProg}
+\end{figure}
+
+By taking one more shortcut we can simplify our problem down even further.
+Since care is taken such that our wall images generally contain the floor-to-ceiling range of walls, we generally do not have any wall images such that one should be projected vertically above the other.
+In essence, we need only to ensure horizontal coverage of our planes, as our images generally line up together at the same height.
+We can thus construct a DAG from the images, again with edge costs defined by our cost function above, and solve a simple shortest path problem to find an optimal subset of images with regard to the cost functions.
+
+Figure \ref{fig:DynProg} demonstrates the construction of a DAG from overlapping images of a long hallway.
+Images are sorted by location (e.g.
+left to right) and become nodes in a graph.
+Edges are placed in the graph between images that overlap.
+The weights of these edges are determined by a cost function, such as image energy, or the sum of squared pixel differences between the two images in the seam region.
+Next, we solve a shortest path problem from the first node in the graph to the last node.
+This provides a set of images that completely covers the plane, but minimizes the cost of the seams produced.
+Note that this only works when all the images completely cover one dimension.
+In this case the vertical dimension of the plane is covered by all images.
+
+In cases where the vertical dimension of the plane is not entirely covered, generally due to suboptimal camera locations, we are left with a hole where no image was chosen to texture.
+Rather than reverting to a 2D-coverage problem, we can elect to simply fill the hole by repeatedly selecting images in a greedy fashion, with respect to our cost function.
+
+At this point, we have accounted for every location on our plane with an image or images that were selected.
+Before actually applying our textures, we will examine how to accomplish the same for ceilings and floors.
 

### 2012-06-18 3dimpvt/paper.tex
first draft all text ready

--- 2012-06-17 3dimpvt/paper.tex
@@
   gathered by modeling systems and increases overall usability. The
-  localization of cameras in 3D scenes with respect to model surfaces
-  often suffers from inaccuracies, resulting in visible discontinuties
-  when different images are directly projected onto a plane for
+  localization of cameras in 3D scenes often suffers from inaccuracies, resulting in visible discontinuties
+  when images are directly projected onto a plane for
   texturing. Previous approaches at minimizing these discontinuities
-  suffer from error accumulation when stitching together multiple
-  images and do not robustly handle a wide range of camera locations
-  and angles. We propose two approaches for reducing discontinuities
-  during texture mapping, tailored towards a backpack-mounted data
-  acquisition system.
+  do not robustly handle a wide range of camera locations and angles, and often suffer from error accumulation when stitching together multiple
+  images. We propose two variants on a new approach for reducing discontinuities
+  during texture mapping, one tailored for optimal images, and one tailored for sub-optimal images.
 \end{abstract}
@@
 overview of the backpack modeling system from which data and examples
-used throughout this paper are from. Section
+used throughout this paper originate. Section
 \ref{sec:textureMappingOverview} describes the general problem of 3D
 texture mapping and reviews existing approaches. Section
-\ref{sec:textureMappingMethods} describes challenges posed by the
-backpack modeling system and presents our two approaches tailored for
-walls and floors/ceilings respectively. Section \ref{sec:results} compares results and
-presents conclusions.
+\ref{sec:textureMappingMethods} describes our new approach towards texture mapping, as well as unique challenges posed by the
+backpack modeling system and our two approaches tailored for
+walls and floors/ceilings respectively. Section \ref{sec:results}
+compares results and presents conclusions.
 
@@
 \label{sec:backpackSystem}
-Human-operated data acquisition systems provide unique advantages over vehicular-mounted systems in
-terms of agility and portability. Unfortunately, human-operated systems also suffer from a lack of
-automation and stability, resulting in higher localization variance
-and leading to the problems discussed in Section 4.
+Human-operated data acquisition systems provide unique advantages over
+vehicular-mounted systems in terms of agility and
+portability. Unfortunately, human-operated systems also suffer from a
+lack of automation and stability, often resulting in much higher data
+variance and localization error. As a result, common methods for
+texture mapping often produce poor results, as examined in section
+XX. Before discussing how to overcome these challenges, we will first
+provide an overview of the backpack modeling system from which our
+test data was obtained.
 
 \subsection{Data Acquisition Hardware}
-The backpack modeling system from which our data was collected
-contains five 2D laser range scanners, two cameras, an orientation
-sensor, and an IMU. The laser
-scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter
-range and a 270$^{\circ}$ field of view. These scanners are mounted
-orthogonally to one another. The two cameras are Point Grey
-Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting
-in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a
-strap-down navigation-grade sensor which combines three ring laser
-gyros with bias stability of less than 0.003$^{\circ}$/hour and three
-precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The
-HG9900 provides highly accurate measurements of all 6 DOF at 200Hz, and the orientation sensor (OS), an InterSense InertiaCube3,
-provides orientation parameters at a rate of 180Hz.
-Wearing this backpack, a human operator then takes great care to walk a path such that every wall in the desired indoor environment is passed and scanned lengthwise at least once.
+\label{sec:backpackHardware}
+The backpack modeling system which we worked with contains five 2D
+laser range scanners, two cameras, an orientation sensor, and an
+IMU. The laser scanners have a 30-meter range and a 270$^{\circ}$
+field of view. The two cameras are equipped with fisheye lenses,
+resulting in a 180$^{\circ}$ field of view, and are mounted with one
+facing left and one facing right. The IMU provides highly accurate
+measurements of all 6 DOF at 200Hz, and is used as a ground truth
+reference. The orientation sensor provides orientation parameters at a
+rate of 180Hz.
+
+With this backpack actively scanning, a human operator then takes
+great care to walk a path such that every wall in the desired indoor
+environment is passed and scanned lengthwise at least once.
 
 \subsection{Environment Reconstruction}
-Using data gathered by the onboard sensors and multiple localization and
-loop-closure algorithms, the backpack is localized over its data
-collection period, and a 3D point cloud of the environment is
-constructed. Approximate normal vectors for each point in the point
-cloud are then calculated by gathering neighboring points within a
-small radius and processing them with Principal Component Analysis. These normal vectors allow for the classification and
-grouping of adjacent points into structures such as walls, ceilings,
-floors, and staircases. A RANSAC algorithm is then employed to fit
-polygonal planes to these structured groupings of points, resulting in
-a fully planar model. This planar model, consisting of multiple 2D
-polygonal planes in 3D space, must then be textured by some subset of the images captured by
-the backpack's camera.
-
-\subsection{Plane Generalization}
-The planes we aim to texture are output by the surface reconstruction
-algorithm briefly explained in Section \ref{sec:backpackSystem}.
-These planes have arbitrary orientation and include simple rectangular
-walls as well as complicated floor planes defined by over 100
-vertices. In order to abstract out the difficulties of dealing with
-complex geometry, a minimal bounding box is constructed for each
-plane, and used as the target for texture mapping. Since the final
-texture created will be a standard rectangular image regardless, we
-can simply leave the area between the plane boundary and its bounding
-box untextured, and make sure to store the plane's original vertices
-for future retrieval.
+\label{sec:environmentReconstruction}
+Using data gathered by the onboard sensors and multiple localization
+and loop-closure algorithms, the backpack is localized over its data
+collection period, and a 3D point cloud of the surrounding environment
+is constructed based on the laser scanner readings. Approximate normal
+vectors for each point in the point cloud are then calculated by
+gathering neighboring points within a small radius and processing them
+using principal component analysis. These normal vectors allow for the
+classification and grouping of adjacent points into structures such as
+walls, ceilings, floors, and staircases. A RANSAC algorithm is then
+employed to fit polygonal planes to these structured groupings of
+points, resulting in a fully planar model. This planar model,
+consisting of multiple 2D polygonal planes in 3D space, must then be
+textured by all or some subset of the images captured by the
+backpack's camera.
 
@@
 \label{sec:imageAssociation}
-In order to speed up the texture mapping process, it is prudent to
+Before discussing texture mapping, we (something goes here based on whether we take credit for stewarts work or not)
+
+In order to speed up our texture mapping process, it is prudent to
 reduce the amount of potential images being considered for texture
@@
 present in (and capable of being textured mapped by) thousands of
-images, at a wide range of distances and angles. Thus, for the sake
-of efficiency, it makes sense to associate each plane with a much
-smaller list of images. When creating this subset of images to be associated with each
-plane, there are three criteria we keep in mind. First, we want such a
-subset of images to be capable of texturing the entirety of a plane,
-so as to ensure there are no holes in our final texture. Second, we
-want all our images to be taken from a relatively close distance to
-the plane, and at as much of a direct, head-on angle as possible. This
-ensures that the image projects squarely onto our desired plane, with
-minimal inclusion of other planes, and we get a texture with high
+images, at a wide range of distances and angles. Thus, for the sake of
+efficiency, it makes sense to associate each plane with a much smaller
+list of images, preferably some set which contains the most desirable images
+according to some metric. Thus we keep three criteria in mind while
+selecting such a subset. First, we want our final collection of images
+to be capable of covering the entirety of a plane, so as to ensure
+there are no holes in our final texture. Second, we want all our
+images to be taken from a relatively close distance to the plane, and
+at as much of a direct, head-on angle as possible. This ensures that
+the image projects squarely onto our desired plane, with minimal
+inclusion of other planes, and we end with a texture with high
 resolution. Third, we desire an amount of overlap between the images
-chosen. This overlap helps us with preprocessing as well as
-postprocessing techniques discussed in Sections x and y.
+chosen. This overlap provides us with a buffer in case we shift images
+as discussed in Section X, and is also required for the blending
+process presented in Section Y.
 
-To meet these three criteria, we divide each plane into [X] triangles
-of [Y] size (our planes often have fairly complex geometry, hence the
-use of triangulation), using an ear-clipping algorithm followed by
-further triangular tesselation. For each triangle, we find all images
-that can be projected upon the entirety of the triangle, accounting
-for occlusion with other planes as well, using the standard
-ray-polygon intersection test shown in figure X. Of these images, we
-then select the best one according to the heuristic in equation X,
-favoring closer distances and more head-on viewing angles. We also
-enforce that no two images are chosen such that they were taken within
-0.5 meters of eachother. This results in a greatly-reduced set of
-images such that each one is objectively the "best" location-wise for
-some number of areas on the plane, addressing the first two
-criteria. Furthermore, since cameras are only at good angles to
-triangles near their center of projection, images will be chosen such
-that there is high overlap between them. With this process completed,
-we have reduced the amount of candidate images for each plane from
-many thousands to around 50, and are ready to begin the texture
-mapping process.
+To meet these three criteria, we divide each plane into small triangles just a few centimers across. Triangulation is used due to the fairly complex
+geometry of many of our planes, and is accomplished by using a
+standard ear-clipping algorithm followed by further triangular
+tesselation. For each triangle, we gather all images that can be
+projected upon the entirety of the triangle, accounting for occlusion
+with other planes as well, using standard ray-polygon intersection
+tests. Of these images, we then select the best one
+according to the heuristic in equation X, which favors closer distances
+and more head-on projection angles. We also enforce that no two images
+are chosen such that they were taken within 0.5 meters of eachother,
+so as to reduce our overall amount of images. The end result is a
+greatly-reduced set of images such that each one is objectively a good choice for texturing some number of areas on the plane. Furthermore, since cameras are only at good
+angles to triangles near their center of projection, and poor
+candidates for triangles near their edges, images will be chosen such
+that there is high overlap between successive images. With the three criteria satisfied, we have reduced the amount of candidate images for
+each plane from many thousands to around 50-100.
+
+\subsection{Occlusion Checking}
+Before we proceed with texturing our planes, we need to ensure that
+each plane's associated images contain only content that should be
+mapped onto the target plane in question. From the above process,
+images were chosen such that they had an unoccluded view of one or
+more trianglular sections upon a plane. This may not necessarily hold
+true however for all areas of the plane, as demonstrated in figure
+SOMETHING. If images are not modified to mask out occluded areas,
+different images could attempt to cover the same location on a plane
+with drastically different textures, inevitably leading to
+undesireable discontinuities in our final texture.
+
+Fortunately, by virtue of our indoor environments, the vast majority
+of surface geometry is either horizontal or vertical, with high
+amounts of right angles. This means that the areas we wish to mask out
+of our images due to occlusion are nearly always rectangular
+areas. Similar to the triangular tesselation performed for image
+association above, we split each image into rectangular pieces, and
+perform occlusion checks for a sampling of points within each
+piece. For rectangles with occluded points, we then subdivide them
+into smaller rectangles, and repeat the process, until we reach some
+manually-set recursion limit. To actually occlude out rectangles, we
+simply remove their texture, as untextured areas will never be chosen
+for texture mapping. We are now ready to begin the texture mapping
+process.
 
@@
 single plane, as the texturing of each of our planes is completely
-independent and can even be completed in parallel.
+independent and can be completed in parallel.
 
@@
 described in the previous section, we are provided with a set of $M$
-candidate images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
+images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
 translates a 3D point in the world coordinate system to a 2D point in
@@
 as well as the extrinsic parameters which specify the rotation and
-translation of the camera center's position with respect to the world
+translation of the camera's position with respect to the world
 coordinates at the time that image $i$ was taken. These extrinsic
@@
 
-A plane to be textured is defined by four corner vertices $C_1$ to $C_4$ in
+For the sake of simplicity, we treat all planes as rectangles by generating a minimum bounding box for them.
+Their original vertices can be recovered later as needed, and used to crop any excess texture.
+A plane to be textured is thus defined by its bounding box with corners $C_i$ in
 world coordinates and a normal vector indicating the front facing side
@@
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-one can texture map the plane simply by discretizing the plane into
-sections and texturing each section with one image. It makes sense to
-texture each section by selecting the best image locally, as was done
-in \ref{sec:imageAssociation}.
+one can texture map the plane by simply applying textures according to
+the image association process and scoring function described in
+Section X. This naive mapping approach independently selects the best
+texture for each trianglular section on the plane, but it also means
+that all of our $M$ images are used for the overall texture, thus
+increasing the potential amount of poor image boundaries.
 
-As Figure \ref{fig:naive} demonstrates, this naive mapping approach
-leads to significant misalignment between successive tiles. This
-suggests that while the errors in the localization system are quite
-low, they are not pixel accurate. For photorealistic texture mapping,
-either the camera matrices need to be refined such that the
-localization is pixel accurate, resulting in a perfect mapping, or
-image stitching techniques need to be applied to provide this
-illusion. A commonly-used technique for each approach is examined
-next.
+As Figure \ref{fig:naive} demonstrates, this approach leads to many
+image boundaries with abrupt discontinuities, due to significant
+misalignment between images. One approach also tuned for our datasets
+attempted to minimize these discontinuities through more intelligent
+image selection, making use of spatial and temporal caching
+mechanisms.
+
+\subsection{Mapping with Caching}
+In order to reduce the severity of discontinuities between adjacent
+triangles, one can texture them with the same image, if possible,
+eliminating the discontinuity outright, or by two images taken from
+similar positions, such that any texture mismatch is ideally less
+pronounced. This is accomplished by adding a 2-level cache to the
+native mapping approach, and sorting triangles in an order such that
+triangle $t_i$ is adjacent to triangle $t_{i+1}$. When a
+triangle is assigned a texture, the image it selected is added to the
+level 1 cache, and other images that were taken nearby in time and
+location, within a predefined threshold, are added to the level 2
+cache. Each subsequent triangle to be textured then searches through
+the level 1 cache, selecting the best image according to the same
+scoring function, and comparing it to some pre-defined threshold. If
+the best image's score is below this threshold, the level 2 cache is
+then searched, and then finally if necessary, the set of all images is
+searched. In this way, the entire plane is textured, with image reuse prioritized, followed by a preference for nearby images.
+
+This approach is the method previously used by the modeling team
+associated with our dataset. Therefore, we will use it as our baseline
+when comparing other approaches.  The addition of the caching
+structure reduces discontinuities overall, as can be seen in the above
+image. Nevertheless, the amount of remaining discontinuities suggests
+that image selection alone cannot produce seamless textures.  In order
+to produce photorealistic texture mapping, either the camera matrices
+need to be refined such that the localization is pixel accurate,
+resulting in a perfect mapping, or image stitching techniques need to
+be applied to provide this illusion. A commonly-used technique for
+each approach is examined next.
 
@@
 Another approach is to refine the camera matrices using image
-correspondences to guide the process. Each image's camera matrix has 6 degrees of freedom. Previous work has attempted to refine
-camera matrices by solving a non-linear optimization problem
+correspondences to guide the process. Each image's camera matrix has 6
+degrees of freedom. Previous work has attempted to refine camera
+matrices by solving a non-linear optimization problem
 \cite{liu2010indoor}. This process is specific to the backpack system
@@
 
-\section{Our Approach}
-Our approach begins with the naive projection of all our images onto separate copies of our plane, such that no projected data is lost.
-We then perform a series of preprocessing steps to rotate and shift each image's projection such that its overlapping regions with other projections are as seamless as possible.
-Following this, we perform a basic intensity-matching algorithm across all images, as images taken from different locations have different levels of overall brightness.
-From here, we assign textures to our planes using one of two methods, dependent on whether they are wall planes or ceiling/floor planes.
-The reasoning for this is explained in section \ref{sec:whydifferent}.
-Lastly, we apply alpha blending to smooth out any remaining seams.
+\section{Our Approach Overview}
+Our approach begins 
+with the projection of all our images onto
+separate copies of our plane, such that no projected data is covered
+and lost.
+Tis is done by discretizing the plane into an arbitrary density of points, and projecting each point into the image plane using the camera matrix $P_i$.
+We then perform a series of preprocessing steps to rotate
+and shift each image's projection such that its overlapping regions
+with other projections are as seamless as possible. From here, we assign textures to our planes
+using one of two methods, dependent on whether they are wall planes or
+ceiling/floor planes. The reasoning for this is explained in section
+\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to smooth out
+any remaining seams.
 
-\subsection{Preprocessing}
-As a starting point, we naively texture map the plane using the given imprecise camera matrices for each image in the set.
-This is done by discretizing the plane into an arbitrary density of pixels and projecting each pixel into the image plane using the estimated camera matrix $P_i$.
-We later intend to shift some of these projected images around on the plane and remove some others.
-Therefore, each image is stored intact in its own data structure so that it can later be merged with the other images on the plane.
-We use a Hough transform to rotate the projected images such that vertical lines are pointing directly upwards.
-This can be effective for indoor modeling, since many indoor scenes contain strong vertical lines from features such as doors, wall panels, or rectangular frames.
+\subsection{Hough Transforms}
+Our first step is to use Hough transforms to rotate
+the projected images such that any strong near-vertical features are made completely vertical. This is effective for indoor modeling, since many indoor
+scenes contain strong vertical lines from features such as doors, wall
+panels, or rectangular frames.
 
 \subsection{Localization Refinement}
-
-The camera matrices generated by the localization algorithm are imprecise so the images are misaligned.
-To fix this, we choose to fix the locations in 2D.
-First we find corresponding points between all pairs of overlapping images using SIFT matches \cite{lowe1999object}.
-An illustration of this is given in Figure \ref{fig:matches}.
-The SIFT matches allow us to determine the correct $x$ and $y$ distances between two images on the plane.
-We already have an estimate of the $x$ and $y$ distances between the two images which was given by the localization algorithms.
-Soon we will compare the original estimates to the SIFT-based distances and use this to improve the quality of the image locations.
+Our next step is to try and fix misalignment between overlapping images.
+We do this by fixing
+the locations in 2D. First we find corresponding points between all
+pairs of overlapping images using SIFT matches
+\cite{lowe1999object}. An illustration of this is given in Figure
+\ref{fig:matches}.
+The SIFT matches allow us to determine feature-based $x$ and $y$ distances between two images on the plane, which we can compare against the $x$ and $y$ distances provided by the camera matrices.
+With these data points, we can reevaluate where each image should be projected.
 
@@
 
-First we need to ensure that the SIFT-based distances are reliable.
-Since SIFT matches frequently include outliers, the RANSAC framework \cite{fischler1981random} is used for a robust estimate of the $x$ and $y$ distances between the two images.
-The RANSAC framework will attempt to build a consensus among the SIFT matches about what the true $x$ and $y$ distance is between the two images while ignoring the influence of outliers that may skew the results.
-The framework handles the consensus-building machinery, and only requires that two functions be specified: the fitting function and the distance function.
-These functions are called for random subsets of the SIFT matches until the best set of inliers is found.
-For this application, the fitting function simply finds the average distance between matches.
-If the matches are exactly correct and the image is frontal and planar then the distances for various SIFT feature matches should be the same.
-Our distance function for a pair of points is the difference between those points' SIFT match distance and the average distance computed by the fitting function.
-We specified a 10 pixel outlier threshold to the framework.
-This means that a SIFT match is labeled as an outlier if its $x$ and $y$ distance is not within 10 pixels of the average distance computed by the fitting function.
+First we need to ensure that the SIFT-based distances are
+reliable. Since SIFT matches frequently include outliers, the RANSAC
+framework \cite{fischler1981random} is used for a robust estimate of
+the $x$ and $y$ distances between the two images. The RANSAC framework
+will attempt to build a consensus among the SIFT matches about what
+the true $x$ and $y$ distance is between the two images while ignoring
+the influence of outliers that may skew the results. The framework
+handles the consensus-building machinery, and only requires that two
+functions be specified: the fitting function and the distance
+function. These functions are called for random subsets of the SIFT
+matches until the best set of inliers is found. For this application,
+the fitting function simply finds the average distance between
+matches. If the matches are exactly correct and the image is frontal
+and planar then the distances for various SIFT feature matches should
+be the same. Our distance function for a pair of points is the
+difference between those points' SIFT match distance and the average
+distance computed by the fitting function. We specified a 10 pixel
+outlier threshold to the framework. This means that a SIFT match is
+labeled as an outlier if its $x$ and $y$ distance is not within 10
+pixels of the average distance computed by the fitting function.
 
@@
 
-There are a total of $M^{2}$ possible pairs of images, however we can only measure distances between images that overlap at SIFT feature points.
-Given these distances and the original image location estimates, we solve a least squares problem ($\textrm{min}_{\beta} ||\beta X - y||_2^2 $) to estimate the correct location of the images on the plane.
-The vector $\beta$ of unknowns are the correct $x$ and $y$ locations of each image on the plane from $1 \dots M$.
-Finding the correct $x$ and $y$ locations are independent from one another so we will only consider the $x$ locations:
+There are a total of $M^{2}$ possible pairs of images, however we can
+only measure distances between images that overlap at SIFT feature
+points. Given these distances and the original image location
+estimates, we solve a least squares problem ($\textrm{min}_{\beta}
+||\beta X - y||_2^2 $) to estimate the correct location of the images
+on the plane. The vector $\beta$ of unknowns are the correct $x$ and
+$y$ locations of each image on the plane from $1 \dots M$. Finding the
+correct $x$ and $y$ locations are independent from one another so we
+will only consider the $x$ locations:
 
@@
 
-The matrix $X$ is constructed with one row for each pair of images with measured distances produced by the SIFT matching stage.
-A row in the matrix has a $-1$ and $1$ in the columns corresponding to the two images in the pair.
-For example, the matrix below indicates that we generated a SIFT-based distance between images 1 and 2, images 1 and 3, images 2 and 3, etc.
+The matrix $X$ is constructed with one row for each pair of images
+with measured distances produced by the SIFT matching stage. A row in
+the matrix has a $-1$ and $1$ in the columns corresponding to the two
+images in the pair. For example, the matrix below indicates that we
+generated a SIFT-based distance between images 1 and 2, images 1 and
+3, images 2 and 3, etc.
 
@@
 
-If only relative distances between images are included then there is no way to determine the absolute location of any of the images and the matrix becomes rank deficient.
-To fix this we choose the first image to serve as the anchor for the rest, meaning all the absolute distances are based on its original location.
-This is done by adding a row with a $1$ in the first column and the rest zeros.
+If only relative distances between images are included then there is
+no way to determine the absolute location of any of the images and the
+matrix becomes rank deficient. To fix this we choose the first image
+to serve as the anchor for the rest, meaning all the absolute
+distances are based on its original location. This is done by adding a
+row with a $1$ in the first column and the rest zeros.
 
-Finally, the observation vector $y$ is constructed using the SIFT-based distances generated earlier in the matching stage.
-The distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based distances.
-The last element in the observation vector is the original location of the first image determined by the localization algorithm.
+Finally, the observation vector $y$ is constructed using the
+SIFT-based distances generated earlier in the matching stage. The
+distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based
+distances. The last element in the observation vector is the original
+location of the first image determined by the localization algorithm.
 
@@
 \begin{pmatrix}
-  d_{1,2}, & d_{1,3}, & d_{2,3}, & \hdots & d_{N-2,N-1}, & d_{N-1,N}, &  x_1
+  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
 \end{pmatrix}
@@
 
-The $\beta$ that minimizes  $||\beta X - y||_2^2$ tells us a set of image locations on the plane that best honors all the SIFT-based distance measurements between images.
-A similar problem is solved for the $y$ dimension.
-In practice there are often cases where there is a break in the chain of images, meaning that no SIFT matches were found between one segment of the plane and another.
-In this case we add rows to the $X$ matrix and observations to the $y$ vector that contain the original $x$ and $y$ distance estimates generated by the localization algorithm.
-Another way to do this is to add rows for all neighboring pairs of images and solve a weighted least squares problem where the SIFT distances are given a higher weight i.e.
-1, and the distances generated by the localization algorithm are given a smaller weight i.e.
-0.01.
+The $\beta$ that minimizes $||\beta X - y||_2^2$ tells us a set of
+image locations on the plane that best honors all the SIFT-based
+distance measurements between images. A similar problem is solved for
+the $y$ dimension. In practice there are often cases where there is a
+break in the chain of images, meaning that no SIFT matches were found
+between one segment of the plane and another. In this case we add rows
+to the $X$ matrix and observations to the $y$ vector that contain the
+original $x$ and $y$ distance estimates generated by the localization
+algorithm. Another way to do this is to add rows for all neighboring
+pairs of images and solve a weighted least squares problem where the
+SIFT distances are given a higher weight i.e. 1, and the distances
+generated by the localization algorithm are given a smaller weight
+i.e. 0.01.
 
-At this point we now have our target plane associated with a list of images as well as their rotated and shifted projections upon the plane.
-We are ready to begin assigning these projections to areas of our plane for texturing.
+At this point we now have our target plane associated with a list of
+images as well as their rotated and shifted projections upon the
+plane. We are ready to begin assigning these projections to areas of
+our plane for texturing.
 
@@
 \label{sec:whydifferent}
-The backpack
-modeling system described in Section \ref{sec:backpackHardware} was designed to prioritize for
-texturing walls. As mentioned previously, the backpack contains two
-fisheye cameras, one aimed directly to the left of the backpack
-operator, and one aimed directly to the right. Thus, in order to
-texture the ceiling above where the operator walked, images from both
-cameras must be combined, with their boundaries meeting overhead. Even more problematic, the floor beneath the
-backpack is physically obscured by the operator's body, and thus must
-be textured by images taken from behind the operator or from the side. This problem of distant cameras at poor angles
-is compounded by the fact that the operator's data acquisition path
-attempts to fully scan each wall, but not necessarily the entirety of
-a floor or ceiling. This means that large swaths of floors and
-ceilings are never walked directly over or under, and thus must be
+The backpack modeling system, as described in Section
+\ref{sec:backpackHardware}, was designed to prioritize for texturing
+walls. As mentioned previously, the backpack contains two fisheye
+cameras, one aimed directly to the left of the backpack operator, and
+one aimed directly to the right. Thus, in order to texture the ceiling
+above where the operator walked, images from both cameras must be
+combined, with their boundaries meeting overhead. Unlike walls, where
+one image generally spans the entire height of a wall, two images are
+required to span the width of a ceiling. Even more problematic, the
+floor beneath the backpack is physically obscured by the operator's
+body, and thus must be textured by images taken from behind the
+operator or from the side. This problem of distant cameras at poor
+angles is compounded by the fact that the operator's data acquisition
+path attempts to fully scan each wall, but not necessarily the
+entirety of a floor or ceiling. This means that large swaths of floors
+and ceilings are never walked directly over or under, and thus must be
 textured by sidelong images taken from further distances and at
-oblique angles.
-Images taken from closer distances are much preferred, as the effects of imprecise localization and camera matrices become multiplied over greater distances.
-We also strongly prefer head-on images because when images
-are projected onto a planar surface at an extreme angle, the resultant
-texture ends up spanning a large portion of the plane, applying
-low-resolution textures to areas at greater distances from the camera
-location.
+oblique angles. These effects are shown in the following figure.
 
-In short, these factors mean that wall planes are generally associated with a
-multitude of upright, uniform images, from a relatively close distance and originally taken head-on at regular intervals, while floors and
-ceilings are associated with images taken from all manner of orientations and
-distances. This major difference suggests we employ two strategies,
-one tailored for each scenario.
+In short, these factors mean that wall planes are generally associated
+with a multitude of upright, uniform images, from a relatively close
+distance and taken head-on at regular intervals, while floors and
+ceilings are associated with images taken from all manner of
+orientations and distances. This major difference suggests we employ
+two strategies, one tailored for each scenario.
 
 \subsection{Texturing Walls}
-Because wall images in general are all good candidates for texturing due to their orientation and location, our goal is less about selecting good images for individual texturing, and more about selecting a set of images that together form a good texture.
+Because wall images tend to all be fairly good candidates for
+texturing due to their orientation and location, our goal is less
+about determining the best images, and more about selecting a set of
+images that together form the most seamless texture.
+
+\subsubsection{Cost Functions}
+
+In order to objectively decide which set of images accomplishes this,
+we need to decide on an overall cost function. As our goal is to reduce
+the seams that occur where two images meet, a simple cost function is
+the sum of squared pixel differences in overlapping regions between
+every pair of images. This encourages image boundaries to occur in
+featureless areas, such as bare walls, on in areas where images are
+very well aligned.
+
+Another possible cost function is edge energy, i.e. the sum of the
+smoothed gradient of the blended seam regions. Minimizing this
+encourages image boundaries to be placed in featureless areas even
+more than the first cost function. For the results shown throughout
+this paper, the first cost function was used, as the regular
+occurrence of featureless areas was not guaranteed in our datasets.
+
+\subsubsection{Image Selection}
+
+Now that we have a cost function defined, we need to mechanically
+select the set of images for which the overall cost function is
+minimized. Since we aim to cover the entirety of our plane, our
+problem is to minimally cover a polygon(our plane) using other
+polygons of arbitrary geometry (our image projections), with the added
+constraint of minimizing our cost function. This is a complex problem,
+though it can be generalized to a number of graph coverage problems,
+as depicted in figure X. Returning again to the optimality of our
+situation when texturing walls however, we can make a quick
+simplification for the sake of efficiency. Given that our wall-texture
+candidate images were all taken from a head-on angle, and assuming only minor rotations were made earlier, we can reason
+that their projections onto the plane are approximately
+rectangular. By discarding any excess texture and cropping them
+all to be rectangular, our problem becomes the conceptually simpler
+problem of filling a polygon with rectangles, such that the sum of all
+edge costs between each pair of rectangles is minimal. An additional
+benefit of working with rectangular units is that borders between any
+two distinct images in our final texture will be either horizontal or
+vertical. Since most environmental features inside buildings are horizontal
+or vertical, any seams in our texture will intersect them miniimally
+and be less noticeable.
+
+By taking one more shortcut we can simplify our problem down even
+further. Since care is taken such that our wall images contain the
+floor-to-ceiling range of walls, we generally do not have any wall
+images such that one should be projected vertically above the
+other. In essence, we need only to ensure horizontal coverage of our
+planes, as our images provide full vertical coverage. We can thus
+construct a Directed Acyclic Graph (DAG) from the images, again with
+edge costs defined by our cost function above, and solve a simple
+shortest path problem to find an optimal subset of images with regard
+to the cost functions.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{DynProg.pdf}
+  \caption{Image Selection is done by constructing a graph of sorted
+    images. Then we solve a shortest path problem where the edge
+    weights represent the cost of a seam between two overlapping
+    images.}
+  \label{fig:DynProg}
+\end{figure}
+
+Figure \ref{fig:DynProg} demonstrates the construction of a DAG from
+overlapping images of a long hallway. Images are sorted by horizontal
+location left to right, and become nodes in a graph. Directed edges
+are placed in the graph from left to right between images that
+overlap. The weights of these edges are determined by the cost
+functions discussed previously. Next, we add two artificial nodes, one
+start node representing the left border of the plane, and one end node
+representing the right border of the plane. The left artificial node
+has directed edges with equal cost to all images that meet the left
+border of the plane, and the right artificial node has directed edges
+from all images that meet the right border of the plane.
+
+We now solve the standard shortest path problem from the start node to
+the end node. This provides a set of images that completely covers the
+plane horizontally, while minimizing the cost of the seams between
+images.
+
+In rare cases where the vertical dimension of the plane is not entirely
+covered by a chosen image, we are left with a hole where no image was
+chosen to texture. Rather than reverting to a 2D-coverage problem, we
+can elect to simply fill the hole by selecting images in a
+greedy fashion, with respect to the same cost function.
+
+At this point, we have mapped every location on our plane to an image
+or images that were selected. Before applying these textures, we will
+examine how to accomplish the same mapping for ceilings and floors.
 
@@
 
-Because the images associated with ceilings and floors are often captured by cameras at sidelong angles, we must be conservative when texture mapping such planes.
-Since localization errors compound over distance, we often have candidate images that project well on areas near the camera itself, but much more poorly at greater distances.
+Because the images associated with ceilings and floors are often
+captured by cameras at sidelong angles, we must be conservative when
+we texture map them. Since localization errors compound over distance,
+we often have candidate images that project well on areas near the
+camera itself, but much more poorly at the greater distances caused by
+higher angles. Using entire images to minimize seams is beneficial for
+wall texturing, but it becomes detrimental on ceilings and floors,
+since the quality of usable texture varies greatly across any one
+image. As evident in the following comparison, ceiling and floor
+images often have a very low amount of optimal texture relative to the
+projection size. This factor suggests that we should segment our images in some way, as many of our images contain both desired as well as undesired portions.
 
-Furthermore, as a result of the projection process and cropping due to occlusion, The geometry of the usable texture projected onto the plane for each image is generally complex and difficult to work with.
+Such segmentation
+implies smaller units of texture, which often leads to more images being
+chosen and unfortunately, more boundaries between different images as
+a result. This goes strongly against our approach for texturing walls,
+in which we attempted to minimize the number of images chosen. Nevertheless, boundaries on
+floors and ceilings are less problematic, since floors and ceilings
+tend to have fewer noticeable features.
 
-These problems suggest that we must segment our images to some extent, as many of our images have desired as well as undesired portions.
-Such segmentation undoubtedly leads to more discontinuities, but floors and ceilings have lame textures
+As shown in the above figure, we define
+a tile length $l1$ as well as an overlap length $l2$, usually about 5
+pixels for each. We then discretize our plane into rectangular tiles
+$l1$x$l1$ in size. Each tile is then associated with a square
+texture of size $(l1+2l2)$x$(l1+2l2)$, such that it shares a large
+overlapping region with its neighboring tiles, allowing for blending afterwards.
+As in wall texturing, rectangles, rather than triangles, are preferred for the high prevalence of horizontal and vertical features, generally light fixtures and floor and ceiling tiles.
 
-\subsection{Evaluation of Methods}
-methods can be used on eachother
+For the actual process of image association, we can reuse the caching method shown earlier.
+This method will balance selection of the best texture for each tile with some amount of image reuse.
+Coupled with image rotation and shifting, as well as the usage of rectangles instead of triangles, we end with a much more seamless texture, even without any blending applied yet, as seen below.
 
-\section{NOTES}
+\subsection{Blending}
+Though our preprocessing steps and image selection attempts above
+attempted to minimize all mismatches between images, there are often
+cases, where due to geometry or projection inaccuracies, we simply
+have unavoidable discontinuities. These can however be partially
+treated by applying alpha blending over our seams.  Whether the units
+we are blending are rectangularly-cropped images for walls, or
+rectangular units for ceilings/floors, we can apply the same blending
+procedure.
 
-\subsection{Occlusion Masking}
-not sure where this section should go. it happens after projections,
-discussed in texture mapping overview, but it's definitely more of a
-preprocessing step.  Before we proceed with texturing our planes, we
-need to ensure that each plane's associated images contain only
-content that should be mapped onto the target plane in question. From
-the above process, images were chosen such that they had an unoccluded
-view of one or more trianglular sections upon a plane. This may not
-necessarily hold true however for all areas of the plane, as
-demonstrated in figure SOMETHING. If images are not modified to mask
-out occluded areas, different images could attempt to cover the same
-location on a plane with drastically different textures, inevitably
-leading to undesireable discontinuities in our final texture.
-
-Fortunately, by virtue of our indoor environments, the vast majority
-of surface geometry is either horizontal or vertical, with high
-amounts of right angles. This means that the areas we wish to mask out
-of our images due to occlusion are nearly always rectangular
-areas. Similar to the triangular tesselation performed for image
-association above, we split our image into
-
-With the steps in this section completed, we have generalized the
-input of our texture mapping problem into rectangular planes that are
-associated with a list of good candidate images, and we are ready to
-begin the texture mapping process.
-
-4.1 Texturing Floors and Ceilings
-
-4.2 Texturing Walls Since our candidate images for texturing a wall
-are all taken from similar distances and orientations relative to our
-wall, their individual "qualities" are all fairly similar. We don't
-have to worry as much about filtering out bad images; rather we seek
-to select some subset of our images which together form a good
-texture.
-
-5 Results and Analysis but also occlusion projection thing. door
-projected onto wall is fine, door projected onto floor is bad.
-
-\section{EVERYTHING AFTER HERE IS TEMPLATE STUFF}
-
-\section{Introduction}
-
-Please follow the steps outlined below when submitting your manuscript
-to the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against
-the use of sticky tape to attach your artwork to the paper), so all
-authors should read this new version.
-
-% -------------------------------------------------------------------------
-\subsection{Language}
-
-All manuscripts must be in English.
-
-\subsection{Dual submission}
-
-By submitting a manuscript to 3DIMPVT, the authors assert that it has
-not been previously published in substantially similar
-form. Furthermore, no paper which contains significant overlap with
-the contributions of this paper either has been or will be submitted
-during the 3DIMPVT 2012 review period to {\bf either a journal} or any
-conference or any workshop.  {\bf Papers violating this condition will
-  be rejected}.
-
-If there are papers that may appear to the reviewers to violate this
-condition, then it is your responsibility to: (1)~cite these papers
-(preserving anonymity as described in Section 1.6 below), (2)~argue in
-the body of your paper why your 3DIMPVT paper is non-trivially
-different from these concurrent submissions, and (3)~include
-anonymized versions of those papers in the supplemental material.
-
-\subsection{Paper length}
-3DIMPVT papers may be between 6 pages and 8 pages.  Overlength papers
-will simply not be reviewed.  This includes papers where the margins
-and formatting are deemed to have been significantly altered from
-those laid down by this style guide.  Note that this \LaTeX\ guide
-already sets figure captions and references in a smaller font.  The
-reason such papers will not be reviewed is that there is no provision
-for supervised revisions of manuscripts.  The reviewing process cannot
-determine the suitability of the paper for presentation in eight pages
-if it is reviewed in eleven.
-
-% -------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in
-the version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the
-ruler should not change the appearance of any other content on the
-page.  The camera ready copy should not contain a ruler. (\LaTeX\
-users may uncomment the \verb'\cvprfinalcopy' command in the document
-preamble.)  Reviewers: note that the ruler measurements do not align
-well with lines in the paper --- this turns out to be very difficult
-to do well when the paper contains many figures and equations, and,
-when done, looks ugly.  Just use fractional references (e.g.\ this
-line is $097.15$), although in most cases one would expect that the
-approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.
-Just because you didn't refer to it in the text doesn't mean some
-future reader might not need to refer to it.  It is cumbersome to have
-to use circumlocutions like ``the equation second from the top of page
-3 column 1''.  (Note that the ruler will not be present in the final
-copy, so is not an alternative to equation numbers).  All authors will
-benefit from reading Mermin's description of how to write mathematics:
-\url{http://www.cvpr.org/doc/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove citations to
-one's own work---in fact it is often impossible to review a paper
-unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that
-you are Lucy Smith, it says that you are building on her work.  If you
-are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
-and Jones show in [7]'' and at the end of the paper, include reference
-7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-  \begin{center}
-    An analysis of the frobnicatable foo filter.
-  \end{center}
-
-  In this paper we present a performance analysis of our previous
-  paper [1], and show it to be inferior to all previously known
-  methods.  Why the previous paper was accepted without this analysis
-  is beyond me.
-
-  [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-  \begin{center}
-    An analysis of the frobnicatable foo filter.
-  \end{center}
-
-  In this paper we present a performance analysis of the paper of
-  Smith \etal [1], and show it to be inferior to all previously known
-  methods.  Why the previous paper was accepted without this analysis
-  is beyond me.
-
-  [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a
-  fundamental contribution to human knowledge''.  Nature 381(12),
-  1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to
-that submission in order to explain the differences, just as you would
-if you had previously published related work.  In such cases, include
-the anonymized parallel submission~\cite{Authors12} as additional
-material and cite it as
-\begin{quote} [1] Authors. ``The frobnicatable foo filter'', F\&G 2012
-  Submission ID 324, Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details
-can be found elsewhere, and refer them to a technical report.  For
-conference submissions, the paper must stand on its own, and not {\em
-  require} the reviewer to go to a techreport for further details.
-Thus, you may say in the body of the paper ``further details may be
-found in~\cite{Authors12b}''.  Then submit the techreport as
-additional material.  Again, you may not assume the reviewers will
-read this material.
-
-Sometimes your paper is about a problem which you tested using a tool
-which is widely known to be restricted to a single institution.  For
-example, let's say it's 1969, you have solved a key problem on the
-Apollo lander, and you believe that the CVPR70 audience would like to
-hear about your solution.  The work is a development of your
-celebrated 1968 paper entitled ``Zero-g frobnication: How being the
-only people in the world with access to the Apollo lander source code
-makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how
-to improve our previous work [Anonymous, 1968].  This time we tested
-the algorithm on a lunar lander [name of lander removed for blind
-review]''.  That would be silly, and would immediately identify the
-authors. Instead write the following:
-\begin{quotation}
-  \noindent
-  We describe a system for zero-g frobnication.  This system is new
-  because it handles the following cases: A, B.  Previous systems
-  [Zeus et al. 1968] didn't handle case B properly.  Ours handles it
-  by including a foo term in the bar integral.
-
-  ...
-
-  The proposed system was integrated with the Apollo lunar lander, and
-  went all the way to the moon, don't you know.  It displayed the
-  following behaviours which show how well we solved cases A and B:
-  ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you
-as the authors.  A reviewer might think it likely that the new paper
-was written by Zeus \etal, but cannot make any decision based on that
-guess.  He or she would have to be sure that no other authors could
-have been contracted to solve problem B.
-
-FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.
-
-\begin{figure}[t]
-  \begin{center}
-    \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
-  \end{center}
-  \caption{Example of caption.  It is set in Roman so that mathematics
-    (always set in Roman: $B \sin A = A \sin B$) may be included
-    without an ugly clash.}
-  \label{fig:long}
-  \label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
-  \verb'$conf_a$' &  $conf_a$ \\
-  \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The
-provided \verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et
-alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}''
-is a complete word.)  However, use it only when there are three or
-more authors.  Thus, the following is correct: `` Frobnication has
-been trendy lately.  It was introduced by Alpher~\cite{Alpher02}, and
-subsequently developed by Alpher and
-Fotheringham-Smythe~\cite{Alpher03}, and Alpher
-\etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher
-\etal~\cite{Alpher03} ...''  because reference~\cite{Alpher03} has
-just two authors.  If you use the \verb'\etal' macro provided, then
-you need not worry about double periods when used at the end of a
-sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors12} to
-\cite{Alpher02,Alpher03,Authors12}.
-
-\begin{figure*}
-  \begin{center}
-    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-  \end{center}
-  \caption{Example of a short caption, which should be centered.}
-  \label{fig:short}
-\end{figure*}
-
-% ------------------------------------------------------------------------
-\section{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of
-the text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches
-(22.54 cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide,
-with a $\frac{5}{16}$ inch (0.8 cm) space between them. The main title
-(on the first page) should begin 1.0 inch (2.54 cm) from the top edge
-of the page. The second and following pages should begin 1.0 inch
-(2.54 cm) from the top edge. On all pages, the bottom margin should be
-1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5
-\times 11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13
-cm) from the bottom edge of the page.
-
-% -------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must
-be kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8
-inches (22.54 cm) high.
-
-% -------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither
-is available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge
-of the first page. The title should be in Times 14-point, boldface
-type.  Capitalize the first letter of nouns, pronouns, verbs,
-adjectives, and adverbs; do not capitalize articles, coordinate
-conjunctions, or prepositions (unless the title begins with such a
-word). Leave two blank lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is
-to be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should
-be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a
-third-order heading (we discourage it), use 10-point Times, boldface,
-initially capitalized, flush left, preceded by one blank line,
-followed by a period and your text on the same line.
-
-% -------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-  often distracts the reader from the main flow of the argument.}
-sparingly.  Indeed, try to avoid footnotes altogether and include
-necessary peripheral observations in the text (within parentheses, if
-you prefer, as in this sentence).  If you wish to use a footnote,
-place it at the bottom of the column on the page on which it is
-referenced. Use Times 8-point type, single-spaced.
-
-% -------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors12}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-  \begin{center}
-    \begin{tabular}{|l|c|}
-      \hline
-      Method & Frobnability \\
-      \hline\hline
-      Theirs & Frumpy \\
-      Yours & Frobbly \\
-      Ours & Makes one's heart Frob\\
-      \hline
-    \end{tabular}
-  \end{center}
-  \caption{Results.   Ours is better.}
-\end{table}
-
-% -------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you
-wish to make is resolvable in a printed copy of the paper.  Resize
-fonts in figures to match the font in the body text, and choose line
-widths which render effectively in print.  Many readers (and
-reviewers), even of an electronic copy, will choose to print your
-paper in order to read it.  You cannot insist that they do otherwise,
-and therefore must not assume that they can zoom in to see tiny
-details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the figure width as a multiple
-of the line width as in the example below {\small\begin{verbatim}
-    \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-% -------------------------------------------------------------------------
-\subsection{Color}
-
-Color is valuable, and will be visible to readers of the electronic
-copy.  However ensure that, when printed on a monochrome printer, no
-important information is lost by the conversion to grayscale.
-
-% ------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you
-submit your finished paper. We MUST have this form before your paper
-can be published in the proceedings.
-
-% Please direct any questions to the production editor in charge of
-% these proceedings at the IEEE Computer Society Press: Phone (714)
-% 821-8380, or Fax (714) 761-1784.
+Our alpha blending technique is widely used, and blends pixels
+linearly across overlapping regions. For each pixel within an
+overlapping region, we simply multiply its intensity (by a factor from 0 to
+1), based on its distance from the image's border, with a cap set at some maximum blending distance. In this way, we
+interpolate between two overlapping images, providing a gradual
+transition between them. Increasing the overlapping and blending distance
+results in a smoother transition, but can also result in more
+blurriness. The final output is shown in Figure X.
 

### 2012-06-19 3dimpvt/paperv1.tex
about to kill a bunch of old text from v1

--- 2012-06-18 3dimpvt/paper.tex
@@
 
-\subsection{Occlusion Checking}
+\subsection{Occlusion Masking}
 Before we proceed with texturing our planes, we need to ensure that
@@
 
-\section{Our Approach Overview}
+\section{Our Approach}
 Our approach begins 

### 2012-06-19 3dimpvt/paper.tex
working on localization

@@
 \begin{abstract}
-  Automated 3D modeling of building interiors is useful in applications
-  such as virtual reality and environment mapping. Accurate texture
-  mapping of these models is vital towards visualizing the data
-  gathered by modeling systems and increases overall usability. The
-  localization of cameras in 3D scenes often suffers from inaccuracies, resulting in visible discontinuties
-  when images are directly projected onto a plane for
-  texturing. Previous approaches at minimizing these discontinuities
-  do not robustly handle a wide range of camera locations and angles, and often suffer from error accumulation when stitching together multiple
-  images. We propose two variants on a new approach for reducing discontinuities
-  during texture mapping, one tailored for optimal images, and one tailored for sub-optimal images.
+  Automated 3D modeling of building interiors is useful in
+  applications such as virtual reality and environment
+  mapping. Applying realistic textures to these models is an important
+  step in generating accurate visualizations of data gathered by
+  modeling systems.  Unfortunately, the localization of cameras in
+  such systems often suffer from inaccuracies, resulting in visible
+  discontinuties when different images are projected adjacently onto a
+  plane for texturing. Previous approaches at minimizing these
+  discontinuities do not robustly handle a wide range of camera
+  locations and angles, and often suffer from error accumulation when
+  stitching together multiple images. We propose two approaches for
+  reducing discontinuities during texture mapping, one to robustly
+  accomodate images of all orientations, and one to take advantage of
+  optimal situations where images have uniform orientation.
 \end{abstract}
@@
 errors and greater variance in camera locations. The paper is
-organized as follows. Section \ref{sec:backpackSystem} provides an
-overview of the backpack modeling system from which data and examples
-used throughout this paper originate. Section
-\ref{sec:textureMappingOverview} describes the general problem of 3D
-texture mapping and reviews existing approaches. Section
-\ref{sec:textureMappingMethods} describes our new approach towards texture mapping, as well as unique challenges posed by the
-backpack modeling system and our two approaches tailored for
-walls and floors/ceilings respectively. Section \ref{sec:results}
-compares results and presents conclusions.
+organized as follows. Section 2 provides an overview of the backpack
+modeling system and data processing pipeline from which input data and
+examples used throughout this paper originate. Section 3 describes the
+general problem of texture mapping and examines two simple mapping
+approaches and their problems.  Section 4 demonstrates previous
+attempts at localization refinement, and presents our new approach to
+image alignment. Section 5 combines our image alignment algorithm with
+a simple image selection approach, as well as with a new method for image selection that
+takes advantage of optimal projections. Section 6 contains results and
+conclusions.
 
 \section{Backpack Modeling System}
-\label{sec:backpackSystem}
 Human-operated data acquisition systems provide unique advantages over
@@
 portability. Unfortunately, human-operated systems also suffer from a
-lack of automation and stability, often resulting in much higher data
+lack of automation and stability, resulting in much higher data
 variance and localization error. As a result, common methods for
-texture mapping often produce poor results, as examined in section
-XX. Before discussing how to overcome these challenges, we will first
+texture mapping generally produce poor results, as shown in section
+3. Before discussing how to overcome these challenges, we will first
 provide an overview of the backpack modeling system from which our
@@
 \subsection{Data Acquisition Hardware}
-\label{sec:backpackHardware}
-The backpack modeling system which we worked with contains five 2D
+The backpack modeling system that captured our data contains five 2D
 laser range scanners, two cameras, an orientation sensor, and an
-IMU. The laser scanners have a 30-meter range and a 270$^{\circ}$
-field of view. The two cameras are equipped with fisheye lenses,
-resulting in a 180$^{\circ}$ field of view, and are mounted with one
-facing left and one facing right. The IMU provides highly accurate
-measurements of all 6 DOF at 200Hz, and is used as a ground truth
-reference. The orientation sensor provides orientation parameters at a
-rate of 180Hz.
+IMU. The laser scanners are mounted orthogonally and have a 30-meter
+range and a 270$^{\circ}$ field of view. The two cameras are equipped
+with fisheye lenses, resulting in a 180$^{\circ}$ field of view, and
+are mounted with one facing left and one facing right. These cameras take images at the rate of 5 Hz. The orientation
+sensor provides orientation parameters at a rate of 180 Hz. The IMU
+provides highly accurate measurements of all 6 DOF at 200 Hz, and is
+used as a ground truth reference.
 
-With this backpack actively scanning, a human operator then takes
-great care to walk a path such that every wall in the desired indoor
-environment is passed and scanned lengthwise at least once.
+With the backpack actively scanning, the human operator wearing it
+then takes great care to walk a path such that every wall in the
+desired indoor environment is passed and scanned lengthwise at least
+once.
 
 \subsection{Environment Reconstruction}
-\label{sec:environmentReconstruction}
 Using data gathered by the onboard sensors and multiple localization
-and loop-closure algorithms, the backpack is localized over its data
+and loop-closure algorithms, the backpack is first localized over its data
 collection period, and a 3D point cloud of the surrounding environment
-is constructed based on the laser scanner readings. Approximate normal
+is constructed based on the laser scanner readings relative to the backpack. Approximate normal
 vectors for each point in the point cloud are then calculated by
 gathering neighboring points within a small radius and processing them
-using principal component analysis. These normal vectors allow for the
-classification and grouping of adjacent points into structures such as
-walls, ceilings, floors, and staircases. A RANSAC algorithm is then
-employed to fit polygonal planes to these structured groupings of
-points, resulting in a fully planar model. This planar model,
-consisting of multiple 2D polygonal planes in 3D space, must then be
-textured by all or some subset of the images captured by the
-backpack's camera.
+through principal component analysis. These normal vectors allow for
+the classification and grouping of adjacent points into structures
+such as walls, ceilings, floors, and staircases. A RANSAC algorithm is
+then employed to fit polygonal planes to these structured groupings of
+points, resulting in a fully planar model. This model,
+consisting of multiple 2D polygonal planes in 3D space, along with the
+set of images captured by the backpack's camera, can be considered the
+input to our texture mapping problem.
 
-\subsection{Image Association}
-\label{sec:imageAssociation}
-Before discussing texture mapping, we (something goes here based on whether we take credit for stewarts work or not)
-
-In order to speed up our texture mapping process, it is prudent to
-reduce the amount of potential images being considered for texture
-mapping each plane. The backpack modeling system takes 5
-pictures/second from both cameras, resulting in each plane being
-present in (and capable of being textured mapped by) thousands of
-images, at a wide range of distances and angles. Thus, for the sake of
-efficiency, it makes sense to associate each plane with a much smaller
-list of images, preferably some set which contains the most desirable images
-according to some metric. Thus we keep three criteria in mind while
-selecting such a subset. First, we want our final collection of images
-to be capable of covering the entirety of a plane, so as to ensure
-there are no holes in our final texture. Second, we want all our
-images to be taken from a relatively close distance to the plane, and
-at as much of a direct, head-on angle as possible. This ensures that
-the image projects squarely onto our desired plane, with minimal
-inclusion of other planes, and we end with a texture with high
-resolution. Third, we desire an amount of overlap between the images
-chosen. This overlap provides us with a buffer in case we shift images
-as discussed in Section X, and is also required for the blending
-process presented in Section Y.
-
-To meet these three criteria, we divide each plane into small triangles just a few centimers across. Triangulation is used due to the fairly complex
-geometry of many of our planes, and is accomplished by using a
-standard ear-clipping algorithm followed by further triangular
-tesselation. For each triangle, we gather all images that can be
-projected upon the entirety of the triangle, accounting for occlusion
-with other planes as well, using standard ray-polygon intersection
-tests. Of these images, we then select the best one
-according to the heuristic in equation X, which favors closer distances
-and more head-on projection angles. We also enforce that no two images
-are chosen such that they were taken within 0.5 meters of eachother,
-so as to reduce our overall amount of images. The end result is a
-greatly-reduced set of images such that each one is objectively a good choice for texturing some number of areas on the plane. Furthermore, since cameras are only at good
-angles to triangles near their center of projection, and poor
-candidates for triangles near their edges, images will be chosen such
-that there is high overlap between successive images. With the three criteria satisfied, we have reduced the amount of candidate images for
-each plane from many thousands to around 50-100.
-
-\subsection{Occlusion Checking}
-Before we proceed with texturing our planes, we need to ensure that
-each plane's associated images contain only content that should be
-mapped onto the target plane in question. From the above process,
-images were chosen such that they had an unoccluded view of one or
-more trianglular sections upon a plane. This may not necessarily hold
-true however for all areas of the plane, as demonstrated in figure
-SOMETHING. If images are not modified to mask out occluded areas,
-different images could attempt to cover the same location on a plane
-with drastically different textures, inevitably leading to
-undesireable discontinuities in our final texture.
-
-Fortunately, by virtue of our indoor environments, the vast majority
-of surface geometry is either horizontal or vertical, with high
-amounts of right angles. This means that the areas we wish to mask out
-of our images due to occlusion are nearly always rectangular
-areas. Similar to the triangular tesselation performed for image
-association above, we split each image into rectangular pieces, and
-perform occlusion checks for a sampling of points within each
-piece. For rectangles with occluded points, we then subdivide them
-into smaller rectangles, and repeat the process, until we reach some
-manually-set recursion limit. To actually occlude out rectangles, we
-simply remove their texture, as untextured areas will never be chosen
-for texture mapping. We are now ready to begin the texture mapping
-process.
-
-\section{Texture Mapping Overview}
-\label{sec:textureMappingOverview}
+\section{Simple Texture Mapping}
 
@@
 
-In this section, we will discuss the process of texture mapping a
-single plane, as the texturing of each of our planes is completely
-independent and can be completed in parallel.
+In all subsequent sections, we will discuss the process of texture
+mapping a single plane, as the texturing of each of our planes is
+completely independent and can be completed in parallel.
 
-The geometry of the general texture mapping process is shown in Figure 1.
-
- As
-described in the previous section, we are provided with a set of $M$
-images for each plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
-translates a 3D point in the world coordinate system to a 2D point in
-image $i$'s coordinates. A camera matrix $P_i$ is composed of the
-camera's intrinsic parameters, such as focal length and image center,
-as well as the extrinsic parameters which specify the rotation and
-translation of the camera's position with respect to the world
-coordinates at the time that image $i$ was taken. These extrinsic
-parameters are determined by the localization hardware and algorithms
-mentioned in Section \ref{sec:backpackSystem}. A point $X$ on the
-plane in 3D space can be related to its corresponding pixel $x$ in image $i$
-through the following equation:
+The geometry of the texture mapping process for a plane is shown in
+Figure 1.  As described in the previous section, we are provided with
+a set of $M$ images with which we must texture our target plane. Each
+image has a camera matrix $P_i$ for $i=1..M$, which translates a 3D
+point in the world coordinate system to a 2D point or pixel in image
+$i$'s coordinates. If the 3D world point is not contained in the image, the 2D
+point will simply be outside of the image boundaries. A camera matrix
+$P_i$ is composed of the camera's intrinsic parameters, such as focal
+length and image center, as well as extrinsic parameters which specify
+the rotation and translation of the camera's position in 3D world coordinates at the time that image $i$ was taken. These
+extrinsic parameters are determined by the backpack hardware and
+localization algorithms mentioned in Section 2. A point $X$ on the
+plane in 3D space can be related to its corresponding pixel $x$ in
+image $i$ through the following equation:
 
@@
 
-For the sake of simplicity, we treat all planes as rectangles by generating a minimum bounding box for them.
-Their original vertices can be recovered later as needed, and used to crop any excess texture.
-A plane to be textured is thus defined by its bounding box with corners $C_i$ in
-world coordinates and a normal vector indicating the front facing side
-of the plane. Our goal is to texture this plane using its associated
-images, while eliminating any visual discontinuities or seams that
-would suggest that the plane's texture was not composed of a single
-continuous image.
+For the sake of simplicity, we treat all planes as rectangles by
+generating minimum bounding boxes for them. Since our final textures will be
+stored as standard rectangular images anyway, we can simply leave the
+area between plane boundary and bounding box untextured, or crop it
+out as needed. A plane to be textured is thus defined by a bounding
+box with corners $C_i$ in world coordinates and a normal vector
+indicating the front facing side of the plane. Our goal is to texture
+this plane using images captured by the backpack, while eliminating
+any visual discontinuities or seams that would suggest that the
+plane's texture was not composed of a single continuous image.
 
-\subsection{Naive Mapping}
-\label{sec:naive}
+\subsection{Direct Mapping}
+
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+we can texture the plane by discretizing it into small square
+tiles, generally about 5 pixels across, and picking an image to texture that tile with. In order to
+do this, we must first gather a list of candidate images for each tile
+$t$. These candidate images must contain all four corners of $t$,
+which we can quickly check using the projection method
+above. Furthermore, each candidate image must have been taken at a
+time when its camera had a clear line-of-sight to the center of $t$,
+which can be calculated using standard ray-polygon intersection tests
+between the camera location, our section, and other planes, all in
+world coordinates.
+
+Once we have a list of candidate images for $t$, we must define a
+scoring function in order to compare images and objectively select the
+best one. Since camera localization errors compound over distance, we
+wish to minimize the distance between cameras used for texturing and
+our plane. Additionally, we desire images that project squarely onto
+the plane, maximizing the resolution and amount of useful texture
+available in their projections.
+
+A scoring function to maximize these two criteria is as follows:
+
 \begin{figure}
   \centering
-  \includegraphics[height=1.5in]{naive.png}
-  \caption{The result of naive texture mapping based on the imprecise
-    camera matrices estimated by the localization system.}
-  \label{fig:naive}
+  \includegraphics[height=1.5in]{scoringFunction.png}
+  \caption{For each tile, we want to select an image such that the
+    function $abcdefg/awerw$ is maximized}
+  \label{fig:scoringFunction}
 \end{figure}
 
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-one can texture map the plane by simply applying textures according to
-the image association process and scoring function described in
-Section X. This naive mapping approach independently selects the best
-texture for each trianglular section on the plane, but it also means
-that all of our $M$ images are used for the overall texture, thus
-increasing the potential amount of poor image boundaries.
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{directMapping.png}
+  \caption{The result of direct texture mapping based on locally optimized textures.}
+  \label{fig:directMapping}
+\end{figure}
 
-As Figure \ref{fig:naive} demonstrates, this approach leads to many
-image boundaries with abrupt discontinuities, due to significant
-misalignment between images. One approach also tuned for our datasets
-attempted to minimize these discontinuities through more intelligent
-image selection, making use of spatial and temporal caching
-mechanisms.
+As Figure \ref{fig:directMapping} demonstrates, this approach leads to
+the best texture for each tile independently, but overall results in
+many image boundaries with abrupt discontinuities, due to significant
+misalignment between images.
 
 \subsection{Mapping with Caching}
-In order to reduce the severity of discontinuities between adjacent
-triangles, one can texture them with the same image, if possible,
-eliminating the discontinuity outright, or by two images taken from
-similar positions, such that any texture mismatch is ideally less
-pronounced. This is accomplished by adding a 2-level cache to the
-native mapping approach, and sorting triangles in an order such that
-triangle $t_i$ is adjacent to triangle $t_{i+1}$. When a
-triangle is assigned a texture, the image it selected is added to the
-level 1 cache, and other images that were taken nearby in time and
-location, within a predefined threshold, are added to the level 2
-cache. Each subsequent triangle to be textured then searches through
-the level 1 cache, selecting the best image according to the same
-scoring function, and comparing it to some pre-defined threshold. If
-the best image's score is below this threshold, the level 2 cache is
-then searched, and then finally if necessary, the set of all images is
-searched. In this way, the entire plane is textured, with image reuse prioritized, followed by a preference for nearby images.
+Since discontinuities occur where adjacent tiles select different
+images that do not match up well, it makes sense to take into account
+image choices made by neighboring tiles while selecting the best image
+for a tile. By using the same image across tile boundaries, we
+eliminate the discontinuity altogether. If this is not possible, using
+very similar images will result in less noticeable discontinuities.
 
-This approach is the method previously used by the modeling team
-associated with our dataset. Therefore, we will use it as our baseline
-when comparing other approaches.  The addition of the caching
-structure reduces discontinuities overall, as can be seen in the above
-image. Nevertheless, the amount of remaining discontinuities suggests
-that image selection alone cannot produce seamless textures.  In order
-to produce photorealistic texture mapping, either the camera matrices
-need to be refined such that the localization is pixel accurate,
-resulting in a perfect mapping, or image stitching techniques need to
-be applied to provide this illusion. A commonly-used technique for
-each approach is examined next.
+Similar to a caching mechanism, we select the best image for a tile
+$t$ by searching through two subsets of images for a good candidate
+before searching through the entire set. The first subset of images is
+the set of images selected by adjacent tiles that have already been
+processed. We must first check which images can map to $t$, and then
+of those, we make a choice according to the same scoring function in
+figure \ref{fig:scoringFunction}. Rather than blindly reusing this
+image, we ensure it meets a predefined score threshold to be
+considered a good image. If no good image is found, we then check our
+second subset of images, which consists of images that were taken near
+the images in the first subset, both spatially and temporally. These
+images are not the same as the ones used for neighboring tiles, but
+they were taken at a similar location and time, suggesting that their
+localization and projection will be very similar. Again, if no good
+image is found according to a threshold, we then must search the
+entire set of candidate images.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{caching.png}
+  \caption{The result of adding a caching system to locally optimized textures.}
+  \label{fig:caching}
+\end{figure}
+
+The results of this caching approach are shown above in figure
+\ref{fig:caching}.  Discontinuities have been reduced overall, but the
+amount of remaining seams suggests that image selection
+alone cannot produce seamless textures. The image projections themselves will have to be adjusted in order to reliably produce clean textures.
+
+\section{Localization Refinement}
+In order to produce photorealistic texture mapping, either camera
+matrices need to be refined such that their localization is pixel
+accurate, resulting in a perfect mapping, or image stitching
+techniques need to be applied to provide this illusion. Before
+examining these approaches, we first obtain a set of images to work
+with.
+
+Rather than perform camera or image adjustments across many thousands
+of images, we choose to work with the more limited set of images
+corresponding to those chosen by the direct mapping approach, without
+caching. This set of images constitutes a good candidate set for
+generating a final seamless texture, since it meets three important
+criteria. First, this set of images contains at least one image that
+covers each tile on our plane. Thus, unless extreme changes in
+localization occur, we can ensure that there will be no holes in our
+final texture. Second, since images are all selected according to the
+same scoring function in figure \ref{fig:scoringFunction}, we know
+that our images are all taken at a head-on angle and should project
+onto the plane in similar ways. Third, as a side result of the scoring
+function, selected images are only good candidates for the tiles near
+their center of projection. Thus, there should be plenty of overlap
+between selected images, allowing for some degree of shifting as well
+as blending between them. With this set of images, we now examine two
+approaches towards refining and combining their projections.
 
@@
 
-\section{Our Approach Overview}
-Our approach begins 
-with the projection of all our images onto
+\section{Our Approach}
+Our approach begins with the projection of all our images onto
 separate copies of our plane, such that no projected data is covered
-and lost.
-Tis is done by discretizing the plane into an arbitrary density of points, and projecting each point into the image plane using the camera matrix $P_i$.
-We then perform a series of preprocessing steps to rotate
-and shift each image's projection such that its overlapping regions
-with other projections are as seamless as possible. From here, we assign textures to our planes
-using one of two methods, dependent on whether they are wall planes or
-ceiling/floor planes. The reasoning for this is explained in section
-\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to smooth out
-any remaining seams.
+and lost. Tis is done by discretizing the plane into an arbitrary
+density of points, and projecting each point into the image plane
+using the camera matrix $P_i$. We then perform a series of
+preprocessing steps to rotate and shift each image's projection such
+that its overlapping regions with other projections are as seamless as
+possible. From here, we assign textures to our planes using one of two
+methods, dependent on whether they are wall planes or ceiling/floor
+planes. The reasoning for this is explained in section
+\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to
+smooth out any remaining seams.
 
 \subsection{Hough Transforms}
-Our first step is to use Hough transforms to rotate
-the projected images such that any strong near-vertical features are made completely vertical. This is effective for indoor modeling, since many indoor
+Our first step is to use Hough transforms to rotate the projected
+images such that any strong near-vertical features are made completely
+vertical. This is effective for indoor modeling, since many indoor
 scenes contain strong vertical lines from features such as doors, wall
@@
 \subsection{Localization Refinement}
-Our next step is to try and fix misalignment between overlapping images.
-We do this by fixing
-the locations in 2D. First we find corresponding points between all
-pairs of overlapping images using SIFT matches
-\cite{lowe1999object}. An illustration of this is given in Figure
-\ref{fig:matches}.
-The SIFT matches allow us to determine feature-based $x$ and $y$ distances between two images on the plane, which we can compare against the $x$ and $y$ distances provided by the camera matrices.
-With these data points, we can reevaluate where each image should be projected.
+Our next step is to try and fix misalignment between overlapping
+images.  We do this by fixing the locations in 2D. First we find
+corresponding points between all pairs of overlapping images using
+SIFT matches \cite{lowe1999object}. An illustration of this is given
+in Figure \ref{fig:matches}. The SIFT matches allow us to determine
+feature-based $x$ and $y$ distances between two images on the plane,
+which we can compare against the $x$ and $y$ distances provided by the
+camera matrices. With these data points, we can reevaluate where each
+image should be projected.
 
@@
 In order to objectively decide which set of images accomplishes this,
-we need to decide on an overall cost function. As our goal is to reduce
-the seams that occur where two images meet, a simple cost function is
-the sum of squared pixel differences in overlapping regions between
-every pair of images. This encourages image boundaries to occur in
-featureless areas, such as bare walls, on in areas where images are
-very well aligned.
+we need to decide on an overall cost function. As our goal is to
+reduce the seams that occur where two images meet, a simple cost
+function is the sum of squared pixel differences in overlapping
+regions between every pair of images. This encourages image boundaries
+to occur in featureless areas, such as bare walls, on in areas where
+images are very well aligned.
 
@@
 simplification for the sake of efficiency. Given that our wall-texture
-candidate images were all taken from a head-on angle, and assuming only minor rotations were made earlier, we can reason
-that their projections onto the plane are approximately
-rectangular. By discarding any excess texture and cropping them
-all to be rectangular, our problem becomes the conceptually simpler
-problem of filling a polygon with rectangles, such that the sum of all
-edge costs between each pair of rectangles is minimal. An additional
-benefit of working with rectangular units is that borders between any
-two distinct images in our final texture will be either horizontal or
-vertical. Since most environmental features inside buildings are horizontal
-or vertical, any seams in our texture will intersect them miniimally
-and be less noticeable.
+candidate images were all taken from a head-on angle, and assuming
+only minor rotations were made earlier, we can reason that their
+projections onto the plane are approximately rectangular. By
+discarding any excess texture and cropping them all to be rectangular,
+our problem becomes the conceptually simpler problem of filling a
+polygon with rectangles, such that the sum of all edge costs between
+each pair of rectangles is minimal. An additional benefit of working
+with rectangular units is that borders between any two distinct images
+in our final texture will be either horizontal or vertical. Since most
+environmental features inside buildings are horizontal or vertical,
+any seams in our texture will intersect them miniimally and be less
+noticeable.
 
@@
 
-In rare cases where the vertical dimension of the plane is not entirely
-covered by a chosen image, we are left with a hole where no image was
-chosen to texture. Rather than reverting to a 2D-coverage problem, we
-can elect to simply fill the hole by selecting images in a
+In rare cases where the vertical dimension of the plane is not
+entirely covered by a chosen image, we are left with a hole where no
+image was chosen to texture. Rather than reverting to a 2D-coverage
+problem, we can elect to simply fill the hole by selecting images in a
 greedy fashion, with respect to the same cost function.
@@
 images often have a very low amount of optimal texture relative to the
-projection size. This factor suggests that we should segment our images in some way, as many of our images contain both desired as well as undesired portions.
+projection size. This factor suggests that we should segment our
+images in some way, as many of our images contain both desired as well
+as undesired portions.
 
-Such segmentation
-implies smaller units of texture, which often leads to more images being
-chosen and unfortunately, more boundaries between different images as
-a result. This goes strongly against our approach for texturing walls,
-in which we attempted to minimize the number of images chosen. Nevertheless, boundaries on
-floors and ceilings are less problematic, since floors and ceilings
-tend to have fewer noticeable features.
+Such segmentation implies smaller units of texture, which often leads
+to more images being chosen and unfortunately, more boundaries between
+different images as a result. This goes strongly against our approach
+for texturing walls, in which we attempted to minimize the number of
+images chosen. Nevertheless, boundaries on floors and ceilings are
+less problematic, since floors and ceilings tend to have fewer
+noticeable features.
 
-As shown in the above figure, we define
-a tile length $l1$ as well as an overlap length $l2$, usually about 5
-pixels for each. We then discretize our plane into rectangular tiles
-$l1$x$l1$ in size. Each tile is then associated with a square
-texture of size $(l1+2l2)$x$(l1+2l2)$, such that it shares a large
-overlapping region with its neighboring tiles, allowing for blending afterwards.
-As in wall texturing, rectangles, rather than triangles, are preferred for the high prevalence of horizontal and vertical features, generally light fixtures and floor and ceiling tiles.
+As shown in the above figure, we define a tile length $l1$ as well as
+an overlap length $l2$, usually about 5 pixels for each. We then
+discretize our plane into rectangular tiles $l1$x$l1$ in size. Each
+tile is then associated with a square texture of size
+$(l1+2l2)$x$(l1+2l2)$, such that it shares a large overlapping region
+with its neighboring tiles, allowing for blending afterwards. As in
+wall texturing, rectangles, rather than triangles, are preferred for
+the high prevalence of horizontal and vertical features, generally
+light fixtures and floor and ceiling tiles.
 
-For the actual process of image association, we can reuse the caching method shown earlier.
-This method will balance selection of the best texture for each tile with some amount of image reuse.
-Coupled with image rotation and shifting, as well as the usage of rectangles instead of triangles, we end with a much more seamless texture, even without any blending applied yet, as seen below.
+For the actual process of image association, we can reuse the caching
+method shown earlier. This method will balance selection of the best
+texture for each tile with some amount of image reuse. Coupled with
+image rotation and shifting, as well as the usage of rectangles
+instead of triangles, we end with a much more seamless texture, even
+without any blending applied yet, as seen below.
 
@@
 linearly across overlapping regions. For each pixel within an
-overlapping region, we simply multiply its intensity (by a factor from 0 to
-1), based on its distance from the image's border, with a cap set at some maximum blending distance. In this way, we
-interpolate between two overlapping images, providing a gradual
-transition between them. Increasing the overlapping and blending distance
-results in a smoother transition, but can also result in more
-blurriness. The final output is shown in Figure X.
+overlapping region, we simply multiply its intensity (by a factor from
+0 to 1), based on its distance from the image's border, with a cap set
+at some maximum blending distance. In this way, we interpolate between
+two overlapping images, providing a gradual transition between
+them. Increasing the overlapping and blending distance results in a
+smoother transition, but can also result in more blurriness. The final
+output is shown in Figure X.
 

### 2012-06-19 3dimpvt/_region_.tex
just waiting for some images

@@
 
-\message{ !name(paper.tex) !offset(139) }
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove citations to
-one's own work---in fact it is often impossible to review a paper
-unless the previous citations are known and available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say that
-you are Lucy Smith, it says that you are building on her work.  If you
-are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
-and Jones show in [7]'' and at the end of the paper, include reference
-7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-  \begin{center}
-    An analysis of the frobnicatable foo filter.
-  \end{center}
-
-  In this paper we present a performance analysis of our previous
-  paper [1], and show it to be inferior to all previously known
-  methods.  Why the previous paper was accepted without this analysis
-  is beyond me.
-
-  [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-  \begin{center}
-    An analysis of the frobnicatable foo filter.
-  \end{center}
-
-  In this paper we present a performance analysis of the paper of
-  Smith \etal [1], and show it to be inferior to all previously known
-  methods.  Why the previous paper was accepted without this analysis
-  is beyond me.
-
-  [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a
-  fundamental contribution to human knowledge''.  Nature 381(12),
-  1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to
-that submission in order to explain the differences, just as you would
-if you had previously published related work.  In such cases, include
-the anonymized parallel submission~\cite{Authors12} as additional
-material and cite it as
-\begin{quote} [1] Authors. ``The frobnicatable foo filter'', F\&G 2012
-  Submission ID 324, Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details
-can be found elsewhere, and refer them to a technical report.  For
-conference submissions, the paper must stand on its own, and not {\em
-  require} the reviewer to go to a techreport for further details.
-Thus, you may say in the body of the paper ``further details may be
-found in~\cite{Authors12b}''.  Then submit the techreport as
-additional material.  Again, you may not assume the reviewers will
-read this material.
-
-Sometimes your paper is about a problem which you tested using a tool
-which is widely known to be restricted to a single institution.  For
-example, let's say it's 1969, you have solved a key problem on the
-Apollo lander, and you believe that the CVPR70 audience would like to
-hear about your solution.  The work is a development of your
-celebrated 1968 paper entitled ``Zero-g frobnication: How being the
-only people in the world with access to the Apollo lander source code
-makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how
-to improve our previous work [Anonymous, 1968].  This time we tested
-the algorithm on a lunar lander [name of lander removed for blind
-review]''.  That would be silly, and would immediately identify the
-authors. Instead write the following:
-\begin{quotation}
-  \noindent
-  We describe a system for zero-g frobnication.  This system is new
-  because it handles the following cases: A, B.  Previous systems
-  [Zeus et al. 1968] didn't handle case B properly.  Ours handles it
-  by including a foo term in the bar integral.
-
-  ...
-
-  The proposed system was integrated with the Apollo lunar lander, and
-  went all the way to the moon, don't you know.  It displayed the
-  following behaviours which show how well we solved cases A and B:
-  ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you
-as the authors.  A reviewer might think it likely that the new paper
-was written by Zeus \etal, but cannot make any decision based on that
-guess.  He or she would have to be sure that no other authors could
-have been contracted to solve problem B.
-
-FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.
-
-\begin{figure}[t]
-  \begin{center}
-    \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
-  \end{center}
-  \caption{Example of caption.  It is set in Roman so that mathematics
-    (always set in Roman: $B \sin A = A \sin B$) may be included
-    without an ugly clash.}
-  \label{fig:long}
-  \label{fig:onecol}
+\message{ !name(paper.tex) !offset(204) }
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{scoringFunction.pdf}
+  \caption{For each tile, we want to select an image such that $d$ and $\alpha$ are minimized}
+  \label{fig:scoringFunction}
 \end{figure}
 
-\message{ !name(paper.tex) !offset(325) }
+%\begin{figure}
+%  \centering
+%  \includegraphics[height=1.5in]{directMapping.png}
+%  \caption{The result of direct texture mapping based on locally
+%    optimized textures.}
+%  \label{fig:directMapping}
+%\end{figure}
+\message{ !name(paper.tex) !offset(699) }
 

### 2012-06-19 3dimpvt/paper.tex
just waiting for some images

@@
 image alignment. Section 5 combines our image alignment algorithm with
-a simple image selection approach, as well as with a new method for image selection that
-takes advantage of optimal projections. Section 6 contains results and
-conclusions.
+a simple image selection approach, as well as with a new method for
+image selection that takes advantage of optimal images. Section 6
+contains results.
 
@@
 range and a 270$^{\circ}$ field of view. The two cameras are equipped
-with fisheye lenses, resulting in a 180$^{\circ}$ field of view, and
-are mounted with one facing left and one facing right. These cameras take images at the rate of 5 Hz. The orientation
-sensor provides orientation parameters at a rate of 180 Hz. The IMU
-provides highly accurate measurements of all 6 DOF at 200 Hz, and is
-used as a ground truth reference.
+with fisheye lenses, reaching an approximately 180$^{\circ}$ field of
+view, and are mounted with one facing left and one facing right. These
+cameras take images at the rate of 5 Hz. The orientation sensor
+provides orientation parameters at a rate of 180 Hz. The IMU provides
+highly accurate measurements of all 6 DOF at 200 Hz, and is used as a
+ground truth reference.
 
 With the backpack actively scanning, the human operator wearing it
-then takes great care to walk a path such that every wall in the
-desired indoor environment is passed and scanned lengthwise at least
-once.
+takes great care to walk a path such that every wall in the desired
+indoor environment is passed and scanned lengthwise at least once.
 
@@
 Using data gathered by the onboard sensors and multiple localization
-and loop-closure algorithms, the backpack is first localized over its data
-collection period, and a 3D point cloud of the surrounding environment
-is constructed based on the laser scanner readings relative to the backpack. Approximate normal
-vectors for each point in the point cloud are then calculated by
-gathering neighboring points within a small radius and processing them
-through principal component analysis. These normal vectors allow for
-the classification and grouping of adjacent points into structures
-such as walls, ceilings, floors, and staircases. A RANSAC algorithm is
-then employed to fit polygonal planes to these structured groupings of
-points, resulting in a fully planar model. This model,
+and loop-closure algorithms, the backpack is first localized over its
+data collection period, and a 3D point cloud of the surrounding
+environment is constructed based on the laser scanner readings
+relative to the backpack \cite{chen2010indoor}. Approximate normal vectors for
+each point in the point cloud are then calculated by gathering
+neighboring points within a small radius and processing them through
+principal component analysis. These normal vectors allow for the
+classification and grouping of adjacent points into structures such as
+walls, ceilings, floors, and staircases. A RANSAC algorithm is then
+employed to fit polygonal planes to these structured groupings of
+points, resulting in a fully planar model \cite{sanchez2012point}. This model,
 consisting of multiple 2D polygonal planes in 3D space, along with the
@@
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square
-tiles, generally about 5 pixels across, and picking an image to texture that tile with. In order to
-do this, we must first gather a list of candidate images for each tile
-$t$. These candidate images must contain all four corners of $t$,
-which we can quickly check using the projection method
+we can texture the plane by discretizing it into small square tiles,
+generally about 5 pixels across, and picking an image to texture each
+tile with. We choose to work with rectangular units to ensure that
+borders between any two distinct images in our final texture will be
+either horizontal or vertical. Since most environmental features
+inside buildings are horizontal or vertical, any seams in our texture
+will intersect them miniimally and be less noticeable.
+
+In order to select an image for texturing tile $t$, we must first
+gather a list of candidate images that contain all four of its
+corners, which we can quickly check using the projection method
 above. Furthermore, each candidate image must have been taken at a
@@
 
-A scoring function to maximize these two criteria is as follows:
+A scoring function to maximize these two criteria is shown in figure \ref{fig:scoringFunction}.
 
@@
   \centering
-  \includegraphics[height=1.5in]{scoringFunction.png}
-  \caption{For each tile, we want to select an image such that the
-    function $abcdefg/awerw$ is maximized}
+  \includegraphics[height=1.5in]{scoringFunction.pdf}
+  \caption{For each tile, we find the image that minimizes $d$ and $\alpha$ by maximizing the following equation: $(1/d \cdot (-1 \cdot C) \cdot N)$}
   \label{fig:scoringFunction}
@@
   \centering
-  \includegraphics[height=1.5in]{directMapping.png}
-  \caption{The result of direct texture mapping based on locally optimized textures.}
+  \includegraphics[width=3in]{wall1_naive.jpg}
+  \caption{The result of direct texture mapping based on locally
+    optimized textures.}
   \label{fig:directMapping}
@@
   \centering
-  \includegraphics[height=1.5in]{caching.png}
+  \includegraphics[width=3in]{wall1_cache_full.jpg}
   \caption{The result of adding a caching system to locally optimized textures.}
@@
 as blending between them. With this set of images, we now examine two
-approaches towards refining and combining their projections.
+approaches towards refining and combining their projections, before demonstrating our own.
 
@@
 
-When images are taken of a plane from arbitrary overlapping positions,
+When images of a plane are taken from arbitrary overlapping positions,
 they are related by homography \cite{hz}. Thus, existing
@@
 to appear as waves on the plane. This image was generated after
-careful hand tuning. Many planes that had fewer features simply
-failed. This led to the conclusion that image mosaicing is not a
+careful hand tuning as well. Many planes that had fewer features simply
+failed outright. This leads to the conclusion that image mosaicing is not a
 robust enough solution for reliably texture mapping our dataset.
@@
 correspondences to guide the process. Each image's camera matrix has 6
-degrees of freedom. Previous work has attempted to refine camera
+degrees of freedom that can be adjusted. Previous work on this problem attempted to refine camera
 matrices by solving a non-linear optimization problem
@@
 flexible in that it does not address projection errors, however, it
-provides noticeable benefits while avoiding the error propagation
+provides significant benefits while avoiding the error propagation
 problem.
 
-\section{Our Approach}
+\subsection{Improved Localization through 2D Matching}
 Our approach begins with the projection of all our images onto
 separate copies of our plane, such that no projected data is covered
-and lost. Tis is done by discretizing the plane into an arbitrary
-density of points, and projecting each point into the image plane
-using the camera matrix $P_i$. We then perform a series of
-preprocessing steps to rotate and shift each image's projection such
-that its overlapping regions with other projections are as seamless as
-possible. From here, we assign textures to our planes using one of two
-methods, dependent on whether they are wall planes or ceiling/floor
-planes. The reasoning for this is explained in section
-\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to
-smooth out any remaining seams.
+up and lost. This is done in the same way as the approaches in section
+3. We then perform Hough transforms to rotate these projections
+similarly, and then shift each image's projection such that its
+overlapping regions with other projections are as seamless as
+possible.
 
 \subsection{Hough Transforms}
-Our first step is to use Hough transforms to rotate the projected
-images such that any strong near-vertical features are made completely
-vertical. This is effective for indoor modeling, since many indoor
-scenes contain strong vertical lines from features such as doors, wall
-panels, or rectangular frames.
+Our first step is to use Hough transforms to adjust the rotation of
+projected images. Rather than try and match the orientation of
+features in each image, we simply apply rotations such that any strong
+near-vertical features are made completely vertical. This is effective
+for indoor modeling, since strong features in indoor scenes usually
+contain vertical lines corresponding to doors, wall panels,
+rectangular frames, etc. If features in the environment are not
+vertical, or there are few features overall, this step should be
+skipped.
 
-\subsection{Localization Refinement}
+\subsection{SIFT Feature Matching}
 Our next step is to try and fix misalignment between overlapping
-images.  We do this by fixing the locations in 2D. First we find
-corresponding points between all pairs of overlapping images using
-SIFT matches \cite{lowe1999object}. An illustration of this is given
-in Figure \ref{fig:matches}. The SIFT matches allow us to determine
+images. We do this by first searching for corresponding points between
+all pairs of overlapping images using SIFT feature matching
+\cite{lowe1999object}. An illustration of this is given in Figure
+\ref{fig:matches}. The SIFT matches allow us to determine
 feature-based $x$ and $y$ distances between two images on the plane,
-which we can compare against the $x$ and $y$ distances provided by the
-camera matrices. With these data points, we can reevaluate where each
-image should be projected.
+which will allow us to reevaluate where each image should be projected.
 
 \subsubsection{Robust SIFT Distances using RANSAC}
-
-First we need to ensure that the SIFT-based distances are
-reliable. Since SIFT matches frequently include outliers, the RANSAC
+Since indoor environments often contain repetitive features, such as floor tiles or doors, we need to ensure that our SIFT-based distances are
+reliable. In order to diminish the effect of incorrect matches and outliers, the RANSAC
 framework \cite{fischler1981random} is used for a robust estimate of
 the $x$ and $y$ distances between the two images. The RANSAC framework
-will attempt to build a consensus among the SIFT matches about what
-the true $x$ and $y$ distance is between the two images while ignoring
-the influence of outliers that may skew the results. The framework
+attempts to build a consensus among the SIFT matches between every pair of images, and tries to generate the horizontal and vertical distance between them while ignoring
+the influence of outliers that would skew the results. The framework
 handles the consensus-building machinery, and only requires that two
@@
 outlier threshold to the framework. This means that a SIFT match is
-labeled as an outlier if its $x$ and $y$ distance is not within 10
+labeled as an outlier if its horizontal or vertical distance is not within 10
 pixels of the average distance computed by the fitting function.
@@
 
-There are a total of $M^{2}$ possible pairs of images, however we can
-only measure distances between images that overlap at SIFT feature
+There are a total of $M^{2}$ possible pairs of images, though we only generate distances between images that overlap at SIFT feature
 points. Given these distances and the original image location
-estimates, we solve a least squares problem ($\textrm{min}_{\beta}
+estimates, we can solve a least squares problem ($\textrm{min}_{\beta}
 ||\beta X - y||_2^2 $) to estimate the correct location of the images
-on the plane. The vector $\beta$ of unknowns are the correct $x$ and
-$y$ locations of each image on the plane from $1 \dots M$. Finding the
-correct $x$ and $y$ locations are independent from one another so we
-will only consider the $x$ locations:
+on the plane. The vector $\beta$ of unknowns represent the correct $x$ and
+$y$ locations of each image on the plane from $1 \dots M$. The optimal $x$ and $y$ locations are calculated in the same way, so we
+will only consider the $x$ locations here:
 
@@
 distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based
-distances. The last element in the observation vector is the original
-location of the first image determined by the localization algorithm.
+distances. The last element in the observation vector is the location of the first image determined by its original localization.
 
@@
 
-The $\beta$ that minimizes $||\beta X - y||_2^2$ tells us a set of
+The $\beta$ that minimizes $||\beta X - y||_2^2$ results in a set of
 image locations on the plane that best honors all the SIFT-based
-distance measurements between images. A similar problem is solved for
-the $y$ dimension. In practice there are often cases where there is a
+distance measurements between images. In practice there are often cases where there is a
 break in the chain of images, meaning that no SIFT matches were found
@@
 
-At this point we now have our target plane associated with a list of
-images as well as their rotated and shifted projections upon the
-plane. We are ready to begin assigning these projections to areas of
-our plane for texturing.
+After completing this same process for the $y$ dimension as well, and making the resultant shifts, our image projections should overlap and match eachother with far greater accuracy.
 
-\subsection{Ceiling/Floor Texturing vs. Wall Texturing}
-\label{sec:whydifferent}
-The backpack modeling system, as described in Section
-\ref{sec:backpackHardware}, was designed to prioritize for texturing
-walls. As mentioned previously, the backpack contains two fisheye
-cameras, one aimed directly to the left of the backpack operator, and
-one aimed directly to the right. Thus, in order to texture the ceiling
-above where the operator walked, images from both cameras must be
-combined, with their boundaries meeting overhead. Unlike walls, where
-one image generally spans the entire height of a wall, two images are
-required to span the width of a ceiling. Even more problematic, the
-floor beneath the backpack is physically obscured by the operator's
-body, and thus must be textured by images taken from behind the
-operator or from the side. This problem of distant cameras at poor
-angles is compounded by the fact that the operator's data acquisition
-path attempts to fully scan each wall, but not necessarily the
-entirety of a floor or ceiling. This means that large swaths of floors
-and ceilings are never walked directly over or under, and thus must be
-textured by sidelong images taken from further distances and at
-oblique angles. These effects are shown in the following figure.
+\section{Improved Texture Mapping with Localization and Blending}
+Now that our images have been relocalized for much greater accuracy relative to eachother, we can revisit the cached mapping approach from section 3.2.
+Since we now have higher confidence in the quality of image boundaries, we can also explore an alternate method that greatly reduces seams in cases where we have an abundance of optimal images.
 
-In short, these factors mean that wall planes are generally associated
-with a multitude of upright, uniform images, from a relatively close
-distance and taken head-on at regular intervals, while floors and
-ceilings are associated with images taken from all manner of
-orientations and distances. This major difference suggests we employ
-two strategies, one tailored for each scenario.
+\subsection{Localized Mapping with Caching}
+In figure \ref{fig:shifted}, we see the same wall from section 3,
+texture mapped using the caching method, both without and with
+localization for comparison.
 
-\subsection{Texturing Walls}
-Because wall images tend to all be fairly good candidates for
-texturing due to their orientation and location, our goal is less
-about determining the best images, and more about selecting a set of
-images that together form the most seamless texture.
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
+  \caption{Localization refinement results in signifcantly fewer
+    discontinuities in the final texture.}
+  \label{fig:shifted}
+\end{figure}
 
-\subsubsection{Cost Functions}
+It should be evident that our localization adjustments resulted in a
+major improvement. A great strength of our tiling approach for image
+selection is that it runs regardless of plane geometry or orientation,
+and can handle images of all types. For example, here is the approach
+as run on a ceiling and floor plane, both of which contain a multitude
+of non-optimal images due to the camera locations on the backpack.
 
-In order to objectively decide which set of images accomplishes this,
-we need to decide on an overall cost function. As our goal is to
-reduce the seams that occur where two images meet, a simple cost
-function is the sum of squared pixel differences in overlapping
-regions between every pair of images. This encourages image boundaries
-to occur in featureless areas, such as bare walls, on in areas where
-images are very well aligned.
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=3in]{localized_caching_ceiling.png}
+%   \caption{Using the graph-based localization refinement algorithm
+%   from [11] suffers from the problem of compounding errors. }
+%   \label{fig:graph}
+% \end{figure}
 
-Another possible cost function is edge energy, i.e. the sum of the
-smoothed gradient of the blended seam regions. Minimizing this
-encourages image boundaries to be placed in featureless areas even
-more than the first cost function. For the results shown throughout
-this paper, the first cost function was used, as the regular
-occurrence of featureless areas was not guaranteed in our datasets.
+Given that the backpack system's hardware and the data collection
+process do strive to collect optimal images for walls however, we can
+be less reserved when texturing walls, and simply fall back to this
+more robust approach as needed.
+
+\subsection{Texture Mapping with Seam Minimization}
+The cached tile approach selected images based on individual quality
+and neighboring quality, in an effort to reduce seams between
+tiles. In a more optimal case, as the backpack system provides for
+walls, images all have near-rectangular projections and thus a great
+score according to the scoring function in figure
+\ref{fig:scoringFunction}. Thus, we can reason that rather than
+selecting the set of best images, since all images are good, we should
+instead select the best set of images, such that the selection results
+in the cleanest texture possible. We will accomplish this by using
+entire images where possible, defining a cost function between images,
+and seeking to maximize our total cost.
+
+\subsection{Occlusion Masking}
+Before we proceed with using our images, we need to ensure that they
+contain only content that should be mapped onto the target plane in
+question. The tiling approach used previously only checked occlusion
+for each tile as it was being textured, so we need to perform
+occlusion checks over the entirety of each image, so we know which
+areas are available for texture mapping. By performing the same
+intersection tests used for tiles, we can determine whether individual
+sections of an image are occluded.
+
+Fortunately, by virtue of our indoor environments, the vast majority
+of surface geometry is either horizontal or vertical, with high
+amounts of right angles. This means that after masking out occluded
+areas, our image projections will remain largely rectangular. We can
+thus recursively split each image into rectangular pieces, and perform
+occlusion checks, similar to the process done for tiles earlier. To
+actually occlude out rectangles, we simply remove their texture, as we
+will ensure that untextured areas are never chosen for texture
+mapping.
+
+\subsubsection{Inter-Image Cost Functions}
+In order to objectively decide which set of images results in the
+cleanest texture, we need a cost function such that we can evaluate
+the visibiilty of seams between images in our set. A straightforward
+cost function that accomplishes this is the sum of squared pixel
+differences in overlapping regions between all pairs of
+images. Minimizing this cost function encourages image boundaries to
+occur in featureless areas, such as bare walls, as well as in areas
+where images match extremely accurately.
+
+Another possible cost function is overall edge energy, i.e. the sum of
+the smoothed gradient over seams. Minimizing this encourages image
+boundaries to be placed in featureless areas even more than the first
+cost function. For the results shown throughout this paper, the first
+cost function was used, as the regular occurrence of featureless areas
+was not guaranteed in our datasets, and our image matches do in fact
+match at the pixel level in many cases.
 
@@
 
-Now that we have a cost function defined, we need to mechanically
-select the set of images for which the overall cost function is
-minimized. Since we aim to cover the entirety of our plane, our
-problem is to minimally cover a polygon(our plane) using other
-polygons of arbitrary geometry (our image projections), with the added
-constraint of minimizing our cost function. This is a complex problem,
-though it can be generalized to a number of graph coverage problems,
-as depicted in figure X. Returning again to the optimality of our
-situation when texturing walls however, we can make a quick
-simplification for the sake of efficiency. Given that our wall-texture
-candidate images were all taken from a head-on angle, and assuming
-only minor rotations were made earlier, we can reason that their
-projections onto the plane are approximately rectangular. By
-discarding any excess texture and cropping them all to be rectangular,
-our problem becomes the conceptually simpler problem of filling a
-polygon with rectangles, such that the sum of all edge costs between
-each pair of rectangles is minimal. An additional benefit of working
-with rectangular units is that borders between any two distinct images
-in our final texture will be either horizontal or vertical. Since most
-environmental features inside buildings are horizontal or vertical,
-any seams in our texture will intersect them miniimally and be less
-noticeable.
+Now that we have a cost function defined, we mechanically select the
+set of images for which the overall cost function is minimized. Since
+we aim to cover the entirety of our plane, our problem is to minimally
+cover a polygon(our plane), using other polygons of arbitrary geometry
+(our image projections), with the added constraint of minimizing our
+cost function between chosen images. This is a complex problem, though
+we can take a number of steps to simplify it. Returning again to the
+optimality of our situation when texturing walls however, we can make
+a quick simplification for the sake of efficiency. Given that our
+wall-texture candidate images were all taken from a head-on angle, and
+assuming only minor rotations were made during localization
+refinement, we can reason that their projections onto the plane are
+approximately rectangular. By discarding the minor excess texture and
+cropping them all to be rectangular, our problem becomes the
+conceptually simpler problem of filling a polygon with rectangles,
+such that the sum of all edge costs between each pair of rectangles is
+minimal. We thus also retain axis-aligned image boundaries, along with
+their advantages explained in section 3.
 
 By taking one more shortcut we can simplify our problem down even
-further. Since care is taken such that our wall images contain the
-floor-to-ceiling range of walls, we generally do not have any wall
-images such that one should be projected vertically above the
-other. In essence, we need only to ensure horizontal coverage of our
-planes, as our images provide full vertical coverage. We can thus
-construct a Directed Acyclic Graph (DAG) from the images, again with
-edge costs defined by our cost function above, and solve a simple
-shortest path problem to find an optimal subset of images with regard
-to the cost functions.
+further. Since this approach is already assuming optimal images, we
+know it will be applied only on walls, which are the focus of the
+backpack modeling system. For wall planes, care is taken so that
+images contain the entirety of their floor-to-ceiling range, and thus
+we do not have wall images such that one should be projected
+vertically above the other. In essence, we need only to ensure
+horizontal coverage of our planes, as our images provide full vertical
+coverage themselves. We can thus construct a Directed Acyclic Graph
+(DAG) from the images, again with edge costs defined by our cost
+function above, and solve a simple shortest path problem to find an
+optimal subset of images with regard to the cost functions.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{DynProg.pdf}
-  \caption{Image Selection is done by constructing a graph of sorted
-    images. Then we solve a shortest path problem where the edge
-    weights represent the cost of a seam between two overlapping
-    images.}
-  \label{fig:DynProg}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=3in]{DynProg.pdf}
+%  \caption{Image Selection is done by constructing a graph of sorted
+%    images. Then we solve a shortest path problem where the edge
+%    weights represent the cost of a seam between two overlapping
+%    images.}
+%  \label{fig:DynProg}
+%\end{figure}
 
@@
 problem, we can elect to simply fill the hole by selecting images in a
-greedy fashion, with respect to the same cost function.
+greedy fashion with respect to the same cost function.
 
-At this point, we have mapped every location on our plane to an image
-or images that were selected. Before applying these textures, we will
-examine how to accomplish the same mapping for ceilings and floors.
+With this completed, we have now mapped every location on our plane to
+at least one image, and have minimized the amount of images, as well
+as the discontinuity between their borders. In the next section, we
+will apply blending between images where they overlap, but for the
+sake of comparison with the unblended tile caching method in section
+5.1, we arbitrarily pick one image for texturing where images
+overlap. The following images compare the tile caching method against
+this seam minimization method.
 
-\subsection{Texturing Ceilings and Floors}
+%\begin{figure}
+%  \centering
+%  \includegraphics[height=2in]{compare_wall.png}
+%  \caption{Planes are specified in 3D space by four corners $C_1$ to
+%    $C_4$. Images are related to each plane through the camera
+%    matrices $P_{1..M}$. }
+  % \caption{The plane is specified in 3D space by the four corners
+  % $C_1$ to $C_4$. Images are related to the plane through the camera
+  % matrices $P_{1..M}$. For example, the 3D point X in the world
+  % coordinate system is related to the image point x shown in the
+  % figure as $x = P_i X$.}
+%  \label{fig:compare_wall}
+%\end{figure}
 
-Because the images associated with ceilings and floors are often
-captured by cameras at sidelong angles, we must be conservative when
-we texture map them. Since localization errors compound over distance,
-we often have candidate images that project well on areas near the
-camera itself, but much more poorly at the greater distances caused by
-higher angles. Using entire images to minimize seams is beneficial for
-wall texturing, but it becomes detrimental on ceilings and floors,
-since the quality of usable texture varies greatly across any one
-image. As evident in the following comparison, ceiling and floor
-images often have a very low amount of optimal texture relative to the
-projection size. This factor suggests that we should segment our
-images in some way, as many of our images contain both desired as well
-as undesired portions.
+Though both methods provide quite accurate texturing thanks to the
+localization refinement process, the seam minimization approach
+results in fewer visible discontinuities, since it directly reduces
+the cost of each image boundary, while the tile caching method uses a
+scoring function that only approximates this effect. Furthermore, seam
+minimization guarantees the best selection of images, while the tile
+caching method may select images early on that turn out to be poor
+choices once subsequent tiles have been processed. This can be a
+problem when localization refinement does not work perfectly. Such an
+effect can be seen in the following image.
 
-Such segmentation implies smaller units of texture, which often leads
-to more images being chosen and unfortunately, more boundaries between
-different images as a result. This goes strongly against our approach
-for texturing walls, in which we attempted to minimize the number of
-images chosen. Nevertheless, boundaries on floors and ceilings are
-less problematic, since floors and ceilings tend to have fewer
-noticeable features.
-
-As shown in the above figure, we define a tile length $l1$ as well as
-an overlap length $l2$, usually about 5 pixels for each. We then
-discretize our plane into rectangular tiles $l1$x$l1$ in size. Each
-tile is then associated with a square texture of size
-$(l1+2l2)$x$(l1+2l2)$, such that it shares a large overlapping region
-with its neighboring tiles, allowing for blending afterwards. As in
-wall texturing, rectangles, rather than triangles, are preferred for
-the high prevalence of horizontal and vertical features, generally
-light fixtures and floor and ceiling tiles.
-
-For the actual process of image association, we can reuse the caching
-method shown earlier. This method will balance selection of the best
-texture for each tile with some amount of image reuse. Coupled with
-image rotation and shifting, as well as the usage of rectangles
-instead of triangles, we end with a much more seamless texture, even
-without any blending applied yet, as seen below.
+In the context of the backpack modeling system, we apply the seam
+minimization approach on walls, due to its superior output when
+provided with optimal images. Floors and ceilings however, given their
+suboptimal images which require segmentation, are textured using the
+tile caching method.
 
 \subsection{Blending}
-Though our preprocessing steps and image selection attempts above
-attempted to minimize all mismatches between images, there are often
-cases, where due to geometry or projection inaccuracies, we simply
-have unavoidable discontinuities. These can however be partially
-treated by applying alpha blending over our seams.  Whether the units
-we are blending are rectangularly-cropped images for walls, or
-rectangular units for ceilings/floors, we can apply the same blending
-procedure.
+Until now, blending of images has not been used, for the sake of clear
+comparisons between texturing methods. We will now apply the same
+blending process on our two final texturing methods: localization
+refinement followed by either tile caching or seam minimization.
+
+Although our preprocessing steps and image selections in either method
+attempt to minimize all mismatches between images, there are cases,
+where due to different lighting conditions or inaccuracies in geometry
+or projection, where we simply have unavoidable discontinuities. These
+can however be treated and smoothed over by applying alpha blending
+over image seams.  Whether the units we are blending are
+rectangularly-cropped images or rectangular tiles, we can apply the
+same blending procedure, as long as we have a guaranteed overlap
+between units.
+
+For the tile caching method, we can ensure overlap by texturing a
+larger tile than we really have. For example, for a tile $l_1 x l_1$
+in size, we can make sure to associate it with a texture $(l_1 + l_2)
+x (l_1 + l_2)$ in size. For the seam minimization method, we have
+already ensured overlap between images. To enforce consistent blending
+however, it is beneficial to add a required overlap distance while
+solving the shortest path problem in section 5.2.3. If images do not
+overlap in a region at least the length of this overlap distance, we
+do not consider them to overlap at all. If images overlap in a region
+greater than the overlap distance, we will only apply blending over an
+area equal to the overlap distance.
 
 Our alpha blending technique is widely used, and blends pixels
-linearly across overlapping regions. For each pixel within an
-overlapping region, we simply multiply its intensity (by a factor from
-0 to 1), based on its distance from the image's border, with a cap set
-at some maximum blending distance. In this way, we interpolate between
-two overlapping images, providing a gradual transition between
-them. Increasing the overlapping and blending distance results in a
-smoother transition, but can also result in more blurriness. The final
-output is shown in Figure X.
+linearly across overlapping regions. For each pixel within such a
+region, we simply scale its intensity (by a factor from 0 to 1),
+based on its distance from the image's border, with a cap set at a fixed distance from the border. In this way, we interpolate between two
+overlapping images, providing a gradual transition between
+them. Increasing the blending distance results in a
+smoother transition, but can also result in more blurriness. A blended and unblended version of each method is shown below for comparison.
+
+%\begin{figure}
+%5  \centering
+ % \includegraphics[height=2in]{compare_blending.png}
+%  \caption{Planes are specified in 3D space by four corners $C_1$ to
+%    $C_4$. Images are related to each plane through the camera
+%    matrices $P_{1..M}$. }
+%  % \caption{The plane is specified in 3D space by the four corners
+  % $C_1$ to $C_4$. Images are related to the plane through the camera
+  % matrices $P_{1..M}$. For example, the 3D point X in the world
+  % coordinate system is related to the image point x shown in the
+  % figure as $x = P_i X$.}
+%  \label{fig:compare_blending}
+%\end{figure}
+
+\section{Conclusion and Results}
+In this paper, we have shown how to accurately texture map models,
+even when provided with imprecise camera localization data. We have
+generalized one approach to any manner of planes and images, and
+successfully textured both simple rectangular walls as well as complex
+floor and ceiling geometry. We have also presented an optimized
+texturing method that takes advantage of our localization refinement
+process and produces cleaner textures on planes where multiple head-on
+images are available. Ceilings and floors textured with the robust
+approach, and walls textured with the optimized approach, are
+displayed in the remainder of this paper. A more detailed walkthrough
+demonstrating fully textured models using the approaches in this paper
+can be seen in the accompanying video to this paper.
 

### 2012-06-20 3dimpvt/paper.tex
draft 1 ready i hope

@@
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{cvpr} \usepackage{times} \usepackage{epsfig}
+\usepackage{graphicx} \usepackage{amsmath} \usepackage{amssymb}
+\usepackage{subfig}
 
@@
 % If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first
+% latex run, let it finish, and you should be clear).
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
@@
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
+% Pages are numbered in submission mode, and unnumbered in
+% camera-ready
 \ifcvprfinal\pagestyle{empty}\fi
@@
 environment is constructed based on the laser scanner readings
-relative to the backpack \cite{chen2010indoor}. Approximate normal vectors for
-each point in the point cloud are then calculated by gathering
-neighboring points within a small radius and processing them through
-principal component analysis. These normal vectors allow for the
-classification and grouping of adjacent points into structures such as
-walls, ceilings, floors, and staircases. A RANSAC algorithm is then
-employed to fit polygonal planes to these structured groupings of
-points, resulting in a fully planar model \cite{sanchez2012point}. This model,
-consisting of multiple 2D polygonal planes in 3D space, along with the
-set of images captured by the backpack's camera, can be considered the
-input to our texture mapping problem.
+relative to the backpack \cite{chen2010indoor}. Approximate normal
+vectors for each point in the point cloud are then calculated by
+gathering neighboring points within a small radius and processing them
+through principal component analysis. These normal vectors allow for
+the classification and grouping of adjacent points into structures
+such as walls, ceilings, floors, and staircases. A RANSAC algorithm is
+then employed to fit polygonal planes to these structured groupings of
+points, resulting in a fully planar model
+\cite{sanchez2012point}. This model, consisting of multiple 2D
+polygonal planes in 3D space, along with the set of images captured by
+the backpack's camera, can be considered the input to our texture
+mapping problem.
 
@@
 point in the world coordinate system to a 2D point or pixel in image
-$i$'s coordinates. If the 3D world point is not contained in the image, the 2D
-point will simply be outside of the image boundaries. A camera matrix
-$P_i$ is composed of the camera's intrinsic parameters, such as focal
-length and image center, as well as extrinsic parameters which specify
-the rotation and translation of the camera's position in 3D world coordinates at the time that image $i$ was taken. These
+$i$'s coordinates. If the 3D world point is not contained in the
+image, the 2D point will simply be outside of the image boundaries. A
+camera matrix $P_i$ is composed of the camera's intrinsic parameters,
+such as focal length and image center, as well as extrinsic parameters
+which specify the rotation and translation of the camera's position in
+3D world coordinates at the time that image $i$ was taken. These
 extrinsic parameters are determined by the backpack hardware and
@@
 For the sake of simplicity, we treat all planes as rectangles by
-generating minimum bounding boxes for them. Since our final textures will be
-stored as standard rectangular images anyway, we can simply leave the
-area between plane boundary and bounding box untextured, or crop it
-out as needed. A plane to be textured is thus defined by a bounding
-box with corners $C_i$ in world coordinates and a normal vector
-indicating the front facing side of the plane. Our goal is to texture
-this plane using images captured by the backpack, while eliminating
-any visual discontinuities or seams that would suggest that the
-plane's texture was not composed of a single continuous image.
+generating minimum bounding boxes for them. Since our final textures
+will be stored as standard rectangular images anyway, we can simply
+leave the area between plane boundary and bounding box untextured, or
+crop it out as needed. A plane to be textured is thus defined by a
+bounding box with corners $C_i$ in world coordinates and a normal
+vector indicating the front facing side of the plane. Our goal is to
+texture this plane using images captured by the backpack, while
+eliminating any visual discontinuities or seams that would suggest
+that the plane's texture was not composed of a single continuous
+image.
 
@@
 
-A scoring function to maximize these two criteria is shown in figure \ref{fig:scoringFunction}.
+A scoring function to maximize these two criteria is shown in figure
+\ref{fig:scoringFunction}.
 
@@
   \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{For each tile, we find the image that minimizes $d$ and $\alpha$ by maximizing the following equation: $(1/d \cdot (-1 \cdot C) \cdot N)$}
+  \caption{For each tile, we find the image that minimizes $d$ and
+    $\alpha$ by maximizing the following equation: \\ $(1/d \cdot (-1
+    \cdot C) \cdot N)$}
   \label{fig:scoringFunction}
@@
   \includegraphics[width=3in]{wall1_cache_full.jpg}
-  \caption{The result of adding a caching system to locally optimized textures.}
+  \caption{The result of adding a caching system to locally optimized
+    textures.}
   \label{fig:caching}
@@
 \ref{fig:caching}.  Discontinuities have been reduced overall, but the
-amount of remaining seams suggests that image selection
-alone cannot produce seamless textures. The image projections themselves will have to be adjusted in order to reliably produce clean textures.
+amount of remaining seams suggests that image selection alone cannot
+produce seamless textures. The image projections themselves will have
+to be adjusted in order to reliably produce clean textures.
 
@@
 as blending between them. With this set of images, we now examine two
-approaches towards refining and combining their projections, before demonstrating our own.
+approaches towards refining and combining their projections, before
+demonstrating our own.
 
@@
 to appear as waves on the plane. This image was generated after
-careful hand tuning as well. Many planes that had fewer features simply
-failed outright. This leads to the conclusion that image mosaicing is not a
-robust enough solution for reliably texture mapping our dataset.
+careful hand tuning as well. Many planes that had fewer features
+simply failed outright. This leads to the conclusion that image
+mosaicing is not a robust enough solution for reliably texture mapping
+our dataset.
 
@@
 correspondences to guide the process. Each image's camera matrix has 6
-degrees of freedom that can be adjusted. Previous work on this problem attempted to refine camera
-matrices by solving a non-linear optimization problem
-\cite{liu2010indoor}. This process is specific to the backpack system
-which generated our dataset, as it must be run during backpack
+degrees of freedom that can be adjusted. Previous work on this problem
+attempted to refine camera matrices by solving a non-linear
+optimization problem \cite{liu2010indoor}. This process is specific to
+the backpack system which generated our dataset, as it must be run
+during backpack
 localization\cite{liu2010indoor,chen2010indoor}. Unfortunately, this
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{matches.jpg}
+  \caption{SIFT feature matches between overlapping images.}
+  \label{fig:matches}
+\end{figure}
+
 \subsection{SIFT Feature Matching}
@@
 feature-based $x$ and $y$ distances between two images on the plane,
-which will allow us to reevaluate where each image should be projected.
+which will allow us to reevaluate where each image should be
+projected.
 
 \subsubsection{Robust SIFT Distances using RANSAC}
-Since indoor environments often contain repetitive features, such as floor tiles or doors, we need to ensure that our SIFT-based distances are
-reliable. In order to diminish the effect of incorrect matches and outliers, the RANSAC
-framework \cite{fischler1981random} is used for a robust estimate of
-the $x$ and $y$ distances between the two images. The RANSAC framework
-attempts to build a consensus among the SIFT matches between every pair of images, and tries to generate the horizontal and vertical distance between them while ignoring
-the influence of outliers that would skew the results. The framework
+Since indoor environments often contain repetitive features, such as
+floor tiles or doors, we need to ensure that our SIFT-based distances
+are reliable. In order to diminish the effect of incorrect matches and
+outliers, the RANSAC framework \cite{fischler1981random} is used for a
+robust estimate of the $x$ and $y$ distances between the two
+images. The RANSAC framework attempts to build a consensus among the
+SIFT matches between every pair of images, and tries to generate the
+horizontal and vertical distance between them while ignoring the
+influence of outliers that would skew the results. The framework
 handles the consensus-building machinery, and only requires that two
@@
 outlier threshold to the framework. This means that a SIFT match is
-labeled as an outlier if its horizontal or vertical distance is not within 10
-pixels of the average distance computed by the fitting function.
+labeled as an outlier if its horizontal or vertical distance is not
+within 10 pixels of the average distance computed by the fitting
+function.
 
@@
 
-There are a total of $M^{2}$ possible pairs of images, though we only generate distances between images that overlap at SIFT feature
+There are a total of $M^{2}$ possible pairs of images, though we only
+generate distances between images that overlap at SIFT feature
 points. Given these distances and the original image location
@@
 ||\beta X - y||_2^2 $) to estimate the correct location of the images
-on the plane. The vector $\beta$ of unknowns represent the correct $x$ and
-$y$ locations of each image on the plane from $1 \dots M$. The optimal $x$ and $y$ locations are calculated in the same way, so we
+on the plane. The vector $\beta$ of unknowns represent the correct $x$
+and $y$ locations of each image on the plane from $1 \dots M$. The
+optimal $x$ and $y$ locations are calculated in the same way, so we
 will only consider the $x$ locations here:
@@
 distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based
-distances. The last element in the observation vector is the location of the first image determined by its original localization.
+distances. The last element in the observation vector is the location
+of the first image determined by its original localization.
 
@@
 image locations on the plane that best honors all the SIFT-based
-distance measurements between images. In practice there are often cases where there is a
-break in the chain of images, meaning that no SIFT matches were found
-between one segment of the plane and another. In this case we add rows
-to the $X$ matrix and observations to the $y$ vector that contain the
-original $x$ and $y$ distance estimates generated by the localization
-algorithm. Another way to do this is to add rows for all neighboring
-pairs of images and solve a weighted least squares problem where the
-SIFT distances are given a higher weight i.e. 1, and the distances
-generated by the localization algorithm are given a smaller weight
-i.e. 0.01.
+distance measurements between images. In practice there are often
+cases where there is a break in the chain of images, meaning that no
+SIFT matches were found between one segment of the plane and
+another. In this case we add rows to the $X$ matrix and observations
+to the $y$ vector that contain the original $x$ and $y$ distance
+estimates generated by the localization algorithm. Another way to do
+this is to add rows for all neighboring pairs of images and solve a
+weighted least squares problem where the SIFT distances are given a
+higher weight i.e. 1, and the distances generated by the localization
+algorithm are given a smaller weight i.e. 0.01.
 
-After completing this same process for the $y$ dimension as well, and making the resultant shifts, our image projections should overlap and match eachother with far greater accuracy.
+After completing this same process for the $y$ dimension as well, and
+making the resultant shifts, our image projections should overlap and
+match eachother with far greater accuracy.
 
 \section{Improved Texture Mapping with Localization and Blending}
-Now that our images have been relocalized for much greater accuracy relative to eachother, we can revisit the cached mapping approach from section 3.2.
-Since we now have higher confidence in the quality of image boundaries, we can also explore an alternate method that greatly reduces seams in cases where we have an abundance of optimal images.
+Now that our images have been relocalized for much greater accuracy
+relative to eachother, we can revisit the cached mapping approach from
+section 3.2. Since we now have higher confidence in the quality of
+image boundaries, we can also explore an alternate method that greatly
+reduces seams in cases where we have an abundance of optimal images.
 
@@
 In figure \ref{fig:shifted}, we see the same wall from section 3,
-texture mapped using the caching method, both without and with
-localization for comparison.
+texture mapped using the caching method after our localization
+refinement process.
 
@@
 major improvement. A great strength of our tiling approach for image
-selection is that it runs regardless of plane geometry or orientation,
-and can handle images of all types. For example, here is the approach
-as run on a ceiling and floor plane, both of which contain a multitude
-of non-optimal images due to the camera locations on the backpack.
+selection is that it extracts the areas with good camera angles from
+each image, and thus can handle images of all types. As demonstrated
+on the floor plane in figure \ref{fig:floor_suboptimal}, we can run
+this process even with extremely poor image projections, where the
+amount of quality texture for each image is limited. Additionally,
+since our plane is discretized, we can easily handle arbitrarily
+complex planes as well.
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=3in]{localized_caching_ceiling.png}
-%   \caption{Using the graph-based localization refinement algorithm
-%   from [11] suffers from the problem of compounding errors. }
-%   \label{fig:graph}
-% \end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{floor_suboptimal.jpg}
+  \caption{The tiling method ensures that only the most optimal
+    portions of each image are used. This allows it to successfully
+    handle all manner of plane and image geometry, as shown in this
+    floor texture.}
+  \label{fig:floor_suboptimal}
+\end{figure}
 
 Given that the backpack system's hardware and the data collection
-process do strive to collect optimal images for walls however, we can
-be less reserved when texturing walls, and simply fall back to this
-more robust approach as needed.
+process strive for optimal wall texturing however, we can aim for a
+less conservative approach when texturing walls, and simply fall back
+to this more robust approach as needed.
 
 \subsection{Texture Mapping with Seam Minimization}
-The cached tile approach selected images based on individual quality
-and neighboring quality, in an effort to reduce seams between
-tiles. In a more optimal case, as the backpack system provides for
-walls, images all have near-rectangular projections and thus a great
-score according to the scoring function in figure
-\ref{fig:scoringFunction}. Thus, we can reason that rather than
-selecting the set of best images, since all images are good, we should
-instead select the best set of images, such that the selection results
-in the cleanest texture possible. We will accomplish this by using
-entire images where possible, defining a cost function between images,
-and seeking to maximize our total cost.
+The cached tile approach selected images based on individual and
+neighboring quality of image selections, in an effort to reduce seams
+between tiles. In a more optimal case, as the backpack system provides
+for walls, images are all taken from close distances and have
+near-rectangular projections and thus a great score according to the
+scoring function in figure \ref{fig:scoringFunction}. Thus, we can
+reason that rather than selecting the set of best images, since all
+images are good, we should instead select the best set of images, such
+that the selection together results in the cleanest final texture. We
+will accomplish this by using entire images where possible, defining a
+cost function between images, and seeking to minimize our total cost.
 
@@
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[width=3in]{DynProg.pdf}
-%  \caption{Image Selection is done by constructing a graph of sorted
-%    images. Then we solve a shortest path problem where the edge
-%    weights represent the cost of a seam between two overlapping
-%    images.}
-%  \label{fig:DynProg}
-%\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{dagCreation.pdf}
+  \caption{DAG construction for the image selection process.}
+  \label{fig:dagCreation}
+\end{figure}
 
-Figure \ref{fig:DynProg} demonstrates the construction of a DAG from
-overlapping images of a long hallway. Images are sorted by horizontal
-location left to right, and become nodes in a graph. Directed edges
-are placed in the graph from left to right between images that
-overlap. The weights of these edges are determined by the cost
-functions discussed previously. Next, we add two artificial nodes, one
-start node representing the left border of the plane, and one end node
-representing the right border of the plane. The left artificial node
-has directed edges with equal cost to all images that meet the left
-border of the plane, and the right artificial node has directed edges
-from all images that meet the right border of the plane.
+Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
+from overlapping images of a long hallway. Images are sorted by
+horizontal location left to right, and become nodes in a
+graph. Directed edges are placed in the graph from left to right
+between images that overlap. The weights of these edges are determined
+by the cost functions discussed previously. Next, we add two
+artificial nodes, one start node representing the left border of the
+plane, and one end node representing the right border of the
+plane. The left artificial node has directed edges with equal cost
+$C_0$ to all images that meet the left border of the plane, and the
+right artificial node has directed edges from all images with that
+meet the right border of the plane, with equal cost $C_0$ as well.
 
@@
 5.1, we arbitrarily pick one image for texturing where images
-overlap. The following images compare the tile caching method against
-this seam minimization method.
+overlap. Figure \ref{fig:compare_unblended} compares the tile caching
+method against this seam minimization method.
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[height=2in]{compare_wall.png}
-%  \caption{Planes are specified in 3D space by four corners $C_1$ to
-%    $C_4$. Images are related to each plane through the camera
-%    matrices $P_{1..M}$. }
-  % \caption{The plane is specified in 3D space by the four corners
-  % $C_1$ to $C_4$. Images are related to the plane through the camera
-  % matrices $P_{1..M}$. For example, the 3D point X in the world
-  % coordinate system is related to the image point x shown in the
-  % figure as $x = P_i X$.}
-%  \label{fig:compare_wall}
-%\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
+  \includegraphics[width=3in]{wall1_dynprog_noblend.jpg}
+  \caption{The tile caching approach is presented above the seam
+    minimization approach.}
+  \label{fig:compare_unblended}
+\end{figure}
 
@@
 caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. This can be a
-problem when localization refinement does not work perfectly. Such an
-effect can be seen in the following image.
+choices once subsequent tiles have been processed.
 
@@
 provided with optimal images. Floors and ceilings however, given their
-suboptimal images which require segmentation, are textured using the
-tile caching method.
+suboptimal images, as shown in figure \ref{fig:floor_suboptimal}, can
+only be textured using the tile caching method.
 
@@
 linearly across overlapping regions. For each pixel within such a
-region, we simply scale its intensity (by a factor from 0 to 1),
-based on its distance from the image's border, with a cap set at a fixed distance from the border. In this way, we interpolate between two
-overlapping images, providing a gradual transition between
-them. Increasing the blending distance results in a
-smoother transition, but can also result in more blurriness. A blended and unblended version of each method is shown below for comparison.
+region, we simply scale its intensity (by a factor from 0 to 1), based
+on its distance from the image's border, with a cap set at a fixed
+distance from the border. In this way, we interpolate between two
+overlapping images, providing a gradual transition between them. Our
+texture mapping process is now complete, and in figure
+\ref{fig:pipeline}, we review our entire pipeline and demonstrate the
+final blended output of both approaches.
 
-%\begin{figure}
-%5  \centering
- % \includegraphics[height=2in]{compare_blending.png}
-%  \caption{Planes are specified in 3D space by four corners $C_1$ to
-%    $C_4$. Images are related to each plane through the camera
-%    matrices $P_{1..M}$. }
-%  % \caption{The plane is specified in 3D space by the four corners
-  % $C_1$ to $C_4$. Images are related to the plane through the camera
-  % matrices $P_{1..M}$. For example, the 3D point X in the world
-  % coordinate system is related to the image point x shown in the
-  % figure as $x = P_i X$.}
-%  \label{fig:compare_blending}
-%\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{pipeline.pdf}
+  \caption{Our final texture processing pipeline, with the final
+    output of both approaches.}
+  \label{fig:pipeline}
+\end{figure}
 
@@
 approach, and walls textured with the optimized approach, are
-displayed in the remainder of this paper. A more detailed walkthrough
-demonstrating fully textured models using the approaches in this paper
-can be seen in the accompanying video to this paper.
+displayed in figure \ref{fig:results}. A more detailed walkthrough
+demonstrating fully textured 3D models using the approaches in this
+paper is available in the accompanying video to this paper.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{4thfloor21.jpg}
+  \includegraphics[width=3in]{4thfloor61.jpg}
+  \includegraphics[width=2in]{4thfloor8.jpg}
+  \includegraphics[width=3in]{fullmodel.png}
+  \caption{Examples of our final texture mapping output for walls, floors, and ceilings}
+  \label{fig:results}
+\end{figure}
 

### 2012-06-20 3dimpvt/paper.tex
sending draft to prof

@@
 %%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for 3DIMPVT Proceedings}
+\title{Texture Mapping Indoor Environments with Imperfect Camera Localization}
 
@@
 
-The first step in automated 3d modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-calculate camera locations within an environment while simulatenously
-reconstructing the 3D structure of the environment itself. This
-problem is studied by the robotics and computer vision communities as
-the simultaneous localization and mapping (SLAM) problem, and is
-generally solved using a combination of laser range scanners, cameras,
-and inertial measurement units (IMUs).
-
 The aim of this paper is to present a solution for texture mapping the
@@
 \section{Backpack Modeling System}
-Human-operated data acquisition systems provide unique advantages over
-vehicular-mounted systems in terms of agility and
+The first step in automated 3D modeling is the physical scanning of
+the environment's geometry. An indoor modeling system must be able to
+calculate camera locations within an environment while simulatenously
+reconstructing the 3D structure of the environment itself. This is
+known as the simultaneous localization and mapping (SLAM) problem, and
+is generally solved by taking readings from laser range scanners,
+cameras, and inertial measurement units (IMUs) at multiple locations
+within the environment.
+
+Mounting such devices on a human-carried platform provides unique
+advantages over vehicular-based systems in terms of agility and
 portability. Unfortunately, human-operated systems also suffer from a
@@
 variance and localization error. As a result, common methods for
-texture mapping generally produce poor results, as shown in section
-3. Before discussing how to overcome these challenges, we will first
-provide an overview of the backpack modeling system from which our
-test data was obtained.
+texture mapping generally produce poor results, as later shown in
+section 3. Before discussing how to overcome these challenges, we will
+first provide an overview of the backpack modeling system from which
+our test data was obtained.
 
 \subsection{Data Acquisition Hardware}
-The backpack modeling system that captured our data contains five 2D
-laser range scanners, two cameras, an orientation sensor, and an
-IMU. The laser scanners are mounted orthogonally and have a 30-meter
-range and a 270$^{\circ}$ field of view. The two cameras are equipped
-with fisheye lenses, reaching an approximately 180$^{\circ}$ field of
-view, and are mounted with one facing left and one facing right. These
-cameras take images at the rate of 5 Hz. The orientation sensor
-provides orientation parameters at a rate of 180 Hz. The IMU provides
-highly accurate measurements of all 6 DOF at 200 Hz, and is used as a
-ground truth reference.
+The backpack-mounted modeling system that captured our data contains
+five 2D laser range scanners, two cameras, an orientation sensor, and
+an IMU. The laser scanners are mounted orthogonally and have a
+30-meter range and a 270$^{\circ}$ field of view. The two cameras are
+equipped with fisheye lenses, reaching an approximately 180$^{\circ}$
+field of view, and are mounted with one facing left and one facing
+right. These cameras take images at the rate of 5 Hz. The orientation
+sensor provides orientation parameters at a rate of 180 Hz. The IMU
+provides highly accurate measurements of all 6 DOF at 200 Hz, and is
+used as a ground truth reference for localization processes.
 
@@
     matrices $P_{1..M}$. }
-  % \caption{The plane is specified in 3D space by the four corners
-  % $C_1$ to $C_4$. Images are related to the plane through the camera
-  % matrices $P_{1..M}$. For example, the 3D point X in the world
-  % coordinate system is related to the image point x shown in the
-  % figure as $x = P_i X$.}
   \label{fig:projection}
@@
 mapping a single plane, as the texturing of each of our planes is
-completely independent and can be completed in parallel.
+independent and can be completed in parallel.
 
 The geometry of the texture mapping process for a plane is shown in
-Figure 1.  As described in the previous section, we are provided with
-a set of $M$ images with which we must texture our target plane. Each
-image has a camera matrix $P_i$ for $i=1..M$, which translates a 3D
-point in the world coordinate system to a 2D point or pixel in image
-$i$'s coordinates. If the 3D world point is not contained in the
-image, the 2D point will simply be outside of the image boundaries. A
-camera matrix $P_i$ is composed of the camera's intrinsic parameters,
-such as focal length and image center, as well as extrinsic parameters
-which specify the rotation and translation of the camera's position in
-3D world coordinates at the time that image $i$ was taken. These
-extrinsic parameters are determined by the backpack hardware and
-localization algorithms mentioned in Section 2. A point $X$ on the
-plane in 3D space can be related to its corresponding pixel $x$ in
-image $i$ through the following equation:
+figure \ref{fig:projection}.  As described in the previous section, we
+are provided with a set of $M$ images with which we must texture our
+target plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
+translates a 3D point in the world coordinate system to a 2D point or
+pixel in image $i$'s coordinates. If the 3D world point is not
+contained in the image, the 2D point will simply be outside of the
+image boundaries. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, such as focal length and image center, as well
+as extrinsic parameters which specify the rotation and translation of
+the camera's position in 3D world coordinates at the time that image
+$i$ was taken. These extrinsic parameters are determined by the
+backpack hardware and localization algorithms mentioned in Section
+2. A point $X$ on the plane in 3D space can be related to its
+corresponding pixel $x$ in image $i$ through the following equation:
 
@@
 generally about 5 pixels across, and picking an image to texture each
-tile with. We choose to work with rectangular units to ensure that
-borders between any two distinct images in our final texture will be
-either horizontal or vertical. Since most environmental features
-inside buildings are horizontal or vertical, any seams in our texture
-will intersect them miniimally and be less noticeable.
+tile with. Since we are provided with far more images than necessary
+to cover our plane, this process is a simple way of assigning
+texturess to locations on our plane. We choose to work with
+rectangular units to ensure that borders between any two distinct
+images in our final texture will be either horizontal or
+vertical. Since most environmental features inside buildings are
+horizontal or vertical, any seams in our texture will intersect them
+miniimally and be less noticeable.
 
@@
 gather a list of candidate images that contain all four of its
-corners, which we can quickly check using the projection method
-above. Furthermore, each candidate image must have been taken at a
-time when its camera had a clear line-of-sight to the center of $t$,
-which can be calculated using standard ray-polygon intersection tests
-between the camera location, our section, and other planes, all in
-world coordinates.
+corners, which we can quickly check by projecting $t$ into each image
+and using the projection method above. Furthermore, each candidate
+image must have been taken at a time when its camera had a clear
+line-of-sight to $t$, which can be calculated using
+standard ray-polygon intersection tests between the camera location,
+the center of $t$, and other planes, all in world coordinates.
 
@@
 Similar to a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a good candidate
+$t$ by searching through two subsets of images for a good candidate,
 before searching through the entire set. The first subset of images is
@@
 
-The results of this caching approach are shown above in figure
+The results of this caching approach are shown in figure
 \ref{fig:caching}.  Discontinuities have been reduced overall, but the
@@
 produce seamless textures. The image projections themselves will have
-to be adjusted in order to reliably produce clean textures.
+to be adjusted in order to reliably generate clean textures.
 
@@
 same scoring function in figure \ref{fig:scoringFunction}, we know
-that our images are all taken at a head-on angle and should project
-onto the plane in similar ways. Third, as a side result of the scoring
-function, selected images are only good candidates for the tiles near
-their center of projection. Thus, there should be plenty of overlap
-between selected images, allowing for some degree of shifting as well
-as blending between them. With this set of images, we now examine two
+that our images are all taken at as much of a head-on angle as
+possible and should project onto the plane in similar ways. Third, as
+a side result of the scoring function, selected images are only good
+candidates for the tiles near their center of projection. Thus, there
+should be plenty of overlap between selected images, allowing for some
+degree of shifting without resulting in holes, as well as area for
+blending between them. With this set of images, we now examine two
 approaches towards refining and combining their projections, before
@@
 amount of quality texture for each image is limited. Additionally,
-since our plane is discretized, we can easily handle arbitrarily
-complex planes as well.
+since our plane is discretized, we can handle arbitrarily
+complex plane geometry as well.
 
@@
 for walls, images are all taken from close distances and have
-near-rectangular projections and thus a great score according to the
+near-rectangular projections and thus more similar scores according to the
 scoring function in figure \ref{fig:scoringFunction}. Thus, we can
@@
 will accomplish this by using entire images where possible, defining a
-cost function between images, and seeking to minimize our total cost.
+cost function between images, and seeking to minimize total cost.
 
@@
 areas, our image projections will remain largely rectangular. We can
-thus recursively split each image into rectangular pieces, and perform
-occlusion checks, similar to the process done for tiles earlier. To
-actually occlude out rectangles, we simply remove their texture, as we
-will ensure that untextured areas are never chosen for texture
-mapping.
+thus make efficiency improvements by recursively splitting each image
+into rectangular pieces, and performing occlusion checks where
+needed. To actually occlude out rectangles, we simply remove their
+texture, as we will ensure that untextured areas are never chosen for
+texture mapping.
 
@@
 occur in featureless areas, such as bare walls, as well as in areas
-where images match extremely accurately.
+where images match extremely well.
 
@@
 cost function was used, as the regular occurrence of featureless areas
-was not guaranteed in our datasets, and our image matches do in fact
-match at the pixel level in many cases.
+was not guaranteed in our datasets.
 
@@
 we can take a number of steps to simplify it. Returning again to the
-optimality of our situation when texturing walls however, we can make
-a quick simplification for the sake of efficiency. Given that our
-wall-texture candidate images were all taken from a head-on angle, and
-assuming only minor rotations were made during localization
-refinement, we can reason that their projections onto the plane are
-approximately rectangular. By discarding the minor excess texture and
-cropping them all to be rectangular, our problem becomes the
-conceptually simpler problem of filling a polygon with rectangles,
-such that the sum of all edge costs between each pair of rectangles is
-minimal. We thus also retain axis-aligned image boundaries, along with
-their advantages explained in section 3.
+optimality of our situation when texturing walls, we can make a quick
+simplification for the sake of efficiency. Given that our wall-texture
+candidate images were all taken from a head-on angle, and assuming
+only minor rotations were made during localization refinement, we can
+reason that their projections onto the plane are approximately
+rectangular. By discarding the minor excess texture and cropping them
+all to be rectangular, our problem becomes the conceptually simpler
+problem of filling a polygon with rectangles, such that the sum of all
+edge costs between each pair of rectangles is minimal. We thus also
+retain axis-aligned image boundaries, along with their advantages
+explained in section 3.
 
-By taking one more shortcut we can simplify our problem down even
+By taking two more shortcut we can simplify our problem down even
 further. Since this approach is already assuming optimal images, we
-know it will be applied only on walls, which are the focus of the
-backpack modeling system. For wall planes, care is taken so that
-images contain the entirety of their floor-to-ceiling range, and thus
-we do not have wall images such that one should be projected
-vertically above the other. In essence, we need only to ensure
-horizontal coverage of our planes, as our images provide full vertical
-coverage themselves. We can thus construct a Directed Acyclic Graph
-(DAG) from the images, again with edge costs defined by our cost
-function above, and solve a simple shortest path problem to find an
-optimal subset of images with regard to the cost functions.
+know it will be applied on walls, which are the focus of the backpack
+modeling system. For wall planes, which are nearly always rectangular,
+care is taken so that images contain the entirety of their
+floor-to-ceiling range, and thus we do not have wall images such that
+one should be projected vertically above the other. In essence, we
+need only to ensure horizontal coverage of our planes, as our images
+provide full vertical coverage themselves. We can thus construct a
+Directed Acyclic Graph (DAG) from the images, with edge costs defined
+by our cost function above, and solve a simple shortest path problem
+to find an optimal subset of images with regard to the cost functions.
 
@@
 image was chosen to texture. Rather than reverting to a 2D-coverage
-problem, we can elect to simply fill the hole by selecting images in a
-greedy fashion with respect to the same cost function.
+problem, we can elect to simply fill the hole by selecting images to
+fill it in a greedy fashion with respect to edge costs of the same
+cost function.
 
@@
 same blending procedure, as long as we have a guaranteed overlap
-between units.
+between units to blend over.
 
@@
 In this paper, we have shown how to accurately texture map models,
-even when provided with imprecise camera localization data. We have
-generalized one approach to any manner of planes and images, and
-successfully textured both simple rectangular walls as well as complex
-floor and ceiling geometry. We have also presented an optimized
-texturing method that takes advantage of our localization refinement
-process and produces cleaner textures on planes where multiple head-on
-images are available. Ceilings and floors textured with the robust
-approach, and walls textured with the optimized approach, are
-displayed in figure \ref{fig:results}. A more detailed walkthrough
-demonstrating fully textured 3D models using the approaches in this
-paper is available in the accompanying video to this paper.
+even when provided with imprecise camera localization data. We were
+able to refine image locations based on feature mapping, and robustly
+handle outliers.  We generalized one approach to texture mapping to
+any manner of planes and images, and successfully textured both simple
+rectangular walls as well as complex floor and ceiling geometry. We
+also presented an optimized texturing method that takes advantage of
+our localization refinement process and produces cleaner textures on
+planes where multiple head-on images are available. Each of these
+approaches is highly modular, and easily tunable for different
+environments and acquisition hardware.
+
+Ceilings and floors textured
+with the robust approach, and walls textured with the optimized
+approach, are displayed in figure \ref{fig:results}. A more detailed
+walkthrough demonstrating fully textured 3D models using the
+approaches in this paper is available in the accompanying video to
+this paper.
 
@@
   \includegraphics[width=3in]{fullmodel.png}
-  \caption{Examples of our final texture mapping output for walls, floors, and ceilings}
+  \caption{Examples of our final texture mapping output for walls,
+    floors, and ceilings}
   \label{fig:results}

### 2012-06-22 3dimpvt/_region_.tex
draft 2.5

@@
 
-\message{ !name(paper.tex) !offset(204) }
+\message{ !name(paper.tex) !offset(-3) }
+
+%%%%%%%%% TITLE
+\title{Texture Mapping 3D Models of Indoor Environments with Noisy
+  Camera Poses}
+
+\author{First Author\\
+  Institution1\\
+  Institution1 address\\
+  {\tt\small firstauthor@i1.org}
+  % For a paper whose authors are all at the same institution, omit
+  % the following lines up until the closing ``}''.  Additional
+  % authors and addresses can be added with ``\and'', just like the
+  % second author.  To save space, use either the email address or
+  % home page, not both
+  \and
+  Second Author\\
+  Institution2\\
+  First line of institution2 address\\
+  {\small\url{http://www.author.org/~second}} }
+
+\maketitle
+% \thispagestyle{empty}
+
+%%%%%%%%% ABSTRACT
+\begin{abstract}
+  Automated 3D modeling of building interiors is useful in
+  applications such as virtual reality and environment
+  mapping. Applying textures to these models is an important step in
+  generating photorealistic visualizations of data gathered by
+  modeling systems.  The localization of cameras in such systems often
+  suffer from inaccuracies, resulting in visible discontinuties when
+  different images are projected adjacently onto a plane for
+  texturing. We propose two approaches for reducing discontinuities
+  during texture mapping, one to robustly accomodate images of all
+  orientations, and one to take advantage of optimal situations where
+  images have uniform orientation. The effectiveness of our approaches
+  will be demonstrated on two indoor datasets.
+\end{abstract}
+
+%%%%%%%%% BODY TEXT
+\section{Introduction}
+\label{sec:introduction}
+Three-dimensional modeling of indoor environments has a variety of
+applications such as training and simulation for disaster management,
+virtual heritage conservation, and mapping of hazardous sites. Manual
+construction of these digital models can be time consuming, and as
+such, automated 3D site modeling has garnered much interest in recent
+years.
+
+The aim of this paper is to present a solution for texture mapping the
+3D models generated by indoor modeling systems, with specific
+attention given to a human-operated system with high camera pose
+errors and great variance in camera locations.
+
+The first step in automated 3D modeling is the physical scanning of
+the environment's geometry. An indoor modeling system must be able to
+recover camera poses within an environment while simulatenously
+reconstructing the 3D structure of the environment itself. This is
+known as the simultaneous localization and mapping (SLAM) problem, and
+is generally solved by taking readings from laser range scanners,
+cameras, and inertial measurement units (IMUs) at multiple locations
+within the environment.
+
+Mounting such devices on a human-carried platform provides unique
+advantages over vehicular-based systems in terms of agility and
+portability. Unfortunately, human-operated systems also result in much
+larger localization error. As a result, common methods for texture
+mapping generally produce poor results, as later shown in Sections
+\ref{sec:simpleTextureMapping} and
+\ref{sec:existingApproaches}. Before discussing how to overcome these
+challenges, we first provide an overview of the backpack modeling
+system from which our test data has been obtained.
+
+Our backpack-mounted modeling system contains five 2D laser range
+scanners, two cameras, and an orientation sensor. The laser scanners
+are mounted orthogonally and have a 30-meter range and a 270$^{\circ}$
+field of view. The two cameras are equipped with fisheye lenses,
+reaching an approximately 180$^{\circ}$ field of view, and are mounted
+with one facing left and the other facing right. These cameras take
+images at the rate of 5 Hz. The orientation sensor provides
+orientation parameters at a rate of 180 Hz.
+
+With the laser scanners active, the human operator wearing the
+backpack takes great care to walk a path such that every wall in the
+desired indoor environment is traversed and scanned lengthwise at
+least once.
+
+Using data gathered by the onboard sensors and multiple localization
+and loop-closure algorithms, the backpack is first localized over its
+data collection period, and a 3D point cloud of the surrounding
+environment is constructed based on the laser scanner readings
+relative to the backpack \cite{chen2010indoor, kua2012loopclosure, liu2010indoor}. Approximate normal vectors for each point in
+the point cloud are then calculated by gathering neighboring points
+within a small radius and processing them through principal component
+analysis. These normal vectors allow for the classification and
+grouping of adjacent points into structures such as walls, ceilings,
+floors, and staircases. A RANSAC algorithm is then employed to fit
+polygonal planes to these structured groupings of points, resulting in
+a fully planar model \cite{sanchez2012point}. This model, consisting
+of multiple 2D polygonal planes in 3D space, along with the set of
+images captured by the backpack's camera, can be considered the input
+to our texture mapping problem.
+
+The remainder of the paper is organized as follows. Section
+\ref{sec:simpleTextureMapping} describes the general problem of
+texture mapping and examines two simple mapping approaches and their
+shortcomings.  Section \ref{sec:existingApproaches} demonstrates two
+previous attempts at localization refinement, and demonstrates their
+inadequacies for our datasets.  Section \ref{sec:proposedApproach}
+presents our proposed approach to texture mapping, combining an
+improved localization refinement process with two image selection
+approaches. Section \ref{sec:resultsAndConclusions} contains results
+and conclusions.
+
+\section{Simple Texture Mapping}
+\label{sec:simpleTextureMapping}
+\begin{figure}
+  \centering
+  \includegraphics[height=2in]{Projection.pdf}
+  \caption{Planes are specified in 3D space by four corners $C_1$ to
+    $C_4$. Images are related to each plane through the camera
+    matrices $P_{1..M}$. }
+  \label{fig:projection}
+\end{figure}
+
+In all subsequent sections, we discuss the process of texture
+mapping a single plane, as the texturing of each of our planes is
+independent and can be completed in parallel.
+
+The geometry of the texture mapping process for a plane is shown in
+Figure \ref{fig:projection}.  As described earlier, we
+are provided with a set of $M$ images with which we must texture our
+target plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
+translates a 3D point in the world coordinate system to a 2D point or
+pixel in image $i$'s coordinates. If the 3D world point is not
+contained in the image, the 2D point will simply be outside of the
+image boundaries. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, such as focal length and image center, as well
+as extrinsic parameters which specify the rotation and translation of
+the camera's position in 3D world coordinates at the time that image
+$i$ is taken. These extrinsic parameters are determined by the
+backpack hardware and localization algorithms mentioned earlier. A point $X$ on the plane in 3D space
+can be related to its corresponding pixel $x$ in image $i$ through the
+following equation:
+
+\[
+x=project(P_iX)
+\]
+
+where
+\[X = \begin{pmatrix} x \\ y \\ z \end{pmatrix} \textrm{ and }
+project(X) = \begin{pmatrix} x/z \\ y/z \end{pmatrix}
+\]
+
+For the sake of simplicity, we treat all planes as rectangles by
+generating minimum bounding boxes for them. Since our final textures
+are stored as standard rectangular images anyway, we can simply
+leave the area between plane boundary and bounding box untextured, or
+crop it out as needed. A plane to be textured is thus defined by a
+bounding box with corners $C_i$ in world coordinates and a normal
+vector indicating the front facing side of the plane. Our goal is to
+texture this plane using images captured by the backpack, while
+eliminating any visual discontinuities or seams that would suggest
+that the plane's texture is not composed of a single continuous
+image.
+
+\subsection{Direct Mapping}
+\label{sec:directMapping}
+
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+we can texture the plane by discretizing it into small square tiles,
+generally about 5 pixels across, and choosing an image to texture each
+tile with. We choose to work with rectangular units to ensure that
+borders between any two distinct images in our final texture are
+either horizontal or vertical. Since most environmental features
+inside buildings are horizontal or vertical, any seams in our texture
+intersect them miniimally and are likely to be less noticeable.
+
+In order to select an image for texturing tile $t$, we must first
+gather a list of candidate images that contain all four of its
+corners, which we can quickly check by projecting $t$ into each image
+using the projection method above. Furthermore, each candidate image
+must have been taken at a time when its camera had a clear
+line-of-sight to $t$, which can be calculated using standard
+ray-polygon intersection tests between the camera location, the center
+of $t$, and other planes, all in world coordinates.
+
+Once we have a list of candidate images for $t$, we must define a
+scoring function in order to compare images and objectively select the
+best one. Since camera localization errors compound over distance, we
+wish to minimize the distance between cameras used for texturing and
+our plane. Additionally, we desire images that are projected
+perpendicularly onto the plane, maximizing the resolution and amount
+of useful texture available in their projections.
+
+These two criteria can be met by maximizing the function
+
+\[
+\frac{1}{d} \cdot (-1 \cdot C) \cdot N
+\]
+
+which minimizes camera angle $\alpha$ and distance $d$ as shown in Figure \ref{fig:scoringFunction}.
+
 \begin{figure}
@@
   \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{For each tile, we want to select an image such that $d$ and $\alpha$ are minimized}
+  \caption{Images are selected by minimizing camera angle $\alpha$ and distance $d$.}
   \label{fig:scoringFunction}
@@
 
-%\begin{figure}
-%  \centering
-%  \includegraphics[height=1.5in]{directMapping.png}
-%  \caption{The result of direct texture mapping based on locally
-%    optimized textures.}
-%  \label{fig:directMapping}
-%\end{figure}
-\message{ !name(paper.tex) !offset(699) }
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{wall1_naive.jpg}
+  \caption{The result of direct texture mapping based on locally
+    optimized textures.}
+  \label{fig:directMapping}
+\end{figure}
+
+As Figure \ref{fig:directMapping} demonstrates, this approach leads to
+the best texture for each tile independently, but overall results in
+many image boundaries with abrupt discontinuities, due to significant
+misalignment between images.
+
+\subsection{Mapping with Caching}
+\label{sec:mappingWithCaching}
+Since discontinuities occur where adjacent tiles select different
+images that do not align, it makes sense to take into account image
+selections made by neighboring tiles while selecting the best image
+for a given tile. By using the same image across tile boundaries, we
+eliminate the discontinuity altogether. If a tile is not visible in
+images chosen by its neighbors, using similar images is likely to
+result in less noticeable discontinuities.
+
+Similar to a caching mechanism, we select the best image for a tile
+$t$ by searching through two subsets of images for a good candidate,
+before searching through the entire set. The first subset of images is
+those selected by adjacent tiles that have already been textured. We
+must first check which images can map to $t$, and then of those, we
+make a choice according to the same scoring function in Figure
+\ref{fig:scoringFunction}. Rather than blindly reusing this image, we
+ensure it meets a threshold, which we set to $\alpha < 45^\circ$, to
+be considered a good image.
+
+If no good image is found, we then check our second subset of images,
+which consists of images that were taken near the images in the first
+subset, both spatially and temporally. These images are not the same
+as the ones used for neighboring tiles, but they were taken at a
+similar location and time, suggesting that their localization and
+projection are very similar. Again, if no good image is found
+according to the same threshold, we then must search the entire set of
+candidate images.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{wall1_cache_full.jpg}
+  \caption{The result of adding a caching system to locally optimized
+    textures.}
+  \label{fig:caching}
+\end{figure}
+
+The result of this caching approach is shown in figure
+\ref{fig:caching}. As compared to \ref{fig:directMapping},
+discontinuities have been reduced overall, but the amount of remaining
+seams suggests that image selection alone cannot produce seamless
+textures. Camera matrices, or the image projections themselves have to
+be adjusted in order to reliably generate clean textures.
+
+\section{Existing Approaches to Image-Aligned Texture Mapping}
+\label{sec:existingApproaches}
+In order to produce seamless texture mapping, either camera matrices
+need to be refined such that their localization is pixel accurate,
+resulting in a perfect mapping, or image stitching techniques need to
+be applied to provide this illusion. Before examining these
+approaches, we first obtain a set of images to work with.
+
+Rather than perform camera or image adjustments across the many
+thousands of images acquired in a typical data collection, we opt to
+work with the more limited set of images corresponding to those chosen
+by the direct mapping approach, without caching. This set of images
+constitutes a good candidate set for generating a final seamless
+texture since it meets three important criteria. First, it contains at least one image that covers each tile on our
+plane; this ensures no holes in our final texture. Second, since
+images are all selected according to the same scoring function in
+Figure \ref{fig:scoringFunction}, they are taken at as much of a head-on angle as possible and should project
+onto the plane in similar ways. Third, as a side result of the scoring
+function, selected images are only good candidates for the tiles near
+their center of projection. Thus, there should be plenty of overlap
+between selected images, allowing for some degree of shifting without
+resulting in holes, as well as area for blending between them. With
+this set of images, we now review two existing approaches towards refining and
+combining their projections.
+
+\subsection{Image Mosaicing}
+\label{sec:imageMosaicing}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{panoMy.jpg}
+  \caption{Image mosaicing. }
+  \label{fig:mosaic}
+\end{figure}
+
+When images of a plane are taken from arbitrary overlapping positions,
+they are related by homography \cite{hz}. Thus, existing
+homography-based image mosaicing algorithms are applicable
+\cite{brown2007automatic}. However, errors can compound when long
+chains of images are mosaiced together using these approaches. For
+example, a pixel in the $n$th image in the chain must be translated
+into the first image's coordinates by multiplying by the $3\times3$
+matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these homography
+matrices is propagated to all further images until the chain is
+broken. For some chains of images this can happen almost immediately
+due to erroneous correspondence matches and the resulting image mosaic
+is grossly misshapen.
+
+Figure \ref{fig:mosaic} shows the output of the AutoStitch software
+package which does homography-based image mosaicing. This plane is
+nearly a best-case scenerio with many features spread uniformly across
+it. Even so, the mosaicing produces errors that causes straight lines
+to appear as waves on the plane. This image was generated after
+careful hand tuning as well. Many planes that had fewer features
+simply failed outright. Thus, image mosaicing is not a robust enough
+solution for reliably texture mapping our dataset.
+
+\subsection{Image-Based 3D Localization Refinement}
+\label{sec:imageBased3DRefinement}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{Graph_crop.pdf}
+  \caption{The graph-based localization refinement algorithm from [11]
+    suffers from the problem of compounding errors. }
+  \label{fig:graph}
+\end{figure}
+
+Another approach is to refine the camera matrices using image
+correspondences to guide the process. Each image's camera matrix has 6
+degrees of freedom that can be adjusted. Previous work on this problem
+attempted to refine camera matrices by solving a non-linear
+optimization problem \cite{liu2010indoor}. This process is specific to
+the backpack system which generated our dataset, as it must be run
+during backpack
+localization\cite{liu2010indoor,chen2010indoor}. Unfortunately, this
+approach suffers from a similar error propagation problem shown in
+Figure \ref{fig:graph}.
+
+\section{Proposed Method for Seamless Texture Mapping}
+\label{sec:proposedApproach}
+Our proposed approach towards texture mapping is a two-step
+process. First, with the same input set of images as described in
+Section \ref{sec:existingApproaches}, we perform image rotation and
+shifting in order to maximize SIFT feature matches between images. We
+then project these images onto our plane, applying textures either
+with the tile caching method from Section
+\ref{sec:mappingWithCaching}, or with the more specialized method
+described in Section \ref{sec:seamMinimization}.
+
+\subsection{Image Projection and Rotation}
+\label{sec:projectionAndRotation}
+Our localization approach begins with the projection of all our images
+onto separate copies of our plane, such that no projected data is
+covered up and lost. This is done in the same way as the approaches in
+Section \ref{sec:simpleTextureMapping}. We then perform rotations on
+these projections, as adjacent images with different orientations will
+result in strong discontinuities.
+
+These rotations are accomplished by using Hough transforms, which
+detect the presence and orientation of linear features in our
+images. Rather than match the orientation of such features in each
+image, we simply apply rotations such that the strongest near-vertical
+features are made completely vertical. This is effective for indoor
+models, since strong features in indoor scenes usually consist of
+parallel vertical lines corresponding to doors, wall panels,
+rectangular frames, etc. If features in the environment are not
+vertical, or are not parallel to eachother, this step is skipped.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{matches.jpg}
+  \caption{SIFT feature matches between overlapping images.}
+  \label{fig:matches}
+\end{figure}
+
+\subsection{Robust SIFT Feature Matching using RANSAC}
+\label{sec:robustSIFTFeatureMatching}
+Our next step is to fix misalignment between overlapping images. We do
+this by first searching for corresponding points between all pairs of
+overlapping images using SIFT feature matching
+\cite{lowe1999object}. An illustration of this is given in Figure
+\ref{fig:matches}. The SIFT matches allow us to determine $dx$ and
+$dy$ distances between each pair of features for two images on the
+plane, determining where they should be projected relative to
+eachother.
+
+Since indoor environments often contain repetitive features such as
+floor tiles or doors, we need to ensure that our SIFT-based distances
+are reliable. In order to mitigate the effect of incorrect matches and
+outliers, the RANSAC framework \cite{fischler1981random} is used for a
+robust estimate of the optimal $dx$ and $dy$ distances between two
+images. The RANSAC framework handles the consensus-building machinery,
+and requires a fitting function and a distance function. For this
+application, the fitting function simply finds the average distance
+between matches in a pair of images. Our distance function for a pair
+of points is the difference between those points' SIFT match distance
+and the average distance computed by the fitting function; we use a 10
+pixel outlier threshold. This means that a SIFT match is labeled as an
+outlier if its horizontal or vertical distance is not within 10 pixels
+of the average distance computed by the fitting function.
+
+\subsubsection{Refining Image Positions using Least Squares}
+\label{sec:refiningImagePositions}
+There are a total of $M^{2}$ possible pairs of images, though we only
+generate distances between images that overlap at SIFT feature
+points. Given these distances and the original image location
+estimates, we can solve a least squares problem ($\textrm{min}_{\vec{\beta}}
+||X \vec{\beta} - \vec{\gamma}||_2^2 $) to estimate the correct location of the images
+on the plane. The $M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
+and $y$ locations of each image on the plane from $1 \dots M$. The
+optimal $x$ and $y$ locations are obtained in the same way, so we
+only consider the $x$ locations here:
+
+% Draw least squares problem here.
+
+\[\vec{\beta} =
+\begin{pmatrix}
+  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
+\end{pmatrix}
+\]
+
+The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row for each pair of images
+with measured distances produced by the SIFT matching stage. A row in
+the matrix has a $-1$ and $1$ in the columns corresponding to the two
+images in the pair. For example, the matrix below indicates that we
+generated a SIFT-based distance between images 1 and 2, images 1 and
+3, images 2 and 3, etc.
+
+\[
+X =
+\begin{pmatrix}
+  -1 & 1 & 0 & \cdots & 0 & 0\\
+  -1 & 0 & 1 & \cdots & 0 & 0\\
+  0 & -1 & 1 & \cdots & 0 & 0\\
+  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
+  0 & 0 & 0 & \cdots & 1 & 0 \\
+  0 & 0 & 0 & \cdots & -1 & 1 \\
+  1 & 0 & 0 & \cdots & 0 & 0 \\
+\end{pmatrix}
+\]
+
+If only relative distances between images are included then there is
+no way to determine the absolute location of any of the images and the
+matrix becomes rank deficient. To fix this we choose the first image
+to serve as the anchor for the rest, meaning all the absolute
+distances are based on its original location. This is done by adding a
+row with a $1$ in the first column and the rest zeros.
+
+Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is constructed using the
+SIFT-based distances generated earlier in the matching stage. The
+distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based
+distances. The last element in the observation vector is the location
+of the first image determined by its original noisy localization, from \cite{chen2010indoor, liu2010indoor}:
+
+\[
+\vec{y}^T =
+\begin{pmatrix}
+  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
+\end{pmatrix}
+\]
+
+The $\vec{\beta}$ that minimizes $||X \vec{\beta} - \vec{\gamma}||_2^2$ results in a set of
+image locations on the plane that best honors all the SIFT-based
+distance measurements between images. In practice there are often
+cases where there is a break in the chain of images, meaning that no
+SIFT matches were found between one segment of the plane and
+another. In this case we add rows to the $X$ matrix and observations
+to the $\vec{\gamma}$ vector that contain the original noisy $x$ and $y$ distance
+estimates generated by the localization algorithm \cite{chen2010indoor, liu2010indoor}. Another way to do
+this is to add rows for all neighboring pairs of images and solve a
+weighted least squares problem where the SIFT distances are given a
+higher weight i.e. 1, and the noisy distances generated by the localization
+algorithm \cite{chen2010indoor, liu2010indoor} are given a smaller weight i.e. 0.01.
+
+After completing this same process for the $y$ dimension as well, and
+making the resultant shifts, our images overlap and
+match each other with far greater accuracy.
+Applying the tile caching method from Section \ref{sec:mappingWithCaching} on these re-localized images, results in the significant improvements shown in Figure \ref{fig:shifted}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
+  \caption{Localization refinement results in signifcantly fewer
+    discontinuities in the final texture.}
+  \label{fig:shifted}
+\end{figure}
+
+\subsection{Texture Mapping with Seam Minimization}
+\label{sec:seamMinimization}
+
+As mentioned earlier, our backpack system has 2 cameras with
+$180^\circ$ fisheye lenses facing to the right and left. Since the
+backpack operator only takes care to fully scan each wall and not
+necessarily the entirety of each ceiling and floor, cameras at higher
+angles with respect to plane normal vectors must be used for texturing
+large areas of floor and ceiling planes. These high camera angles
+translate into images that span extremely large areas once projected
+onto their planes. Such image projections have good scores (from
+Figure \ref{fig:scoringFunction}) for certain areas on the plane, but
+much worse scores for other areas. This can be seen in Figure
+\ref{fig:highCameraAngle}. The tiling approach used in Section
+\ref{sec:simpleTextureMapping} was thus a good choice for texturing,
+as it allowed us to only use the parts of image projections that were
+good choices for their respective plane locations.
+
+For wall planes however, we have images all taken from close distances
+and more head-on angles, and thus much smaller near-rectangular
+projections to work with. As a result, there is less deviation over
+the score of each tile within an image, as well as over the average
+scores of all images. This means that the scoring criteria from Figure
+\ref{fig:scoringFunction} is less relevant to walls, which enjoy an
+abundance of head-on images.
+
+Thus, for planes with optimal images, rather than selecting the set of
+best images, since all images are near in quality, we instead select
+the best set of images, such that the selection together results in
+the cleanest final texture. We will accomplish this by using entire
+images where possible, and defining a cost function to minimize the
+visibility of seams in our final texture.
+
+\subsection{Occlusion Masking}
+\label{sec:occlusionMasking}
+To begin with, we need to ensure that our images contain only content
+that should be mapped onto the target plane in question. The tiling
+approach used previously only checks occlusion for each tile as it is
+being textured. For our new approach, we use entire images, so we need
+to perform occlusion checks over the entirety of each image to
+determine available areas for texture mapping.
+
+Fortunately, by virtue of our indoor environments, the vast majority
+of surface geometry is either horizontal or vertical, with high
+amounts of right angles. This means that after masking out occluded
+areas, our image projections will remain largely rectangular. We can
+thus be efficient by recursively splitting each image into rectangular
+pieces, and performing the same occlusion checks used in the tiling
+process where needed. To actually occlude out rectangles, we simply
+remove their texture, as we will ensure that untextured areas are
+never chosen for texture mapping.
+
+\subsection{Image Selection}
+\label{sec:imageSelection}
+To determine the set of images that results in the cleanest texture,
+we need a cost function to evaluate the visibiilty of seams between
+images in our set. A straightforward cost function that accomplishes
+this is the sum of squared pixel differences in overlapping regions
+between all pairs of images after they have been aligned as described
+in Section \ref{sec:projectionAndRotation}. Minimizing this cost
+function encourages image boundaries to occur either in featureless
+areas, such as bare walls, or in areas where images match extremely
+well.
+
+With the cost function defined, we must now select the set of images
+for which the overall cost function is minimized. Since nearly all the
+images for our optimal case are head on, the best strategy to minimize
+seams is to choose as few images as possible while texturing a given
+plane. Thus,to cover the entirety of a plane, our problem can be
+defined as minimally covering a polygon i.e. the plane, using other
+polygons of arbitrary geometry i.e. our image projections, with the
+added constraint of minimizing our cost function between chosen
+images.  This is a complex problem, though we can take a number of
+steps to simplify it. Given that our wall-texture candidate images are
+all taken from a head-on angle, and assuming only minor rotations are
+made during localization refinement, we can reason that their
+projections onto the plane are approximately rectangular, as in Figure
+\ref{sec:goodCameraAngle}. By discarding the minor excess texture and
+cropping them all to be rectangular, our problem becomes the
+conceptually simpler one of filling a polygon with rectangles, such
+that the sum of all edge costs between each pair of rectangles is
+minimal. We thus also retain the advantages of working with
+rectangular units, as explained in section
+\ref{sec:simpleTextureMapping}.
+
+The location and orientation of the cameras on our backpack is such
+that our images nearly always contain the entirety of the floor to
+ceiling range of wall planes. Images are therefore rarely projected
+with one above the other when texturing wall planes, which correspond
+to the optimal planes we are working with.  In essence, we need only
+to ensure horizontal coverage of our planes, as our images provide
+full vertical coverage themselves. We can thus construct a Directed
+Acyclic Graph (DAG) from the images, with edge costs defined by our
+cost function above, and solve a simple shortest path problem to find
+an optimal subset of images with regard to the cost functions.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{dagCreation.pdf}
+  \caption{DAG construction for the image selection process.}
+  \label{fig:dagCreation}
+\end{figure}
+
+Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
+from overlapping images of a long hallway. Images are sorted by
+horizontal location left to right, and become nodes in a
+graph. Directed edges are placed in the graph from left to right
+between images that overlap. The weights of these edges are determined
+by the cost functions discussed previously. Next, we add two
+artificial nodes, one start node representing the left border of the
+plane, and one end node representing the right border of the
+plane. The left(right) artificial node has directed edges with equal
+cost $C_0$ to(from) all images that meet the left(right) border of the
+plane.
+
+We now solve the standard shortest path problem from the start node to
+the end node \cite{shortestPath}. This provides a set of images
+completely covering the plane horizontally, while minimizing the cost
+of the seams between images.
+
+In rare cases where the vertical dimension of the plane is not
+entirely covered by a chosen image, we are left with a hole where no
+image is chosen to texture.
+
+SOMETHING HERE ABOUT CRAP CRAP
+
+Rather than reverting to a 2D-coverage problem, we can elect to simply
+fill the hole by selecting images to fill it in a greedy fashion with
+respect to edge costs of the same cost function.
+
+With this completed, we have now mapped every location on our plane to
+at least one image, and have minimized the number of images, as well
+as the discontinuity between their borders. In the next section, we
+apply blending between images where they overlap, but for the sake of
+comparison with the unblended tile caching method in Section
+\ref{sec:mappingWithCaching}, we arbitrarily choose one image for
+texturing where images overlap. Figure \ref{fig:compare_unblended}
+compares the tile caching method against this seam minimization
+method.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
+  \includegraphics[width=3in]{wall1_dynprog_noblend.jpg}
+  \caption{The tile caching approach is presented above the seam
+    minimization approach.}
+  \label{fig:compare_unblended}
+\end{figure}
+
+Though both methods provide quite accurate texturing thanks to the
+alignment process, the seam minimization approach results in fewer
+visible discontinuities, since it directly reduces the cost of each
+image boundary, while the tile caching method uses a scoring function
+that only approximates this effect. Furthermore, seam minimization
+guarantees the best selection of images, while the sequential tile
+caching method may select images early on that turn out to be poor
+choices once subsequent tiles have been processed.
+
+In the context of the backpack modeling system, we apply the seam
+minimization approach on walls, due to its superior output when
+provided with head-on images. Floors and ceilings however, given their
+images taken at oblique angles, as shown in Figure \ref{fig:floor_suboptimal}, are textured using the tile caching method.
+
+\subsection{Blending}
+\label{sec:blending}
+We now apply the same blending process on our two texturing methods:
+localization refinement followed by either tile caching or seam
+minimization.
+
+Although our preprocessing steps and image selections in either method
+attempt to minimize all mismatches between images, there are
+unavoidable discontinuities due to different lighting conditions or
+inaccuracies in planar geometry or projection. These can however be
+treated and smoothed over by applying alpha blending over image seams.
+Whether the units we are blending are rectangularly-cropped images or
+rectangular tiles, we can apply the same blending procedure, as long
+as we have a guaranteed overlap between units to blend over.
+
+For the tile caching method, we can ensure overlap by texturing a
+larger tile than needed for display. For example, for a rendered tile
+$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
+\times (l_1 + l_2)$ in size. For the seam minimization method, we have
+already ensured overlap between images. To enforce consistent blending
+however, it is beneficial to add a minimuum required overlap distance
+while solving the shortest path problem in Section
+\ref{sec:imageSelection}. If images overlap in a region greater than
+the overlap distance, we only apply blending over an area equal to the
+overlap distance.
+
+We apply alpha blending to blend pixels
+linearly across overlapping regions. Figure
+\ref{fig:pipeline} shows our entire texture mapping pipeline and demonstrates the
+final blended output of both approaches.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{pipeline.pdf}
+  \caption{Our final texture processing pipeline, with the final
+    output of both approaches.}
+  \label{fig:pipeline}
+\end{figure}
+
+\section{Results and Conclusions}
+\label{sec:resultsAndConclusions}
+In this paper, we have developed an approach to texture map models with noisy camera localization data. We are
+able to refine image locations based on feature matching, and robustly
+handle outliers.  We generalized one approach to texture mapping to
+any manner of planes and images, and successfully textured both simple
+rectangular walls as well as complex floor and ceiling geometry. We
+also presented an optimized texturing method that takes advantage of
+our localization refinement process and produces more seamless textures on
+planes where multiple head-on images are available. Each of these
+approaches is highly modular, and easily tunable for different
+environments and acquisition hardware.
+
+Ceilings and floors textured with the tile caching approach, and walls
+textured with the seam minimization approach, are displayed in Figure
+\ref{fig:results}. A more detailed walkthrough demonstrating fully
+textured 3D models using the approaches in this paper is available in
+the accompanying video to this paper.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{4thfloor21.jpg}
+  \includegraphics[width=3in]{4thfloor61.jpg}
+  \includegraphics[width=2in]{4thfloor8.jpg}
+  \includegraphics[width=3in]{fullmodel.png}
+  \caption{Examples of our final texture mapping output for walls,
+    floors, and ceilings}
+  \label{fig:results}
+\end{figure}
+
+{\small \bibliographystyle{ieee} \bibliography{egbib} }
 
 \end{document}
+
+\message{ !name(paper.tex) !offset(-770) }

### 2012-06-22 3dimpvt/paper.tex
draft 2.5

@@
 %%%%%%%%% TITLE
-\title{Texture Mapping Indoor Environments with Imperfect Camera Localization}
+\title{Texture Mapping 3D Models of Indoor Environments with Noisy
+  Camera Poses}
 
@@
   applications such as virtual reality and environment
-  mapping. Applying realistic textures to these models is an important
-  step in generating accurate visualizations of data gathered by
-  modeling systems.  Unfortunately, the localization of cameras in
-  such systems often suffer from inaccuracies, resulting in visible
-  discontinuties when different images are projected adjacently onto a
-  plane for texturing. Previous approaches at minimizing these
-  discontinuities do not robustly handle a wide range of camera
-  locations and angles, and often suffer from error accumulation when
-  stitching together multiple images. We propose two approaches for
-  reducing discontinuities during texture mapping, one to robustly
-  accomodate images of all orientations, and one to take advantage of
-  optimal situations where images have uniform orientation.
+  mapping. Applying textures to these models is an important step in
+  generating photorealistic visualizations of data gathered by
+  modeling systems.  The localization of cameras in such systems often
+  suffer from inaccuracies, resulting in visible discontinuties when
+  different images are projected adjacently onto a plane for
+  texturing. We propose two approaches for reducing discontinuities
+  during texture mapping, one to robustly accomodate images of all
+  orientations, and one to take advantage of optimal situations where
+  images have uniform orientation. The effectiveness of our approaches
+  will be demonstrated on two indoor datasets.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:introduction}
 Three-dimensional modeling of indoor environments has a variety of
@@
 3D models generated by indoor modeling systems, with specific
-attention given to a human-operated system with higher localization
-errors and greater variance in camera locations. The paper is
-organized as follows. Section 2 provides an overview of the backpack
-modeling system and data processing pipeline from which input data and
-examples used throughout this paper originate. Section 3 describes the
-general problem of texture mapping and examines two simple mapping
-approaches and their problems.  Section 4 demonstrates previous
-attempts at localization refinement, and presents our new approach to
-image alignment. Section 5 combines our image alignment algorithm with
-a simple image selection approach, as well as with a new method for
-image selection that takes advantage of optimal images. Section 6
-contains results.
+attention given to a human-operated system with high camera pose
+errors and great variance in camera locations.
 
-\section{Backpack Modeling System}
 The first step in automated 3D modeling is the physical scanning of
 the environment's geometry. An indoor modeling system must be able to
-calculate camera locations within an environment while simulatenously
+recover camera poses within an environment while simulatenously
 reconstructing the 3D structure of the environment itself. This is
@@
 advantages over vehicular-based systems in terms of agility and
-portability. Unfortunately, human-operated systems also suffer from a
-lack of automation and stability, resulting in much higher data
-variance and localization error. As a result, common methods for
-texture mapping generally produce poor results, as later shown in
-section 3. Before discussing how to overcome these challenges, we will
-first provide an overview of the backpack modeling system from which
-our test data was obtained.
+portability. Unfortunately, human-operated systems also result in much
+larger localization error. As a result, common methods for texture
+mapping generally produce poor results, as later shown in Sections
+\ref{sec:simpleTextureMapping} and
+\ref{sec:existingApproaches}. Before discussing how to overcome these
+challenges, we first provide an overview of the backpack modeling
+system from which our test data has been obtained.
 
-\subsection{Data Acquisition Hardware}
-The backpack-mounted modeling system that captured our data contains
-five 2D laser range scanners, two cameras, an orientation sensor, and
-an IMU. The laser scanners are mounted orthogonally and have a
-30-meter range and a 270$^{\circ}$ field of view. The two cameras are
-equipped with fisheye lenses, reaching an approximately 180$^{\circ}$
-field of view, and are mounted with one facing left and one facing
-right. These cameras take images at the rate of 5 Hz. The orientation
-sensor provides orientation parameters at a rate of 180 Hz. The IMU
-provides highly accurate measurements of all 6 DOF at 200 Hz, and is
-used as a ground truth reference for localization processes.
+Our backpack-mounted modeling system contains five 2D laser range
+scanners, two cameras, and an orientation sensor. The laser scanners
+are mounted orthogonally and have a 30-meter range and a 270$^{\circ}$
+field of view. The two cameras are equipped with fisheye lenses,
+reaching an approximately 180$^{\circ}$ field of view, and are mounted
+with one facing left and the other facing right. These cameras take
+images at the rate of 5 Hz. The orientation sensor provides
+orientation parameters at a rate of 180 Hz.
 
-With the backpack actively scanning, the human operator wearing it
-takes great care to walk a path such that every wall in the desired
-indoor environment is passed and scanned lengthwise at least once.
+With the laser scanners active, the human operator wearing the
+backpack takes great care to walk a path such that every wall in the
+desired indoor environment is traversed and scanned lengthwise at
+least once.
 
-\subsection{Environment Reconstruction}
 Using data gathered by the onboard sensors and multiple localization
-and loop-closure algorithms, the backpack is first localized over its
+and loop-closure algorithms, the backpack is then localized over its
 data collection period, and a 3D point cloud of the surrounding
-environment is constructed based on the laser scanner readings
-relative to the backpack \cite{chen2010indoor}. Approximate normal
-vectors for each point in the point cloud are then calculated by
-gathering neighboring points within a small radius and processing them
-through principal component analysis. These normal vectors allow for
-the classification and grouping of adjacent points into structures
-such as walls, ceilings, floors, and staircases. A RANSAC algorithm is
-then employed to fit polygonal planes to these structured groupings of
-points, resulting in a fully planar model
-\cite{sanchez2012point}. This model, consisting of multiple 2D
-polygonal planes in 3D space, along with the set of images captured by
-the backpack's camera, can be considered the input to our texture
-mapping problem.
+environment is constructed \cite{chen2010indoor, kua2012loopclosure,
+  liu2010indoor}. Approximate normal vectors for each point in the
+point cloud are then calculated by gathering neighboring points within
+a small radius and processing them through principal component
+analysis. These normal vectors allow for the classification and
+grouping of adjacent points into structures such as walls, ceilings,
+floors, and staircases. A RANSAC algorithm is then employed to fit
+polygonal planes to these structured groupings of points, resulting in
+a fully planar model \cite{sanchez2012point}. This model, consisting
+of multiple 2D polygonal planes in 3D space, along with the set of
+images captured by the backpack's cameras and their 3D poses, can be
+considered the input to our texture mapping problem
+
+The remainder of the paper is organized as follows. Section
+\ref{sec:simpleTextureMapping} describes the general problem of
+texture mapping and examines two simple mapping approaches and their
+shortcomings.  Section \ref{sec:existingApproaches} demonstrates two
+previous attempts at localization refinement, and demonstrates their
+inadequacies for our datasets.  Section \ref{sec:proposedApproach}
+presents our proposed approach to texture mapping, combining an
+improved localization refinement process with two image selection
+approaches. Section \ref{sec:resultsAndConclusions} contains results
+and conclusions.
 
 \section{Simple Texture Mapping}
-
+\label{sec:simpleTextureMapping}
 \begin{figure}
@@
 
-In all subsequent sections, we will discuss the process of texture
-mapping a single plane, as the texturing of each of our planes is
-independent and can be completed in parallel.
+In all subsequent sections, we discuss the process of texture mapping
+a single plane, as the texturing of each of our planes is independent
+and can be completed in parallel.
 
 The geometry of the texture mapping process for a plane is shown in
-figure \ref{fig:projection}.  As described in the previous section, we
-are provided with a set of $M$ images with which we must texture our
-target plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
+Figure \ref{fig:projection}.  As described earlier, we are provided
+with a set of $M$ images with which we must texture our target
+plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
 translates a 3D point in the world coordinate system to a 2D point or
@@
 the camera's position in 3D world coordinates at the time that image
-$i$ was taken. These extrinsic parameters are determined by the
-backpack hardware and localization algorithms mentioned in Section
-2. A point $X$ on the plane in 3D space can be related to its
-corresponding pixel $x$ in image $i$ through the following equation:
+$i$ is taken. These extrinsic parameters are determined by the
+backpack hardware and localization algorithms mentioned earlier. A
+point $X$ on the plane in 3D space can be related to its corresponding
+pixel $x$ in image $i$ through the following equation:
 
@@
 generating minimum bounding boxes for them. Since our final textures
-will be stored as standard rectangular images anyway, we can simply
-leave the area between plane boundary and bounding box untextured, or
-crop it out as needed. A plane to be textured is thus defined by a
-bounding box with corners $C_i$ in world coordinates and a normal
-vector indicating the front facing side of the plane. Our goal is to
-texture this plane using images captured by the backpack, while
+are stored as standard rectangular images anyway, we can simply leave
+the area between plane boundary and bounding box untextured, or crop
+it out as needed. A plane to be textured is thus defined by a bounding
+box with corners $C_i$ in world coordinates and a normal vector
+indicating the front facing side of the plane. Our goal is to texture
+this plane using images captured by the backpack system, while
 eliminating any visual discontinuities or seams that would suggest
-that the plane's texture was not composed of a single continuous
-image.
+that the plane's texture is not composed of a single continuous image.
 
 \subsection{Direct Mapping}
+\label{sec:directMapping}
 
@@
 we can texture the plane by discretizing it into small square tiles,
-generally about 5 pixels across, and picking an image to texture each
-tile with. Since we are provided with far more images than necessary
-to cover our plane, this process is a simple way of assigning
-texturess to locations on our plane. We choose to work with
-rectangular units to ensure that borders between any two distinct
-images in our final texture will be either horizontal or
-vertical. Since most environmental features inside buildings are
-horizontal or vertical, any seams in our texture will intersect them
-miniimally and be less noticeable.
+generally about 5 pixels across, and choosing an image to texture each
+tile with. We choose to work with rectangular units to ensure that
+borders between any two distinct images in our final texture are
+either horizontal or vertical. Since most environmental features
+inside buildings are horizontal or vertical, any seams in our texture
+intersect them miniimally and are likely to be less noticeable.
 
@@
 corners, which we can quickly check by projecting $t$ into each image
-and using the projection method above. Furthermore, each candidate
-image must have been taken at a time when its camera had a clear
-line-of-sight to $t$, which can be calculated using
-standard ray-polygon intersection tests between the camera location,
-the center of $t$, and other planes, all in world coordinates.
+using the projection method above. Furthermore, each candidate image
+must have been taken at a time when its camera had a clear
+line-of-sight to $t$, which can be calculated using standard
+ray-polygon intersection tests between the camera location, the center
+of $t$, and other planes, all in world coordinates.
 
@@
 wish to minimize the distance between cameras used for texturing and
-our plane. Additionally, we desire images that project squarely onto
-the plane, maximizing the resolution and amount of useful texture
-available in their projections.
+our plane. Additionally, we desire images that are projected
+perpendicularly onto the plane, maximizing the resolution and amount
+of useful texture available in their projections.
 
-A scoring function to maximize these two criteria is shown in figure
-\ref{fig:scoringFunction}.
+These two criteria can be met by maximizing the function
+
+\[
+\frac{1}{d} \cdot (-1 \cdot C) \cdot N
+\]
+
+which minimizes camera angle $\alpha$ and distance $d$ as shown in
+Figure \ref{fig:scoringFunction}.
 
@@
   \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{For each tile, we find the image that minimizes $d$ and
-    $\alpha$ by maximizing the following equation: \\ $(1/d \cdot (-1
-    \cdot C) \cdot N)$}
+  \caption{Images are selected by minimizing camera angle $\alpha$ and
+    distance $d$.}
   \label{fig:scoringFunction}
@@
 \subsection{Mapping with Caching}
+\label{sec:mappingWithCaching}
 Since discontinuities occur where adjacent tiles select different
-images that do not match up well, it makes sense to take into account
-image choices made by neighboring tiles while selecting the best image
-for a tile. By using the same image across tile boundaries, we
-eliminate the discontinuity altogether. If this is not possible, using
-very similar images will result in less noticeable discontinuities.
+images that do not align, it makes sense to take into account image
+selections made by neighboring tiles while selecting the best image
+for a given tile. By using the same image across tile boundaries, we
+eliminate the discontinuity altogether. If a tile is not visible in
+images chosen by its neighbors, using similar images is likely to
+result in less noticeable discontinuities.
 
@@
 before searching through the entire set. The first subset of images is
-the set of images selected by adjacent tiles that have already been
-processed. We must first check which images can map to $t$, and then
-of those, we make a choice according to the same scoring function in
-figure \ref{fig:scoringFunction}. Rather than blindly reusing this
-image, we ensure it meets a predefined score threshold to be
-considered a good image. If no good image is found, we then check our
-second subset of images, which consists of images that were taken near
-the images in the first subset, both spatially and temporally. These
-images are not the same as the ones used for neighboring tiles, but
-they were taken at a similar location and time, suggesting that their
-localization and projection will be very similar. Again, if no good
-image is found according to a threshold, we then must search the
-entire set of candidate images.
+those selected by adjacent tiles that have already been textured. We
+must first check which images can map to $t$, and then of those, we
+make a choice according to the same scoring function in Figure
+\ref{fig:scoringFunction}. Rather than blindly reusing this image, we
+ensure it meets a threshold, which we set to $\alpha < 45^\circ$, to
+be considered a good image.
+
+If no good image is found, we then check our second subset of images,
+which consists of images that were taken near the images in the first
+subset, both spatially and temporally. These images are not the same
+as the ones used for neighboring tiles, but they were taken at a
+similar location and time, suggesting that their localization and
+projection are very similar. Again, if no good image is found
+according to the same threshold, we then must search the entire set of
+candidate images.
 
@@
 
-The results of this caching approach are shown in figure
-\ref{fig:caching}.  Discontinuities have been reduced overall, but the
-amount of remaining seams suggests that image selection alone cannot
-produce seamless textures. The image projections themselves will have
-to be adjusted in order to reliably generate clean textures.
+The result of this caching approach is shown in figure
+\ref{fig:caching}. As compared to \ref{fig:directMapping},
+discontinuities have been reduced overall, but the amount of remaining
+seams suggests that image selection alone cannot produce seamless
+textures. Camera matrices, or the image projections themselves have to
+be adjusted in order to reliably generate clean textures.
 
-\section{Localization Refinement}
-In order to produce photorealistic texture mapping, either camera
-matrices need to be refined such that their localization is pixel
-accurate, resulting in a perfect mapping, or image stitching
-techniques need to be applied to provide this illusion. Before
-examining these approaches, we first obtain a set of images to work
-with.
+\section{Existing Approaches to Image-Aligned Texture Mapping}
+\label{sec:existingApproaches}
+In order to produce seamless texture mapping, either camera matrices
+need to be refined such that their localization is pixel accurate,
+resulting in a perfect mapping, or image stitching techniques need to
+be applied to provide this illusion. Before examining these
+approaches, we first obtain a set of images to work with.
 
-Rather than perform camera or image adjustments across many thousands
-of images, we choose to work with the more limited set of images
-corresponding to those chosen by the direct mapping approach, without
-caching. This set of images constitutes a good candidate set for
-generating a final seamless texture, since it meets three important
-criteria. First, this set of images contains at least one image that
-covers each tile on our plane. Thus, unless extreme changes in
-localization occur, we can ensure that there will be no holes in our
-final texture. Second, since images are all selected according to the
-same scoring function in figure \ref{fig:scoringFunction}, we know
-that our images are all taken at as much of a head-on angle as
-possible and should project onto the plane in similar ways. Third, as
-a side result of the scoring function, selected images are only good
-candidates for the tiles near their center of projection. Thus, there
-should be plenty of overlap between selected images, allowing for some
-degree of shifting without resulting in holes, as well as area for
-blending between them. With this set of images, we now examine two
-approaches towards refining and combining their projections, before
-demonstrating our own.
+Rather than perform camera or image adjustments across the many
+thousands of images acquired in a typical data collection, we opt to
+work with the more limited set of images corresponding to those chosen
+by the direct mapping approach, without caching. This set of images
+constitutes a good candidate set for generating a final seamless
+texture since it meets three important criteria. First, it contains at least one image that covers each tile on our
+plane; this ensures no holes in our final texture. Second, since
+images are all selected according to the same scoring function in
+Figure \ref{fig:scoringFunction}, they are taken at as much of a head-on angle as possible and should project
+onto the plane in similar ways. Third, as a side result of the scoring
+function, selected images are only good candidates for the tiles near
+their center of projection. Thus, there should be plenty of overlap
+between selected images, allowing for some degree of shifting without
+resulting in holes, as well as area for blending between them. With
+this set of images, we now review two existing approaches towards refining and
+combining their projections.
 
 \subsection{Image Mosaicing}
-
+\label{sec:imageMosaicing}
 \begin{figure}
@@
 careful hand tuning as well. Many planes that had fewer features
-simply failed outright. This leads to the conclusion that image
-mosaicing is not a robust enough solution for reliably texture mapping
-our dataset.
+simply failed outright. Thus, image mosaicing is not a robust enough
+solution for reliably texture mapping our dataset.
 
 \subsection{Image-Based 3D Localization Refinement}
-
+\label{sec:imageBased3DRefinement}
 \begin{figure}
@@
   \includegraphics[width=3in]{Graph_crop.pdf}
-  \caption{Using the graph-based localization refinement algorithm
-    from [11] suffers from the problem of compounding errors. }
+  \caption{The graph-based localization refinement algorithm from [11]
+    suffers from the problem of compounding errors. }
   \label{fig:graph}
@@
 approach suffers from a similar error propagation problem shown in
-Figure \ref{fig:graph}. In our new approach, we also refine the
-placement of images using image correspondences. However, we do so in
-two dimensions on the plane whereas this previous work did so over all
-6 degrees of freedom. Refining in two dimensions on the plane is less
-flexible in that it does not address projection errors, however, it
-provides significant benefits while avoiding the error propagation
-problem.
+Figure \ref{fig:graph}.
 
-\subsection{Improved Localization through 2D Matching}
-Our approach begins with the projection of all our images onto
-separate copies of our plane, such that no projected data is covered
-up and lost. This is done in the same way as the approaches in section
-3. We then perform Hough transforms to rotate these projections
-similarly, and then shift each image's projection such that its
-overlapping regions with other projections are as seamless as
-possible.
+\section{Proposed Method for Seamless Texture Mapping}
+\label{sec:proposedApproach}
+Our proposed approach towards texture mapping is a two-step
+process. First, with the same input set of images as described in
+Section \ref{sec:existingApproaches}, we perform image rotation and
+shifting in order to maximize SIFT feature matches between images. We
+then project these images onto our plane, applying textures either
+with the tile caching method from Section
+\ref{sec:mappingWithCaching}, or with the more specialized method
+described in Section \ref{sec:seamMinimization}.
 
-\subsection{Hough Transforms}
-Our first step is to use Hough transforms to adjust the rotation of
-projected images. Rather than try and match the orientation of
-features in each image, we simply apply rotations such that any strong
-near-vertical features are made completely vertical. This is effective
-for indoor modeling, since strong features in indoor scenes usually
-contain vertical lines corresponding to doors, wall panels,
+\subsection{Image Projection and Rotation}
+\label{sec:projectionAndRotation}
+Our localization approach begins with the projection of all our images
+onto separate copies of our plane, such that no projected data is
+covered up and lost. This is done in the same way as the approaches in
+Section \ref{sec:simpleTextureMapping}. We then perform rotations on
+these projections, as adjacent images with different orientations will
+result in strong discontinuities.
+
+These rotations are accomplished by using Hough transforms, which
+detect the presence and orientation of linear features in our
+images. Rather than match the orientation of such features in each
+image, we simply apply rotations such that the strongest near-vertical
+features are made completely vertical. This is effective for indoor
+models, since strong features in indoor scenes usually consist of
+parallel vertical lines corresponding to doors, wall panels,
 rectangular frames, etc. If features in the environment are not
-vertical, or there are few features overall, this step should be
-skipped.
+vertical, or are not parallel to eachother, this step is skipped.
 
@@
 
-\subsection{SIFT Feature Matching}
-Our next step is to try and fix misalignment between overlapping
-images. We do this by first searching for corresponding points between
-all pairs of overlapping images using SIFT feature matching
+\subsection{Robust SIFT Feature Matching using RANSAC}
+\label{sec:robustSIFTFeatureMatching}
+Our next step is to fix misalignment between overlapping images. We do
+this by first searching for corresponding points between all pairs of
+overlapping images using SIFT feature matching
 \cite{lowe1999object}. An illustration of this is given in Figure
-\ref{fig:matches}. The SIFT matches allow us to determine
-feature-based $x$ and $y$ distances between two images on the plane,
-which will allow us to reevaluate where each image should be
-projected.
+\ref{fig:matches}. The SIFT matches allow us to determine $dx$ and
+$dy$ distances between each pair of features for two images on the
+plane, determining where they should be projected relative to
+eachother.
 
-\subsubsection{Robust SIFT Distances using RANSAC}
-Since indoor environments often contain repetitive features, such as
+Since indoor environments often contain repetitive features such as
 floor tiles or doors, we need to ensure that our SIFT-based distances
-are reliable. In order to diminish the effect of incorrect matches and
+are reliable. In order to mitigate the effect of incorrect matches and
 outliers, the RANSAC framework \cite{fischler1981random} is used for a
-robust estimate of the $x$ and $y$ distances between the two
-images. The RANSAC framework attempts to build a consensus among the
-SIFT matches between every pair of images, and tries to generate the
-horizontal and vertical distance between them while ignoring the
-influence of outliers that would skew the results. The framework
-handles the consensus-building machinery, and only requires that two
-functions be specified: the fitting function and the distance
-function. These functions are called for random subsets of the SIFT
-matches until the best set of inliers is found. For this application,
-the fitting function simply finds the average distance between
-matches. If the matches are exactly correct and the image is frontal
-and planar then the distances for various SIFT feature matches should
-be the same. Our distance function for a pair of points is the
-difference between those points' SIFT match distance and the average
-distance computed by the fitting function. We specified a 10 pixel
-outlier threshold to the framework. This means that a SIFT match is
-labeled as an outlier if its horizontal or vertical distance is not
-within 10 pixels of the average distance computed by the fitting
-function.
+robust estimate of the optimal $dx$ and $dy$ distances between two
+images. The RANSAC framework handles the consensus-building machinery,
+and requires a fitting function and a distance function. For this
+application, the fitting function simply finds the average distance
+between matches in a pair of images. Our distance function for a pair
+of points is the difference between those points' SIFT match distance
+and the average distance computed by the fitting function; we use a 10
+pixel outlier threshold. This means that a SIFT match is labeled as an
+outlier if its horizontal or vertical distance is not within 10 pixels
+of the average distance computed by the fitting function.
 
 \subsubsection{Refining Image Positions using Least Squares}
-
+\label{sec:refiningImagePositions}
 There are a total of $M^{2}$ possible pairs of images, though we only
@@
 points. Given these distances and the original image location
-estimates, we can solve a least squares problem ($\textrm{min}_{\beta}
-||\beta X - y||_2^2 $) to estimate the correct location of the images
-on the plane. The vector $\beta$ of unknowns represent the correct $x$
+estimates, we can solve a least squares problem ($\textrm{min}_{\vec{\beta}}
+||X \vec{\beta} - \vec{\gamma}||_2^2 $) to estimate the correct location of the images
+on the plane. The $M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
 and $y$ locations of each image on the plane from $1 \dots M$. The
-optimal $x$ and $y$ locations are calculated in the same way, so we
-will only consider the $x$ locations here:
+optimal $x$ and $y$ locations are obtained in the same way, so we
+only consider the $x$ locations here:
 
@@
 
-\[\beta =
+\[\vec{\beta} =
 \begin{pmatrix}
@@
 
-The matrix $X$ is constructed with one row for each pair of images
+The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row for each pair of images
 with measured distances produced by the SIFT matching stage. A row in
@@
 
-Finally, the observation vector $y$ is constructed using the
+Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is constructed using the
 SIFT-based distances generated earlier in the matching stage. The
@@
 distances. The last element in the observation vector is the location
-of the first image determined by its original localization.
+of the first image determined by its original noisy localization, from \cite{chen2010indoor, liu2010indoor}:
 
 \[
-y^T =
+\vec{y}^T =
 \begin{pmatrix}
@@
 
-The $\beta$ that minimizes $||\beta X - y||_2^2$ results in a set of
+The $\vec{\beta}$ that minimizes $||X \vec{\beta} - \vec{\gamma}||_2^2$ results in a set of
 image locations on the plane that best honors all the SIFT-based
@@
 another. In this case we add rows to the $X$ matrix and observations
-to the $y$ vector that contain the original $x$ and $y$ distance
-estimates generated by the localization algorithm. Another way to do
+to the $\vec{\gamma}$ vector that contain the original noisy $x$ and $y$ distance
+estimates generated by the localization algorithm \cite{chen2010indoor, liu2010indoor}. Another way to do
 this is to add rows for all neighboring pairs of images and solve a
 weighted least squares problem where the SIFT distances are given a
-higher weight i.e. 1, and the distances generated by the localization
-algorithm are given a smaller weight i.e. 0.01.
+higher weight i.e. 1, and the noisy distances generated by the localization
+algorithm \cite{chen2010indoor, liu2010indoor} are given a smaller weight i.e. 0.01.
 
 After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our image projections should overlap and
-match eachother with far greater accuracy.
-
-\section{Improved Texture Mapping with Localization and Blending}
-Now that our images have been relocalized for much greater accuracy
-relative to eachother, we can revisit the cached mapping approach from
-section 3.2. Since we now have higher confidence in the quality of
-image boundaries, we can also explore an alternate method that greatly
-reduces seams in cases where we have an abundance of optimal images.
-
-\subsection{Localized Mapping with Caching}
-In figure \ref{fig:shifted}, we see the same wall from section 3,
-texture mapped using the caching method after our localization
-refinement process.
+making the resultant shifts, our images overlap and
+match each other with far greater accuracy.
+Applying the tile caching method from Section \ref{sec:mappingWithCaching} on these re-localized images, results in the significant improvements shown in Figure \ref{fig:shifted}.
 
@@
 
-It should be evident that our localization adjustments resulted in a
-major improvement. A great strength of our tiling approach for image
-selection is that it extracts the areas with good camera angles from
-each image, and thus can handle images of all types. As demonstrated
-on the floor plane in figure \ref{fig:floor_suboptimal}, we can run
-this process even with extremely poor image projections, where the
-amount of quality texture for each image is limited. Additionally,
-since our plane is discretized, we can handle arbitrarily
-complex plane geometry as well.
+\subsection{Texture Mapping with Seam Minimization}
+\label{sec:seamMinimization}
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{floor_suboptimal.jpg}
-  \caption{The tiling method ensures that only the most optimal
-    portions of each image are used. This allows it to successfully
-    handle all manner of plane and image geometry, as shown in this
-    floor texture.}
-  \label{fig:floor_suboptimal}
-\end{figure}
+As mentioned earlier, our backpack system has 2 cameras with
+$180^\circ$ fisheye lenses facing to the right and left. Since the
+backpack operator only takes care to fully scan each wall and not
+necessarily the entirety of each ceiling and floor, cameras at higher
+angles with respect to plane normal vectors must be used for texturing
+large areas of floor and ceiling planes. These high camera angles
+translate into images that span extremely large areas once projected
+onto their planes. Such image projections have good scores (from
+Figure \ref{fig:scoringFunction}) for certain areas on the plane, but
+much worse scores for other areas. This can be seen in Figure
+\ref{fig:highCameraAngle}. The tiling approach used in Section
+\ref{sec:simpleTextureMapping} was thus a good choice for texturing,
+as it allowed us to only use the parts of image projections that were
+good choices for their respective plane locations.
 
-Given that the backpack system's hardware and the data collection
-process strive for optimal wall texturing however, we can aim for a
-less conservative approach when texturing walls, and simply fall back
-to this more robust approach as needed.
+For wall planes however, we have images all taken from close distances
+and more head-on angles, and thus much smaller near-rectangular
+projections to work with. As a result, there is less deviation over
+the score of each tile within an image, as well as over the average
+scores of all images. This means that the scoring criteria from Figure
+\ref{fig:scoringFunction} is less relevant to walls, which enjoy an
+abundance of head-on images.
 
-\subsection{Texture Mapping with Seam Minimization}
-The cached tile approach selected images based on individual and
-neighboring quality of image selections, in an effort to reduce seams
-between tiles. In a more optimal case, as the backpack system provides
-for walls, images are all taken from close distances and have
-near-rectangular projections and thus more similar scores according to the
-scoring function in figure \ref{fig:scoringFunction}. Thus, we can
-reason that rather than selecting the set of best images, since all
-images are good, we should instead select the best set of images, such
-that the selection together results in the cleanest final texture. We
-will accomplish this by using entire images where possible, defining a
-cost function between images, and seeking to minimize total cost.
+Thus, for planes with optimal images, rather than selecting the set of
+best images, since all images are near in quality, we instead select
+the best set of images, such that the selection together results in
+the cleanest final texture. We will accomplish this by using entire
+images where possible, and defining a cost function to minimize the
+visibility of seams in our final texture.
 
 \subsection{Occlusion Masking}
-Before we proceed with using our images, we need to ensure that they
-contain only content that should be mapped onto the target plane in
-question. The tiling approach used previously only checked occlusion
-for each tile as it was being textured, so we need to perform
-occlusion checks over the entirety of each image, so we know which
-areas are available for texture mapping. By performing the same
-intersection tests used for tiles, we can determine whether individual
-sections of an image are occluded.
+\label{sec:occlusionMasking}
+To begin with, we need to ensure that our images contain only content
+that should be mapped onto the target plane in question. The tiling
+approach used previously only checks occlusion for each tile as it is
+being textured. For our new approach, we use entire images, so we need
+to perform occlusion checks over the entirety of each image to
+determine available areas for texture mapping.
 
@@
 areas, our image projections will remain largely rectangular. We can
-thus make efficiency improvements by recursively splitting each image
-into rectangular pieces, and performing occlusion checks where
-needed. To actually occlude out rectangles, we simply remove their
-texture, as we will ensure that untextured areas are never chosen for
-texture mapping.
+thus be efficient by recursively splitting each image into rectangular
+pieces, and performing the same occlusion checks used in the tiling
+process where needed. To actually occlude out rectangles, we simply
+remove their texture, as we will ensure that untextured areas are
+never chosen for texture mapping.
 
-\subsubsection{Inter-Image Cost Functions}
-In order to objectively decide which set of images results in the
-cleanest texture, we need a cost function such that we can evaluate
-the visibiilty of seams between images in our set. A straightforward
-cost function that accomplishes this is the sum of squared pixel
-differences in overlapping regions between all pairs of
-images. Minimizing this cost function encourages image boundaries to
-occur in featureless areas, such as bare walls, as well as in areas
-where images match extremely well.
+\subsection{Image Selection}
+\label{sec:imageSelection}
+To determine the set of images that results in the cleanest texture,
+we need a cost function to evaluate the visibiilty of seams between
+images in our set. A straightforward cost function that accomplishes
+this is the sum of squared pixel differences in overlapping regions
+between all pairs of images after they have been aligned as described
+in Section \ref{sec:projectionAndRotation}. Minimizing this cost
+function encourages image boundaries to occur either in featureless
+areas, such as bare walls, or in areas where images match extremely
+well.
 
-Another possible cost function is overall edge energy, i.e. the sum of
-the smoothed gradient over seams. Minimizing this encourages image
-boundaries to be placed in featureless areas even more than the first
-cost function. For the results shown throughout this paper, the first
-cost function was used, as the regular occurrence of featureless areas
-was not guaranteed in our datasets.
+With the cost function defined, we must now select the set of images
+for which the overall cost function is minimized. Since nearly all the
+images for our optimal case are head on, the best strategy to minimize
+seams is to choose as few images as possible while texturing a given
+plane. Thus,to cover the entirety of a plane, our problem can be
+defined as minimally covering a polygon i.e. the plane, using other
+polygons of arbitrary geometry i.e. our image projections, with the
+added constraint of minimizing our cost function between chosen
+images.  This is a complex problem, though we can take a number of
+steps to simplify it. Given that our wall-texture candidate images are
+all taken from a head-on angle, and assuming only minor rotations are
+made during localization refinement, we can reason that their
+projections onto the plane are approximately rectangular, as in Figure
+\ref{sec:goodCameraAngle}. By discarding the minor excess texture and
+cropping them all to be rectangular, our problem becomes the
+conceptually simpler one of filling a polygon with rectangles, such
+that the sum of all edge costs between each pair of rectangles is
+minimal. We thus also retain the advantages of working with
+rectangular units, as explained in section
+\ref{sec:simpleTextureMapping}.
 
-\subsubsection{Image Selection}
-
-Now that we have a cost function defined, we mechanically select the
-set of images for which the overall cost function is minimized. Since
-we aim to cover the entirety of our plane, our problem is to minimally
-cover a polygon(our plane), using other polygons of arbitrary geometry
-(our image projections), with the added constraint of minimizing our
-cost function between chosen images. This is a complex problem, though
-we can take a number of steps to simplify it. Returning again to the
-optimality of our situation when texturing walls, we can make a quick
-simplification for the sake of efficiency. Given that our wall-texture
-candidate images were all taken from a head-on angle, and assuming
-only minor rotations were made during localization refinement, we can
-reason that their projections onto the plane are approximately
-rectangular. By discarding the minor excess texture and cropping them
-all to be rectangular, our problem becomes the conceptually simpler
-problem of filling a polygon with rectangles, such that the sum of all
-edge costs between each pair of rectangles is minimal. We thus also
-retain axis-aligned image boundaries, along with their advantages
-explained in section 3.
-
-By taking two more shortcut we can simplify our problem down even
-further. Since this approach is already assuming optimal images, we
-know it will be applied on walls, which are the focus of the backpack
-modeling system. For wall planes, which are nearly always rectangular,
-care is taken so that images contain the entirety of their
-floor-to-ceiling range, and thus we do not have wall images such that
-one should be projected vertically above the other. In essence, we
-need only to ensure horizontal coverage of our planes, as our images
-provide full vertical coverage themselves. We can thus construct a
-Directed Acyclic Graph (DAG) from the images, with edge costs defined
-by our cost function above, and solve a simple shortest path problem
-to find an optimal subset of images with regard to the cost functions.
+The location and orientation of the cameras on our backpack is such
+that our images nearly always contain the entirety of the floor to
+ceiling range of wall planes. Images are therefore rarely projected
+with one above the other when texturing wall planes, which correspond
+to the optimal planes we are working with.  In essence, we need only
+to ensure horizontal coverage of our planes, as our images provide
+full vertical coverage themselves. We can thus construct a Directed
+Acyclic Graph (DAG) from the images, with edge costs defined by our
+cost function above, and solve a simple shortest path problem to find
+an optimal subset of images with regard to the cost functions.
 
@@
 plane, and one end node representing the right border of the
-plane. The left artificial node has directed edges with equal cost
-$C_0$ to all images that meet the left border of the plane, and the
-right artificial node has directed edges from all images with that
-meet the right border of the plane, with equal cost $C_0$ as well.
+plane. The left(right) artificial node has directed edges with equal
+cost $C_0$ to(from) all images that meet the left(right) border of the
+plane.
 
-We now solve the standard shortest path problem from the start node to
-the end node. This provides a set of images that completely covers the
-plane horizontally, while minimizing the cost of the seams between
-images.
+We now solve the shortest path problem from the start node to
+the end node \cite{dijkstra}. This provides a set of images
+completely covering the plane horizontally, while minimizing the cost
+of the seams between images.
 
@@
 entirely covered by a chosen image, we are left with a hole where no
-image was chosen to texture. Rather than reverting to a 2D-coverage
-problem, we can elect to simply fill the hole by selecting images to
-fill it in a greedy fashion with respect to edge costs of the same
-cost function.
+image is chosen to texture.
+
+SOMETHING HERE ABOUT CRAP CRAP
+
+Rather than reverting to a 2D-coverage problem, we can elect to simply
+fill the hole by selecting images to fill it in a greedy fashion with
+respect to edge costs of the same cost function.
 
 With this completed, we have now mapped every location on our plane to
-at least one image, and have minimized the amount of images, as well
+at least one image, and have minimized the number of images, as well
 as the discontinuity between their borders. In the next section, we
-will apply blending between images where they overlap, but for the
-sake of comparison with the unblended tile caching method in section
-5.1, we arbitrarily pick one image for texturing where images
-overlap. Figure \ref{fig:compare_unblended} compares the tile caching
-method against this seam minimization method.
+apply blending between images where they overlap, but for the sake of
+comparison with the unblended tile caching method in Section
+\ref{sec:mappingWithCaching}, we arbitrarily choose one image for
+texturing where images overlap. Figure \ref{fig:compare_unblended}
+compares the tile caching method against this seam minimization
+method.
 
@@
 Though both methods provide quite accurate texturing thanks to the
-localization refinement process, the seam minimization approach
-results in fewer visible discontinuities, since it directly reduces
-the cost of each image boundary, while the tile caching method uses a
-scoring function that only approximates this effect. Furthermore, seam
-minimization guarantees the best selection of images, while the tile
+alignment process, the seam minimization approach results in fewer
+visible discontinuities, since it directly reduces the cost of each
+image boundary, while the tile caching method uses a scoring function
+that only approximates this effect. Furthermore, seam minimization
+guarantees the best selection of images, while the sequential tile
 caching method may select images early on that turn out to be poor
@@
 minimization approach on walls, due to its superior output when
-provided with optimal images. Floors and ceilings however, given their
-suboptimal images, as shown in figure \ref{fig:floor_suboptimal}, can
-only be textured using the tile caching method.
+provided with head-on images. Floors and ceilings however, given their
+images taken at oblique angles, as shown in Figure \ref{fig:floor_suboptimal}, are textured using the tile caching method.
 
 \subsection{Blending}
-Until now, blending of images has not been used, for the sake of clear
-comparisons between texturing methods. We will now apply the same
-blending process on our two final texturing methods: localization
-refinement followed by either tile caching or seam minimization.
+\label{sec:blending}
+We now apply the same blending process on our two texturing methods:
+localization refinement followed by either tile caching or seam
+minimization.
 
 Although our preprocessing steps and image selections in either method
-attempt to minimize all mismatches between images, there are cases,
-where due to different lighting conditions or inaccuracies in geometry
-or projection, where we simply have unavoidable discontinuities. These
-can however be treated and smoothed over by applying alpha blending
-over image seams.  Whether the units we are blending are
-rectangularly-cropped images or rectangular tiles, we can apply the
-same blending procedure, as long as we have a guaranteed overlap
-between units to blend over.
+attempt to minimize all mismatches between images, there are
+unavoidable discontinuities due to different lighting conditions or
+inaccuracies in planar geometry or projection. These can however be
+treated and smoothed over by applying alpha blending over image seams.
+Whether the units we are blending are rectangularly-cropped images or
+rectangular tiles, we can apply the same blending procedure, as long
+as we have a guaranteed overlap between units to blend over.
 
 For the tile caching method, we can ensure overlap by texturing a
-larger tile than we really have. For example, for a tile $l_1 x l_1$
-in size, we can make sure to associate it with a texture $(l_1 + l_2)
-x (l_1 + l_2)$ in size. For the seam minimization method, we have
+larger tile than needed for display. For example, for a rendered tile
+$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
+\times (l_1 + l_2)$ in size. For the seam minimization method, we have
 already ensured overlap between images. To enforce consistent blending
-however, it is beneficial to add a required overlap distance while
-solving the shortest path problem in section 5.2.3. If images do not
-overlap in a region at least the length of this overlap distance, we
-do not consider them to overlap at all. If images overlap in a region
-greater than the overlap distance, we will only apply blending over an
-area equal to the overlap distance.
+however, it is beneficial to add a minimuum required overlap distance
+while solving the shortest path problem in Section
+\ref{sec:imageSelection}. If images overlap in a region greater than
+the overlap distance, we only apply blending over an area equal to the
+overlap distance.
 
-Our alpha blending technique is widely used, and blends pixels
-linearly across overlapping regions. For each pixel within such a
-region, we simply scale its intensity (by a factor from 0 to 1), based
-on its distance from the image's border, with a cap set at a fixed
-distance from the border. In this way, we interpolate between two
-overlapping images, providing a gradual transition between them. Our
-texture mapping process is now complete, and in figure
-\ref{fig:pipeline}, we review our entire pipeline and demonstrate the
+We apply alpha blending to blend pixels
+linearly across overlapping regions. Figure
+\ref{fig:pipeline} shows our entire texture mapping pipeline and demonstrates the
 final blended output of both approaches.
@@
 
-\section{Conclusion and Results}
-In this paper, we have shown how to accurately texture map models,
-even when provided with imprecise camera localization data. We were
-able to refine image locations based on feature mapping, and robustly
+\section{Results and Conclusions}
+\label{sec:resultsAndConclusions}
+In this paper, we have developed an approach to texture map models with noisy camera localization data. We are
+able to refine image locations based on feature matching, and robustly
 handle outliers.  We generalized one approach to texture mapping to
@@
 also presented an optimized texturing method that takes advantage of
-our localization refinement process and produces cleaner textures on
+our localization refinement process and produces more seamless textures on
 planes where multiple head-on images are available. Each of these
@@
 
-Ceilings and floors textured
-with the robust approach, and walls textured with the optimized
-approach, are displayed in figure \ref{fig:results}. A more detailed
-walkthrough demonstrating fully textured 3D models using the
-approaches in this paper is available in the accompanying video to
-this paper.
+Ceilings and floors textured with the tile caching approach, and walls
+textured with the seam minimization approach, are displayed in Figure
+\ref{fig:results}. A more detailed walkthrough demonstrating fully
+textured 3D models using the approaches in this paper is available in
+the accompanying video to this paper.
 

### 2012-06-22 3dimpvt/paper.tex
completed v2 changes

@@
 inside buildings are horizontal or vertical, any seams in our texture
-intersect them miniimally and are likely to be less noticeable.
+intersect them minimally and are likely to be less noticeable.
 
@@
 
-These two criteria can be met by maximizing the function
-
-\[
-\frac{1}{d} \cdot (-1 \cdot C) \cdot N
-\]
-
-which minimizes camera angle $\alpha$ and distance $d$ as shown in
+These two criteria can be met by maximizing the function shown in
 Figure \ref{fig:scoringFunction}.
@@
   \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{Images are selected by minimizing camera angle $\alpha$ and
-    distance $d$.}
+  \caption{Images with minimal camera angle $\alpha$ and distance $d$
+    are selected by maximizing the function}
+  \begin{center}$\frac{1}{d} \cdot (-1 \cdot C) \cdot N$ \end{center}
   \label{fig:scoringFunction}
@@
 for a given tile. By using the same image across tile boundaries, we
-eliminate the discontinuity altogether. If a tile is not visible in
-images chosen by its neighbors, using similar images is likely to
-result in less noticeable discontinuities.
+eliminate the discontinuity altogether. If this is not possible
+because a tile is not visible in images chosen by its neighbors, using
+similar images is likely to result in less noticeable discontinuities.
 
@@
 must first check which images can map to $t$, and then of those, we
-make a choice according to the same scoring function in Figure
+make a choice according to the same scoring function in
 \ref{fig:scoringFunction}. Rather than blindly reusing this image, we
@@
 
-If no good image is found, we then check our second subset of images,
-which consists of images that were taken near the images in the first
-subset, both spatially and temporally. These images are not the same
-as the ones used for neighboring tiles, but they were taken at a
-similar location and time, suggesting that their localization and
+If no satisfactory image is found, we then check our second subset of
+images, which consists of images that were taken near the images in
+the first subset, both spatially and temporally. These images are not
+the same as the ones used for neighboring tiles, but they were taken
+at a similar location and time, suggesting that their localization and
 projection are very similar. Again, if no good image is found
-according to the same threshold, we then must search the entire set of
+according to the same threshold, we must then search the entire set of
 candidate images.
@@
 
-The result of this caching approach is shown in figure
-\ref{fig:caching}. As compared to \ref{fig:directMapping},
+The result of this caching approach is shown in Figure
+\ref{fig:caching}. As compared to Figure \ref{fig:directMapping},
 discontinuities have been reduced overall, but the amount of remaining
@@
 constitutes a good candidate set for generating a final seamless
-texture since it meets three important criteria. First, it contains at least one image that covers each tile on our
-plane; this ensures no holes in our final texture. Second, since
-images are all selected according to the same scoring function in
-Figure \ref{fig:scoringFunction}, they are taken at as much of a head-on angle as possible and should project
-onto the plane in similar ways. Third, as a side result of the scoring
-function, selected images are only good candidates for the tiles near
-their center of projection. Thus, there should be plenty of overlap
-between selected images, allowing for some degree of shifting without
-resulting in holes, as well as area for blending between them. With
-this set of images, we now review two existing approaches towards refining and
+texture since it meets three important criteria. First, each tile on our planeis covered by at least one image in this set; this ensures no
+holes in our final texture. Second, since images are all selected
+according to the same scoring function in Figure
+\ref{fig:scoringFunction}, they are taken at as much of a head-on
+angle as possible and should project onto the plane in similar
+ways. Third, as a side result of the scoring function, selected images
+are only good candidates for the tiles near their center of
+projection. Thus, there should be plenty of overlap between selected
+images, allowing for some degree of shifting without resulting in
+holes, as well as area for blending between them. With this set of
+images, we now review two existing approaches towards refining and
 combining their projections.
@@
   \includegraphics[width=3in]{Graph_crop.pdf}
-  \caption{The graph-based localization refinement algorithm from [11]
+  \caption{The graph-based localization refinement algorithm from \cite{chen2010indoor}
     suffers from the problem of compounding errors. }
@@
 during backpack
-localization\cite{liu2010indoor,chen2010indoor}. Unfortunately, this
-approach suffers from a similar error propagation problem shown in
+localization\cite{liu2010indoor, chen2010indoor}. Unfortunately, this
+approach suffers from a similar error propagation problem as shown in
 Figure \ref{fig:graph}.
 
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{pipeline.pdf}
+  \caption{Our proposed method for seamless texture mapping.}
+  \label{fig:pipeline}
+\end{figure}
 \section{Proposed Method for Seamless Texture Mapping}
 \label{sec:proposedApproach}
-Our proposed approach towards texture mapping is a two-step
-process. First, with the same input set of images as described in
-Section \ref{sec:existingApproaches}, we perform image rotation and
-shifting in order to maximize SIFT feature matches between images. We
-then project these images onto our plane, applying textures either
-with the tile caching method from Section
-\ref{sec:mappingWithCaching}, or with the more specialized method
-described in Section \ref{sec:seamMinimization}.
+In this section, we will describe our proposed method for seamless
+texture mapping. Our approach contains 4 steps, as seen in
+\ref{fig:pipeline}.  First, we obtain a set of images to work with, as
+already described in Section \ref{sec:existingApproaches}. Next, we perform
+image rotation and shifting in order to maximize SIFT feature matches
+in overlapping areas between images. We then project these images onto
+our plane, applying textures either with the tile caching method from
+Section \ref{sec:mappingWithCaching}, or with the more specialized
+method described in Section \ref{sec:seamMinimization}. We then finish
+by applying linear alphar blending to smooth out any remaining seams.
 
@@
 points. Given these distances and the original image location
-estimates, we can solve a least squares problem ($\textrm{min}_{\vec{\beta}}
-||X \vec{\beta} - \vec{\gamma}||_2^2 $) to estimate the correct location of the images
-on the plane. The $M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-and $y$ locations of each image on the plane from $1 \dots M$. The
-optimal $x$ and $y$ locations are obtained in the same way, so we
-only consider the $x$ locations here:
+estimates, we can solve a least squares problem
+($\textrm{min}_{\vec{\beta}} ||X \vec{\beta} - \vec{\gamma}||_2^2 $)
+to estimate the correct location of the images on the plane. The
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$ and
+$y$ locations of each image on the plane from $1 \dots M$. The optimal
+$x$ and $y$ locations are obtained in the same way, so we only
+consider the $x$ locations here:
 
@@
 
-The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row for each pair of images
-with measured distances produced by the SIFT matching stage. A row in
-the matrix has a $-1$ and $1$ in the columns corresponding to the two
-images in the pair. For example, the matrix below indicates that we
-generated a SIFT-based distance between images 1 and 2, images 1 and
-3, images 2 and 3, etc.
+The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row
+for each pair of images with measured distances produced by the SIFT
+matching stage. A row in the matrix has a $-1$ and $1$ in the columns
+corresponding to the two images in the pair. For example, the matrix
+below indicates that we generated a SIFT-based distance between images
+1 and 2, images 1 and 3, images 2 and 3, etc.
 
@@
 
-Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is constructed using the
-SIFT-based distances generated earlier in the matching stage. The
-distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based
-distances. The last element in the observation vector is the location
-of the first image determined by its original noisy localization, from \cite{chen2010indoor, liu2010indoor}:
+Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
+constructed using the SIFT-based distances generated earlier in the
+matching stage. The distances are denoted as $d_1 \dots d_N$ for $N$
+SIFT-based distances. The last element in the observation vector is
+the location of the first image determined by its original noisy
+localization, from \cite{chen2010indoor, liu2010indoor}:
 
@@
 
-The $\vec{\beta}$ that minimizes $||X \vec{\beta} - \vec{\gamma}||_2^2$ results in a set of
-image locations on the plane that best honors all the SIFT-based
-distance measurements between images. In practice there are often
-cases where there is a break in the chain of images, meaning that no
-SIFT matches were found between one segment of the plane and
-another. In this case we add rows to the $X$ matrix and observations
-to the $\vec{\gamma}$ vector that contain the original noisy $x$ and $y$ distance
-estimates generated by the localization algorithm \cite{chen2010indoor, liu2010indoor}. Another way to do
-this is to add rows for all neighboring pairs of images and solve a
-weighted least squares problem where the SIFT distances are given a
-higher weight i.e. 1, and the noisy distances generated by the localization
-algorithm \cite{chen2010indoor, liu2010indoor} are given a smaller weight i.e. 0.01.
+The $\vec{\beta}$ that minimizes $||X \vec{\beta} -
+\vec{\gamma}||_2^2$ results in a set of image locations on the plane
+that best honors all the SIFT-based distance measurements between
+images. In practice there are often cases where there is a break in
+the chain of images, meaning that no SIFT matches were found between
+one segment of the plane and another. In this case we add rows to the
+$X$ matrix and observations to the $\vec{\gamma}$ vector that contain
+the original noisy $x$ and $y$ distance estimates generated by the
+localization algorithm \cite{chen2010indoor, liu2010indoor}. Another
+way to do this is to add rows for all neighboring pairs of images and
+solve a weighted least squares problem where the SIFT distances are
+given a higher weight i.e. 1, and the noisy distances generated by the
+localization algorithm \cite{chen2010indoor, liu2010indoor} are given
+a smaller weight i.e. 0.01.
 
 After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and
-match each other with far greater accuracy.
-Applying the tile caching method from Section \ref{sec:mappingWithCaching} on these re-localized images, results in the significant improvements shown in Figure \ref{fig:shifted}.
+making the resultant shifts, our images overlap and match each other
+with far greater accuracy. Applying the tile caching method from
+Section \ref{sec:mappingWithCaching} on these re-localized images
+results in the significant improvements shown in Figure
+\ref{fig:shifted}, as compared to Figure \ref{fig:caching}.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{highCameraAngle.pdf}
+  \caption{The image on the left projects head-on not only onto point A, but most visible areas of the wall that point A is on.
+The image's projection onto point B will be at a high angle, but it will still be much more usable than the projection onto point C.}
+  \label{fig:highCameraAngle}
+\end{figure}
+
 As mentioned earlier, our backpack system has 2 cameras with
@@
 large areas of floor and ceiling planes. These high camera angles
-translate into images that span extremely large areas once projected
-onto their planes. Such image projections have good scores (from
-Figure \ref{fig:scoringFunction}) for certain areas on the plane, but
-much worse scores for other areas. This can be seen in Figure
+translate into images that span extremely large areas once
+projected. Such image projections have good scores (from Figure
+\ref{fig:scoringFunction}) for certain areas on the plane, but much
+worse scores for other areas. This can be seen in Figure
 \ref{fig:highCameraAngle}. The tiling approach used in Section
@@
 approach used previously only checks occlusion for each tile as it is
-being textured. For our new approach, we use entire images, so we need
+being textured. For our new approach, we prefer entire images, so we need
 to perform occlusion checks over the entirety of each image to
@@
 projections onto the plane are approximately rectangular, as in Figure
-\ref{sec:goodCameraAngle}. By discarding the minor excess texture and
+\ref{fig:highCameraAngle}. By discarding the minor excess texture and
 cropping them all to be rectangular, our problem becomes the
@@
 minimal. We thus also retain the advantages of working with
-rectangular units, as explained in section
+rectangular units, as explained in Section
 \ref{sec:simpleTextureMapping}.
@@
 
-We now solve the shortest path problem from the start node to
-the end node \cite{dijkstra}. This provides a set of images
-completely covering the plane horizontally, while minimizing the cost
-of the seams between images.
+We now solve the shortest path problem from the start node to the end
+node \cite{dijkstra}. This provides a set of images completely
+covering the plane horizontally, while minimizing the cost of the
+seams between images.
 
 In rare cases where the vertical dimension of the plane is not
-entirely covered by a chosen image, we are left with a hole where no
-image is chosen to texture.
-
-SOMETHING HERE ABOUT CRAP CRAP
-
-Rather than reverting to a 2D-coverage problem, we can elect to simply
-fill the hole by selecting images to fill it in a greedy fashion with
-respect to edge costs of the same cost function.
+entirely covered by one or more chosen images, we are left with holes where no
+images are selected to texture.
+Rather than reverting to a 2D-coverage problem, we simply repeat the process, but first modify the edges chosen by our shortest path solution such that they have higher cost than all other edges in our DAG.
+This ensures that these edges will not be chosen again unless they are the only available option.
+After solving the shortest path problem with these modified edge costs, we receive a new set of chosen images, and only retain those that cover areas not covered by the first set.
+This process can be repeated as many times as needed, until holes are no longer present.
+This method is not as optimal as a 2D-coverage solution would be, but it is quick to run and adequately handles the few holes we run into.
 
@@
 provided with head-on images. Floors and ceilings however, given their
-images taken at oblique angles, as shown in Figure \ref{fig:floor_suboptimal}, are textured using the tile caching method.
+many images taken at oblique angles, as shown in Figure
+\ref{fig:highCameraAngle}, are textured using the tile caching
+method.
 
@@
 
-We apply alpha blending to blend pixels
-linearly across overlapping regions. Figure
-\ref{fig:pipeline} shows our entire texture mapping pipeline and demonstrates the
-final blended output of both approaches.
+After blending pixels linearly across overlapping
+regions using alpha blending, our texture mapping is complete.
+Figure \ref{fig:pipelineimages} shows each incremental step of our texture mapping approach, as well as the final blended output resulting from both of our methods.
 
@@
   \centering
-  \includegraphics[width=3in]{pipeline.pdf}
-  \caption{Our final texture processing pipeline, with the final
-    output of both approaches.}
-  \label{fig:pipeline}
+  \includegraphics[width=3in]{pipelineimages.pdf}
+  \caption{Textures corresponding to each step in our texture mapping pipeline.}
+  \label{fig:pipelineimages}
 \end{figure}
@@
   \includegraphics[width=3in]{4thfloor61.jpg}
+  \includegraphics[width=3in]{wall3final.jpg}
   \includegraphics[width=2in]{4thfloor8.jpg}
+  \includegraphics[width=3in]{floorfinal.jpg}
   \includegraphics[width=3in]{fullmodel.png}

### 2012-06-25 3dimpvt/paper.tex
fixed first half, need more refs and waiting for second half

@@
   mapping. Applying textures to these models is an important step in
-  generating photorealistic visualizations of data gathered by
-  modeling systems.  The localization of cameras in such systems often
-  suffer from inaccuracies, resulting in visible discontinuties when
+  generating photorealistic visualizations of data collected by
+  modeling systems.  Camera pose recovery in such systems often
+  suffers from inaccuracies, resulting in visible discontinuties when
   different images are projected adjacently onto a plane for
-  texturing. We propose two approaches for reducing discontinuities
-  during texture mapping, one to robustly accomodate images of all
-  orientations, and one to take advantage of optimal situations where
-  images have uniform orientation. The effectiveness of our approaches
-  will be demonstrated on two indoor datasets.
+  texturing. We propose two approaches for reducing discontinuities in
+  texture mapping 3d models made of planar surfaces. The first one is
+  tile based and can be used where camera axes are at arbitrary angles
+  with respect to the plane normals of the surfaces. The second one
+  results in a more seamless texture but is only applicable where
+  camera axes for imagery are closely aligned with plane normals. The
+  effectiveness of our approaches are demonstrated on two indoor
+  datasets.
 \end{abstract}
@@
 
-The aim of this paper is to present a solution for texture mapping the
-3D models generated by indoor modeling systems, with specific
-attention given to a human-operated system with high camera pose
-errors and great variance in camera locations.
-
 The first step in automated 3D modeling is the physical scanning of
@@
 recover camera poses within an environment while simulatenously
-reconstructing the 3D structure of the environment itself. This is
+reconstructing the 3D structure of the environment itself
+\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}.This is
 known as the simultaneous localization and mapping (SLAM) problem, and
@@
 Mounting such devices on a human-carried platform provides unique
-advantages over vehicular-based systems in terms of agility and
-portability. Unfortunately, human-operated systems also result in much
+advantages over vehicular-based systems on wheels in terms of agility and
+portability, but can also result in much
 larger localization error. As a result, common methods for texture
-mapping generally produce poor results, as later shown in Sections
-\ref{sec:simpleTextureMapping} and
-\ref{sec:existingApproaches}. Before discussing how to overcome these
-challenges, we first provide an overview of the backpack modeling
-system from which our test data has been obtained.
+mapping generally produce poor results.
 
-Our backpack-mounted modeling system contains five 2D laser range
-scanners, two cameras, and an orientation sensor. The laser scanners
-are mounted orthogonally and have a 30-meter range and a 270$^{\circ}$
-field of view. The two cameras are equipped with fisheye lenses,
-reaching an approximately 180$^{\circ}$ field of view, and are mounted
-with one facing left and the other facing right. These cameras take
-images at the rate of 5 Hz. The orientation sensor provides
-orientation parameters at a rate of 180 Hz.
+In this paper, we present a number of approaches to texture mapping 3D models of indoor environments made of planar surfaces in the presence of uncertainty and noise in camera poses.
+In particular, we consider a human-operated backpack system with a number of laser range scanners as well as 2 cameras facing left and right, each equipped with fisheye lenses reaching an approximately 180$^{\circ}$ field of view.
+Considering that the human operator walks at about 1 meter/second, and images are captured at 5 Hz, there is a considerable amount of overlap between successive images.
 
@@
 
-Using data gathered by the onboard sensors and multiple localization
-and loop-closure algorithms, the backpack is then localized over its
-data collection period, and a 3D point cloud of the surrounding
-environment is constructed \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}. Approximate normal vectors for each point in the
+Using data collected by the onboard sensors and applying multiple localization
+and loop-closure algorithms \cite{chen2010indoor, kua2012loopclosure,
+  liu2010indoor}, the backpack is then localized over its
+data collection period.
+This requires recovering the 6 degrees of freedom for the backpack as well as all its sensors, including the cameras mounted on it.
+\footnote{In this paper, we use the terms localization and pose recovery interchangeably, in that they both refer to recovering position and orientation.} Once this is complete, the data from the laser range scanners is used to generate a 3D point cloud of the surrounding environment.
+Approximate normal vectors for each point in the
 point cloud are then calculated by gathering neighboring points within
@@
 of multiple 2D polygonal planes in 3D space, along with the set of
-images captured by the backpack's cameras and their 3D poses, can be
-considered the input to our texture mapping problem
+images captured by the backpack's cameras and their noisy 3D poses,
+can be considered the input to our texture mapping problem.
 
@@
 \ref{sec:simpleTextureMapping} describes the general problem of
-texture mapping and examines two simple mapping approaches and their
+texture mapping and examines two variants of a tile-based mapping approach and their
 shortcomings.  Section \ref{sec:existingApproaches} demonstrates two
-previous attempts at localization refinement, and demonstrates their
+previous attempts at improving texture alignment, and demonstrates their
 inadequacies for our datasets.  Section \ref{sec:proposedApproach}
@@
 
-\section{Simple Texture Mapping}
+In all subsequent sections, we discuss the process of texture mapping
+a single plane, as the texturing of each of our planes is independent
+and can be completed in parallel.
+
+\section{Tile-Based Texture Mapping}
 \label{sec:simpleTextureMapping}
@@
 
-In all subsequent sections, we discuss the process of texture mapping
-a single plane, as the texturing of each of our planes is independent
-and can be completed in parallel.
-
 The geometry of the texture mapping process for a plane is shown in
@@
 translates a 3D point in the world coordinate system to a 2D point or
-pixel in image $i$'s coordinates. If the 3D world point is not
-contained in the image, the 2D point will simply be outside of the
-image boundaries. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, such as focal length and image center, as well
-as extrinsic parameters which specify the rotation and translation of
-the camera's position in 3D world coordinates at the time that image
-$i$ is taken. These extrinsic parameters are determined by the
-backpack hardware and localization algorithms mentioned earlier. A
-point $X$ on the plane in 3D space can be related to its corresponding
-pixel $x$ in image $i$ through the following equation:
+pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
+the camera's intrinsic parameters, such as focal length and image
+center, as well as extrinsic parameters which specify the rotation and
+translation of the camera's position in 3D world coordinates at the
+time that image $i$ is taken. These extrinsic parameters are
+determined by the backpack hardware and localization algorithms
+\cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are quite
+noisy.
 
-\[
-x=project(P_iX)
-\]
-
-where
-\[X = \begin{pmatrix} x \\ y \\ z \end{pmatrix} \textrm{ and }
-project(X) = \begin{pmatrix} x/z \\ y/z \end{pmatrix}
-\]
-
-For the sake of simplicity, we treat all planes as rectangles by
-generating minimum bounding boxes for them. Since our final textures
-are stored as standard rectangular images anyway, we can simply leave
-the area between plane boundary and bounding box untextured, or crop
-it out as needed. A plane to be textured is thus defined by a bounding
-box with corners $C_i$ in world coordinates and a normal vector
-indicating the front facing side of the plane. Our goal is to texture
-this plane using images captured by the backpack system, while
-eliminating any visual discontinuities or seams that would suggest
-that the plane's texture is not composed of a single continuous image.
+Our goal is to texture each plane using images captured by the
+backpack system, while eliminating any visual discontinuities or seams
+that would suggest that the plane's texture is not composed of a
+single continuous image.
 
@@
 ray-polygon intersection tests between the camera location, the center
-of $t$, and other planes, all in world coordinates.
+of $t$, and every other plane, all in world coordinates
+\cite{rayintersection}.
 
@@
 best one. Since camera localization errors compound over distance, we
-wish to minimize the distance between cameras used for texturing and
-our plane. Additionally, we desire images that are projected
+wish to minimize the distance between cameras and the plane they
+texture. Additionally, we desire images that are projected
 perpendicularly onto the plane, maximizing the resolution and amount
-of useful texture available in their projections.
-
-These two criteria can be met by maximizing the function shown in
-Figure \ref{fig:scoringFunction}.
+of useful texture available in their projections. In other words, we
+wish to minimize the angle between the plane normal and the camera
+axis for images selected for texture mapping. These two criteria can
+be met by maximizing the function $\frac{1}{d} (-1 \cdot \vec{C})
+\cdot \vec{N}$ with the parameters shown in Figure
+\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
+the centers of a camera and a tile, and $\vec{N}$ and $\vec{C}$ are
+the directions of the plane's normal and the camera axis respectively.
 
@@
   \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{Images with minimal camera angle $\alpha$ and distance $d$
-    are selected by maximizing the function}
-  \begin{center}$\frac{1}{d} \cdot (-1 \cdot C) \cdot N$ \end{center}
+  \caption{We wish to minimize camera angle $\alpha$ and distance $d$}
   \label{fig:scoringFunction}
@@
   \centering
-  \includegraphics[width=3in]{wall1_naive.jpg}
-  \caption{The result of direct texture mapping based on locally
-    optimized textures.}
-  \label{fig:directMapping}
+  \subfloat[][]{\includegraphics[width=3in]{wall1_naive.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{wall1_cache_full.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{wall1_cache_full_shifted.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{wall1_dynprog_noblend.jpg}}
+  \caption{(a): Direct mapping. (b): Mapping with caching. (c):
+    Mapping with caching after image alignment. (d): Seam minimization approach (including image alignment)}
+  \label{fig:compareAll}
 \end{figure}
 
-As Figure \ref{fig:directMapping} demonstrates, this approach leads to
-the best texture for each tile independently, but overall results in
-many image boundaries with abrupt discontinuities, due to significant
-misalignment between images.
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads
+to the best texture for each tile independently, but overall results
+in many image boundaries with abrupt discontinuities, due to
+significant misalignment between images, as a result of camera pose
+inaccuracies.
 
@@
 \label{sec:mappingWithCaching}
-Since discontinuities occur where adjacent tiles select different
+Since discontinuities occur where adjacent tiles select non-aligned
 images that do not align, it makes sense to take into account image
@@
 for a given tile. By using the same image across tile boundaries, we
-eliminate the discontinuity altogether. If this is not possible
+can eliminate a discontinuity altogether. If this is not possible
 because a tile is not visible in images chosen by its neighbors, using
@@
 must first check which images can map to $t$, and then of those, we
-make a choice according to the same scoring function in
-\ref{fig:scoringFunction}. Rather than blindly reusing this image, we
-ensure it meets a threshold, which we set to $\alpha < 45^\circ$, to
-be considered a good image.
+make a choice according to the same scoring function. Before reusing
+this image, we ensure it meets a threshold, which we set
+unconditionally to $\alpha < 45^\circ$, to be considered a viable
+image, with $\alpha$ as the camera angle as shown in Figure
+\ref{fig:scoringFunction}.
 
-If no satisfactory image is found, we then check our second subset of
-images, which consists of images that were taken near the images in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but they were taken
-at a similar location and time, suggesting that their localization and
-projection are very similar. Again, if no good image is found
-according to the same threshold, we must then search the entire set of
-candidate images.
+If no satisfactory image is found in the first subset, we then check
+our second subset of images, which consists of images that were taken
+near the images in the first subset, both spatially and
+temporally. These images are not the same as the ones used for
+neighboring tiles, but they were taken at a similar location and time,
+suggesting that their localization and projection are very
+similar. Again, if no good image is found according to the same
+threshold, we must then search the entire set of candidate images,
+selecting based on the criteria from Figure \ref{fig:scoringFunction}.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{wall1_cache_full.jpg}
-  \caption{The result of adding a caching system to locally optimized
-    textures.}
-  \label{fig:caching}
-\end{figure}
-
-The result of this caching approach is shown in Figure
-\ref{fig:caching}. As compared to Figure \ref{fig:directMapping},
-discontinuities have been reduced overall, but the amount of remaining
-seams suggests that image selection alone cannot produce seamless
-textures. Camera matrices, or the image projections themselves have to
-be adjusted in order to reliably generate clean textures.
+The results of this caching approach are shown in Figure
+\ref{fig:compareAll}(b). As compared to Figure
+\ref{fig:compareAll}(a), discontinuities are reduced overall, but
+the amount of remaining seams suggests that image selection alone
+cannot produce seamless textures. Camera matrices, or the image
+projections themselves have to be adjusted in order to reliably
+generate clean textures.
 
@@
 In order to produce seamless texture mapping, either camera matrices
-need to be refined such that their localization is pixel accurate,
-resulting in a perfect mapping, or image stitching techniques need to
-be applied to provide this illusion. Before examining these
-approaches, we first obtain a set of images to work with.
+need to be refined such that their localization is pixel accurate, or
+image stitching techniques need to be applied to provide this
+illusion.
 
-Rather than perform camera or image adjustments across the many
-thousands of images acquired in a typical data collection, we opt to
-work with the more limited set of images corresponding to those chosen
-by the direct mapping approach, without caching. This set of images
-constitutes a good candidate set for generating a final seamless
-texture since it meets three important criteria. First, each tile on our planeis covered by at least one image in this set; this ensures no
-holes in our final texture. Second, since images are all selected
-according to the same scoring function in Figure
-\ref{fig:scoringFunction}, they are taken at as much of a head-on
-angle as possible and should project onto the plane in similar
-ways. Third, as a side result of the scoring function, selected images
-are only good candidates for the tiles near their center of
-projection. Thus, there should be plenty of overlap between selected
-images, allowing for some degree of shifting without resulting in
-holes, as well as area for blending between them. With this set of
-images, we now review two existing approaches towards refining and
-combining their projections.
+Before examining these approaches, we first obtain a set of images to
+work with.  Rather than perform camera or image adjustments across the
+many thousands of images acquired in a typical data collection, we opt
+to work with the more limited set of images corresponding to those
+chosen by the direct mapping approach, without caching (Section
+\ref{sec:directMapping}. This set of images constitutes a good
+candidate set for generating a final seamless texture since it meets
+three important criteria. First, each tile on our planeis covered by
+at least one image in this set; this ensures no holes in our final
+texture. Second, images are all selected according to the scoring
+function in Figure \ref{fig:scoringFunction}, ensuring good camera
+distances and angles. Third, as a side result of the scoring function,
+selected images are only viable candidates for the tiles near their
+center of projection. Thus, there should be plenty of overlap between
+selected images, allowing for some degree of shifting without
+resulting in holes, as well as area for blending between them. With
+this set of images, we now review two existing approaches towards
+refining and combining their projections.
 
@@
 \label{sec:imageMosaicing}
+
 \begin{figure}
   \centering
-  \includegraphics[width=3in]{panoMy.jpg}
-  \caption{Image mosaicing. }
-  \label{fig:mosaic}
+  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
+  \caption{Both image mosaicing (a) and the graph-based localization refinement algorithm from
+    \cite{chen2010indoor} (b) suffer from the problem of compounding
+    errors.}
+  \label{fig:mosaic3D}
 \end{figure}
@@
 
-Figure \ref{fig:mosaic} shows the output of the AutoStitch software
+Figure \ref{fig:mosaic3D}(a) shows the output of the AutoStitch software
 package which does homography-based image mosaicing. This plane is
@@
 it. Even so, the mosaicing produces errors that causes straight lines
-to appear as waves on the plane. This image was generated after
-careful hand tuning as well. Many planes that had fewer features
+to appear as waves on the plane, despite the fact that it was
+generated after careful hand tuning. Many planes with fewer features
 simply failed outright. Thus, image mosaicing is not a robust enough
@@
 \label{sec:imageBased3DRefinement}
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{Graph_crop.pdf}
-  \caption{The graph-based localization refinement algorithm from \cite{chen2010indoor}
-    suffers from the problem of compounding errors. }
-  \label{fig:graph}
-\end{figure}
 
@@
 the backpack system which generated our dataset, as it must be run
-during backpack
-localization\cite{liu2010indoor, chen2010indoor}. Unfortunately, this
-approach suffers from a similar error propagation problem as shown in
-Figure \ref{fig:graph}.
+during backpack localization\cite{liu2010indoor,
+  chen2010indoor}. This approach suffers from a similar
+error propagation problem as shown in Figure \ref{fig:mosaic3D}(b).
 
@@
 \end{figure}
+
 \section{Proposed Method for Seamless Texture Mapping}
@@
 In this section, we will describe our proposed method for seamless
-texture mapping. Our approach contains 4 steps, as seen in
-\ref{fig:pipeline}.  First, we obtain a set of images to work with, as
-already described in Section \ref{sec:existingApproaches}. Next, we perform
-image rotation and shifting in order to maximize SIFT feature matches
-in overlapping areas between images. We then project these images onto
-our plane, applying textures either with the tile caching method from
-Section \ref{sec:mappingWithCaching}, or with the more specialized
-method described in Section \ref{sec:seamMinimization}. We then finish
-by applying linear alphar blending to smooth out any remaining seams.
+texture mapping. Our approach consists of 4 steps, as seen in Figure
+\ref{fig:pipeline}.  First, we choose a subset of $M$ images to work
+with via the direct mapping approach of Section
+\ref{sec:directMapping}. Next, we perform image rotation and shifting
+in order to maximize SIFT feature matches in overlapping areas between
+images. We then project these images onto our plane, applying textures
+either with the tile caching method from Section
+\ref{sec:mappingWithCaching}, or with the more specialized method to
+be described in Section \ref{sec:seamMinimization}. This choice
+depends on the availability of head-on images for a given plane. We
+then finish by applying linear alphar blending to smooth out any
+remaining seams.
 
@@
 \label{sec:projectionAndRotation}
-Our localization approach begins with the projection of all our images
-onto separate copies of our plane, such that no projected data is
-covered up and lost. This is done in the same way as the approaches in
-Section \ref{sec:simpleTextureMapping}. We then perform rotations on
-these projections, as adjacent images with different orientations will
-result in strong discontinuities.
+We begin with the projection of all images onto the plane. This is
+done in the same way as the approaches in Section
+\ref{sec:simpleTextureMapping}. We then perform rotations on these
+projections, as adjacent images with different orientations result in
+strong discontinuities.
 
@@
 image, we simply apply rotations such that the strongest near-vertical
-features are made completely vertical. This is effective for indoor
-models, since strong features in indoor scenes usually consist of
-parallel vertical lines corresponding to doors, wall panels,
-rectangular frames, etc. If features in the environment are not
-vertical, or are not parallel to eachother, this step is skipped.
+features are made completely vertical. This is effective for vertical
+planes in indoor models, since they usually consist of parallel
+vertical lines corresponding to doors, wall panels, rectangular
+frames, etc. If features in the environment are not vertical, or are
+not parallel to eachother, this step is skipped.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{matches.jpg}
-  \caption{SIFT feature matches between overlapping images.}
-  \label{fig:matches}
-\end{figure}
-
-\subsection{Robust SIFT Feature Matching using RANSAC}
+\subsection{Image Pose Refinement}
 \label{sec:robustSIFTFeatureMatching}
-Our next step is to fix misalignment between overlapping images. We do
-this by first searching for corresponding points between all pairs of
-overlapping images using SIFT feature matching
-\cite{lowe1999object}. An illustration of this is given in Figure
-\ref{fig:matches}. The SIFT matches allow us to determine $dx$ and
-$dy$ distances between each pair of features for two images on the
-plane, determining where they should be projected relative to
-eachother.
+Our next step is to align overlapping images by searching for
+corresponding points between all pairs of overlapping images using
+SIFT feature matching \cite{lowe1999object}. The SIFT matches
+determine $dx$ and $dy$ distances between each pair of features for
+two images on the plane, though these distances may not always be the
+same for different features.
 
@@
 consider the $x$ locations here:
-
-% Draw least squares problem here.
 
@@
 results in the significant improvements shown in Figure
-\ref{fig:shifted}, as compared to Figure \ref{fig:caching}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
-  \caption{Localization refinement results in signifcantly fewer
-    discontinuities in the final texture.}
-  \label{fig:shifted}
-\end{figure}
+\ref{fig:compareAll}(c), as compared to Figure \ref{fig:compareAll}(d).
 
@@
   \includegraphics[width=3in]{highCameraAngle.pdf}
-  \caption{The image on the left projects head-on not only onto point A, but most visible areas of the wall that point A is on.
-The image's projection onto point B will be at a high angle, but it will still be much more usable than the projection onto point C.}
+  \caption{(1) projects perpendicularly onto a wall and provides
+    uniformly high resolution textures over its entire projection
+    (2). (3) on the other hand projects at a poor angle onto the
+    ceiling (4), resulting in usable texture at point A, but
+    increasingly low resolution texture towards point B.}
   \label{fig:highCameraAngle}
@@
 as it allowed us to only use the parts of image projections that were
-good choices for their respective plane locations.
+good choices for their respective plane locations, e.g. areas near
+point A in Figure \ref{fig:highCameraAngle}, but not near point B.
 
 For wall planes however, we have images all taken from close distances
-and more head-on angles, and thus much smaller near-rectangular
+and more head-on angles, and thus higher resolution, near-rectangular
 projections to work with. As a result, there is less deviation over
@@
 
-\subsection{Occlusion Masking}
+\subsubsection{Occlusion Masking}
 \label{sec:occlusionMasking}
@@
 approach used previously only checks occlusion for each tile as it is
-being textured. For our new approach, we prefer entire images, so we need
-to perform occlusion checks over the entirety of each image to
+being textured. For our new approach, we prefer entire images, so we
+need to perform occlusion checks over the entirety of each image to
 determine available areas for texture mapping.
@@
 
-\subsection{Image Selection}
+\subsubsection{Image Selection}
 \label{sec:imageSelection}
@@
 this is the sum of squared pixel differences in overlapping regions
-between all pairs of images after they have been aligned as described
+between all pairs of images, after they have been aligned as described
 in Section \ref{sec:projectionAndRotation}. Minimizing this cost
@@
 for which the overall cost function is minimized. Since nearly all the
-images for our optimal case are head on, the best strategy to minimize
-seams is to choose as few images as possible while texturing a given
-plane. Thus,to cover the entirety of a plane, our problem can be
-defined as minimally covering a polygon i.e. the plane, using other
+images for these optimal cases are head on, the best strategy to
+minimize seams is to choose as few images as possible while texturing
+a given plane. Thus,to cover the entirety of a plane, our problem can
+be defined as minimally covering a polygon i.e. the plane, using other
 polygons of arbitrary geometry i.e. our image projections, with the
@@
 projections onto the plane are approximately rectangular, as in Figure
-\ref{fig:highCameraAngle}. By discarding the minor excess texture and
-cropping them all to be rectangular, our problem becomes the
-conceptually simpler one of filling a polygon with rectangles, such
-that the sum of all edge costs between each pair of rectangles is
-minimal. We thus also retain the advantages of working with
-rectangular units, as explained in Section
+\ref{fig:highCameraAngle}. By cropping them all to be rectangular, our
+problem becomes the conceptually simpler one of filling a polygon with
+rectangles, such that the sum of all edge costs between each pair of
+rectangles is minimal. We thus also retain the advantages of working
+with rectangular units, as explained in Section
 \ref{sec:simpleTextureMapping}.
@@
 ceiling range of wall planes. Images are therefore rarely projected
-with one above the other when texturing wall planes, which correspond
-to the optimal planes we are working with.  In essence, we need only
-to ensure horizontal coverage of our planes, as our images provide
-full vertical coverage themselves. We can thus construct a Directed
-Acyclic Graph (DAG) from the images, with edge costs defined by our
-cost function above, and solve a simple shortest path problem to find
-an optimal subset of images with regard to the cost functions.
+with one above another when texturing wall planes, which correspond to
+the optimal case we are working with.  In essence, we need only to
+ensure horizontal coverage of our planes, as our images provide full
+vertical coverage themselves. We can thus construct a Directed Acyclic
+Graph (DAG) from the images, with edge costs defined by our cost
+function above, and solve a simple shortest path problem to find an
+optimal subset of images with regard to the cost functions
+\cite{dijkstra}.
 
@@
 We now solve the shortest path problem from the start node to the end
-node \cite{dijkstra}. This provides a set of images completely
-covering the plane horizontally, while minimizing the cost of the
-seams between images.
+node. This provides a set of images completely covering the plane
+horizontally, while minimizing the cost of seams between images.
 
 In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes where no
-images are selected to texture.
-Rather than reverting to a 2D-coverage problem, we simply repeat the process, but first modify the edges chosen by our shortest path solution such that they have higher cost than all other edges in our DAG.
-This ensures that these edges will not be chosen again unless they are the only available option.
-After solving the shortest path problem with these modified edge costs, we receive a new set of chosen images, and only retain those that cover areas not covered by the first set.
-This process can be repeated as many times as needed, until holes are no longer present.
-This method is not as optimal as a 2D-coverage solution would be, but it is quick to run and adequately handles the few holes we run into.
+entirely covered by one or more chosen images, we are left with holes
+where no images are selected to texture. To address this, we simply
+modify the edges chosen by our shortest path solution such that they
+have higher cost than all other edges in our DAG, and solve for a new
+shortest path. This ensures that these edges will not be chosen again
+unless they are the only available option. Our second shortest path
+solution will result in a new set of chosen images, of which we only
+retain those that cover areas not covered by the first set. This
+process can be repeated as many times as needed, until holes are no
+longer present. This method is not as optimal as a 2D-coverage
+solution would be, but it is a quick approximation, and adequately
+handles the few holes we run into.
 
@@
 at least one image, and have minimized the number of images, as well
-as the discontinuity between their borders. In the next section, we
+as the discontinuities between their borders. In the next section, we
 apply blending between images where they overlap, but for the sake of
@@
 \ref{sec:mappingWithCaching}, we arbitrarily choose one image for
-texturing where images overlap. Figure \ref{fig:compare_unblended}
-compares the tile caching method against this seam minimization
+texturing where images overlap. Figures \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d)
+compare the tile caching method against this seam minimization
 method.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
-  \includegraphics[width=3in]{wall1_dynprog_noblend.jpg}
-  \caption{The tile caching approach is presented above the seam
-    minimization approach.}
-  \label{fig:compare_unblended}
-\end{figure}
 
@@
 caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed.
+choices once subsequent tiles have been processed. The seam minimization approach is also less intensive in terms of memory usage and runtime, as it does not require discretizing planes or images.
 
@@
 many images taken at oblique angles, as shown in Figure
-\ref{fig:highCameraAngle}, are textured using the tile caching
-method.
+\ref{fig:highCameraAngle}, are textured using the tile caching method.
 
@@
 localization refinement followed by either tile caching or seam
-minimization.
+minimization for texturing.
 
 Although our preprocessing steps and image selections in either method
-attempt to minimize all mismatches between images, there are
-unavoidable discontinuities due to different lighting conditions or
-inaccuracies in planar geometry or projection. These can however be
-treated and smoothed over by applying alpha blending over image seams.
-Whether the units we are blending are rectangularly-cropped images or
-rectangular tiles, we can apply the same blending procedure, as long
-as we have a guaranteed overlap between units to blend over.
+attempt to minimize all mismatches between images, there are sometimes
+unavoidable discontinuities in our final texture due to different
+lighting conditions or inaccuracies in planar geometry or
+projection. These can however be treated and smoothed over by applying
+alpha blending over image seams.  Whether the units we are blending
+are rectangularly-cropped images or rectangular tiles, we can apply
+the same blending procedure, as long as we have a guaranteed overlap
+between units to blend over.
 
@@
 already ensured overlap between images. To enforce consistent blending
-however, it is beneficial to add a minimuum required overlap distance
-while solving the shortest path problem in Section
-\ref{sec:imageSelection}. If images overlap in a region greater than
-the overlap distance, we only apply blending over an area equal to the
-overlap distance.
+however, we add a minimuum required overlap distance while solving the
+shortest path problem in Section
+\ref{sec:imageSelection}. Additionally, if images overlap in a region
+greater than the overlap distance, we only apply blending over an area
+equal to the overlap distance.
 
-After blending pixels linearly across overlapping
-regions using alpha blending, our texture mapping is complete.
-Figure \ref{fig:pipelineimages} shows each incremental step of our texture mapping approach, as well as the final blended output resulting from both of our methods.
+After blending pixels linearly across overlapping regions using alpha
+blending, our texture mapping is complete. Figure
+\ref{fig:pipelineimages} shows each incremental step of our texture
+mapping approach, as well as the final blended output resulting from
+both of our methods.
 
@@
   \includegraphics[width=3in]{pipelineimages.pdf}
-  \caption{Textures corresponding to each step in our texture mapping pipeline.}
+  \caption{Textures corresponding to each step in our texture mapping
+    pipeline.}
   \label{fig:pipelineimages}
@@
 \label{sec:resultsAndConclusions}
-In this paper, we have developed an approach to texture map models with noisy camera localization data. We are
-able to refine image locations based on feature matching, and robustly
-handle outliers.  We generalized one approach to texture mapping to
-any manner of planes and images, and successfully textured both simple
-rectangular walls as well as complex floor and ceiling geometry. We
-also presented an optimized texturing method that takes advantage of
-our localization refinement process and produces more seamless textures on
-planes where multiple head-on images are available. Each of these
-approaches is highly modular, and easily tunable for different
-environments and acquisition hardware.
+In this paper, we have developed an approach to texture map models
+with noisy camera localization data. We are able to refine image
+locations based on feature matching, and robustly handle outliers.  We
+generalized one texture mapping approach to any manner of planes and
+images, and successfully textured both simple rectangular walls as
+well as complex floor and ceiling geometry. We also presented an
+optimized texturing method that takes advantage of our localization
+refinement process and produces more seamless textures on planes where
+multiple head-on images are available. Each of these approaches is
+highly modular, and easily tunable for different environments and
+acquisition hardware.
 
@@
 textured with the seam minimization approach, are displayed in Figure
-\ref{fig:results}. A more detailed walkthrough demonstrating fully
-textured 3D models using the approaches in this paper is available in
-the accompanying video to this paper.
+\ref{fig:results}. High resolution texture comparisons, as well as a
+walkthrough of a fully textured 3D model are available in the
+accompanying video to this paper.
 
@@
   \includegraphics[width=3in]{wall3final.jpg}
-  \includegraphics[width=2in]{4thfloor8.jpg}
-  \includegraphics[width=3in]{floorfinal.jpg}
+  \includegraphics[width=3in]{4thfloor8.jpg}
+  \includegraphics[width=3in]{floorcropped.jpg}
   \includegraphics[width=3in]{fullmodel.png}
-  \caption{Examples of our final texture mapping output for walls,
-    floors, and ceilings}
+  \caption{Examples of our final texture mapping output for walls, a
+    ceiling, an entire floor, as well as a fully textured model}
   \label{fig:results}

### 2012-06-25 3dimpvt/paper.tex
progress

@@
 outliers, the RANSAC framework \cite{fischler1981random} is used for a
-robust estimate of the optimal $dx$ and $dy$ distances between two
-images. The RANSAC framework handles the consensus-building machinery,
+robust estimate of the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
+images $i$ and $j$. The RANSAC framework handles the consensus-building machinery,
 and requires a fitting function and a distance function. For this
 application, the fitting function simply finds the average distance
-between matches in a pair of images. Our distance function for a pair
-of points is the difference between those points' SIFT match distance
+between matches in a pair of images. The distance function for a pair
+of points is chosen to be the difference between those points' SIFT match distance
 and the average distance computed by the fitting function; we use a 10
@@
 
-\subsubsection{Refining Image Positions using Least Squares}
-\label{sec:refiningImagePositions}
-There are a total of $M^{2}$ possible pairs of images, though we only
+We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair of images to refine their positions using least squares.
+Recall that there are a total of $M^{2}$ possible pairs of images, though we only
 generate distances between images that overlap at SIFT feature
@@
 estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||X \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the correct location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$ and
-$y$ locations of each image on the plane from $1 \dots M$. The optimal
+($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
+to estimate the location of the images on the plane. The
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$ location of each image on the plane for $1 \dots M$. The optimal
 $x$ and $y$ locations are obtained in the same way, so we only
@@
 
-The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row
+The $N \times (M+1)$ dimensional matrix $A$ is constructed with one row
 for each pair of images with measured distances produced by the SIFT
@@
 \[
-X =
+A =
 \begin{pmatrix}
@@
 constructed using the SIFT-based distances generated earlier in the
-matching stage. The distances are denoted as $d_1 \dots d_N$ for $N$
-SIFT-based distances. The last element in the observation vector is
+RANSAC matching stage. The last element in the observation vector is
 the location of the first image determined by its original noisy
-localization, from \cite{chen2010indoor, liu2010indoor}:
+localization, from \cite{chen2010indoor, liu2010indoor}. Thus $\vec{\gamma}$ can be written as:
 
 \[
-\vec{y}^T =
+\vec{\gamma}^T =
 \begin{pmatrix}
@@
 one segment of the plane and another. In this case we add rows to the
-$X$ matrix and observations to the $\vec{\gamma}$ vector that contain
+$A$ matrix and observations to the $\vec{\gamma}$ vector that contain
 the original noisy $x$ and $y$ distance estimates generated by the
@@
 results in the significant improvements shown in Figure
-\ref{fig:compareAll}(c), as compared to Figure \ref{fig:compareAll}(d).
+\ref{fig:compareAll}(c), as compared to Figure \ref{fig:compareAll}(b).
 
-\subsection{Texture Mapping with Seam Minimization}
+\subsection{Seam Minimization}
 \label{sec:seamMinimization}
@@
   \centering
-  \includegraphics[width=3in]{highCameraAngle.pdf}
-  \caption{(1) projects perpendicularly onto a wall and provides
-    uniformly high resolution textures over its entire projection
-    (2). (3) on the other hand projects at a poor angle onto the
-    ceiling (4), resulting in usable texture at point A, but
-    increasingly low resolution texture towards point B.}
-  \label{fig:highCameraAngle}
+  \subfloat[][]{\includegraphics[width=3in]{projectionWall.jpg}}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{projectionCeiling.jpg}}
+  \caption{(a): Undistorted fisheye images for vertical planes such as
+    walls are tilted, but their effective camera axis is more or less
+    normal to the plane. (b): The effective camera axis for ceilings
+    is at an angle with respect to the plane normal.}
+  \label{fig:projectionAngles}
 \end{figure}
 
-As mentioned earlier, our backpack system has 2 cameras with
-$180^\circ$ fisheye lenses facing to the right and left. Since the
-backpack operator only takes care to fully scan each wall and not
-necessarily the entirety of each ceiling and floor, cameras at higher
-angles with respect to plane normal vectors must be used for texturing
-large areas of floor and ceiling planes. These high camera angles
-translate into images that span extremely large areas once
-projected. Such image projections have good scores (from Figure
-\ref{fig:scoringFunction}) for certain areas on the plane, but much
-worse scores for other areas. This can be seen in Figure
-\ref{fig:highCameraAngle}. The tiling approach used in Section
-\ref{sec:simpleTextureMapping} was thus a good choice for texturing,
-as it allowed us to only use the parts of image projections that were
-good choices for their respective plane locations, e.g. areas near
-point A in Figure \ref{fig:highCameraAngle}, but not near point B.
+As mentioned earlier, the mobile backpack system used to capture data
+in this paper contains 2 cameras with $180^\circ$ fisheye lenses
+facing to the right and left. Since most human operators do not carry
+the backpack in a perfectly upright position and are bent forwards at
+15 to 20 degrees with respect to the vertical direction, the
+undistorted fisheye images are head on with respect to vertical walls,
+but at an angle with respect to horizontal floors and ceilings. This
+is depicted in Figure \ref{fig:projectionAngles}.
 
-For wall planes however, we have images all taken from close distances
-and more head-on angles, and thus higher resolution, near-rectangular
-projections to work with. As a result, there is less deviation over
-the score of each tile within an image, as well as over the average
-scores of all images. This means that the scoring criteria from Figure
-\ref{fig:scoringFunction} is less relevant to walls, which enjoy an
-abundance of head-on images.
+These oblique camera angles translate into textures that span
+extremely large areas once projected. Using the tile-based texture
+mapping criteria from Figure \ref{fig:scoringFunction}, such
+projections have good scores for certain areas on the plane, but worse
+scores for others. The tiling approach in Section
+\ref{sec:simpleTextureMapping} is thus a good choice for texturing
+floors and ceilings, as it uses the parts of image projections that
+are good choices for their respective plane locations, e.g. areas near
+point A in Figure \ref{fig:projectionAngles}(b), but not near point B.
 
-Thus, for planes with optimal images, rather than selecting the set of
-best images, since all images are near in quality, we instead select
-the best set of images, such that the selection together results in
-the cleanest final texture. We will accomplish this by using entire
-images where possible, and defining a cost function to minimize the
-visibility of seams in our final texture.
+For wall planes however, most images are taken from close distances
+and more or less head-on angles, resulting in higher resolution
+fronto-parallel projections. As a result, for each tile on a wall
+plane, the cost function of Figure \ref{fig:scoringFunction} is
+relatively flat with respect to a large number of captured images, as
+they are all more or less head on. Thus it is conceivable to use a
+different texturing strategy for walls so as to minimize the visible
+seams for texture mapped planes. One way to do so is to choose the
+smallest possible set of images that (a) covers the entire plane and
+(b) minimizes the amount of visible seams. A straigntforward cost
+function that accomplishes the latter is the sum of squared pixel
+differences in overlapping regions between all pairs of images, after
+they have been aligned as described in Section
+\ref{sec:projectionAndRotation}. Minimizing this cost function, which
+we refer to as SSD, encourages image boundaries to occur either in
+featureless areas, such as bare walls, or in areas where images match
+extremely well.
 
-\subsubsection{Occlusion Masking}
-\label{sec:occlusionMasking}
-To begin with, we need to ensure that our images contain only content
-that should be mapped onto the target plane in question. The tiling
-approach used previously only checks occlusion for each tile as it is
-being textured. For our new approach, we prefer entire images, so we
-need to perform occlusion checks over the entirety of each image to
-determine available areas for texture mapping.
-
-Fortunately, by virtue of our indoor environments, the vast majority
-of surface geometry is either horizontal or vertical, with high
-amounts of right angles. This means that after masking out occluded
-areas, our image projections will remain largely rectangular. We can
-thus be efficient by recursively splitting each image into rectangular
-pieces, and performing the same occlusion checks used in the tiling
-process where needed. To actually occlude out rectangles, we simply
-remove their texture, as we will ensure that untextured areas are
-never chosen for texture mapping.
-
-\subsubsection{Image Selection}
-\label{sec:imageSelection}
-To determine the set of images that results in the cleanest texture,
-we need a cost function to evaluate the visibiilty of seams between
-images in our set. A straightforward cost function that accomplishes
-this is the sum of squared pixel differences in overlapping regions
-between all pairs of images, after they have been aligned as described
-in Section \ref{sec:projectionAndRotation}. Minimizing this cost
-function encourages image boundaries to occur either in featureless
-areas, such as bare walls, or in areas where images match extremely
-well.
-
-With the cost function defined, we must now select the set of images
-for which the overall cost function is minimized. Since nearly all the
-images for these optimal cases are head on, the best strategy to
-minimize seams is to choose as few images as possible while texturing
-a given plane. Thus,to cover the entirety of a plane, our problem can
-be defined as minimally covering a polygon i.e. the plane, using other
-polygons of arbitrary geometry i.e. our image projections, with the
-added constraint of minimizing our cost function between chosen
-images.  This is a complex problem, though we can take a number of
-steps to simplify it. Given that our wall-texture candidate images are
-all taken from a head-on angle, and assuming only minor rotations are
-made during localization refinement, we can reason that their
-projections onto the plane are approximately rectangular, as in Figure
-\ref{fig:highCameraAngle}. By cropping them all to be rectangular, our
+To cover the entirety of a plane, our problem can be defined as
+minimally covering a polygon i.e. the plane, using other polygons of
+arbitrary geometry i.e. image projections, with the added constraint
+of minimizing the cost function between chosen images.  This is a
+complex problem, though we can take a number of steps to simplify
+it. Given that wall-texture candidate images are taken from more or
+less head-on angles, and assuming only minor rotations are made during
+localization refinement, we can reason that their projections onto the
+plane are approximately rectangular. By cropping them all to be
+rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
 problem becomes the conceptually simpler one of filling a polygon with
-rectangles, such that the sum of all edge costs between each pair of
+rectangles, such that the sum of all costs between each pair of
 rectangles is minimal. We thus also retain the advantages of working
@@
 
-The location and orientation of the cameras on our backpack is such
-that our images nearly always contain the entirety of the floor to
-ceiling range of wall planes. Images are therefore rarely projected
-with one above another when texturing wall planes, which correspond to
-the optimal case we are working with.  In essence, we need only to
-ensure horizontal coverage of our planes, as our images provide full
-vertical coverage themselves. We can thus construct a Directed Acyclic
-Graph (DAG) from the images, with edge costs defined by our cost
-function above, and solve a simple shortest path problem to find an
-optimal subset of images with regard to the cost functions
-\cite{dijkstra}.
+The location and orientation of the cameras on the acquisition
+backpack is such that images nearly always contain the entirety of the
+floor to ceiling range of wall planes. Images are therefore rarely
+projected with one above another when texturing wall planes. In
+essence, we need only to ensure horizontal coverage of wall planes, as
+our images provide full vertical coverage themselves. We can thus
+construct a Directed Acyclic Graph (DAG) from the images, with edge
+costs defined by the SSD cost function, and solve a simple shortest
+path problem to find an optimal subset of images with regard to the
+cost function \cite{dijkstra}.
 
@@
 between images that overlap. The weights of these edges are determined
-by the cost functions discussed previously. Next, we add two
+by the SSD cost function. Next, we add two
 artificial nodes, one start node representing the left border of the
@@
 entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. To address this, we simply
-modify the edges chosen by our shortest path solution such that they
+where no images are selected to texture. To address this, we solve for a new shortest path after modifying the edges chosen by the original shortest path solution such that they
 have higher cost than all other edges in our DAG, and solve for a new
-shortest path. This ensures that these edges will not be chosen again
+shortest path. This ensures that these edges are not chosen again
 unless they are the only available option. Our second shortest path
-solution will result in a new set of chosen images, of which we only
+solution results in a new set of chosen images, of which we only
 retain those that cover areas not covered by the first set. This
@@
 longer present. This method is not as optimal as a 2D-coverage
-solution would be, but it is a quick approximation, and adequately
-handles the few holes we run into.
+solution would be, but it is a fast approximation, and adequately
+handles the few holes we encounter.
 
-With this completed, we have now mapped every location on our plane to
+With this completed, we have now mapped every location on the plane to
 at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. In the next section, we
-apply blending between images where they overlap, but for the sake of
-comparison with the unblended tile caching method in Section
-\ref{sec:mappingWithCaching}, we arbitrarily choose one image for
-texturing where images overlap. Figures \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d)
-compare the tile caching method against this seam minimization
-method.
-
-Though both methods provide quite accurate texturing thanks to the
-alignment process, the seam minimization approach results in fewer
+as the discontinuities between their borders. Figures \ref{fig:compareAll}(c) and
+\ref{fig:compareAll}(d) compare the tile caching method against this
+seam minimization method.
+For the latter, we arbitrarily choose one image for texturing where images overlap.
+Though both methods provide aligned texturing, the seam minimization approach results in fewer
 visible discontinuities, since it directly reduces the cost of each
@@
 caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. The seam minimization approach is also less intensive in terms of memory usage and runtime, as it does not require discretizing planes or images.
+choices once subsequent tiles have been processed. The seam
+minimization approach is also less intensive in terms of memory usage
+and runtime, as it does not require discretizing planes or images.
 
-In the context of the backpack modeling system, we apply the seam
+In the context of texturing an entire 3D planar model, we apply the seam
 minimization approach on walls, due to its superior output when
 provided with head-on images. Floors and ceilings however, given their
-many images taken at oblique angles, as shown in Figure
-\ref{fig:highCameraAngle}, are textured using the tile caching method.
+many images taken at oblique angles, are textured using the tile caching method.
 
@@
 \label{sec:blending}
-We now apply the same blending process on our two texturing methods:
+We now apply the same blending process to the two texturing methods:
 localization refinement followed by either tile caching or seam
-minimization for texturing.
+minimization.
 
-Although our preprocessing steps and image selections in either method
-attempt to minimize all mismatches between images, there are sometimes
-unavoidable discontinuities in our final texture due to different
+Although the preprocessing steps and image selection in both methods
+attempt to minimize all mismatches between images, there are occasional
+unavoidable discontinuities in the final texture due to different
 lighting conditions or inaccuracies in planar geometry or
@@
 shortest path problem in Section
-\ref{sec:imageSelection}. Additionally, if images overlap in a region
+\ref{sec:seamMinimization}. Additionally, if images overlap in a region
 greater than the overlap distance, we only apply blending over an area
@@
 After blending pixels linearly across overlapping regions using alpha
-blending, our texture mapping is complete. Figure
+blending, texture mapping is complete. Figure
 \ref{fig:pipelineimages} shows each incremental step of our texture
-mapping approach, as well as the final blended output resulting from
+mapping approach for a different wall, as well as the final blended output resulting from
 both of our methods.
@@
 with noisy camera localization data. We are able to refine image
-locations based on feature matching, and robustly handle outliers.  We
-generalized one texture mapping approach to any manner of planes and
-images, and successfully textured both simple rectangular walls as
-well as complex floor and ceiling geometry. We also presented an
-optimized texturing method that takes advantage of our localization
-refinement process and produces more seamless textures on planes where
+locations based on feature matching, and robustly handle outliers. The tile-based mapping approach can be used to texture both simple rectangular walls as
+well as complex floor and ceiling geometry. We also presented a seam minimization texturing method that produces seamless textures on planes where
 multiple head-on images are available. Each of these approaches is
@@
 
-Ceilings and floors textured with the tile caching approach, and walls
+Examples of ceilings and floors textured with the tile caching approach, and walls
 textured with the seam minimization approach, are displayed in Figure

### 2012-06-25 3dimpvt/paper.tex
nearly finished draft 4

@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{projectionWall.jpg}}
+  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{projectionCeiling.jpg}}
-  \caption{(a): Undistorted fisheye images for vertical planes such as
-    walls are tilted, but their effective camera axis is more or less
+  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
+  \caption{(a): Undistorted fisheye images for vertical planes are tilted, but their effective camera axis is more or less
     normal to the plane. (b): The effective camera axis for ceilings
-    is at an angle with respect to the plane normal.}
+    is at an angle with respect to the plane normal. (c): Wall images are cropped to be rectangular.}
   \label{fig:projectionAngles}
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=6in]{pipelineimages.pdf}
+  \caption{Textures corresponding to each step in our texture mapping
+    pipeline.}
+  \label{fig:pipelineimages}
+\end{figure*}
+
 \subsection{Blending}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{pipelineimages.pdf}
-  \caption{Textures corresponding to each step in our texture mapping
-    pipeline.}
-  \label{fig:pipelineimages}
-\end{figure}
-
 \section{Results and Conclusions}
@@
   \centering
-  \includegraphics[width=3in]{4thfloor21.jpg}
-  \includegraphics[width=3in]{4thfloor61.jpg}
-  \includegraphics[width=3in]{wall3final.jpg}
-  \includegraphics[width=3in]{4thfloor8.jpg}
-  \includegraphics[width=3in]{floorcropped.jpg}
-  \includegraphics[width=3in]{fullmodel.png}
-  \caption{Examples of our final texture mapping output for walls, a
-    ceiling, an entire floor, as well as a fully textured model}
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{4thfloor8.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{floorcropped.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
+  \caption{Examples of our final texture mapping output for (a) walls, (b) a
+    ceiling, (c) an entire floor, (d) a full model}
   \label{fig:results}
@@
 
+\appendix
+\section{Occlusion Masking}
+\label{sec:occlusionMasking}
+For the seam minimization process, we need to ensure that our images contain only content
+that should be mapped onto the target plane in question. The tiling
+approach only checks occlusion for each tile as it is
+being textured. For seam minimization, entire images are used, so occlusion checks need to be performed over the entirety of each image to
+determine available areas for texture mapping.
+
+Fortunately, by virtue of our indoor environments, the vast majority
+of surface geometry is either horizontal or vertical, with high
+amounts of right angles. This means that after masking out occluded
+areas, image projections will remain largely rectangular. We can
+be efficient by recursively splitting each image into rectangular
+pieces, and performing the same occlusion checks used in the tiling
+process where needed. To occlude out rectangles, their texture is removed, as untextured areas are
+never used for texture mapping.
+
 \end{document}

### 2012-06-25 3dimpvt/_region_.tex
completed v2 changes
fixed first half, need more refs and waiting for second half
next draft

--- 2012-06-19 3dimpvt/_region_.tex
@@
 
-\message{ !name(paper.tex) !offset(204) }
+\message{ !name(paper.tex) !offset(509) }
 \begin{figure}
   \centering
-  \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{For each tile, we want to select an image such that $d$ and $\alpha$ are minimized}
-  \label{fig:scoringFunction}
+  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
+  \caption{(a): Undistorted fisheye images for vertical planes are
+    tilted, but their effective camera axis is more or less normal to
+    the plane. (b): The effective camera axis for ceilings is at an
+    angle with respect to the plane normal. (c): Wall images are
+    cropped to be rectangular.}
+  \label{fig:projectionAngles}
 \end{figure}
-
-%\begin{figure}
-%  \centering
-%  \includegraphics[height=1.5in]{directMapping.png}
-%  \caption{The result of direct texture mapping based on locally
-%    optimized textures.}
-%  \label{fig:directMapping}
-%\end{figure}
-\message{ !name(paper.tex) !offset(699) }
+\message{ !name(paper.tex) !offset(734) }
 

### 2012-06-25 3dimpvt/paper.tex
next draft

@@
 Mounting such devices on a human-carried platform provides unique
-advantages over vehicular-based systems on wheels in terms of agility and
-portability, but can also result in much
-larger localization error. As a result, common methods for texture
-mapping generally produce poor results.
+advantages over vehicular-based systems on wheels in terms of agility
+and portability, but can also result in much larger localization
+error. As a result, common methods for texture mapping generally
+produce poor results.
 
-In this paper, we present a number of approaches to texture mapping 3D models of indoor environments made of planar surfaces in the presence of uncertainty and noise in camera poses.
-In particular, we consider a human-operated backpack system with a number of laser range scanners as well as 2 cameras facing left and right, each equipped with fisheye lenses reaching an approximately 180$^{\circ}$ field of view.
-Considering that the human operator walks at about 1 meter/second, and images are captured at 5 Hz, there is a considerable amount of overlap between successive images.
+In this paper, we present a number of approaches to texture mapping 3D
+models of indoor environments made of planar surfaces in the presence
+of uncertainty and noise in camera poses. In particular, we consider a
+human-operated backpack system with a number of laser range scanners
+as well as 2 cameras facing left and right, each equipped with fisheye
+lenses reaching an approximately 180$^{\circ}$ field of view. With the
+laser scanners active, the human operator wearing the backpack takes
+great care to walk a path such that every wall in the desired indoor
+environment is traversed and scanned lengthwise at least once.
 
-With the laser scanners active, the human operator wearing the
-backpack takes great care to walk a path such that every wall in the
-desired indoor environment is traversed and scanned lengthwise at
-least once.
+Using data collected by the onboard sensors and applying multiple
+localization and loop-closure algorithms \cite{chen2010indoor,
+  kua2012loopclosure, liu2010indoor}, the backpack is then localized
+over its data collection period. This requires recovering the 6
+degrees of freedom for the backpack as well as all its sensors,
+including the cameras mounted on it\footnote{In this paper, we use the
+  terms localization and pose recovery interchangeably, in that they
+  both refer to recovering position and orientation.}. Once this is
+complete, the data from the laser range scanners is used to generate a
+3D point cloud of the surrounding environment.  Approximate normal
+vectors for each point in the point cloud are then calculated by
+gathering neighboring points within a small radius and processing them
+through principal component analysis. These normal vectors allow for
+the classification and grouping of adjacent points into structures
+such as walls, ceilings, floors, and staircases. A RANSAC algorithm is
+then employed to fit polygonal planes to these structured groupings of
+points, resulting in a fully planar model
+\cite{sanchez2012point}. This model, consisting of multiple 2D
+polygonal planes in 3D space, along with the set of images captured by
+the backpack's cameras and their noisy 3D poses, can be considered the
+input to our texture mapping problem.
 
-Using data collected by the onboard sensors and applying multiple localization
-and loop-closure algorithms \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, the backpack is then localized over its
-data collection period.
-This requires recovering the 6 degrees of freedom for the backpack as well as all its sensors, including the cameras mounted on it.
-\footnote{In this paper, we use the terms localization and pose recovery interchangeably, in that they both refer to recovering position and orientation.} Once this is complete, the data from the laser range scanners is used to generate a 3D point cloud of the surrounding environment.
-Approximate normal vectors for each point in the
-point cloud are then calculated by gathering neighboring points within
-a small radius and processing them through principal component
-analysis. These normal vectors allow for the classification and
-grouping of adjacent points into structures such as walls, ceilings,
-floors, and staircases. A RANSAC algorithm is then employed to fit
-polygonal planes to these structured groupings of points, resulting in
-a fully planar model \cite{sanchez2012point}. This model, consisting
-of multiple 2D polygonal planes in 3D space, along with the set of
-images captured by the backpack's cameras and their noisy 3D poses,
-can be considered the input to our texture mapping problem.
+Our problem is different from others in that we are more interested in
+creating accurate and seamless textures than in recovering geometry
+out of our photos, as is a main concern in many related works
+\cite{bernardinimultiplescans, debevechybrid,
+  liu2010indoor}. Additionally, our surfaces to be textured are planes
+captured from close distances, so we do not always have many visual
+reference points to work with, as is the case when texturing detailed objects
+at high resolutions \cite{bernardinimultiplescans, wangmultipleviews}, or when creating
+large scene panoramas \cite{agarwalapanoramas, bernardinimultiplescans,
+  debevecviewdependent}. Instead, we need to adjust image projections
+relative to each other, while still taking the noisy camera
+poses provided by our localization algorithms into account. Using these camera
+poses, we also aim for complete automation and improved runtime over
+non-localized processes, such as structure from motion or image-based
+rendering \cite{agarwalapanoramas, debevechybrid,
+  snavelyphototourism}.
 
@@
 \ref{sec:simpleTextureMapping} describes the general problem of
-texture mapping and examines two variants of a tile-based mapping approach and their
-shortcomings.  Section \ref{sec:existingApproaches} demonstrates two
-previous attempts at improving texture alignment, and demonstrates their
-inadequacies for our datasets.  Section \ref{sec:proposedApproach}
-presents our proposed approach to texture mapping, combining an
-improved localization refinement process with two image selection
-approaches. Section \ref{sec:resultsAndConclusions} contains results
-and conclusions.
+texture mapping and examines two variants of a tile-based mapping
+approach and their shortcomings.  Section \ref{sec:existingApproaches}
+demonstrates two previous attempts at improving texture alignment, and
+demonstrates their inadequacies for our datasets. Section
+\ref{sec:proposedApproach} presents our proposed approach to texture
+mapping, combining an improved localization refinement process with
+two image selection approaches. Section
+\ref{sec:resultsAndConclusions} contains results and conclusions.
 
@@
 corners, which we can quickly check by projecting $t$ into each image
-using the projection method above. Furthermore, each candidate image
+using the $P_i$ camera matrices. Furthermore, each candidate image
 must have been taken at a time when its camera had a clear
@@
 ray-polygon intersection tests between the camera location, the center
-of $t$, and every other plane, all in world coordinates
-\cite{rayintersection}.
+of $t$, and every other plane \cite{rayintersection}.
 
@@
   \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{We wish to minimize camera angle $\alpha$ and distance $d$}
+  \caption{We minimize camera angle $\alpha$ and distance $d$ by maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{C})
+\cdot \vec{N}$}
   \label{fig:scoringFunction}
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{wall1_naive.jpg}}
+  \subfloat[][]{\includegraphics[width=2.3in]{wall2_naive.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{wall1_cache_full.jpg}}
+  \subfloat[][]{\includegraphics[width=2.3in]{wall2_cache.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{wall1_cache_full_shifted.jpg}}
+  \subfloat[][]{\includegraphics[width=2.3in]{wall2_cache_shift.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{wall1_dynprog_noblend.jpg}}
+  \subfloat[][]{\includegraphics[width=2.3in]{wall2_dynprog_noblend.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=2.3in]{wall2_cache_shift_blend.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=2.3in]{wall2_dynprog.jpg}}
   \caption{(a): Direct mapping. (b): Mapping with caching. (c):
-    Mapping with caching after image alignment. (d): Seam minimization approach (including image alignment)}
+    Mapping with caching after image alignment. (d): Seam minimization after image alignment). (e): (c) after blending. (f): (d) after blending.}
   \label{fig:compareAll}
@@
 Since discontinuities occur where adjacent tiles select non-aligned
-images that do not align, it makes sense to take into account image
-selections made by neighboring tiles while selecting the best image
-for a given tile. By using the same image across tile boundaries, we
-can eliminate a discontinuity altogether. If this is not possible
-because a tile is not visible in images chosen by its neighbors, using
-similar images is likely to result in less noticeable discontinuities.
+images, it makes sense to take into account image selections made by
+neighboring tiles while selecting the best image for a given tile. By
+using the same image across tile boundaries, we can eliminate a
+discontinuity altogether. If this is not possible because a tile is
+not visible in images chosen by its neighbors, using similar images is
+likely to result in less noticeable discontinuities.
 
@@
 those selected by adjacent tiles that have already been textured. We
-must first check which images can map to $t$, and then of those, we
-make a choice according to the same scoring function. Before reusing
-this image, we ensure it meets a threshold, which we set
-unconditionally to $\alpha < 45^\circ$, to be considered a viable
-image, with $\alpha$ as the camera angle as shown in Figure
-\ref{fig:scoringFunction}.
+must first check which of these images can map to $t$, and then of
+those, we make a choice according to the scoring function in Figure
+\ref{fig:scoringFunction}. Before reusing this image, we ensure it
+meets a threshold, which we set unconditionally to $\alpha <
+45^\circ$, to be considered a viable image, with $\alpha$ as the
+camera angle as shown in Figure \ref{fig:scoringFunction}.
 
@@
 threshold, we must then search the entire set of candidate images,
-selecting based on the criteria from Figure \ref{fig:scoringFunction}.
+selecting based on the same scoring function from Figure
+\ref{fig:scoringFunction}.
 
@@
 \ref{fig:compareAll}(b). As compared to Figure
-\ref{fig:compareAll}(a), discontinuities are reduced overall, but
-the amount of remaining seams suggests that image selection alone
-cannot produce seamless textures. Camera matrices, or the image
-projections themselves have to be adjusted in order to reliably
-generate clean textures.
+\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
+amount of remaining seams suggests that image selection alone cannot
+produce seamless textures. Camera matrices, or the image projections
+themselves have to be adjusted in order to reliably generate clean
+textures.
 
@@
 candidate set for generating a final seamless texture since it meets
-three important criteria. First, each tile on our planeis covered by
+three important criteria. First, each tile on our plane is covered by
 at least one image in this set; this ensures no holes in our final
@@
 Figure \ref{fig:mosaic3D}(a) shows the output of the AutoStitch software
-package which does homography-based image mosaicing. This plane is
+package which performs homography-based image mosaicing. This plane is
 nearly a best-case scenerio with many features spread uniformly across
@@
 with via the direct mapping approach of Section
-\ref{sec:directMapping}. Next, we perform image rotation and shifting
-in order to maximize SIFT feature matches in overlapping areas between
-images. We then project these images onto our plane, applying textures
-either with the tile caching method from Section
-\ref{sec:mappingWithCaching}, or with the more specialized method to
-be described in Section \ref{sec:seamMinimization}. This choice
-depends on the availability of head-on images for a given plane. We
-then finish by applying linear alphar blending to smooth out any
-remaining seams.
+\ref{sec:directMapping}. Next, we project these images onto the plane
+and perform rotation and shifting in order to maximize SIFT feature
+matches in overlapping areas between these projections. We then select
+which textures to be used either with the tile caching method from
+Section \ref{sec:mappingWithCaching}, or with the more specialized
+method to be described in Section \ref{sec:seamMinimization}. This
+choice depends on the availability of head-on images for a given
+plane. We then finish by applying linear alpha blending to smooth out
+any remaining seams.
 
@@
 corresponding points between all pairs of overlapping images using
-SIFT feature matching \cite{lowe1999object}. The SIFT matches
+SIFT feature matching \cite{lowe1999object}. SIFT matches
 determine $dx$ and $dy$ distances between each pair of features for
@@
 outliers, the RANSAC framework \cite{fischler1981random} is used for a
-robust estimate of the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
-images $i$ and $j$. The RANSAC framework handles the consensus-building machinery,
-and requires a fitting function and a distance function. For this
-application, the fitting function simply finds the average distance
-between matches in a pair of images. The distance function for a pair
-of points is chosen to be the difference between those points' SIFT match distance
-and the average distance computed by the fitting function; we use a 10
-pixel outlier threshold. This means that a SIFT match is labeled as an
-outlier if its horizontal or vertical distance is not within 10 pixels
-of the average distance computed by the fitting function.
+robust estimate of the optimal $dx_{i,j}$ and $dy_{i,j}$ distances
+between two images $i$ and $j$. The RANSAC framework handles the
+consensus-building machinery, and requires a fitting function and a
+distance function. For this application, the fitting function simply
+finds the average distance between matches in a pair of images. The
+distance function for a pair of points is chosen to be the difference
+between those points' SIFT match distance and the average distance
+computed by the fitting function. We use a 10 pixel outlier
+threshold, so that SIFT matches are labeled as outliers if
+their horizontal or vertical distances are not within 10 pixels of the
+average distance computed by the fitting function.
 
-We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair of images to refine their positions using least squares.
-Recall that there are a total of $M^{2}$ possible pairs of images, though we only
+We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
+of images to refine their positions using least squares. Recall that
+there are a total of $M^{2}$ possible pairs of images, though we only
 generate distances between images that overlap at SIFT feature
@@
 to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$ location of each image on the plane for $1 \dots M$. The optimal
-$x$ and $y$ locations are obtained in the same way, so we only
-consider the $x$ locations here:
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
+location of each image on the plane for $1 \dots M$. The optimal $x$
+and $y$ locations are obtained in the same way, so we only consider
+the $x$ locations here:
 
@@
 
-The $N \times (M+1)$ dimensional matrix $A$ is constructed with one row
-for each pair of images with measured distances produced by the SIFT
-matching stage. A row in the matrix has a $-1$ and $1$ in the columns
-corresponding to the two images in the pair. For example, the matrix
-below indicates that we generated a SIFT-based distance between images
-1 and 2, images 1 and 3, images 2 and 3, etc.
+The $N \times (M+1)$ dimensional matrix $A$ is constructed with one
+row for each pair of images with measured distances produced by the
+SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the
+columns corresponding to the two images in the pair. For example, the
+matrix below indicates that we generated a SIFT-based distance between
+images 1 and 2, images 1 and 3, images 2 and 3, etc.
 
@@
 the location of the first image determined by its original noisy
-localization, from \cite{chen2010indoor, liu2010indoor}. Thus $\vec{\gamma}$ can be written as:
+localization, from \cite{chen2010indoor, liu2010indoor}. Thus
+$\vec{\gamma}$ can be written as:
 
@@
 
-The $\vec{\beta}$ that minimizes $||X \vec{\beta} -
+The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
 \vec{\gamma}||_2^2$ results in a set of image locations on the plane
@@
 results in the significant improvements shown in Figure
-\ref{fig:compareAll}(c), as compared to Figure \ref{fig:compareAll}(b).
+\ref{fig:compareAll}(c), as compared to Figure
+\ref{fig:compareAll}(b).
 
@@
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a): Undistorted fisheye images for vertical planes are tilted, but their effective camera axis is more or less
-    normal to the plane. (b): The effective camera axis for ceilings
-    is at an angle with respect to the plane normal. (c): Wall images are cropped to be rectangular.}
+  \caption{(a): Undistorted fisheye images for vertical planes are
+    tilted, but their effective camera axis is more or less normal to
+    the plane. (b): The effective camera axis for ceilings is at an
+    angle with respect to the plane normal. (c): Wall images are
+    cropped to be rectangular.}
   \label{fig:projectionAngles}
@@
 between images that overlap. The weights of these edges are determined
-by the SSD cost function. Next, we add two
-artificial nodes, one start node representing the left border of the
-plane, and one end node representing the right border of the
-plane. The left(right) artificial node has directed edges with equal
-cost $C_0$ to(from) all images that meet the left(right) border of the
-plane.
+by the SSD cost function. Next, we add two artificial nodes, one start
+node representing the left border of the plane, and one end node
+representing the right border of the plane. The left(right) artificial
+node has directed edges with equal cost $C_0$ to(from) all images that
+meet the left(right) border of the plane.
 
@@
 entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. To address this, we solve for a new shortest path after modifying the edges chosen by the original shortest path solution such that they
-have higher cost than all other edges in our DAG, and solve for a new
-shortest path. This ensures that these edges are not chosen again
-unless they are the only available option. Our second shortest path
-solution results in a new set of chosen images, of which we only
-retain those that cover areas not covered by the first set. This
-process can be repeated as many times as needed, until holes are no
-longer present. This method is not as optimal as a 2D-coverage
-solution would be, but it is a fast approximation, and adequately
-handles the few holes we encounter.
+where no images are selected to texture. To address this, we solve for
+a new shortest path after modifying the edges chosen by the original
+shortest path solution such that they have higher cost than all other
+edges in our DAG, and solve for a new shortest path. This ensures that
+these edges are not chosen again unless they are the only available
+option. Our second shortest path solution results in a new set of
+chosen images, of which we only retain those that cover areas not
+covered by the first set. This process can be repeated as many times
+as needed, until holes are no longer present. This method is not as
+optimal as a 2D-coverage solution would be, but it is a fast
+approximation, and adequately handles the few holes we encounter.
 
@@
 at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. Figures \ref{fig:compareAll}(c) and
-\ref{fig:compareAll}(d) compare the tile caching method against this
-seam minimization method.
-For the latter, we arbitrarily choose one image for texturing where images overlap.
-Though both methods provide aligned texturing, the seam minimization approach results in fewer
-visible discontinuities, since it directly reduces the cost of each
-image boundary, while the tile caching method uses a scoring function
-that only approximates this effect. Furthermore, seam minimization
-guarantees the best selection of images, while the sequential tile
-caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. The seam
-minimization approach is also less intensive in terms of memory usage
-and runtime, as it does not require discretizing planes or images.
+as the discontinuities between their borders. Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) compare the tile
+caching method against this seam minimization method. In Figure
+\ref{fig:compareAll}(d), we arbitrarily chose one image for texturing
+where images overlap, as blending will be discussed in the next
+section. Though both methods provide aligned texturing, the seam
+minimization approach results in fewer visible discontinuities, since
+it directly reduces the cost of each image boundary, while the tile
+caching method uses a scoring function that only approximates this
+effect. Furthermore, seam minimization guarantees the best selection
+of images, while the sequential tile caching method may select images
+early on that turn out to be poor choices once subsequent tiles have
+been processed. The seam minimization approach is also far less intensive
+in terms of memory usage and runtime, as it does not require
+discretizing planes or images.
 
-In the context of texturing an entire 3D planar model, we apply the seam
-minimization approach on walls, due to its superior output when
+In the context of texturing an entire 3D planar model, we apply the
+seam minimization approach on walls, due to its superior output when
 provided with head-on images. Floors and ceilings however, given their
-many images taken at oblique angles, are textured using the tile caching method.
+many images taken at oblique angles, are textured using the tile
+caching method.
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=6in]{pipelineimages.pdf}
-  \caption{Textures corresponding to each step in our texture mapping
-    pipeline.}
-  \label{fig:pipelineimages}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=6in]{pipelineimages.pdf}
+%   \caption{Textures corresponding to each step in our texture
+%   mapping pipeline.}
+%   \label{fig:pipelineimages}
+% \end{figure*}
 
@@
 Although the preprocessing steps and image selection in both methods
-attempt to minimize all mismatches between images, there are occasional
-unavoidable discontinuities in the final texture due to different
-lighting conditions or inaccuracies in planar geometry or
+attempt to minimize all mismatches between images, there are
+occasional unavoidable discontinuities in the final texture due to
+different lighting conditions or inaccuracies in planar geometry or
 projection. These can however be treated and smoothed over by applying
@@
 shortest path problem in Section
-\ref{sec:seamMinimization}. Additionally, if images overlap in a region
-greater than the overlap distance, we only apply blending over an area
-equal to the overlap distance.
+\ref{sec:seamMinimization}. Additionally, if images overlap in a
+region greater than the overlap distance, we only apply blending over
+an area equal to the overlap distance.
 
 After blending pixels linearly across overlapping regions using alpha
-blending, texture mapping is complete. Figure
-\ref{fig:pipelineimages} shows each incremental step of our texture
-mapping approach for a different wall, as well as the final blended output resulting from
-both of our methods.
+blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
+and \ref{fig:compareAll}(f) show the final blended output resulting
+from both of our methods.
 
@@
 \label{sec:occlusionMasking}
-For the seam minimization process, we need to ensure that our images contain only content
-that should be mapped onto the target plane in question. The tiling
-approach only checks occlusion for each tile as it is
-being textured. For seam minimization, entire images are used, so occlusion checks need to be performed over the entirety of each image to
-determine available areas for texture mapping.
+For the seam minimization process, it is important that images contain
+only content that should be mapped onto the target plane in
+question. The tiling approach checks occlusion for each tile as it is
+being textured, whereas the seam minimization approach uses entire
+images.  Occlusion checks thus need to be performed over the entirety
+of each image to determine available areas for texture mapping.
 
@@
 amounts of right angles. This means that after masking out occluded
-areas, image projections will remain largely rectangular. We can
-be efficient by recursively splitting each image into rectangular
-pieces, and performing the same occlusion checks used in the tiling
-process where needed. To occlude out rectangles, their texture is removed, as untextured areas are
-never used for texture mapping.
+areas, image projections will remain largely rectangular. We can be
+efficient by recursively splitting each image into rectangular pieces,
+and performing the same occlusion checks used in the tiling process
+where needed. To occlude out rectangular pieces, their texture is
+removed, as untextured areas are never used for texture mapping.
 

### 2012-06-29 3dimpvt/_region_.tex
references in, too long

@@
 
-\message{ !name(paper.tex) !offset(509) }
+\message{ !name(paper.tex) !offset(200) }
 \begin{figure}
   \centering
-  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_naive.jpg}}
+
   \centering
-  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_cache.jpg}}
+
   \centering
-  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a): Undistorted fisheye images for vertical planes are
-    tilted, but their effective camera axis is more or less normal to
-    the plane. (b): The effective camera axis for ceilings is at an
-    angle with respect to the plane normal. (c): Wall images are
-    cropped to be rectangular.}
-  \label{fig:projectionAngles}
+  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_cache_shift.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_dynprog_noblend.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_cache_shift_blend.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=3in, clip=true]{wall1_dynprog.jpg}}
+  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
+    with caching after image alignment. (d) Seam minimization after
+    image alignment). (e) same as (c) with blending. (f) same as (d)
+    with blending.}
+  \label{fig:compareAll}
 \end{figure}
-\message{ !name(paper.tex) !offset(734) }
+\message{ !name(paper.tex) !offset(715) }
 

### 2012-06-29 3dimpvt/paper.tex
references in, too long

@@
   generating photorealistic visualizations of data collected by
-  modeling systems.  Camera pose recovery in such systems often
-  suffers from inaccuracies, resulting in visible discontinuties when
-  different images are projected adjacently onto a plane for
-  texturing. We propose two approaches for reducing discontinuities in
-  texture mapping 3d models made of planar surfaces. The first one is
-  tile based and can be used where camera axes are at arbitrary angles
-  with respect to the plane normals of the surfaces. The second one
-  results in a more seamless texture but is only applicable where
-  camera axes for imagery are closely aligned with plane normals. The
-  effectiveness of our approaches are demonstrated on two indoor
-  datasets.
+  modeling systems. Camera pose recovery in such systems often suffers
+  from inaccuracies, resulting in visible discontinuties when images
+  are projected adjacently onto a plane for texturing. We propose two
+  approaches for reducing discontinuities in texture mapping 3D models
+  made of planar surfaces. The first one is tile based and can be used
+  for images and planes at arbitrary angles relative to each
+  other. The second one, which we refer to as our seam minimization
+  approach, results in a more seamless texture but is only applicable
+  where camera axes for images are closely aligned with plane normals
+  of the surfaces to be textured. The effectiveness of our approaches
+  are demonstrated on two indoor datasets.
 \end{abstract}
@@
 
-Mounting such devices on a human-carried platform provides unique
-advantages over vehicular-based systems on wheels in terms of agility
-and portability, but can also result in much larger localization
-error. As a result, common methods for texture mapping generally
-produce poor results.
+Mounting such devices on a platform carried by an ambulatory human
+provides unique advantages over vehicular-based systems on wheels in
+terms of agility and portability, but can also result in larger
+localization error \cite{liu2010indoor}. As a result, common methods
+for texture mapping generally produce poor results.
 
@@
 as well as 2 cameras facing left and right, each equipped with fisheye
-lenses reaching an approximately 180$^{\circ}$ field of view. With the
-laser scanners active, the human operator wearing the backpack takes
-great care to walk a path such that every wall in the desired indoor
-environment is traversed and scanned lengthwise at least once.
+lenses reaching an approximately 180$^{\circ}$ field of view and
+taking photos at a rate of 5 Hz. With the cameras and laser scanners
+active, the human operator wearing the backpack takes great care to
+walk a path such that every wall in the desired indoor environment is
+traversed and scanned lengthwise at least once, resulting in many
+thousands of captured images.
 
-Using data collected by the onboard sensors and applying multiple
-localization and loop-closure algorithms \cite{chen2010indoor,
-  kua2012loopclosure, liu2010indoor}, the backpack is then localized
-over its data collection period. This requires recovering the 6
-degrees of freedom for the backpack as well as all its sensors,
-including the cameras mounted on it\footnote{In this paper, we use the
-  terms localization and pose recovery interchangeably, in that they
-  both refer to recovering position and orientation.}. Once this is
-complete, the data from the laser range scanners is used to generate a
-3D point cloud of the surrounding environment.  Approximate normal
-vectors for each point in the point cloud are then calculated by
+Applying multiple localization and loop-closure algorithms on the data
+collected by the ondoor sensors \cite{chen2010indoor,
+  kua2012loopclosure, liu2010indoor}, the backpack is
+localized\footnote{In this paper, we use the terms localization and
+  pose recovery interchangeably, in that they both refer to recovering
+  position and orientation.}  over its data collection period. This
+requires recovering the 6 degrees of freedom for the backpack as well
+as all its sensors, including the cameras rigidly mounted on it. Once
+this is complete, the data from the laser range scanners is used to
+generate a 3D point cloud of the surrounding environment and a 3D
+planar model is generated \cite{sanchez2012point}. To do so, we
+approximate normal vectors for each point in the point cloud by
 gathering neighboring points within a small radius and processing them
@@
 then employed to fit polygonal planes to these structured groupings of
-points, resulting in a fully planar model
-\cite{sanchez2012point}. This model, consisting of multiple 2D
-polygonal planes in 3D space, along with the set of images captured by
-the backpack's cameras and their noisy 3D poses, can be considered the
-input to our texture mapping problem.
+points, resulting in a fully planar model. This model, consisting of
+multiple 2D polygonal planes in 3D space, along with the set of images
+captured by the backpack's cameras and their noisy 3D poses, can be
+considered the input to our texture mapping problem.
 
-Our problem is different from others in that we are more interested in
-creating accurate and seamless textures than in recovering geometry
-out of our photos, as is a main concern in many related works
-\cite{bernardinimultiplescans, debevechybrid,
-  liu2010indoor}. Additionally, our surfaces to be textured are planes
-captured from close distances, so we do not always have many visual
-reference points to work with, as is the case when texturing detailed objects
-at high resolutions \cite{bernardinimultiplescans, wangmultipleviews}, or when creating
-large scene panoramas \cite{agarwalapanoramas, bernardinimultiplescans,
-  debevecviewdependent}. Instead, we need to adjust image projections
-relative to each other, while still taking the noisy camera
-poses provided by our localization algorithms into account. Using these camera
-poses, we also aim for complete automation and improved runtime over
-non-localized processes, such as structure from motion or image-based
-rendering \cite{agarwalapanoramas, debevechybrid,
-  snavelyphototourism}.
+This problem straddles the fields of image-based localization
+refinement as well as image alignment and mosaicing, and thus our
+proposed solution shares many similarities with past research in those
+areas, which will be examined in Section \ref{sec:existingApproaches}.
+However, given our knowledge of approximate camera poses as well as the 3D geometry of the environment to be textured, we can more accurately and efficiently texture our planes.
 
 The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} describes the general problem of
-texture mapping and examines two variants of a tile-based mapping
-approach and their shortcomings.  Section \ref{sec:existingApproaches}
-demonstrates two previous attempts at improving texture alignment, and
-demonstrates their inadequacies for our datasets. Section
-\ref{sec:proposedApproach} presents our proposed approach to texture
-mapping, combining an improved localization refinement process with
-two image selection approaches. Section
-\ref{sec:resultsAndConclusions} contains results and conclusions.
+\ref{sec:simpleTextureMapping} describes two variants of a tile-based
+mapping approach and their shortcomings.  Section
+\ref{sec:existingApproaches} discusses past research in related
+fields, demonstrates two previous attempts at improving texture
+alignment, and exhibits their inadequacies for our datasets. Section
+\ref{sec:proposedApproach} presents our proposed seam minimization
+approach to texture mapping. Section \ref{sec:resultsAndConclusions}
+contains results and conclusions.
 
@@
 Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images with which we must texture our target
+with a set of $M$ images with which we must texture the target
 plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
@@
 
-Our goal is to texture each plane using images captured by the
-backpack system, while eliminating any visual discontinuities or seams
-that would suggest that the plane's texture is not composed of a
-single continuous image.
+Because the backpack system takes photos at a rate of 5 Hz, thousands
+of images are available for texturing each plane. Our goal in creating
+a texture mapping process is to decide which of these images should be
+used, and where their contents should map onto the plane, in order to
+eliminate any visual discontinuities or seams that would suggest that
+the plane's final texture is not composed of a single continuous image.
 
@@
 
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square tiles,
-generally about 5 pixels across, and choosing an image to texture each
-tile with. We choose to work with rectangular units to ensure that
-borders between any two distinct images in our final texture are
-either horizontal or vertical. Since most environmental features
-inside buildings are horizontal or vertical, any seams in our texture
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate, we can texture the plane by discretizing it into small square tiles, generally about 5 pixels across, and choosing an image to texture each tile.
+
+We choose to work with rectangular units to ensure that borders
+between any two distinct images in our final texture are either
+horizontal or vertical. Since most environmental features inside
+buildings are horizontal or vertical, any seams in our texture
 intersect them minimally and are likely to be less noticeable.
@@
 
-Once we have a list of candidate images for $t$, we must define a
-scoring function in order to compare images and objectively select the
-best one. Since camera localization errors compound over distance, we
-wish to minimize the distance between cameras and the plane they
-texture. Additionally, we desire images that are projected
-perpendicularly onto the plane, maximizing the resolution and amount
-of useful texture available in their projections. In other words, we
-wish to minimize the angle between the plane normal and the camera
-axis for images selected for texture mapping. These two criteria can
-be met by maximizing the function $\frac{1}{d} (-1 \cdot \vec{C})
-\cdot \vec{N}$ with the parameters shown in Figure
+Once we have a list of candidate images for $t$, we define a scoring
+function in order to objectively select the best image. Since camera
+pose errors compound over distance, we wish to minimize the distance
+between cameras and the plane they texture. Additionally, we desire
+images that are projected perpendicularly onto the plane, maximizing
+the resolution and amount of useful texture available in their
+projections, as well as minimizing any parallax effects. In other words, we wish to minimize the angle between the
+plane normal and the camera axis for images selected for texture
+mapping. These two criteria can be met by maximizing the function
+$\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ as shown in Figure
 \ref{fig:scoringFunction}. Specifically, $d$ is the distance between
-the centers of a camera and a tile, and $\vec{N}$ and $\vec{C}$ are
+the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
 the directions of the plane's normal and the camera axis respectively.
@@
   \centering
-  \includegraphics[height=1.5in]{scoringFunction.pdf}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{C})
-\cdot \vec{N}$}
+  \includegraphics[height=1.5in]{scoringFunction.jpg}
+  \caption{We minimize camera angle $\alpha$ and distance $d$ by
+    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
+    \cdot \vec{n}$}
   \label{fig:scoringFunction}
@@
 
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=2.3in]{wall2_naive.jpg}}
+\begin{figure}[h!]
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.9in]{wall2_naive.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=2.3in]{wall2_cache.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.9in]{wall2_cache.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=2.3in]{wall2_cache_shift.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.9in]{wall2_cache_shift.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=2.3in]{wall2_dynprog_noblend.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.9in]{wall2_dynprog_noblend.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=2.3in]{wall2_cache_shift_blend.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.9in]{wall2_cache_shift_blend.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=2.3in]{wall2_dynprog.jpg}}
-  \caption{(a): Direct mapping. (b): Mapping with caching. (c):
-    Mapping with caching after image alignment. (d): Seam minimization after image alignment). (e): (c) after blending. (f): (d) after blending.}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.9in]{wall2_dynprog.jpg}}
+  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
+    with caching after image alignment. (d) Seam minimization after
+    image alignment). (e) same as (c) with blending. (f) same as (d)
+    with blending.}
   \label{fig:compareAll}
@@
 
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads
-to the best texture for each tile independently, but overall results
-in many image boundaries with abrupt discontinuities, due to
-significant misalignment between images, as a result of camera pose
-inaccuracies.
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
+the best texture for each tile independently, but overall results in
+many image boundaries with abrupt discontinuities, due to significant
+misalignment between images, as a result of camera pose inaccuracies.
 
@@
 images, it makes sense to take into account image selections made by
-neighboring tiles while selecting the best image for a given tile. By
-using the same image across tile boundaries, we can eliminate a
-discontinuity altogether. If this is not possible because a tile is
-not visible in images chosen by its neighbors, using similar images is
-likely to result in less noticeable discontinuities.
+neighboring tiles while texture mapping a given tile. By using the
+same image across tile boundaries, we can eliminate a discontinuity
+altogether. If this is not possible because a tile is not visible in
+images chosen by its neighbors, using similar images across a tile boundary will result in minimal discontinuities.
 
 Similar to a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a good candidate,
+$t$ by searching through two subsets of images for a viable candidate,
 before searching through the entire set. The first subset of images is
@@
 \ref{fig:scoringFunction}. Before reusing this image, we ensure it
-meets a threshold, which we set unconditionally to $\alpha <
-45^\circ$, to be considered a viable image, with $\alpha$ as the
-camera angle as shown in Figure \ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we then check
-our second subset of images, which consists of images that were taken
-near the images in the first subset, both spatially and
-temporally. These images are not the same as the ones used for
-neighboring tiles, but they were taken at a similar location and time,
-suggesting that their localization and projection are very
-similar. Again, if no good image is found according to the same
-threshold, we must then search the entire set of candidate images,
-selecting based on the same scoring function from Figure
+meets the criteria $\alpha < 45^\circ$, in order to be considered a
+viable image, with $\alpha$ as the camera angle as shown in Figure
 \ref{fig:scoringFunction}.
 
-The results of this caching approach are shown in Figure
+If no satisfactory image is found in the first subset, we check the
+second subset of images, consisting of those taken near the ones in
+the first subset, both spatially and temporally. These images are not
+the same as the ones used for neighboring tiles, but were taken at a
+similar location and time, suggesting that their localization and
+projection are very similar. Again, if no viable image is found
+according to the same criteria, we search the entire set of candidate
+images, selecting based on the same scoring function from Figure
+\ref{fig:scoringFunction}.
+
+The result of this caching approach is shown in Figure
 \ref{fig:compareAll}(b). As compared to Figure
@@
 
-\section{Existing Approaches to Image-Aligned Texture Mapping}
+\section{Existing Approaches to Image Alignment}
 \label{sec:existingApproaches}
@@
 to work with the more limited set of images corresponding to those
-chosen by the direct mapping approach, without caching (Section
-\ref{sec:directMapping}. This set of images constitutes a good
+chosen by the direct mapping approach, without caching, of Section
+\ref{sec:directMapping}. This set of images constitutes a reasonable
 candidate set for generating a final seamless texture since it meets
-three important criteria. First, each tile on our plane is covered by
-at least one image in this set; this ensures no holes in our final
+three important criteria. First, each tile on the plane is covered by
+at least one image in this set; this ensures no holes in the final
 texture. Second, images are all selected according to the scoring
-function in Figure \ref{fig:scoringFunction}, ensuring good camera
-distances and angles. Third, as a side result of the scoring function,
-selected images are only viable candidates for the tiles near their
+function in Figure \ref{fig:scoringFunction}, ensuring reasonable
+camera distances and angles. Third, as a side result of the scoring
+function, selected images are only viable for the tiles near their
 center of projection. Thus, there should be plenty of overlap between
@@
 resulting in holes, as well as area for blending between them. With
-this set of images, we now review two existing approaches towards
-refining and combining their projections.
+this set of images, we now review approaches towards refining and
+combining their projections.
 
-\subsection{Image Mosaicing}
-\label{sec:imageMosaicing}
+One way to align image projections is to refine their noisy camera
+poses, such that they become pixel accurate. This can be done by using
+image correspondences to adjust each image's camera matrix over 6
+degrees of freedom (DOF) \cite{coorg1997matching,
+  liu2010indoor, shum2000systems, szeliski1997creating}. Using our same modeling datasets, recent work
+followed this approach by solving a non-linear optimization problem to
+refine camera poses during backpack localization \cite{liu2010indoor,
+  chen2010indoor}. This approach however suffers from error
+accumulation and drift as shown in Figure \ref{fig:mosaic3D}(a), as
+well as high complexity and runtime.
+
+Refining camera poses is analogous to image alignment or mosaicing,
+which perform translations on images in order to align them directly.
+One common approach to image alignment is to iteratively match images
+on intensity differences in selected patches, often in a spatial
+hierarchy \cite{hager1998efficient, lucas1981iterative,
+  shum2000systems, szeliski2006image}. Another widely-used approach is
+to perform feature matching, which requires the detection of visual
+features and their existence in multiple images
+\cite{brown2007automatic, cho2003automatic,
+  mikolajczyk2005performance, szeliski2006image,
+  yun2003comprehensive}. Notably, both approaches rely on the presence
+of multiple visual references, as when texturing detailed objects at
+high resolutions \cite{bernardinimultiplescans, wangmultipleviews}, or
+when creating large scene panoramas \cite{agarwalapanoramas,
+  bernardinimultiplescans, debevecviewdependent,
+  snavelyphototourism}. In contrast, our indoor datasets have a high
+prevalence of bare walls and ceilings, resulting in few reference
+points that can be used to judge alignment.
+
+Additionally, our datasets often contain long chains of images, which
+leads to error accumulation when image correspondences are not
+accurate. For example, when matching a long chain of images through
+homography, a pixel in the $nth$ image must be translated into the
+first image's coordinates by multiplying by the $3\times3$ matrix $H_1
+H_2 H_3 ... H_n$. Any error in one of these homography matrices is
+propagated to all further images, resulting in drift. Figure
+\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
+package, which performs homography-based image mosaicing
+\cite{autostitch}. Even with many features spread across this plane,
+the mosaicing produces errors that causes straight lines to appear as
+waves on the plane, despite the fact that it was generated after
+careful hand tuning. Many planes with fewer features simply failed
+outright.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
+  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
-  \caption{Both image mosaicing (a) and the graph-based localization refinement algorithm from
-    \cite{chen2010indoor} (b) suffer from the problem of compounding
-    errors.}
+  \centering \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
+  \caption{Texture alignment via (a) the graph-based localization
+    refinement algorithm from \cite{chen2010indoor} and (b) image
+    mosaicing}
   \label{fig:mosaic3D}
@@
 
-When images of a plane are taken from arbitrary overlapping positions,
-they are related by homography \cite{hz}. Thus, existing
-homography-based image mosaicing algorithms are applicable
-\cite{brown2007automatic}. However, errors can compound when long
-chains of images are mosaiced together using these approaches. For
-example, a pixel in the $n$th image in the chain must be translated
-into the first image's coordinates by multiplying by the $3\times3$
-matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these homography
-matrices is propagated to all further images until the chain is
-broken. For some chains of images this can happen almost immediately
-due to erroneous correspondence matches and the resulting image mosaic
-is grossly misshapen.
-
-Figure \ref{fig:mosaic3D}(a) shows the output of the AutoStitch software
-package which performs homography-based image mosaicing. This plane is
-nearly a best-case scenerio with many features spread uniformly across
-it. Even so, the mosaicing produces errors that causes straight lines
-to appear as waves on the plane, despite the fact that it was
-generated after careful hand tuning. Many planes with fewer features
-simply failed outright. Thus, image mosaicing is not a robust enough
-solution for reliably texture mapping our dataset.
-
-\subsection{Image-Based 3D Localization Refinement}
-\label{sec:imageBased3DRefinement}
-
-Another approach is to refine the camera matrices using image
-correspondences to guide the process. Each image's camera matrix has 6
-degrees of freedom that can be adjusted. Previous work on this problem
-attempted to refine camera matrices by solving a non-linear
-optimization problem \cite{liu2010indoor}. This process is specific to
-the backpack system which generated our dataset, as it must be run
-during backpack localization\cite{liu2010indoor,
-  chen2010indoor}. This approach suffers from a similar
-error propagation problem as shown in Figure \ref{fig:mosaic3D}(b).
+\section{Seamless Texture Mapping}
+\label{sec:proposedApproach}
 
@@
 
-\section{Proposed Method for Seamless Texture Mapping}
-\label{sec:proposedApproach}
-In this section, we will describe our proposed method for seamless
-texture mapping. Our approach consists of 4 steps, as seen in Figure
+In this section, we describe our proposed method for seamless texture
+mapping. Our approach consists of 4 steps, as seen in Figure
 \ref{fig:pipeline}.  First, we choose a subset of $M$ images to work
@@
 
-\subsection{Image Projection and Rotation}
+\subsection{Image Rotation}
 \label{sec:projectionAndRotation}
@@
 done in the same way as the approaches in Section
-\ref{sec:simpleTextureMapping}. We then perform rotations on these
-projections, as adjacent images with different orientations result in
-strong discontinuities.
+\ref{sec:simpleTextureMapping}.
+Rather than work with all 6 DOF, which is computationally intensive, we choose to work only in two dimensions, performing 2D rotations and translations on the image projections, as errors in either lead to the greatest discontinuities.
 
-These rotations are accomplished by using Hough transforms, which
+We perform rotations using Hough transforms, which
 detect the presence and orientation of linear features in our
@@
 vertical lines corresponding to doors, wall panels, rectangular
-frames, etc. If features in the environment are not vertical, or are
-not parallel to eachother, this step is skipped.
+frames, etc. If features in the environment are not vertical, e.g. for
+floors and ceilings, or are not parallel to each other, this step is
+skipped.
 
-\subsection{Image Pose Refinement}
+\subsection{Image Shifting}
 \label{sec:robustSIFTFeatureMatching}
 Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images using
-SIFT feature matching \cite{lowe1999object}. SIFT matches
-determine $dx$ and $dy$ distances between each pair of features for
-two images on the plane, though these distances may not always be the
-same for different features.
+corresponding points between all pairs of overlapping images.
+We use SIFT features for their high detection rate, and choose to use feature alignment rather than intensity-based alignment due to the differences in lighting as well as possible occlusion among our images, both of which feature alignment is less sensitive to \cite{lai1999robust, lowe1999object, mikolajczyk2005performance, szeliski2006image}.
+
+SIFT matches determine $d^x$ and $d^y$ distances between each pair of
+features for two images on the plane, though these distances may not
+always be the same for different features.
 
 Since indoor environments often contain repetitive features such as
-floor tiles or doors, we need to ensure that our SIFT-based distances
-are reliable. In order to mitigate the effect of incorrect matches and
+floor tiles or doors, we need to ensure that SIFT-based distances are
+reliable. In order to mitigate the effect of incorrect matches and
 outliers, the RANSAC framework \cite{fischler1981random} is used for a
-robust estimate of the optimal $dx_{i,j}$ and $dy_{i,j}$ distances
+robust estimate of the optimal $d^x_{i,j}$ and $d^y_{i,j}$ distances
 between two images $i$ and $j$. The RANSAC framework handles the
@@
 between those points' SIFT match distance and the average distance
-computed by the fitting function. We use a 10 pixel outlier
-threshold, so that SIFT matches are labeled as outliers if
-their horizontal or vertical distances are not within 10 pixels of the
-average distance computed by the fitting function.
+computed by the fitting function. We use a 10 pixel outlier threshold,
+so that SIFT matches are labeled as outliers if their horizontal or
+vertical distances are not within 10 pixels of the average distance
+computed by the fitting function.
 
-We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
+We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
 of images to refine their positions using least squares. Recall that
@@
 images. In practice there are often cases where there is a break in
-the chain of images, meaning that no SIFT matches were found between
+the chain of images, meaning that no SIFT matches are found between
 one segment of the plane and another. In this case we add rows to the
@@
 with far greater accuracy. Applying the tile caching method from
-Section \ref{sec:mappingWithCaching} on these re-localized images
-results in the significant improvements shown in Figure
+Section \ref{sec:mappingWithCaching} on these rotated and shifted
+images results in the significant improvements shown in Figure
 \ref{fig:compareAll}(c), as compared to Figure
@@
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a): Undistorted fisheye images for vertical planes are
+  \caption{(a) Undistorted fisheye images for vertical planes are
     tilted, but their effective camera axis is more or less normal to
-    the plane. (b): The effective camera axis for ceilings is at an
-    angle with respect to the plane normal. (c): Wall images are
+    the plane. (b) The effective camera axis for ceilings is at an
+    angle with respect to the plane normal. (c) Wall images are
     cropped to be rectangular.}
@@
 but at an angle with respect to horizontal floors and ceilings. This
-is depicted in Figure \ref{fig:projectionAngles}.
-
-These oblique camera angles translate into textures that span
-extremely large areas once projected. Using the tile-based texture
-mapping criteria from Figure \ref{fig:scoringFunction}, such
-projections have good scores for certain areas on the plane, but worse
-scores for others. The tiling approach in Section
+is depicted in Figure \ref{fig:projectionAngles}. These oblique camera
+angles translate into textures that span extremely large areas once
+projected. Using the tile-based texture mapping criteria from Figure
+\ref{fig:scoringFunction}, such projections have high or low scores
+depending on the location on the plane, as shown in Figure
+\ref{fig:projectionAngles}(b). The tiling approach in Section
 \ref{sec:simpleTextureMapping} is thus a good choice for texturing
 floors and ceilings, as it uses the parts of image projections that
-are good choices for their respective plane locations, e.g. areas near
-point A in Figure \ref{fig:projectionAngles}(b), but not near point B.
+are viable choices for their respective plane locations, e.g. areas
+near point A in Figure \ref{fig:projectionAngles}(b), but not near
+point B.
 
@@
 (b) minimizes the amount of visible seams. A straigntforward cost
-function that accomplishes the latter is the sum of squared pixel
-differences in overlapping regions between all pairs of images, after
-they have been aligned as described in Section
-\ref{sec:projectionAndRotation}. Minimizing this cost function, which
-we refer to as SSD, encourages image boundaries to occur either in
-featureless areas, such as bare walls, or in areas where images match
-extremely well.
+function that accomplishes the latter is the Sum of Squared pixel
+Differences (SSD) in overlapping regions between all pairs of images,
+after they have been aligned as described in Section
+\ref{sec:projectionAndRotation}. Minimizing this cost function
+encourages image boundaries to occur either in featureless areas, such
+as bare walls, or in areas where images match extremely well.
 
@@
 it. Given that wall-texture candidate images are taken from more or
-less head-on angles, and assuming only minor rotations are made during
-localization refinement, we can reason that their projections onto the
-plane are approximately rectangular. By cropping them all to be
-rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
-problem becomes the conceptually simpler one of filling a polygon with
-rectangles, such that the sum of all costs between each pair of
-rectangles is minimal. We thus also retain the advantages of working
-with rectangular units, as explained in Section
-\ref{sec:simpleTextureMapping}.
+less head-on angles, and assuming only minor rotations are made in
+Section \ref{sec:projectionAndRotation}, we can reason that their
+projections onto the plane are approximately rectangular. By cropping
+them all to be rectangular, as shown in Figure
+\ref{fig:projectionAngles}(c), our problem becomes the conceptually
+simpler one of filling a polygon with rectangles, such that the sum of
+all costs between each pair of rectangles is minimal. We thus also
+retain the advantages of working with rectangular units, as explained
+in Section \ref{sec:simpleTextureMapping}.
 
-The location and orientation of the cameras on the acquisition
-backpack is such that images nearly always contain the entirety of the
-floor to ceiling range of wall planes. Images are therefore rarely
-projected with one above another when texturing wall planes. In
-essence, we need only to ensure horizontal coverage of wall planes, as
-our images provide full vertical coverage themselves. We can thus
-construct a Directed Acyclic Graph (DAG) from the images, with edge
-costs defined by the SSD cost function, and solve a simple shortest
-path problem to find an optimal subset of images with regard to the
-cost function \cite{dijkstra}.
+The location and orientation of the cameras and the fisheye lenses on
+the acquisition backpack is such that images nearly always contain the
+entirety of the floor to ceiling range of wall planes. Images are
+therefore rarely projected with one above another when texturing wall
+planes. In essence, we need only to ensure lateral coverage of wall
+planes, e.g. from left to right, as our images provide full vertical
+coverage themselves. We can thus construct a Directed Acyclic Graph
+(DAG) from the images, with edge costs defined by the SSD cost
+function, and solve a simple shortest path problem to find an optimal
+subset of images with regard to the cost function \cite{dijkstra}.
 
@@
 at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) compare the tile
-caching method against this seam minimization method. In Figure
-\ref{fig:compareAll}(d), we arbitrarily chose one image for texturing
-where images overlap, as blending will be discussed in the next
-section. Though both methods provide aligned texturing, the seam
-minimization approach results in fewer visible discontinuities, since
-it directly reduces the cost of each image boundary, while the tile
+as the discontinuities between their borders. As seen in Figure
+\ref{fig:compareAll}(d), this seam minimization method has fewer
+visible discontinuities than Figure \ref{fig:compareAll}(c)
+corresponding to the tile caching approach\footnote{In Figure
+  \ref{fig:compareAll}(d), we arbitrarily chose one image for
+  texturing where images overlap, as blending will be discussed in the
+  next section.}.
+This is especially evident when comparing the posters in the images, which have clear misalignment over seams in Figure \ref{fig:compareAll}(c), but are much more aligned in Figure \ref{fig:compareAll}(d).
+This is because the seam minimization approach
+directly reduces the cost of each image boundary, while the tile
 caching method uses a scoring function that only approximates this
@@
 early on that turn out to be poor choices once subsequent tiles have
-been processed. The seam minimization approach is also far less intensive
-in terms of memory usage and runtime, as it does not require
+been processed. The seam minimization approach is also far less
+intensive in terms of memory usage and runtime, as it does not require
 discretizing planes or images.
 
-In the context of texturing an entire 3D planar model, we apply the
-seam minimization approach on walls, due to its superior output when
-provided with head-on images. Floors and ceilings however, given their
-many images taken at oblique angles, are textured using the tile
-caching method.
+In the context of texturing an entire 3D planar model, we choose to
+apply the seam minimization approach on walls, due to its superior
+output when provided with head-on images. Floors and ceilings however,
+given their many images taken at oblique angles, are textured using
+the tile caching method.
 
@@
 blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the final blended output resulting
-from both of our methods.
+and \ref{fig:compareAll}(f) show the blended versions of Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
+is clear that the seam minimization approach still exhibits better
+alignment and fewer seams than the tile-caching method, as Figure
+\ref{fig:compareAll}(f) has the best visual quality among the textures
+in Figure \ref{fig:compareAll}.
 
@@
 \label{sec:resultsAndConclusions}
+Examples of ceilings and floors textured with the tile caching
+approach, and walls textured with the seam minimization approach, are
+displayed in Figure \ref{fig:results}. High resolution texture
+comparisons, as well as a walkthrough of a fully textured 3D model are
+available in the accompanying video to this paper.
+
 In this paper, we have developed an approach to texture map models
 with noisy camera localization data. We are able to refine image
-locations based on feature matching, and robustly handle outliers. The tile-based mapping approach can be used to texture both simple rectangular walls as
-well as complex floor and ceiling geometry. We also presented a seam minimization texturing method that produces seamless textures on planes where
-multiple head-on images are available. Each of these approaches is
-highly modular, and easily tunable for different environments and
-acquisition hardware.
-
-Examples of ceilings and floors textured with the tile caching approach, and walls
-textured with the seam minimization approach, are displayed in Figure
-\ref{fig:results}. High resolution texture comparisons, as well as a
-walkthrough of a fully textured 3D model are available in the
-accompanying video to this paper.
+locations based on feature matching, and robustly handle outliers. The
+tile-based mapping approach can be used to texture both simple
+rectangular walls as well as complex floor and ceiling geometry. We
+also presented a seam minimization texturing method that produces
+seamless textures on vertical planes where multiple head-on images are
+available. Each of these approaches is highly modular, and easily
+tunable for different environments and acquisition hardware.
 
@@
 
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{4thfloor8.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=3in]{4thfloor8.jpg}}
 
@@
 
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
-  \caption{Examples of our final texture mapping output for (a) walls, (b) a
-    ceiling, (c) an entire floor, (d) a full model}
+  \centering \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
+  \caption{Examples of our final texture mapping output for (a) walls,
+    (b) a ceiling, (c) an entire floor, (d) a full model}
   \label{fig:results}
@@
 \appendix
-\section{Occlusion Masking}
+\section*{Appendix A. Occlusion Masking}
 \label{sec:occlusionMasking}

### 2012-06-29 3dimpvt/paper.tex
removing references to step 1

@@
   modeling systems. Camera pose recovery in such systems often suffers
-  from inaccuracies, resulting in visible discontinuties when images
-  are projected adjacently onto a plane for texturing. We propose two
-  approaches for reducing discontinuities in texture mapping 3D models
-  made of planar surfaces. The first one is tile based and can be used
-  for images and planes at arbitrary angles relative to each
-  other. The second one, which we refer to as our seam minimization
-  approach, results in a more seamless texture but is only applicable
-  where camera axes for images are closely aligned with plane normals
-  of the surfaces to be textured. The effectiveness of our approaches
-  are demonstrated on two indoor datasets.
+  from inaccuracies, resulting in visible discontinuties when
+  successive images are projected adjacently onto a plane for
+  texturing. We propose two approaches to reduce discontinuities in
+  texture mapping 3D models made of planar surfaces. The first one is
+  tile based and can be used for images and planes at arbitrary angles
+  relative to each other. The second one results in a more seamless
+  texture, but is only applicable where camera axes for images are
+  closely aligned with plane normals of the surfaces to be
+  textured. The effectiveness of our approaches are demonstrated on
+  two indoor datasets.
 \end{abstract}
@@
 reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}.This is
+\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
 known as the simultaneous localization and mapping (SLAM) problem, and
@@
 models of indoor environments made of planar surfaces in the presence
-of uncertainty and noise in camera poses. In particular, we consider a
-human-operated backpack system with a number of laser range scanners
-as well as 2 cameras facing left and right, each equipped with fisheye
-lenses reaching an approximately 180$^{\circ}$ field of view and
-taking photos at a rate of 5 Hz. With the cameras and laser scanners
-active, the human operator wearing the backpack takes great care to
-walk a path such that every wall in the desired indoor environment is
-traversed and scanned lengthwise at least once, resulting in many
-thousands of captured images.
-
-Applying multiple localization and loop-closure algorithms on the data
-collected by the ondoor sensors \cite{chen2010indoor,
-  kua2012loopclosure, liu2010indoor}, the backpack is
-localized\footnote{In this paper, we use the terms localization and
-  pose recovery interchangeably, in that they both refer to recovering
-  position and orientation.}  over its data collection period. This
-requires recovering the 6 degrees of freedom for the backpack as well
-as all its sensors, including the cameras rigidly mounted on it. Once
-this is complete, the data from the laser range scanners is used to
-generate a 3D point cloud of the surrounding environment and a 3D
-planar model is generated \cite{sanchez2012point}. To do so, we
-approximate normal vectors for each point in the point cloud by
-gathering neighboring points within a small radius and processing them
-through principal component analysis. These normal vectors allow for
-the classification and grouping of adjacent points into structures
-such as walls, ceilings, floors, and staircases. A RANSAC algorithm is
-then employed to fit polygonal planes to these structured groupings of
-points, resulting in a fully planar model. This model, consisting of
-multiple 2D polygonal planes in 3D space, along with the set of images
-captured by the backpack's cameras and their noisy 3D poses, can be
-considered the input to our texture mapping problem.
+of uncertainty and noise in camera poses. In particular, we consider
+data obtained from a human-operated backpack system with a number of
+laser range scanners as well as 2 cameras facing left and right, each
+equipped with fisheye lenses reaching an approximately 180$^{\circ}$
+field of view and taking photos at a rate of 5 Hz. Applying multiple
+localization and loop-closure algorithms on the raw data collected by
+the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
+  liu2010indoor}, the backpack is localized\footnote{In this paper, we
+  use the terms localization and pose recovery interchangeably, in
+  that they both refer to recovering position and orientation.}  over
+its data collection period. This requires recovering the 6 degrees of
+freedom for the backpack as well as the cameras rigidly mounted on
+it. Once this is complete, the data from the laser range scanners is
+used to generate a 3D point cloud of the surrounding environment, from which a
+3D planar model is created \cite{sanchez2012point}. This model, consisting of 2D
+polygonal planes in 3D space, along with the set of images captured by
+the backpack's cameras and their noisy 3D poses, can be considered the
+input to our texture mapping problem.
 
@@
 proposed solution shares many similarities with past research in those
-areas, which will be examined in Section \ref{sec:existingApproaches}.
-However, given our knowledge of approximate camera poses as well as the 3D geometry of the environment to be textured, we can more accurately and efficiently texture our planes.
+areas, which will be examined in Section
+\ref{sec:existingApproaches}. However, we can exploit known
+approximate camera poses as well as the 3D geometry of the environment
+to more accurately and efficiently texture the planes.
 
@@
 In all subsequent sections, we discuss the process of texture mapping
-a single plane, as the texturing of each of our planes is independent
-and can be completed in parallel.
+a single plane, as the texturing of each plane is independent and can
+be completed in parallel.
 
@@
 Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images with which we must texture the target
+with a set of $M$ images to texture the target
 plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
@@
 a texture mapping process is to decide which of these images should be
-used, and where their contents should map onto the plane, in order to
-eliminate any visual discontinuities or seams that would suggest that
-the plane's final texture is not composed of a single continuous image.
+used, and where their contents should map onto the texture, in order
+to eliminate any visual discontinuities or seams that would suggest
+that the plane's final texture is not composed of a single continuous
+image.
 
@@
 
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate, we can texture the plane by discretizing it into small square tiles, generally about 5 pixels across, and choosing an image to texture each tile.
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+we can texture the plane by discretizing it into small square tiles,
+generally about 5 pixels across, and choosing an image to texture each
+tile.
 
 We choose to work with rectangular units to ensure that borders
-between any two distinct images in our final texture are either
+between any two distinct images in the final texture are either
 horizontal or vertical. Since most environmental features inside
@@
 
-In order to select an image for texturing tile $t$, we must first
+In order to select an image for texturing a tile $t$, we must first
 gather a list of candidate images that contain all four of its
@@
 the resolution and amount of useful texture available in their
-projections, as well as minimizing any parallax effects. In other words, we wish to minimize the angle between the
-plane normal and the camera axis for images selected for texture
-mapping. These two criteria can be met by maximizing the function
-$\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ as shown in Figure
+projections, as well as minimizing any parallax effects. In other
+words, we wish to minimize the angle between the plane normal and the
+camera axis for images selected for texture mapping. These two
+criteria can be met by maximizing the function $\frac{1}{d} (-1 \cdot
+\vec{c}) \cdot \vec{n}$ as shown in Figure
 \ref{fig:scoringFunction}. Specifically, $d$ is the distance between
@@
 altogether. If this is not possible because a tile is not visible in
-images chosen by its neighbors, using similar images across a tile boundary will result in minimal discontinuities.
+images chosen by its neighbors, using similar images across tile
+boundaries also leads to less noticeable discontinuities.
 
@@
 the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but were taken at a
+the same as the ones used for neighboring tiles, but are taken at a
 similar location and time, suggesting that their localization and
-projection are very similar. Again, if no viable image is found
+projection are quite similar. Again, if no viable image is found
 according to the same criteria, we search the entire set of candidate
@@
 
-Before examining these approaches, we first obtain a set of images to
-work with.  Rather than perform camera or image adjustments across the
-many thousands of images acquired in a typical data collection, we opt
-to work with the more limited set of images corresponding to those
-chosen by the direct mapping approach, without caching, of Section
-\ref{sec:directMapping}. This set of images constitutes a reasonable
-candidate set for generating a final seamless texture since it meets
-three important criteria. First, each tile on the plane is covered by
-at least one image in this set; this ensures no holes in the final
-texture. Second, images are all selected according to the scoring
-function in Figure \ref{fig:scoringFunction}, ensuring reasonable
-camera distances and angles. Third, as a side result of the scoring
-function, selected images are only viable for the tiles near their
-center of projection. Thus, there should be plenty of overlap between
-selected images, allowing for some degree of shifting without
-resulting in holes, as well as area for blending between them. With
-this set of images, we now review approaches towards refining and
-combining their projections.
+Image projections can be aligned by refining their noisy camera poses,
+using image correspondences to adjust each image's camera matrix over
+6 degrees of freedom (DOF) \cite{coorg1997matching, liu2010indoor,
+  shum2000systems, szeliski1997creating}. Applying such approaches to
+our datasets however results in error accumulation and drift as shown
+in Figure \ref{fig:mosaic3D}(a), as well as high complexity and
+runtime \cite{liu2010indoor}.
 
-One way to align image projections is to refine their noisy camera
-poses, such that they become pixel accurate. This can be done by using
-image correspondences to adjust each image's camera matrix over 6
-degrees of freedom (DOF) \cite{coorg1997matching,
-  liu2010indoor, shum2000systems, szeliski1997creating}. Using our same modeling datasets, recent work
-followed this approach by solving a non-linear optimization problem to
-refine camera poses during backpack localization \cite{liu2010indoor,
-  chen2010indoor}. This approach however suffers from error
-accumulation and drift as shown in Figure \ref{fig:mosaic3D}(a), as
-well as high complexity and runtime.
-
-Refining camera poses is analogous to image alignment or mosaicing,
-which perform translations on images in order to align them directly.
-One common approach to image alignment is to iteratively match images
-on intensity differences in selected patches, often in a spatial
-hierarchy \cite{hager1998efficient, lucas1981iterative,
-  shum2000systems, szeliski2006image}. Another widely-used approach is
-to perform feature matching, which requires the detection of visual
-features and their existence in multiple images
-\cite{brown2007automatic, cho2003automatic,
+Another common approach to image alignment is to
+iteratively match images on intensity differences in selected patches,
+often in a spatial hierarchy \cite{hager1998efficient,
+  lucas1981iterative, shum2000systems, szeliski2006image}. Another
+widely-used approach is to perform feature matching, which requires
+the detection of visual features and their existence in multiple
+images \cite{brown2007automatic, cho2003automatic,
   mikolajczyk2005performance, szeliski2006image,
@@
 the mosaicing produces errors that causes straight lines to appear as
-waves on the plane, despite the fact that it was generated after
+waves on the plane, despite the fact that it is generated after
 careful hand tuning. Many planes with fewer features simply failed
-outright.
+outright using this approach.
 
@@
   \centering
-  \includegraphics[width=3in]{pipeline.pdf}
+  \includegraphics[width=3.5in]{pipeline.pdf}
   \caption{Our proposed method for seamless texture mapping.}
@@
 We begin with the projection of all images onto the plane. This is
-done in the same way as the approaches in Section
-\ref{sec:simpleTextureMapping}.
-Rather than work with all 6 DOF, which is computationally intensive, we choose to work only in two dimensions, performing 2D rotations and translations on the image projections, as errors in either lead to the greatest discontinuities.
+done in the same way as in Section
+\ref{sec:simpleTextureMapping}. Rather than work with all 6 DOF, which
+is computationally intensive, we choose to work only in two
+dimensions, performing 2D rotations and translations on the image
+projections, as errors in either lead to the greatest discontinuities.
 
-We perform rotations using Hough transforms, which
-detect the presence and orientation of linear features in our
-images. Rather than match the orientation of such features in each
-image, we simply apply rotations such that the strongest near-vertical
-features are made completely vertical. This is effective for vertical
-planes in indoor models, since they usually consist of parallel
-vertical lines corresponding to doors, wall panels, rectangular
-frames, etc. If features in the environment are not vertical, e.g. for
-floors and ceilings, or are not parallel to each other, this step is
-skipped.
+We perform rotations using Hough transforms, which detect the presence
+and orientation of linear features in our images. Rather than match
+the orientation of such features in each image, we simply apply
+rotations such that the strongest near-vertical features are made
+completely vertical. This is effective for vertical planes in indoor
+models, since they usually consist of parallel vertical lines
+corresponding to doors, wall panels, rectangular frames, etc. If
+features in the area are not vertical, e.g. for floors and
+ceilings, this step is skipped.
 
@@
 Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images.
-We use SIFT features for their high detection rate, and choose to use feature alignment rather than intensity-based alignment due to the differences in lighting as well as possible occlusion among our images, both of which feature alignment is less sensitive to \cite{lai1999robust, lowe1999object, mikolajczyk2005performance, szeliski2006image}.
+corresponding points between all pairs of overlapping images. We use
+SIFT features for their high detection rate, and choose to use feature
+alignment rather than intensity-based alignment due to the differences
+in lighting as well as possible occlusion among our images, both of
+which feature alignment is less sensitive to \cite{lai1999robust,
+  lowe1999object, mikolajczyk2005performance, szeliski2006image}.
 
@@
 features for two images on the plane, though these distances may not
-always be the same for different features.
-
-Since indoor environments often contain repetitive features such as
-floor tiles or doors, we need to ensure that SIFT-based distances are
-reliable. In order to mitigate the effect of incorrect matches and
-outliers, the RANSAC framework \cite{fischler1981random} is used for a
-robust estimate of the optimal $d^x_{i,j}$ and $d^y_{i,j}$ distances
-between two images $i$ and $j$. The RANSAC framework handles the
-consensus-building machinery, and requires a fitting function and a
-distance function. For this application, the fitting function simply
-finds the average distance between matches in a pair of images. The
-distance function for a pair of points is chosen to be the difference
-between those points' SIFT match distance and the average distance
-computed by the fitting function. We use a 10 pixel outlier threshold,
-so that SIFT matches are labeled as outliers if their horizontal or
-vertical distances are not within 10 pixels of the average distance
-computed by the fitting function.
+always be the same for different features. Since indoor environments
+often contain repetitive features such as floor tiles or doors, we
+need to ensure that SIFT-based distances are reliable. In order to
+mitigate the effect of incorrect matches and outliers, the RANSAC
+framework \cite{fischler1981random} is used for a robust estimate of
+the optimal $d^x_{i,j}$ and $d^y_{i,j}$ distances between two images
+$i$ and $j$. The RANSAC framework handles the consensus-building
+machinery, and requires a fitting function and a distance
+function. For this application, the fitting function simply finds the
+average distance between matches in a pair of images. The distance
+function for a pair of points is chosen to be the difference between
+those points' SIFT match distance and the average distance computed by
+the fitting function. We use a 10 pixel outlier threshold, so that
+SIFT matches are labeled as outliers if their horizontal or vertical
+distances are not within 10 pixels of the average distance computed by
+the fitting function.
 
@@
 columns corresponding to the two images in the pair. For example, the
-matrix below indicates that we generated a SIFT-based distance between
-images 1 and 2, images 1 and 3, images 2 and 3, etc.
+matrix below indicates a SIFT-based distance between images 1 and 2,
+images 1 and 3, images 2 and 3, etc.
 
@@
 that best honors all the SIFT-based distance measurements between
-images. In practice there are often cases where there is a break in
+images. In practice there is often a break in
 the chain of images, meaning that no SIFT matches are found between
@@
 $A$ matrix and observations to the $\vec{\gamma}$ vector that contain
-the original noisy $x$ and $y$ distance estimates generated by the
-localization algorithm \cite{chen2010indoor, liu2010indoor}. Another
-way to do this is to add rows for all neighboring pairs of images and
-solve a weighted least squares problem where the SIFT distances are
-given a higher weight i.e. 1, and the noisy distances generated by the
-localization algorithm \cite{chen2010indoor, liu2010indoor} are given
-a smaller weight i.e. 0.01.
+the original noisy $x$ and $y$ distance estimates from the original
+camera poses. Another way to do this is to add rows for all
+neighboring pairs of images and solve a weighted least squares problem
+where the SIFT distances are given a higher weight i.e. 1, and the
+noisy distances generated by the original camera poses
+\cite{chen2010indoor, liu2010indoor} are given a smaller weight
+e.g. 0.01.
 
@@
 but at an angle with respect to horizontal floors and ceilings. This
-is depicted in Figure \ref{fig:projectionAngles}. These oblique camera
-angles translate into textures that span extremely large areas once
-projected. Using the tile-based texture mapping criteria from Figure
-\ref{fig:scoringFunction}, such projections have high or low scores
-depending on the location on the plane, as shown in Figure
-\ref{fig:projectionAngles}(b). The tiling approach in Section
-\ref{sec:simpleTextureMapping} is thus a good choice for texturing
-floors and ceilings, as it uses the parts of image projections that
-are viable choices for their respective plane locations, e.g. areas
-near point A in Figure \ref{fig:projectionAngles}(b), but not near
-point B.
+is depicted for wall and ceiling planes in Figures
+\ref{fig:projectionAngles}(a) and \ref{fig:projectionAngles}(b)
+respectively. These oblique camera angles for ceilings translate into
+textures that span extremely large areas once projected, as shown in
+Figure \ref{fig:projectionAngles}(b). Using the tile-based texture
+mapping criteria from Figure \ref{fig:scoringFunction}, such
+projections have highly varying scores depending on the location on
+the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
+tiling approach in Section \ref{sec:simpleTextureMapping} is a reasonable
+choice for texturing floors and ceilings, as it uses the parts of
+image projections that are viable choices for their respective plane
+locations, e.g. areas near point A in Figure
+\ref{fig:projectionAngles}(b), but not near point B.
 
@@
 fronto-parallel projections. As a result, for each tile on a wall
-plane, the cost function of Figure \ref{fig:scoringFunction} is
+plane, the scoring function of Figure \ref{fig:scoringFunction} is
 relatively flat with respect to a large number of captured images, as
-they are all more or less head on. Thus it is conceivable to use a
-different texturing strategy for walls so as to minimize the visible
-seams for texture mapped planes. One way to do so is to choose the
-smallest possible set of images that (a) covers the entire plane and
-(b) minimizes the amount of visible seams. A straigntforward cost
-function that accomplishes the latter is the Sum of Squared pixel
-Differences (SSD) in overlapping regions between all pairs of images,
-after they have been aligned as described in Section
+they are all more or less head on. Thus, the scoring function is less
+signifcant for walls, and it is conceivable to use a different
+texturing strategy for them so as to minimize visible seams in texture
+mapped planes. This can be done by choosing the smallest possible set
+of images that (a) covers the entire plane and (b) minimizes the
+amount of visible seams between them. A straigntforward cost function
+that accomplishes the latter is the Sum of Squared Differences (SSD)
+of pixels in overlapping regions between all pairs of images, after
+they have been rotated as described in Section
 \ref{sec:projectionAndRotation}. Minimizing this cost function
@@
 graph. Directed edges are placed in the graph from left to right
-between images that overlap. The weights of these edges are determined
+between overlapping images. The weights of these edges are determined
 by the SSD cost function. Next, we add two artificial nodes, one start
@@
 We now solve the shortest path problem from the start node to the end
-node. This provides a set of images completely covering the plane
+node. This results in a set of images completely covering the plane
 horizontally, while minimizing the cost of seams between images.
@@
 shortest path solution such that they have higher cost than all other
-edges in our DAG, and solve for a new shortest path. This ensures that
+edges in the DAG, and solve for a new shortest path. This ensures that
 these edges are not chosen again unless they are the only available
@@
   texturing where images overlap, as blending will be discussed in the
-  next section.}.
-This is especially evident when comparing the posters in the images, which have clear misalignment over seams in Figure \ref{fig:compareAll}(c), but are much more aligned in Figure \ref{fig:compareAll}(d).
-This is because the seam minimization approach
-directly reduces the cost of each image boundary, while the tile
-caching method uses a scoring function that only approximates this
-effect. Furthermore, seam minimization guarantees the best selection
-of images, while the sequential tile caching method may select images
-early on that turn out to be poor choices once subsequent tiles have
-been processed. The seam minimization approach is also far less
-intensive in terms of memory usage and runtime, as it does not require
-discretizing planes or images.
+  next section.}. This is especially evident when comparing the
+posters in the images, which have clear misalignment over seams in
+Figure \ref{fig:compareAll}(c), but are much more aligned in Figure
+\ref{fig:compareAll}(d). This is because the seam minimization
+approach directly reduces the cost of each image boundary, while the
+tile caching method uses a scoring function that only approximates
+this effect. Furthermore, seam minimization guarantees the best
+selection of images, while the sequential tile caching method may
+select images early on that turn out to be poor choices once
+subsequent tiles have been processed. The seam minimization approach
+is also far less intensive in terms of memory usage and runtime, both
+during texture generation and rendering, as it does not require
+discretizing planes or images\footnote{ For the seam minimization
+  process, it is important that images only contain content that
+  should be mapped onto the target plane in question. The tiling
+  approach checks occlusion for each tile as it is being textured,
+  whereas the seam minimization approach uses entire images.
+  Occlusion checks thus need to be performed over the entirety of each
+  image to determine available areas for texture mapping a given
+  plane.  }.
 
@@
 We now apply the same blending process to the two texturing methods:
-localization refinement followed by either tile caching or seam
+image alignment followed by either tile caching or seam
 minimization.
@@
 also presented a seam minimization texturing method that produces
-seamless textures on vertical planes where multiple head-on images are
+seamless textures on planes where multiple head-on images are
 available. Each of these approaches is highly modular, and easily
@@
   \caption{Examples of our final texture mapping output for (a) walls,
-    (b) a ceiling, (c) an entire floor, (d) a full model}
+    (b) a ceiling, (c) an entire floor, (d) a full model.}
   \label{fig:results}
@@
 
-\appendix
-\section*{Appendix A. Occlusion Masking}
-\label{sec:occlusionMasking}
-For the seam minimization process, it is important that images contain
-only content that should be mapped onto the target plane in
-question. The tiling approach checks occlusion for each tile as it is
-being textured, whereas the seam minimization approach uses entire
-images.  Occlusion checks thus need to be performed over the entirety
-of each image to determine available areas for texture mapping.
-
-Fortunately, by virtue of our indoor environments, the vast majority
-of surface geometry is either horizontal or vertical, with high
-amounts of right angles. This means that after masking out occluded
-areas, image projections will remain largely rectangular. We can be
-efficient by recursively splitting each image into rectangular pieces,
-and performing the same occlusion checks used in the tiling process
-where needed. To occlude out rectangular pieces, their texture is
-removed, as untextured areas are never used for texture mapping.
-
 \end{document}

### 2012-12-17 spie/_region_.tex
added spie dir

--- 2012-06-29 3dimpvt/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\message{ !name(paper.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}
 
@@
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+ \cvprfinalcopy % *** Uncomment this line for the final submission
 
-\def\cvprPaperID{****} % *** Enter the 3DIMPVT Paper ID here
+\def\cvprPaperID{84} % *** Enter the 3DIMPVT Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 
+\message{ !name(paper.tex) !offset(-3) }
+
 %%%%%%%%% TITLE
-\title{Texture Mapping 3D Models of Indoor Environments with Noisy
+\title{Texture Mapping 3D Planar Models of Indoor Environments with Noisy
   Camera Poses}
 
-\author{First Author\\
-  Institution1\\
-  Institution1 address\\
-  {\tt\small firstauthor@i1.org}
+\author{Peter Cheng\\
+  UC Berkeley
+  \and
+  Michael Anderson
+  \and
+  Stewart He
+  \and
+  Avideh Zakhor
+  %Institution1 address\\
+  %{\tt\small firstauthor@i1.org}
   % For a paper whose authors are all at the same institution, omit
@@
   % home page, not both
-  \and
-  Second Author\\
-  Institution2\\
-  First line of institution2 address\\
-  {\small\url{http://www.author.org/~second}} }
-
+  %\and
+  %Second Author\\
+  %\and
+  %Third Author\\
+  %\and
+  %Fourth Author\\
+%  Institution2\\
+%  First line of institution2 address\\
+%  {\small\url{http://www.author.org/~second}} }
+}
 \maketitle
@@
   modeling systems. Camera pose recovery in such systems often suffers
-  from inaccuracies, resulting in visible discontinuties when
+  from inaccuracies, resulting in visible discontinuities when
   successive images are projected adjacently onto a plane for
@@
 the environment's geometry. An indoor modeling system must be able to
-recover camera poses within an environment while simulatenously
+recover camera poses within an environment while simultaneously
 reconstructing the 3D structure of the environment itself
@@
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_naive.jpg}}
+    height=0.97in]{wall2_naive.pdf}}
 
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_cache.jpg}}
+    height=0.97in]{wall2_cache.pdf}}
 
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_cache_shift.jpg}}
+    height=0.97in]{wall2_cache_shift.pdf}}
 
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_dynprog_noblend.jpg}}
+    height=0.97in]{wall2_dynprog_noblend.pdf}}
 
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_cache_shift_blend.jpg}}
+    height=0.97in]{wall2_cache_shift_blend.pdf}}
 
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_dynprog.jpg}}
+    height=0.97in]{wall2_dynprog.pdf}}
   \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
@@
     refinement algorithm from \cite{chen2010indoor} and (b) image
-    mosaicing}
+    mosaicing.}
   \label{fig:mosaic3D}
@@
   \centering
-  \includegraphics[width=3.5in]{pipeline.pdf}
+  \includegraphics[width=3in]{pipeline.pdf}
   \caption{Our proposed method for seamless texture mapping.}
@@
 mapping. Our approach consists of 4 steps, as seen in Figure
-\ref{fig:pipeline}.  First, we choose a subset of $M$ images to work
-with via the direct mapping approach of Section
-\ref{sec:directMapping}. Next, we project these images onto the plane
-and perform rotation and shifting in order to maximize SIFT feature
-matches in overlapping areas between these projections. We then select
-which textures to be used either with the tile caching method from
-Section \ref{sec:mappingWithCaching}, or with the more specialized
-method to be described in Section \ref{sec:seamMinimization}. This
-choice depends on the availability of head-on images for a given
-plane. We then finish by applying linear alpha blending to smooth out
-any remaining seams.
+\ref{fig:pipeline}.  First, we project all images onto the plane and
+rotate them for verticality. Next,we perform 2D shifting in order to
+maximize SIFT feature matches in overlapping areas between these
+projections. We then select which textures to be used either with the
+tile caching method from Section \ref{sec:mappingWithCaching}, or with
+the more specialized method to be described in Section
+\ref{sec:seamMinimization}. This choice depends on the availability of
+head-on images for a given plane. We then finish by applying linear
+alpha blending to smooth out any remaining seams.
 
@@
 corresponding to doors, wall panels, rectangular frames, etc. If
-features in the area are not vertical, e.g. for floors and
-ceilings, this step is skipped.
+features in the area are not vertical, e.g. for floors and ceilings,
+this step is skipped.
 
@@
 images 1 and 3, images 2 and 3, etc.
-
 \[
@@
 \]
-
 If only relative distances between images are included then there is
@@
 that best honors all the SIFT-based distance measurements between
-images. In practice there is often a break in
-the chain of images, meaning that no SIFT matches are found between
-one segment of the plane and another. In this case we add rows to the
-$A$ matrix and observations to the $\vec{\gamma}$ vector that contain
-the original noisy $x$ and $y$ distance estimates from the original
-camera poses. Another way to do this is to add rows for all
-neighboring pairs of images and solve a weighted least squares problem
-where the SIFT distances are given a higher weight i.e. 1, and the
-noisy distances generated by the original camera poses
-\cite{chen2010indoor, liu2010indoor} are given a smaller weight
-e.g. 0.01.
+images. In practice there is often a break in the chain of images,
+meaning that no SIFT matches are found between one segment of the
+plane and another. In this case we add rows to the $A$ matrix and
+observations to the $\vec{\gamma}$ vector that contain the original
+noisy $x$ and $y$ distance estimates from the original camera
+poses. Another way to do this is to add rows for all neighboring pairs
+of images and solve a weighted least squares problem where the SIFT
+distances are given a higher weight i.e. 1, and the noisy distances
+generated by the original camera poses \cite{chen2010indoor,
+  liu2010indoor} are given a smaller weight e.g. 0.01.
 
@@
 the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
-tiling approach in Section \ref{sec:simpleTextureMapping} is a reasonable
-choice for texturing floors and ceilings, as it uses the parts of
-image projections that are viable choices for their respective plane
-locations, e.g. areas near point A in Figure
+tiling approach in Section \ref{sec:simpleTextureMapping} is a
+reasonable choice for texturing floors and ceilings, as it uses the
+parts of image projections that are viable choices for their
+respective plane locations, e.g. areas near point A in Figure
 \ref{fig:projectionAngles}(b), but not near point B.
@@
 they are all more or less head on. Thus, the scoring function is less
-signifcant for walls, and it is conceivable to use a different
+significant for walls, and it is conceivable to use a different
 texturing strategy for them so as to minimize visible seams in texture
@@
 of images that (a) covers the entire plane and (b) minimizes the
-amount of visible seams between them. A straigntforward cost function
+amount of visible seams between them. A straightforward cost function
 that accomplishes the latter is the Sum of Squared Differences (SSD)
@@
 of minimizing the cost function between chosen images.  This is a
-complex problem, though we can take a number of steps to simplify
-it. Given that wall-texture candidate images are taken from more or
-less head-on angles, and assuming only minor rotations are made in
-Section \ref{sec:projectionAndRotation}, we can reason that their
-projections onto the plane are approximately rectangular. By cropping
-them all to be rectangular, as shown in Figure
-\ref{fig:projectionAngles}(c), our problem becomes the conceptually
-simpler one of filling a polygon with rectangles, such that the sum of
-all costs between each pair of rectangles is minimal. We thus also
-retain the advantages of working with rectangular units, as explained
-in Section \ref{sec:simpleTextureMapping}.
+complex problem, though we can take a number of steps to simplify it.
+
+Given that wall-texture candidate images are taken from more or less
+head-on angles, and assuming only minor rotations are made in Section
+\ref{sec:projectionAndRotation}, we can reason that their projections
+onto the plane are approximately rectangular. By cropping them all to
+be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
+problem becomes the conceptually simpler one of filling a polygon with
+rectangles, such that the sum of all costs between each pair of
+rectangles is minimal. We thus also retain the advantages of working
+with rectangular units, as explained in Section
+\ref{sec:simpleTextureMapping}.
 
@@
   \includegraphics[width=3in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process.}
+  \caption{DAG construction for the image selection process. \\}
   \label{fig:dagCreation}
@@
 during texture generation and rendering, as it does not require
-discretizing planes or images\footnote{ For the seam minimization
-  process, it is important that images only contain content that
-  should be mapped onto the target plane in question. The tiling
-  approach checks occlusion for each tile as it is being textured,
-  whereas the seam minimization approach uses entire images.
-  Occlusion checks thus need to be performed over the entirety of each
-  image to determine available areas for texture mapping a given
-  plane.  }.
+discretizing planes or images\footnote {For the seam minimization
+  approach, occlusion checks are performed over the entirety of each
+  image to determine available areas for texture mapping. Since indoor
+  environments mostly consist of vertical or horizontal surfaces with
+  high amounts of right angles, image projections remain largely
+  rectangular after masking out occluded areas. Therefore, as a
+  preprocessing step, we can recursively split each image into
+  rectangular pieces and check for occlusions in a similar manner as
+  in the tiling process.  }.
 
@@
 We now apply the same blending process to the two texturing methods:
-image alignment followed by either tile caching or seam
-minimization.
+image alignment followed by either tile caching or seam minimization.
 
@@
 already ensured overlap between images. To enforce consistent blending
-however, we add a minimuum required overlap distance while solving the
+however, we add a minimum required overlap distance while solving the
 shortest path problem in Section
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
   \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in]{4thfloor8.jpg}}
+  ~~~~~~
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{floorcropped.jpg}}
-
+  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
+  ~~~~~~~~
   \centering \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
   \caption{Examples of our final texture mapping output for (a) walls,
-    (b) a ceiling, (c) an entire floor, (d) a full model.}
+    (b) ceilings, (c) an entire floor, (d) a full model.}
   \label{fig:results}
-\end{figure}
+\end{figure*}
 
@@
 
+\message{ !name(paper.tex) !offset(-5) }
+
 \end{document}

### 2012-12-23 spie/_region_.tex
starting spie stuff

--- 2012-06-29 3dimpvt/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\message{ !name(paper.tex)}%  article.tex (Version 3.3, released 19 January 2008)
+%  Article to demonstrate format for SPIE Proceedings
+%  Special instructions are included in this file after the
+%  symbol %>>>>
+%  Numerous commands are commented out, but included to show how
+%  to effect various options, e.g., to print page numbers, etc.
+%  This LaTeX source file is composed for LaTeX2e.
 
-\usepackage{cvpr} \usepackage{times} \usepackage{epsfig}
-\usepackage{graphicx} \usepackage{amsmath} \usepackage{amssymb}
-\usepackage{subfig}
+%  The following commands have been added in the SPIE class 
+%  file (spie.cls) and will not be understood in other classes:
+%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
+%  The bibliography style file is called spiebib.bst, 
+%  which replaces the standard style unstr.bst.
 
-% Include other packages here, before hyperref.
+\documentclass[]{spie}  %>>> use for US letter paper
+%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
+%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
+%% \addtolength{\voffset}{9mm}   %>>> moves text field down
+%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
+%  The following command loads a graphics package to include images 
+%  in the document. It may be necessary to specify a DVI driver option,
+%  e.g., [dvips], but that may be inappropriate for some LaTeX 
+%  installations. 
+\usepackage[]{graphicx}
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first
-% latex run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+%>>>> The author is responsible for formatting the 
+%  author list and their institutions.  Use  \skiplinehalf 
+%  to separate author list from addresses and between each address.
+%  The correspondence between each author and his/her address
+%  can be indicated with a superscript in italics, 
+%  which is easily obtained with \supit{}.
 
-\def\cvprPaperID{****} % *** Enter the 3DIMPVT Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+\author{Peter Cheng, Michael Anderson, Stewart He, Avideh Zakhor
+\skiplinehalf
+University of California, Berkeley ; \\
+}
 
-% Pages are numbered in submission mode, and unnumbered in
-% camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+%>>>> Further information about the authors, other than their 
+%  institution and addresses, should be included as a footnote, 
+%  which is facilitated by the \authorinfo{} command.
+
+\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
+%%>>>> when using amstex, you need to use @@ instead of @
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%>>>> uncomment following for page numbers
+% \pagestyle{plain}    
+%>>>> uncomment following to start page numbering at 301 
+%\setcounter{page}{301}
+
   \begin{document}
 
-%%%%%%%%% TITLE
-\title{Texture Mapping 3D Models of Indoor Environments with Noisy
-  Camera Poses}
+\message{ !name(paper.tex) !offset(-42) }
+\documentclass[]{spie}  %>>> use for US letter paper
+%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
+%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
+%% \addtolength{\voffset}{9mm}   %>>> moves text field down
+%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
+%  The following command loads a graphics package to include images 
+%  in the document. It may be necessary to specify a DVI driver option,
+%  e.g., [dvips], but that may be inappropriate for some LaTeX 
+%  installations. 
+\usepackage[]{graphicx}
 
-\author{First Author\\
-  Institution1\\
-  Institution1 address\\
-  {\tt\small firstauthor@i1.org}
-  % For a paper whose authors are all at the same institution, omit
-  % the following lines up until the closing ``}''.  Additional
-  % authors and addresses can be added with ``\and'', just like the
-  % second author.  To save space, use either the email address or
-  % home page, not both
-  \and
-  Second Author\\
-  Institution2\\
-  First line of institution2 address\\
-  {\small\url{http://www.author.org/~second}} }
+\title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
 
-\maketitle
-% \thispagestyle{empty}
+%>>>> The author is responsible for formatting the 
+%  author list and their institutions.  Use  \skiplinehalf 
+%  to separate author list from addresses and between each address.
+%  The correspondence between each author and his/her address
+%  can be indicated with a superscript in italics, 
+%  which is easily obtained with \supit{}.
 
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  Automated 3D modeling of building interiors is useful in
-  applications such as virtual reality and environment
-  mapping. Applying textures to these models is an important step in
-  generating photorealistic visualizations of data collected by
-  modeling systems. Camera pose recovery in such systems often suffers
-  from inaccuracies, resulting in visible discontinuties when
-  successive images are projected adjacently onto a plane for
-  texturing. We propose two approaches to reduce discontinuities in
-  texture mapping 3D models made of planar surfaces. The first one is
-  tile based and can be used for images and planes at arbitrary angles
-  relative to each other. The second one results in a more seamless
-  texture, but is only applicable where camera axes for images are
-  closely aligned with plane normals of the surfaces to be
-  textured. The effectiveness of our approaches are demonstrated on
-  two indoor datasets.
-\end{abstract}
+\author{Peter Cheng, Michael Anderson, Stewart He, Avideh Zakhor
+\skiplinehalf
+University of California, Berkeley ; \\
+}
 
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:introduction}
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and as
-such, automated 3D site modeling has garnered much interest in recent
-years.
+%>>>> Further information about the authors, other than their 
+%  institution and addresses, should be included as a footnote, 
+%  which is facilitated by the \authorinfo{} command.
 
-The first step in automated 3D modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-recover camera poses within an environment while simulatenously
-reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
-known as the simultaneous localization and mapping (SLAM) problem, and
-is generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment.
+\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
+%%>>>> when using amstex, you need to use @@ instead of @
 
-Mounting such devices on a platform carried by an ambulatory human
-provides unique advantages over vehicular-based systems on wheels in
-terms of agility and portability, but can also result in larger
-localization error \cite{liu2010indoor}. As a result, common methods
-for texture mapping generally produce poor results.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%>>>> uncomment following for page numbers
+% \pagestyle{plain}    
+%>>>> uncomment following to start page numbering at 301 
+%\setcounter{page}{301}
 
-In this paper, we present a number of approaches to texture mapping 3D
-models of indoor environments made of planar surfaces in the presence
-of uncertainty and noise in camera poses. In particular, we consider
-data obtained from a human-operated backpack system with a number of
-laser range scanners as well as 2 cameras facing left and right, each
-equipped with fisheye lenses reaching an approximately 180$^{\circ}$
-field of view and taking photos at a rate of 5 Hz. Applying multiple
-localization and loop-closure algorithms on the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, the backpack is localized\footnote{In this paper, we
-  use the terms localization and pose recovery interchangeably, in
-  that they both refer to recovering position and orientation.}  over
-its data collection period. This requires recovering the 6 degrees of
-freedom for the backpack as well as the cameras rigidly mounted on
-it. Once this is complete, the data from the laser range scanners is
-used to generate a 3D point cloud of the surrounding environment, from which a
-3D planar model is created \cite{sanchez2012point}. This model, consisting of 2D
-polygonal planes in 3D space, along with the set of images captured by
-the backpack's cameras and their noisy 3D poses, can be considered the
-input to our texture mapping problem.
-
-This problem straddles the fields of image-based localization
-refinement as well as image alignment and mosaicing, and thus our
-proposed solution shares many similarities with past research in those
-areas, which will be examined in Section
-\ref{sec:existingApproaches}. However, we can exploit known
-approximate camera poses as well as the 3D geometry of the environment
-to more accurately and efficiently texture the planes.
-
-The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} describes two variants of a tile-based
-mapping approach and their shortcomings.  Section
-\ref{sec:existingApproaches} discusses past research in related
-fields, demonstrates two previous attempts at improving texture
-alignment, and exhibits their inadequacies for our datasets. Section
-\ref{sec:proposedApproach} presents our proposed seam minimization
-approach to texture mapping. Section \ref{sec:resultsAndConclusions}
-contains results and conclusions.
-
-In all subsequent sections, we discuss the process of texture mapping
-a single plane, as the texturing of each plane is independent and can
-be completed in parallel.
-
-\section{Tile-Based Texture Mapping}
-\label{sec:simpleTextureMapping}
-\begin{figure}
-  \centering
-  \includegraphics[height=2in]{Projection.pdf}
-  \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera
-    matrices $P_{1..M}$. }
-  \label{fig:projection}
-\end{figure}
-
-The geometry of the texture mapping process for a plane is shown in
-Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images to texture the target
-plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
-translates a 3D point in the world coordinate system to a 2D point or
-pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
-the camera's intrinsic parameters, such as focal length and image
-center, as well as extrinsic parameters which specify the rotation and
-translation of the camera's position in 3D world coordinates at the
-time that image $i$ is taken. These extrinsic parameters are
-determined by the backpack hardware and localization algorithms
-\cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are quite
-noisy.
-
-Because the backpack system takes photos at a rate of 5 Hz, thousands
-of images are available for texturing each plane. Our goal in creating
-a texture mapping process is to decide which of these images should be
-used, and where their contents should map onto the texture, in order
-to eliminate any visual discontinuities or seams that would suggest
-that the plane's final texture is not composed of a single continuous
-image.
-
-\subsection{Direct Mapping}
-\label{sec:directMapping}
-
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square tiles,
-generally about 5 pixels across, and choosing an image to texture each
-tile.
-
-We choose to work with rectangular units to ensure that borders
-between any two distinct images in the final texture are either
-horizontal or vertical. Since most environmental features inside
-buildings are horizontal or vertical, any seams in our texture
-intersect them minimally and are likely to be less noticeable.
-
-In order to select an image for texturing a tile $t$, we must first
-gather a list of candidate images that contain all four of its
-corners, which we can quickly check by projecting $t$ into each image
-using the $P_i$ camera matrices. Furthermore, each candidate image
-must have been taken at a time when its camera had a clear
-line-of-sight to $t$, which can be calculated using standard
-ray-polygon intersection tests between the camera location, the center
-of $t$, and every other plane \cite{rayintersection}.
-
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image. Since camera
-pose errors compound over distance, we wish to minimize the distance
-between cameras and the plane they texture. Additionally, we desire
-images that are projected perpendicularly onto the plane, maximizing
-the resolution and amount of useful texture available in their
-projections, as well as minimizing any parallax effects. In other
-words, we wish to minimize the angle between the plane normal and the
-camera axis for images selected for texture mapping. These two
-criteria can be met by maximizing the function $\frac{1}{d} (-1 \cdot
-\vec{c}) \cdot \vec{n}$ as shown in Figure
-\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
-the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-the directions of the plane's normal and the camera axis respectively.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=1.5in]{scoringFunction.jpg}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by
-    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-    \cdot \vec{n}$}
-  \label{fig:scoringFunction}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_naive.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_cache.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_cache_shift.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_dynprog_noblend.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_cache_shift_blend.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.9in]{wall2_dynprog.jpg}}
-  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
-    with caching after image alignment. (d) Seam minimization after
-    image alignment). (e) same as (c) with blending. (f) same as (d)
-    with blending.}
-  \label{fig:compareAll}
-\end{figure}
-
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but overall results in
-many image boundaries with abrupt discontinuities, due to significant
-misalignment between images, as a result of camera pose inaccuracies.
-
-\subsection{Mapping with Caching}
-\label{sec:mappingWithCaching}
-Since discontinuities occur where adjacent tiles select non-aligned
-images, it makes sense to take into account image selections made by
-neighboring tiles while texture mapping a given tile. By using the
-same image across tile boundaries, we can eliminate a discontinuity
-altogether. If this is not possible because a tile is not visible in
-images chosen by its neighbors, using similar images across tile
-boundaries also leads to less noticeable discontinuities.
-
-Similar to a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set. The first subset of images is
-those selected by adjacent tiles that have already been textured. We
-must first check which of these images can map to $t$, and then of
-those, we make a choice according to the scoring function in Figure
-\ref{fig:scoringFunction}. Before reusing this image, we ensure it
-meets the criteria $\alpha < 45^\circ$, in order to be considered a
-viable image, with $\alpha$ as the camera angle as shown in Figure
-\ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check the
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar. Again, if no viable image is found
-according to the same criteria, we search the entire set of candidate
-images, selecting based on the same scoring function from Figure
-\ref{fig:scoringFunction}.
-
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(b). As compared to Figure
-\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
-amount of remaining seams suggests that image selection alone cannot
-produce seamless textures. Camera matrices, or the image projections
-themselves have to be adjusted in order to reliably generate clean
-textures.
-
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-In order to produce seamless texture mapping, either camera matrices
-need to be refined such that their localization is pixel accurate, or
-image stitching techniques need to be applied to provide this
-illusion.
-
-Image projections can be aligned by refining their noisy camera poses,
-using image correspondences to adjust each image's camera matrix over
-6 degrees of freedom (DOF) \cite{coorg1997matching, liu2010indoor,
-  shum2000systems, szeliski1997creating}. Applying such approaches to
-our datasets however results in error accumulation and drift as shown
-in Figure \ref{fig:mosaic3D}(a), as well as high complexity and
-runtime \cite{liu2010indoor}.
-
-Another common approach to image alignment is to
-iteratively match images on intensity differences in selected patches,
-often in a spatial hierarchy \cite{hager1998efficient,
-  lucas1981iterative, shum2000systems, szeliski2006image}. Another
-widely-used approach is to perform feature matching, which requires
-the detection of visual features and their existence in multiple
-images \cite{brown2007automatic, cho2003automatic,
-  mikolajczyk2005performance, szeliski2006image,
-  yun2003comprehensive}. Notably, both approaches rely on the presence
-of multiple visual references, as when texturing detailed objects at
-high resolutions \cite{bernardinimultiplescans, wangmultipleviews}, or
-when creating large scene panoramas \cite{agarwalapanoramas,
-  bernardinimultiplescans, debevecviewdependent,
-  snavelyphototourism}. In contrast, our indoor datasets have a high
-prevalence of bare walls and ceilings, resulting in few reference
-points that can be used to judge alignment.
-
-Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not
-accurate. For example, when matching a long chain of images through
-homography, a pixel in the $nth$ image must be translated into the
-first image's coordinates by multiplying by the $3\times3$ matrix $H_1
-H_2 H_3 ... H_n$. Any error in one of these homography matrices is
-propagated to all further images, resulting in drift. Figure
-\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
-package, which performs homography-based image mosaicing
-\cite{autostitch}. Even with many features spread across this plane,
-the mosaicing produces errors that causes straight lines to appear as
-waves on the plane, despite the fact that it is generated after
-careful hand tuning. Many planes with fewer features simply failed
-outright using this approach.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm from \cite{chen2010indoor} and (b) image
-    mosaicing}
-  \label{fig:mosaic3D}
-\end{figure}
-
-\section{Seamless Texture Mapping}
-\label{sec:proposedApproach}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3.5in]{pipeline.pdf}
-  \caption{Our proposed method for seamless texture mapping.}
-  \label{fig:pipeline}
-\end{figure}
-
-In this section, we describe our proposed method for seamless texture
-mapping. Our approach consists of 4 steps, as seen in Figure
-\ref{fig:pipeline}.  First, we choose a subset of $M$ images to work
-with via the direct mapping approach of Section
-\ref{sec:directMapping}. Next, we project these images onto the plane
-and perform rotation and shifting in order to maximize SIFT feature
-matches in overlapping areas between these projections. We then select
-which textures to be used either with the tile caching method from
-Section \ref{sec:mappingWithCaching}, or with the more specialized
-method to be described in Section \ref{sec:seamMinimization}. This
-choice depends on the availability of head-on images for a given
-plane. We then finish by applying linear alpha blending to smooth out
-any remaining seams.
-
-\subsection{Image Rotation}
-\label{sec:projectionAndRotation}
-We begin with the projection of all images onto the plane. This is
-done in the same way as in Section
-\ref{sec:simpleTextureMapping}. Rather than work with all 6 DOF, which
-is computationally intensive, we choose to work only in two
-dimensions, performing 2D rotations and translations on the image
-projections, as errors in either lead to the greatest discontinuities.
-
-We perform rotations using Hough transforms, which detect the presence
-and orientation of linear features in our images. Rather than match
-the orientation of such features in each image, we simply apply
-rotations such that the strongest near-vertical features are made
-completely vertical. This is effective for vertical planes in indoor
-models, since they usually consist of parallel vertical lines
-corresponding to doors, wall panels, rectangular frames, etc. If
-features in the area are not vertical, e.g. for floors and
-ceilings, this step is skipped.
-
-\subsection{Image Shifting}
-\label{sec:robustSIFTFeatureMatching}
-Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images. We use
-SIFT features for their high detection rate, and choose to use feature
-alignment rather than intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lai1999robust,
-  lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-
-SIFT matches determine $d^x$ and $d^y$ distances between each pair of
-features for two images on the plane, though these distances may not
-always be the same for different features. Since indoor environments
-often contain repetitive features such as floor tiles or doors, we
-need to ensure that SIFT-based distances are reliable. In order to
-mitigate the effect of incorrect matches and outliers, the RANSAC
-framework \cite{fischler1981random} is used for a robust estimate of
-the optimal $d^x_{i,j}$ and $d^y_{i,j}$ distances between two images
-$i$ and $j$. The RANSAC framework handles the consensus-building
-machinery, and requires a fitting function and a distance
-function. For this application, the fitting function simply finds the
-average distance between matches in a pair of images. The distance
-function for a pair of points is chosen to be the difference between
-those points' SIFT match distance and the average distance computed by
-the fitting function. We use a 10 pixel outlier threshold, so that
-SIFT matches are labeled as outliers if their horizontal or vertical
-distances are not within 10 pixels of the average distance computed by
-the fitting function.
-
-We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
-of images to refine their positions using least squares. Recall that
-there are a total of $M^{2}$ possible pairs of images, though we only
-generate distances between images that overlap at SIFT feature
-points. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
-
-\[\vec{\beta} =
-\begin{pmatrix}
-  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
-\end{pmatrix}
-\]
-
-The $N \times (M+1)$ dimensional matrix $A$ is constructed with one
-row for each pair of images with measured distances produced by the
-SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the
-columns corresponding to the two images in the pair. For example, the
-matrix below indicates a SIFT-based distance between images 1 and 2,
-images 1 and 3, images 2 and 3, etc.
-
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & \cdots & 0 & 0\\
-  -1 & 0 & 1 & \cdots & 0 & 0\\
-  0 & -1 & 1 & \cdots & 0 & 0\\
-  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
-  0 & 0 & 0 & \cdots & 1 & 0 \\
-  0 & 0 & 0 & \cdots & -1 & 1 \\
-  1 & 0 & 0 & \cdots & 0 & 0 \\
-\end{pmatrix}
-\]
-
-If only relative distances between images are included then there is
-no way to determine the absolute location of any of the images and the
-matrix becomes rank deficient. To fix this we choose the first image
-to serve as the anchor for the rest, meaning all the absolute
-distances are based on its original location. This is done by adding a
-row with a $1$ in the first column and the rest zeros.
-
-Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
-constructed using the SIFT-based distances generated earlier in the
-RANSAC matching stage. The last element in the observation vector is
-the location of the first image determined by its original noisy
-localization, from \cite{chen2010indoor, liu2010indoor}. Thus
-$\vec{\gamma}$ can be written as:
-
-\[
-\vec{\gamma}^T =
-\begin{pmatrix}
-  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
-\end{pmatrix}
-\]
-
-The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
-\vec{\gamma}||_2^2$ results in a set of image locations on the plane
-that best honors all the SIFT-based distance measurements between
-images. In practice there is often a break in
-the chain of images, meaning that no SIFT matches are found between
-one segment of the plane and another. In this case we add rows to the
-$A$ matrix and observations to the $\vec{\gamma}$ vector that contain
-the original noisy $x$ and $y$ distance estimates from the original
-camera poses. Another way to do this is to add rows for all
-neighboring pairs of images and solve a weighted least squares problem
-where the SIFT distances are given a higher weight i.e. 1, and the
-noisy distances generated by the original camera poses
-\cite{chen2010indoor, liu2010indoor} are given a smaller weight
-e.g. 0.01.
-
-After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and match each other
-with far greater accuracy. Applying the tile caching method from
-Section \ref{sec:mappingWithCaching} on these rotated and shifted
-images results in the significant improvements shown in Figure
-\ref{fig:compareAll}(c), as compared to Figure
-\ref{fig:compareAll}(b).
-
-\subsection{Seam Minimization}
-\label{sec:seamMinimization}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a) Undistorted fisheye images for vertical planes are
-    tilted, but their effective camera axis is more or less normal to
-    the plane. (b) The effective camera axis for ceilings is at an
-    angle with respect to the plane normal. (c) Wall images are
-    cropped to be rectangular.}
-  \label{fig:projectionAngles}
-\end{figure}
-
-As mentioned earlier, the mobile backpack system used to capture data
-in this paper contains 2 cameras with $180^\circ$ fisheye lenses
-facing to the right and left. Since most human operators do not carry
-the backpack in a perfectly upright position and are bent forwards at
-15 to 20 degrees with respect to the vertical direction, the
-undistorted fisheye images are head on with respect to vertical walls,
-but at an angle with respect to horizontal floors and ceilings. This
-is depicted for wall and ceiling planes in Figures
-\ref{fig:projectionAngles}(a) and \ref{fig:projectionAngles}(b)
-respectively. These oblique camera angles for ceilings translate into
-textures that span extremely large areas once projected, as shown in
-Figure \ref{fig:projectionAngles}(b). Using the tile-based texture
-mapping criteria from Figure \ref{fig:scoringFunction}, such
-projections have highly varying scores depending on the location on
-the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
-tiling approach in Section \ref{sec:simpleTextureMapping} is a reasonable
-choice for texturing floors and ceilings, as it uses the parts of
-image projections that are viable choices for their respective plane
-locations, e.g. areas near point A in Figure
-\ref{fig:projectionAngles}(b), but not near point B.
-
-For wall planes however, most images are taken from close distances
-and more or less head-on angles, resulting in higher resolution
-fronto-parallel projections. As a result, for each tile on a wall
-plane, the scoring function of Figure \ref{fig:scoringFunction} is
-relatively flat with respect to a large number of captured images, as
-they are all more or less head on. Thus, the scoring function is less
-signifcant for walls, and it is conceivable to use a different
-texturing strategy for them so as to minimize visible seams in texture
-mapped planes. This can be done by choosing the smallest possible set
-of images that (a) covers the entire plane and (b) minimizes the
-amount of visible seams between them. A straigntforward cost function
-that accomplishes the latter is the Sum of Squared Differences (SSD)
-of pixels in overlapping regions between all pairs of images, after
-they have been rotated as described in Section
-\ref{sec:projectionAndRotation}. Minimizing this cost function
-encourages image boundaries to occur either in featureless areas, such
-as bare walls, or in areas where images match extremely well.
-
-To cover the entirety of a plane, our problem can be defined as
-minimally covering a polygon i.e. the plane, using other polygons of
-arbitrary geometry i.e. image projections, with the added constraint
-of minimizing the cost function between chosen images.  This is a
-complex problem, though we can take a number of steps to simplify
-it. Given that wall-texture candidate images are taken from more or
-less head-on angles, and assuming only minor rotations are made in
-Section \ref{sec:projectionAndRotation}, we can reason that their
-projections onto the plane are approximately rectangular. By cropping
-them all to be rectangular, as shown in Figure
-\ref{fig:projectionAngles}(c), our problem becomes the conceptually
-simpler one of filling a polygon with rectangles, such that the sum of
-all costs between each pair of rectangles is minimal. We thus also
-retain the advantages of working with rectangular units, as explained
-in Section \ref{sec:simpleTextureMapping}.
-
-The location and orientation of the cameras and the fisheye lenses on
-the acquisition backpack is such that images nearly always contain the
-entirety of the floor to ceiling range of wall planes. Images are
-therefore rarely projected with one above another when texturing wall
-planes. In essence, we need only to ensure lateral coverage of wall
-planes, e.g. from left to right, as our images provide full vertical
-coverage themselves. We can thus construct a Directed Acyclic Graph
-(DAG) from the images, with edge costs defined by the SSD cost
-function, and solve a simple shortest path problem to find an optimal
-subset of images with regard to the cost function \cite{dijkstra}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process.}
-  \label{fig:dagCreation}
-\end{figure}
-
-Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a long hallway. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
-between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal cost $C_0$ to(from) all images that
-meet the left(right) border of the plane.
-
-We now solve the shortest path problem from the start node to the end
-node. This results in a set of images completely covering the plane
-horizontally, while minimizing the cost of seams between images.
-
-In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. To address this, we solve for
-a new shortest path after modifying the edges chosen by the original
-shortest path solution such that they have higher cost than all other
-edges in the DAG, and solve for a new shortest path. This ensures that
-these edges are not chosen again unless they are the only available
-option. Our second shortest path solution results in a new set of
-chosen images, of which we only retain those that cover areas not
-covered by the first set. This process can be repeated as many times
-as needed, until holes are no longer present. This method is not as
-optimal as a 2D-coverage solution would be, but it is a fast
-approximation, and adequately handles the few holes we encounter.
-
-With this completed, we have now mapped every location on the plane to
-at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. As seen in Figure
-\ref{fig:compareAll}(d), this seam minimization method has fewer
-visible discontinuities than Figure \ref{fig:compareAll}(c)
-corresponding to the tile caching approach\footnote{In Figure
-  \ref{fig:compareAll}(d), we arbitrarily chose one image for
-  texturing where images overlap, as blending will be discussed in the
-  next section.}. This is especially evident when comparing the
-posters in the images, which have clear misalignment over seams in
-Figure \ref{fig:compareAll}(c), but are much more aligned in Figure
-\ref{fig:compareAll}(d). This is because the seam minimization
-approach directly reduces the cost of each image boundary, while the
-tile caching method uses a scoring function that only approximates
-this effect. Furthermore, seam minimization guarantees the best
-selection of images, while the sequential tile caching method may
-select images early on that turn out to be poor choices once
-subsequent tiles have been processed. The seam minimization approach
-is also far less intensive in terms of memory usage and runtime, both
-during texture generation and rendering, as it does not require
-discretizing planes or images\footnote{ For the seam minimization
-  process, it is important that images only contain content that
-  should be mapped onto the target plane in question. The tiling
-  approach checks occlusion for each tile as it is being textured,
-  whereas the seam minimization approach uses entire images.
-  Occlusion checks thus need to be performed over the entirety of each
-  image to determine available areas for texture mapping a given
-  plane.  }.
-
-In the context of texturing an entire 3D planar model, we choose to
-apply the seam minimization approach on walls, due to its superior
-output when provided with head-on images. Floors and ceilings however,
-given their many images taken at oblique angles, are textured using
-the tile caching method.
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=6in]{pipelineimages.pdf}
-%   \caption{Textures corresponding to each step in our texture
-%   mapping pipeline.}
-%   \label{fig:pipelineimages}
-% \end{figure*}
-
-\subsection{Blending}
-\label{sec:blending}
-We now apply the same blending process to the two texturing methods:
-image alignment followed by either tile caching or seam
-minimization.
-
-Although the preprocessing steps and image selection in both methods
-attempt to minimize all mismatches between images, there are
-occasional unavoidable discontinuities in the final texture due to
-different lighting conditions or inaccuracies in planar geometry or
-projection. These can however be treated and smoothed over by applying
-alpha blending over image seams.  Whether the units we are blending
-are rectangularly-cropped images or rectangular tiles, we can apply
-the same blending procedure, as long as we have a guaranteed overlap
-between units to blend over.
-
-For the tile caching method, we can ensure overlap by texturing a
-larger tile than needed for display. For example, for a rendered tile
-$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size. For the seam minimization method, we have
-already ensured overlap between images. To enforce consistent blending
-however, we add a minimuum required overlap distance while solving the
-shortest path problem in Section
-\ref{sec:seamMinimization}. Additionally, if images overlap in a
-region greater than the overlap distance, we only apply blending over
-an area equal to the overlap distance.
-
-After blending pixels linearly across overlapping regions using alpha
-blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the seam minimization approach still exhibits better
-alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
-
-\section{Results and Conclusions}
-\label{sec:resultsAndConclusions}
-Examples of ceilings and floors textured with the tile caching
-approach, and walls textured with the seam minimization approach, are
-displayed in Figure \ref{fig:results}. High resolution texture
-comparisons, as well as a walkthrough of a fully textured 3D model are
-available in the accompanying video to this paper.
-
-In this paper, we have developed an approach to texture map models
-with noisy camera localization data. We are able to refine image
-locations based on feature matching, and robustly handle outliers. The
-tile-based mapping approach can be used to texture both simple
-rectangular walls as well as complex floor and ceiling geometry. We
-also presented a seam minimization texturing method that produces
-seamless textures on planes where multiple head-on images are
-available. Each of these approaches is highly modular, and easily
-tunable for different environments and acquisition hardware.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in]{4thfloor8.jpg}}
-
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{floorcropped.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) a ceiling, (c) an entire floor, (d) a full model.}
-  \label{fig:results}
-\end{figure}
-
-{\small \bibliographystyle{ieee} \bibliography{egbib} }
+\message{ !name(paper.tex) !offset(197) }
 

### 2012-12-23 spie/assets/_region_.tex
starting spie stuff

--- 2012-06-29 3dimpvt/paper.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\message{ !name(oldpaper.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}
 
@@
 
+\message{ !name(oldpaper.tex) !offset(-3) }
+
 %%%%%%%%% TITLE
-\title{Texture Mapping 3D Models of Indoor Environments with Noisy
+\title{Texture Mapping 3D Planar Models of Indoor Environments with Noisy
   Camera Poses}
 
-\author{First Author\\
-  Institution1\\
-  Institution1 address\\
-  {\tt\small firstauthor@i1.org}
-  % For a paper whose authors are all at the same institution, omit
-  % the following lines up until the closing ``}''.  Additional
-  % authors and addresses can be added with ``\and'', just like the
-  % second author.  To save space, use either the email address or
-  % home page, not both
-  \and
-  Second Author\\
-  Institution2\\
-  First line of institution2 address\\
-  {\small\url{http://www.author.org/~second}} }
-
+\author{Peter Cheng \hspace*{2em} Michael Anderson \hspace*{2em} Stewart He \hspace*{2em} Avideh Zakhor\\
+  UC Berkeley\\
+}
 \maketitle
@@
 Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images to texture the target
-plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
-translates a 3D point in the world coordinate system to a 2D point or
-pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
-the camera's intrinsic parameters, such as focal length and image
-center, as well as extrinsic parameters which specify the rotation and
-translation of the camera's position in 3D world coordinates at the
-time that image $i$ is taken. These extrinsic parameters are
-determined by the backpack hardware and localization algorithms
-\cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are quite
-noisy.
+with a set of $M$ images to texture the target plane. Each image has a
+camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
+world coordinate system to a 2D point or pixel in image $i$'s
+coordinates. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, such as focal length and image center, as well
+as extrinsic parameters which specify the rotation and translation of
+the camera's position in 3D world coordinates at the time that image
+$i$ is taken. These extrinsic parameters are determined by the
+backpack hardware and localization algorithms \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure} and are quite noisy.
 
@@
 \end{document}
+
+\message{ !name(oldpaper.tex) !offset(-739) }

### 2012-12-23 spie/paper.tex
starting spie stuff

%  article.tex (Version 3.3, released 19 January 2008)
%  Article to demonstrate format for SPIE Proceedings
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, e.g., to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class 
%  file (spie.cls) and will not be understood in other classes:
%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
%  The bibliography style file is called spiebib.bst, 
%  which replaces the standard style unstr.bst.

\documentclass[]{spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  e.g., [dvips], but that may be inappropriate for some LaTeX 
%  installations. 
\usepackage[]{graphicx}

\title{Texture mapping 3D planar models of indoor environments with noisy camera poses}

%>>>> The author is responsible for formatting the 
%  author list and their institutions.  Use  \skiplinehalf 
%  to separate author list from addresses and between each address.
%  The correspondence between each author and his/her address
%  can be indicated with a superscript in italics, 
%  which is easily obtained with \supit{}.

\author{Peter Cheng, Michael Anderson, Stewart He, Avideh Zakhor
\skiplinehalf
University of California, Berkeley\\
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%>>>> uncomment following for page numbers
% \pagestyle{plain}    
%>>>> uncomment following to start page numbering at 301 
%\setcounter{page}{301}

  \begin{document} 
  \maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
abstract goes here and stuff
\end{abstract}

%>>>> Include a list of keywords after the abstract

\keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:intro}  % \label{} allows reference to this section

This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.\footnote{The basic format was developed in 1995 by Rick Herman (SPIE) and Ken Hanson (Los Alamos National Lab.).} It is prepared using LaTeX2e\cite{Lamport94} with the class file {\tt spie.cls}.  The LaTeX source file used to create this document is {\tt article.tex}, which contains important formatting information embedded in it.  These files are available on the Internet at {\tt http://home.lanl.gov/kmh/spie/}.  The font used throughout is the LaTeX default font, Computer Modern Roman, which is equivalent to the Times Roman font available on many systems.  If this font is not available, use a similar serif font.  Normal text has a font size of 10 points\footnote{Font sizes are specified in points, abbreviated pt., which is a unit of length.  One inch = 72.27 pt.; one cm = 28.4 pt.} for which the actual height of a capital E is about 2.4 mm (7 pt.) and the line-to-line spacing is about 4.2 mm (12 pt.).  The font attributes for other parts of the manuscript, summarized in Table~\ref{tab:fonts}, are described in the following sections.  Normal text should be justified to both the left and right margins.  Appendix~\ref{sec:latex} has information about PostScript fonts.

To be properly reproduced in the Proceedings, all text and figures must fit inside a rectangle 6.75-in.\ wide by 8.75-in.\ high or 17.15 cm by 22.23 cm.  The text width and height are set in {\tt spie.cls} to match this requirement.
%% This table is carefully placed in the source file to make 
%% it appear at bottom of page, but above the footnotes.  
%% Use of [h] in following command forces table to appear "here".
\begin{table}[h]
\caption{Fonts sizes to be used for various parts of the manuscript.  All fonts are Computer Modern Roman or an equivalent.  Table captions should be centered above the table.  When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, centered  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names and affiliations & 12 pt., normal, centered   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 11 pt., bold, centered (all caps)  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 11 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 10 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 10 pt., normal  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions & \, 9 pt., normal \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Footnote & \, 9 pt., normal \\
\hline 
\end{tabular}
\end{center}
\end{table} 
The text should begin 1.00 in.\ or 2.54 cm from the top of the page.  The right and left margins should be 0.875~in.\ or 2.22 cm for US letter-size paper (8.5 in.\ by 11 in.) or 1.925 cm for A4 paper (210 mm by 297 mm) to horizontally center the text on the page.  See Appendix~\ref{sec:latex} for guidance regarding paper-size specification.

Authors are encouraged to follow the principles of sound technical writing, as described in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.  Many aspects of technical writing are addressed in the {\em AIP Style Manual}, published by the American Institute of Physics.  It is available on line at {\tt http://www.aip.org/pubservs/style/4thed/toc.html} or {\tt http://public.lanl.gov/kmh/AIP\verb+_+Style\verb+_+4thed.pdf}. A spelling checker is helpful for finding misspelled words.

An author may use this LaTeX source file as a template by substituting his/her own text in each field.  This document is not meant to be a complete guide on how to use LaTeX.  For that, refer to books on LaTeX usage, such as the definitive work by Lamport\cite{Lamport94} or the very useful compendium by Mittelbach et al.\cite{Mittelbach04}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PARTS OF MANUSCRIPT}

This section describes the normal structure of a manuscript and how each part should be handled.  The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.  In LaTeX, paragraphs are separated by blank lines in the source file.

At times it may be desired, for formatting reasons, to break a line without starting a new paragraph.  This situation may occur, for example, when formatting the article title, author information, or section headings.  Line breaks are inserted in LaTeX by entering \verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired location.

%%%%%Sometimes it is necessary to precede the double slash 
%%%%%by \verb|\protect| to get the desired result, 
%%%%%for example, in article titles.

%%-----------------------------------------------------------
\subsection{Title and Author Information} 
\label{sec:title}

The article title appears centered at the top of the first page.  The title font is 16 point, bold.  The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.  Avoid using acronyms in the title.  Keep in mind that people outside your area of expertise might read your article.  Appendix~\ref{sec:misc} contains more about acronyms.

The list of authors immediately follows the title after a blank vertical space of about 7 mm.  The font is 12 point, normal with each line centered.  The authors' affiliations and addresses follow the author list after another blank space of about 4 mm, also in 12-point, normal font and centered.  Do not use acronyms in affiliations and addresses. For multiple affiliations, each affiliation should appear on a new line, separated from the following address by a semicolon.  Italicized superscripts may be used to identify the correspondence between the authors and their respective affiliations.  Further author information, such as e-mail address, complete postal address, and web-site location, may be provided in a footnote by using \verb|\authorinfo{}|, as demonstrated above.

When the abbreviated title or author information is too long to fit on one line, multiple lines may be used; insert line breaks appropriately to achieve a visually pleasing format.  The proper spacing of one and one-half lines between the title, author list, and their affiliations is achieved with the command \verb|\skiplinehalf| defined in {\tt spie.cls}.

%%-----------------------------------------------------------
\subsection{Abstract and Keywords} 
The title and author information is immediately followed by the Abstract. The Abstract should concisely summarize the key findings of the paper.  It should consist of a single paragraph containing no more than 200 words.  The Abstract does not have a section number.  A list of up to ten keywords should immediately follow the Abstract after a blank line.  These keywords will be included in a searchable database at SPIE.

%%-----------------------------------------------------------
\subsection{Body of Paper} 
The body of the paper consists of numbered sections that present the main findings.  These sections should be organized to best present the material.  See Sec.~\ref{sec:sections} for formatting instructions.

%%-----------------------------------------------------------
\subsection{Appendices} 
Auxiliary material that is best left out of the main body of the paper, for example, derivations of equations, proofs of theorems, and details of algorithms, may be included in appendices.  Appendices are enumerated with uppercase Latin letters in alphabetic order, and appear just before the Acknowledgments and References.

%%-----------------------------------------------------------
\subsection{Acknowledgments} 
In the Acknowledgments section, appearing just before the References, the authors may credit others for their guidance or help.  Also, funding sources may be stated.  The Acknowledgments section does not have a section number.

%%-----------------------------------------------------------
\subsection{References} 
The References section lists books, articles, and reports that are cited in the paper.  It does not have a section number.  The references are numbered in the order in which they are cited.  Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\tt report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\tt spiebib.bst}, as specified in the \verb|\bibliographystyle{spiebib}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors, book title (in italics), page or chapter numbers, publisher, city, and year of publication.  A reference to a journal article\cite{Metropolis53} includes the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers, and year.  By convention\cite{Lamport94}, article titles are capitalized as described in Sec.~\ref{sec:title}.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), if appropriate, editors, volume or series title (in italics), volume number (in bold), if applicable, inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

Citations to the references are made using superscript numerals, as demonstrated in the preceding paragraph.  One may also directly refer to a reference within the text, e.g., ``as shown in Ref.~\citenum{Metropolis53} ..."

%%-----------------------------------------------------------
\subsection{Footnotes} 
Footnotes\footnote{Footnotes are indicated as superscript symbols to avoid confusion with citations.} may be used to provide auxiliary information that doesn't need to appear in the text, e.g., to explain measurement units.  They should be used sparingly, however.

Only nine footnote symbols are available in LaTeX. If you have more than nine footnotes, you will need to restart the sequence using the command  \verb|\footnote[1]{Your footnote text goes here.}|. If you don't, LaTeX will provide the error message {\tt Counter too large.}, followed by the offending footnote command.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SECTION FORMATTING} \label{sec:sections}

Section headings are centered and formatted completely in uppercase 11-point bold font.  Sections should be numbered sequentially, starting with the first section after the Abstract.  The heading starts with the section number, followed by a period.  In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style\cite{Lamport94}.  The same goes for leading paragraphs of subsections and sub-subsections.  Subsequent paragraphs are standard paragraphs, with 14-pt.\ (5 mm) indentation.  An extra half-line space should be inserted between paragraphs.  In LaTeX, this spacing is specified by the parameter \verb|\parskip|, which is set in {\tt spie.cls}.  Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

%%-----------------------------------------------------------
\subsection{Subsection Attributes}

The subsection heading is left justified and set in 11-point, bold font.  Capitalization rules are the same as those for book titles.  The first word of a subsection heading is capitalized.  The remaining words are also capitalized, except for minor words with fewer than four letters, such as articles (a, an, and the), short prepositions (of, at, by, for, in, etc.), and short conjunctions (and, or, as, but, etc.).  Subsection numbers consist of the section number, followed by a period, and the subsection number within that section.

%%-----------
\subsubsection{Sub-subsection attributes} 
The sub-subsection heading is left justified and its font is 10 point, bold.  Capitalize as for sentences.  The first word of a sub-subsection heading is capitalized.  The rest of the heading is not capitalized, except for acronyms and proper names.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FIGURES AND TABLES}

Figures are numbered in the order of their first citation.  They should appear in numerical order and on or after the same page as their first reference in the text.  Alternatively, all figures may be placed at the end of the manuscript, that is, after the Reference section.  It is preferable to have figures appear at the top or bottom of the page.  Figures, along with their captions, should be separated from the main text by at least 0.2 in.\ or 5 mm.

Figure captions are centered below the figure or graph.  Figure captions start with the figure number in 9-point bold font, followed by a period; the text is in 9-point normal font; for example, ``{\footnotesize{Figure 3.}  Original image...}".  See Fig.~\ref{fig:example} for an example of a figure caption.  When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.

Tables are handled identically to figures, except that their captions appear above the table. 
%%  Use following command to specify that graphics file is in 
%%  a directory other than this LaTeX source file.
%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
%%\graphicspath{{H:/HANSON/SPIESTY/}}
%% tabular environment useful for creating an array of images  
%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{naive.jpg}
   \end{tabular}
   \end{center}
   \caption[example] 
%>>>> use \label inside caption to get Fig. number with \ref{}
   { \label{fig:example} 
Figure captions are used to describe the figure and help the reader understand it's significance.  The caption should be centered underneath the figure and set in 9-point font.  It is preferable for figures and tables to be placed at the top or bottom of the page. LaTeX tends to adhere to this standard.}
   \end{figure} 
%-------------

For further details concerning the inclusion of grayscale and color images, consult SPIE's {\it Author Guide for Publication and Presentation}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix    %>>>> this command starts appendixes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MISCELLANEOUS FORMATTING DETAILS} \label{sec:misc}

It is often useful to refer back (or forward) to other sections in the article.  Such references are made by section number.  When a section reference starts a sentence, Section is spelled out; otherwise use its abbreviation, for example, ``In Sec.~2 we showed..." or ``Section~2.1 contained a description...".  References to figures, tables, and theorems are handled the same way.

At the first occurrence of an acronym, spell it out, followed by the acronym in parentheses, e.g., noise power spectrum (NPS).

%%-----------------------------------------------
\subsection{Formatting Equations} 
Equations may appear in line with the text, if they are simple, short, and not of major importance; e.g., $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the minus-log-posterior is
	\begin{equation}
	\label{eq:alpha}
\phi = |{\rm\bf y} - {\rm\bf A}{\rm\bf x}|^2 + \alpha \log p({\rm\bf x}) \, ,
	\end{equation}
where $\alpha$ determines the strength of ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma follows the equation because the next line is a subordinate clause.  If the equation ends the sentence, a period should follow the equation.  The line following an equation should not be indented unless it is meant to start a new paragraph.  Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:alpha}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..."  Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks.

%%-----------------------------------------------------------
\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified and followed by a period.  The text of the theorem continues on the same line in normal, 10-point font.  For example,

\noindent{\bf Theorem 1.} For any unbiased estimator...

Formal statements of lemmas and algorithms receive a similar treatment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SOME LATEX GUIDANCE} \label{sec:latex}

%%-----------------------------------------------------------
\subsection{Margins and PostScript Fonts}

Manuscripts submitted electronically to as PostScript (PS) files must have the correct margins. LaTeX margins are related to the document's paper size. The paper size is set at two separate places in the process of creating a PS file. The first place is in {\tt latex}. The default in {\tt article.tex}, on which {\tt spie.cls} is based, is USA letter paper. To format a document for A4 paper, the first line of the LaTeX source file should be \verb|\documentclass[a4paper]{spie}|.

The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.  The application DVIPS is typically used to convert the DVI file to a PS file.  DVIPS has its own default paper size, which can be overridden with the option ``{\tt -t letter}" or ``{\tt -t a4}".  
If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command, for example.

Another DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file. This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.  The option ``{\tt -P pdf}" makes DVIPS include these fonts in its output PS file.

%%-----------------------------------------------------------
\subsection{Bold Math Symbols}

The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX. It also provides many useful capabilities for creating elaborate mathematical expressions. You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
\verb+\usepackage[]{amsmath}+ \\[1ex]
Then for bold math symbols use \verb+\boldsymbol+ in equations, e.g., 
\verb+$\boldsymbol{\pi}$+ 
yields a bold pi.  You can make it easier to use by defining a command:\\[1ex]
\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
and then using it like so \verb+$\bm{\pi}$+.

Not all math symbols are available in bold.  In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+. This command approximates a bold character with a superposition of several, slightly displaced unbold characters.

If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
Then, in the title, use something like:\\[1ex]
\verb+\title{Estimation of {\LARGE$\boldsymbol\alpha$} by a Monte Carlo technique}+ \\[1ex]
Note that the command to create the alpha character is enclosed within braces to form a self-contained environment. The use of \verb+\LARGE+ in this example may not be needed when using nondefault font packages, such as the {\tt times} package, because of how the article title is handled in {\tt spie.cls}.

%%-----------------------------------------------------------
\subsection{Uppercase letters and special symbols in BibTex}

BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case. BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.

The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged in braces. Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
\verb+ @article{Kaczmarz37,+ \\ 
\verb+ author = "S. Kaczmarz",+ \\ 
\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen linearer {G}leichungen",+ \\ 
\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
\verb+ volume = "A35",+ \\ 
\verb+ pages  = "355-357",+ \\	
\verb+ year   = "1937"	} + \\[1ex]
This example shows the use of both umlauts and uppercase letters.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}

This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document}

### 2012-12-23 spie/paper.tex
intro parts

@@
 \begin{abstract}
-abstract goes here and stuff
+  Automated 3D modeling of building interiors is used in applications
+  such as virtual reality and environment mapping. Incorporating
+  images and texture mapping these models allows for photorealistic
+  visualizations of the data collected by such modeling systems. Pose
+  estimates obtained by these systems often suffer from inaccuracies,
+  resulting in visible discontinuities when successive images are
+  projected adjacently onto a surface for texturing. Existing methods
+  to stitch images together are often computationally expensive and
+  work independently of pose estimates and geometry information. We
+  propose a method to refine camera poses using both existing
+  estimates and geometry information, followed by two different
+  methods to composite images together, based on the uniformity of
+  available images. The effectiveness of our methods are demonstrated
+  on a number of disparate indoor environments.
 \end{abstract}
 
-%>>>> Include a list of keywords after the abstract
+% >>>> Include a list of keywords after the abstract
 
@@
 \section{INTRODUCTION}
-\label{sec:intro}  % \label{} allows reference to this section
+\label{sec:introduction} % \label{} allows reference to this section
+Three-dimensional modeling of indoor environments has a variety of
+applications such as training and simulation for disaster management,
+virtual heritage conservation, and mapping of hazardous sites. Manual
+construction of these digital models can be time-consuming, and as a
+result, automated 3D site modeling has garnered much interest in
+recent years. CITATION
 
-This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.\footnote{The basic format was developed in 1995 by Rick Herman (SPIE) and Ken Hanson (Los Alamos National Lab.).} It is prepared using LaTeX2e\cite{Lamport94} with the class file {\tt spie.cls}.
-The LaTeX source file used to create this document is {\tt article.tex}, which contains important formatting information embedded in it.
-These files are available on the Internet at {\tt http://home.lanl.gov/kmh/spie/}.
-The font used throughout is the LaTeX default font, Computer Modern Roman, which is equivalent to the Times Roman font available on many systems.
-If this font is not available, use a similar serif font.
-Normal text has a font size of 10 points\footnote{Font sizes are specified in points, abbreviated pt., which is a unit of length.
-One inch = 72.27 pt.; one cm = 28.4 pt.} for which the actual height of a capital E is about 2.4 mm (7 pt.) and the line-to-line spacing is about 4.2 mm (12 pt.).
-The font attributes for other parts of the manuscript, summarized in Table~\ref{tab:fonts}, are described in the following sections.
-Normal text should be justified to both the left and right margins.
-Appendix~\ref{sec:latex} has information about PostScript fonts.
+The first step in automated 3D modeling is the physical scanning of
+the environment's geometry. An indoor modeling system must recover its
+own poses within an environment while simultaneously reconstructing
+the 3D structure of the environment itself. CITATION. This is known as
+the simultaneous localization and mapping (SLAM) problem, and is
+generally solved by taking readings from laser range scanners,
+cameras, and inertial measurement units (IMUs) at multiple locations
+within the environment.
 
-To be properly reproduced in the Proceedings, all text and figures must fit inside a rectangle 6.75-in.\ wide by 8.75-in.\ high or 17.15 cm by 22.23 cm.
-The text width and height are set in {\tt spie.cls} to match this requirement.
-%% This table is carefully placed in the source file to make 
-%% it appear at bottom of page, but above the footnotes.  
-%% Use of [h] in following command forces table to appear "here".
-\begin{table}[h]
-\caption{Fonts sizes to be used for various parts of the manuscript.
-All fonts are Computer Modern Roman or an equivalent.
-Table captions should be centered above the table.
-When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.}
-\label{tab:fonts}
-\begin{center}       
-\begin{tabular}{|l|l|} %% this creates two columns
-%% |l|l| to left justify each column entry
-%% |c|c| to center each column entry
-%% use of \rule[]{}{} below opens up each row
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, centered  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Author names and affiliations & 12 pt., normal, centered   \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Section heading & 11 pt., bold, centered (all caps)  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 11 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 10 pt., bold, left justified  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Normal text & 10 pt., normal  \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Figure and table captions & \, 9 pt., normal \\
-\hline
-\rule[-1ex]{0pt}{3.5ex}  Footnote & \, 9 pt., normal \\
-\hline 
-\end{tabular}
-\end{center}
-\end{table} 
-The text should begin 1.00 in.\ or 2.54 cm from the top of the page.
-The right and left margins should be 0.875~in.\ or 2.22 cm for US letter-size paper (8.5 in.\ by 11 in.) or 1.925 cm for A4 paper (210 mm by 297 mm) to horizontally center the text on the page.
-See Appendix~\ref{sec:latex} for guidance regarding paper-size specification.
+In this paper, we work with data obtained from a backpack-mounted
+system, carried by an ambulatory human. Such a system provides
+advantages over more common wheel-mounted systems in terms of agility
+and portability, but results in much higher localization error and
+uncertainty overall. CITATION. As a result, common methods for texture
+mapping generally produce poor results, leading to the development of
+the approaches contained in this paper. Besides localization
+information and images, environment geometry is required as well for
+texture mapping. In this paper we work mainly with models obtained
+through plane-fitting surfaces to point clouds generated by the
+backpack system. CITATION. We have also developed an appropriate
+method to work with near-planar models, as described in APPENDIX
+SOMETHING.
 
-Authors are encouraged to follow the principles of sound technical writing, as described in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.
-Many aspects of technical writing are addressed in the {\em AIP Style Manual}, published by the American Institute of Physics.
-It is available on line at {\tt http://www.aip.org/pubservs/style/4thed/toc.html} or {\tt http://public.lanl.gov/kmh/AIP\verb+_+Style\verb+_+4thed.pdf}.
-A spelling checker is helpful for finding misspelled words.
+Though our texture mapping procedure was designed with the
+aforementioned system in mind, it is easily generalizable to any other
+system, provided the required inputs of surface geometry, images with
+rough extrinsic pose estimates, and either provided or estimated
+intrinsic camera calibration matrices. An added benefit of our method
+is its relatively fast running time and modularity of each step,
+allowing for quick tuning of parameters and easy accomodation of new
+input data given updates in localization or model-generation
+algorithms.
 
-An author may use this LaTeX source file as a template by substituting his/her own text in each field.
-This document is not meant to be a complete guide on how to use LaTeX.
-For that, refer to books on LaTeX usage, such as the definitive work by Lamport\cite{Lamport94} or the very useful compendium by Mittelbach et al.\cite{Mittelbach04}
-
+The remainder of the paper is organized as follows. Section X explains
+how input images are projected onto our geometry and simple approaches
+towards texturing. Section X covers more sophisticated existing
+approaches to image matching and stitching, and their performance on
+our datasets. Section X contains our approach towards image matching,
+followed by Section X, which describes compositing approaches. Section
+X contains further results and conclusions.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-This section describes the normal structure of a manuscript and how each part should be handled.
-The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.
-In LaTeX, paragraphs are separated by blank lines in the source file.
+This section describes the normal structure of a manuscript and how
+each part should be handled.  The appropriate vertical spacing between
+various parts of this document is achieved in LaTeX through the proper
+use of defined constructs, such as \verb|\section{}|.  In LaTeX,
+paragraphs are separated by blank lines in the source file.
 
-At times it may be desired, for formatting reasons, to break a line without starting a new paragraph.
-This situation may occur, for example, when formatting the article title, author information, or section headings.
-Line breaks are inserted in LaTeX by entering \verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired location.
+At times it may be desired, for formatting reasons, to break a line
+without starting a new paragraph.  This situation may occur, for
+example, when formatting the article title, author information, or
+section headings.  Line breaks are inserted in LaTeX by entering
+\verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired
+location.
 
-%%%%%Sometimes it is necessary to precede the double slash 
-%%%%%by \verb|\protect| to get the desired result, 
-%%%%%for example, in article titles.
+%%%%% Sometimes it is necessary to precede the double slash by
+%%%%% \verb|\protect| to get the desired result, for example, in
+%%%%% article titles.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Title and Author Information}
@@
 
-The article title appears centered at the top of the first page.
-The title font is 16 point, bold.
-The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.
-Avoid using acronyms in the title.
-Keep in mind that people outside your area of expertise might read your article.
-Appendix~\ref{sec:misc} contains more about acronyms.
+The article title appears centered at the top of the first page.  The
+title font is 16 point, bold.  The rules for capitalizing the title
+are the same as for sentences; only the first word, proper nouns, and
+acronyms should be capitalized.  Avoid using acronyms in the title.
+Keep in mind that people outside your area of expertise might read
+your article.  Appendix~\ref{sec:misc} contains more about acronyms.
 
-The list of authors immediately follows the title after a blank vertical space of about 7 mm.
-The font is 12 point, normal with each line centered.
-The authors' affiliations and addresses follow the author list after another blank space of about 4 mm, also in 12-point, normal font and centered.
-Do not use acronyms in affiliations and addresses.
-For multiple affiliations, each affiliation should appear on a new line, separated from the following address by a semicolon.
-Italicized superscripts may be used to identify the correspondence between the authors and their respective affiliations.
-Further author information, such as e-mail address, complete postal address, and web-site location, may be provided in a footnote by using \verb|\authorinfo{}|, as demonstrated above.
+The list of authors immediately follows the title after a blank
+vertical space of about 7 mm.  The font is 12 point, normal with each
+line centered.  The authors' affiliations and addresses follow the
+author list after another blank space of about 4 mm, also in 12-point,
+normal font and centered.  Do not use acronyms in affiliations and
+addresses. For multiple affiliations, each affiliation should appear
+on a new line, separated from the following address by a semicolon.
+Italicized superscripts may be used to identify the correspondence
+between the authors and their respective affiliations.  Further author
+information, such as e-mail address, complete postal address, and
+web-site location, may be provided in a footnote by using
+\verb|\authorinfo{}|, as demonstrated above.
 
-When the abbreviated title or author information is too long to fit on one line, multiple lines may be used; insert line breaks appropriately to achieve a visually pleasing format.
-The proper spacing of one and one-half lines between the title, author list, and their affiliations is achieved with the command \verb|\skiplinehalf| defined in {\tt spie.cls}.
+When the abbreviated title or author information is too long to fit on
+one line, multiple lines may be used; insert line breaks appropriately
+to achieve a visually pleasing format.  The proper spacing of one and
+one-half lines between the title, author list, and their affiliations
+is achieved with the command \verb|\skiplinehalf| defined in {\tt
+  spie.cls}.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Abstract and Keywords}
-The title and author information is immediately followed by the Abstract.
-The Abstract should concisely summarize the key findings of the paper.
-It should consist of a single paragraph containing no more than 200 words.
-The Abstract does not have a section number.
-A list of up to ten keywords should immediately follow the Abstract after a blank line.
-These keywords will be included in a searchable database at SPIE.
+The title and author information is immediately followed by the
+Abstract. The Abstract should concisely summarize the key findings of
+the paper.  It should consist of a single paragraph containing no more
+than 200 words.  The Abstract does not have a section number.  A list
+of up to ten keywords should immediately follow the Abstract after a
+blank line.  These keywords will be included in a searchable database
+at SPIE.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Body of Paper}
-The body of the paper consists of numbered sections that present the main findings.
-These sections should be organized to best present the material.
-See Sec.~\ref{sec:sections} for formatting instructions.
+The body of the paper consists of numbered sections that present the
+main findings.  These sections should be organized to best present the
+material.  See Sec.~\ref{sec:sections} for formatting instructions.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Appendices}
-Auxiliary material that is best left out of the main body of the paper, for example, derivations of equations, proofs of theorems, and details of algorithms, may be included in appendices.
-Appendices are enumerated with uppercase Latin letters in alphabetic order, and appear just before the Acknowledgments and References.
+Auxiliary material that is best left out of the main body of the
+paper, for example, derivations of equations, proofs of theorems, and
+details of algorithms, may be included in appendices.  Appendices are
+enumerated with uppercase Latin letters in alphabetic order, and
+appear just before the Acknowledgments and References.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Acknowledgments}
-In the Acknowledgments section, appearing just before the References, the authors may credit others for their guidance or help.
-Also, funding sources may be stated.
-The Acknowledgments section does not have a section number.
+In the Acknowledgments section, appearing just before the References,
+the authors may credit others for their guidance or help.  Also,
+funding sources may be stated.  The Acknowledgments section does not
+have a section number.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{References}
-The References section lists books, articles, and reports that are cited in the paper.
-It does not have a section number.
-The references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this document.
+The References section lists books, articles, and reports that are
+cited in the paper.  It does not have a section number.  The
+references are numbered in the order in which they are cited.
+Examples of the format to be followed are given at the end of this
+document.
 
-The reference list at the end of this document is created using BibTeX, which looks through the file {\tt report.bib} for the entries cited in the LaTeX source file.
-The format of the reference list is determined by the bibliography style file {\tt spiebib.bst}, as specified in the \verb|\bibliographystyle{spiebib}| command.
-Alternatively, the references may be directly formatted in the LaTeX source file.
+The reference list at the end of this document is created using
+BibTeX, which looks through the file {\tt report.bib} for the entries
+cited in the LaTeX source file.  The format of the reference list is
+determined by the bibliography style file {\tt spiebib.bst}, as
+specified in the \verb|\bibliographystyle{spiebib}| command.
+Alternatively, the references may be directly formatted in the LaTeX
+source file.
 
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors, book title (in italics), page or chapter numbers, publisher, city, and year of publication.
-A reference to a journal article\cite{Metropolis53} includes the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers, and year.
-By convention\cite{Lamport94}, article titles are capitalized as described in Sec.~\ref{sec:title}.
-A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), if appropriate, editors, volume or series title (in italics), volume number (in bold), if applicable, inclusive page numbers, publisher, city, and year.
-References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.
+For books\cite{Lamport94,Alred03,Goossens97} the listing includes the
+list of authors, book title (in italics), page or chapter numbers,
+publisher, city, and year of publication.  A reference to a journal
+article\cite{Metropolis53} includes the author list, title of the
+article (in quotes), journal name (in italics, properly abbreviated),
+volume number (in bold), inclusive page numbers, and year.  By
+convention\cite{Lamport94}, article titles are capitalized as
+described in Sec.~\ref{sec:title}.  A reference to a proceedings paper
+or a chapter in an edited book\cite{Gull89a} includes the author list,
+title of the article (in quotes), conference name (in italics), if
+appropriate, editors, volume or series title (in italics), volume
+number (in bold), if applicable, inclusive page numbers, publisher,
+city, and year.  References to an article in the SPIE Proceedings may
+include the conference name, as shown in Ref.~\citenum{Hanson93c}.
 
-Citations to the references are made using superscript numerals, as demonstrated in the preceding paragraph.
-One may also directly refer to a reference within the text, e.g., ``as shown in Ref.~\citenum{Metropolis53} ..."
+Citations to the references are made using superscript numerals, as
+demonstrated in the preceding paragraph.  One may also directly refer
+to a reference within the text, e.g., ``as shown in
+Ref.~\citenum{Metropolis53} ..."
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Footnotes}
-Footnotes\footnote{Footnotes are indicated as superscript symbols to avoid confusion with citations.} may be used to provide auxiliary information that doesn't need to appear in the text, e.g., to explain measurement units.
-They should be used sparingly, however.
+Footnotes\footnote{Footnotes are indicated as superscript symbols to
+  avoid confusion with citations.} may be used to provide auxiliary
+information that doesn't need to appear in the text, e.g., to explain
+measurement units.  They should be used sparingly, however.
 
-Only nine footnote symbols are available in LaTeX.
-If you have more than nine footnotes, you will need to restart the sequence using the command  \verb|\footnote[1]{Your footnote text goes here.}|.
-If you don't, LaTeX will provide the error message {\tt Counter too large.}, followed by the offending footnote command.
+Only nine footnote symbols are available in LaTeX. If you have more
+than nine footnotes, you will need to restart the sequence using the
+command \verb|\footnote[1]{Your footnote text goes here.}|. If you
+don't, LaTeX will provide the error message {\tt Counter too large.},
+followed by the offending footnote command.
 
@@
 
-Section headings are centered and formatted completely in uppercase 11-point bold font.
-Sections should be numbered sequentially, starting with the first section after the Abstract.
-The heading starts with the section number, followed by a period.
-In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.
+Section headings are centered and formatted completely in uppercase
+11-point bold font.  Sections should be numbered sequentially,
+starting with the first section after the Abstract.  The heading
+starts with the section number, followed by a period.  In LaTeX, a new
+section is created with the \verb|\section{}| command, which
+automatically numbers the sections.
 
-Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style\cite{Lamport94}.
-The same goes for leading paragraphs of subsections and sub-subsections.
-Subsequent paragraphs are standard paragraphs, with 14-pt.\ (5 mm) indentation.
-An extra half-line space should be inserted between paragraphs.
-In LaTeX, this spacing is specified by the parameter \verb|\parskip|, which is set in {\tt spie.cls}.
-Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.
+Paragraphs that immediately follow a section heading are leading
+paragraphs and should not be indented, according to standard
+publishing style\cite{Lamport94}.  The same goes for leading
+paragraphs of subsections and sub-subsections.  Subsequent paragraphs
+are standard paragraphs, with 14-pt.\ (5 mm) indentation.  An extra
+half-line space should be inserted between paragraphs.  In LaTeX, this
+spacing is specified by the parameter \verb|\parskip|, which is set in
+{\tt spie.cls}.  Indentation of the first line of a paragraph may be
+avoided by starting it with \verb|\noindent|.
 
-%%-----------------------------------------------------------
+%% -----------------------------------------------------------
 \subsection{Subsection Attributes}
 
-The subsection heading is left justified and set in 11-point, bold font.
-Capitalization rules are the same as those for book titles.
-The first word of a subsection heading is capitalized.
-The remaining words are also capitalized, except for minor words with fewer than four letters, such as articles (a, an, and the), short prepositions (of, at, by, for, in, etc.), and short conjunctions (and, or, as, but, etc.).
-Subsection numbers consist of the section number, followed by a period, and the subsection number within that section.
+The subsection heading is left justified and set in 11-point, bold
+font.  Capitalization rules are the same as those for book titles.
+The first word of a subsection heading is capitalized.  The remaining
+words are also capitalized, except for minor words with fewer than
+four letters, such as articles (a, an, and the), short prepositions
+(of, at, by, for, in, etc.), and short conjunctions (and, or, as, but,
+etc.).  Subsection numbers consist of the section number, followed by
+a period, and the subsection number within that section.
 
-%%-----------
+%% -----------
 \subsubsection{Sub-subsection attributes}
-The sub-subsection heading is left justified and its font is 10 point, bold.
-Capitalize as for sentences.
-The first word of a sub-subsection heading is capitalized.
-The rest of the heading is not capitalized, except for acronyms and proper names.
+The sub-subsection heading is left justified and its font is 10 point,
+bold.  Capitalize as for sentences.  The first word of a
+sub-subsection heading is capitalized.  The rest of the heading is not
+capitalized, except for acronyms and proper names.
 
@@
 
-Figures are numbered in the order of their first citation.
-They should appear in numerical order and on or after the same page as their first reference in the text.
-Alternatively, all figures may be placed at the end of the manuscript, that is, after the Reference section.
-It is preferable to have figures appear at the top or bottom of the page.
-Figures, along with their captions, should be separated from the main text by at least 0.2 in.\ or 5 mm.
+Figures are numbered in the order of their first citation.  They
+should appear in numerical order and on or after the same page as
+their first reference in the text.  Alternatively, all figures may be
+placed at the end of the manuscript, that is, after the Reference
+section.  It is preferable to have figures appear at the top or bottom
+of the page.  Figures, along with their captions, should be separated
+from the main text by at least 0.2 in.\ or 5 mm.
 
-Figure captions are centered below the figure or graph.
-Figure captions start with the figure number in 9-point bold font, followed by a period; the text is in 9-point normal font; for example, ``{\footnotesize{Figure 3.}  Original image...}".
-See Fig.~\ref{fig:example} for an example of a figure caption.
-When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.
+Figure captions are centered below the figure or graph.  Figure
+captions start with the figure number in 9-point bold font, followed
+by a period; the text is in 9-point normal font; for example,
+``{\footnotesize{Figure 3.}  Original image...}".  See
+Fig.~\ref{fig:example} for an example of a figure caption.  When the
+caption is too long to fit on one line, it should be justified to the
+right and left margins of the body of the text.
 
-Tables are handled identically to figures, except that their captions appear above the table. 
-%%  Use following command to specify that graphics file is in 
-%%  a directory other than this LaTeX source file.
-%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
-%%\graphicspath{{H:/HANSON/SPIESTY/}}
-%% tabular environment useful for creating an array of images  
-%-------------
+Tables are handled identically to figures, except that their captions
+appear above the table.
+%% Use following command to specify that graphics file is in a
+%% directory other than this LaTeX source file.  Note use of / to
+%% separate subdirectories, for UNIX and Windows OS.
+%% \graphicspath{{H:/HANSON/SPIESTY/}} tabular environment useful for
+%% creating an array of images
+% -------------
 \begin{figure}
@@
   \caption[example]
-%>>>> use \label inside caption to get Fig. number with \ref{}
-   { \label{fig:example} 
-Figure captions are used to describe the figure and help the reader understand it's significance.
-The caption should be centered underneath the figure and set in 9-point font.
-It is preferable for figures and tables to be placed at the top or bottom of the page.
-LaTeX tends to adhere to this standard.}
+  % >>>> use \label inside caption to get Fig. number with \ref{}
+  { \label{fig:example} Figure captions are used to describe the
+    figure and help the reader understand it's significance.  The
+    caption should be centered underneath the figure and set in
+    9-point font.  It is preferable for figures and tables to be
+    placed at the top or bottom of the page. LaTeX tends to adhere to
+    this standard.}
 \end{figure}
-%-------------
+% -------------
 
-For further details concerning the inclusion of grayscale and color images, consult SPIE's {\it Author Guide for Publication and Presentation}.
+For further details concerning the inclusion of grayscale and color
+images, consult SPIE's {\it Author Guide for Publication and
+  Presentation}.
 

### 2012-12-24 spie/_region_.tex
did existing stuff

@@
 \skiplinehalf
-University of California, Berkeley ; \\
+University of California, Berkeley\\
 }
-
-%>>>> Further information about the authors, other than their 
-%  institution and addresses, should be included as a footnote, 
-%  which is facilitated by the \authorinfo{} command.
-
-\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
-%%>>>> when using amstex, you need to use @@ instead of @
 
@@
 
-\message{ !name(paper.tex) !offset(-42) }
-\documentclass[]{spie}  %>>> use for US letter paper
-%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
-%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
-%% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
-%  The following command loads a graphics package to include images 
-%  in the document. It may be necessary to specify a DVI driver option,
-%  e.g., [dvips], but that may be inappropriate for some LaTeX 
-%  installations. 
-\usepackage[]{graphicx}
+\message{ !name(paper.tex) !offset(106) }
+\subsection{Direct Mapping}
+\label{sec:directMapping}
 
-\title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+we can texture the plane by discretizing it into small square tiles,
+in our case 5 pixels across, and choosing an image to texture each
+tile.
 
-%>>>> The author is responsible for formatting the 
-%  author list and their institutions.  Use  \skiplinehalf 
-%  to separate author list from addresses and between each address.
-%  The correspondence between each author and his/her address
-%  can be indicated with a superscript in italics, 
-%  which is easily obtained with \supit{}.
+We choose to work with rectangular units to ensure that borders
+between any two distinct images in the final texture are either
+horizontal or vertical. Since most strong environmental features
+inside buildings are horizontal or vertical, any visible seams in our
+texture intersect them minimally and are less noticeable.
 
-\author{Peter Cheng, Michael Anderson, Stewart He, Avideh Zakhor
-\skiplinehalf
-University of California, Berkeley ; \\
-}
+In order to select an image for texturing a tile $t$, we must first
+gather a list of candidate images that contain all four of its
+corners, which we can quickly check by projecting $t$ into each image
+using the $P_i$ camera matrices. Furthermore, each candidate image
+must have been taken at a time when its camera had a clear
+line-of-sight to $t$, which can be calculated using standard
+ray-polygon intersection tests between the camera location, $t$, and
+every other plane \cite{rayintersection}.
 
-%>>>> Further information about the authors, other than their 
-%  institution and addresses, should be included as a footnote, 
-%  which is facilitated by the \authorinfo{} command.
+Once we have a list of candidate images for $t$, we define a scoring
+function in order to objectively select the best image for texturing
+$t$. Since camera pose errors compound over distance, we wish to
+minimize the distance between cameras and the surfaces they
+texture. Additionally, we desire images that are projected
+perpendicularly onto the plane, maximizing the resolution and amount
+of useful texture available in their projections, as well as
+minimizing any parallax effects due to real-world geometry not
+represented by our digital model. In other words, we wish to minimize
+the angle between the tile's normal vector and the camera axis for
+images selected for texture mapping. These two criteria can be met by
+maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
+as shown in Figure \ref{fig:scoringFunction}. Specifically, $d$ is the
+distance between the centers of a camera and a tile, and $\vec{n}$ and
+$\vec{c}$ are the directions of the plane's normal and the camera axis
+respectively.
 
-\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
-%%>>>> when using amstex, you need to use @@ instead of @
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{scoringFunction.jpg}
+  \caption{We minimize camera angle $\alpha$ and distance $d$ by
+    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
+    \cdot \vec{n}$}
+  \label{fig:scoringFunction}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%>>>> uncomment following for page numbers
-% \pagestyle{plain}    
-%>>>> uncomment following to start page numbering at 301 
-%\setcounter{page}{301}
+\begin{figure}[h!]
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_naive.pdf}}
 
-\message{ !name(paper.tex) !offset(197) }
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_cache.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_cache_shift.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_dynprog_noblend.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_cache_shift_blend.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_dynprog.pdf}}
+  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
+    with caching after image alignment. (d) Seam minimization after
+    image alignment). (e) same as (c) with blending. (f) same as (d)
+    with blending.}
+  \label{fig:compareAll}
+\end{figure}
+
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
+the best texture for each tile independently, but overall results in
+many image boundaries with abrupt discontinuities, due to significant
+misalignment between images, as a result of camera pose inaccuracies.
+
+\message{ !name(paper.tex) !offset(416) }
 

### 2012-12-24 spie/paper.tex
did existing stuff

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Simple Texture Mapping}
+\label{sec:simpleTextureMapping}
+\begin{figure}
+  \centering
+  \includegraphics[height=2in]{Projection.pdf}
+  \caption{Planes are specified in 3D space by four corners $C_1$ to
+    $C_4$. Images are related to each plane through the camera matrics
+    $P_{1..m}$. }
+  \label{fig:projection}
+\end{figure}
+
+The geometry of the texture mapping process for a plane is shown in
+Figure \ref{fig:projection}.  As described earlier, we are provided
+with a set of $M$ images to texture the target plane. Each image has a
+camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
+world coordinate system to a 2D point or pixel in image $i$'s
+coordinates. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, such as focal length and image center, as well
+as extrinsic parameters which specify the rotation and translation of
+the camera's position in 3D world coordinates at the time that image
+$i$ is taken. These extrinsic parameters are determined by the
+backpack hardware and localization algorithms \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure} and are quite noisy.
+
+Because our backpack system takes photos at a rate of 5 Hz, thousands
+of images are available for texturing each surface in our model. Our
+goal in designing a texture mapping process is to decide which of
+these images should be used, and where their contents should map onto
+the texture, in order to minimize any visual discontinuities or seams
+that would suggest that the plane's final texture is not composed of a
+single continuous image.
+
+\subsection{Direct Mapping}
+\label{sec:directMapping}
+
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+we can texture the plane by discretizing it into small square tiles,
+in our case 5 pixels across, and choosing an image to texture each
+tile.
+
+We choose to work with rectangular units to ensure that borders
+between any two distinct images in the final texture are either
+horizontal or vertical. Since most strong environmental features
+inside buildings are horizontal or vertical, any visible seams in our
+texture intersect them minimally and are less noticeable.
+
+In order to select an image for texturing a tile $t$, we must first
+gather a list of candidate images that contain all four of its
+corners, which we can quickly check by projecting $t$ into each image
+using the $P_i$ camera matrices. Furthermore, each candidate image
+must have been taken at a time when its camera had a clear
+line-of-sight to $t$, which can be calculated using standard
+ray-polygon intersection tests between the camera location, $t$, and
+every other plane \cite{rayintersection}.
+
+Once we have a list of candidate images for $t$, we define a scoring
+function in order to objectively select the best image for texturing
+$t$. Since camera pose errors compound over distance, we wish to
+minimize the distance between cameras and the surfaces they
+texture. Additionally, we desire images that are projected
+perpendicularly onto the plane, maximizing the resolution and amount
+of useful texture available in their projections, as well as
+minimizing any parallax effects due to real-world geometry not
+represented by our digital model. In other words, we wish to minimize
+the angle between the tile's normal vector and the camera axis for
+images selected for texture mapping. These two criteria can be met by
+maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
+as shown in Figure \ref{fig:scoringFunction}. Specifically, $d$ is the
+distance between the centers of a camera and a tile, and $\vec{n}$ and
+$\vec{c}$ are the directions of the plane's normal and the camera axis
+respectively.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{scoringFunction.jpg}
+  \caption{We minimize camera angle $\alpha$ and distance $d$ by
+    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
+    \cdot \vec{n}$}
+  \label{fig:scoringFunction}
+\end{figure}
+
+\begin{figure}[h!]
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_naive.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_cache.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_cache_shift.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_dynprog_noblend.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_cache_shift_blend.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=0.97in]{wall2_dynprog.pdf}}
+  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
+    with caching after image alignment. (d) Seam minimization after
+    image alignment). (e) same as (c) with blending. (f) same as (d)
+    with blending.}
+  \label{fig:compareAll}
+\end{figure}
+
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
+the best texture for each tile independently, but overall results in
+many image boundaries with abrupt discontinuities, due to significant
+misalignment between images, as a result of camera pose inaccuracies.
+
+\subsection{Mapping with Caching}
+\label{sec:mappingWithCaching}
+Since discontinuities occur where adjacent tiles select non-aligned
+images, it makes sense to take into account image selections made by
+neighboring tiles while texture mapping a given tile. By using the
+same image across tile boundaries, we can eliminate a discontinuity
+altogether. If this is not possible because a tile is not visible in
+images used by neighboring tiles, using similar images across tile
+boundaries also leads to less noticeable discontinuities.
+
+Essentially a caching mechanism, we select the best image for a tile
+$t$ by searching through two subsets of images for a viable candidate,
+before searching through the entire set of valid images. The first
+subset of images is the images selected by adjacent tiles that have
+already been textured. We must first check which of these images can
+map to $t$, and then of those, we make a choice according to the
+scoring function in Figure \ref{fig:scoringFunction}. Before reusing
+this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
+order to be considered a viable image, with $\alpha$ as the camera
+angle as shown in Figure \ref{fig:scoringFunction}.
+
+If no satisfactory image is found in the first subset, we check the
+second subset of images, consisting of those taken near the ones in
+the first subset, both spatially and temporally. These images are not
+the same as the ones used for neighboring tiles, but are taken at a
+similar location and time, suggesting that their localization and
+projection are quite similar, allowing us to minimize any differences
+in localization error as well as a parallax effects. Again, if no
+viable image is found according to the same criteria, we search the
+entire set of candidate images, selecting based on the same scoring
+function from Figure \ref{fig:scoringFunction}.
+
+The result of this caching approach is shown in Figure
+\ref{fig:compareAll}(b). As compared to Figure
+\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
+amount of remaining seams suggests that despite our high volume of
+images, image selection alone cannot produce seamless textures. Camera
+matrices, or the image projections themselves, have to be adjusted in
+order to reliably generate clean textures.
+
+\section{Existing Approaches to Image Alignment}
+\label{sec:existingApproaches}
+Stitching together multiple images to produce a larger image is a
+commonly performed task, with many successful approaches over the past
+few decades. Parts of images are first matched to eachother, through
+direct pixel comparisons, or more commonly through feature detection
+and matching. Images are then adjusted to maximize matches, either by
+directly calculating homographies between pairs of images, or by
+modifying camera poses from 1 to 6 degrees of freedom.
+
+Feature detection and matching works best when multiple unique visual
+references exist in the environment and are present within multiple
+images. This allows for accurate matching when texturing detailed
+objects at high resolutions CiTATION, or when creating outdoor
+panoramas CITATION. In contrast, our indoor environments have a high
+prevalence of bare surfaces, as well as repeating textures that cause
+difficulty in distinguishing features. The lack of strong reference
+points results in high uncertainty when matching images together.
+
+Additionally, our datasets often contain long chains of images, which
+leads to error accumulation when image correspondences are not
+accurate. For example, when matching a long chain of images through
+homographies, a pixel in the $nth$ image must be translated into the
+first image's coordinates by multiplying by the $3\times3$ matrix $H_1
+H_2 H_3 ... H_n$. Any error in one of these homography matrices is
+propagated to all further images, resulting in drift. Figure
+\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
+package, which performs homography-based image mosaicing
+\cite{autostitch}. Even with many features spread across this surface,
+the mosaicing produces errors that cause straight lines to appear as
+distorted, despite the fact that it was generated after careful hand
+tuning. Many areas with fewer visual features simply failed outright
+using this approach.
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
+  \caption{Texture alignment via (a) the graph-based localization
+    refinement algorithm from \cite{chen2010indoor} and (b) image
+    mosaicing.}
+  \label{fig:mosaic3D}
+\end{figure}
+
+Image projections can also be aligned by iteratively adjusting camera poses to maximize matches.
+This is generally done over 6 degrees of freedom.
+CITATION.
+Applying the approach in the LIU2010INDOOR paper however, results again in error accumulation and drift as shown in Figure \ref{fig:mosaic3D}(a).
+Furthermore, such nonlinear optimization approaches have an extremely high complexity and runtime, and the entire solution must be recomputed given any changes in input data.
+
+\section{Our Image Alignment with Cool Name}
+\section{Image Compositing}
+\section{Results and Conclusions}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%poop below
 \section{PARTS OF MANUSCRIPT}

### 2012-12-25 spie/paper.tex
going oing going

@@
   Automated 3D modeling of building interiors is used in applications
-  such as virtual reality and environment mapping. Incorporating
-  images and texture mapping these models allows for photorealistic
-  visualizations of the data collected by such modeling systems. Pose
-  estimates obtained by these systems often suffer from inaccuracies,
-  resulting in visible discontinuities when successive images are
-  projected adjacently onto a surface for texturing. Existing methods
-  to stitch images together are often computationally expensive and
-  work independently of pose estimates and geometry information. We
-  propose a method to refine camera poses using both existing
-  estimates and geometry information, followed by two different
-  methods to composite images together, based on the uniformity of
-  available images. The effectiveness of our methods are demonstrated
-  on a number of disparate indoor environments.
+  such as virtual reality and environment mapping. Texturing these
+  models allows for photorealistic visualizations of the data
+  collected by such modeling systems. Camera poses obtained by these
+  systems often suffer from inaccuracies, resulting in visible
+  discontinuities when successive images are projected adjacently onto
+  a surface for texturing. Existing methods to stitch images together
+  are often computationally expensive and work independently of pose
+  estimates and geometry information. We propose a method to refine
+  camera poses using both existing estimates and geometry information,
+  followed by two different methods to composite images together,
+  based on the uniformity of available images. The effectiveness of
+  our methods is demonstrated on a number of different indoor
+  environments.
 \end{abstract}
@@
 The first step in automated 3D modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must recover its
+an environment's geometry. An indoor modeling system must recover its
 own poses within an environment while simultaneously reconstructing
@@
 texture mapping. In this paper we work mainly with models obtained
-through plane-fitting surfaces to point clouds generated by the
+by fitting planar surfaces to point clouds generated by the
 backpack system. CITATION. We have also developed an appropriate
-method to work with near-planar models, as described in APPENDIX
+method to work with near-planar triangular meshes, as described in APPENDIX
 SOMETHING.
@@
 aforementioned system in mind, it is easily generalizable to any other
-system, provided the required inputs of surface geometry, images with
-rough extrinsic pose estimates, and either provided or estimated
-intrinsic camera calibration matrices. An added benefit of our method
-is its relatively fast running time and modularity of each step,
+system, provided the required inputs of planar geometry, images with
+rough extrinsic pose estimates, and either known or estimated
+intrinsic camera calibration matrices. An important benefit of our method
+is its relatively low complexity and modularity of each step,
 allowing for quick tuning of parameters and easy accomodation of new
@@
 approaches to image matching and stitching, and their performance on
-our datasets. Section X contains our approach towards image matching,
+our datasets. Section X contains our approach towards image alignment,
 followed by Section X, which describes compositing approaches. Section
@@
 
-\subsection{Direct Mapping}
-\label{sec:directMapping}
-
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
@@
 minimizing any parallax effects due to real-world geometry not
-represented by our digital model. In other words, we wish to minimize
-the angle between the tile's normal vector and the camera axis for
-images selected for texture mapping. These two criteria can be met by
-maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
-as shown in Figure \ref{fig:scoringFunction}. Specifically, $d$ is the
-distance between the centers of a camera and a tile, and $\vec{n}$ and
-$\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively.
+accurately represented by our digital model. In other words, we wish
+to minimize the angle between the tile's normal vector and the camera
+axis for images selected for texture mapping. These two criteria can
+be met by maximizing the function $\frac{1}{d} (-1 \cdot \vec{c})
+\cdot \vec{n}$ as shown in Figure
+\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
+the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
+the directions of the plane's normal and the camera axis respectively.
 
@@
 many image boundaries with abrupt discontinuities, due to significant
-misalignment between images, as a result of camera pose inaccuracies.
-
-\subsection{Mapping with Caching}
-\label{sec:mappingWithCaching}
-Since discontinuities occur where adjacent tiles select non-aligned
-images, it makes sense to take into account image selections made by
-neighboring tiles while texture mapping a given tile. By using the
-same image across tile boundaries, we can eliminate a discontinuity
-altogether. If this is not possible because a tile is not visible in
-images used by neighboring tiles, using similar images across tile
-boundaries also leads to less noticeable discontinuities.
-
-Essentially a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set of valid images. The first
-subset of images is the images selected by adjacent tiles that have
-already been textured. We must first check which of these images can
-map to $t$, and then of those, we make a choice according to the
-scoring function in Figure \ref{fig:scoringFunction}. Before reusing
-this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
-order to be considered a viable image, with $\alpha$ as the camera
-angle as shown in Figure \ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check the
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar, allowing us to minimize any differences
-in localization error as well as a parallax effects. Again, if no
-viable image is found according to the same criteria, we search the
-entire set of candidate images, selecting based on the same scoring
-function from Figure \ref{fig:scoringFunction}.
-
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(b). As compared to Figure
-\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
-amount of remaining seams suggests that despite our high volume of
-images, image selection alone cannot produce seamless textures. Camera
-matrices, or the image projections themselves, have to be adjusted in
-order to reliably generate clean textures.
+misalignment between images.
+Given our high number of input images, one approach might be to more intelligently only select images that match up well, but the far more robust solution is to match up images directly such that we maximize our amount of useful images.
 
@@
 
-Image projections can also be aligned by iteratively adjusting camera poses to maximize matches.
-This is generally done over 6 degrees of freedom.
-CITATION.
-Applying the approach in the LIU2010INDOOR paper however, results again in error accumulation and drift as shown in Figure \ref{fig:mosaic3D}(a).
-Furthermore, such nonlinear optimization approaches have an extremely high complexity and runtime, and the entire solution must be recomputed given any changes in input data.
+Image projections can also be aligned by iteratively adjusting camera
+poses to maximize matches. This is generally done over 6 degrees of
+freedom. CITATION. Applying the approach in the LIU2010INDOOR paper
+however, results again in error accumulation and drift as shown in
+Figure \ref{fig:mosaic3D}(a). Furthermore, such nonlinear optimization
+approaches have an extremely high complexity and runtime, and the
+entire solution must be recomputed given any changes in input data.
 
-\section{Our Image Alignment with Cool Name}
+\section{Efficient Image Alignment with Geometry Information}
+
+In this section, we describe our method of efficient and robust image
+alignment. Our approach consists of four parts. First, all images are
+projected onto the surface and rotated such that detected lines within
+them are parallel to lines comprising the surface's boundary and
+intersection with other surfaces. Next, these projections are shifted
+such that interior lines near surface intersections are matched
+up. Following this, occlusion checks are performed across each image
+to remove invalid parts of each image for the target surface. These
+first three steps are all image-independent and can be considered
+pre-processing steps and performed in parallel. Finally, we detect
+SIFT feature matches between pairs of images and solve a linear least
+squares problem in 2D to maximize matches.
+
+\subsection{Geometry-based Alignment}
+\label{sec:projectionAndRotation}
+After computing each image's projection onto the target surface, as
+described in Section \ref{sec:simpleTextureMapping}, we can detect
+lines in the projections using Hough transforms. Experience and
+intuition show that walls in indoor environments contain linear
+features that are either horizontal or vertical, often corresponding
+to doors, windows, posters, etc. Thus, when texturing walls, we rotate
+images in 2D such that dominant lines are made to be horizontal or
+vertical. Though not as relevant in our datasets, this can be extended
+such that lines are oriented with a wall's boundaries, for example in
+areas with a slanted roof.
+
+At this point in time, image occlusions have not been accounted
+for. As a result, some image projections contain texture that should
+project to an adjacent surface, generally with a linear boundary where
+the two surfaces meet. If this linear boundary is detected by Hough
+transform, it makes sense to rotate and align this boundary such that
+the visual boundary between two surfaces matches the physical boundary
+in our digital model.
+
+To perform the rotation and alignment, we do MAGIC.  Then we indicate
+that magic has been done so that in the next step stuff is good. Mark
+as anchor images.
+
+\subsection{Image Occlusion}
+get from github i guess i dunno. or check avz email
+
+\subsection{2D Feature Alignment}
+\label{sec:robustSIFTFeatureMatching}
+Our next step is to align overlapping images by searching for
+corresponding points between all pairs of overlapping images. We use
+SIFT features for their high detection rate, and choose to use feature
+alignment rather than intensity-based alignment due to the differences
+in lighting as well as possible occlusion among our images, both of
+which feature alignment is less sensitive to \cite{lai1999robust,
+  lowe1999object, mikolajczyk2005performance, szeliski2006image}.
+SIFTGPU MORE CITATION SIFT matches determine $d^x$ and $d^y$ distances
+between each pair of features for two images on the plane, though
+these distances may not always be the same for different
+features. Since indoor environments often contain repetitive features
+such as floor tiles or doors, we need to ensure that SIFT-based
+distances are reliable. In order to mitigate the effect of incorrect
+matches and outliers, the RANSAC framework \cite{fischler1981random}
+is used for a robust estimate of the optimal $d^x_{i,j}$ and
+$d^y_{i,j}$ distances between two images $i$ and $j$. The RANSAC
+framework handles the consensus-building machinery, and requires a
+fitting function and a distance function. For this application, the
+fitting function simply finds the average distance between matches in
+a pair of images. The distance function for a pair of points is chosen
+to be the difference between those points' SIFT match distance and the
+average distance computed by the fitting function. We use a 10 pixel
+outlier threshold, so that SIFT matches are labeled as outliers if
+their horizontal or vertical distances are not within 10 pixels of the
+average distance computed by the fitting function.
+
+We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
+of images to refine their positions using least squares. Recall that
+there are a total of $M^{2}$ possible pairs of images, though we only
+generate distances between images that overlap at SIFT feature
+points. Given these distances and the original image location
+estimates, we can solve a least squares problem
+($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
+to estimate the location of the images on the plane. The
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
+location of each image on the plane for $1 \dots M$. The optimal $x$
+and $y$ locations are obtained in the same way, so we only consider
+the $x$ locations here:
+
+\[\vec{\beta} =
+\begin{pmatrix}
+  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
+\end{pmatrix}
+\]
+
+The $N \times (M+1)$ dimensional matrix $A$ is constructed with one
+row for each pair of images with measured distances produced by the
+SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the
+columns corresponding to the two images in the pair. For example, the
+matrix below indicates a SIFT-based distance between images 1 and 2,
+images 1 and 3, images 2 and 3, etc.
+\[
+A =
+\begin{pmatrix}
+  -1 & 1 & 0 & \cdots & 0 & 0\\
+  -1 & 0 & 1 & \cdots & 0 & 0\\
+  0 & -1 & 1 & \cdots & 0 & 0\\
+  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
+  0 & 0 & 0 & \cdots & 1 & 0 \\
+  0 & 0 & 0 & \cdots & -1 & 1 \\
+  1 & 0 & 0 & \cdots & 0 & 0 \\
+\end{pmatrix}
+\]
+If only relative distances between images are included then there is
+no way to determine the absolute location of any of the images and the
+matrix becomes rank deficient. To fix this we choose the first image
+to serve as the anchor for the rest, meaning all the absolute
+distances are based on its original location. This is done by adding a
+row with a $1$ in the first column and the rest zeros.
+
+Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
+constructed using the SIFT-based distances generated earlier in the
+RANSAC matching stage. The last element in the observation vector is
+the location of the first image determined by its original noisy
+localization, from \cite{chen2010indoor, liu2010indoor}. Thus
+$\vec{\gamma}$ can be written as:
+
+\[
+\vec{\gamma}^T =
+\begin{pmatrix}
+  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
+\end{pmatrix}
+\]
+
+The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
+\vec{\gamma}||_2^2$ results in a set of image locations on the plane
+that best honors all the SIFT-based distance measurements between
+images. In practice there is often a break in the chain of images,
+meaning that no SIFT matches are found between one segment of the
+plane and another. In this case we add rows to the $A$ matrix and
+observations to the $\vec{\gamma}$ vector that contain the original
+noisy $x$ and $y$ distance estimates from the original camera
+poses. Another way to do this is to add rows for all neighboring pairs
+of images and solve a weighted least squares problem where the SIFT
+distances are given a higher weight i.e. 1, and the noisy distances
+generated by the original camera poses \cite{chen2010indoor,
+  liu2010indoor} are given a smaller weight e.g. 0.01.
+
+After completing this same process for the $y$ dimension as well, and
+making the resultant shifts, our images overlap and match each other
+with far greater accuracy. Applying the tile caching method from
+Section \ref{sec:mappingWithCaching} on these rotated and shifted
+images results in the significant improvements shown in Figure
+\ref{fig:compareAll}(c), as compared to Figure
+\ref{fig:compareAll}(b).
+
 \section{Image Compositing}
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
+  \caption{(a) Undistorted fisheye images for vertical planes are
+    tilted, but their effective camera axis is more or less normal to
+    the plane. (b) The effective camera axis for ceilings is at an
+    angle with respect to the plane normal. (c) Wall images are
+    cropped to be rectangular.}
+  \label{fig:projectionAngles}
+\end{figure}
+
+As mentioned earlier, the mobile backpack system used to capture data
+in this paper contains 2 cameras with $180^\circ$ fisheye lenses
+facing to the right and left. Since most human operators do not carry
+the backpack in a perfectly upright position and are bent forwards at
+15 to 20 degrees with respect to the vertical direction, the
+undistorted fisheye images are head on with respect to vertical walls,
+but at an angle with respect to horizontal floors and ceilings. This
+is depicted for wall and ceiling planes in Figures
+\ref{fig:projectionAngles}(a) and \ref{fig:projectionAngles}(b)
+respectively. These oblique camera angles for ceilings translate into
+textures that span extremely large areas once projected, as shown in
+Figure \ref{fig:projectionAngles}(b). Using the tile-based texture
+mapping criteria from Figure \ref{fig:scoringFunction}, such
+projections have highly varying scores depending on the location on
+the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
+tiling approach in Section \ref{sec:simpleTextureMapping} is a
+reasonable choice for texturing floors and ceilings, as it uses the
+parts of image projections that are viable choices for their
+respective plane locations, e.g. areas near point A in Figure
+\ref{fig:projectionAngles}(b), but not near point B.
+
+\subsection{Tile-Mapping with Caching}
+\label{sec:mappingWithCaching}
+Since discontinuities occur where adjacent tiles select non-aligned
+images, it makes sense to take into account image selections made by
+neighboring tiles while texture mapping a given tile. By using the
+same image across tile boundaries, we can eliminate a discontinuity
+altogether. If this is not possible because a tile is not visible in
+images used by neighboring tiles, using similar images across tile
+boundaries also leads to less noticeable discontinuities.
+
+Essentially a caching mechanism, we select the best image for a tile
+$t$ by searching through two subsets of images for a viable candidate,
+before searching through the entire set of valid images. The first
+subset of images is the images selected by adjacent tiles that have
+already been textured. We must first check which of these images can
+map to $t$, and then of those, we make a choice according to the
+scoring function in Figure \ref{fig:scoringFunction}. Before reusing
+this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
+order to be considered a viable image, with $\alpha$ as the camera
+angle as shown in Figure \ref{fig:scoringFunction}.
+
+If no satisfactory image is found in the first subset, we check the
+second subset of images, consisting of those taken near the ones in
+the first subset, both spatially and temporally. These images are not
+the same as the ones used for neighboring tiles, but are taken at a
+similar location and time, suggesting that their localization and
+projection are quite similar, allowing us to minimize any differences
+in localization error as well as a parallax effects. Again, if no
+viable image is found according to the same criteria, we search the
+entire set of candidate images, selecting based on the same scoring
+function from Figure \ref{fig:scoringFunction}.
+
+The result of this caching approach is shown in Figure
+\ref{fig:compareAll}(b). As compared to Figure
+\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
+amount of remaining seams suggests that despite our high volume of
+images, image selection alone cannot produce seamless textures. Camera
+matrices, or the image projections themselves, have to be adjusted in
+order to reliably generate clean textures.
+
+\subsection{Shortest}
+For wall planes however, most images are taken from close distances
+and more or less head-on angles, resulting in higher resolution
+fronto-parallel projections. As a result, for each tile on a wall
+plane, the scoring function of Figure \ref{fig:scoringFunction} is
+relatively flat with respect to a large number of captured images, as
+they are all more or less head on. Thus, the scoring function is less
+significant for walls, and it is conceivable to use a different
+texturing strategy for them so as to minimize visible seams in texture
+mapped planes. This can be done by choosing the smallest possible set
+of images that (a) covers the entire plane and (b) minimizes the
+amount of visible seams between them. A straightforward cost function
+that accomplishes the latter is the Sum of Squared Differences (SSD)
+of pixels in overlapping regions between all pairs of images, after
+they have been rotated as described in Section
+\ref{sec:projectionAndRotation}. Minimizing this cost function
+encourages image boundaries to occur either in featureless areas, such
+as bare walls, or in areas where images match extremely well.
+
+To cover the entirety of a plane, our problem can be defined as
+minimally covering a polygon i.e. the plane, using other polygons of
+arbitrary geometry i.e. image projections, with the added constraint
+of minimizing the cost function between chosen images.  This is a
+complex problem, though we can take a number of steps to simplify it.
+
+Given that wall-texture candidate images are taken from more or less
+head-on angles, and assuming only minor rotations are made in Section
+\ref{sec:projectionAndRotation}, we can reason that their projections
+onto the plane are approximately rectangular. By cropping them all to
+be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
+problem becomes the conceptually simpler one of filling a polygon with
+rectangles, such that the sum of all costs between each pair of
+rectangles is minimal. We thus also retain the advantages of working
+with rectangular units, as explained in Section
+\ref{sec:simpleTextureMapping}.
+
+The location and orientation of the cameras and the fisheye lenses on
+the acquisition backpack is such that images nearly always contain the
+entirety of the floor to ceiling range of wall planes. Images are
+therefore rarely projected with one above another when texturing wall
+planes. In essence, we need only to ensure lateral coverage of wall
+planes, e.g. from left to right, as our images provide full vertical
+coverage themselves. We can thus construct a Directed Acyclic Graph
+(DAG) from the images, with edge costs defined by the SSD cost
+function, and solve a simple shortest path problem to find an optimal
+subset of images with regard to the cost function \cite{dijkstra}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{dagCreation.pdf}
+  \caption{DAG construction for the image selection process. \\}
+  \label{fig:dagCreation}
+\end{figure}
+
+Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
+from overlapping images of a long hallway. Images are sorted by
+horizontal location left to right, and become nodes in a
+graph. Directed edges are placed in the graph from left to right
+between overlapping images. The weights of these edges are determined
+by the SSD cost function. Next, we add two artificial nodes, one start
+node representing the left border of the plane, and one end node
+representing the right border of the plane. The left(right) artificial
+node has directed edges with equal cost $C_0$ to(from) all images that
+meet the left(right) border of the plane.
+
+We now solve the shortest path problem from the start node to the end
+node. This results in a set of images completely covering the plane
+horizontally, while minimizing the cost of seams between images.
+
+In rare cases where the vertical dimension of the plane is not
+entirely covered by one or more chosen images, we are left with holes
+where no images are selected to texture. To address this, we solve for
+a new shortest path after modifying the edges chosen by the original
+shortest path solution such that they have higher cost than all other
+edges in the DAG, and solve for a new shortest path. This ensures that
+these edges are not chosen again unless they are the only available
+option. Our second shortest path solution results in a new set of
+chosen images, of which we only retain those that cover areas not
+covered by the first set. This process can be repeated as many times
+as needed, until holes are no longer present. This method is not as
+optimal as a 2D-coverage solution would be, but it is a fast
+approximation, and adequately handles the few holes we encounter.
+
+With this completed, we have now mapped every location on the plane to
+at least one image, and have minimized the number of images, as well
+as the discontinuities between their borders. As seen in Figure
+\ref{fig:compareAll}(d), this seam minimization method has fewer
+visible discontinuities than Figure \ref{fig:compareAll}(c)
+corresponding to the tile caching approach\footnote{In Figure
+  \ref{fig:compareAll}(d), we arbitrarily chose one image for
+  texturing where images overlap, as blending will be discussed in the
+  next section.}. This is especially evident when comparing the
+posters in the images, which have clear misalignment over seams in
+Figure \ref{fig:compareAll}(c), but are much more aligned in Figure
+\ref{fig:compareAll}(d). This is because the seam minimization
+approach directly reduces the cost of each image boundary, while the
+tile caching method uses a scoring function that only approximates
+this effect. Furthermore, seam minimization guarantees the best
+selection of images, while the sequential tile caching method may
+select images early on that turn out to be poor choices once
+subsequent tiles have been processed. The seam minimization approach
+is also far less intensive in terms of memory usage and runtime, both
+during texture generation and rendering, as it does not require
+discretizing planes or images\footnote {For the seam minimization
+  approach, occlusion checks are performed over the entirety of each
+  image to determine available areas for texture mapping. Since indoor
+  environments mostly consist of vertical or horizontal surfaces with
+  high amounts of right angles, image projections remain largely
+  rectangular after masking out occluded areas. Therefore, as a
+  preprocessing step, we can recursively split each image into
+  rectangular pieces and check for occlusions in a similar manner as
+  in the tiling process.  }.
+
+In the context of texturing an entire 3D planar model, we choose to
+apply the seam minimization approach on walls, due to its superior
+output when provided with head-on images. Floors and ceilings however,
+given their many images taken at oblique angles, are textured using
+the tile caching method.
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=6in]{pipelineimages.pdf}
+%   \caption{Textures corresponding to each step in our texture
+%   mapping pipeline.}
+%   \label{fig:pipelineimages}
+% \end{figure*}
+
+\subsection{Blending}
+\label{sec:blending}
+We now apply the same blending process to the two texturing methods:
+image alignment followed by either tile caching or seam minimization.
+
+Although the preprocessing steps and image selection in both methods
+attempt to minimize all mismatches between images, there are
+occasional unavoidable discontinuities in the final texture due to
+different lighting conditions or inaccuracies in planar geometry or
+projection. These can however be treated and smoothed over by applying
+alpha blending over image seams.  Whether the units we are blending
+are rectangularly-cropped images or rectangular tiles, we can apply
+the same blending procedure, as long as we have a guaranteed overlap
+between units to blend over.
+
+For the tile caching method, we can ensure overlap by texturing a
+larger tile than needed for display. For example, for a rendered tile
+$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
+\times (l_1 + l_2)$ in size. For the seam minimization method, we have
+already ensured overlap between images. To enforce consistent blending
+however, we add a minimum required overlap distance while solving the
+shortest path problem in Section
+\ref{sec:seamMinimization}. Additionally, if images overlap in a
+region greater than the overlap distance, we only apply blending over
+an area equal to the overlap distance.
+
+After blending pixels linearly across overlapping regions using alpha
+blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
+and \ref{fig:compareAll}(f) show the blended versions of Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
+is clear that the seam minimization approach still exhibits better
+alignment and fewer seams than the tile-caching method, as Figure
+\ref{fig:compareAll}(f) has the best visual quality among the textures
+in Figure \ref{fig:compareAll}.
+
 \section{Results and Conclusions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%poop below
-\section{PARTS OF MANUSCRIPT}
-
-This section describes the normal structure of a manuscript and how
-each part should be handled.  The appropriate vertical spacing between
-various parts of this document is achieved in LaTeX through the proper
-use of defined constructs, such as \verb|\section{}|.  In LaTeX,
-paragraphs are separated by blank lines in the source file.
-
-At times it may be desired, for formatting reasons, to break a line
-without starting a new paragraph.  This situation may occur, for
-example, when formatting the article title, author information, or
-section headings.  Line breaks are inserted in LaTeX by entering
-\verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired
-location.
-
-%%%%% Sometimes it is necessary to precede the double slash by
-%%%%% \verb|\protect| to get the desired result, for example, in
-%%%%% article titles.
-
-%% -----------------------------------------------------------
-\subsection{Title and Author Information}
-\label{sec:title}
-
-The article title appears centered at the top of the first page.  The
-title font is 16 point, bold.  The rules for capitalizing the title
-are the same as for sentences; only the first word, proper nouns, and
-acronyms should be capitalized.  Avoid using acronyms in the title.
-Keep in mind that people outside your area of expertise might read
-your article.  Appendix~\ref{sec:misc} contains more about acronyms.
-
-The list of authors immediately follows the title after a blank
-vertical space of about 7 mm.  The font is 12 point, normal with each
-line centered.  The authors' affiliations and addresses follow the
-author list after another blank space of about 4 mm, also in 12-point,
-normal font and centered.  Do not use acronyms in affiliations and
-addresses. For multiple affiliations, each affiliation should appear
-on a new line, separated from the following address by a semicolon.
-Italicized superscripts may be used to identify the correspondence
-between the authors and their respective affiliations.  Further author
-information, such as e-mail address, complete postal address, and
-web-site location, may be provided in a footnote by using
-\verb|\authorinfo{}|, as demonstrated above.
-
-When the abbreviated title or author information is too long to fit on
-one line, multiple lines may be used; insert line breaks appropriately
-to achieve a visually pleasing format.  The proper spacing of one and
-one-half lines between the title, author list, and their affiliations
-is achieved with the command \verb|\skiplinehalf| defined in {\tt
-  spie.cls}.
-
-%% -----------------------------------------------------------
-\subsection{Abstract and Keywords}
-The title and author information is immediately followed by the
-Abstract. The Abstract should concisely summarize the key findings of
-the paper.  It should consist of a single paragraph containing no more
-than 200 words.  The Abstract does not have a section number.  A list
-of up to ten keywords should immediately follow the Abstract after a
-blank line.  These keywords will be included in a searchable database
-at SPIE.
-
-%% -----------------------------------------------------------
-\subsection{Body of Paper}
-The body of the paper consists of numbered sections that present the
-main findings.  These sections should be organized to best present the
-material.  See Sec.~\ref{sec:sections} for formatting instructions.
-
-%% -----------------------------------------------------------
-\subsection{Appendices}
-Auxiliary material that is best left out of the main body of the
-paper, for example, derivations of equations, proofs of theorems, and
-details of algorithms, may be included in appendices.  Appendices are
-enumerated with uppercase Latin letters in alphabetic order, and
-appear just before the Acknowledgments and References.
-
-%% -----------------------------------------------------------
-\subsection{Acknowledgments}
-In the Acknowledgments section, appearing just before the References,
-the authors may credit others for their guidance or help.  Also,
-funding sources may be stated.  The Acknowledgments section does not
-have a section number.
-
-%% -----------------------------------------------------------
-\subsection{References}
-The References section lists books, articles, and reports that are
-cited in the paper.  It does not have a section number.  The
-references are numbered in the order in which they are cited.
-Examples of the format to be followed are given at the end of this
-document.
-
-The reference list at the end of this document is created using
-BibTeX, which looks through the file {\tt report.bib} for the entries
-cited in the LaTeX source file.  The format of the reference list is
-determined by the bibliography style file {\tt spiebib.bst}, as
-specified in the \verb|\bibliographystyle{spiebib}| command.
-Alternatively, the references may be directly formatted in the LaTeX
-source file.
-
-For books\cite{Lamport94,Alred03,Goossens97} the listing includes the
-list of authors, book title (in italics), page or chapter numbers,
-publisher, city, and year of publication.  A reference to a journal
-article\cite{Metropolis53} includes the author list, title of the
-article (in quotes), journal name (in italics, properly abbreviated),
-volume number (in bold), inclusive page numbers, and year.  By
-convention\cite{Lamport94}, article titles are capitalized as
-described in Sec.~\ref{sec:title}.  A reference to a proceedings paper
-or a chapter in an edited book\cite{Gull89a} includes the author list,
-title of the article (in quotes), conference name (in italics), if
-appropriate, editors, volume or series title (in italics), volume
-number (in bold), if applicable, inclusive page numbers, publisher,
-city, and year.  References to an article in the SPIE Proceedings may
-include the conference name, as shown in Ref.~\citenum{Hanson93c}.
-
-Citations to the references are made using superscript numerals, as
-demonstrated in the preceding paragraph.  One may also directly refer
-to a reference within the text, e.g., ``as shown in
-Ref.~\citenum{Metropolis53} ..."
-
-%% -----------------------------------------------------------
-\subsection{Footnotes}
-Footnotes\footnote{Footnotes are indicated as superscript symbols to
-  avoid confusion with citations.} may be used to provide auxiliary
-information that doesn't need to appear in the text, e.g., to explain
-measurement units.  They should be used sparingly, however.
-
-Only nine footnote symbols are available in LaTeX. If you have more
-than nine footnotes, you will need to restart the sequence using the
-command \verb|\footnote[1]{Your footnote text goes here.}|. If you
-don't, LaTeX will provide the error message {\tt Counter too large.},
-followed by the offending footnote command.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SECTION FORMATTING} \label{sec:sections}
-
-Section headings are centered and formatted completely in uppercase
-11-point bold font.  Sections should be numbered sequentially,
-starting with the first section after the Abstract.  The heading
-starts with the section number, followed by a period.  In LaTeX, a new
-section is created with the \verb|\section{}| command, which
-automatically numbers the sections.
-
-Paragraphs that immediately follow a section heading are leading
-paragraphs and should not be indented, according to standard
-publishing style\cite{Lamport94}.  The same goes for leading
-paragraphs of subsections and sub-subsections.  Subsequent paragraphs
-are standard paragraphs, with 14-pt.\ (5 mm) indentation.  An extra
-half-line space should be inserted between paragraphs.  In LaTeX, this
-spacing is specified by the parameter \verb|\parskip|, which is set in
-{\tt spie.cls}.  Indentation of the first line of a paragraph may be
-avoided by starting it with \verb|\noindent|.
-
-%% -----------------------------------------------------------
-\subsection{Subsection Attributes}
-
-The subsection heading is left justified and set in 11-point, bold
-font.  Capitalization rules are the same as those for book titles.
-The first word of a subsection heading is capitalized.  The remaining
-words are also capitalized, except for minor words with fewer than
-four letters, such as articles (a, an, and the), short prepositions
-(of, at, by, for, in, etc.), and short conjunctions (and, or, as, but,
-etc.).  Subsection numbers consist of the section number, followed by
-a period, and the subsection number within that section.
-
-%% -----------
-\subsubsection{Sub-subsection attributes}
-The sub-subsection heading is left justified and its font is 10 point,
-bold.  Capitalize as for sentences.  The first word of a
-sub-subsection heading is capitalized.  The rest of the heading is not
-capitalized, except for acronyms and proper names.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{FIGURES AND TABLES}
-
-Figures are numbered in the order of their first citation.  They
-should appear in numerical order and on or after the same page as
-their first reference in the text.  Alternatively, all figures may be
-placed at the end of the manuscript, that is, after the Reference
-section.  It is preferable to have figures appear at the top or bottom
-of the page.  Figures, along with their captions, should be separated
-from the main text by at least 0.2 in.\ or 5 mm.
-
-Figure captions are centered below the figure or graph.  Figure
-captions start with the figure number in 9-point bold font, followed
-by a period; the text is in 9-point normal font; for example,
-``{\footnotesize{Figure 3.}  Original image...}".  See
-Fig.~\ref{fig:example} for an example of a figure caption.  When the
-caption is too long to fit on one line, it should be justified to the
-right and left margins of the body of the text.
-
-Tables are handled identically to figures, except that their captions
-appear above the table.
-%% Use following command to specify that graphics file is in a
-%% directory other than this LaTeX source file.  Note use of / to
-%% separate subdirectories, for UNIX and Windows OS.
-%% \graphicspath{{H:/HANSON/SPIESTY/}} tabular environment useful for
-%% creating an array of images
-% -------------
-\begin{figure}
-  \begin{center}
-    \begin{tabular}{c}
-      \includegraphics[height=7cm]{naive.jpg}
-    \end{tabular}
-  \end{center}
-  \caption[example]
-  % >>>> use \label inside caption to get Fig. number with \ref{}
-  { \label{fig:example} Figure captions are used to describe the
-    figure and help the reader understand it's significance.  The
-    caption should be centered underneath the figure and set in
-    9-point font.  It is preferable for figures and tables to be
-    placed at the top or bottom of the page. LaTeX tends to adhere to
-    this standard.}
-\end{figure}
-% -------------
-
-For further details concerning the inclusion of grayscale and color
-images, consult SPIE's {\it Author Guide for Publication and
-  Presentation}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix    %>>>> this command starts appendixes
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{MISCELLANEOUS FORMATTING DETAILS} \label{sec:misc}
-
-It is often useful to refer back (or forward) to other sections in the article.
-Such references are made by section number.
-When a section reference starts a sentence, Section is spelled out; otherwise use its abbreviation, for example, ``In Sec.~2 we showed..." or ``Section~2.1 contained a description...".
-References to figures, tables, and theorems are handled the same way.
-
-At the first occurrence of an acronym, spell it out, followed by the acronym in parentheses, e.g., noise power spectrum (NPS).
-
-%%-----------------------------------------------
-\subsection{Formatting Equations} 
-Equations may appear in line with the text, if they are simple, short, and not of major importance; e.g., $\beta = b/r$.
-Important equations appear on their own line.
-Such equations are centered.
-For example, ``The expression for the minus-log-posterior is
-	\begin{equation}
-	\label{eq:alpha}
-\phi = |{\rm\bf y} - {\rm\bf A}{\rm\bf x}|^2 + \alpha \log p({\rm\bf x}) \, ,
-	\end{equation}
-where $\alpha$ determines the strength of ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.
-
-Equations are considered to be part of a sentence and should be punctuated accordingly.
-In the above example, a comma follows the equation because the next line is a subordinate clause.
-If the equation ends the sentence, a period should follow the equation.
-The line following an equation should not be indented unless it is meant to start a new paragraph.
-Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.
-
-References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:alpha}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..."  Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks.
-
-%%-----------------------------------------------------------
-\subsection{Formatting Theorems}
-
-To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified and followed by a period.
-The text of the theorem continues on the same line in normal, 10-point font.
-For example,
-
-\noindent{\bf Theorem 1.} For any unbiased estimator...
-
-Formal statements of lemmas and algorithms receive a similar treatment.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{SOME LATEX GUIDANCE} \label{sec:latex}
-
-%%-----------------------------------------------------------
-\subsection{Margins and PostScript Fonts}
-
-Manuscripts submitted electronically to as PostScript (PS) files must have the correct margins.
-LaTeX margins are related to the document's paper size.
-The paper size is set at two separate places in the process of creating a PS file.
-The first place is in {\tt latex}.
-The default in {\tt article.tex}, on which {\tt spie.cls} is based, is USA letter paper.
-To format a document for A4 paper, the first line of the LaTeX source file should be \verb|\documentclass[a4paper]{spie}|.
-
-The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.
-The application DVIPS is typically used to convert the DVI file to a PS file.
-DVIPS has its own default paper size, which can be overridden with the option ``{\tt -t letter}" or ``{\tt -t a4}".
-If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command, for example.
-
-Another DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file.
-This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.
-The option ``{\tt -P pdf}" makes DVIPS include these fonts in its output PS file.
-
-%%-----------------------------------------------------------
-\subsection{Bold Math Symbols}
-
-The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX.
-It also provides many useful capabilities for creating elaborate mathematical expressions.
-You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
-\verb+\usepackage[]{amsmath}+ \\[1ex]
-Then for bold math symbols use \verb+\boldsymbol+ in equations, e.g., 
-\verb+$\boldsymbol{\pi}$+ 
-yields a bold pi.  You can make it easier to use by defining a command:\\[1ex]
-\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
-and then using it like so \verb+$\bm{\pi}$+.
-
-Not all math symbols are available in bold.
-In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+.
-This command approximates a bold character with a superposition of several, slightly displaced unbold characters.
-
-If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
-Then, in the title, use something like:\\[1ex]
-\verb+\title{Estimation of {\LARGE$\boldsymbol\alpha$} by a Monte Carlo technique}+ \\[1ex]
-Note that the command to create the alpha character is enclosed within braces to form a self-contained environment.
-The use of \verb+\LARGE+ in this example may not be needed when using nondefault font packages, such as the {\tt times} package, because of how the article title is handled in {\tt spie.cls}.
-
-%%-----------------------------------------------------------
-\subsection{Uppercase letters and special symbols in BibTex}
-
-BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case.
-BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.
-
-The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged in braces.
-Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
-\verb+ @article{Kaczmarz37,+ \\ 
-\verb+ author = "S. Kaczmarz",+ \\ 
-\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen linearer {G}leichungen",+ \\ 
-\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
-\verb+ volume = "A35",+ \\ 
-\verb+ pages  = "355-357",+ \\	
-\verb+ year   = "1937"	} + \\[1ex]
-This example shows the use of both umlauts and uppercase letters.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}
-
-This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.
+\label{sec:resultsAndConclusions}
 

### 2012-12-25 spie/_region_.tex
text doneish

--- 2012-12-23 spie/_region_.tex
@@
 
-\message{ !name(paper.tex) !offset(-42) }
-\documentclass[]{spie}  %>>> use for US letter paper
-%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
-%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
-%% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
-%  The following command loads a graphics package to include images 
-%  in the document. It may be necessary to specify a DVI driver option,
-%  e.g., [dvips], but that may be inappropriate for some LaTeX 
-%  installations. 
-\usepackage[]{graphicx}
+\message{ !name(paper.tex) !offset(594) }
+\subsection{Blending}
+\label{sec:blending}
+We now apply the same blending process to the two texturing methods:
+tile caching or seam minimization.
 
-\title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
+Although the image alignment steps and image selection in both methods
+attempt to minimize all mismatches between images, there are
+occasional unavoidable discontinuities in the final texture due to
+different lighting conditions or inaccuracies in planar geometry or
+projection. These can however be treated and smoothed over by applying
+alpha blending over image seams.  Whether the units we are blending
+are rectangularly-cropped images or rectangular tiles, we can apply
+the same blending procedure, as long as we have a guaranteed overlap
+between units to blend over.
 
-%>>>> The author is responsible for formatting the 
-%  author list and their institutions.  Use  \skiplinehalf 
-%  to separate author list from addresses and between each address.
-%  The correspondence between each author and his/her address
-%  can be indicated with a superscript in italics, 
-%  which is easily obtained with \supit{}.
+For the tile caching method, we can ensure overlap by texturing a
+larger tile than needed for display. For example, for a rendered tile
+$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
+\times (l_1 + l_2)$ in size. We have found $l_2 = \frac{l_1}{2}$ to provide a
+good amount of blending without blurring features. For the seam
+minimization method, we have already ensured overlap between
+images. To enforce consistent blending however, we add a minimum
+required overlap distance while solving the shortest path problem in
+Section \ref{sec:seamMinimization}. Additionally, if images overlap in
+a region greater than the overlap distance, we only apply blending
+over an area equal to the overlap distance.
 
-\author{Peter Cheng, Michael Anderson, Stewart He, Avideh Zakhor
-\skiplinehalf
-University of California, Berkeley ; \\
-}
+After blending pixels linearly across overlapping regions using alpha
+blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
+and \ref{fig:compareAll}(f) show the blended versions of Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
+is clear that the seam minimization approach still exhibits better
+alignment and fewer seams than the tile-caching method, as Figure
+\ref{fig:compareAll}(f) has the best visual quality among the textures
+in Figure \ref{fig:compareAll}.
 
-%>>>> Further information about the authors, other than their 
-%  institution and addresses, should be included as a footnote, 
-%  which is facilitated by the \authorinfo{} command.
-
-\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
-%%>>>> when using amstex, you need to use @@ instead of @
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%>>>> uncomment following for page numbers
-% \pagestyle{plain}    
-%>>>> uncomment following to start page numbering at 301 
-%\setcounter{page}{301}
-
-\message{ !name(paper.tex) !offset(197) }
+\message{ !name(paper.tex) !offset(604) }
 

### 2012-12-25 spie/paper.tex
text doneish

@@
 
-The first step in automated 3D modeling is the physical scanning of
-an environment's geometry. An indoor modeling system must recover its
-own poses within an environment while simultaneously reconstructing
-the 3D structure of the environment itself. CITATION. This is known as
-the simultaneous localization and mapping (SLAM) problem, and is
-generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment.
+The first step in automated 3D modeling is the physical scanning of an
+environment's geometry. An indoor modeling system must recover its own
+poses within an environment while simultaneously reconstructing the 3D
+structure of the environment itself. CITATION. This is known as the
+simultaneous localization and mapping (SLAM) problem, and is generally
+solved by taking readings from laser range scanners, cameras, and
+inertial measurement units (IMUs) at multiple locations within the
+environment.
 
@@
 information and images, environment geometry is required as well for
-texture mapping. In this paper we work mainly with models obtained
-by fitting planar surfaces to point clouds generated by the
-backpack system. CITATION. We have also developed an appropriate
-method to work with near-planar triangular meshes, as described in APPENDIX
+texture mapping. In this paper we work mainly with models obtained by
+fitting planar surfaces to point clouds generated by the backpack
+system. CITATION. We have also developed an appropriate method to work
+with near-planar triangular meshes, as described in APPENDIX
 SOMETHING.
@@
 rough extrinsic pose estimates, and either known or estimated
-intrinsic camera calibration matrices. An important benefit of our method
-is its relatively low complexity and modularity of each step,
+intrinsic camera calibration matrices. An important benefit of our
+method is its relatively low complexity and modularity of each step,
 allowing for quick tuning of parameters and easy accomodation of new
@@
 followed by Section X, which describes compositing approaches. Section
-X contains further results and conclusions.
+X contains further results and conclusions, as well as areas for
+future work.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 many image boundaries with abrupt discontinuities, due to significant
-misalignment between images.
-Given our high number of input images, one approach might be to more intelligently only select images that match up well, but the far more robust solution is to match up images directly such that we maximize our amount of useful images.
+misalignment between images. Given our high number of input images, it
+makese sense to intelligently select only the images that match up
+well, as performed in Section X, but for our solution to be robust, we
+must align images directly such that we maximize the accuracy of each image.
 
@@
 and matching. Images are then adjusted to maximize matches, either by
-directly calculating homographies between pairs of images, or by
+calculating homographies between pairs of images, or by
 modifying camera poses from 1 to 6 degrees of freedom.
@@
 references exist in the environment and are present within multiple
-images. This allows for accurate matching when texturing detailed
-objects at high resolutions CiTATION, or when creating outdoor
-panoramas CITATION. In contrast, our indoor environments have a high
+images. In contrast, our indoor environments have a high
 prevalence of bare surfaces, as well as repeating textures that cause
-difficulty in distinguishing features. The lack of strong reference
+difficulty in disambiguating features. This lack of strong reference
 points results in high uncertainty when matching images together.
@@
 \cite{autostitch}. Even with many features spread across this surface,
-the mosaicing produces errors that cause straight lines to appear as
-distorted, despite the fact that it was generated after careful hand
+the mosaicing produces errors that cause straight lines to appear distorted, despite the fact that it was generated after careful hand
 tuning. Many areas with fewer visual features simply failed outright
@@
 Figure \ref{fig:mosaic3D}(a). Furthermore, such nonlinear optimization
-approaches have an extremely high complexity and runtime, and the
+approaches IS IT? BETTER CHECK have high complexity and runtime, and the
 entire solution must be recomputed given any changes in input data.
@@
 such that interior lines near surface intersections are matched
-up. Following this, occlusion checks are performed across each image
-to remove invalid parts of each image for the target surface. These
-first three steps are all image-independent and can be considered
-pre-processing steps and performed in parallel. Finally, we detect
-SIFT feature matches between pairs of images and solve a linear least
-squares problem in 2D to maximize matches.
+up. Following this, occlusion checks are performed to remove invalid
+parts of each image for the target surface. These first three steps
+are all image-independent and are performed in parallel. Finally, we
+detect SIFT feature matches between pairs of images and solve a linear
+least squares problem in 2D to maximize matches.
+
+EVERYTHING IS IN 2D BECAUSE PITCH BECOMES WHATEVO
 
@@
 images in 2D such that dominant lines are made to be horizontal or
-vertical. Though not as relevant in our datasets, this can be extended
+vertical. Though not relevant in our datasets, this can be extrapolated
 such that lines are oriented with a wall's boundaries, for example in
@@
 the two surfaces meet. If this linear boundary is detected by Hough
-transform, it makes sense to rotate and align this boundary such that
+transform, the image is rotated and shifted in 2D such that
 the visual boundary between two surfaces matches the physical boundary
@@
 \subsection{Image Occlusion}
-get from github i guess i dunno. or check avz email
+get from github i guess i dunno. or check avz email. maybe put in appendix
 
@@
 SIFT features for their high detection rate, and choose to use feature
-alignment rather than intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lai1999robust,
-  lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-SIFTGPU MORE CITATION SIFT matches determine $d^x$ and $d^y$ distances
-between each pair of features for two images on the plane, though
-these distances may not always be the same for different
-features. Since indoor environments often contain repetitive features
-such as floor tiles or doors, we need to ensure that SIFT-based
-distances are reliable. In order to mitigate the effect of incorrect
-matches and outliers, the RANSAC framework \cite{fischler1981random}
-is used for a robust estimate of the optimal $d^x_{i,j}$ and
-$d^y_{i,j}$ distances between two images $i$ and $j$. The RANSAC
-framework handles the consensus-building machinery, and requires a
-fitting function and a distance function. For this application, the
-fitting function simply finds the average distance between matches in
-a pair of images. The distance function for a pair of points is chosen
-to be the difference between those points' SIFT match distance and the
-average distance computed by the fitting function. We use a 10 pixel
-outlier threshold, so that SIFT matches are labeled as outliers if
-their horizontal or vertical distances are not within 10 pixels of the
-average distance computed by the fitting function.
+alignment rather than pixel or intensity-based alignment due to the
+differences in lighting as well as possible occlusion among our
+images, both of which feature alignment is less sensitive to
+\cite{lai1999robust, lowe1999object, mikolajczyk2005performance,
+  szeliski2006image}.  SiftGPU, by PERSON CITATION, is used both for
+feature detection as well as pairwise matching. These matches
+determine $d^x$ and $d^y$ distances between each pair of features for
+two image projections, though these distances may not always be the
+same for different features. Since indoor environments often contain
+repetitive features such as floor tiles or doors, we need to ensure
+that SIFT-based distances are reliable. In order to mitigate the
+effect of incorrect matches and outliers, the RANSAC framework
+\cite{fischler1981random} is used for a robust estimate of the optimal
+$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
+$j$. The RANSAC framework handles the consensus-building machinery,
+and requires a fitting function and a distance function. For this
+application, the fitting function simply finds the average distance
+between matches in a pair of images. The distance function for a pair
+of points is chosen to be the difference between those points' SIFT
+match distance and the average distance computed by the fitting
+function. We use a 10 pixel outlier threshold, so that SIFT matches
+are labeled as outliers if their horizontal or vertical distances are
+not within 10 pixels of the average distance computed by the fitting
+function.
 
@@
 no way to determine the absolute location of any of the images and the
-matrix becomes rank deficient. To fix this we choose the first image
-to serve as the anchor for the rest, meaning all the absolute
-distances are based on its original location. This is done by adding a
-row with a $1$ in the first column and the rest zeros.
+matrix becomes rank deficient. From Section X, a number of images were
+anchored to geometry points, and thus their locations can be used to
+anchor the rest in place. In case no anchor images exist, we simply
+arbitrarily pick an image. In the above matrix, the first image is set
+to be such an anchor.
 
 Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
-constructed using the SIFT-based distances generated earlier in the
-RANSAC matching stage. The last element in the observation vector is
-the location of the first image determined by its original noisy
-localization, from \cite{chen2010indoor, liu2010indoor}. Thus
-$\vec{\gamma}$ can be written as:
+constructed using the SIFT-based distances generated in the RANSAC
+matching stage. Elements in the observation vector corresponding to
+anchor images are simply their locations as determined by the original
+noisy localization. Thus $\vec{\gamma}$ can be written as:
 
@@
 meaning that no SIFT matches are found between one segment of the
-plane and another. In this case we add rows to the $A$ matrix and
-observations to the $\vec{\gamma}$ vector that contain the original
-noisy $x$ and $y$ distance estimates from the original camera
-poses. Another way to do this is to add rows for all neighboring pairs
-of images and solve a weighted least squares problem where the SIFT
-distances are given a higher weight i.e. 1, and the noisy distances
-generated by the original camera poses \cite{chen2010indoor,
-  liu2010indoor} are given a smaller weight e.g. 0.01.
+plane and another. To solve this, we add rows to the $A$ matrix and
+observations to the $\vec{\gamma}$ vector corresponding to the
+original noisy distances. We then solve a weighted least squares
+problem where the SIFT distances and anchor values are given a high
+weight e.g. 1, while the noisy distances are given a smaller weight
+e.g. 0.01.
 
@@
 making the resultant shifts, our images overlap and match each other
-with far greater accuracy. Applying the tile caching method from
-Section \ref{sec:mappingWithCaching} on these rotated and shifted
-images results in the significant improvements shown in Figure
-\ref{fig:compareAll}(c), as compared to Figure
-\ref{fig:compareAll}(b).
+with far greater accuracy. Applying the simple mapping scheme in
+Section X results in X, which is far more seamless, but a more
+intelligent image selection scheme can still be used.
 
 \section{Image Compositing}
+
+In this section, we revisit the tile-based texturing approach from
+Section X, with an added caching mechanism to reduce image
+boundaries. This method works well given all manner of camera poses and
+surfaces, but for cases where we have large sections of usable texture
+from images, we propose an alternate method that further reduces image
+boundaries.
+
+\subsection{Tile-Mapping with Caching}
+\label{sec:mappingWithCaching}
+From Section X, we saw that discontinuities occur where adjacent tiles
+select different images. Though image alignment reduces or removes
+many such discontinuities, there are still cases where seams are
+visible, for example due to lighting differences or imprecise
+matching. To reduce the cases where this happens, it makes sense to
+take into account image selections made by neighboring tiles while
+texture mapping a given tile. By using the same image across tile
+boundaries, we can eliminate a discontinuity altogether. If this is
+not possible because a tile is not visible in images used by
+neighboring tiles, using similar images across tile boundaries also
+leads to less noticeable discontinuities.
+
+Essentially a caching mechanism, we select the best image for a tile
+$t$ by searching through two subsets of images for a viable candidate,
+before searching through the entire set of valid images. The first
+subset of images is the images selected by adjacent tiles that have
+already been textured. We must first check which of these images can
+map to $t$, and then of those, we make a choice according to the
+scoring function in Figure \ref{fig:scoringFunction}. Before reusing
+this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
+order to ensure a high resolution projection, with $\alpha$ as the
+camera angle as shown in Figure \ref{fig:scoringFunction}.
+
+If no satisfactory image is found in the first subset, we check the
+second subset of images, consisting of those taken near the ones in
+the first subset, both spatially and temporally. These images are not
+the same as the ones used for neighboring tiles, but are taken at a
+similar location and time, suggesting that their localization and
+projection are quite similar, and thus likely matched more
+accurately. Again, if no viable image is found according to the same
+criteria, we search the entire set of candidate images, selecting
+based on the same scoring function from Figure
+\ref{fig:scoringFunction}.
+
+The result of this caching approach is shown in Figure X. Seams are now greatly reduced, and LIFE IS HAPPY.
 
@@
 mapping criteria from Figure \ref{fig:scoringFunction}, such
-projections have highly varying scores depending on the location on
-the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
+projections have highly varying scores depending on the location of a tile on
+the plane, as shown again in Figure \ref{fig:projectionAngles}(b). Thus, the
 tiling approach in Section \ref{sec:simpleTextureMapping} is a
-reasonable choice for texturing floors and ceilings, as it uses the
-parts of image projections that are viable choices for their
+good choice for texturing floors and ceilings, as it uses the
+parts of image projections that maximize resolution and accuracy for their
 respective plane locations, e.g. areas near point A in Figure
@@
 
-\subsection{Tile-Mapping with Caching}
-\label{sec:mappingWithCaching}
-Since discontinuities occur where adjacent tiles select non-aligned
-images, it makes sense to take into account image selections made by
-neighboring tiles while texture mapping a given tile. By using the
-same image across tile boundaries, we can eliminate a discontinuity
-altogether. If this is not possible because a tile is not visible in
-images used by neighboring tiles, using similar images across tile
-boundaries also leads to less noticeable discontinuities.
+\subsection{Shortest Path Texturing}
 
-Essentially a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set of valid images. The first
-subset of images is the images selected by adjacent tiles that have
-already been textured. We must first check which of these images can
-map to $t$, and then of those, we make a choice according to the
-scoring function in Figure \ref{fig:scoringFunction}. Before reusing
-this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
-order to be considered a viable image, with $\alpha$ as the camera
-angle as shown in Figure \ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check the
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar, allowing us to minimize any differences
-in localization error as well as a parallax effects. Again, if no
-viable image is found according to the same criteria, we search the
-entire set of candidate images, selecting based on the same scoring
-function from Figure \ref{fig:scoringFunction}.
-
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(b). As compared to Figure
-\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
-amount of remaining seams suggests that despite our high volume of
-images, image selection alone cannot produce seamless textures. Camera
-matrices, or the image projections themselves, have to be adjusted in
-order to reliably generate clean textures.
-
-\subsection{Shortest}
 For wall planes however, most images are taken from close distances
-and more or less head-on angles, resulting in higher resolution
-fronto-parallel projections. As a result, for each tile on a wall
-plane, the scoring function of Figure \ref{fig:scoringFunction} is
-relatively flat with respect to a large number of captured images, as
-they are all more or less head on. Thus, the scoring function is less
-significant for walls, and it is conceivable to use a different
-texturing strategy for them so as to minimize visible seams in texture
-mapped planes. This can be done by choosing the smallest possible set
-of images that (a) covers the entire plane and (b) minimizes the
-amount of visible seams between them. A straightforward cost function
-that accomplishes the latter is the Sum of Squared Differences (SSD)
-of pixels in overlapping regions between all pairs of images, after
-they have been rotated as described in Section
-\ref{sec:projectionAndRotation}. Minimizing this cost function
-encourages image boundaries to occur either in featureless areas, such
-as bare walls, or in areas where images match extremely well.
+and head-on angles, resulting in higher resolution fronto-parallel
+projections. As a result, for each tile on a wall plane, the scoring
+function of Figure \ref{fig:scoringFunction} is relatively flat with
+respect to a large number of captured images, as they are all more or
+less head on. Thus, the scoring function is less significant for
+walls, and it is conceivable to use a different texturing strategy for
+them so as to directly minimize visible seams when texturing
+them. This can be done by choosing the smallest possible set of images
+that (a) covers the entire plane and (b) minimizes the amount of
+visible seams between them. A straightforward cost function that
+accomplishes the latter is the Sum of Squared Differences (SSD) of
+pixels in overlapping regions between all pairs of images. Minimizing
+this cost function encourages image boundaries to occur either in
+featureless areas, such as bare walls, or in areas where images match
+extremely well.
 
 To cover the entirety of a plane, our problem can be defined as
-minimally covering a polygon i.e. the plane, using other polygons of
-arbitrary geometry i.e. image projections, with the added constraint
-of minimizing the cost function between chosen images.  This is a
-complex problem, though we can take a number of steps to simplify it.
+minimally covering a polygon i.e. the planar surface, using other
+polygons of arbitrary geometry i.e. image projections, with the added
+constraint of minimizing the cost function between chosen images.
+This is a complex problem, though we can take a number of steps to
+simplify it.
 
@@
 entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. To address this, we solve for
-a new shortest path after modifying the edges chosen by the original
-shortest path solution such that they have higher cost than all other
-edges in the DAG, and solve for a new shortest path. This ensures that
-these edges are not chosen again unless they are the only available
-option. Our second shortest path solution results in a new set of
-chosen images, of which we only retain those that cover areas not
-covered by the first set. This process can be repeated as many times
-as needed, until holes are no longer present. This method is not as
-optimal as a 2D-coverage solution would be, but it is a fast
-approximation, and adequately handles the few holes we encounter.
+where no images are selected to texture. Since these holes are rare,
+and generally fairly small, we use a greedy approach, repeatedly
+filling the hole with images that result in the lowest SSD costs in a
+10 px border region around the hole. This method is not as optimal as
+a 2D-coverage solution would be, but it is a fast approximation, and
+adequately handles the few holes we encounter.
 
@@
 during texture generation and rendering, as it does not require
-discretizing planes or images\footnote {For the seam minimization
-  approach, occlusion checks are performed over the entirety of each
-  image to determine available areas for texture mapping. Since indoor
-  environments mostly consist of vertical or horizontal surfaces with
-  high amounts of right angles, image projections remain largely
-  rectangular after masking out occluded areas. Therefore, as a
-  preprocessing step, we can recursively split each image into
-  rectangular pieces and check for occlusions in a similar manner as
-  in the tiling process.  }.
+discretizing planes or images.
 
@@
 We now apply the same blending process to the two texturing methods:
-image alignment followed by either tile caching or seam minimization.
+tile caching or seam minimization.
 
-Although the preprocessing steps and image selection in both methods
+Although the image alignment steps and image selection in both methods
 attempt to minimize all mismatches between images, there are
@@
 $l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size. For the seam minimization method, we have
-already ensured overlap between images. To enforce consistent blending
-however, we add a minimum required overlap distance while solving the
-shortest path problem in Section
-\ref{sec:seamMinimization}. Additionally, if images overlap in a
-region greater than the overlap distance, we only apply blending over
-an area equal to the overlap distance.
+\times (l_1 + l_2)$ in size.  We have found $l_2 = \frac{l_1}{2}$ to
+provide enough blending without blurring features. For the seam
+minimization method, we have already ensured overlap between
+images. To enforce consistent blending however, we add a minimum
+required overlap distance of 40 px while solving the shortest path
+problem in Section \ref{sec:seamMinimization}. Additionally, if images
+overlap in a region greater than the overlap distance, we only apply
+blending over an area equal to the overlap distance.
 
 After blending pixels linearly across overlapping regions using alpha
-blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the seam minimization approach still exhibits better
-alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
+blending, our texture mapping process is complete. Figures
+\ref{fig:compareAll}(e) and \ref{fig:compareAll}(f) show the blended
+versions of Figures \ref{fig:compareAll}(c) and
+\ref{fig:compareAll}(d) respectively. It is clear that the seam
+minimization approach exhibits better alignment and fewer seams
+than the tile-caching method, as Figure \ref{fig:compareAll}(f) has
+the best visual quality among the textures in Figure
+\ref{fig:compareAll}.
 
@@
 \label{sec:resultsAndConclusions}
+Examples of ceilings and floors textured with the tile caching
+approach, and walls textured with the seam minimization approach, are
+displayed in Figure \ref{fig:results}. High resolution texture
+comparisons, as well as a walkthrough of a fully textured 3D model are
+available in the accompanying video to this paper.
+
+As mentioned earlier, our approach is fairly efficient, with the X by
+X pixel image in figure X, spanning an X meter long wall and
+consisting of X input images taking under a minute to generate on a
+2.8Ghz dual-core laptop. While not fast enough for real-time
+visualization, the procedure is quick enough for quick evaluation given
+changes in various internal parameters or modifications to input data.
+
+\subsection{Future stuff}
+For the sake of simplicity, - cases where multiple whatever
+are few, but for true generality, should go to 3d adjustments
 

### 2012-12-26 spie/_region_.tex
again text done

--- 2012-12-24 spie/_region_.tex
@@
 
-\message{ !name(paper.tex) !offset(106) }
-\subsection{Direct Mapping}
-\label{sec:directMapping}
+\message{ !name(paper.tex) !offset(76) }
+\section{bla}
+
+\label{sec:simpleTextureMapping}
+\begin{figure}
+  \centering
+  \includegraphics[height=2in]{Projection.pdf}
+  \caption{Planes are specified in 3D space by four corners $C_1$ to
+    $C_4$. Images are related to each plane through the camera matrics
+    $P_{1..m}$. }
+  \label{fig:projection}
+\end{figure}
+
+The geometry of the texture mapping process for a plane is shown in
+Figure \ref{fig:projection}.  As described earlier, we are provided
+with a set of $M$ images to texture the target plane. Each image has a
+camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
+world coordinate system to a 2D point or pixel in image $i$'s
+coordinates. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, such as focal length and image center, as well
+as extrinsic parameters which specify the rotation and translation of
+the camera's position in 3D world coordinates at the time that image
+$i$ is taken. These extrinsic parameters are determined by the
+backpack hardware and localization algorithms \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure} and are quite noisy.
+
+Because our backpack system takes photos at a rate of 5 Hz, thousands
+of images are available for texturing each surface in our model. Our
+goal in designing a texture mapping process is to decide which of
+these images should be used, and where their contents should map onto
+the texture, in order to minimize any visual discontinuities or seams
+that would suggest that the plane's final texture is not composed of a
+single continuous image.
 
@@
 many image boundaries with abrupt discontinuities, due to significant
-misalignment between images, as a result of camera pose inaccuracies.
+misalignment between images. Given our high number of input images, it
+makese sense to intelligently select only the images that match up
+well, as performed in Section X, but for our solution to be robust, we
+must align images directly such that we maximize the accuracy of each image.
 
-\message{ !name(paper.tex) !offset(416) }
+\message{ !name(paper.tex) !offset(539) }
 

### 2012-12-26 spie/paper.tex
again text done

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+\section{Introduction}
 \label{sec:introduction} % \label{} allows reference to this section
@@
 makese sense to intelligently select only the images that match up
-well, as performed in Section X, but for our solution to be robust, we
-must align images directly such that we maximize the accuracy of each image.
+well, as performed in Section \ref{sec:imageCompositing}, but for our
+solution to be more robust, we perform image alignment in order
+maximize the accuracy of each image.
 
@@
 
-\section{Efficient Image Alignment with Geometry Information}
-
+\section{2D Image Alignment with Geometry Information}
+\label{sec:2dAlignment}
 In this section, we describe our method of efficient and robust image
@@
 
-EVERYTHING IS IN 2D BECAUSE PITCH BECOMES WHATEVO
+All of our calculations and alignments are performed in 2D, partly for
+efficiency, and partly because the nature of our input data is such
+that the majority of localization error is 2D, in the same plane as
+the surface being projected onto. Recall that our data acquisition
+system is backpack-mounted, with cameras facing to the sides of the
+operator. The operator attempts to walk parallel to walls, and the
+localization and model-generation algorithms that provide our input
+can conform the operator's path to be straight and parallel to
+detected surfaces. Since the operator walks as upright as possible,
+errors in roll and yaw, as well as the operator's distance from
+parallel surfaces are minimal. Thus, our highest errors stem from
+uncertainty in the operator's pitch, equivalent to rotation around the
+camera axes, as well as location along surfaces. These equate to 2D
+rotation and translation in a surface's plane.
 
 \subsection{Geometry-based Alignment}
-\label{sec:projectionAndRotation}
+\label{sec:geometryAlignment}
 After computing each image's projection onto the target surface, as
-described in Section \ref{sec:simpleTextureMapping}, we can detect
-lines in the projections using Hough transforms. Experience and
-intuition show that walls in indoor environments contain linear
-features that are either horizontal or vertical, often corresponding
-to doors, windows, posters, etc. Thus, when texturing walls, we rotate
-images in 2D such that dominant lines are made to be horizontal or
-vertical. Though not relevant in our datasets, this can be extrapolated
-such that lines are oriented with a wall's boundaries, for example in
-areas with a slanted roof.
+described in Section \ref{sec:simpleTextureMapping}, we detect lines
+in the projections using Hough transforms. Experience and intuition
+show that walls in indoor environments contain linear features that
+are either horizontal or vertical, often corresponding to doors,
+windows, posters, etc. Thus, when texturing walls, we rotate images in
+2D such that dominant lines are made to be horizontal or
+vertical. Though not relevant in our datasets, this can be
+extrapolated such that lines are oriented with a wall's boundaries,
+for example in areas with a slanted roof.
 
@@
 the two surfaces meet. If this linear boundary is detected by Hough
-transform, the image is rotated and shifted in 2D such that
-the visual boundary between two surfaces matches the physical boundary
-in our digital model.
+transform, the image is rotated and shifted in 2D such that the visual
+boundary between two surfaces matches the physical boundary in our
+digital model.
 
-To perform the rotation and alignment, we do MAGIC.  Then we indicate
-that magic has been done so that in the next step stuff is good. Mark
-as anchor images.
+To perform the rotation and alignment, a robust method would be to
+detect all line matches and solve for an optimal homography. In nearly
+all cases however, we find that a single 2D rotation is sufficient to
+properly align lines in an image. We also rarely have more than one
+linear geometry feature to match to.
+As a result, we do WHATEVER WE DO, and then for each image shifted, we indicate that they have been shifted to match geometry, which is referenced in Section \ref{sec:robustSIFTFeatureMatching}
 
 \subsection{Image Occlusion}
-get from github i guess i dunno. or check avz email. maybe put in appendix
+\label{sec:imageOcclusion}
+Now that images have been aligned to geometry where possible, we
+perform a simple recursive occlusion procedure on each image. This is
+done by performing the intersection tests in section
+\ref{sec:simpleTextureMapping} in a regularly spaced grid. Where four
+corners of a rectangular region are occluded, texture is
+removed. Where no corners are occluded, nothing occurs. Where there is
+a mixture of both, the rectangular region is subdivided into four, and
+the same process is performed on each. By performing Section
+\ref{sec:geometryAlignment}'s alignment procedure before occlusion, we
+remove all erroneous texture belonging to other surfaces, which is
+necessary for the next section.
 
@@
 \cite{lai1999robust, lowe1999object, mikolajczyk2005performance,
-  szeliski2006image}.  SiftGPU, by PERSON CITATION, is used both for
-feature detection as well as pairwise matching. These matches
-determine $d^x$ and $d^y$ distances between each pair of features for
-two image projections, though these distances may not always be the
-same for different features. Since indoor environments often contain
-repetitive features such as floor tiles or doors, we need to ensure
-that SIFT-based distances are reliable. In order to mitigate the
-effect of incorrect matches and outliers, the RANSAC framework
-\cite{fischler1981random} is used for a robust estimate of the optimal
-$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
-$j$. The RANSAC framework handles the consensus-building machinery,
-and requires a fitting function and a distance function. For this
-application, the fitting function simply finds the average distance
-between matches in a pair of images. The distance function for a pair
-of points is chosen to be the difference between those points' SIFT
-match distance and the average distance computed by the fitting
-function. We use a 10 pixel outlier threshold, so that SIFT matches
-are labeled as outliers if their horizontal or vertical distances are
-not within 10 pixels of the average distance computed by the fitting
-function.
+  szeliski2006image}.  In our implementation, we use SiftGPU, by
+PERSON CITATION, for both feature detection as well as pairwise
+matching. These matches determine $d^x$ and $d^y$ distances between
+each pair of features for two image projections, though these
+distances may not always be the same for different features. Since
+indoor environments often contain repetitive features such as floor
+tiles or doors, we need to ensure that SIFT-based distances are
+reliable. First, we only perform alignment on pairs of images that
+overlap given the original noisy poses. Secondly, we discard feature
+matches that correspond to an image distance greater than 40 pixels
+from what the noisy poses estimate. In order to utilize the remaining
+feature matches robustly, the RANSAC framework
+\cite{fischler1981random} is used to estimate the optimal $d^x_{i,j}$
+and $d^y_{i,j}$ distances between two images $i$ and $j$. The RANSAC
+framework requires a fitting function and a distance function. For
+this application, the fitting function simply finds the average
+distance between matches in a pair of images. The distance function
+for a pair of points is chosen to be the difference between those
+points' SIFT match distance and the average distance computed by the
+fitting function. We use a 10 pixel outlier threshold, so that SIFT
+matches are labeled as outliers if their horizontal or vertical
+distances are not within 10 pixels of the average distance computed by
+the fitting function.
 
-We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
-of images to refine their positions using least squares. Recall that
-there are a total of $M^{2}$ possible pairs of images, though we only
-generate distances between images that overlap at SIFT feature
-points. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
+We now use the calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
+between each pair of images to refine their positions using weighted
+linear least squares. Recall that there are a total of $M^{2}$
+possible pairs of images, though we only generate distances between
+images that overlap at SIFT feature points. Given these distances and
+the original image location estimates, we can solve a least squares
+problem ($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
+\vec{\gamma}||_2^2 $) to estimate the location of the images on the
+plane. The $M$-dimensional vector $\vec{\beta}$ represents the unknown
+$x$ location of each image on the plane for $1 \dots M$. The optimal
+$x$ and $y$ locations are obtained in the same way, so we only
+consider the $x$ locations here:
 
@@
 \]
-If only relative distances between images are included then there is
-no way to determine the absolute location of any of the images and the
-matrix becomes rank deficient. From Section X, a number of images were
-anchored to geometry points, and thus their locations can be used to
-anchor the rest in place. In case no anchor images exist, we simply
-arbitrarily pick an image. In the above matrix, the first image is set
-to be such an anchor.
+If only relative distances between images are included, the absolute
+location of the images can not be calculated, and the matrix is rank
+deficient. From Section \ref{geometryBasedAlignemtn}, a number of
+images are anchored to geometry points, and thus their locations can
+be used to anchor the rest in place. In case no anchor images exist,
+we simply arbitrarily pick an image. In the above matrix, the first
+image is set to be such an anchor, simply by placing a $1$ in its
+column
 
-Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
-constructed using the SIFT-based distances generated in the RANSAC
-matching stage. Elements in the observation vector corresponding to
-anchor images are simply their locations as determined by the original
-noisy localization. Thus $\vec{\gamma}$ can be written as:
+The $N$-dimensional observation vector $\vec{\gamma}$ is constructed
+using the SIFT-based distances generated in the RANSAC matching
+stage. Elements in the observation vector corresponding to anchor
+images are simply their locations as determined by the original noisy
+localization. Thus $\vec{\gamma}$ can be written as:
 
@@
 that best honors all the SIFT-based distance measurements between
-images. In practice there is often a break in the chain of images,
-meaning that no SIFT matches are found between one segment of the
-plane and another. To solve this, we add rows to the $A$ matrix and
-observations to the $\vec{\gamma}$ vector corresponding to the
-original noisy distances. We then solve a weighted least squares
-problem where the SIFT distances and anchor values are given a high
-weight e.g. 1, while the noisy distances are given a smaller weight
-e.g. 0.01.
+images. This solution however does not make use of our noisy camera
+poses, and will fail when no SIFT matches are found between one
+segment of the plane and another. To account for this, we add rows to
+the $A$ matrix and observations to the $\vec{\gamma}$ vector
+corresponding to the original noisy distances. We then solve a
+weighted least squares problem where the SIFT distances and anchor
+values are given a high weight e.g. 1, while the noisy distances are
+given a smaller weight e.g. 0.01.
 
@@
 with far greater accuracy. Applying the simple mapping scheme in
-Section X results in X, which is far more seamless, but a more
-intelligent image selection scheme can still be used.
+Section \ref{sec:simpleTextureMapping} results in X, which has far
+fewer seams, but can still be improved.
 
@@
 \label{sec:mappingWithCaching}
-From Section X, we saw that discontinuities occur where adjacent tiles
-select different images. Though image alignment reduces or removes
-many such discontinuities, there are still cases where seams are
-visible, for example due to lighting differences or imprecise
-matching. To reduce the cases where this happens, it makes sense to
-take into account image selections made by neighboring tiles while
-texture mapping a given tile. By using the same image across tile
-boundaries, we can eliminate a discontinuity altogether. If this is
-not possible because a tile is not visible in images used by
-neighboring tiles, using similar images across tile boundaries also
-leads to less noticeable discontinuities.
+From Section \ref{sec:simpleTextureMapping}, we saw that
+discontinuities occur where adjacent tiles are textured by different
+images. Though image alignment removes many such discontinuities,
+there are still cases where seams are visible due to imprecise
+matching or other factors such as lighting differences. To reduce the
+cases where this happens, it makes sense to take into account image
+selections made by neighboring tiles while texture mapping a given
+tile. By using the same image across tile boundaries, we can eliminate
+a discontinuity altogether. If this is not possible because a tile is
+not visible in images used by neighboring tiles, using similar images
+across tile boundaries also leads to less noticeable discontinuities.
 
@@
 
-The result of this caching approach is shown in Figure X. Seams are now greatly reduced, and LIFE IS HAPPY.
+The result of this caching approach is shown in Figure X, where seams
+are now greatly reduced as compared to Figure X2.
 
@@
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a) Undistorted fisheye images for vertical planes are
-    tilted, but their effective camera axis is more or less normal to
-    the plane. (b) The effective camera axis for ceilings is at an
-    angle with respect to the plane normal. (c) Wall images are
-    cropped to be rectangular.}
+  \caption{(a) Images for vertical planes are tilted, but their
+    effective camera axis is more or less normal to the plane. (b) The
+    effective camera axis for ceilings is at an angle with respect to
+    the plane normal. (c) Wall images are cropped to be rectangular.}
   \label{fig:projectionAngles}
@@
 
-As mentioned earlier, the mobile backpack system used to capture data
-in this paper contains 2 cameras with $180^\circ$ fisheye lenses
-facing to the right and left. Since most human operators do not carry
-the backpack in a perfectly upright position and are bent forwards at
-15 to 20 degrees with respect to the vertical direction, the
-undistorted fisheye images are head on with respect to vertical walls,
-but at an angle with respect to horizontal floors and ceilings. This
-is depicted for wall and ceiling planes in Figures
-\ref{fig:projectionAngles}(a) and \ref{fig:projectionAngles}(b)
-respectively. These oblique camera angles for ceilings translate into
-textures that span extremely large areas once projected, as shown in
-Figure \ref{fig:projectionAngles}(b). Using the tile-based texture
-mapping criteria from Figure \ref{fig:scoringFunction}, such
-projections have highly varying scores depending on the location of a tile on
-the plane, as shown again in Figure \ref{fig:projectionAngles}(b). Thus, the
-tiling approach in Section \ref{sec:simpleTextureMapping} is a
-good choice for texturing floors and ceilings, as it uses the
-parts of image projections that maximize resolution and accuracy for their
+As mentioned earlier, our data comes from a mobile backpack
+system. Human operators can not carry the backpack in a perfectly
+upright position and are bent forwards at 15 to 20 degrees with
+respect to the vertical direction. As a result, cameras facing
+sideways are head on with respect to vertical walls, while cameras
+oriented towards the top or bottom of the backpack are at an angle
+with respect to horizontal floors and ceilings. This is depicted in
+Figures \ref{fig:projectionAngles}(a) and
+\ref{fig:projectionAngles}(b). These oblique camera angles for
+horizontal surfaces translate into textures that span extremely large
+areas once projected, as shown in Figure
+\ref{fig:projectionAngles}(b). Using the tile-based texture mapping
+criteria from Figure \ref{fig:scoringFunction}, such projections have
+highly varying scores depending on the location of a tile on the
+plane, as shown again in Figure \ref{fig:projectionAngles}(b). Thus,
+the tiling approach in this section is a
+good choice for texturing floors and ceilings, as it uses the parts of
+image projections that maximize resolution and accuracy for their
 respective plane locations, e.g. areas near point A in Figure
@@
 
-For wall planes however, most images are taken from close distances
-and head-on angles, resulting in higher resolution fronto-parallel
+For vertical walls, most images are taken from close distances and
+head-on angles, resulting in high resolution fronto-parallel
 projections. As a result, for each tile on a wall plane, the scoring
 function of Figure \ref{fig:scoringFunction} is relatively flat with
-respect to a large number of captured images, as they are all more or
-less head on. Thus, the scoring function is less significant for
-walls, and it is conceivable to use a different texturing strategy for
-them so as to directly minimize visible seams when texturing
-them. This can be done by choosing the smallest possible set of images
-that (a) covers the entire plane and (b) minimizes the amount of
-visible seams between them. A straightforward cost function that
-accomplishes the latter is the Sum of Squared Differences (SSD) of
-pixels in overlapping regions between all pairs of images. Minimizing
-this cost function encourages image boundaries to occur either in
-featureless areas, such as bare walls, or in areas where images match
-extremely well.
+respect to candidate images, as they are all more or less head
+on. Thus, the scoring function is less significant for walls, and it
+is conceivable to use a different texturing strategy to directly
+minimize visible seams when texturing them. This is done by choosing
+the smallest possible set of images that (a) covers the entire plane
+and (b) minimizes the visibility of borders between them. A
+straightforward cost function that accomplishes the latter is the sum
+of squared differences (SSD) of pixels in overlapping regions between
+all pairs of images. Minimizing this cost function encourages image
+boundaries to occur either in featureless areas, such as bare walls,
+or in areas where images match extremely well.
 
@@
 head-on angles, and assuming only minor rotations are made in Section
-\ref{sec:projectionAndRotation}, we can reason that their projections
-onto the plane are approximately rectangular. By cropping them all to
-be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
+\ref{sec:2dAlignment}, we can reason that their projections onto the
+plane are approximately rectangular. By cropping them all to be
+rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
 problem becomes the conceptually simpler one of filling a polygon with
@@
 
-The location and orientation of the cameras and the fisheye lenses on
-the acquisition backpack is such that images nearly always contain the
-entirety of the floor to ceiling range of wall planes. Images are
-therefore rarely projected with one above another when texturing wall
-planes. In essence, we need only to ensure lateral coverage of wall
-planes, e.g. from left to right, as our images provide full vertical
-coverage themselves. We can thus construct a Directed Acyclic Graph
-(DAG) from the images, with edge costs defined by the SSD cost
-function, and solve a simple shortest path problem to find an optimal
-subset of images with regard to the cost function \cite{dijkstra}.
+The operator's path, and the location and orientation of the cameras
+on the acquisition backpack is such that images nearly always contain
+the entirety of the floor to ceiling range of wall planes. Images
+therefore rarely need to be projected with one above another when
+texturing wall planes. In essence, we need only to ensure lateral
+coverage of wall planes, e.g. from left to right, as our images
+provide full vertical coverage themselves. We can thus construct a
+Directed Acyclic Graph (DAG) from the images, with edge costs defined
+by the SSD cost function, and solve a simple shortest path problem to
+find an optimal subset of images with regard to the SSD cost function
+\cite{dijkstra}.
 
@@
 Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a long hallway. Images are sorted by
+from overlapping images of a hallway wall. Images are sorted by
 horizontal location left to right, and become nodes in a
@@
 representing the right border of the plane. The left(right) artificial
-node has directed edges with equal cost $C_0$ to(from) all images that
-meet the left(right) border of the plane.
+node has directed edges with equal and arbitrary cost $C_0$ to(from)
+all images that meet the left(right) border of the plane.
 
@@
 10 px border region around the hole. This method is not as optimal as
-a 2D-coverage solution would be, but it is a fast approximation, and
-adequately handles the few holes we encounter.
+a true 2D-coverage solution would be, but it is a fast approximation,
+and adequately handles the few holes we encounter.
 
@@
 at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. As seen in Figure
-\ref{fig:compareAll}(d), this seam minimization method has fewer
-visible discontinuities than Figure \ref{fig:compareAll}(c)
-corresponding to the tile caching approach\footnote{In Figure
-  \ref{fig:compareAll}(d), we arbitrarily chose one image for
-  texturing where images overlap, as blending will be discussed in the
-  next section.}. This is especially evident when comparing the
-posters in the images, which have clear misalignment over seams in
-Figure \ref{fig:compareAll}(c), but are much more aligned in Figure
-\ref{fig:compareAll}(d). This is because the seam minimization
-approach directly reduces the cost of each image boundary, while the
-tile caching method uses a scoring function that only approximates
-this effect. Furthermore, seam minimization guarantees the best
-selection of images, while the sequential tile caching method may
-select images early on that turn out to be poor choices once
-subsequent tiles have been processed. The seam minimization approach
-is also far less intensive in terms of memory usage and runtime, both
-during texture generation and rendering, as it does not require
-discretizing planes or images.
+as the discontinuities at their borders. As seen in Figure
+\ref{fig:compareAll}(d), this shortest path method has fewer visible
+discontinuities than Figure \ref{fig:compareAll}(c) corresponding to
+the tile caching approach\footnote{In Figure \ref{fig:compareAll}(d),
+  we arbitrarily chose one image for texturing where images overlap,
+  as blending will be discussed in section \ref{sec:blending}.}. This
+is especially evident when comparing the posters in the images, which
+have clear misalignment over seams in Figure \ref{fig:compareAll}(c),
+but are much more aligned in Figure \ref{fig:compareAll}(d). This
+shortest path approach approach directly reduces the cost of each
+image boundary, while the tile caching method uses a scoring function
+that only approximates this effect. Furthermore, seam minimization
+guarantees the best selection of images, while the sequential tile
+caching method may select images early on that turn out to be poor
+choices once subsequent tiles have been processed. The seam
+minimization approach is also far less intensive in terms of memory
+usage and runtime, both during texture generation and rendering, as it
+does not require discretizing planes or images.
 
-In the context of texturing an entire 3D planar model, we choose to
-apply the seam minimization approach on walls, due to its superior
-output when provided with head-on images. Floors and ceilings however,
-given their many images taken at oblique angles, are textured using
-the tile caching method.
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=6in]{pipelineimages.pdf}
-%   \caption{Textures corresponding to each step in our texture
-%   mapping pipeline.}
-%   \label{fig:pipelineimages}
-% \end{figure*}
+When texturing an entire 3D planar model, we apply the seam
+minimization approach on walls, due to its superior output when
+provided with head-on images. Floors and ceilings however, given their
+many images taken at oblique angles, are textured using the tile
+caching method.
 
@@
 \label{sec:blending}
-We now apply the same blending process to the two texturing methods:
-tile caching or seam minimization.
-
-Although the image alignment steps and image selection in both methods
-attempt to minimize all mismatches between images, there are
-occasional unavoidable discontinuities in the final texture due to
-different lighting conditions or inaccuracies in planar geometry or
-projection. These can however be treated and smoothed over by applying
-alpha blending over image seams.  Whether the units we are blending
-are rectangularly-cropped images or rectangular tiles, we can apply
-the same blending procedure, as long as we have a guaranteed overlap
+We now apply a blending procedure to both texturing methods. Although
+the image alignment steps and image selection in both methods attempt
+to minimize all mismatches between images, there are occasional
+unavoidable discontinuities in the final texture due to different
+lighting conditions or inaccuracies in planar geometry. These can
+however be treated and smoothed over by applying alpha blending over
+image seams.  Whether the units we are blending are
+rectangularly-cropped images or rectangular tiles, we can apply the
+same blending procedure, as long as we have a guaranteed overlap
 between units to blend over.
@@
 \times (l_1 + l_2)$ in size.  We have found $l_2 = \frac{l_1}{2}$ to
-provide enough blending without blurring features. For the seam
-minimization method, we have already ensured overlap between
+provide a balance between blending and keeping features unblurred. For
+the shortest path method, we have already ensured overlap between
 images. To enforce consistent blending however, we add a minimum
@@
 
-After blending pixels linearly across overlapping regions using alpha
-blending, our texture mapping process is complete. Figures
-\ref{fig:compareAll}(e) and \ref{fig:compareAll}(f) show the blended
-versions of Figures \ref{fig:compareAll}(c) and
-\ref{fig:compareAll}(d) respectively. It is clear that the seam
-minimization approach exhibits better alignment and fewer seams
-than the tile-caching method, as Figure \ref{fig:compareAll}(f) has
-the best visual quality among the textures in Figure
-\ref{fig:compareAll}.
+After performing linear alpha blending across overlapping regions, our
+texture mapping process is complete. Figures \ref{fig:compareAll}(e)
+and \ref{fig:compareAll}(f) show the blended versions of Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
+is clear that the shortest path approach exhibits better alignment
+and fewer seams than the tile-caching method, as Figure
+\ref{fig:compareAll}(f) has the best visual quality among the textures
+in Figure \ref{fig:compareAll}.
 

### 2012-12-26 spie/_region_.tex
figure placeholders

--- 2012-12-25 spie/_region_.tex
@@
 %  installations. 
-\usepackage[]{graphicx}
+\usepackage{graphicx}
+\usepackage{subfig}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-\message{ !name(paper.tex) !offset(594) }
-\subsection{Blending}
-\label{sec:blending}
-We now apply the same blending process to the two texturing methods:
-tile caching or seam minimization.
+\message{ !name(paper.tex) !offset(674) }
+\subsection{Future stuff}
+For the sake of simplicity, - cases where multiple whatever are few,
+but for true generality, should go to 3d adjustments
 
-Although the image alignment steps and image selection in both methods
-attempt to minimize all mismatches between images, there are
-occasional unavoidable discontinuities in the final texture due to
-different lighting conditions or inaccuracies in planar geometry or
-projection. These can however be treated and smoothed over by applying
-alpha blending over image seams.  Whether the units we are blending
-are rectangularly-cropped images or rectangular tiles, we can apply
-the same blending procedure, as long as we have a guaranteed overlap
-between units to blend over.
+\begin{figure*}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
+  ~~~~~~~~
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
 
-For the tile caching method, we can ensure overlap by texturing a
-larger tile than needed for display. For example, for a rendered tile
-$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size. We have found $l_2 = \frac{l_1}{2}$ to provide a
-good amount of blending without blurring features. For the seam
-minimization method, we have already ensured overlap between
-images. To enforce consistent blending however, we add a minimum
-required overlap distance while solving the shortest path problem in
-Section \ref{sec:seamMinimization}. Additionally, if images overlap in
-a region greater than the overlap distance, we only apply blending
-over an area equal to the overlap distance.
+  \centering 
+  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
+  ~~~~~~~~
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
+  \caption{Examples of our final texture mapping output for (a) walls,
+    (b) ceilings, (c) an entire floor, (d) a full model.}
+  \label{fig:results}
+\end{figure*}
 
-After blending pixels linearly across overlapping regions using alpha
-blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the seam minimization approach still exhibits better
-alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% References %%%%%
 
-\message{ !name(paper.tex) !offset(604) }
+\bibliography{report} %>>>> bibliography data in report.bib
+\bibliographystyle{spiebib} %>>>> makes bibtex use spiebib.bst
+
+\message{ !name(paper.tex) !offset(672) }
 

### 2012-12-26 spie/paper.tex
figure placeholders

@@
 %  installations. 
-\usepackage[]{graphicx}
+\usepackage{graphicx}
+\usepackage{subfig}
 
@@
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache.pdf}}
+    height=0.97in]{wall2_naive_shift.pdf}}
 
@@
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog_noblend.pdf}}
+    height=0.97in]{wall2_shortest_shift.pdf}}
 
@@
   \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog.pdf}}
-  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
-    with caching after image alignment. (d) Seam minimization after
-    image alignment). (e) same as (c) with blending. (f) same as (d)
-    with blending.}
+    height=0.97in]{wall2_shortest_shift_blend.pdf}}
+  \caption{(a) Simple mapping. (b) Simple mapping after image
+    alignment. (c) Mapping with caching after image alignment. (d)
+    Shortest path texturing after image alignment). (e) same as (c)
+    with blending. (f) same as (d) with blending.}
   \label{fig:compareAll}
@@
 As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but overall results in
-many image boundaries with abrupt discontinuities, due to significant
-misalignment between images. Given our high number of input images, it
-makese sense to intelligently select only the images that match up
-well, as performed in Section \ref{sec:imageCompositing}, but for our
-solution to be more robust, we perform image alignment in order
-maximize the accuracy of each image.
+the best texture for each tile independently, but results in many
+image boundaries with abrupt discontinuities between tiles, due to
+significant misalignment between images. Given our high number of
+input images, it makese sense to further refine the image selection
+procedure, as performed in Section \ref{sec:imageCompositing}, but for
+our solution to be more robust, we first perform image alignment in
+order maximize the accuracy of each image.
 
@@
 calculating homographies between pairs of images, or by
-modifying camera poses from 1 to 6 degrees of freedom.
+modifying camera poses in 1 to 6 degrees of freedom.
 
@@
 
-  \centering \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
   \caption{Texture alignment via (a) the graph-based localization
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[height=1.5in]{geometryFeature.jpg}
+  \includegraphics[height=1.5in]{imageCorner.jpg}
+  \includegraphics[height=1.5in]{geometryImageAlign.jpg}
+  \caption{(a) The red lines indidcate plane intersections that can be used as geometry reference points.
+(b) A corresponding corner in an image, detected as a line.
+(c) The image rotated and shifted to align with geometry.}
+  \label{fig:geometryAlignment}
+\end{figure}
+
 At this point in time, image occlusions have not been accounted
@@
 boundary between two surfaces matches the physical boundary in our
-digital model.
+digital model. An example of such an adjustment is in Figure \ref{fig:geometryAlignment}
 
@@
 properly align lines in an image. We also rarely have more than one
-linear geometry feature to match to.
-As a result, we do WHATEVER WE DO, and then for each image shifted, we indicate that they have been shifted to match geometry, which is referenced in Section \ref{sec:robustSIFTFeatureMatching}
+linear geometry feature to match to. As a result, we do WHATEVER WE DO, and then indicate which images are aligned to geometry, which is useful in Section \ref{sec:robustSIFTFeatureMatching}
 
@@
 \section{Image Compositing}
-
+\label{sec:imageCompositing}
 In this section, we revisit the tile-based texturing approach from
-Section X, with an added caching mechanism to reduce image
-boundaries. This method works well given all manner of camera poses and
-surfaces, but for cases where we have large sections of usable texture
-from images, we propose an alternate method that further reduces image
-boundaries.
+Section \ref{sec:simpleTextureMapping}, with an added caching
+mechanism to reduce image boundaries. This method works well given all
+manner of camera poses and surfaces, but for cases where we have large
+sections of usable texture from images, we propose an alternate method
+that further reduces image boundaries.
 
@@
 plane, as shown again in Figure \ref{fig:projectionAngles}(b). Thus,
-the tiling approach in this section is a
-good choice for texturing floors and ceilings, as it uses the parts of
-image projections that maximize resolution and accuracy for their
-respective plane locations, e.g. areas near point A in Figure
-\ref{fig:projectionAngles}(b), but not near point B.
+the tiling approach in this section is a good choice for texturing
+floors and ceilings, as it uses the parts of image projections that
+maximize resolution and accuracy for their respective plane locations,
+e.g. areas near point A in Figure \ref{fig:projectionAngles}(b), but
+not near point B.
 
 \subsection{Shortest Path Texturing}
-
+\label{sec:shortestPath}
 For vertical walls, most images are taken from close distances and
@@
 required overlap distance of 40 px while solving the shortest path
-problem in Section \ref{sec:seamMinimization}. Additionally, if images
+problem in Section \ref{sec:shortestPath}. Additionally, if images
 overlap in a region greater than the overlap distance, we only apply
@@
 \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the shortest path approach exhibits better alignment
-and fewer seams than the tile-caching method, as Figure
+is clear that the shortest path approach exhibits better alignment and
+fewer seams than the tile-caching method, as Figure
 \ref{fig:compareAll}(f) has the best visual quality among the textures
@@
 Examples of ceilings and floors textured with the tile caching
-approach, and walls textured with the seam minimization approach, are
+approach, and walls textured with the shortest path approach, are
 displayed in Figure \ref{fig:results}. High resolution texture
@@
 X pixel image in figure X, spanning an X meter long wall and
-consisting of X input images taking under a minute to generate on a
-2.8Ghz dual-core laptop. While not fast enough for real-time
-visualization, the procedure is quick enough for quick evaluation given
-changes in various internal parameters or modifications to input data.
+consisting of X input images, taking under a minute to generate on a
+2.8Ghz dual-core laptop, using the shortest path method. While not
+fast enough for real-time visualization, the procedure is quick enough
+for quick evaluation given changes in various internal parameters or
+modifications to input data.
 
 \subsection{Future stuff}
-For the sake of simplicity, - cases where multiple whatever
-are few, but for true generality, should go to 3d adjustments
+For the sake of simplicity, - cases where multiple whatever are few,
+but for true generality, should go to 3d adjustments
+
+\begin{figure*}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
+  ~~~~~~~~
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
+
+  \centering 
+  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
+  ~~~~~~~~
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
+  \caption{Examples of our final texture mapping output for (a) walls,
+    (b) ceilings, (c) an entire floor, (d) a full model.}
+  \label{fig:results}
+\end{figure*}
 

### 2012-12-30 spie/_region_.tex
few more holes to fill

--- 2012-12-26 spie/_region_.tex
@@
 %  installations. 
-\usepackage[]{graphicx}
+\usepackage{graphicx}
+\usepackage{subfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{hyperref}
 
@@
 
-\message{ !name(paper.tex) !offset(76) }
-\section{bla}
-
+\message{ !name(paper.tex) !offset(80) }
+\section{Simple Texture Mapping}
 \label{sec:simpleTextureMapping}
-\begin{figure}
-  \centering
-  \includegraphics[height=2in]{Projection.pdf}
-  \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera matrics
-    $P_{1..m}$. }
-  \label{fig:projection}
-\end{figure}
 
@@
 
+\begin{figure}[ht]
+  \begin{minipage}[b]{0.45\linewidth}
+  \centering
+  \includegraphics[height=2in]{Projection.pdf}
+  \caption{Planes are specified in 3D space by four corners $C_1$ to
+    $C_4$. Images are related to each plane through the camera matrics
+    $P_{1..m}$. }
+  \label{fig:projection}
+  \end{minipage}
+  \hspace{0.5cm}
+  \begin{minipage}[b]{0.45\linewidth}
+  \centering
+  \includegraphics[height=1.5in]{scoringFunction.jpg}
+  \caption{We minimize camera angle $\alpha$ and distance $d$ by
+    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
+    \cdot \vec{n}$}
+  \label{fig:scoringFunction}
+  \end{minipage}
+\end{figure}
+
+\subsection{Tile-based Texture Mapping}
+\label{sec:tileBasedMapping}
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
@@
   \centering 
-  \includegraphics[height=1.5in]{scoringFunction.jpg}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by
-    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-    \cdot \vec{n}$}
-  \label{fig:scoringFunction}
-\end{figure}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive_shift.pdf}}
 
-\begin{figure}[h!]
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_naive.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog_noblend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog.pdf}}
-  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
-    with caching after image alignment. (d) Seam minimization after
-    image alignment). (e) same as (c) with blending. (f) same as (d)
-    with blending.}
+  \centering 
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift_blend.pdf}}
+  \caption{(a) Tile-based texturing. (b) Tile-based texturing after
+    image alignment. (c) Tile-based texturing after image alignment
+    with caching. (d) Shortest path texturing after image
+    alignment). (e) Same as (c) with blending. (f) Same as (d) with
+    blending.}
   \label{fig:compareAll}
@@
 As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but overall results in
-many image boundaries with abrupt discontinuities, due to significant
-misalignment between images. Given our high number of input images, it
-makese sense to intelligently select only the images that match up
-well, as performed in Section X, but for our solution to be robust, we
-must align images directly such that we maximize the accuracy of each image.
+the best texture for each tile independently, but results in many
+image boundaries with abrupt discontinuities between tiles, due to
+significant misalignment between images. Given our high number of
+input images, it makese sense to further refine the image selection
+procedure, as performed in Section \ref{sec:imageCompositing}, but for
+our solution to be more robust, we first perform image alignment in
+order maximize the accuracy of each image.
 
-\message{ !name(paper.tex) !offset(539) }
+\message{ !name(paper.tex) !offset(613) }
 

### 2012-12-30 spie/paper.tex
few more holes to fill

@@
 \usepackage{subfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{hyperref}
 
@@
 \begin{abstract}
+
   Automated 3D modeling of building interiors is used in applications
@@
 \label{sec:introduction} % \label{} allows reference to this section
+
 Three-dimensional modeling of indoor environments has a variety of
@@
 result, automated 3D site modeling has garnered much interest in
-recent years. CITATION
+recent years.
 
@@
 poses within an environment while simultaneously reconstructing the 3D
-structure of the environment itself. CITATION. This is known as the
+structure of the environment itself. \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure}. This is known as the
 simultaneous localization and mapping (SLAM) problem, and is generally
@@
 advantages over more common wheel-mounted systems in terms of agility
-and portability, but results in much higher localization error and
-uncertainty overall. CITATION. As a result, common methods for texture
-mapping generally produce poor results, leading to the development of
-the approaches contained in this paper. Besides localization
-information and images, environment geometry is required as well for
-texture mapping. In this paper we work mainly with models obtained by
-fitting planar surfaces to point clouds generated by the backpack
-system. CITATION. We have also developed an appropriate method to work
-with near-planar triangular meshes, as described in APPENDIX
-SOMETHING.
+and portability, but results in much higher localization error
+\cite{liu2010indoor}. As a result, common methods for texture mapping
+generally produce poor results, leading to the development of the
+approaches contained in this paper. Besides localization information
+and images, environment geometry is required as well for texture
+mapping. In this paper we work mainly with models obtained by fitting
+planar surfaces to point clouds generated by the backpack system
+\cite{sanchez2012point}. We have also developed an appropriate method
+to work with near-planar triangular meshes, as described in Appendix
+A.
 
 Though our texture mapping procedure was designed with the
-aforementioned system in mind, it is easily generalizable to any other
-system, provided the required inputs of planar geometry, images with
-rough extrinsic pose estimates, and either known or estimated
-intrinsic camera calibration matrices. An important benefit of our
-method is its relatively low complexity and modularity of each step,
-allowing for quick tuning of parameters and easy accomodation of new
-input data given updates in localization or model-generation
-algorithms.
+aforementioned system in mind, it is applicable to other systems,
+provided the required inputs of planar geometry, images with rough
+extrinsic pose estimates, and either known or estimated intrinsic
+camera calibration matrices. An important benefit of our method is its
+relatively low complexity and runtime, and independence of many
+steps, allowing for quick tuning of parameters and easy
+accomodation of new input data given updates in localization or
+model-generation algorithms.
 
-The remainder of the paper is organized as follows. Section X explains
-how input images are projected onto our geometry and simple approaches
-towards texturing. Section X covers more sophisticated existing
+The remainder of the paper is organized as follows. Section
+\ref{sec:simpleTextureMapping} explains how input images are projected
+onto our geometry and simple approaches towards texturing. Section
+\ref{sec:existingApproaches} covers more sophisticated existing
 approaches to image matching and stitching, and their performance on
-our datasets. Section X contains our approach towards image alignment,
-followed by Section X, which describes compositing approaches. Section
-X contains further results and conclusions, as well as areas for
-future work.
+our datasets. Section \ref{sec:imageAlignment} contains our approach
+towards image alignment, followed by Section
+\ref{sec:imageCompositing}, which describes compositing
+approaches. Section \ref{sec:resultsAndConclusions} contains further
+results and conclusions, as well as areas of ongoing and future work.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:simpleTextureMapping}
-\begin{figure}
-  \centering
-  \includegraphics[height=2in]{Projection.pdf}
-  \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera matrics
-    $P_{1..m}$. }
-  \label{fig:projection}
-\end{figure}
 
@@
 
+\begin{figure}
+  \begin{minipage}[b]{0.45\linewidth}
+  \centering
+  \includegraphics[height=2in]{Projection.pdf}
+  \caption{Planes are specified in 3D space by four corners $C_1$ to
+    $C_4$. Images are related to each plane through the camera matrics
+    $P_{1..m}$. }
+  \label{fig:projection}
+  \end{minipage}
+  \hspace{0.5cm}
+  \begin{minipage}[b]{0.45\linewidth}
+  \centering
+  \includegraphics[height=1.5in]{scoringFunction.jpg}
+  \caption{We minimize camera angle $\alpha$ and distance $d$ by
+    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
+    \cdot \vec{n}$}
+  \label{fig:scoringFunction}
+  \end{minipage}
+\end{figure}
+
+\subsection{Tile-based Texture Mapping}
+\label{sec:tileBasedMapping}
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
@@
   \centering 
-  \includegraphics[height=1.5in]{scoringFunction.jpg}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by
-    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-    \cdot \vec{n}$}
-  \label{fig:scoringFunction}
-\end{figure}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive_shift.pdf}}
 
-\begin{figure}[h!]
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_naive.pdf}}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_naive_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_shortest_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_shortest_shift_blend.pdf}}
-  \caption{(a) Simple mapping. (b) Simple mapping after image
-    alignment. (c) Mapping with caching after image alignment. (d)
-    Shortest path texturing after image alignment). (e) same as (c)
-    with blending. (f) same as (d) with blending.}
+  \centering 
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift_blend.pdf}}
+  \caption{(a) Tile-based texturing. (b) Tile-based texturing after
+    image alignment. (c) Tile-based texturing after image alignment
+    with caching. (d) Shortest path texturing after image
+    alignment). (e) Same as (c) with blending. (f) Same as (d) with
+    blending.}
   \label{fig:compareAll}
@@
 and matching. Images are then adjusted to maximize matches, either by
-calculating homographies between pairs of images, or by
-modifying camera poses in 1 to 6 degrees of freedom.
+calculating homographies between pairs of images, or by modifying
+camera poses in 1 to 6 degrees of freedom.
 
@@
 references exist in the environment and are present within multiple
-images. In contrast, our indoor environments have a high
-prevalence of bare surfaces, as well as repeating textures that cause
-difficulty in disambiguating features. This lack of strong reference
-points results in high uncertainty when matching images together.
+images. In contrast, our indoor environments have a high prevalence of
+bare surfaces, as well as repeating textures that cause difficulty in
+disambiguating features. This lack of strong reference points results
+in high uncertainty when matching images together.
 
@@
 \cite{autostitch}. Even with many features spread across this surface,
-the mosaicing produces errors that cause straight lines to appear distorted, despite the fact that it was generated after careful hand
+the mosaicing produces errors that cause straight lines to appear
+distorted, despite the fact that it was generated after careful hand
 tuning. Many areas with fewer visual features simply failed outright
@@
   \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
+  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
   \caption{Texture alignment via (a) the graph-based localization
@@
 poses to maximize matches. This is generally done over 6 degrees of
-freedom. CITATION. Applying the approach in the LIU2010INDOOR paper
-however, results again in error accumulation and drift as shown in
-Figure \ref{fig:mosaic3D}(a). Furthermore, such nonlinear optimization
-approaches IS IT? BETTER CHECK have high complexity and runtime, and the
-entire solution must be recomputed given any changes in input data.
+freedom \cite{liu2010indoor}. The approach in the cited paper works
+well locally, given high feature density, but over larger areas
+results again in error accumulation and drift, especially in
+feature-sparse areas, as shown in Figure
+\ref{fig:mosaic3D}(a). Furthermore, it adjusts image locations using
+an iterative process, which results in high runtime.
 
@@
 In this section, we describe our method of efficient and robust image
-alignment. Our approach consists of four parts. First, all images are
-projected onto the surface and rotated such that detected lines within
-them are parallel to lines comprising the surface's boundary and
-intersection with other surfaces. Next, these projections are shifted
-such that interior lines near surface intersections are matched
-up. Following this, occlusion checks are performed to remove invalid
-parts of each image for the target surface. These first three steps
-are all image-independent and are performed in parallel. Finally, we
-detect SIFT feature matches between pairs of images and solve a linear
-least squares problem in 2D to maximize matches.
+alignment. Our approach consists of three main parts. First, all
+images are projected onto the surface and lines within these
+projections are detected. These lines are then matched up with
+geometry-based lines comprising the surface's boundary and
+intersection with other surfaces. Second, occlusion checks are
+performed to remove invalid parts of each image for the target
+surface. These two steps are image-independent and performed in
+parallel. Third, we detect SIFT feature matches between pairs of
+images and solve a linear least squares problem in 2D to maximize
+matches.
 
-All of our calculations and alignments are performed in 2D, partly for
-efficiency, and partly because the nature of our input data is such
-that the majority of localization error is 2D, in the same plane as
-the surface being projected onto. Recall that our data acquisition
-system is backpack-mounted, with cameras facing to the sides of the
-operator. The operator attempts to walk parallel to walls, and the
-localization and model-generation algorithms that provide our input
-can conform the operator's path to be straight and parallel to
-detected surfaces. Since the operator walks as upright as possible,
-errors in roll and yaw, as well as the operator's distance from
+All of our following calculations and alignments are performed in 2D,
+partly for efficiency, and partly because the nature of our input data
+is such that localization error chiefly occurs in two dimensions, in
+the same plane as the surface being projected onto. Recall that our
+data acquisition system is backpack-mounted, with cameras facing to
+the sides of the operator. The operator makes efforts to walk parallel
+to walls, and the localization and model-generation algorithms that
+provide our input often conform the operator's path to be straight and
+parallel to detected surfaces \cite{kua2012loopclosure,
+  sanchez2012point}. Since the operator walks in as upright a position
+as possible, errors in roll, yaw, and the operator's distance from
 parallel surfaces are minimal. Thus, our highest errors stem from
@@
 2D such that dominant lines are made to be horizontal or
-vertical. Though not relevant in our datasets, this can be
-extrapolated such that lines are oriented with a wall's boundaries,
-for example in areas with a slanted roof.
+vertical. This can be further extrapolated by orienting lines with a
+wall's boundaries, for example in areas with a slanted roof.
 
@@
   \includegraphics[height=1.5in]{geometryImageAlign.jpg}
-  \caption{(a) The red lines indidcate plane intersections that can be used as geometry reference points.
-(b) A corresponding corner in an image, detected as a line.
-(c) The image rotated and shifted to align with geometry.}
+  \caption{(a) The red lines indidcate geometry-based lines,
+    consisting of boundaries and intersections. (b) A matching
+    image-based line, corresponding to a corner. (c) The image rotated
+    and shifted such that the matched lines align align with
+    geometry.}
   \label{fig:geometryAlignment}
@@
 boundary between two surfaces matches the physical boundary in our
-digital model. An example of such an adjustment is in Figure \ref{fig:geometryAlignment}
+digital model. An example of such an adjustment is in Figure
+\ref{fig:geometryAlignment}
 
-To perform the rotation and alignment, a robust method would be to
-detect all line matches and solve for an optimal homography. In nearly
-all cases however, we find that a single 2D rotation is sufficient to
+To perform the rotation and alignment, one method would be to detect
+all line matches and solve for an optimal homography. In nearly all
+cases however, we find that a single 2D rotation is sufficient to
 properly align lines in an image. We also rarely have more than one
-linear geometry feature to match to. As a result, we do WHATEVER WE DO, and then indicate which images are aligned to geometry, which is useful in Section \ref{sec:robustSIFTFeatureMatching}
+linear geometry feature to match to in each orthogonal
+direction. Thus, for a rotation angle, we simply take all angles
+between image-based and geometry-based lines under 5 degrees, and
+average them. After the image is rotated, we find the horizontal and
+vertical image-based and geometry-based line segments with minimum
+orthogonal distance between them. For both distances, if it is under 5
+mm, we apply the corresponding shift, and indicate that the image was
+aligned to geometry in one or both dimensions, which reduces further
+shifting in Section \ref{sec:robustSIFTFeatureMatching}.
 
@@
 the same process is performed on each. By performing Section
-\ref{sec:geometryAlignment}'s alignment procedure before occlusion, we
-remove all erroneous texture belonging to other surfaces, which is
+\ref{sec:geometryAlignment}'s alignment procedure before occlusion,
+texture belonging to other surfaces is accurately removed, which is
 necessary for the next section.
@@
 images, both of which feature alignment is less sensitive to
-\cite{lai1999robust, lowe1999object, mikolajczyk2005performance,
-  szeliski2006image}.  In our implementation, we use SiftGPU, by
-PERSON CITATION, for both feature detection as well as pairwise
-matching. These matches determine $d^x$ and $d^y$ distances between
-each pair of features for two image projections, though these
-distances may not always be the same for different features. Since
-indoor environments often contain repetitive features such as floor
-tiles or doors, we need to ensure that SIFT-based distances are
-reliable. First, we only perform alignment on pairs of images that
-overlap given the original noisy poses. Secondly, we discard feature
-matches that correspond to an image distance greater than 40 pixels
-from what the noisy poses estimate. In order to utilize the remaining
-feature matches robustly, the RANSAC framework
+\cite{lowe1999object, mikolajczyk2005performance, szeliski2006image}.
+We use SiftGPU \cite{siftgpu} for its high performance on both feature
+detection as well as pairwise matching. These matches determine $d^x$
+and $d^y$ distances between each pair of features for two image
+projections, though these distances may not always be the same for
+different features. Since indoor environments often contain repetitive
+features such as floor tiles or doors, we need to ensure that
+SIFT-based distances are reliable. First, we only perform alignment on
+pairs of images that overlap given the original noisy poses. Second,
+we discard feature matches that correspond to an image distance
+greater than 40 pixels from what the noisy poses estimate. In order to
+utilize the remaining feature matches robustly, the RANSAC framework
 \cite{fischler1981random} is used to estimate the optimal $d^x_{i,j}$
@@
 framework requires a fitting function and a distance function. For
-this application, the fitting function simply finds the average
-distance between matches in a pair of images. The distance function
-for a pair of points is chosen to be the difference between those
-points' SIFT match distance and the average distance computed by the
-fitting function. We use a 10 pixel outlier threshold, so that SIFT
-matches are labeled as outliers if their horizontal or vertical
-distances are not within 10 pixels of the average distance computed by
-the fitting function.
+this application, the fitting function finds the average distance
+between matches in a pair of images, and the distance function for a
+pair of points is chosen to be the difference between those points'
+SIFT match distance and the average distance computed by the fitting
+function. We use a 10 pixel threshold, so that SIFT matches are
+labeled as outliers if their horizontal or vertical distances are not
+within 10 pixels of the average distance computed by the fitting
+function.
 
@@
 between each pair of images to refine their positions using weighted
-linear least squares. Recall that there are a total of $M^{2}$
-possible pairs of images, though we only generate distances between
-images that overlap at SIFT feature points. Given these distances and
-the original image location estimates, we can solve a least squares
-problem ($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
-\vec{\gamma}||_2^2 $) to estimate the location of the images on the
-plane. The $M$-dimensional vector $\vec{\beta}$ represents the unknown
-$x$ location of each image on the plane for $1 \dots M$. The optimal
-$x$ and $y$ locations are obtained in the same way, so we only
-consider the $x$ locations here:
+linear least squares. There are a total of $M^{2}$ possible pairs of
+images, though we only generate distances between images with SIFT
+matches. Given these distances and the original image location
+estimates, we can solve a least squares problem
+($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
+to estimate the location of the images on the plane. The
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
+location of each image on the plane for $1 \dots M$. The optimal $x$
+and $y$ locations are obtained in the same way, so we only consider
+the $x$ locations here:
 
@@
 
-The $N \times (M+1)$ dimensional matrix $A$ is constructed with one
-row for each pair of images with measured distances produced by the
-SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the
-columns corresponding to the two images in the pair. For example, the
-matrix below indicates a SIFT-based distance between images 1 and 2,
-images 1 and 3, images 2 and 3, etc.
+The $N \times M$ matrix $A$ is constructed with one row for each pair
+of images with measured distances produced by the SIFT matching
+stage. A row in the matrix has a $-1$ and $1$ in the columns
+corresponding to the two images in the pair. For example, the matrix
+below indicates a SIFT-based distance between images 1 and 2, images 1
+and 3, images 2 and 3, etc.
 \[
@@
   0 & 0 & 0 & \cdots & -1 & 1 \\
-  1 & 0 & 0 & \cdots & 0 & 0 \\
+  1 & 0 & 0 & \cdots & 0 & 0\\
 \end{pmatrix}
@@
 deficient. From Section \ref{geometryBasedAlignemtn}, a number of
-images are anchored to geometry points, and thus their locations can
-be used to anchor the rest in place. In case no anchor images exist,
-we simply arbitrarily pick an image. In the above matrix, the first
+images are anchored to geometry points, in one or both dimensions, and
+thus their locations can be used to fix the rest in place. In case no
+anchor images exist, we simply arbitrarily pick an image, as we have
+no other reference points to work with. In the above matrix, the first
 image is set to be such an anchor, simply by placing a $1$ in its
-column
+column.
 
@@
 images are simply their locations as determined by the original noisy
-localization. Thus $\vec{\gamma}$ can be written as:
+localization. Thus a $\vec{\gamma}$ corresponding to the above matrix
+can be written as:
 
@@
 the $A$ matrix and observations to the $\vec{\gamma}$ vector
-corresponding to the original noisy distances. We then solve a
-weighted least squares problem where the SIFT distances and anchor
+corresponding to the original noisy distances. We then add weighting
+to our least squares problem where the SIFT distances and anchor
 values are given a high weight e.g. 1, while the noisy distances are
@@
 with far greater accuracy. Applying the simple mapping scheme in
-Section \ref{sec:simpleTextureMapping} results in X, which has far
-fewer seams, but can still be improved.
+Section \ref{sec:tileBasedMapping} to the same wall used in that section results in Figure \ref{fig:compareAll}(b), which has far
+fewer seams, though some are still visible.
 
@@
 mechanism to reduce image boundaries. This method works well given all
-manner of camera poses and surfaces, but for cases where we have large
-sections of usable texture from images, we propose an alternate method
-that further reduces image boundaries.
+manner of camera poses and surfaces, but for optimal cases where we
+have large sections of usable texture from images, we propose a
+superior method that further reduces image boundaries.
 
@@
 \label{sec:mappingWithCaching}
-From Section \ref{sec:simpleTextureMapping}, we saw that
-discontinuities occur where adjacent tiles are textured by different
-images. Though image alignment removes many such discontinuities,
-there are still cases where seams are visible due to imprecise
-matching or other factors such as lighting differences. To reduce the
-cases where this happens, it makes sense to take into account image
-selections made by neighboring tiles while texture mapping a given
-tile. By using the same image across tile boundaries, we can eliminate
-a discontinuity altogether. If this is not possible because a tile is
-not visible in images used by neighboring tiles, using similar images
-across tile boundaries also leads to less noticeable discontinuities.
+From Section \ref{sec:tileBasedMapping}, we saw that discontinuities
+occur where adjacent tiles are textured by different images. Though
+Section \ref{sec:2dAlignment}'s image alignment removes many such
+discontinuities, there are still cases where seams are visible due to
+imprecise matching or other factors such as model-based errors. To
+reduce the cases where this happens, it makes sense to take into
+account image selections made by neighboring tiles while texture
+mapping a given tile. By using the same image across tile boundaries,
+we can eliminate a discontinuity altogether. If this is not possible
+because a tile is not visible in images used by neighboring tiles,
+using similar images across tile boundaries also leads to less
+noticeable discontinuities.
 
@@
 
-If no satisfactory image is found in the first subset, we check the
+If no satisfactory image is found in the first subset, we check a
 second subset of images, consisting of those taken near the ones in
@@
 similar location and time, suggesting that their localization and
-projection are quite similar, and thus likely matched more
-accurately. Again, if no viable image is found according to the same
-criteria, we search the entire set of candidate images, selecting
-based on the same scoring function from Figure
-\ref{fig:scoringFunction}.
+projection are quite similar, and thus likely matched more cleanly. If
+no viable image is found according to the same criteria as before, we
+search the entire set of candidate images, selecting based on the same
+scoring function from Figure \ref{fig:scoringFunction}.
 
-The result of this caching approach is shown in Figure X, where seams
-are now greatly reduced as compared to Figure X2.
+The result of this caching approach is shown in Figure
+\ref{fig:compareAll}(c), where seams are now greatly reduced as
+compared to Figure \ref{fig:compareAll}(b).
 
@@
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a) Images for vertical planes are tilted, but their
-    effective camera axis is more or less normal to the plane. (b) The
-    effective camera axis for ceilings is at an angle with respect to
-    the plane normal. (c) Wall images are cropped to be rectangular.}
+  \caption{(a) Images for vertical planes are tilted, but their camera
+    axes are more or less normal to their respective planes. (b)
+    Camera axes for ceiling images are at large angles with respect to
+    plane normals. (c) Wall images are cropped to be rectangular.}
   \label{fig:projectionAngles}
@@
 \ref{fig:projectionAngles}(b). These oblique camera angles for
-horizontal surfaces translate into textures that span extremely large
-areas once projected, as shown in Figure
-\ref{fig:projectionAngles}(b). Using the tile-based texture mapping
-criteria from Figure \ref{fig:scoringFunction}, such projections have
-highly varying scores depending on the location of a tile on the
-plane, as shown again in Figure \ref{fig:projectionAngles}(b). Thus,
-the tiling approach in this section is a good choice for texturing
-floors and ceilings, as it uses the parts of image projections that
-maximize resolution and accuracy for their respective plane locations,
-e.g. areas near point A in Figure \ref{fig:projectionAngles}(b), but
-not near point B.
+horizontal surfaces translate into textures that span large areas once
+projected, as shown in Figure \ref{fig:projectionAngles}(b). Using the
+tile-based texture mapping criteria from Figure
+\ref{fig:scoringFunction}, such projections have highly varying scores
+depending on the location of a tile on the plane. Thus, the tiling
+approach in this section is a good choice for texturing floors and
+ceilings, as it uses the parts of image projections that maximize
+resolution and accuracy for their respective plane locations,
+e.g. areas near point A and not near point B, in Figure \ref{fig:projectionAngles}(b).
 
@@
 
+The first step in this procedure is to obtain a list of images useful
+for texturing the wall. A simple way to do this is to use the images
+selected by the tiling process in Section
+\ref{sec:tileBasedMapping}. Such a list of images is guaranteed to
+cover the entire wall, and consists of desired camera poses overall.
+
 To cover the entirety of a plane, our problem can be defined as
@@
 Given that wall-texture candidate images are taken from more or less
-head-on angles, and assuming only minor rotations are made in Section
-\ref{sec:2dAlignment}, we can reason that their projections onto the
-plane are approximately rectangular. By cropping them all to be
-rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
+head-on angles, and knowing that only minor rotations are made in
+Section \ref{sec:2dAlignment}, we can reason that their projections
+onto the plane are approximately rectangular. By cropping them all to
+be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
 problem becomes the conceptually simpler one of filling a polygon with
@@
 with rectangular units, as explained in Section
-\ref{sec:simpleTextureMapping}.
+\ref{sec:tileBasedMapping}.
 
@@
 filling the hole with images that result in the lowest SSD costs in a
-10 px border region around the hole. This method is not as optimal as
-a true 2D-coverage solution would be, but it is a fast approximation,
-and adequately handles the few holes we encounter.
+blending region around the hole, as discussed in Section
+\ref{sec:blending}. This method is not as optimal as a true
+2D-coverage solution would be, but it is a fast approximation, and
+adequately handles the few holes we encounter.
 
@@
 image boundary, while the tile caching method uses a scoring function
-that only approximates this effect. Furthermore, seam minimization
-guarantees the best selection of images, while the sequential tile
-caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. The seam
-minimization approach is also far less intensive in terms of memory
+that only approximates this effect. Furthermore, this approach
+guarantees the best selection of images to minimize seams, while the
+sequential tile caching method may select images early on that turn
+out to be poor choices once subsequent tiles have been processed. This
+shortest path approach is also far less intensive in terms of memory
 usage and runtime, both during texture generation and rendering, as it
@@
 
-When texturing an entire 3D planar model, we apply the seam
-minimization approach on walls, due to its superior output when
-provided with head-on images. Floors and ceilings however, given their
-many images taken at oblique angles, are textured using the tile
-caching method.
+When texturing an entire 3D planar model, we apply the shortest path
+method on walls, due to its superior output when provided with head-on
+images. Floors and ceilings however, given their many images taken at
+oblique angles, are textured using the tile caching method.
 
@@
 unavoidable discontinuities in the final texture due to different
-lighting conditions or inaccuracies in planar geometry. These can
+lighting conditions or inaccuracies in model geometry. These can
 however be treated and smoothed over by applying alpha blending over
@@
 
-As mentioned earlier, our approach is fairly efficient, with the X by
-X pixel image in figure X, spanning an X meter long wall and
-consisting of X input images, taking under a minute to generate on a
-2.8Ghz dual-core laptop, using the shortest path method. While not
-fast enough for real-time visualization, the procedure is quick enough
-for quick evaluation given changes in various internal parameters or
-modifications to input data.
+As mentioned earlier, our approach is fairly efficient. The top wall
+in Figure \ref{fig:results}(a) is 7543 $\times$ 776 pixels, and spans a
+40-meter long wall. Given 41000 input images, it takes approximately a
+minute to pick 36 candidate images, followed, by another minute to
+perform the shortest path texturing, both on a consumer-grade 2.8GHz
+dual-core laptop with 4GB RAM. While not fast enough for real-time
+visualization, the procedure is quick enough for quick evaluation
+given changes in various internal parameters or modifications to input
+data.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
-  ~~~~~~~~
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
   \centering
@@
 
-  \centering 
-  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
-  ~~~~~~~~
-  \centering
+  \centering \subfloat[][]{\includegraphics[height=2in,
+    width=3in]{floorcropped.jpg}} ~~~~~~~~ \centering
   \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
@@
 \end{figure*}
+
+\appendix
+\section{Working with Near-Planar Geometry}
+do stuff and stuff
 

### 2012-12-31 spie/_region_.tex
nead final result and wrapup now

--- 2012-12-26 spie/_region_.tex
@@
 \usepackage{subfig}
-\usepackage{caption}
-\usepackage{subcaption}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{hyperref}
 
@@
 
-\message{ !name(paper.tex) !offset(674) }
-\subsection{Future stuff}
-For the sake of simplicity, - cases where multiple whatever are few,
-but for true generality, should go to 3d adjustments
+\message{ !name(paper.tex) !offset(278) }
+\subsection{Geometry-based Alignment}
+\label{sec:geometryAlignment}
+After computing each image's projection onto the target surface, as
+described in Section \ref{sec:simpleTextureMapping}, we detect lines
+in the projections using Hough transforms. Experience and intuition
+show that walls in indoor environments contain linear features that
+are either horizontal or vertical, often corresponding to doors,
+windows, posters, etc. Thus, when texturing walls, we rotate images in
+2D such that dominant lines are made to be horizontal or
+vertical. This can be further extrapolated by orienting lines with a
+wall's boundaries, for example in areas with a slanted roof.
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
-  ~~~~~~~~
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
+  \includegraphics[height=1.5in]{geometryAlign_planes.png}
+  \includegraphics[height=1.5in]{geometryAlignment.jpg}
+  \caption{(a) When texturing the red surface, it makes sense to align images to surface boundaries and intersections.
+(b) Red lines are geometry-based lines, while green lines are detected in the image via Hough transform.
+Above is the original projection, and below is the image adjusted for alignment.}
+  \label{fig:geometryAlignment}
+\end{figure}
 
-  \centering 
-  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
-  ~~~~~~~~
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) an entire floor, (d) a full model.}
-  \label{fig:results}
-\end{figure*}
+At this point in time, image occlusions have not been accounted
+for. As a result, some image projections contain texture that should
+project to an adjacent surface, generally with a linear boundary where
+the two surfaces meet. If this linear boundary is detected by Hough
+transform, the image is rotated and shifted in 2D such that the visual
+boundary between two surfaces matches the physical boundary in our
+digital model. An example of such an adjustment is in Figure
+\ref{fig:geometryAlignment}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% References %%%%%
+To perform the rotation and alignment, one method would be to detect
+all line matches and solve for an optimal homography. In nearly all
+cases however, we find that a single 2D rotation is sufficient to
+properly align lines in an image. We also rarely have more than one
+linear geometry feature to match to in each orthogonal
+direction. Thus, for a rotation angle, we simply take all angles
+between image-based and geometry-based lines under 5 degrees, and
+average them. After the image is rotated, we find the horizontal and
+vertical image-based and geometry-based line segments with minimum
+orthogonal distance between them. For both distances, if it is under 5
+mm, we apply the corresponding shift, and indicate that the image was
+aligned to geometry in one or both dimensions, which reduces further
+shifting in Section \ref{sec:robustSIFTFeatureMatching}.
 
-\bibliography{report} %>>>> bibliography data in report.bib
-\bibliographystyle{spiebib} %>>>> makes bibtex use spiebib.bst
-
-\message{ !name(paper.tex) !offset(672) }
+\message{ !name(paper.tex) !offset(679) }
 

### 2012-12-31 spie/paper.tex
nead final result and wrapup now

@@
 approaches to image matching and stitching, and their performance on
-our datasets. Section \ref{sec:imageAlignment} contains our approach
+our datasets. Section \ref{sec:2dAlignment} contains our approach
 towards image alignment, followed by Section
@@
   \centering
-  \includegraphics[height=1.5in]{geometryFeature.jpg}
-  \includegraphics[height=1.5in]{imageCorner.jpg}
-  \includegraphics[height=1.5in]{geometryImageAlign.jpg}
-  \caption{(a) The red lines indidcate geometry-based lines,
-    consisting of boundaries and intersections. (b) A matching
-    image-based line, corresponding to a corner. (c) The image rotated
-    and shifted such that the matched lines align align with
-    geometry.}
+  \includegraphics[height=1.5in]{geometryAlign_planes.png}
+  \includegraphics[height=1.5in]{geometryAlignment.jpg}
+  \caption{(a) When texturing the red surface, it makes sense to align images to surface boundaries and intersections.
+(b) Red lines are geometry-based lines, while green lines are detected in the image via Hough transform.
+Above is the original projection, and below is the image adjusted for alignment.}
   \label{fig:geometryAlignment}
@@
 location of the images can not be calculated, and the matrix is rank
-deficient. From Section \ref{geometryBasedAlignemtn}, a number of
+deficient. From Section \ref{sec:geometryAlignment}, a number of
 images are anchored to geometry points, in one or both dimensions, and

### 2013-01-10 spie/_region_.tex
new paper draft

--- 2012-12-26 spie/_region_.tex
@@
 
-\message{ !name(paper.tex) !offset(674) }
-\subsection{Future stuff}
-For the sake of simplicity, - cases where multiple whatever are few,
-but for true generality, should go to 3d adjustments
+\message{ !name(paper.tex) !offset(690) }
+\section{Results and Conclusions}
+\label{sec:resultsAndConclusions}
+Examples of ceilings and floors textured with the tile caching
+approach, and walls textured with the shortest path approach, are
+displayed in Figure \ref{fig:results}. High resolution texture
+comparisons, as well as a walkthrough of a fully textured 3D model are
+available in the accompanying video to this paper.
 
-\begin{figure*}
+As mentioned earlier, our approach is quite efficient. The top wall in
+Figure \ref{fig:results}(a) was generated with 7543 $\times$ 776
+pixels, and spans a 40-meter long wall. Given 41000 input images, a
+2.8GHz consumer-grade laptop takes approximately a minute to pick 36
+candidate images, followed by another minute to perform both image alignment and the shortest
+path texturing method, with the majority of computation time spent
+calculating SIFT matches within the SiftGPU framework. While not quite
+real-time visualization, the process is capable of generating quick
+updates after changes in various parameters or modifications to input
+data.
+
+In this paper, we have developed two approaches to texture map models
+with noisy camera localization data. We are able to refine image
+locations based on geometry references and feature matching, and
+robustly handle outliers. The tile-based mapping approach can be used
+to texture both simple rectangular walls as well as complex floor and
+ceiling geometry. We also developed a shortest path texturing method
+that produces seamless textures on planes where multiple head-on
+images are available. Both of these approaches are highly modular, and
+easily tunable for different environments and acquisition systems.
+
+\begin{figure}
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
-  ~~~~~~~~
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
   \centering
@@
 
-  \centering 
-  \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
-  ~~~~~~~~
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
+  \centering \subfloat[][]{
+    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
+    \includegraphics[width=3in]{pier15floor.jpg}
+  }
+
+  \centering{
+    \includegraphics[width=1.9in]{fullmodel.png}
+    \includegraphics[width=1.9in]{threestoryfull2.png}
+    \includegraphics[width=1.9in]{pier15.png} \\
+    \includegraphics[width=6in]{threestoryfull.png}
+  }
+
+  \centering \subfloat[][]{ }
   \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) an entire floor, (d) a full model.}
+    (b) ceilings, (c) floors, (d) full models.}
   \label{fig:results}
-\end{figure*}
+\end{figure}
 
@@
 
-\message{ !name(paper.tex) !offset(672) }
+\message{ !name(paper.tex) !offset(688) }
 

### 2013-01-10 spie/paper.tex
new paper draft

@@
   collected by such modeling systems. Camera poses obtained by these
-  systems often suffer from inaccuracies, resulting in visible
-  discontinuities when successive images are projected adjacently onto
-  a surface for texturing. Existing methods to stitch images together
-  are often computationally expensive and work independently of pose
-  estimates and geometry information. We propose a method to refine
-  camera poses using both existing estimates and geometry information,
-  followed by two different methods to composite images together,
-  based on the uniformity of available images. The effectiveness of
-  our methods is demonstrated on a number of different indoor
-  environments.
+  systems and used for texturing often suffer from inaccuracies
+  however, resulting in visible discontinuities when successive images
+  are projected adjacently onto a surface for texturing. Existing
+  methods to stitch images together are often computationally
+  expensive and work independently of pose estimates and geometry
+  information. We propose a method to refine camera poses using both
+  existing estimates and geometry information, followed by two
+  different methods to composite images together, based on the
+  uniformity of available images. The effectiveness of our methods is
+  demonstrated on a number of different indoor environments.
 \end{abstract}
@@
 and images, environment geometry is required as well for texture
-mapping. In this paper we work mainly with models obtained by fitting
-planar surfaces to point clouds generated by the backpack system
-\cite{sanchez2012point}. We have also developed an appropriate method
-to work with near-planar triangular meshes, as described in Appendix
-A.
+mapping. In this paper we work with models obtained by fitting planar
+surfaces to point clouds generated by the backpack system
+\cite{sanchez2012point}.A.
 
@@
 camera calibration matrices. An important benefit of our method is its
-relatively low complexity and runtime, and independence of many
-steps, allowing for quick tuning of parameters and easy
-accomodation of new input data given updates in localization or
-model-generation algorithms.
+relatively low complexity and runtime, and independence of many steps,
+allowing for live tuning of parameters and easy accomodation of new
+input data given updates in localization or model-generation
+algorithms.
 
@@
 \ref{sec:simpleTextureMapping} explains how input images are projected
-onto our geometry and simple approaches towards texturing. Section
+onto our geometry and a simple approach towards texturing. Section
 \ref{sec:existingApproaches} covers more sophisticated existing
-approaches to image matching and stitching, and their performance on
-our datasets. Section \ref{sec:2dAlignment} contains our approach
+approaches, using image matching and stitching, and their performance
+on our datasets. Section \ref{sec:2dAlignment} contains our approach
 towards image alignment, followed by Section
-\ref{sec:imageCompositing}, which describes compositing
-approaches. Section \ref{sec:resultsAndConclusions} contains further
-results and conclusions, as well as areas of ongoing and future work.
+\ref{sec:imageCompositing}, which describes our two methods of compositing images. Section \ref{sec:resultsAndConclusions} contains results and conclusions.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The geometry of the texture mapping process for a plane is shown in
-Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images to texture the target plane. Each image has a
-camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
-world coordinate system to a 2D point or pixel in image $i$'s
-coordinates. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, such as focal length and image center, as well
-as extrinsic parameters which specify the rotation and translation of
-the camera's position in 3D world coordinates at the time that image
-$i$ is taken. These extrinsic parameters are determined by the
-backpack hardware and localization algorithms \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure} and are quite noisy.
+The geometry of the texture mapping process for a planar surface is
+shown in Figure \ref{fig:projection}.  As described earlier, we are
+provided with a set of $M$ images to texture a target plane. Each
+image has a camera matrix $P_i$ for $i=1..M$, which translates a 3D
+point in the world coordinate system to a 2D point or pixel in image
+$i$'s coordinates. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, containing focal length and image center, as
+well as extrinsic parameters which specify the rotation and
+translation of the camera's position in 3D world coordinates at the
+time that image $i$ is taken. These extrinsic parameters are
+determined by the backpack hardware and localization algorithms
+\cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are quite
+noisy.
 
@@
 these images should be used, and where their contents should map onto
-the texture, in order to minimize any visual discontinuities or seams
-that would suggest that the plane's final texture is not composed of a
+the final texture, in order to minimize any visual discontinuities or
+seams that would suggest that the plane's texture is not composed of a
 single continuous image.
@@
     \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera matrics
-    $P_{1..m}$. }
+      $C_4$. Images are related to each plane through the camera
+      matrics $P_{1..m}$. }
     \label{fig:projection}
@@
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square tiles,
-in our case 5 pixels across, and choosing an image to texture each
-tile.
+a simple texturing approach can be performed by discretizing the
+target plane into small square tiles, in our case 5 pixels across, and
+choosing an image to texture each tile.
 
@@
 function in order to objectively select the best image for texturing
-$t$. Since camera pose errors compound over distance, we wish to
-minimize the distance between cameras and the surfaces they
-texture. Additionally, we desire images that are projected
-perpendicularly onto the plane, maximizing the resolution and amount
-of useful texture available in their projections, as well as
-minimizing any parallax effects due to real-world geometry not
+$t$. Since resolution decreases and camera pose errors compound over
+distance, we wish to minimize the distance between cameras and the
+surfaces they texture. Additionally, we desire images that are
+projected perpendicularly onto the plane, maximizing the resolution
+and amount of useful texture available in their projections, as well
+as minimizing any parallax effects due to real-world geometry not
 accurately represented by our digital model. In other words, we wish
@@
 \begin{figure}
-  \centering 
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive.pdf}}
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive_shift.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=1.2in]{wall2_naive.jpg}}
+  \subfloat[][]{\includegraphics[width=3in,
+    height=1.2in]{wall2_naive_shift.jpg}}
 
-  \centering
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift.pdf}}
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=1.2in]{wall2_cache_shift.jpg}}
+  \subfloat[][]{\includegraphics[width=3in,
+    height=1.2in]{wall2_shortest_shift.pdf}}
 
-  \centering 
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift_blend.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=3in,
+    height=1.2in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=3in,
+    height=1.2in]{wall2_shortest_shift_blend.pdf}}
   \caption{(a) Tile-based texturing. (b) Tile-based texturing after
@@
 image boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images. Given our high number of
-input images, it makese sense to further refine the image selection
-procedure, as performed in Section \ref{sec:imageCompositing}, but for
-our solution to be more robust, we first perform image alignment in
-order maximize the accuracy of each image.
+significant misalignment between images.
+Given our high number of input images, a better image selection procedure could be used, as described in Section \ref{sec:imageCompositing}, but a more significant and reliable improvement can be found through the alignment of our images.
 
@@
 bare surfaces, as well as repeating textures that cause difficulty in
-disambiguating features. This lack of strong reference points results
-in high uncertainty when matching images together.
+disambiguating features. This lack of reliable reference points often
+results in errors when matching images together.
 
@@
 accurate. For example, when matching a long chain of images through
-homographies, a pixel in the $nth$ image must be translated into the
-first image's coordinates by multiplying by the $3\times3$ matrix $H_1
-H_2 H_3 ... H_n$. Any error in one of these homography matrices is
+homographies, a pixel in the $nth$ image is translated into the
+first image's coordinates by multiplying by the $3\times3$ matrices $H_1
+H_2 H_3 ... H_n$. Errors in any of these homography matrices are
 propagated to all further images, resulting in drift. Figure
-\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
+\ref{fig:mosaic3D}(a) shows the output of the AutoStitch software
 package, which performs homography-based image mosaicing
-\cite{autostitch}. Even with many features spread across this surface,
-the mosaicing produces errors that cause straight lines to appear
-distorted, despite the fact that it was generated after careful hand
-tuning. Many areas with fewer visual features simply failed outright
-using this approach.
+\cite{autostitch}. Though AutoStitch performs well in areas with dense
+features, it has difficulty with even short segments of bare walls,
+and produces errors that cause straight lines to appear
+distorted. Many areas with fewer visual features or repeating texture patterns failed
+outright using AutoStitch.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
-  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{autostitchResult.jpg}}
 
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm from \cite{chen2010indoor} and (b) image
-    mosaicing.}
+  \centering
+  \subfloat[][]{\includegraphics[width=6in]{graphApproach.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=6in]{finalLong.jpg}}
+
+  \caption{Texture alignment via (a) image mosaicing, (b) the
+    graph-based localization refinement algorithm from
+    \cite{chen2010indoor}, and (c) the method proposed in this paper.}
   \label{fig:mosaic3D}
@@
 freedom \cite{liu2010indoor}. The approach in the cited paper works
-well locally, given high feature density, but over larger areas
-results again in error accumulation and drift, especially in
-feature-sparse areas, as shown in Figure
-\ref{fig:mosaic3D}(a). Furthermore, it adjusts image locations using
-an iterative process, which results in high runtime.
+well locally, but over larger areas results again in error
+accumulation and drift, as shown in Figure
+\ref{fig:mosaic3D}(b). Furthermore, it adjusts image locations using
+a long iterative process, which results in high runtime.
 
@@
 All of our following calculations and alignments are performed in 2D,
-partly for efficiency, and partly because the nature of our input data
-is such that localization error chiefly occurs in two dimensions, in
-the same plane as the surface being projected onto. Recall that our
-data acquisition system is backpack-mounted, with cameras facing to
-the sides of the operator. The operator makes efforts to walk parallel
-to walls, and the localization and model-generation algorithms that
-provide our input often conform the operator's path to be straight and
+partly for efficiency, partly because we have a large number of images
+to choose from, and partly because the nature of our input data is
+such that localization error chiefly occurs in two dimensions, in the
+same plane as the surface being projected onto. Recall that our data
+acquisition system is backpack-mounted, with cameras facing to the
+sides of the operator. The operator makes efforts to walk parallel to
+walls, and the localization and model-generation algorithms that
+provide our input conform the operator's path to be straight and
 parallel to detected surfaces \cite{kua2012loopclosure,
@@
 After computing each image's projection onto the target surface, as
-described in Section \ref{sec:simpleTextureMapping}, we detect lines
-in the projections using Hough transforms. Experience and intuition
-show that walls in indoor environments contain linear features that
-are either horizontal or vertical, often corresponding to doors,
-windows, posters, etc. Thus, when texturing walls, we rotate images in
-2D such that dominant lines are made to be horizontal or
+described in Section \ref{sec:simpleTextureMapping}, we detect line
+segments in the image projections using Hough transforms. Experience
+and intuition show that walls in indoor environments often contain
+linear features that are either horizontal or vertical, corresponding
+to doors, windows, posters, etc. Thus, when texturing walls, we rotate
+images in 2D such that dominant lines are made to be horizontal or
 vertical. This can be further extrapolated by orienting lines with a
@@
   \centering
-  \includegraphics[height=1.5in]{geometryAlign_planes.png}
-  \includegraphics[height=1.5in]{geometryAlignment.jpg}
-  \caption{(a) When texturing the red surface, it makes sense to align images to surface boundaries and intersections.
-(b) Red lines are geometry-based lines, while green lines are detected in the image via Hough transform.
-Above is the original projection, and below is the image adjusted for alignment.}
+  \subfloat[][]{\includegraphics[height=1.5in]{geometryAlign_planes.png}}
+  \subfloat[][]{\includegraphics[height=1.5in]{geometryAlignment.jpg}}
+  \caption{(a) When texturing the red surface, it makes sense to align
+    images to surface boundaries and intersections with other
+    surfaces. (b) Red lines are geometry-based lines, while green
+    lines are detected in the image via Hough transform. Above is the
+    original projection using the input camera poses, and below is the
+    projection after being adjusted for alignment.}
   \label{fig:geometryAlignment}
@@
 transform, the image is rotated and shifted in 2D such that the visual
-boundary between two surfaces matches the physical boundary in our
-digital model. An example of such an adjustment is in Figure
-\ref{fig:geometryAlignment}
+boundary between two surfaces in an image projection matches the
+physical boundary in our digital model. An example of such an
+adjustment is in Figure \ref{fig:geometryAlignment}
 
-To perform the rotation and alignment, one method would be to detect
-all line matches and solve for an optimal homography. In nearly all
-cases however, we find that a single 2D rotation is sufficient to
-properly align lines in an image. We also rarely have more than one
-linear geometry feature to match to in each orthogonal
-direction. Thus, for a rotation angle, we simply take all angles
-between image-based and geometry-based lines under 5 degrees, and
-average them. After the image is rotated, we find the horizontal and
-vertical image-based and geometry-based line segments with minimum
-orthogonal distance between them. For both distances, if it is under 5
-mm, we apply the corresponding shift, and indicate that the image was
-aligned to geometry in one or both dimensions, which reduces further
-shifting in Section \ref{sec:robustSIFTFeatureMatching}.
+To perform the rotation and alignment, we use the RANSAC
+\cite{fischler1981random} framework. RANSAC allows us to determine an
+optimal rotation and translation to match up two groups of line
+segments, while accounting for outliers. First, a rotation angle is
+computed by gathering all pairs of image line segments and geometry
+line segments with less than 20 degrees between them. We then run the
+RANSAC algorithm by sampling 4 of these angles at a time, and using
+their average as the fitting function. Angles over 2 degrees from this
+average are considered outliers. Once this 2d rotation angle is
+determined, it is applied to the image, and projections are
+re-calculated and image-based lines are re-detected. Now, all pairs of
+image line segments and geometry line segments with less than 0.2
+degree difference and less than 250 mm distance at their furthest
+points are gathered. RANSAC is then similarly employed to calculate
+optimal horizontal and vertical translations independently, by
+sampling 4 pairs at a time and considering an outlier threshold of 10
+mm. If a translation is applied, we indicate that the image was
+aligned to geometry in one or both dimensions, which will reduce
+further shifting in Section \ref{sec:robustSIFTFeatureMatching}.
 
@@
 SIFT-based distances are reliable. First, we only perform alignment on
-pairs of images that overlap given the original noisy poses. Second,
+parts of images that overlap given the original noisy poses. Second,
 we discard feature matches that correspond to an image distance
 greater than 40 pixels from what the noisy poses estimate. In order to
-utilize the remaining feature matches robustly, the RANSAC framework
-\cite{fischler1981random} is used to estimate the optimal $d^x_{i,j}$
-and $d^y_{i,j}$ distances between two images $i$ and $j$. The RANSAC
-framework requires a fitting function and a distance function. For
-this application, the fitting function finds the average distance
-between matches in a pair of images, and the distance function for a
-pair of points is chosen to be the difference between those points'
-SIFT match distance and the average distance computed by the fitting
-function. We use a 10 pixel threshold, so that SIFT matches are
-labeled as outliers if their horizontal or vertical distances are not
-within 10 pixels of the average distance computed by the fitting
-function.
+utilize the remaining feature matches robustly, RANSAC
+\cite{fischler1981random} is again used to estimate the optimal $d^x_{i,j}$
+and $d^y_{i,j}$ distances between two images $i$ and $j$. For this
+application, the RANSAC fitting function finds the average distance
+between selected matches in a pair of images, and the distance
+function for a pair of points is chosen to be the difference between
+those points' SIFT match distance and the average distance computed by
+the fitting function. We use a 10 pixel threshold, so that SIFT
+matches are labeled as outliers if their horizontal or vertical
+distances are not within 10 pixels of the average distance computed by
+the fitting function.
 
-We now use the calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
+We now use the RANSAC-calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
 between each pair of images to refine their positions using weighted
@@
 with far greater accuracy. Applying the simple mapping scheme in
-Section \ref{sec:tileBasedMapping} to the same wall used in that section results in Figure \ref{fig:compareAll}(b), which has far
-fewer seams, though some are still visible.
+Section \ref{sec:tileBasedMapping} to the same wall used in that
+section results in Figure \ref{fig:compareAll}(b), which has far fewer
+discontinuities, though errors due to lighting differences and
+repeating features are still visible.
 
@@
 The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(c), where seams are now greatly reduced as
+\ref{fig:compareAll}(c), where seams are now reduced as
 compared to Figure \ref{fig:compareAll}(b).
@@
 resolution and accuracy for their respective plane locations,
-e.g. areas near point A and not near point B, in Figure \ref{fig:projectionAngles}(b).
+e.g. areas near point A and not near point B, in Figure
+\ref{fig:projectionAngles}(b).
 
@@
 node has directed edges with equal and arbitrary cost $C_0$ to(from)
-all images that meet the left(right) border of the plane.
-
-We now solve the shortest path problem from the start node to the end
-node. This results in a set of images completely covering the plane
-horizontally, while minimizing the cost of seams between images.
+all images that meet the left(right) border of the plane. We now solve
+the shortest path problem from the start node to the end node. This
+results in a set of images completely covering the plane horizontally,
+while minimizing the cost of seams between images.
 
@@
 \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the shortest path approach exhibits better alignment and
-fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
+is clear that the shortest path approach exhibits much better
+alignment and fewer seams than the tile-caching method, as Figure
+\ref{fig:compareAll}(f) clearly has the best visual quality among the
+textures in Figure \ref{fig:compareAll}.
 
@@
 displayed in Figure \ref{fig:results}. High resolution texture
-comparisons, as well as a walkthrough of a fully textured 3D model are
-available in the accompanying video to this paper.
+comparisons, as well as further examples and interactive walkthroughs are
+available at \footnote{\url{http://www.eecs.berkeley.edu/~pcheng/textureMapping}}.
 
-As mentioned earlier, our approach is fairly efficient. The top wall
-in Figure \ref{fig:results}(a) is 7543 $\times$ 776 pixels, and spans a
-40-meter long wall. Given 41000 input images, it takes approximately a
-minute to pick 36 candidate images, followed, by another minute to
-perform the shortest path texturing, both on a consumer-grade 2.8GHz
-dual-core laptop with 4GB RAM. While not fast enough for real-time
-visualization, the procedure is quick enough for quick evaluation
-given changes in various internal parameters or modifications to input
-data.
+As mentioned earlier, our approach is quite efficient. The top wall in
+Figure \ref{fig:results}(a) was generated with 7543 $\times$ 776
+pixels, and spans a 40-meter long wall. Given 41000 input images, a
+2.8GHz consumer-grade laptop takes approximately a minute to pick 36
+candidate images, followed by another minute to perform both image
+alignment and the shortest path texturing method, with the majority of
+computation time spent calculating SIFT matches within the SiftGPU
+framework. While not quite real-time visualization, the process is
+capable of generating quick updates after changes in various
+parameters or modifications to input data.
 
-\subsection{Future stuff}
-For the sake of simplicity, - cases where multiple whatever are few,
-but for true generality, should go to 3d adjustments
+In this paper, we have developed an approach to texture mapping models
+with noisy camera localization data. We are able to refine image
+locations based on geometry references and feature matching, and
+robustly handle outliers. Using the tile-based mapping approach, we
+can texture both simple rectangular walls as well as complex floor and
+ceiling geometry. We also implemented a shortest path texturing method
+that produces seamless textures on planes where multiple head-on
+images are available. Both of these approaches are highly modular, and
+easily tunable for different environments and acquisition systems.
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
 
-  \centering \subfloat[][]{\includegraphics[height=2in,
-    width=3in]{floorcropped.jpg}} ~~~~~~~~ \centering
-  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
+  \centering \subfloat[][]{
+    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
+    \includegraphics[width=3in]{pier15floor.jpg}
+  }
+
+  \centering{
+    \includegraphics[width=1.9in]{fullmodel.png}
+    \includegraphics[width=1.9in]{threestoryfull2.png}
+    \includegraphics[width=1.9in]{pier15.png} \\
+    \includegraphics[width=6in]{threestoryfull.png}
+  }
+
+  \centering \subfloat[][]{ }
   \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) an entire floor, (d) a full model.}
+    (b) ceilings, (c) floors, (d) full models.}
   \label{fig:results}
-\end{figure*}
-
-\appendix
-\section{Working with Near-Planar Geometry}
-do stuff and stuff
+\end{figure}
 

### 2013-01-18 spie/_region_.tex
new paper

@@
 
-\message{ !name(paper.tex) !offset(690) }
-\section{Results and Conclusions}
-\label{sec:resultsAndConclusions}
-Examples of ceilings and floors textured with the tile caching
-approach, and walls textured with the shortest path approach, are
-displayed in Figure \ref{fig:results}. High resolution texture
-comparisons, as well as a walkthrough of a fully textured 3D model are
-available in the accompanying video to this paper.
+\message{ !name(paper.tex) !offset(357) }
+\subsection{2D Feature Alignment}
+\label{sec:robustSIFTFeatureMatching}
+Our next step is to align overlapping images by searching for
+corresponding points between all pairs of overlapping images. We use
+SIFT features for their high detection rate, and choose to use feature
+alignment rather than pixel or intensity-based alignment due to the
+differences in lighting as well as possible occlusion among our
+images, both of which feature alignment is less sensitive to
+\cite{lowe1999object, mikolajczyk2005performance, szeliski2006image}.
+We use SiftGPU \cite{siftgpu} for its high performance on both feature
+detection as well as pairwise matching. These matches determine $d^x$
+and $d^y$ distances between each pair of features for two image
+projections, though these distances may not always be the same for
+different features. Since indoor environments often contain repetitive
+features such as floor tiles or doors, we need to ensure that
+SIFT-based distances are reliable. First, we only perform alignment on
+parts of images that overlap given the original noisy poses. Second,
+we discard feature matches that correspond to an image distance
+greater than 40 pixels from what the noisy poses estimate. In order to
+utilize the remaining feature matches robustly, RANSAC
+\cite{fischler1981random} is again used to estimate the optimal $d^x_{i,j}$
+and $d^y_{i,j}$ distances between two images $i$ and $j$. For this
+application, the RANSAC fitting function finds the average distance
+between selected matches in a pair of images, and the distance
+function for a pair of points is chosen to be the difference between
+those points' SIFT match distance and the average distance computed by
+the fitting function. We use a 10 pixel threshold, so that SIFT
+matches are labeled as outliers if their horizontal or vertical
+distances are not within 10 pixels of the average distance computed by
+the fitting function.
 
-As mentioned earlier, our approach is quite efficient. The top wall in
-Figure \ref{fig:results}(a) was generated with 7543 $\times$ 776
-pixels, and spans a 40-meter long wall. Given 41000 input images, a
-2.8GHz consumer-grade laptop takes approximately a minute to pick 36
-candidate images, followed by another minute to perform both image alignment and the shortest
-path texturing method, with the majority of computation time spent
-calculating SIFT matches within the SiftGPU framework. While not quite
-real-time visualization, the process is capable of generating quick
-updates after changes in various parameters or modifications to input
-data.
+We now use the RANSAC-calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
+between each pair of images to refine their positions using weighted
+linear least squares. There are a total of $M^{2}$ possible pairs of
+images, though we only generate distances between images with SIFT
+matches. Given these distances and the original image location
+estimates, we can solve a least squares problem
+($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
+to estimate the location of the images on the plane. The
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
+location of each image on the plane for $1 \dots M$. The optimal $x$
+and $y$ locations are obtained in the same way, so we only consider
+the $x$ locations here:
 
-In this paper, we have developed two approaches to texture map models
-with noisy camera localization data. We are able to refine image
-locations based on geometry references and feature matching, and
-robustly handle outliers. The tile-based mapping approach can be used
-to texture both simple rectangular walls as well as complex floor and
-ceiling geometry. We also developed a shortest path texturing method
-that produces seamless textures on planes where multiple head-on
-images are available. Both of these approaches are highly modular, and
-easily tunable for different environments and acquisition systems.
+\[\vec{\beta} =
+\begin{pmatrix}
+  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
+\end{pmatrix}
+\]
 
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
+The $N \times M$ matrix $A$ is constructed with one row for each pair
+of images with measured distances produced by the SIFT matching
+stage. A row in the matrix has a $-1$ and $1$ in the columns
+corresponding to the two images in the pair. For example, the matrix
+below indicates a SIFT-based distance between images 1 and 2, images 1
+and 3, images 2 and 3, etc.
+\[
+A =
+\begin{pmatrix}
+  -1 & 1 & 0 & \cdots & 0 & 0\\
+  -1 & 0 & 1 & \cdots & 0 & 0\\
+  0 & -1 & 1 & \cdots & 0 & 0\\
+  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
+  0 & 0 & 0 & \cdots & 1 & 0 \\
+  0 & 0 & 0 & \cdots & -1 & 1 \\
+  1 & 0 & 0 & \cdots & 0 & 0\\
+\end{pmatrix}
+\]
+If only relative distances between images are included, the absolute
+location of the images can not be calculated, and the matrix is rank
+deficient. From Section \ref{sec:geometryAlignment}, a number of
+images are anchored to geometry points, in one or both dimensions, and
+thus their locations can be used to fix the rest in place. In case no
+anchor images exist, we simply arbitrarily pick an image, as we have
+no other reference points to work with. In the above matrix, the first
+image is set to be such an anchor, simply by placing a $1$ in its
+column.
 
-  \centering \subfloat[][]{
-    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
-    \includegraphics[width=3in]{pier15floor.jpg}
-  }
+The $N$-dimensional observation vector $\vec{\gamma}$ is constructed
+using the SIFT-based distances generated in the RANSAC matching
+stage. Elements in the observation vector corresponding to anchor
+images are simply their locations as determined by the original noisy
+localization. Thus a $\vec{\gamma}$ corresponding to the above matrix
+can be written as:
 
-  \centering{
-    \includegraphics[width=1.9in]{fullmodel.png}
-    \includegraphics[width=1.9in]{threestoryfull2.png}
-    \includegraphics[width=1.9in]{pier15.png} \\
-    \includegraphics[width=6in]{threestoryfull.png}
-  }
+\[
+\vec{\gamma}^T =
+\begin{pmatrix}
+  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
+\end{pmatrix}
+\]
 
-  \centering \subfloat[][]{ }
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) floors, (d) full models.}
-  \label{fig:results}
-\end{figure}
+The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
+\vec{\gamma}||_2^2$ results in a set of image locations on the plane
+that best honors all the SIFT-based distance measurements between
+images. This solution however does not make use of our noisy camera
+poses, and will fail when no SIFT matches are found between one
+segment of the plane and another. To account for this, we add rows to
+the $A$ matrix and observations to the $\vec{\gamma}$ vector
+corresponding to the original noisy distances. We then add weighting
+to our least squares problem where the SIFT distances and anchor
+values are given a high weight e.g. 1, while the noisy distances are
+given a smaller weight e.g. 0.01.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% References %%%%%
+After completing this same process for the $y$ dimension as well, and
+making the resultant shifts, our images overlap and match each other
+with far greater accuracy. Applying the simple mapping scheme in
+Section \ref{sec:tileBasedMapping} to the same wall used in that
+section results in Figure \ref{fig:compareAll}(b), which has far fewer
+discontinuities, though errors due to lighting differences and
+repeating features are still visible.
 
-\bibliography{report} %>>>> bibliography data in report.bib
-\bibliographystyle{spiebib} %>>>> makes bibtex use spiebib.bst
-
-\message{ !name(paper.tex) !offset(688) }
+\message{ !name(paper.tex) !offset(650) }
 

### 2013-01-18 spie/newpaper.tex
new paper

--- 2012-12-30 spie/paper.tex
@@
 \begin{abstract}
-
   Automated 3D modeling of building interiors is used in applications
@@
   collected by such modeling systems. Camera poses obtained by these
-  systems often suffer from inaccuracies, resulting in visible
-  discontinuities when successive images are projected adjacently onto
-  a surface for texturing. Existing methods to stitch images together
-  are often computationally expensive and work independently of pose
-  estimates and geometry information. We propose a method to refine
-  camera poses using both existing estimates and geometry information,
-  followed by two different methods to composite images together,
-  based on the uniformity of available images. The effectiveness of
-  our methods is demonstrated on a number of different indoor
-  environments.
+  systems and used for texturing often suffer from inaccuracies
+  however, resulting in visible discontinuities when successive images
+  are projected onto a surface for texturing. Existing methods to
+  stitch images together are often computationally expensive and work
+  independently of pose estimates and geometry information. Using data
+  from a human-operated backpack system, we propose an efficient
+  method to refine camera poses in 2D using both existing estimates
+  and geometry information, followed by two different methods to
+  composite images together, based on the geometry of surfaces being
+  textured. The effectiveness of our methods is demonstrated on a
+  number of different indoor environments.
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:introduction} % \label{} allows reference to this section
+\label{sec:introduction}
+Three-dimensional modeling of indoor environments has a variety of
+applications in fields such as architecture and simulation. Adding
+accurate textures to these models is important in adding context to
+digital visualizations, and allows for image-based analysis of
+environments.  In this paper, we work with a backpack-mounted system,
+carried by an ambulatory human. This backpack system contains a series
+of laser scanners and inertial measurement units, allowing it to solve
+the simultaneous localization and mapping (SLAM) problem, which
+produces backpack poses over time, and a point cloud representing its
+environment. For our environment geometry, we work with models
+obtained by fitting low-resolution planar surfaces to these point
+clouds.  While a human-carried system provides advantages over more
+common wheel-mounted systems in terms of agility and portability, it
+often leads to relatively high localization error even after applying
+sophisticated localization techniques. Furthermore, our model geometry
+often contains some error as well, and is often adjusted to ignore
+low-resolution features, such as small walls, furniture, and various
+small features commonly found in indoor environments. As a result,
+methods for texture mapping that rely on accurate camera poses
+generally produce poor results.
 
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time-consuming, and as a
-result, automated 3D site modeling has garnered much interest in
-recent years.
+Our goal of texturing planar surfaces with misaligned camera poses
+straddles a number of highly-researched fields, including image
+stitching, panorama generation, and image-based localization
+algorithims. We will examine the results of existing approaches in
+Section X, and compare them with our approach, which utilizes several
+aspects of our modeling system and input data.
 
-The first step in automated 3D modeling is the physical scanning of an
-environment's geometry. An indoor modeling system must recover its own
-poses within an environment while simultaneously reconstructing the 3D
-structure of the environment itself. \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure}. This is known as the
-simultaneous localization and mapping (SLAM) problem, and is generally
-solved by taking readings from laser range scanners, cameras, and
-inertial measurement units (IMUs) at multiple locations within the
-environment.
-
-In this paper, we work with data obtained from a backpack-mounted
-system, carried by an ambulatory human. Such a system provides
-advantages over more common wheel-mounted systems in terms of agility
-and portability, but results in much higher localization error
-\cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results, leading to the development of the
-approaches contained in this paper. Besides localization information
-and images, environment geometry is required as well for texture
-mapping. In this paper we work mainly with models obtained by fitting
-planar surfaces to point clouds generated by the backpack system
-\cite{sanchez2012point}. We have also developed an appropriate method
-to work with near-planar triangular meshes, as described in Appendix
-A.
-
-Though our texture mapping procedure was designed with the
-aforementioned system in mind, it is applicable to other systems,
-provided the required inputs of planar geometry, images with rough
-extrinsic pose estimates, and either known or estimated intrinsic
-camera calibration matrices. An important benefit of our method is its
-relatively low complexity and runtime, and independence of many
-steps, allowing for quick tuning of parameters and easy
-accomodation of new input data given updates in localization or
-model-generation algorithms.
-
-The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} explains how input images are projected
-onto our geometry and simple approaches towards texturing. Section
-\ref{sec:existingApproaches} covers more sophisticated existing
-approaches to image matching and stitching, and their performance on
-our datasets. Section \ref{sec:imageAlignment} contains our approach
-towards image alignment, followed by Section
-\ref{sec:imageCompositing}, which describes compositing
-approaches. Section \ref{sec:resultsAndConclusions} contains further
-results and conclusions, as well as areas of ongoing and future work.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Simple Texture Mapping}
-\label{sec:simpleTextureMapping}
-
-The geometry of the texture mapping process for a plane is shown in
-Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images to texture the target plane. Each image has a
-camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
-world coordinate system to a 2D point or pixel in image $i$'s
-coordinates. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, such as focal length and image center, as well
-as extrinsic parameters which specify the rotation and translation of
-the camera's position in 3D world coordinates at the time that image
-$i$ is taken. These extrinsic parameters are determined by the
-backpack hardware and localization algorithms \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure} and are quite noisy.
-
-Because our backpack system takes photos at a rate of 5 Hz, thousands
-of images are available for texturing each surface in our model. Our
-goal in designing a texture mapping process is to decide which of
-these images should be used, and where their contents should map onto
-the texture, in order to minimize any visual discontinuities or seams
-that would suggest that the plane's final texture is not composed of a
-single continuous image.
-
-\begin{figure}
-  \begin{minipage}[b]{0.45\linewidth}
-  \centering
-  \includegraphics[height=2in]{Projection.pdf}
-  \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera matrics
-    $P_{1..m}$. }
-  \label{fig:projection}
-  \end{minipage}
-  \hspace{0.5cm}
-  \begin{minipage}[b]{0.45\linewidth}
-  \centering
-  \includegraphics[height=1.5in]{scoringFunction.jpg}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by
-    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-    \cdot \vec{n}$}
-  \label{fig:scoringFunction}
-  \end{minipage}
-\end{figure}
-
-\subsection{Tile-based Texture Mapping}
-\label{sec:tileBasedMapping}
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square tiles,
-in our case 5 pixels across, and choosing an image to texture each
-tile.
-
-We choose to work with rectangular units to ensure that borders
-between any two distinct images in the final texture are either
-horizontal or vertical. Since most strong environmental features
-inside buildings are horizontal or vertical, any visible seams in our
-texture intersect them minimally and are less noticeable.
-
-In order to select an image for texturing a tile $t$, we must first
-gather a list of candidate images that contain all four of its
-corners, which we can quickly check by projecting $t$ into each image
-using the $P_i$ camera matrices. Furthermore, each candidate image
-must have been taken at a time when its camera had a clear
-line-of-sight to $t$, which can be calculated using standard
-ray-polygon intersection tests between the camera location, $t$, and
-every other plane \cite{rayintersection}.
-
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image for texturing
-$t$. Since camera pose errors compound over distance, we wish to
-minimize the distance between cameras and the surfaces they
-texture. Additionally, we desire images that are projected
-perpendicularly onto the plane, maximizing the resolution and amount
-of useful texture available in their projections, as well as
-minimizing any parallax effects due to real-world geometry not
-accurately represented by our digital model. In other words, we wish
-to minimize the angle between the tile's normal vector and the camera
-axis for images selected for texture mapping. These two criteria can
-be met by maximizing the function $\frac{1}{d} (-1 \cdot \vec{c})
-\cdot \vec{n}$ as shown in Figure
-\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
-the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-the directions of the plane's normal and the camera axis respectively.
-
-\begin{figure}
-  \centering 
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive.pdf}}
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_naive_shift.pdf}}
-
-  \centering
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift.pdf}}
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift.pdf}}
-
-  \centering 
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3in, height=0.97in]{wall2_shortest_shift_blend.pdf}}
-  \caption{(a) Tile-based texturing. (b) Tile-based texturing after
-    image alignment. (c) Tile-based texturing after image alignment
-    with caching. (d) Shortest path texturing after image
-    alignment). (e) Same as (c) with blending. (f) Same as (d) with
-    blending.}
-  \label{fig:compareAll}
-\end{figure}
-
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but results in many
-image boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images. Given our high number of
-input images, it makese sense to further refine the image selection
-procedure, as performed in Section \ref{sec:imageCompositing}, but for
-our solution to be more robust, we first perform image alignment in
-order maximize the accuracy of each image.
-
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-Stitching together multiple images to produce a larger image is a
-commonly performed task, with many successful approaches over the past
-few decades. Parts of images are first matched to eachother, through
-direct pixel comparisons, or more commonly through feature detection
-and matching. Images are then adjusted to maximize matches, either by
-calculating homographies between pairs of images, or by modifying
-camera poses in 1 to 6 degrees of freedom.
-
-Feature detection and matching works best when multiple unique visual
-references exist in the environment and are present within multiple
-images. In contrast, our indoor environments have a high prevalence of
-bare surfaces, as well as repeating textures that cause difficulty in
-disambiguating features. This lack of strong reference points results
-in high uncertainty when matching images together.
-
-Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not
-accurate. For example, when matching a long chain of images through
-homographies, a pixel in the $nth$ image must be translated into the
-first image's coordinates by multiplying by the $3\times3$ matrix $H_1
-H_2 H_3 ... H_n$. Any error in one of these homography matrices is
-propagated to all further images, resulting in drift. Figure
-\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
-package, which performs homography-based image mosaicing
-\cite{autostitch}. Even with many features spread across this surface,
-the mosaicing produces errors that cause straight lines to appear
-distorted, despite the fact that it was generated after careful hand
-tuning. Many areas with fewer visual features simply failed outright
-using this approach.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
-  \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
-
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm from \cite{chen2010indoor} and (b) image
-    mosaicing.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-Image projections can also be aligned by iteratively adjusting camera
-poses to maximize matches. This is generally done over 6 degrees of
-freedom \cite{liu2010indoor}. The approach in the cited paper works
-well locally, given high feature density, but over larger areas
-results again in error accumulation and drift, especially in
-feature-sparse areas, as shown in Figure
-\ref{fig:mosaic3D}(a). Furthermore, it adjusts image locations using
-an iterative process, which results in high runtime.
-
-\section{2D Image Alignment with Geometry Information}
-\label{sec:2dAlignment}
-In this section, we describe our method of efficient and robust image
-alignment. Our approach consists of three main parts. First, all
-images are projected onto the surface and lines within these
-projections are detected. These lines are then matched up with
-geometry-based lines comprising the surface's boundary and
-intersection with other surfaces. Second, occlusion checks are
-performed to remove invalid parts of each image for the target
-surface. These two steps are image-independent and performed in
-parallel. Third, we detect SIFT feature matches between pairs of
-images and solve a linear least squares problem in 2D to maximize
-matches.
-
-All of our following calculations and alignments are performed in 2D,
-partly for efficiency, and partly because the nature of our input data
-is such that localization error chiefly occurs in two dimensions, in
-the same plane as the surface being projected onto. Recall that our
-data acquisition system is backpack-mounted, with cameras facing to
-the sides of the operator. The operator makes efforts to walk parallel
-to walls, and the localization and model-generation algorithms that
-provide our input often conform the operator's path to be straight and
-parallel to detected surfaces \cite{kua2012loopclosure,
-  sanchez2012point}. Since the operator walks in as upright a position
-as possible, errors in roll, yaw, and the operator's distance from
-parallel surfaces are minimal. Thus, our highest errors stem from
-uncertainty in the operator's pitch, equivalent to rotation around the
-camera axes, as well as location along surfaces. These equate to 2D
-rotation and translation in a surface's plane.
-
-\subsection{Geometry-based Alignment}
-\label{sec:geometryAlignment}
-After computing each image's projection onto the target surface, as
-described in Section \ref{sec:simpleTextureMapping}, we detect lines
-in the projections using Hough transforms. Experience and intuition
-show that walls in indoor environments contain linear features that
-are either horizontal or vertical, often corresponding to doors,
-windows, posters, etc. Thus, when texturing walls, we rotate images in
-2D such that dominant lines are made to be horizontal or
-vertical. This can be further extrapolated by orienting lines with a
-wall's boundaries, for example in areas with a slanted roof.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=1.5in]{geometryFeature.jpg}
-  \includegraphics[height=1.5in]{imageCorner.jpg}
-  \includegraphics[height=1.5in]{geometryImageAlign.jpg}
-  \caption{(a) The red lines indidcate geometry-based lines,
-    consisting of boundaries and intersections. (b) A matching
-    image-based line, corresponding to a corner. (c) The image rotated
-    and shifted such that the matched lines align align with
-    geometry.}
-  \label{fig:geometryAlignment}
-\end{figure}
-
-At this point in time, image occlusions have not been accounted
-for. As a result, some image projections contain texture that should
-project to an adjacent surface, generally with a linear boundary where
-the two surfaces meet. If this linear boundary is detected by Hough
-transform, the image is rotated and shifted in 2D such that the visual
-boundary between two surfaces matches the physical boundary in our
-digital model. An example of such an adjustment is in Figure
-\ref{fig:geometryAlignment}
-
-To perform the rotation and alignment, one method would be to detect
-all line matches and solve for an optimal homography. In nearly all
-cases however, we find that a single 2D rotation is sufficient to
-properly align lines in an image. We also rarely have more than one
-linear geometry feature to match to in each orthogonal
-direction. Thus, for a rotation angle, we simply take all angles
-between image-based and geometry-based lines under 5 degrees, and
-average them. After the image is rotated, we find the horizontal and
-vertical image-based and geometry-based line segments with minimum
-orthogonal distance between them. For both distances, if it is under 5
-mm, we apply the corresponding shift, and indicate that the image was
-aligned to geometry in one or both dimensions, which reduces further
-shifting in Section \ref{sec:robustSIFTFeatureMatching}.
-
-\subsection{Image Occlusion}
-\label{sec:imageOcclusion}
-Now that images have been aligned to geometry where possible, we
-perform a simple recursive occlusion procedure on each image. This is
-done by performing the intersection tests in section
-\ref{sec:simpleTextureMapping} in a regularly spaced grid. Where four
-corners of a rectangular region are occluded, texture is
-removed. Where no corners are occluded, nothing occurs. Where there is
-a mixture of both, the rectangular region is subdivided into four, and
-the same process is performed on each. By performing Section
-\ref{sec:geometryAlignment}'s alignment procedure before occlusion,
-texture belonging to other surfaces is accurately removed, which is
-necessary for the next section.
-
-\subsection{2D Feature Alignment}
-\label{sec:robustSIFTFeatureMatching}
-Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images. We use
-SIFT features for their high detection rate, and choose to use feature
-alignment rather than pixel or intensity-based alignment due to the
-differences in lighting as well as possible occlusion among our
-images, both of which feature alignment is less sensitive to
-\cite{lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-We use SiftGPU \cite{siftgpu} for its high performance on both feature
-detection as well as pairwise matching. These matches determine $d^x$
-and $d^y$ distances between each pair of features for two image
-projections, though these distances may not always be the same for
-different features. Since indoor environments often contain repetitive
-features such as floor tiles or doors, we need to ensure that
-SIFT-based distances are reliable. First, we only perform alignment on
-pairs of images that overlap given the original noisy poses. Second,
-we discard feature matches that correspond to an image distance
-greater than 40 pixels from what the noisy poses estimate. In order to
-utilize the remaining feature matches robustly, the RANSAC framework
-\cite{fischler1981random} is used to estimate the optimal $d^x_{i,j}$
-and $d^y_{i,j}$ distances between two images $i$ and $j$. The RANSAC
-framework requires a fitting function and a distance function. For
-this application, the fitting function finds the average distance
-between matches in a pair of images, and the distance function for a
-pair of points is chosen to be the difference between those points'
-SIFT match distance and the average distance computed by the fitting
-function. We use a 10 pixel threshold, so that SIFT matches are
-labeled as outliers if their horizontal or vertical distances are not
-within 10 pixels of the average distance computed by the fitting
-function.
-
-We now use the calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
-between each pair of images to refine their positions using weighted
-linear least squares. There are a total of $M^{2}$ possible pairs of
-images, though we only generate distances between images with SIFT
-matches. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
-
-\[\vec{\beta} =
-\begin{pmatrix}
-  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
-\end{pmatrix}
-\]
-
-The $N \times M$ matrix $A$ is constructed with one row for each pair
-of images with measured distances produced by the SIFT matching
-stage. A row in the matrix has a $-1$ and $1$ in the columns
-corresponding to the two images in the pair. For example, the matrix
-below indicates a SIFT-based distance between images 1 and 2, images 1
-and 3, images 2 and 3, etc.
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & \cdots & 0 & 0\\
-  -1 & 0 & 1 & \cdots & 0 & 0\\
-  0 & -1 & 1 & \cdots & 0 & 0\\
-  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
-  0 & 0 & 0 & \cdots & 1 & 0 \\
-  0 & 0 & 0 & \cdots & -1 & 1 \\
-  1 & 0 & 0 & \cdots & 0 & 0\\
-\end{pmatrix}
-\]
-If only relative distances between images are included, the absolute
-location of the images can not be calculated, and the matrix is rank
-deficient. From Section \ref{geometryBasedAlignemtn}, a number of
-images are anchored to geometry points, in one or both dimensions, and
-thus their locations can be used to fix the rest in place. In case no
-anchor images exist, we simply arbitrarily pick an image, as we have
-no other reference points to work with. In the above matrix, the first
-image is set to be such an anchor, simply by placing a $1$ in its
-column.
-
-The $N$-dimensional observation vector $\vec{\gamma}$ is constructed
-using the SIFT-based distances generated in the RANSAC matching
-stage. Elements in the observation vector corresponding to anchor
-images are simply their locations as determined by the original noisy
-localization. Thus a $\vec{\gamma}$ corresponding to the above matrix
-can be written as:
-
-\[
-\vec{\gamma}^T =
-\begin{pmatrix}
-  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
-\end{pmatrix}
-\]
-
-The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
-\vec{\gamma}||_2^2$ results in a set of image locations on the plane
-that best honors all the SIFT-based distance measurements between
-images. This solution however does not make use of our noisy camera
-poses, and will fail when no SIFT matches are found between one
-segment of the plane and another. To account for this, we add rows to
-the $A$ matrix and observations to the $\vec{\gamma}$ vector
-corresponding to the original noisy distances. We then add weighting
-to our least squares problem where the SIFT distances and anchor
-values are given a high weight e.g. 1, while the noisy distances are
-given a smaller weight e.g. 0.01.
-
-After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and match each other
-with far greater accuracy. Applying the simple mapping scheme in
-Section \ref{sec:tileBasedMapping} to the same wall used in that section results in Figure \ref{fig:compareAll}(b), which has far
-fewer seams, though some are still visible.
-
-\section{Image Compositing}
-\label{sec:imageCompositing}
-In this section, we revisit the tile-based texturing approach from
-Section \ref{sec:simpleTextureMapping}, with an added caching
-mechanism to reduce image boundaries. This method works well given all
-manner of camera poses and surfaces, but for optimal cases where we
-have large sections of usable texture from images, we propose a
-superior method that further reduces image boundaries.
-
-\subsection{Tile-Mapping with Caching}
-\label{sec:mappingWithCaching}
-From Section \ref{sec:tileBasedMapping}, we saw that discontinuities
-occur where adjacent tiles are textured by different images. Though
-Section \ref{sec:2dAlignment}'s image alignment removes many such
-discontinuities, there are still cases where seams are visible due to
-imprecise matching or other factors such as model-based errors. To
-reduce the cases where this happens, it makes sense to take into
-account image selections made by neighboring tiles while texture
-mapping a given tile. By using the same image across tile boundaries,
-we can eliminate a discontinuity altogether. If this is not possible
-because a tile is not visible in images used by neighboring tiles,
-using similar images across tile boundaries also leads to less
-noticeable discontinuities.
-
-Essentially a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set of valid images. The first
-subset of images is the images selected by adjacent tiles that have
-already been textured. We must first check which of these images can
-map to $t$, and then of those, we make a choice according to the
-scoring function in Figure \ref{fig:scoringFunction}. Before reusing
-this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
-order to ensure a high resolution projection, with $\alpha$ as the
-camera angle as shown in Figure \ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check a
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar, and thus likely matched more cleanly. If
-no viable image is found according to the same criteria as before, we
-search the entire set of candidate images, selecting based on the same
-scoring function from Figure \ref{fig:scoringFunction}.
-
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(c), where seams are now greatly reduced as
-compared to Figure \ref{fig:compareAll}(b).
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a) Images for vertical planes are tilted, but their camera
-    axes are more or less normal to their respective planes. (b)
-    Camera axes for ceiling images are at large angles with respect to
-    plane normals. (c) Wall images are cropped to be rectangular.}
-  \label{fig:projectionAngles}
-\end{figure}
-
-As mentioned earlier, our data comes from a mobile backpack
-system. Human operators can not carry the backpack in a perfectly
-upright position and are bent forwards at 15 to 20 degrees with
-respect to the vertical direction. As a result, cameras facing
-sideways are head on with respect to vertical walls, while cameras
-oriented towards the top or bottom of the backpack are at an angle
-with respect to horizontal floors and ceilings. This is depicted in
-Figures \ref{fig:projectionAngles}(a) and
-\ref{fig:projectionAngles}(b). These oblique camera angles for
-horizontal surfaces translate into textures that span large areas once
-projected, as shown in Figure \ref{fig:projectionAngles}(b). Using the
-tile-based texture mapping criteria from Figure
-\ref{fig:scoringFunction}, such projections have highly varying scores
-depending on the location of a tile on the plane. Thus, the tiling
-approach in this section is a good choice for texturing floors and
-ceilings, as it uses the parts of image projections that maximize
-resolution and accuracy for their respective plane locations,
-e.g. areas near point A and not near point B, in Figure \ref{fig:projectionAngles}(b).
-
-\subsection{Shortest Path Texturing}
-\label{sec:shortestPath}
-For vertical walls, most images are taken from close distances and
-head-on angles, resulting in high resolution fronto-parallel
-projections. As a result, for each tile on a wall plane, the scoring
-function of Figure \ref{fig:scoringFunction} is relatively flat with
-respect to candidate images, as they are all more or less head
-on. Thus, the scoring function is less significant for walls, and it
-is conceivable to use a different texturing strategy to directly
-minimize visible seams when texturing them. This is done by choosing
-the smallest possible set of images that (a) covers the entire plane
-and (b) minimizes the visibility of borders between them. A
-straightforward cost function that accomplishes the latter is the sum
-of squared differences (SSD) of pixels in overlapping regions between
-all pairs of images. Minimizing this cost function encourages image
-boundaries to occur either in featureless areas, such as bare walls,
-or in areas where images match extremely well.
-
-The first step in this procedure is to obtain a list of images useful
-for texturing the wall. A simple way to do this is to use the images
-selected by the tiling process in Section
-\ref{sec:tileBasedMapping}. Such a list of images is guaranteed to
-cover the entire wall, and consists of desired camera poses overall.
-
-To cover the entirety of a plane, our problem can be defined as
-minimally covering a polygon i.e. the planar surface, using other
-polygons of arbitrary geometry i.e. image projections, with the added
-constraint of minimizing the cost function between chosen images.
-This is a complex problem, though we can take a number of steps to
-simplify it.
-
-Given that wall-texture candidate images are taken from more or less
-head-on angles, and knowing that only minor rotations are made in
-Section \ref{sec:2dAlignment}, we can reason that their projections
-onto the plane are approximately rectangular. By cropping them all to
-be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
-problem becomes the conceptually simpler one of filling a polygon with
-rectangles, such that the sum of all costs between each pair of
-rectangles is minimal. We thus also retain the advantages of working
-with rectangular units, as explained in Section
-\ref{sec:tileBasedMapping}.
-
-The operator's path, and the location and orientation of the cameras
-on the acquisition backpack is such that images nearly always contain
-the entirety of the floor to ceiling range of wall planes. Images
-therefore rarely need to be projected with one above another when
-texturing wall planes. In essence, we need only to ensure lateral
-coverage of wall planes, e.g. from left to right, as our images
-provide full vertical coverage themselves. We can thus construct a
-Directed Acyclic Graph (DAG) from the images, with edge costs defined
-by the SSD cost function, and solve a simple shortest path problem to
-find an optimal subset of images with regard to the SSD cost function
-\cite{dijkstra}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process. \\}
-  \label{fig:dagCreation}
-\end{figure}
-
-Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a hallway wall. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
-between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal and arbitrary cost $C_0$ to(from)
-all images that meet the left(right) border of the plane.
-
-We now solve the shortest path problem from the start node to the end
-node. This results in a set of images completely covering the plane
-horizontally, while minimizing the cost of seams between images.
-
-In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. Since these holes are rare,
-and generally fairly small, we use a greedy approach, repeatedly
-filling the hole with images that result in the lowest SSD costs in a
-blending region around the hole, as discussed in Section
-\ref{sec:blending}. This method is not as optimal as a true
-2D-coverage solution would be, but it is a fast approximation, and
-adequately handles the few holes we encounter.
-
-With this completed, we have now mapped every location on the plane to
-at least one image, and have minimized the number of images, as well
-as the discontinuities at their borders. As seen in Figure
-\ref{fig:compareAll}(d), this shortest path method has fewer visible
-discontinuities than Figure \ref{fig:compareAll}(c) corresponding to
-the tile caching approach\footnote{In Figure \ref{fig:compareAll}(d),
-  we arbitrarily chose one image for texturing where images overlap,
-  as blending will be discussed in section \ref{sec:blending}.}. This
-is especially evident when comparing the posters in the images, which
-have clear misalignment over seams in Figure \ref{fig:compareAll}(c),
-but are much more aligned in Figure \ref{fig:compareAll}(d). This
-shortest path approach approach directly reduces the cost of each
-image boundary, while the tile caching method uses a scoring function
-that only approximates this effect. Furthermore, this approach
-guarantees the best selection of images to minimize seams, while the
-sequential tile caching method may select images early on that turn
-out to be poor choices once subsequent tiles have been processed. This
-shortest path approach is also far less intensive in terms of memory
-usage and runtime, both during texture generation and rendering, as it
-does not require discretizing planes or images.
-
-When texturing an entire 3D planar model, we apply the shortest path
-method on walls, due to its superior output when provided with head-on
-images. Floors and ceilings however, given their many images taken at
-oblique angles, are textured using the tile caching method.
-
-\subsection{Blending}
-\label{sec:blending}
-We now apply a blending procedure to both texturing methods. Although
-the image alignment steps and image selection in both methods attempt
-to minimize all mismatches between images, there are occasional
-unavoidable discontinuities in the final texture due to different
-lighting conditions or inaccuracies in model geometry. These can
-however be treated and smoothed over by applying alpha blending over
-image seams.  Whether the units we are blending are
-rectangularly-cropped images or rectangular tiles, we can apply the
-same blending procedure, as long as we have a guaranteed overlap
-between units to blend over.
-
-For the tile caching method, we can ensure overlap by texturing a
-larger tile than needed for display. For example, for a rendered tile
-$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size.  We have found $l_2 = \frac{l_1}{2}$ to
-provide a balance between blending and keeping features unblurred. For
-the shortest path method, we have already ensured overlap between
-images. To enforce consistent blending however, we add a minimum
-required overlap distance of 40 px while solving the shortest path
-problem in Section \ref{sec:shortestPath}. Additionally, if images
-overlap in a region greater than the overlap distance, we only apply
-blending over an area equal to the overlap distance.
-
-After performing linear alpha blending across overlapping regions, our
-texture mapping process is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the shortest path approach exhibits better alignment and
-fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
-
-\section{Results and Conclusions}
-\label{sec:resultsAndConclusions}
-Examples of ceilings and floors textured with the tile caching
-approach, and walls textured with the shortest path approach, are
-displayed in Figure \ref{fig:results}. High resolution texture
-comparisons, as well as a walkthrough of a fully textured 3D model are
-available in the accompanying video to this paper.
-
-As mentioned earlier, our approach is fairly efficient. The top wall
-in Figure \ref{fig:results}(a) is 7543 $\times$ 776 pixels, and spans a
-40-meter long wall. Given 41000 input images, it takes approximately a
-minute to pick 36 candidate images, followed, by another minute to
-perform the shortest path texturing, both on a consumer-grade 2.8GHz
-dual-core laptop with 4GB RAM. While not fast enough for real-time
-visualization, the procedure is quick enough for quick evaluation
-given changes in various internal parameters or modifications to input
-data.
-
-\subsection{Future stuff}
-For the sake of simplicity, - cases where multiple whatever are few,
-but for true generality, should go to 3d adjustments
-
-\begin{figure*}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[height=2in,
-    width=3in]{floorcropped.jpg}} ~~~~~~~~ \centering
-  \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) an entire floor, (d) a full model.}
-  \label{fig:results}
-\end{figure*}
-
-\appendix
-\section{Working with Near-Planar Geometry}
-do stuff and stuff
+The remainder of the paper is organized as follows.
+Section X demonstrates 2 existing algorithms on our datasets and discusses unique aspects of our modeling system.
+Section X describes the basics of image projection, and a tile-based mapping approach and its shortcomings.
+Section X presents our approach towards image alignment, followed by Section X, which describes our two methods of compositing images.
+Section X contains results and conclusions.
 

### 2013-01-18 spie/paper.tex
new paper

@@
   however, resulting in visible discontinuities when successive images
-  are projected adjacently onto a surface for texturing. Existing
-  methods to stitch images together are often computationally
-  expensive and work independently of pose estimates and geometry
-  information. We propose a method to refine camera poses using both
-  existing estimates and geometry information, followed by two
-  different methods to composite images together, based on the
-  uniformity of available images. The effectiveness of our methods is
+  are projected onto a surface for texturing. Existing methods to
+  stitch images together are often computationally expensive and work
+  independently of pose estimates and geometry information. We propose
+  an efficient method to refine camera poses in 2D using both existing
+  estimates and geometry information, followed by two different
+  methods to composite images together, based on the geometry of
+  surfaces being textured. The effectiveness of our methods is
   demonstrated on a number of different indoor environments.
@@
 poses within an environment while simultaneously reconstructing the 3D
-structure of the environment itself. \cite{chen2010indoor,
+structure of the environment itself \cite{chen2010indoor,
   liu2010indoor, kua2012loopclosure}. This is known as the
@@
 advantages over more common wheel-mounted systems in terms of agility
-and portability, but results in much higher localization error
-\cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results, leading to the development of the
-approaches contained in this paper. Besides localization information
-and images, environment geometry is required as well for texture
-mapping. In this paper we work with models obtained by fitting planar
-surfaces to point clouds generated by the backpack system
-\cite{sanchez2012point}.A.
+and portability, but results in higher difficulty and error when
+performing localization \cite{liu2010indoor}. As a result, approaches
+to texture mapping that rely on accurate camera poses produce poor
+results, leading to the development of the methods contained in this
+paper. Besides localization information and images, environment
+geometry is required as well for texture mapping. In this paper we
+work with low-resolution models obtained by fitting planar surfaces to
+point clouds generated by the backpack system \cite{sanchez2012point}.
 
-Though our texture mapping procedure was designed with the
-aforementioned system in mind, it is applicable to other systems,
-provided the required inputs of planar geometry, images with rough
-extrinsic pose estimates, and either known or estimated intrinsic
-camera calibration matrices. An important benefit of our method is its
-relatively low complexity and runtime, and independence of many steps,
-allowing for live tuning of parameters and easy accomodation of new
-input data given updates in localization or model-generation
-algorithms.
+SOME CONCLUSION TO THE INTRODUCTION GOES HERE Though our texture
+mapping procedure was designed with the aforementioned system in mind,
+it is applicable to other systems, provided the required inputs of
+planar geometry, images with rough extrinsic pose estimates, and
+either known or estimated intrinsic camera calibration matrices. An
+important benefit of our method is its relatively low complexity and
+runtime, and independence of many steps, allowing for efficient tuning
+of parameters and easy accomodation of new input data given updates in
+localization or model-generation algorithms.
 
@@
 towards image alignment, followed by Section
-\ref{sec:imageCompositing}, which describes our two methods of compositing images. Section \ref{sec:resultsAndConclusions} contains results and conclusions.
+\ref{sec:imageCompositing}, which describes our two methods of
+compositing images. Section \ref{sec:resultsAndConclusions} contains
+results and conclusions.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Background}
+\label{sec:background}
+\subsection{Existing Approaches}
+\label{sec:existingApproaches}
+\subsection{
 
@@
   determined by the backpack hardware and localization algorithms
-\cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are quite
-noisy.
+  \cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are
+  quite noisy.
 
-Because our backpack system takes photos at a rate of 5 Hz, thousands
-of images are available for texturing each surface in our model. Our
-goal in designing a texture mapping process is to decide which of
-these images should be used, and where their contents should map onto
-the final texture, in order to minimize any visual discontinuities or
-seams that would suggest that the plane's texture is not composed of a
-single continuous image.
+  Because our backpack system takes photos at a rate of 5 Hz,
+  thousands of images are available for texturing each surface in our
+  model. Our goal in designing a texture mapping process is to decide
+  which of these images should be used, and where their contents
+  should map onto the final texture, in order to minimize any visual
+  discontinuities or seams that would suggest that the plane's texture
+  is not composed of a single continuous image.
 
@@
       \centering
-    \includegraphics[height=2in]{Projection.pdf}
-    \caption{Planes are specified in 3D space by four corners $C_1$ to
-      $C_4$. Images are related to each plane through the camera
+      \includegraphics[height=1.5in]{Projection.pdf}
+      \caption{Planes are specified in 3D space by four corners $C_1$
+        to $C_4$. Images are related to each plane through the camera
         matrics $P_{1..m}$. }
@@
       \centering
-    \includegraphics[height=1.5in]{scoringFunction.jpg}
+      \includegraphics[height=1.125in]{scoringFunction.jpg}
       \caption{We minimize camera angle $\alpha$ and distance $d$ by
-      maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-      \cdot \vec{n}$}
+        maximizing the scoring function $\frac{1}{d} (-1 \cdot
+        \vec{c}) \cdot \vec{n}$}
       \label{fig:scoringFunction}
@@
   \label{sec:tileBasedMapping}
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-a simple texturing approach can be performed by discretizing the
-target plane into small square tiles, in our case 5 pixels across, and
-choosing an image to texture each tile.
+  Ignoring the fact that the camera matrices $P_{1..M}$ are
+  inaccurate, a simple texturing approach can be performed by
+  discretizing the target plane into small square tiles, in our case 5
+  pixels across, and choosing an image to texture each tile.
 
@@
   horizontal or vertical. Since most strong environmental features
-inside buildings are horizontal or vertical, any visible seams in our
-texture intersect them minimally and are less noticeable.
+  inside buildings are horizontal or vertical, any visible seams in
+  our texture thus intersect them minimally and are less noticeable.
 
@@
   gather a list of candidate images that contain all four of its
-corners, which we can quickly check by projecting $t$ into each image
-using the $P_i$ camera matrices. Furthermore, each candidate image
-must have been taken at a time when its camera had a clear
+  corners, which we can quickly check by projecting $t$ into each
+  image using the $P_i$ camera matrices. Furthermore, each candidate
+  image must have been taken at a time when its camera had a clear
   line-of-sight to $t$, which can be calculated using standard
@@
   accurately represented by our digital model. In other words, we wish
-to minimize the angle between the tile's normal vector and the camera
-axis for images selected for texture mapping. These two criteria can
-be met by maximizing the function $\frac{1}{d} (-1 \cdot \vec{c})
-\cdot \vec{n}$ as shown in Figure
+  to minimize the angle between the tile's normal vector and the
+  camera axis for images selected for texture mapping. These two
+  criteria can be met by maximizing the function $\frac{1}{d} (-1
+  \cdot \vec{c}) \cdot \vec{n}$ as shown in Figure
   \ref{fig:scoringFunction}. Specifically, $d$ is the distance between
   the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-the directions of the plane's normal and the camera axis respectively.
+  the directions of the plane's normal and the camera axis
+  respectively.
 
 \begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=3in,
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=3in,
+  \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_naive_shift.jpg}}
 
-  \centering \subfloat[][]{\includegraphics[width=3in,
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_cache_shift.jpg}}
-  \subfloat[][]{\includegraphics[width=3in,
+  \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_shortest_shift.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=3in,
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_cache_shift_details.png}}
+  \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_shortest_shift_details.png}}
+
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3in,
+  \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_shortest_shift_blend.pdf}}
-  \caption{(a) Tile-based texturing. (b) Tile-based texturing after
-    image alignment. (c) Tile-based texturing after image alignment
-    with caching. (d) Shortest path texturing after image
-    alignment). (e) Same as (c) with blending. (f) Same as (d) with
-    blending.}
+
+  \caption{(a): Tile-based texturing. (b): Tile-based texturing after
+    image alignment. (c): Tile-based texturing after image alignment
+    with caching. (d): Shortest path texturing after image
+    alignment). (e,f): Comparison of image artifacts in (c)
+    vs. (d). (g,h): Blending applied to (c) and (d).}
   \label{fig:compareAll}
@@
 image boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images.
-Given our high number of input images, a better image selection procedure could be used, as described in Section \ref{sec:imageCompositing}, but a more significant and reliable improvement can be found through the alignment of our images.
+significant misalignment between images. Given our high number of
+input images, a better image selection procedure could be used, as
+described in Section \ref{sec:imageCompositing}, but a more
+significant and reliable improvement can be found through the
+alignment of our images.
 
@@
 accurate. For example, when matching a long chain of images through
-homographies, a pixel in the $nth$ image is translated into the
-first image's coordinates by multiplying by the $3\times3$ matrices $H_1
-H_2 H_3 ... H_n$. Errors in any of these homography matrices are
+homographies, a pixel in the $nth$ image is translated into the first
+image's coordinates by multiplying by the $3\times3$ matrices $H_1 H_2
+H_3 ... H_n$. Errors in any of these homography matrices are
 propagated to all further images, resulting in drift. Figure
@@
 and produces errors that cause straight lines to appear
-distorted. Many areas with fewer visual features or repeating texture patterns failed
-outright using AutoStitch.
+distorted. Many areas with fewer visual features or repeating texture
+patterns failed outright using AutoStitch.
 
@@
 
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{finalLong.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=6in]{finalLong.jpg}}
 
@@
 poses to maximize matches. This is generally done over 6 degrees of
-freedom \cite{liu2010indoor}. The approach in the cited paper works
-well locally, but over larger areas results again in error
-accumulation and drift, as shown in Figure
-\ref{fig:mosaic3D}(b). Furthermore, it adjusts image locations using
-a long iterative process, which results in high runtime.
+freedom \cite{liu2010indoor}. The approach in [2] works well locally,
+but over larger areas results again in error accumulation and drift,
+as shown in Figure \ref{fig:mosaic3D}(b). Furthermore, it adjusts
+image locations using a long iterative process, which results in high
+runtime.
 
@@
   \subfloat[][]{\includegraphics[height=1.5in]{geometryAlign_planes.png}}
-  \subfloat[][]{\includegraphics[height=1.5in]{geometryAlignment.jpg}}
+  \subfloat[][]{\includegraphics[height=1.5in]{geomAlign}}
   \caption{(a) When texturing the red surface, it makes sense to align
     images to surface boundaries and intersections with other
-    surfaces. (b) Red lines are geometry-based lines, while green
-    lines are detected in the image via Hough transform. Above is the
-    original projection using the input camera poses, and below is the
-    projection after being adjusted for alignment.}
+    surfaces. (b) The darker lines are geometry-based lines, while
+    lighter lines are lines detected in the image via Hough
+    transform. Above is the original projection using the input camera
+    poses, and below is the projection after rotation and translation
+    for alignment.}
   \label{fig:geometryAlignment}
@@
 utilize the remaining feature matches robustly, RANSAC
-\cite{fischler1981random} is again used to estimate the optimal $d^x_{i,j}$
-and $d^y_{i,j}$ distances between two images $i$ and $j$. For this
-application, the RANSAC fitting function finds the average distance
-between selected matches in a pair of images, and the distance
-function for a pair of points is chosen to be the difference between
-those points' SIFT match distance and the average distance computed by
-the fitting function. We use a 10 pixel threshold, so that SIFT
-matches are labeled as outliers if their horizontal or vertical
+\cite{fischler1981random} is again used to estimate the optimal
+$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
+$j$. For this application, the RANSAC fitting function finds the
+average distance between selected matches in a pair of images, and the
+distance function for a pair of points is chosen to be the difference
+between those points' SIFT match distance and the average distance
+computed by the fitting function. We use a 10 pixel threshold, so that
+SIFT matches are labeled as outliers if their horizontal or vertical
 distances are not within 10 pixels of the average distance computed by
@@
 The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(c), where seams are now reduced as
-compared to Figure \ref{fig:compareAll}(b).
+\ref{fig:compareAll}(c), where seams are now reduced as compared to
+Figure \ref{fig:compareAll}(b). However, some discontinuities are
+still present, as visible in the many posters on the wall with breaks
+in their borders.
 
@@
   as blending will be discussed in section \ref{sec:blending}.}. This
-is especially evident when comparing the posters in the images, which
-have clear misalignment over seams in Figure \ref{fig:compareAll}(c),
-but are much more aligned in Figure \ref{fig:compareAll}(d). This
-shortest path approach approach directly reduces the cost of each
-image boundary, while the tile caching method uses a scoring function
-that only approximates this effect. Furthermore, this approach
-guarantees the best selection of images to minimize seams, while the
-sequential tile caching method may select images early on that turn
-out to be poor choices once subsequent tiles have been processed. This
-shortest path approach is also far less intensive in terms of memory
-usage and runtime, both during texture generation and rendering, as it
-does not require discretizing planes or images.
+is especially evident when comparing the posters in the images, as
+seen in Figures \ref{fig:compareAll}(e) and
+\ref{fig:compareAll}(f). This shortest path approach approach directly
+reduces the cost of each image boundary, while the tile caching method
+uses a scoring function that only approximates this
+effect. Furthermore, this approach guarantees the best selection of
+images to minimize seams, while the sequential tile caching method may
+select images early on that turn out to be poor choices once
+subsequent tiles have been processed. This shortest path approach is
+also far less intensive in terms of memory usage and runtime, both
+during texture generation and rendering, as it does not require
+discretizing planes or images.
 
@@
 After performing linear alpha blending across overlapping regions, our
-texture mapping process is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
+texture mapping process is complete. Figures \ref{fig:compareAll}(g)
+and \ref{fig:compareAll}(h) show the blended versions of Figures
 \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
@@
 alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) clearly has the best visual quality among the
+\ref{fig:compareAll}(h) clearly has the best visual quality among the
 textures in Figure \ref{fig:compareAll}.
@@
 approach, and walls textured with the shortest path approach, are
-displayed in Figure \ref{fig:results}. High resolution texture
-comparisons, as well as further examples and interactive walkthroughs are
-available at \footnote{\url{http://www.eecs.berkeley.edu/~pcheng/textureMapping}}.
+displayed in Figure \ref{fig:results}. High resolution colored texture
+comparisons, as well as further examples and interactive walkthroughs
+are available at
+\footnote{\url{http://www.eecs.berkeley.edu/~pcheng/indoormapping}}.
 
@@
 candidate images, followed by another minute to perform both image
-alignment and the shortest path texturing method, with the majority of
-computation time spent calculating SIFT matches within the SiftGPU
-framework. While not quite real-time visualization, the process is
-capable of generating quick updates after changes in various
-parameters or modifications to input data.
+alignment and the shortest path texturing method, though over 75\% of
+that time is spent calculating SIFT matches within the SiftGPU
+framework. While not real-time, the process is capable of generating
+quick updates after changes in various parameters or modifications to
+input data, and if integrated directly into a modeling system, could
+provide live visualization as data is collected.
 

### 2013-01-19 spie/paper.tex
everything except geom stuff draft

@@
   such as virtual reality and environment mapping. Texturing these
-  models allows for photorealistic visualizations of the data
-  collected by such modeling systems. Camera poses obtained by these
-  systems and used for texturing often suffer from inaccuracies
+  models allows for photo-realistic visualizations of the data
+  collected by such modeling systems. We perform these tasks using a
+  backpack-mounted data acquisition system. Camera poses obtained by
+  this system and used for texturing often suffer from inaccuracies
   however, resulting in visible discontinuities when successive images
@@
   stitch images together are often computationally expensive and work
-  independently of pose estimates and geometry information. We propose
-  an efficient method to refine camera poses in 2D using both existing
-  estimates and geometry information, followed by two different
-  methods to composite images together, based on the geometry of
-  surfaces being textured. The effectiveness of our methods is
-  demonstrated on a number of different indoor environments.
+  independently of pose estimates and geometry information. By
+  intelligently selecting images for texturing, we develop
+  an efficient method to adjust camera poses in 2D, followed by two
+  different methods to composite images together, based on the
+  geometry of surfaces being textured. The effectiveness of our
+  method is demonstrated on a number of different indoor
+  environments.
 \end{abstract}
@@
 \label{sec:introduction} % \label{} allows reference to this section
+Three-dimensional modeling of indoor environments has a variety of
+applications in fields such as architecture, conservation, and
+simulation. Applying accurate textures to these models is important to
+add context to digital visualizations, and allows for image-based
+analysis of environments.
 
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time-consuming, and as a
-result, automated 3D site modeling has garnered much interest in
-recent years.
+In this paper, we perform data acquisition with a backpack-mounted
+system carried by an ambulatory human \cite{liu2010indoor}. This
+backpack system contains a series of cameras, laser scanners, and
+inertial measurement units, used to solve the simultaneous
+localization and mapping (SLAM) problem, which produces backpack (and
+therefore camera) poses over time as well as a point cloud
+representing the surrounding environment \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure}. For environment geometry, we
+work with models obtained by fitting low-resolution planar surfaces to
+these point clouds \cite{sanchez2012point}.
 
-The first step in automated 3D modeling is the physical scanning of an
-environment's geometry. An indoor modeling system must recover its own
-poses within an environment while simultaneously reconstructing the 3D
-structure of the environment itself \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure}. This is known as the
-simultaneous localization and mapping (SLAM) problem, and is generally
-solved by taking readings from laser range scanners, cameras, and
-inertial measurement units (IMUs) at multiple locations within the
-environment.
-
-In this paper, we work with data obtained from a backpack-mounted
-system, carried by an ambulatory human. Such a system provides
-advantages over more common wheel-mounted systems in terms of agility
-and portability, but results in higher difficulty and error when
-performing localization \cite{liu2010indoor}. As a result, approaches
-to texture mapping that rely on accurate camera poses produce poor
-results, leading to the development of the methods contained in this
-paper. Besides localization information and images, environment
-geometry is required as well for texture mapping. In this paper we
-work with low-resolution models obtained by fitting planar surfaces to
-point clouds generated by the backpack system \cite{sanchez2012point}.
-
-SOME CONCLUSION TO THE INTRODUCTION GOES HERE Though our texture
-mapping procedure was designed with the aforementioned system in mind,
-it is applicable to other systems, provided the required inputs of
-planar geometry, images with rough extrinsic pose estimates, and
-either known or estimated intrinsic camera calibration matrices. An
-important benefit of our method is its relatively low complexity and
-runtime, and independence of many steps, allowing for efficient tuning
-of parameters and easy accomodation of new input data given updates in
-localization or model-generation algorithms.
+While a human-carried system provides advantages over more common
+wheeled systems in terms of agility and portability, it often leads to
+relatively high localization error even after applying sophisticated
+localization techniques \cite{liu2010indoor}. Furthermore, our model
+geometry usually contains some error as well, and is often tuned to
+ignore low-resolution features, such as small walls, furniture, and
+other minor non-planar features commonly found in indoor
+environments. As a result, methods for texture mapping that rely on
+accurate camera poses and projection surfaces generally produce poor
+results, while more sophisticated methods to accurately align images
+in 3D lead to high runtime on our typically very large datasets. In
+contrast, we present a method, which given a high number of images,
+searches for a subset of them that can be successfully aligned with 2D
+adjustments alone.
 
 The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} explains how input images are projected
-onto our geometry and a simple approach towards texturing. Section
+\ref{sec:simpleTextureMapping} explains how images are projected onto
+our geometry and explains a simple approach towards texturing. Section
 \ref{sec:existingApproaches} covers more sophisticated existing
-approaches, using image matching and stitching, and their performance
-on our datasets. Section \ref{sec:2dAlignment} contains our approach
-towards image alignment, followed by Section
-\ref{sec:imageCompositing}, which describes our two methods of
-compositing images. Section \ref{sec:resultsAndConclusions} contains
-results and conclusions.
+approaches, and their performance on our datasets. Section
+\ref{sec:2dAlignment} contains our efficient approach towards image
+alignment, followed by Section \ref{sec:imageCompositing}, which
+describes our two methods of compositing images. Section
+\ref{sec:resultsAndConclusions} contains results and conclusions.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Background}
-\label{sec:background}
-\subsection{Existing Approaches}
-\label{sec:existingApproaches}
-\subsection{
 
@@
 The geometry of the texture mapping process for a planar surface is
-  shown in Figure \ref{fig:projection}.  As described earlier, we are
-  provided with a set of $M$ images to texture a target plane. Each
-  image has a camera matrix $P_i$ for $i=1..M$, which translates a 3D
-  point in the world coordinate system to a 2D point or pixel in image
-  $i$'s coordinates. A camera matrix $P_i$ is composed of the camera's
-  intrinsic parameters, containing focal length and image center, as
-  well as extrinsic parameters which specify the rotation and
-  translation of the camera's position in 3D world coordinates at the
-  time that image $i$ is taken. These extrinsic parameters are
-  determined by the backpack hardware and localization algorithms
-  \cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are
-  quite noisy.
+shown in Figure \ref{fig:projection}.  We are provided with a set of
+$M$ images to texture a target plane. Each image has a camera matrix
+$P_i$ for $i=1..M$, which translates a 3D point in the world
+coordinate system to a 2D point or pixel in image $i$'s coordinates. A
+camera matrix $P_i$ is composed of the camera's intrinsic parameters,
+containing focal length and image center, as well as extrinsic
+parameters which specify the rotation and translation of the camera's
+position in 3D world coordinates at the time that image $i$ is
+taken. These extrinsic parameters are determined by the backpack
+hardware and localization algorithms \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure} and are substantially noisy.
 
-  Because our backpack system takes photos at a rate of 5 Hz,
-  thousands of images are available for texturing each surface in our
-  model. Our goal in designing a texture mapping process is to decide
-  which of these images should be used, and where their contents
-  should map onto the final texture, in order to minimize any visual
-  discontinuities or seams that would suggest that the plane's texture
-  is not composed of a single continuous image.
+Because our backpack system takes photos at a rate of 5 Hz, thousands
+of images are available for texturing each surface in our model. Our
+goal in designing a texture mapping process is to decide which of
+these images should be used, and where their contents should map onto
+the final texture, in order to minimize any visual discontinuities or
+seams that would suggest that the plane's texture is not composed of a
+single continuous image.
 
@@
     \includegraphics[height=1.5in]{Projection.pdf}
-      \caption{Planes are specified in 3D space by four corners $C_1$
-        to $C_4$. Images are related to each plane through the camera
-        matrics $P_{1..m}$. }
+    \caption{Surfaces to be textured are specified in 3D space by
+      corners $C_i$. Images are related to each plane through the
+      camera matrics $P_{1..m}$. }
     \label{fig:projection}
@@
     \caption{We minimize camera angle $\alpha$ and distance $d$ by
-        maximizing the scoring function $\frac{1}{d} (-1 \cdot
-        \vec{c}) \cdot \vec{n}$}
+      maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
+      \cdot \vec{n}$}
     \label{fig:scoringFunction}
@@
 \label{sec:tileBasedMapping}
-  Ignoring the fact that the camera matrices $P_{1..M}$ are
-  inaccurate, a simple texturing approach can be performed by
-  discretizing the target plane into small square tiles, in our case 5
-  pixels across, and choosing an image to texture each tile.
+Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
+a simple texturing approach can be performed by discretizing the
+target plane into small square tiles, in our case 5 pixels across, and
+choosing an image to texture each tile directly.
 
@@
 horizontal or vertical. Since most strong environmental features
-  inside buildings are horizontal or vertical, any visible seams in
-  our texture thus intersect them minimally and are less noticeable.
+inside buildings are horizontal or vertical, any visible seams in our
+texture will intersect them minimally and be less noticeable.
 
-  In order to select an image for texturing a tile $t$, we must first
-  gather a list of candidate images that contain all four of its
-  corners, which we can quickly check by projecting $t$ into each
-  image using the $P_i$ camera matrices. Furthermore, each candidate
-  image must have been taken at a time when its camera had a clear
-  line-of-sight to $t$, which can be calculated using standard
-  ray-polygon intersection tests between the camera location, $t$, and
-  every other plane \cite{rayintersection}.
+In order to select an image for texturing a tile $t$, we first gather
+a list of candidate images that contain all four of its corners, which
+we can quickly check by projecting $t$ into each image using the $P_i$
+camera matrices. Furthermore, each candidate image must have been
+taken at a time when its camera had a clear line-of-sight to $t$,
+which can be calculated using standard ray-polygon intersection tests
+between the camera location, $t$, and every other plane
+\cite{rayintersection}.
 
@@
 function in order to objectively select the best image for texturing
-  $t$. Since resolution decreases and camera pose errors compound over
-  distance, we wish to minimize the distance between cameras and the
-  surfaces they texture. Additionally, we desire images that are
-  projected perpendicularly onto the plane, maximizing the resolution
-  and amount of useful texture available in their projections, as well
-  as minimizing any parallax effects due to real-world geometry not
-  accurately represented by our digital model. In other words, we wish
-  to minimize the angle between the tile's normal vector and the
-  camera axis for images selected for texture mapping. These two
-  criteria can be met by maximizing the function $\frac{1}{d} (-1
-  \cdot \vec{c}) \cdot \vec{n}$ as shown in Figure
-  \ref{fig:scoringFunction}. Specifically, $d$ is the distance between
-  the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-  the directions of the plane's normal and the camera axis
+$t$. Since resolution decreases and camera pose errors become more
+extreme over distance, we wish to minimize the distance between
+cameras and the surfaces they texture. Additionally, we desire images
+that are projected perpendicularly onto the plane, maximizing the
+resolution and amount of useful texture available in their
+projections, as well as minimizing any parallax effects due to
+real-world geometry not accurately represented by our digital
+model. In other words, we wish to minimize the angle between the
+tile's normal vector and the camera axis for images selected for
+texturing that tile. These two criteria can be met by maximizing the
+function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ as shown in
+Figure \ref{fig:scoringFunction}. Specifically, $d$ is the distance
+between the centers of a camera and a tile, and $\vec{n}$ and
+$\vec{c}$ are the directions of the plane's normal and the camera axis
 respectively.
@@
 
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but results in many
-image boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images. Given our high number of
-input images, a better image selection procedure could be used, as
-described in Section \ref{sec:imageCompositing}, but a more
-significant and reliable improvement can be found through the
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach seleccts
+images with high resolution, and handles parallax effects well, as
+seen with the table and the poster at the lower-right of the
+image. Obviously, there are many image boundaries with abrupt
+discontinuities between tiles, due to significant misalignment between
+images, though most of it appears to be reconcilable using 2d
+transforms. Given our high number of input images, a better image
+selection procedure will further improve results, as described in
+Section \ref{sec:imageCompositing}, but a more significant and
+reliable improvement can be found through first improving the
 alignment of our images.
@@
 \section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-Stitching together multiple images to produce a larger image is a
-commonly performed task, with many successful approaches over the past
-few decades. Parts of images are first matched to eachother, through
-direct pixel comparisons, or more commonly through feature detection
-and matching. Images are then adjusted to maximize matches, either by
-calculating homographies between pairs of images, or by modifying
-camera poses in 1 to 6 degrees of freedom.
+Stitching together multiple images to produce a larger, seamless image
+is a commonly performed task, with many successful approaches over the
+past years. Generally, parts of images are matched to each other,
+usually through direct comparisons or feature detection and
+matching. Images are then transformed to maximize matches, often by
+calculating homographies between pairs of images, or by iteratively
+adjusting camera poses in 1 to 6 degrees of freedom.
 
-Feature detection and matching works best when multiple unique visual
-references exist in the environment and are present within multiple
-images. In contrast, our indoor environments have a high prevalence of
-bare surfaces, as well as repeating textures that cause difficulty in
-disambiguating features. This lack of reliable reference points often
-results in errors when matching images together.
+Feature matching has a number of advantages over direct matching that
+make it more suitable for our often non-planar data, and rotational
+differences, as covered in X. Feature matching however, works best
+when multiple unique visual references exist in the environment that
+can be detected in multiple images. In contrast, our indoor
+environments have a high prevalence of bare surfaces, as well as
+repeating textures, such as similar windows, doors, and wall-mounted
+decorations, that cause difficulty in disambiguating features. This
+lack of reliable reference points often results in errors when
+matching images together.
 
 Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not
-accurate. For example, when matching a long chain of images through
-homographies, a pixel in the $nth$ image is translated into the first
-image's coordinates by multiplying by the $3\times3$ matrices $H_1 H_2
-H_3 ... H_n$. Errors in any of these homography matrices are
-propagated to all further images, resulting in drift. Figure
-\ref{fig:mosaic3D}(a) shows the output of the AutoStitch software
-package, which performs homography-based image mosaicing
-\cite{autostitch}. Though AutoStitch performs well in areas with dense
-features, it has difficulty with even short segments of bare walls,
-and produces errors that cause straight lines to appear
-distorted. Many areas with fewer visual features or repeating texture
-patterns failed outright using AutoStitch.
+leads to error accumulation when image correspondences are not exact
+and are compounded together. For example, when matching a long chain
+of images through homographies, a pixel in the $nth$ image is
+translated into the first image's coordinates by multiplying by the
+$3\times3$ matrices $H_1 H_2 H_3 ... H_n$. Errors in any of these
+homography matrices are propagated to all further images, resulting in
+drift.
 
@@
 
-Image projections can also be aligned by iteratively adjusting camera
-poses to maximize matches. This is generally done over 6 degrees of
-freedom \cite{liu2010indoor}. The approach in [2] works well locally,
-but over larger areas results again in error accumulation and drift,
-as shown in Figure \ref{fig:mosaic3D}(b). Furthermore, it adjusts
-image locations using a long iterative process, which results in high
-runtime.
+Past work with our data acquisition backpack integrated image
+stitching with an iterative localization algorithm, and performed
+homography-based camera pose refinement. When run on long chains of
+images, especially where features are sparse, it produces distorted
+textures, as seen in Figure X, due to the problems described
+above. This approach is also WHATEVER NONLINEAR, and its iterative
+camera adjustment process over our large datasets is not guaranteed to
+SOMETHING, and leads to prohibitively long computation time.
+
+The AutoStitch software package performs homography-based alignment as
+well, with additional provisions that attempt to reduce drift (cite
+X,X). Though AutoStitch also performs well in areas with dense
+features, it can not handle areas without features, and has trouble
+aligning wall sections with even short segments of bare texture. The
+example in Figure X was generated after manual tuning, and areas with
+fewer visual features or repeating texture patterns simply failed
+outright with AutoStitch.
 
@@
 \label{sec:2dAlignment}
+
 In this section, we describe our method of efficient and robust image
-alignment. Our approach consists of three main parts. First, all
+alignment. Though state-of-the-art techniques towards image stitching
+work in 3D, we sacrifice THAT WORD for efficiency, and elect to
+perform image alignments entirely in 2D. Besides the reduced
+complexity, we have found 2D alignment to work well for two main
+reasons. First, because we have such a large number of images to
+choose from, we have found that the compositing approache in Section X
+is able to select a subset of images that align well, given only 2D
+alignments. Furthermore, the nature of our input data is such that
+localization error chiefly occurs in two dimensions, in the same plane
+as the surface being projected onto. Recall that our data acquisition
+system is backpack-mounted, with cameras facing to the sides of the
+operator. The operator makes efforts to walk parallel to walls, and
+the localization and model-generation algorithms that provide our
+input conform the operator's path to be straight and parallel to
+detected surfaces \cite{kua2012loopclosure, sanchez2012point}. Since
+the operator walks in as upright a position as possible, errors in
+roll, yaw, and the operator's distance from parallel surfaces are
+minimal. Thus, our highest errors stem from uncertainty in the
+operator's pitch, equivalent to rotation around the camera axes, as
+well as location along surfaces. These equate to 2D rotation and
+translation in a surface's plane.
+
+Our alignment procedure consists of three main parts. First, all
 images are projected onto the surface and lines within these
@@
 matches.
-
-All of our following calculations and alignments are performed in 2D,
-partly for efficiency, partly because we have a large number of images
-to choose from, and partly because the nature of our input data is
-such that localization error chiefly occurs in two dimensions, in the
-same plane as the surface being projected onto. Recall that our data
-acquisition system is backpack-mounted, with cameras facing to the
-sides of the operator. The operator makes efforts to walk parallel to
-walls, and the localization and model-generation algorithms that
-provide our input conform the operator's path to be straight and
-parallel to detected surfaces \cite{kua2012loopclosure,
-  sanchez2012point}. Since the operator walks in as upright a position
-as possible, errors in roll, yaw, and the operator's distance from
-parallel surfaces are minimal. Thus, our highest errors stem from
-uncertainty in the operator's pitch, equivalent to rotation around the
-camera axes, as well as location along surfaces. These equate to 2D
-rotation and translation in a surface's plane.
 

### 2013-01-19 spie/paper.tex
geom stuff amlost

@@
 \ref{sec:simpleTextureMapping} explains how images are projected onto
-our geometry and explains a simple approach towards texturing. Section
-\ref{sec:existingApproaches} covers more sophisticated existing
-approaches, and their performance on our datasets. Section
-\ref{sec:2dAlignment} contains our efficient approach towards image
-alignment, followed by Section \ref{sec:imageCompositing}, which
-describes our two methods of compositing images. Section
-\ref{sec:resultsAndConclusions} contains results and conclusions.
+our geometry and explains a simple approach towards selecting images
+for texturing. Section \ref{sec:existingApproaches} covers
+sophisticated existing approaches to image stitching, and their
+performance on our datasets. Section \ref{sec:2dAlignment} contains
+our efficient approach towards 2D image alignment, followed by Section
+\ref{sec:imageCompositing}, which describes our two methods of
+compositing images. Section \ref{sec:resultsAndConclusions} contains
+results and conclusions.
 
@@
 a simple texturing approach can be performed by discretizing the
-target plane into small square tiles, in our case 5 pixels across, and
-choosing an image to texture each tile directly.
+target plane into small square tiles, and choosing an image to texture
+each tile directly.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{autostitchResult.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{graphApproach.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{graphApproach.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{autostitchResult.jpg}}
 
@@
 images, especially where features are sparse, it produces distorted
-textures, as seen in Figure X, due to the problems described
-above. This approach is also WHATEVER NONLINEAR, and its iterative
-camera adjustment process over our large datasets is not guaranteed to
-SOMETHING, and leads to prohibitively long computation time.
+textures, as seen in Figure \ref{fig:mosaic3D}(a), due to the problems
+described above. This approach is also not closed-form, and its
+iterative camera adjustment process over our large datasets leads to
+prohibitively long computation time.
 
 The AutoStitch software package performs homography-based alignment as
-well, with additional provisions that attempt to reduce drift (cite
-X,X). Though AutoStitch also performs well in areas with dense
-features, it can not handle areas without features, and has trouble
-aligning wall sections with even short segments of bare texture. The
-example in Figure X was generated after manual tuning, and areas with
-fewer visual features or repeating texture patterns simply failed
-outright with AutoStitch.
+well, with additional provisions that attempt to reduce drift
+\cite{panorama2d, autostitch}. Though AutoStitch also performs well in
+areas with dense features, it can not handle areas without features,
+and has trouble aligning wall sections with even short segments of
+bare texture. The example in Figure \ref{fig:mosaic3D}(b) was
+generated after manual tuning, and areas with fewer visual features or
+repeating texture patterns simply failed outright with AutoStitch.
 
@@
 alignment. Though state-of-the-art techniques towards image stitching
-work in 3D, we sacrifice THAT WORD for efficiency, and elect to
-perform image alignments entirely in 2D. Besides the reduced
-complexity, we have found 2D alignment to work well for two main
-reasons. First, because we have such a large number of images to
-choose from, we have found that the compositing approache in Section X
-is able to select a subset of images that align well, given only 2D
+work in 3D, we elect to perform image alignments entirely in
+2D. Besides the benifits of reduced complexity, we have found 2D
+alignment to work well for two main reasons. First, because we have
+such a large number of images to choose from, we have found that the
+compositing approaches in Section \ref{sec:imageCompositing} is able
+to select a subset of images that align well, given only 2D
 alignments. Furthermore, the nature of our input data is such that
@@
 
-Our alignment procedure consists of three main parts. First, all
+Our 2D alignment procedure consists of three main parts. First, all
 images are projected onto the surface and lines within these
-projections are detected. These lines are then matched up with
-geometry-based lines comprising the surface's boundary and
+projections are detected. These lines are then rotated and shifted to
+match geometry-based lines comprising the surface's boundary and
 intersection with other surfaces. Second, occlusion checks are
@@
 images in 2D such that dominant lines are made to be horizontal or
-vertical. This can be further extrapolated by orienting lines with a
-wall's boundaries, for example in areas with a slanted roof.
+vertical. This can be further generalized by instead orienting lines
+to be parallel with a surface's boundaries, which makes it applicable
+to non-rectangular surfaces, such as ceilings, floors, or slanted
+walls.
 
@@
     images to surface boundaries and intersections with other
-    surfaces. (b) The darker lines are geometry-based lines, while
-    lighter lines are lines detected in the image via Hough
-    transform. Above is the original projection using the input camera
-    poses, and below is the projection after rotation and translation
-    for alignment.}
+    surfaces. (b) In this example, we project two images at once for
+    the sake of demonstration, where the red lines are geometry-based
+    lines where surfaces intersect, and the green ines are lines
+    detected in the image via Hough transform. Above are the original
+    projections using input camera poses, and below are the
+    projections after rotation and translation for alignment.}
   \label{fig:geometryAlignment}
@@
 
-At this point in time, image occlusions have not been accounted
-for. As a result, some image projections contain texture that should
-project to an adjacent surface, generally with a linear boundary where
-the two surfaces meet. If this linear boundary is detected by Hough
-transform, the image is rotated and shifted in 2D such that the visual
-boundary between two surfaces in an image projection matches the
-physical boundary in our digital model. An example of such an
-adjustment is in Figure \ref{fig:geometryAlignment}
+Furthermore, at this point in time, image occlusions have not been
+accounted for. As a result, some image projections contain texture
+that should project to an adjacent surface, sometimes with a visible
+linear boundary where the two surfaces meet. If this linear boundary
+is detected by Hough transform, the image is rotated and shifted in 2D
+such that the visual boundary between two surfaces in an image
+projection matches the physical boundary in our digital model. An
+example of such an adjustment is in Figure \ref{fig:geometryAlignment}
 
@@
 optimal rotation and translation to match up two groups of line
-segments, while accounting for outliers. First, a rotation angle is
-computed by gathering all pairs of image line segments and geometry
-line segments with less than 20 degrees between them. We then run the
-RANSAC algorithm by sampling 4 of these angles at a time, and using
-their average as the fitting function. Angles over 2 degrees from this
-average are considered outliers. Once this 2d rotation angle is
-determined, it is applied to the image, and projections are
-re-calculated and image-based lines are re-detected. Now, all pairs of
-image line segments and geometry line segments with less than 0.2
-degree difference and less than 250 mm distance at their furthest
-points are gathered. RANSAC is then similarly employed to calculate
-optimal horizontal and vertical translations independently, by
-sampling 4 pairs at a time and considering an outlier threshold of 10
-mm. If a translation is applied, we indicate that the image was
-aligned to geometry in one or both dimensions, which will reduce
-further shifting in Section \ref{sec:robustSIFTFeatureMatching}.
+segments, while accounting for outliers. The parameters we specify
+were chosen after some tuning on our datasets, and are likely to vary
+based on input data. First, a rotation angle is computed by gathering
+all pairs of image line segments and geometry line segments with less
+than 20 degrees between them. We then run the RANSAC algorithm by
+sampling 4 of these angles at a time, and using their average as the
+fitting function. Angles over 1 degree from this average are
+considered outliers. Once a 2D rotation angle is determined, it is
+applied to the image, and image line segments with length below a
+certain threshold are discarded. Now, all pairs of image line segments
+and geometry line segments with less than 0.1 degree difference in
+orientation and less than 250 mm distance at their furthest points are
+gathered. RANSAC is then similarly employed to calculate a shift that maximizes matches among these pairs of lines.
+
+In an ideal case, homography might be applied here, but poop
+In our datasets we have success sides for walls, floors and ceilings we have found often difficulty matching, so we often align only in X, and save this info later.
+For floors and ceilings, we have more success, and since images smaller upwards, only one match usually, and so we save the slope for later.
+
+optimal
+horizontal and vertical translations independently, by sampling 4
+pairs at a time and considering an outlier threshold of 10 mm. If a
+translation is applied, we indicate that the image was aligned to
+geometry in one or both dimensions, which will reduce further shifting
+in Section \ref{sec:robustSIFTFeatureMatching}.
 

### 2013-01-20 spie/_region_.tex
draft

@@
 
-\message{ !name(paper.tex) !offset(357) }
+\message{ !name(paper.tex) !offset(374) }
 \subsection{2D Feature Alignment}
@@
 utilize the remaining feature matches robustly, RANSAC
-\cite{fischler1981random} is again used to estimate the optimal $d^x_{i,j}$
-and $d^y_{i,j}$ distances between two images $i$ and $j$. For this
-application, the RANSAC fitting function finds the average distance
-between selected matches in a pair of images, and the distance
-function for a pair of points is chosen to be the difference between
-those points' SIFT match distance and the average distance computed by
-the fitting function. We use a 10 pixel threshold, so that SIFT
-matches are labeled as outliers if their horizontal or vertical
-distances are not within 10 pixels of the average distance computed by
-the fitting function.
+\cite{fischler1981random} is again used to estimate the optimal
+$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
+$j$. We use a 10 pixel threshold for RANSAC, so that SIFT matches are
+labeled as outliers if their distance is not within 10 pixels of the
+sampled average distance.
 
-We now use the RANSAC-calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
-between each pair of images to refine their positions using weighted
-linear least squares. There are a total of $M^{2}$ possible pairs of
-images, though we only generate distances between images with SIFT
-matches. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
+We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
+of images to refine their positions using weighted linear least
+squares. The variables we wish to solve for are the $x$ and $y$
+positions of our images, while our equations are the SIFT-based
+distances between pairs of images, images fixed to geometry with 0 or
+1 degrees of freedom, and the original camera poses. Ignoring
+weighting for now, an example setup for solving
+$\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $
+with 3 images is shown below.
+
+\[
+A =
+\begin{pmatrix}
+  -1 & 1 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & -1 & 1 & 0\\
+  0 & -1 & 1 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & -1 & 1\\
+  1 & 0 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 1 & 0 & 0\\
+  0 & -m & 0 & 0 & 1 & 0\\
+\end{pmatrix}
+\]
 
@@
 \begin{pmatrix}
-  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
+  x_1, & x_2, & x_3, & y_1, & y_2, & y_3
 \end{pmatrix}
 \]
-
-The $N \times M$ matrix $A$ is constructed with one row for each pair
-of images with measured distances produced by the SIFT matching
-stage. A row in the matrix has a $-1$ and $1$ in the columns
-corresponding to the two images in the pair. For example, the matrix
-below indicates a SIFT-based distance between images 1 and 2, images 1
-and 3, images 2 and 3, etc.
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & \cdots & 0 & 0\\
-  -1 & 0 & 1 & \cdots & 0 & 0\\
-  0 & -1 & 1 & \cdots & 0 & 0\\
-  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
-  0 & 0 & 0 & \cdots & 1 & 0 \\
-  0 & 0 & 0 & \cdots & -1 & 1 \\
-  1 & 0 & 0 & \cdots & 0 & 0\\
-\end{pmatrix}
-\]
-If only relative distances between images are included, the absolute
-location of the images can not be calculated, and the matrix is rank
-deficient. From Section \ref{sec:geometryAlignment}, a number of
-images are anchored to geometry points, in one or both dimensions, and
-thus their locations can be used to fix the rest in place. In case no
-anchor images exist, we simply arbitrarily pick an image, as we have
-no other reference points to work with. In the above matrix, the first
-image is set to be such an anchor, simply by placing a $1$ in its
-column.
-
-The $N$-dimensional observation vector $\vec{\gamma}$ is constructed
-using the SIFT-based distances generated in the RANSAC matching
-stage. Elements in the observation vector corresponding to anchor
-images are simply their locations as determined by the original noisy
-localization. Thus a $\vec{\gamma}$ corresponding to the above matrix
-can be written as:
 
@@
 \begin{pmatrix}
-  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
+  dx_{1,2}, &dy_{1,2}, &dx_{2,3}, &dy_{2,3}, &t1_x, &t1_y, & -mx_2 +
+  ty_2
 \end{pmatrix}
@@
 
-The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
-\vec{\gamma}||_2^2$ results in a set of image locations on the plane
-that best honors all the SIFT-based distance measurements between
-images. This solution however does not make use of our noisy camera
-poses, and will fail when no SIFT matches are found between one
-segment of the plane and another. To account for this, we add rows to
-the $A$ matrix and observations to the $\vec{\gamma}$ vector
-corresponding to the original noisy distances. We then add weighting
-to our least squares problem where the SIFT distances and anchor
-values are given a high weight e.g. 1, while the noisy distances are
-given a smaller weight e.g. 0.01.
+In this scenario, a SIFT-based distance of $dx_{1,2}$, $dy_{1,2}$ was
+calculated between images 1 and 2. This corresponds to the first and
+second of $A$, while the third and fourth row of $A$ represent the
+same for images 2 and 3. Rows 5 and 6 of $A$ correspond to a fixed
+location of $tx_1$, $ty_1$ for image 1, while Row 7 corresponds to a
+constraint to a line of slope $m$, with current location $tx_2$,
+$ty_2$, both results of the geometry alignment procedure in Section
+\ref{sec:geometryAlignment}. If we do not have enough SIFT matches, or
+lack images matched to geometry, our matrix becomes rank-deficient and
+our problem cannot be solved. As a result, we add rows for each image
+corresponding to the original noisy image locations, and downweight
+them heavily, e.g. with a weight of 0.01 versus 1.
 
-After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and match each other
+Because our problem is linear, it is quickly solved, and after
+applying the resulting shifts, our images overlap and match each other
 with far greater accuracy. Applying the simple mapping scheme in
@@
 
-\message{ !name(paper.tex) !offset(650) }
+\message{ !name(paper.tex) !offset(667) }
 

### 2013-01-20 spie/paper.tex
draft

@@
 add context to digital visualizations, and allows for image-based
-analysis of environments.
-
-In this paper, we perform data acquisition with a backpack-mounted
-system carried by an ambulatory human \cite{liu2010indoor}. This
-backpack system contains a series of cameras, laser scanners, and
-inertial measurement units, used to solve the simultaneous
-localization and mapping (SLAM) problem, which produces backpack (and
-therefore camera) poses over time as well as a point cloud
-representing the surrounding environment \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure}. For environment geometry, we
-work with models obtained by fitting low-resolution planar surfaces to
-these point clouds \cite{sanchez2012point}.
+analysis of environments. In this paper, we perform data acquisition
+with a backpack-mounted system carried by an ambulatory human
+\cite{liu2010indoor}. This backpack system contains a series of
+cameras, laser scanners, and inertial measurement units, used to solve
+the simultaneous localization and mapping (SLAM) problem, which
+produces backpack (and therefore camera) poses over time as well as a
+point cloud representing the surrounding environment
+\cite{chen2010indoor, liu2010indoor, kua2012loopclosure}. For
+environment geometry, we work with models obtained by fitting
+low-resolution planar surfaces to these point clouds
+\cite{sanchez2012point}.
 
@@
 our geometry and explains a simple approach towards selecting images
-for texturing. Section \ref{sec:existingApproaches} covers
-sophisticated existing approaches to image stitching, and their
-performance on our datasets. Section \ref{sec:2dAlignment} contains
-our efficient approach towards 2D image alignment, followed by Section
+for texturing. Section \ref{sec:existingApproaches} covers existing
+approaches to image stitching, and their performance on our
+datasets. Section \ref{sec:2dAlignment} contains our approach towards
+efficient 2D image alignment, followed by Section
 \ref{sec:imageCompositing}, which describes our two methods of
@@
 shown in Figure \ref{fig:projection}.  We are provided with a set of
-$M$ images to texture a target plane. Each image has a camera matrix
-$P_i$ for $i=1..M$, which translates a 3D point in the world
+$M$ images to texture a target plane, where each image has a camera
+matrix $P_i$ for $i=1..M$, which translates a 3D point in the world
 coordinate system to a 2D point or pixel in image $i$'s coordinates. A
@@
 
-Because our backpack system takes photos at a rate of 5 Hz, thousands
+Because our backpack system takes photos at a rate of 5 Hz, hundreds
 of images are available for texturing each surface in our model. Our
@@
     \caption{Surfaces to be textured are specified in 3D space by
-      corners $C_i$. Images are related to each plane through the
+      corners $C_i$. Images are related to each surface through the
       camera matrics $P_{1..m}$. }
@@
 \section{Existing Approaches to Image Alignment}
+\label{sec:existingApproaches}
 Stitching together multiple images to produce a larger, seamless image
@@
 make it more suitable for our often non-planar data, and rotational
-differences, as covered in X. Feature matching however, works best
+differences \cite{szeliski2006image}. Feature matching however, works best
 when multiple unique visual references exist in the environment that
@@
 alignment to work well for two main reasons. First, because we have
-such a large number of images to choose from, we have found that the
-compositing approaches in Section \ref{sec:imageCompositing} is able
-to select a subset of images that align well, given only 2D
-alignments. Furthermore, the nature of our input data is such that
-localization error chiefly occurs in two dimensions, in the same plane
-as the surface being projected onto. Recall that our data acquisition
-system is backpack-mounted, with cameras facing to the sides of the
-operator. The operator makes efforts to walk parallel to walls, and
-the localization and model-generation algorithms that provide our
-input conform the operator's path to be straight and parallel to
-detected surfaces \cite{kua2012loopclosure, sanchez2012point}. Since
-the operator walks in as upright a position as possible, errors in
-roll, yaw, and the operator's distance from parallel surfaces are
-minimal. Thus, our highest errors stem from uncertainty in the
-operator's pitch, equivalent to rotation around the camera axes, as
-well as location along surfaces. These equate to 2D rotation and
-translation in a surface's plane.
+such a large number of images to choose from, the compositing
+approaches in Section \ref{sec:imageCompositing} are able to select a
+subset of images that align well, given only 2D alignments. Second,
+the nature of our input data is such that localization error chiefly
+occurs in two dimensions, in the same plane as the surface being
+projected onto. Our data acquisition system contains cameras facing to
+the sides of the operator. The operator makes efforts to walk parallel
+to walls, and the localization and model-generation algorithms that
+provide our input conform the operator's path to be straight and
+parallel to detected surfaces \cite{kua2012loopclosure,
+  sanchez2012point}. Since the operator walks in as upright a position
+as possible, errors in roll, yaw, and the operator's distance from
+parallel surfaces are minimal. Thus, our highest errors stem from
+uncertainty in the operator's pitch, equivalent to rotation around the
+camera axes, as well as location along surfaces. These equate to 2D
+rotation and translation in a surface's plane.
 
@@
 parallel. Third, we detect SIFT feature matches between pairs of
-images and solve a linear least squares problem in 2D to maximize
-matches.
+images and solve a weighted linear least squares problem in 2D to
+maximize matches.
 
@@
 described in Section \ref{sec:simpleTextureMapping}, we detect line
-segments in the image projections using Hough transforms. Experience
-and intuition show that walls in indoor environments often contain
-linear features that are either horizontal or vertical, corresponding
-to doors, windows, posters, etc. Thus, when texturing walls, we rotate
-images in 2D such that dominant lines are made to be horizontal or
-vertical. This can be further generalized by instead orienting lines
-to be parallel with a surface's boundaries, which makes it applicable
-to non-rectangular surfaces, such as ceilings, floors, or slanted
-walls.
+segments in the image projections using Hough transforms, as shown in
+Figure \ref{fig:geometryAlignment}(a). Experience and intuition show
+that walls in indoor environments often contain linear features that
+are either horizontal or vertical, corresponding to doors, windows,
+posters, etc. Thus, when texturing walls, we rotate images in 2D such
+that dominant lines are made to be horizontal or vertical. This can be
+further generalized by instead orienting lines to be parallel with a
+surface's boundaries, which makes it applicable to non-rectangular
+surfaces, such as ceilings, floors, or slanted walls.
 
@@
 linear boundary where the two surfaces meet. If this linear boundary
-is detected by Hough transform, the image is rotated and shifted in 2D
-such that the visual boundary between two surfaces in an image
+can be detected by Hough transform, the image is rotated and shifted
+in 2D such that the visual boundary between two surfaces in an image
 projection matches the physical boundary in our digital model. An
-example of such an adjustment is in Figure \ref{fig:geometryAlignment}
+example of such an adjustment is in Figure
+\ref{fig:geometryAlignment}(b) and \ref{fig:geometryAlignment}(c).
 
-To perform the rotation and alignment, we use the RANSAC
-\cite{fischler1981random} framework. RANSAC allows us to determine an
-optimal rotation and translation to match up two groups of line
-segments, while accounting for outliers. The parameters we specify
-were chosen after some tuning on our datasets, and are likely to vary
-based on input data. First, a rotation angle is computed by gathering
-all pairs of image line segments and geometry line segments with less
-than 20 degrees between them. We then run the RANSAC algorithm by
-sampling 4 of these angles at a time, and using their average as the
-fitting function. Angles over 1 degree from this average are
-considered outliers. Once a 2D rotation angle is determined, it is
-applied to the image, and image line segments with length below a
-certain threshold are discarded. Now, all pairs of image line segments
-and geometry line segments with less than 0.1 degree difference in
-orientation and less than 250 mm distance at their furthest points are
-gathered. RANSAC is then similarly employed to calculate a shift that maximizes matches among these pairs of lines.
-
-In an ideal case, homography might be applied here, but poop
-In our datasets we have success sides for walls, floors and ceilings we have found often difficulty matching, so we often align only in X, and save this info later.
-For floors and ceilings, we have more success, and since images smaller upwards, only one match usually, and so we save the slope for later.
-
-optimal
-horizontal and vertical translations independently, by sampling 4
-pairs at a time and considering an outlier threshold of 10 mm. If a
-translation is applied, we indicate that the image was aligned to
-geometry in one or both dimensions, which will reduce further shifting
-in Section \ref{sec:robustSIFTFeatureMatching}.
+To perform rotation, we use a RANSAC \cite{fischler1981random}
+framework to determine an optimal rotation angle between lines in our
+image and lines in our geometry. RANSAC allows us to ignore erroneous
+lines in our image, such as the slanted lines corresponding to the
+ladder in Figure \ref{fig:geometryAlignment}(a). Once this rotation is
+discovered and applied, we gather all pairs of image line segments and
+geometry line segments with less than $0.1^\circ$ difference in
+orientation and less than 250 mm distance at their furthest points. If
+2 or more pairs exist, we select the 2 that contain the longest
+noncollinear image-based line segments, and perform the corresponding
+fixed translation to match them. If we only have 1 pair, we perform
+the minimal shift to match the lines of that pair, and make note of
+their orientation, for usage in Section
+\ref{robustSIFTFeatureMatching}.
 
@@
 corners of a rectangular region are occluded, texture is
-removed. Where no corners are occluded, nothing occurs. Where there is
-a mixture of both, the rectangular region is subdivided into four, and
-the same process is performed on each. By performing Section
+removed. Where no corners are occluded, the recursion stops. Where
+there is a mixture of both, the rectangular region is subdivided into
+four, and the same process is performed on each. By performing Section
 \ref{sec:geometryAlignment}'s alignment procedure before occlusion,
@@
 $d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
-$j$. For this application, the RANSAC fitting function finds the
-average distance between selected matches in a pair of images, and the
-distance function for a pair of points is chosen to be the difference
-between those points' SIFT match distance and the average distance
-computed by the fitting function. We use a 10 pixel threshold, so that
-SIFT matches are labeled as outliers if their horizontal or vertical
-distances are not within 10 pixels of the average distance computed by
-the fitting function.
+$j$. We use a 10 pixel threshold for RANSAC, so that SIFT matches are
+labeled as outliers if their distance is not within 10 pixels of the
+sampled average distance.
 
-We now use the RANSAC-calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
-between each pair of images to refine their positions using weighted
-linear least squares. There are a total of $M^{2}$ possible pairs of
-images, though we only generate distances between images with SIFT
-matches. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
+We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
+of images to refine their positions using weighted linear least
+squares. The variables we wish to solve for are the $x$ and $y$
+positions of our images, while our equations are the SIFT-based
+distances between pairs of images, images fixed to geometry with 0 or
+1 degrees of freedom, and the original camera poses. Ignoring
+weighting for now, an example setup for solving
+$\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $
+with 3 images is shown below.
+
+\[
+A =
+\begin{pmatrix}
+  -1 & 1 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & -1 & 1 & 0\\
+  0 & -1 & 1 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & -1 & 1\\
+  1 & 0 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 1 & 0 & 0\\
+  0 & -m & 0 & 0 & 1 & 0\\
+\end{pmatrix}
+\]
 
@@
 
-The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
-\vec{\gamma}||_2^2$ results in a set of image locations on the plane
-that best honors all the SIFT-based distance measurements between
-images. This solution however does not make use of our noisy camera
-poses, and will fail when no SIFT matches are found between one
-segment of the plane and another. To account for this, we add rows to
-the $A$ matrix and observations to the $\vec{\gamma}$ vector
-corresponding to the original noisy distances. We then add weighting
-to our least squares problem where the SIFT distances and anchor
-values are given a high weight e.g. 1, while the noisy distances are
-given a smaller weight e.g. 0.01.
+In this scenario, a SIFT-based distance of $dx_{1,2}$, $dy_{1,2}$ was
+calculated between images 1 and 2. This corresponds to the first and
+second of $A$, while the third and fourth row of $A$ represent the
+same for images 2 and 3. Rows 5 and 6 of $A$ correspond to a fixed
+location of $tx_1$, $ty_1$ for image 1, while Row 7 corresponds to a
+constraint to a line of slope $m$, with current location $tx_2$,
+$ty_2$, both results of the geometry alignment procedure in Section
+\ref{sec:geometryAlignment}. If we do not have enough SIFT matches, or
+lack images matched to geometry, our matrix becomes rank-deficient and
+our problem cannot be solved. As a result, we add rows for each image
+corresponding to the original noisy image locations, and downweight
+them heavily, e.g. with a weight of 0.01 versus 1.
 
-After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and match each other
+Because our problem is linear, it is easily and quickly solved, and after
+applying the resulting shifts, our images overlap and match each other
 with far greater accuracy. Applying the simple mapping scheme in
@@
   as blending will be discussed in section \ref{sec:blending}.}. This
-is especially evident when comparing the posters in the images, as
-seen in Figures \ref{fig:compareAll}(e) and
-\ref{fig:compareAll}(f). This shortest path approach approach directly
-reduces the cost of each image boundary, while the tile caching method
-uses a scoring function that only approximates this
-effect. Furthermore, this approach guarantees the best selection of
-images to minimize seams, while the sequential tile caching method may
-select images early on that turn out to be poor choices once
-subsequent tiles have been processed. This shortest path approach is
-also far less intensive in terms of memory usage and runtime, both
-during texture generation and rendering, as it does not require
-discretizing planes or images.
+is especially evident when comparing the posters in the images. This
+shortest path approach approach directly reduces the cost of each
+image boundary, while the tile caching method uses a scoring function
+that only approximates this effect. Furthermore, this approach
+guarantees the best selection of images to minimize seams, while the
+sequential tile caching method may select images early on that turn
+out to be poor choices once subsequent tiles have been processed. This
+shortest path approach is also far less intensive in terms of memory
+usage and runtime, both during texture generation and rendering, as it
+does not require discretizing planes or images.
 
@@
 After performing linear alpha blending across overlapping regions, our
-texture mapping process is complete. Figures \ref{fig:compareAll}(g)
-and \ref{fig:compareAll}(h) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the shortest path approach exhibits much better
-alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(h) clearly has the best visual quality among the
-textures in Figure \ref{fig:compareAll}.
+texture mapping process is complete. Figures \ref{fig:compareAll}(e)
+and \ref{fig:compareAll}(f) show the blended versions of Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. The
+remaining images in Figure \ref{fig:compareAll} highlight differences
+between the two methods, showing that Figure \ref{fig:compareAll}(f)
+clearly has the best visual quality and the best texturing approach
+among the textures in Figure \ref{fig:compareAll}.
 
@@
 input data, and if integrated directly into a modeling system, could
-provide live visualization as data is collected.
+provide live visualization as data is collected. Our full models
+consist of our input model file, textures that we generate, and a
+mapping of image points to model vertices. The models shown in Figure
+\ref{fig:results} are roughly 20 MB in size, and are visualized using
+the OpenSceneGraph toolkit \cite{openscenegraph}, which allows for export to many common
+model formats, as well as efficient visualization, even in web
+browsers or mobile devices.
 
@@
 images are available. Both of these approaches are highly modular, and
-easily tunable for different environments and acquisition systems.
+easily tunable for similar systems across multiple environments.
 

### 2013-01-20 spie/paper.tex
just geom figure now

@@
 
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach seleccts
-images with high resolution, and handles parallax effects well, as
-seen with the table and the poster at the lower-right of the
-image. Obviously, there are many image boundaries with abrupt
-discontinuities between tiles, due to significant misalignment between
-images, though most of it appears to be reconcilable using 2d
-transforms. Given our high number of input images, a better image
-selection procedure will further improve results, as described in
-Section \ref{sec:imageCompositing}, but a more significant and
-reliable improvement can be found through first improving the
-alignment of our images.
+As Figure \ref{fig:compareAll}(a) demonstrates, there are many image
+boundaries with abrupt discontinuities between tiles, due to
+significant misalignment between images, though most of it appears to
+be reconcilable using 2D transforms. Given our high number of input
+images, a better image selection procedure will further improve
+results, as described in Section \ref{sec:imageCompositing}, but a
+more significant and reliable improvement can be found through first
+improving the alignment of our images.
 
@@
 make it more suitable for our often non-planar data, and rotational
-differences \cite{szeliski2006image}. Feature matching however, works best
-when multiple unique visual references exist in the environment that
-can be detected in multiple images. In contrast, our indoor
+differences \cite{szeliski2006image}. Feature matching however, works
+best when multiple unique visual references exist in the environment
+that can be detected in multiple images. In contrast, our indoor
 environments have a high prevalence of bare surfaces, as well as
@@
 
-  \caption{Texture alignment via (a) image mosaicing, (b) the
-    graph-based localization refinement algorithm from
-    \cite{chen2010indoor}, and (c) the method proposed in this paper.}
+  \caption{Texture alignment via (a) the graph-based localization
+    refinement algorithm, (b) the AutoStitch software package, and (c)
+    our method.}
   \label{fig:mosaic3D}
@@
 stitching with an iterative localization algorithm, and performed
-homography-based camera pose refinement. When run on long chains of
-images, especially where features are sparse, it produces distorted
-textures, as seen in Figure \ref{fig:mosaic3D}(a), due to the problems
-described above. This approach is also not closed-form, and its
-iterative camera adjustment process over our large datasets leads to
-prohibitively long computation time.
+homography-based camera pose refinement \cite{liu2010indoor}. When run
+on long chains of images, especially where features are sparse, it
+produces distorted textures, as seen in Figure \ref{fig:mosaic3D}(a),
+due to the problems described above. This approach is also not
+closed-form, and its iterative camera adjustment process over our
+large datasets leads to prohibitively long computation time.
 
@@
 
-\section{2D Image Alignment with Geometry Information}
+\section{2D Image Alignment}
 \label{sec:2dAlignment}
@@
 parallel to detected surfaces \cite{kua2012loopclosure,
-  sanchez2012point}. Since the operator walks in as upright a position
-as possible, errors in roll, yaw, and the operator's distance from
-parallel surfaces are minimal. Thus, our highest errors stem from
-uncertainty in the operator's pitch, equivalent to rotation around the
-camera axes, as well as location along surfaces. These equate to 2D
-rotation and translation in a surface's plane.
+  sanchez2012point}. Since the operator also walks in a manner to keep
+the backpack balanced, errors in roll and yaw are minimal. Thus, our
+highest errors stem from uncertainty in the operator's pitch,
+equivalent to rotation around the camera axes, as well as location
+along surfaces. These equate to 2D rotation and translation in a
+surface's plane.
 
-Our 2D alignment procedure consists of three main parts. First, all
-images are projected onto the surface and lines within these
-projections are detected. These lines are then rotated and shifted to
-match geometry-based lines comprising the surface's boundary and
+Our 2D alignment procedure consists of three parts. First, all images
+are projected onto the surface and lines within these projections are
+detected. These lines are then rotated and shifted to match
+geometry-based lines comprising the surface's boundary and
 intersection with other surfaces. Second, occlusion checks are
@@
 their orientation, for usage in Section
-\ref{robustSIFTFeatureMatching}.
+\ref{sec:robustSIFTFeatureMatching}.
 
@@
 perform a simple recursive occlusion procedure on each image. This is
-done by performing the intersection tests in section
+done by performing the intersection tests in Section
 \ref{sec:simpleTextureMapping} in a regularly spaced grid. Where four
@@
 \label{sec:robustSIFTFeatureMatching}
-Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images. We use
-SIFT features for their high detection rate, and choose to use feature
-alignment rather than pixel or intensity-based alignment due to the
-differences in lighting as well as possible occlusion among our
-images, both of which feature alignment is less sensitive to
-\cite{lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-We use SiftGPU \cite{siftgpu} for its high performance on both feature
-detection as well as pairwise matching. These matches determine $d^x$
-and $d^y$ distances between each pair of features for two image
-projections, though these distances may not always be the same for
-different features. Since indoor environments often contain repetitive
-features such as floor tiles or doors, we need to ensure that
-SIFT-based distances are reliable. First, we only perform alignment on
-parts of images that overlap given the original noisy poses. Second,
-we discard feature matches that correspond to an image distance
-greater than 40 pixels from what the noisy poses estimate. In order to
-utilize the remaining feature matches robustly, RANSAC
-\cite{fischler1981random} is again used to estimate the optimal
-$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
-$j$. We use a 10 pixel threshold for RANSAC, so that SIFT matches are
-labeled as outliers if their distance is not within 10 pixels of the
-sampled average distance.
+Our next step is to align images by searching for corresponding points
+between all pairs of overlapping images. We use feature alignment
+rather than pixel or intensity-based alignment due to the differences
+in lighting as well as possible occlusion among our images, both of
+which feature alignment is less sensitive to \cite{lowe1999object,
+  mikolajczyk2005performance, szeliski2006image}.  We use SiftGPU
+\cite{siftgpu} for its high performance on both feature detection as
+well as pairwise matching. These matches determine $dx$ and $dy$
+distances between each pair of features for two image projections,
+though these distances may not always be the same for different
+features. Since indoor environments often contain repetitive features
+such as floor tiles or doors, we need to ensure that SIFT-based
+distances are reliable. First, we only perform alignment on parts of
+images that overlap given the original noisy poses. Second, we discard
+feature matches that correspond to an image distance greater than 200
+mm from what the noisy poses estimate. In order to utilize the
+remaining feature matches robustly, RANSAC \cite{fischler1981random}
+is again used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$
+distances between two images $i$ and $j$. We use a 5 mm threshold for
+RANSAC, so that SIFT matches are labeled as outliers if their distance
+is not within 5 mm of the sampled average distance.
 
-We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
+We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
 of images to refine their positions using weighted linear least
-squares. The variables we wish to solve for are the $x$ and $y$
+squares. The variables we wish to solve for are the $_ix$ and $y_i$
 positions of our images, while our equations are the SIFT-based
@@
 1 degrees of freedom, and the original camera poses. Ignoring
-weighting for now, an example setup for solving
-$\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $
-with 3 images is shown below.
+weighting and the original camera poses for now, an example setup for
+solving $\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
+\vec{\gamma}||_2^2 $ with 3 images is shown below.
 
@@
 calculated between images 1 and 2. This corresponds to the first and
-second of $A$, while the third and fourth row of $A$ represent the
+second row of $A$, while the third and fourth row of $A$ represent the
 same for images 2 and 3. Rows 5 and 6 of $A$ correspond to a fixed
@@
 constraint to a line of slope $m$, with current location $tx_2$,
-$ty_2$, both results of the geometry alignment procedure in Section
-\ref{sec:geometryAlignment}. If we do not have enough SIFT matches, or
-lack images matched to geometry, our matrix becomes rank-deficient and
-our problem cannot be solved. As a result, we add rows for each image
-corresponding to the original noisy image locations, and downweight
-them heavily, e.g. with a weight of 0.01 versus 1.
+$ty_2$, both possible results of the geometry alignment procedure in
+Section \ref{sec:geometryAlignment}. If we do not have enough SIFT
+matches, or lack images matched to geometry, our matrix becomes
+rank-deficient and our problem cannot be solved. As a result, we add
+rows for each image corresponding to the original noisy image
+locations, and downweight them heavily, e.g. with a weight of 0.01
+versus 1.
 
-Because our problem is linear, it is easily and quickly solved, and after
-applying the resulting shifts, our images overlap and match each other
-with far greater accuracy. Applying the simple mapping scheme in
+Because our problem is linear, it is easily and quickly solved, and
+after applying the resulting shifts, our images overlap and match each
+other with far greater accuracy. Applying the simple mapping scheme in
 Section \ref{sec:tileBasedMapping} to the same wall used in that
@@
 discontinuities, though errors due to lighting differences and
-repeating features are still visible.
+parallax effects are still visible.
 
@@
 Figure \ref{fig:compareAll}(b). However, some discontinuities are
-still present, as visible in the many posters on the wall with breaks
+still present, as visible in the posters on the wall with breaks
 in their borders.
@@
   \centering
-  \includegraphics[width=3in]{dagCreation.pdf}
+  \includegraphics[width=5in]{dagCreation.pdf}
   \caption{DAG construction for the image selection process. \\}
@@
 pixels, and spans a 40-meter long wall. Given 41000 input images, a
-2.8GHz consumer-grade laptop takes approximately a minute to pick 36
-candidate images, followed by another minute to perform both image
-alignment and the shortest path texturing method, though over 75\% of
-that time is spent calculating SIFT matches within the SiftGPU
+2.8GHz dual-core consumer-grade laptop takes approximately a minute to
+pick 36 candidate images, followed by another minute to perform both
+image alignment and the shortest path texturing method, though over
+75\% of that time is spent calculating SIFT matches within the SiftGPU
 framework. While not real-time, the process is capable of generating
@@
 \ref{fig:results} are roughly 20 MB in size, and are visualized using
-the OpenSceneGraph toolkit \cite{openscenegraph}, which allows for export to many common
-model formats, as well as efficient visualization, even in web
-browsers or mobile devices.
+the OpenSceneGraph toolkit \cite{openscenegraph}, which allows for
+export to many common model formats, as well as efficient
+visualization, even in web browsers or mobile devices.
 

### 2013-01-20 spie/_region_.tex
now zoomed images

@@
 
-\message{ !name(paper.tex) !offset(374) }
+\message{ !name(paper.tex) !offset(371) }
 \subsection{2D Feature Alignment}
 \label{sec:robustSIFTFeatureMatching}
-Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images. We use
-SIFT features for their high detection rate, and choose to use feature
-alignment rather than pixel or intensity-based alignment due to the
-differences in lighting as well as possible occlusion among our
-images, both of which feature alignment is less sensitive to
-\cite{lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-We use SiftGPU \cite{siftgpu} for its high performance on both feature
-detection as well as pairwise matching. These matches determine $d^x$
-and $d^y$ distances between each pair of features for two image
-projections, though these distances may not always be the same for
-different features. Since indoor environments often contain repetitive
-features such as floor tiles or doors, we need to ensure that
-SIFT-based distances are reliable. First, we only perform alignment on
-parts of images that overlap given the original noisy poses. Second,
-we discard feature matches that correspond to an image distance
-greater than 40 pixels from what the noisy poses estimate. In order to
-utilize the remaining feature matches robustly, RANSAC
-\cite{fischler1981random} is again used to estimate the optimal
-$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
-$j$. We use a 10 pixel threshold for RANSAC, so that SIFT matches are
-labeled as outliers if their distance is not within 10 pixels of the
-sampled average distance.
+Our next step is to align images by searching for corresponding points
+between all pairs of overlapping images. We use feature alignment
+rather than pixel or intensity-based alignment due to the differences
+in lighting as well as possible occlusion among our images, both of
+which feature alignment is less sensitive to \cite{lowe1999object,
+  mikolajczyk2005performance, szeliski2006image}.  We use SiftGPU
+\cite{siftgpu} for its high performance on both feature detection as
+well as pairwise matching. These matches determine $dx$ and $dy$
+distances between each pair of features for two image projections,
+though these distances may not always be the same for different
+features. Since indoor environments often contain repetitive features
+such as floor tiles or doors, we need to ensure that SIFT-based
+distances are reliable. First, we only perform alignment on parts of
+images that overlap given the original noisy poses. Second, we discard
+feature matches that correspond to an image distance greater than 200
+mm from what the noisy poses estimate. In order to utilize the
+remaining feature matches robustly, RANSAC \cite{fischler1981random}
+is again used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$
+distances between two images $i$ and $j$. We use a 5 mm threshold for
+RANSAC, so that SIFT matches are labeled as outliers if their distance
+is not within 5 mm of the sampled average distance.
 
-We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
+We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
 of images to refine their positions using weighted linear least
-squares. The variables we wish to solve for are the $x$ and $y$
+squares. The variables we wish to solve for are the $_ix$ and $y_i$
 positions of our images, while our equations are the SIFT-based
@@
   0 & -m & 0 & 0 & 1 & 0\\
+\end{pmatrix}\quad
+\vec{\beta} =
+\begin{pmatrix}
+  x_1, \\ x_2, \\ x_3, \\ y_1, \\ y_2, \\ y_3
 \end{pmatrix}
-\]
-
-\[\vec{\beta} =
+\vec{\gamma} =
 \begin{pmatrix}
-  x_1, & x_2, & x_3, & y_1, & y_2, & y_3
-\end{pmatrix}
-\]
-
-\[
-\vec{\gamma}^T =
-\begin{pmatrix}
-  dx_{1,2}, &dy_{1,2}, &dx_{2,3}, &dy_{2,3}, &t1_x, &t1_y, & -mx_2 +
+  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ t1_x, \\ t1_y, \\ -mx_2 +
   ty_2
@@
 constraint to a line of slope $m$, with current location $tx_2$,
-$ty_2$, both results of the geometry alignment procedure in Section
-\ref{sec:geometryAlignment}. If we do not have enough SIFT matches, or
-lack images matched to geometry, our matrix becomes rank-deficient and
-our problem cannot be solved. As a result, we add rows for each image
-corresponding to the original noisy image locations, and downweight
-them heavily, e.g. with a weight of 0.01 versus 1.
+$ty_2$, both possible results of the geometry alignment procedure in
+Section \ref{sec:geometryAlignment}. If we do not have enough SIFT
+matches, or lack images matched to geometry, our matrix becomes
+rank-deficient and our problem cannot be solved. As a result, we add
+rows for each image corresponding to the original noisy image
+locations, and downweight them heavily, e.g. with a weight of 0.01
+versus 1.
 
-Because our problem is linear, it is quickly solved, and after
-applying the resulting shifts, our images overlap and match each other
-with far greater accuracy. Applying the simple mapping scheme in
+Because our problem is linear, it is easily and quickly solved, and
+after applying the resulting shifts, our images overlap and match each
+other with far greater accuracy. Applying the simple mapping scheme in
 Section \ref{sec:tileBasedMapping} to the same wall used in that
@@
 discontinuities, though errors due to lighting differences and
-repeating features are still visible.
+parallax effects are still visible.
 
-\message{ !name(paper.tex) !offset(667) }
+\message{ !name(paper.tex) !offset(668) }
 

### 2013-01-20 spie/paper.tex
now zoomed images

@@
   \centering
-  \subfloat[][]{\includegraphics[height=1.5in]{geometryAlign_planes.png}}
-  \subfloat[][]{\includegraphics[height=1.5in]{geomAlign}}
-  \caption{(a) When texturing the red surface, it makes sense to align
-    images to surface boundaries and intersections with other
-    surfaces. (b) In this example, we project two images at once for
-    the sake of demonstration, where the red lines are geometry-based
-    lines where surfaces intersect, and the green ines are lines
-    detected in the image via Hough transform. Above are the original
-    projections using input camera poses, and below are the
-    projections after rotation and translation for alignment.}
+  \subfloat[][]{\includegraphics[height=3in]{detectedLines.png}}
+  \hspace{0.4 cm}
+  \subfloat[][]{\includegraphics[height=3in, width=4in]{bothunalignedaligned.png}}
+  \caption{(a) Lines detected in image projections via Hough transform
+    (b) In this example, we project two images at once for the sake of
+    demonstration, where the red lines are geometry-based lines where
+    surfaces intersect, and the green ines are lines detected in the
+    image. Above are the original projections using input camera
+    poses, and below are the projections after rotation and
+    translation for alignment.}
   \label{fig:geometryAlignment}

### 2013-01-21 spie/paper.tex
ready to send off?

@@
 \usepackage{hyperref}
-
+\usepackage{float}
 \title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
@@
     \centering
-    \includegraphics[height=1.5in]{Projection.pdf}
+    \includegraphics[height=1.8in]{Projection.pdf}
     \caption{Surfaces to be textured are specified in 3D space by
       corners $C_i$. Images are related to each surface through the
-      camera matrics $P_{1..m}$. }
+      camera matrices $P_{1..m}$. }
     \label{fig:projection}
@@
     \centering
-    \includegraphics[height=1.125in]{scoringFunction.jpg}
+    \includegraphics[height=1.8in]{scoringFunction.jpg}
     \caption{We minimize camera angle $\alpha$ and distance $d$ by
@@
 
-\begin{figure}
+As Figure \ref{fig:compareAll}(a) demonstrates, there are many image
+boundaries with abrupt discontinuities between tiles, due to
+significant misalignment between images, though most of it appears to
+be reconcilable using 2D transforms. Given our high number of input
+images, a better image selection procedure will further improve
+results, as described in Section \ref{sec:imageCompositing}, but a
+more significant and reliable improvement can be found through first
+improving the alignment of our images.
+
+\begin{figure}[H]
   \centering \subfloat[][]{\includegraphics[width=3.4in,
@@
   \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift_details.png}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift_details.png}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
     height=1.2in]{wall2_cache_shift_blend.pdf}}
@@
 
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
+    height=3.4in]{wall2_cache_comparison.png}}
+  \subfloat[][]{\includegraphics[width=3.4in,
+    height=3.4in]{wall2_shortest_comparison.png}}
+
   \caption{(a): Tile-based texturing. (b): Tile-based texturing after
@@
     with caching. (d): Shortest path texturing after image
-    alignment). (e,f): Comparison of image artifacts in (c)
-    vs. (d). (g,h): Blending applied to (c) and (d).}
+    alignment). (e,f): Blending applied to (c) and (d). (g,h): Zoomed in views of discontinuities in (e) vs. in (f).}
   \label{fig:compareAll}
 \end{figure}
-
-As Figure \ref{fig:compareAll}(a) demonstrates, there are many image
-boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images, though most of it appears to
-be reconcilable using 2D transforms. Given our high number of input
-images, a better image selection procedure will further improve
-results, as described in Section \ref{sec:imageCompositing}, but a
-more significant and reliable improvement can be found through first
-improving the alignment of our images.
 
@@
 work in 3D, we elect to perform image alignments entirely in
-2D. Besides the benifits of reduced complexity, we have found 2D
+2D. Besides the benefits of reduced complexity, we have found 2D
 alignment to work well for two main reasons. First, because we have
@@
   \subfloat[][]{\includegraphics[height=3in, width=4in]{bothunalignedaligned.png}}
-  \caption{(a) Lines detected in image projections via Hough transform
+  \caption{(a) Lines detected in image projections via Hough transform.
     (b) In this example, we project two images at once for the sake of
     demonstration, where the red lines are geometry-based lines where
-    surfaces intersect, and the green ines are lines detected in the
+    surfaces intersect, and the green lines are lines detected in the
     image. Above are the original projections using input camera
@@
 images. To enforce consistent blending however, we add a minimum
-required overlap distance of 40 px while solving the shortest path
+required overlap distance of 200 mm while solving the shortest path
 problem in Section \ref{sec:shortestPath}. Additionally, if images
@@
 
+\subsection{Future Work}
+While our method works well on our datasets, it is heavily reliant on
+having a large number of input images, and minimal non-2D error. An
+approach towards resolving camera error in 3D that would mesh well
+with our approach is to perform matching between image lines and
+geometry in 3D, which can be done reasonably efficiently
+\cite{linebased, rectangularstructures}. Using linear features on top
+of our SIFT features is also likely to result in improved matches, as
+indoor scenes often have long, unbroken lines spanning multiple images
+\cite{linearposeestimation}. Finally, our blending approach is quite
+basic, and applying more sophisticated methods of blending as well as
+normalization would benefit our final visual quality, and more
+robustly handle motion-based or parallax errors.
+
 \begin{figure}

### 2013-02-03 spie/2dpaper.tex
revision time

--- 2013-01-21 spie/paper.tex
@@
   independently of pose estimates and geometry information. By
-  intelligently selecting images for texturing, we develop
-  an efficient method to adjust camera poses in 2D, followed by two
-  different methods to composite images together, based on the
-  geometry of surfaces being textured. The effectiveness of our
-  method is demonstrated on a number of different indoor
-  environments.
+  intelligently selecting images for texturing, we develop an
+  efficient method to adjust camera poses in 2D, using linear features
+  to match images to geometry, and point features to match images
+  together. This is followed by two different methods to composite
+  images together, based on the geometry of surfaces being
+  textured. The effectiveness of our method is demonstrated on a
+  number of different indoor environments.
 \end{abstract}
@@
 with a backpack-mounted system carried by an ambulatory human
-\cite{liu2010indoor}. This backpack system contains a series of
-cameras, laser scanners, and inertial measurement units, used to solve
-the simultaneous localization and mapping (SLAM) problem, which
-produces backpack (and therefore camera) poses over time as well as a
-point cloud representing the surrounding environment
-\cite{chen2010indoor, liu2010indoor, kua2012loopclosure}. For
+\cite{liu2010indoor}. This backpack system contains 2 fisheye cameras
+as well as laser scanners and inertial measurement units,
+used to solve the simultaneous localization and mapping (SLAM)
+problem, which produces backpack (and therefore camera) poses over
+time as well as a point cloud representing the surrounding environment
+\cite{chen2010indoor, liu2010indoor, kua2012loopclosure}. SHOW PICTURE OF BACKPACK. For
 environment geometry, we work with models obtained by fitting
@@
     with caching. (d): Shortest path texturing after image
-    alignment). (e,f): Blending applied to (c) and (d). (g,h): Zoomed in views of discontinuities in (e) vs. in (f).}
+    alignment). (e,f): Blending applied to (c) and (d). (g,h): Zoomed
+    in views of discontinuities in (e) vs. in (f).}
   \label{fig:compareAll}
@@
 Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not exact
-and are compounded together. For example, when matching a long chain
-of images through homographies, a pixel in the $nth$ image is
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrices $H_1 H_2 H_3 ... H_n$. Errors in any of these
-homography matrices are propagated to all further images, resulting in
-drift.
+can lead to large overall error when images are matched together. For
+example, a slight error in image correspondences in the middle of a
+chain could lead to high global error at one or both ends of the
+chain.
 
@@
 closed-form, and its iterative camera adjustment process over our
-large datasets leads to prohibitively long computation time.
+large datasets led to prohibitively long computation time.
 
 The AutoStitch software package performs homography-based alignment as
-well, with additional provisions that attempt to reduce drift
-\cite{panorama2d, autostitch}. Though AutoStitch also performs well in
-areas with dense features, it can not handle areas without features,
-and has trouble aligning wall sections with even short segments of
-bare texture. The example in Figure \ref{fig:mosaic3D}(b) was
-generated after manual tuning, and areas with fewer visual features or
-repeating texture patterns simply failed outright with AutoStitch.
+well, with additional provisions that attempt to reduce drift and
+increase efficiency \cite{panorama2d, autostitch}. Though AutoStitch
+also performs well in areas with dense features, it can not handle
+areas without features, and has trouble aligning wall sections with
+even short segments of bare texture. The example in Figure
+\ref{fig:mosaic3D}(b) was generated after manual tuning, and areas
+with fewer visual features or repeating texture patterns simply failed
+outright with AutoStitch.
 
-\section{2D Image Alignment}
+More importantly, neither approach
+
+\section{2d Image Alignment}
 \label{sec:2dAlignment}
@@
 that dominant lines are made to be horizontal or vertical. This can be
-further generalized by instead orienting lines to be parallel with a
-surface's boundaries, which makes it applicable to non-rectangular
-surfaces, such as ceilings, floors, or slanted walls.
+further generalized by instead orienting lines to be parallel or
+perpendicular with a surface's boundaries, which makes it applicable
+to ceilings and floors, where inner walls and interior features tend
+to be parallel or perpendicular to outer walls.
 
@@
   \subfloat[][]{\includegraphics[height=3in]{detectedLines.png}}
-  \hspace{0.4 cm}
-  \subfloat[][]{\includegraphics[height=3in, width=4in]{bothunalignedaligned.png}}
-  \caption{(a) Lines detected in image projections via Hough transform.
-    (b) In this example, we project two images at once for the sake of
-    demonstration, where the red lines are geometry-based lines where
-    surfaces intersect, and the green lines are lines detected in the
-    image. Above are the original projections using input camera
-    poses, and below are the projections after rotation and
-    translation for alignment.}
+  \hspace{0.4 cm} \subfloat[][]{\includegraphics[height=3in,
+    width=4in]{bothunalignedaligned.png}}
+  \caption{(a) Lines detected in image projections via Hough
+    transform.  (b) In this example, we project two images at once for
+    the sake of demonstration. Red line segments represent where
+    surfaces intersect, and green line segments are line segments
+    detected in the image. Above are the original projections using
+    input camera poses, and below are the projections after rotation
+    and translation for alignment.}
   \label{fig:geometryAlignment}
@@
 
-To perform rotation, we use a RANSAC \cite{fischler1981random}
+To perform these alignments, we use a RANSAC \cite{fischler1981random}
 framework to determine an optimal rotation angle between lines in our
@@
 \begin{pmatrix}
-  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ t1_x, \\ t1_y, \\ -mx_2 +
-  ty_2
+  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ t1_x, \\ t1_y,
+  \\ -mx_2 + ty_2
 \end{pmatrix}
@@
 Figure \ref{fig:compareAll}(b). However, some discontinuities are
-still present, as visible in the posters on the wall with breaks
-in their borders.
+still present, as visible in the posters on the wall with breaks in
+their borders.
 
@@
 
-To cover the entirety of a plane, our problem can be defined as
-minimally covering a polygon i.e. the planar surface, using other
-polygons of arbitrary geometry i.e. image projections, with the added
-constraint of minimizing the cost function between chosen images.
-This is a complex problem, though we can take a number of steps to
-simplify it.
-
-Given that wall-texture candidate images are taken from more or less
-head-on angles, and knowing that only minor rotations are made in
-Section \ref{sec:2dAlignment}, we can reason that their projections
-onto the plane are approximately rectangular. By cropping them all to
-be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
-problem becomes the conceptually simpler one of filling a polygon with
-rectangles, such that the sum of all costs between each pair of
-rectangles is minimal. We thus also retain the advantages of working
-with rectangular units, as explained in Section
-\ref{sec:tileBasedMapping}.
-
-The operator's path, and the location and orientation of the cameras
-on the acquisition backpack is such that images nearly always contain
-the entirety of the floor to ceiling range of wall planes. Images
-therefore rarely need to be projected with one above another when
-texturing wall planes. In essence, we need only to ensure lateral
-coverage of wall planes, e.g. from left to right, as our images
-provide full vertical coverage themselves. We can thus construct a
-Directed Acyclic Graph (DAG) from the images, with edge costs defined
-by the SSD cost function, and solve a simple shortest path problem to
-find an optimal subset of images with regard to the SSD cost function
-\cite{dijkstra}.
+In the general case, our problem can be defined as minimally covering
+a polygon i.e. the planar surface, using other polygons of arbitrary
+geometry i.e. image projections, with the added constraint of
+minimizing the cost function between chosen images. Given that
+wall-texture candidate images are taken from more or less head-on
+angles, and knowing that only minor rotations are made in Section
+\ref{sec:2dAlignment}, we can crop our image projections to be
+rectangular with minimal texture loss. Furthermore, because our
+fisheye camera lenses have full floor-to-ceiling coverage of nearly
+all walls, and our backpack operator logically only moves
+horizontally, we only need to ensure lateral coverage of our wall
+planes. We can thus construct a Directed Acyclic Graph (DAG) from the
+images, with edge costs defined by the SSD cost function, and solve a
+simple shortest path problem to find an optimal subset of images with
+regard to the SSD cost function \cite{dijkstra}.
 
@@
 
-In rare cases where the vertical dimension of the plane is not
+In very rare cases where the vertical dimension of the plane is not
 entirely covered by one or more chosen images, we are left with holes
@@
 between the two methods, showing that Figure \ref{fig:compareAll}(f)
-clearly has the best visual quality and the best texturing approach
-among the textures in Figure \ref{fig:compareAll}.
+has the best visual quality and the best texturing approach among the
+textures in Figure \ref{fig:compareAll}.
 
@@
 approach, and walls textured with the shortest path approach, are
-displayed in Figure \ref{fig:results}. High resolution colored texture
-comparisons, as well as further examples and interactive walkthroughs
-are available at
+displayed in Figure \ref{fig:results}. These results are as accurate
+and clean as the best results we obtained using the two algorithms
+mentioned in Section \ref{sec:existingApproaches}. High resolution
+colored texture comparisons, as well as video and interactive
+walkthroughs of full models are available at
 \footnote{\url{http://www.eecs.berkeley.edu/~pcheng/indoormapping}}.
@@
 Figure \ref{fig:results}(a) was generated with 7543 $\times$ 776
-pixels, and spans a 40-meter long wall. Given 41000 input images, a
-2.8GHz dual-core consumer-grade laptop takes approximately a minute to
-pick 36 candidate images, followed by another minute to perform both
-image alignment and the shortest path texturing method, though over
-75\% of that time is spent calculating SIFT matches within the SiftGPU
-framework. While not real-time, the process is capable of generating
-quick updates after changes in various parameters or modifications to
-input data, and if integrated directly into a modeling system, could
-provide live visualization as data is collected. Our full models
-consist of our input model file, textures that we generate, and a
-mapping of image points to model vertices. The models shown in Figure
-\ref{fig:results} are roughly 20 MB in size, and are visualized using
-the OpenSceneGraph toolkit \cite{openscenegraph}, which allows for
-export to many common model formats, as well as efficient
-visualization, even in web browsers or mobile devices.
+pixels, and spans a 40-meter long wall. Given 41000 input images of
+the entire dataset, a 2.8GHz dual-core consumer-grade laptop takes
+approximately a minute to pick 36 candidate images, followed by under
+a minute to perform both image alignment and the shortest path
+texturing method, though over 75\% of that time is spent calculating
+SIFT matches within the SiftGPU framework. While not real-time, the
+process is capable of generating quick updates after changes in
+various parameters or modifications to input data, and if integrated
+directly into a modeling system, could provide live visualization as
+data is collected. Our full models consist of our input model file,
+textures that we generate, and a mapping of image points to model
+vertices. The models shown in Figure \ref{fig:results} are roughly 20
+MB in size, and are visualized using the OpenSceneGraph toolkit
+\cite{openscenegraph}, which allows for export to many common model
+formats, as well as efficient visualization, even in web browsers or
+mobile devices.
 
@@
 While our method works well on our datasets, it is heavily reliant on
-having a large number of input images, and minimal non-2D error. An
-approach towards resolving camera error in 3D that would mesh well
-with our approach is to perform matching between image lines and
-geometry in 3D, which can be done reasonably efficiently
-\cite{linebased, rectangularstructures}. Using linear features on top
-of our SIFT features is also likely to result in improved matches, as
-indoor scenes often have long, unbroken lines spanning multiple images
+having a large number of input images, and minimal non-2D error. A
+technique for resolving camera error in 3D that would mesh well with
+our approach is to perform matching between image lines and geometry
+in 3D, which can be done reasonably efficiently \cite{linebased,
+  rectangularstructures}. Using linear features on top of our SIFT
+features is also likely to result in improved matches, as indoor
+scenes often have long, unbroken lines spanning multiple images
 \cite{linearposeestimation}. Finally, our blending approach is quite

### 2013-02-03 spie/_region_.tex
revision time

@@
 
-\message{ !name(paper.tex) !offset(371) }
+\message{ !name(paper.tex) !offset(376) }
 \subsection{2D Feature Alignment}
@@
 weighting and the original camera poses for now, an example setup for
-solving $\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
-\vec{\gamma}||_2^2 $ with 3 images is shown below.
+solving $\textrm{min}_{\vec{\beta}} ||W^\frac{1}{2}(A \vec{\beta} -
+\vec{\gamma})||_2^2 $ with 3 images is shown below.
 
@@
   0 & 0 & 0 & 0 & -1 & 1\\
+  0 & -m_2 & 0 & 0 & 1 & 0\\
   1 & 0 & 0 & 0 & 0 & 0\\
   0 & 0 & 0 & 1 & 0 & 0\\
-  0 & -m & 0 & 0 & 1 & 0\\
+  1 & 0 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 1 & 0 & 0\\
+
 \end{pmatrix}\quad
@@
 \begin{pmatrix}
-  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ t1_x, \\ t1_y, \\ -mx_2 +
-  ty_2
+  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ -m_2gx_2 + gy_2, 
+  \\ gx_1, \\ gy_1, \\ tx_1, \\ ty_1
+
+\end{pmatrix}
+\vec{W} = 
+\begin{pmatrix}
+  1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 0.01, \\ 0.01
 \end{pmatrix}
@@
 
-\message{ !name(paper.tex) !offset(668) }
+\message{ !name(paper.tex) !offset(678) }
 

### 2013-02-03 spie/paper.tex
revision time

@@
   models allows for photo-realistic visualizations of the data
-  collected by such modeling systems. We perform these tasks using a
-  backpack-mounted data acquisition system. Camera poses obtained by
-  this system and used for texturing often suffer from inaccuracies
-  however, resulting in visible discontinuities when successive images
+  collected by such modeling systems.
+While data acquisition times for mobile mapping systems are considerably shorter than for static ones, their recovered camera poses often suffer from inaccuracies, resulting in visible discontinuities when successive images
   are projected onto a surface for texturing. Existing methods to
   stitch images together are often computationally expensive and work
-  independently of pose estimates and geometry information. By
-  intelligently selecting images for texturing, we develop
-  an efficient method to adjust camera poses in 2D, followed by two
-  different methods to composite images together, based on the
-  geometry of surfaces being textured. The effectiveness of our
-  method is demonstrated on a number of different indoor
-  environments.
+  independently of pose estimates and geometry data.
+
+The approach in this paper minimizes complexity by refining camera poses in 2D, which works well given our high amount of images and minimal 3D pose errors.
+We also align images to geometry as well as to each other, which produces visually consistent textures even in the presence of inaccurate surface geometry.
+We also present two different methods for selecting and compositing images into a single texture, depending on the geometry of surfaces being textured.
+The effectiveness of our method is demonstrated on a number of different indoor environments.
+
+By
+  intelligently selecting images for texturing, we develop an
+  efficient method to adjust camera poses in 2D, using linear features
+  to match images to geometry, and point features to match images
+  together. This is followed by two different methods to composite
+  images together, based on the geometry of surfaces being
+  textured. The effectiveness of our method is demonstrated on a
+  number of different indoor environments.
 \end{abstract}
@@
 We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
-of images to refine their positions using weighted linear least
-squares. The variables we wish to solve for are the $_ix$ and $y_i$
+of images, as well as our previous geometry alignment results to refine their positions using weighted linear least
+squares. The variables we wish to solve for are the $x_i$ and $y_i$
 positions of our images, while our equations are the SIFT-based
 distances between pairs of images, images fixed to geometry with 0 or
-1 degrees of freedom, and the original camera poses. Ignoring
-weighting and the original camera poses for now, an example setup for
-solving $\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
-\vec{\gamma}||_2^2 $ with 3 images is shown below.
+1 degrees of freedom, and the original camera poses. An example setup for
+solving our weighted linear least squares problem $\textrm{min}_{\vec{\beta}} ||W^\frac{1}{2}(A \vec{\beta} -
+\vec{\gamma})||_2^2 $ with 3 images is shown below.
 
@@
 second row of $A$, while the third and fourth row of $A$ represent the
-same for images 2 and 3. Rows 5 and 6 of $A$ correspond to a fixed
+same for images 2 and 3. Row 5 corresponds to a constraint of image 2's location to a line of slope $m_2$, passing through point $gx_2$, $gy_2$. 
+Row 6 and 7 do stuff and 8 and 9 ensure that we are not rank deficient in case of whatever.
+
+ Rows 5 and 6 of $A$ correspond to a fixed
 location of $tx_1$, $ty_1$ for image 1, while Row 7 corresponds to a

### 2013-02-04 spie/paper.tex
done with text-based edits

@@
   models allows for photo-realistic visualizations of the data
-  collected by such modeling systems.
-While data acquisition times for mobile mapping systems are considerably shorter than for static ones, their recovered camera poses often suffer from inaccuracies, resulting in visible discontinuities when successive images
-  are projected onto a surface for texturing. Existing methods to
-  stitch images together are often computationally expensive and work
-  independently of pose estimates and geometry data.
-
-The approach in this paper minimizes complexity by refining camera poses in 2D, which works well given our high amount of images and minimal 3D pose errors.
-We also align images to geometry as well as to each other, which produces visually consistent textures even in the presence of inaccurate surface geometry.
-We also present two different methods for selecting and compositing images into a single texture, depending on the geometry of surfaces being textured.
-The effectiveness of our method is demonstrated on a number of different indoor environments.
-
-By
-  intelligently selecting images for texturing, we develop an
-  efficient method to adjust camera poses in 2D, using linear features
-  to match images to geometry, and point features to match images
-  together. This is followed by two different methods to composite
-  images together, based on the geometry of surfaces being
-  textured. The effectiveness of our method is demonstrated on a
-  number of different indoor environments.
+  collected by such modeling systems. While data acquisition times for
+  mobile mapping systems are considerably shorter than for static
+  ones, their recovered camera poses often suffer from inaccuracies,
+  resulting in visible discontinuities when successive images are
+  projected onto a surface for texturing. Existing methods to stitch
+  images together are often computationally expensive and work
+  independently of pose estimates and geometry data. We present a
+  method for texture mapping that reduces complexity by selecting
+  images whose camera poses can be align in 2D. We perform alignment
+  of images to geometry as well as images to each other, which
+  produces visually consistent textures even in the presence of
+  inaccurate surface geometry. We also present two different methods
+  for selecting and compositing images into a single texture,
+  depending on the geometry of the surface being textured. The
+  effectiveness of these methods is demonstrated on a number of different
+  indoor environments.
 \end{abstract}
@@
 Three-dimensional modeling of indoor environments has a variety of
-applications in fields such as architecture, conservation, and
-simulation. Applying accurate textures to these models is important to
-add context to digital visualizations, and allows for image-based
-analysis of environments. In this paper, we perform data acquisition
-with a backpack-mounted system carried by an ambulatory human
-\cite{liu2010indoor}. This backpack system contains 2 fisheye cameras
-as well as laser scanners and inertial measurement units,
-used to solve the simultaneous localization and mapping (SLAM)
-problem, which produces backpack (and therefore camera) poses over
-time as well as a point cloud representing the surrounding environment
-\cite{chen2010indoor, liu2010indoor, kua2012loopclosure}. SHOW PICTURE OF BACKPACK. For
-environment geometry, we work with models obtained by fitting
-low-resolution planar surfaces to these point clouds
-\cite{sanchez2012point}.
+applications such as training and simulation for disaster management,
+virtual heritage conservation, and mapping of hazardous sites. Manual
+construction of these digital models can be time consuming, and as
+such, automated 3D site modeling has garnered much interest in recent
+years.
 
-While a human-carried system provides advantages over more common
-wheeled systems in terms of agility and portability, it often leads to
-relatively high localization error even after applying sophisticated
-localization techniques \cite{liu2010indoor}. Furthermore, our model
-geometry usually contains some error as well, and is often tuned to
-ignore low-resolution features, such as small walls, furniture, and
-other minor non-planar features commonly found in indoor
-environments. As a result, methods for texture mapping that rely on
-accurate camera poses and projection surfaces generally produce poor
-results, while more sophisticated methods to accurately align images
-in 3D lead to high runtime on our typically very large datasets. In
-contrast, we present a method, which given a high number of images,
-searches for a subset of them that can be successfully aligned with 2D
-adjustments alone.
+The first step in automated 3D modeling is the physical scanning of
+the environment's geometry. An indoor modeling system must be able to
+recover camera poses within an environment while simultaneously
+reconstructing the 3D structure of the environment itself
+\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
+known as the simultaneous localization and mapping (SLAM) problem, and
+is generally solved by taking readings from laser range scanners,
+cameras, and inertial measurement units (IMUs) at multiple locations
+within the environment.
+
+Mounting such devices on a platform carried by an ambulatory human
+provides unique advantages over vehicular-based systems on wheels in
+terms of agility and portability, but can also result in larger
+localization error \cite{liu2010indoor}. As a result, common methods
+for texture mapping generally produce poor results.
+
+In this paper, we present a number of approaches to texture mapping 3D
+models of indoor environments made of planar surfaces in the presence
+of uncertainty and noise in camera poses. In particular, we consider
+data obtained from a human-operated backpack system with a number of
+laser range scanners as well as 2 cameras facing left and right, each
+equipped with fisheye lenses reaching an approximately 180$^{\circ}$
+field of view and taking photos at a rate of 5 Hz. Applying multiple
+localization and loop-closure algorithms on the raw data collected by
+the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
+  liu2010indoor}, the backpack is localized\footnote{In this paper, we
+  use the terms localization and pose recovery interchangeably, in
+  that they both refer to recovering position and orientation.}  over
+its data collection period. This requires recovering the 6 degrees of
+freedom for the backpack as well as the cameras rigidly mounted on
+it. Once this is complete, the data from the laser range scanners is
+used to generate a 3D point cloud of the surrounding environment, from
+which a 3D planar model is created \cite{sanchez2012point}. This
+model, consisting of 2D polygonal planes in 3D space, along with the
+set of images captured by the backpack's cameras and their noisy 3D
+poses, can be considered the input to our texture mapping problem.
+
+We perform texture mapping on each planar surface independently and in
+parallel. For each surface, we begin by obtaining a set of images that
+spans the entire surface with high resolution imagery. We then use our
+noisy camera poses to project these selected images onto the
+surface. These projections are then refined in 2D, in order to
+maximally align them with the surface's geometry, as well as to each
+other, allowing us to handle both errors in geometry as well as camera
+poses. For surfaces and camera poses at any location or orientation,
+we demonstrate a simple tile-based approach for sampling
+high-resolution portions of images and compositing them into a
+texture. In cases where cameras have consistently perpendicular
+viewing angles, we demonstrate a superior approach that leads to more
+seamless textures.
 
@@
 \ref{sec:simpleTextureMapping} explains how images are projected onto
-our geometry and explains a simple approach towards selecting images
-for texturing. Section \ref{sec:existingApproaches} covers existing
-approaches to image stitching, and their performance on our
-datasets. Section \ref{sec:2dAlignment} contains our approach towards
-efficient 2D image alignment, followed by Section
-\ref{sec:imageCompositing}, which describes our two methods of
-compositing images. Section \ref{sec:resultsAndConclusions} contains
+geometry and shows a simple texture mapping procedure. Section
+\ref{sec:existingApproaches} covers existing approaches to image
+stitching, and their performance on our datasets. Section
+\ref{sec:2dAlignment} contains our approach towards efficient 2D image
+alignment, followed by Section \ref{sec:imageCompositing}, which
+describes two methods of selecting and compositing images to create
+the final texture. Section \ref{sec:resultsAndConclusions} contains
 results and conclusions.
@@
 
-The geometry of the texture mapping process for a planar surface is
-shown in Figure \ref{fig:projection}.  We are provided with a set of
-$M$ images to texture a target plane, where each image has a camera
-matrix $P_i$ for $i=1..M$, which translates a 3D point in the world
-coordinate system to a 2D point or pixel in image $i$'s coordinates. A
-camera matrix $P_i$ is composed of the camera's intrinsic parameters,
-containing focal length and image center, as well as extrinsic
-parameters which specify the rotation and translation of the camera's
-position in 3D world coordinates at the time that image $i$ is
-taken. These extrinsic parameters are determined by the backpack
-hardware and localization algorithms \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure} and are substantially noisy.
+Before describing our texture mapping procedure, we use this section
+to explain basic texture mapping and a method for selecting images for
+texturing. The geometry of the texture mapping process for a planar
+surface is shown in Figure \ref{fig:projection}.  Given a set of $M$
+images to texture a target plane, camera matrix $P_i$ for the $ith$
+image, translates a 3D point in the world coordinate system to a 2D
+point or pixel in image $i$'s coordinates. A camera matrix $P_i$ is
+composed of the camera's intrinsic parameters, containing focal length
+and image center, as well as extrinsic parameters which specify the
+rotation and translation of the camera's position in 3D world
+coordinates at the time that image $i$ is taken. These extrinsic
+parameters are determined by the backpack hardware and localization
+algorithms \cite{chen2010indoor, liu2010indoor, kua2012loopclosure}
+and are substantially noisy.
 
-Because our backpack system takes photos at a rate of 5 Hz, hundreds
-of images are available for texturing each surface in our model. Our
-goal in designing a texture mapping process is to decide which of
-these images should be used, and where their contents should map onto
-the final texture, in order to minimize any visual discontinuities or
-seams that would suggest that the plane's texture is not composed of a
-single continuous image.
+Because the backpack system takes pictures at a rate of 5 Hz, hundreds
+of images are available for texturing each surface in the model. Our
+objective in designing a texture mapping process is to determine which
+of these images should be used, and where their contents should map
+onto the final texture, in order to minimize any visual
+discontinuities or seams that would suggest that the plane's texture
+is not composed of a single continuous image. In the remainder of this
+section, we provide an overview of a simple tile-based texture mapping
+procedure.
 
@@
 
-\subsection{Tile-based Texture Mapping}
-\label{sec:tileBasedMapping}
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-a simple texturing approach can be performed by discretizing the
-target plane into small square tiles, and choosing an image to texture
-each tile directly.
-
-We choose to work with rectangular units to ensure that borders
-between any two distinct images in the final texture are either
-horizontal or vertical. Since most strong environmental features
-inside buildings are horizontal or vertical, any visible seams in our
-texture will intersect them minimally and be less noticeable.
+the most straightforward approach is to discretize the target plane
+into small square tiles, and choose an image to texture each tile
+directly. We choose to work with rectangular units to ensure that
+borders between any two distinct images in the final texture are
+either horizontal or vertical. Since most strong environmental
+features inside buildings are horizontal or vertical, any visible
+seams in the texture intersect them minimally and are less noticeable.
 
@@
 a list of candidate images that contain all four of its corners, which
-we can quickly check by projecting $t$ into each image using the $P_i$
+we can rapidly check by projecting $t$ into each image using the $P_i$
 camera matrices. Furthermore, each candidate image must have been
 taken at a time when its camera had a clear line-of-sight to $t$,
-which can be calculated using standard ray-polygon intersection tests
-between the camera location, $t$, and every other plane
+which can be determined using standard ray-polygon intersection tests
+between the camera location, $t$, and every other surface
 \cite{rayintersection}.
@@
 $t$. Since resolution decreases and camera pose errors become more
-extreme over distance, we wish to minimize the distance between
+pronounced with distance, we wish to minimize the distance between
 cameras and the surfaces they texture. Additionally, we desire images
-that are projected perpendicularly onto the plane, maximizing the
-resolution and amount of useful texture available in their
-projections, as well as minimizing any parallax effects due to
-real-world geometry not accurately represented by our digital
-model. In other words, we wish to minimize the angle between the
-tile's normal vector and the camera axis for images selected for
+that are projected perpendicularly, rather than obliquely, onto the
+plane, maximizing the resolution and amount of useful texture
+available in their projections, as well as minimizing any parallax
+effects due to real-world geometry not accurately represented by the
+digital model. In other words, we wish to minimize the angle between
+the tile's normal vector and the camera axis for images selected for
 texturing that tile. These two criteria can be met by maximizing the
 function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ as shown in
-Figure \ref{fig:scoringFunction}. Specifically, $d$ is the distance
-between the centers of a camera and a tile, and $\vec{n}$ and
-$\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively.
+Figure \ref{fig:scoringFunction}, where $d$ is the distance between
+the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
+the directions of the plane's normal and the camera axis respectively.
 
-As Figure \ref{fig:compareAll}(a) demonstrates, there are many image
-boundaries with abrupt discontinuities between tiles, due to
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach results
+in image boundaries with abrupt discontinuities between tiles, due to
 significant misalignment between images, though most of it appears to
-be reconcilable using 2D transforms. Given our high number of input
-images, a better image selection procedure will further improve
-results, as described in Section \ref{sec:imageCompositing}, but a
-more significant and reliable improvement can be found through first
-improving the alignment of our images.
+be reconcilable using 2D transforms. Given the large number of input
+images, it is possible to develop a more sophisticated image selection
+procedure, as described in Section \ref{sec:imageCompositing},
+however, a more significant and reliable improvement can be found
+through first improving the alignment of the images as shown in the
+next 2 sections.
 
@@
 best when multiple unique visual references exist in the environment
-that can be detected in multiple images. In contrast, our indoor
+that can be detected in multiple images. In contrast, indoor
 environments have a high prevalence of bare surfaces, as well as
@@
 
-Additionally, our datasets often contain long chains of images, which
-can lead to large overall error when images are matched together. For
-example, a slight error in image correspondences in the middle of a
-chain could lead to high global error at one or both ends of the
-chain.
+Additionally, our datasets often contain long chains of images,
+corresponding to long hallways and corridors as shown in Figure
+\ref{fig:mosaic3D}, which leads to error accumulation when image
+correspondences are not accurate. For example, when matching a long
+chain of images through homography, a pixel in the $nth$ image must be
+translated into the first image's coordinates by multiplying by the
+$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these
+homography matrices is propagated to all further images, resulting in
+drift.
 
@@
     refinement algorithm, (b) the AutoStitch software package, and (c)
-    our method.}
+    the proposed method.}
   \label{fig:mosaic3D}
@@
 
-Past work with our data acquisition backpack integrated image
-stitching with an iterative localization algorithm, and performed
-homography-based camera pose refinement \cite{liu2010indoor}. When run
-on long chains of images, especially where features are sparse, it
-produces distorted textures, as seen in Figure \ref{fig:mosaic3D}(a),
-due to the problems described above. This approach is also not
-closed-form, and its iterative camera adjustment process over our
-large datasets led to prohibitively long computation time.
+In prior work, we experimented with integrating image stitching with
+an iterative localization algorithm \cite{liu2010indoor}. When run on
+long chains of images, especially where features are sparse, this
+approach produces distorted textures, as seen in Figure
+\ref{fig:mosaic3D}(a). Furthermore, this approach is not closed-form,
+and its iterative camera adjustment process over large datasets led to
+prohibitively long computation time.
 
@@
 even short segments of bare texture. The example in Figure
-\ref{fig:mosaic3D}(b) was generated after manual tuning, and areas
-with fewer visual features or repeating texture patterns simply failed
-outright with AutoStitch.
+\ref{fig:mosaic3D}(b) was generated after many rounds of manual
+tuning, and areas with fewer visual features or repeating texture
+patterns simply failed outright with AutoStitch.
 
-More importantly, neither approach
+\section{2D Image Alignment}
+\label{sec:2dAlignment}
+In this section, we describe our method for efficient and robust image
+alignment. Rather than attempt to register all of our images in 3D, as
+many state-of-the-art techniques for image stitching do, we instead
+select a subset of images that can be aligned in 2D. The subset of
+images we select for alignment and subsequent texturing corresponds to
+the images selected by the tile-based texturing procedure described in
+Section \ref{sec:simpleTextureMapping}.
 
-\section{2d Image Alignment}
-\label{sec:2dAlignment}
+We have found that applying 2D alignments to this set of images works
+well for a few reasons. First, the nature of our input data and the
+selected images is such that localization error chiefly occurs in two
+dimensions, which correspond to the plane of the surface being
+projected onto. This is because our backpack operator, during data
+acquisition, makes efforts to walk within a few meters of, and
+parallel to all walls being scanned. As a result, the translational
+error of camera poses is quite minimal in the dimension perpendicular
+to the surface being textured. Furthermore, because our set of images
+was selected to have minimal distance from our surface, rotational
+errors have a lesser effect, except for rotation around the axis
+perpendicular to the surface being textured. Therefore, the majority
+of both our translation and rotational errors occur in the 2
+dimensions of the surface's plane. This of course does not apply for
+ceilings and floors; however, the lack of features on most ceilings
+and floors means that 3D misalignment does not often have a visible
+effect, beyond what can be fixed in 2D.
 
-In this section, we describe our method of efficient and robust image
-alignment. Though state-of-the-art techniques towards image stitching
-work in 3D, we elect to perform image alignments entirely in
-2D. Besides the benefits of reduced complexity, we have found 2D
-alignment to work well for two main reasons. First, because we have
-such a large number of images to choose from, the compositing
-approaches in Section \ref{sec:imageCompositing} are able to select a
-subset of images that align well, given only 2D alignments. Second,
-the nature of our input data is such that localization error chiefly
-occurs in two dimensions, in the same plane as the surface being
-projected onto. Our data acquisition system contains cameras facing to
-the sides of the operator. The operator makes efforts to walk parallel
-to walls, and the localization and model-generation algorithms that
-provide our input conform the operator's path to be straight and
-parallel to detected surfaces \cite{kua2012loopclosure,
-  sanchez2012point}. Since the operator also walks in a manner to keep
-the backpack balanced, errors in roll and yaw are minimal. Thus, our
-highest errors stem from uncertainty in the operator's pitch,
-equivalent to rotation around the camera axes, as well as location
-along surfaces. These equate to 2D rotation and translation in a
-surface's plane.
-
-Our 2D alignment procedure consists of three parts. First, all images
+Our proposed 2D alignment procedure consists of three parts. First, images
 are projected onto the surface and lines within these projections are
-detected. These lines are then rotated and shifted to match
-geometry-based lines comprising the surface's boundary and
-intersection with other surfaces. Second, occlusion checks are
-performed to remove invalid parts of each image for the target
-surface. These two steps are image-independent and performed in
-parallel. Third, we detect SIFT feature matches between pairs of
-images and solve a weighted linear least squares problem in 2D to
-maximize matches.
+detected.
+These lines are then used to transform images such that they match geometry-based lines composing the boundaries of the surface being textured.
+Second, occlusion checks are performed to remove invalid parts of each image for the target surface.
+Third, SIFT feature matches are detected between pairs of images, and a weighted linear least squares problem is solved in order to maximize all image and geometry-based alignments.
+Each step will now be explained in detail.
 
@@
 \label{sec:geometryAlignment}
-After computing each image's projection onto the target surface, as
-described in Section \ref{sec:simpleTextureMapping}, we detect line
-segments in the image projections using Hough transforms, as shown in
-Figure \ref{fig:geometryAlignment}(a). Experience and intuition show
-that walls in indoor environments often contain linear features that
-are either horizontal or vertical, corresponding to doors, windows,
-posters, etc. Thus, when texturing walls, we rotate images in 2D such
-that dominant lines are made to be horizontal or vertical. This can be
-further generalized by instead orienting lines to be parallel or
-perpendicular with a surface's boundaries, which makes it applicable
-to ceilings and floors, where inner walls and interior features tend
-to be parallel or perpendicular to outer walls.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[height=3in]{detectedLines.png}}
-  \hspace{0.4 cm} \subfloat[][]{\includegraphics[height=3in,
-    width=4in]{bothunalignedaligned.png}}
-  \caption{(a) Lines detected in image projections via Hough
-    transform.  (b) In this example, we project two images at once for
-    the sake of demonstration. Red line segments represent where
-    surfaces intersect, and green line segments are line segments
-    detected in the image. Above are the original projections using
-    input camera poses, and below are the projections after rotation
-    and translation for alignment.}
+  \caption{}
   \label{fig:geometryAlignment}
@@
 
-Furthermore, at this point in time, image occlusions have not been
-accounted for. As a result, some image projections contain texture
-that should project to an adjacent surface, sometimes with a visible
-linear boundary where the two surfaces meet. If this linear boundary
-can be detected by Hough transform, the image is rotated and shifted
-in 2D such that the visual boundary between two surfaces in an image
-projection matches the physical boundary in our digital model. An
-example of such an adjustment is in Figure
-\ref{fig:geometryAlignment}(b) and \ref{fig:geometryAlignment}(c).
+After computing each image's projection onto the target surface, as
+described in Section \ref{sec:simpleTextureMapping}, we obtain a set
+of image-based line segments by using Hough transforms to detect lines
+in the image projections. We then gather a set of geometry-based
+lines, which correspond to the lines comprising the target surface's
+border, as well as lines formed where other surfaces intersect the
+target surface. An example of these lines is shown for a ceiling
+surface in Figure \ref{fig:geometryAlignment}. Given perfect camera
+poses and surface geometry, the lines in images corresponding to
+corners between surfaces should match up exactly with borders and
+intersections of surfaces. By inducing such lines to match, we fit our
+camera poses more accurately to our surface, and therefore to
+eachother.
 
-To perform these alignments, we use a RANSAC \cite{fischler1981random}
-framework to determine an optimal rotation angle between lines in our
-image and lines in our geometry. RANSAC allows us to ignore erroneous
-lines in our image, such as the slanted lines corresponding to the
-ladder in Figure \ref{fig:geometryAlignment}(a). Once this rotation is
-discovered and applied, we gather all pairs of image line segments and
-geometry line segments with less than $0.1^\circ$ difference in
-orientation and less than 250 mm distance at their furthest points. If
-2 or more pairs exist, we select the 2 that contain the longest
-noncollinear image-based line segments, and perform the corresponding
-fixed translation to match them. If we only have 1 pair, we perform
-the minimal shift to match the lines of that pair, and make note of
-their orientation, for usage in Section
-\ref{sec:robustSIFTFeatureMatching}.
+To perform geometry-based alignment, we collect pairs of image-based
+and geometry-based lines, which are within a distance and orientation
+difference threshold of each other. We have found a distance threshold
+of 250 mm and an orientation difference threshold of $10^\circ$ to
+work well for our datasets. In practice, we rarely have more than 2
+such pairs, but if so, we select the 2 noncollinear pairs with the
+most similar orientation difference and continue. With 2 noncollinear
+pairs, we select the pair with the longer image-based line, and
+perform a rotation of the image such that the lines in that pair
+become parallel. We then perform a translation such that the lines in
+that same pair overlap. This translation has ambiguity in the
+dimension along that line, which is resolved by matching the midpoint
+of the image-based line in the second pair to its corresponding
+geometry-based line. Thus, with 2 or more pairs, we can obtain a fixed
+rotation and translation, which we save for usage in Section
+\ref{sec:robustSIFTFeatureMatching}. If we only have 1 pair, we
+perform a rotation and a minimal translation to match its lines. This
+translation's ambiguity however, can not be resolved, but is saved
+also to be used in Section
+\ref{sec:robustSIFTFeatureMatching}. Finally, in the case where we
+have no matches, we can still perform rotations in order to exploit
+patterns in indoor environments. For instance, doors, windows,
+furniture, etc. all tend to have linear edges that are parallel to the
+edges of the surfaces they are on. Similarly, lights, visible interior
+walls, etc. which are visible in floor and ceiling images, all tend to
+be parallel to exterior walls corresponding to the edges of ceiling
+and floor surfaces. Thus, we choose to minimize the angle between
+image-based lines and any geometry-based line. We do this using the
+RANSAC framework, which successfully ignores outliers
+\cite{fischler1981random}.
+
+After these steps are performed, our image projections line up well with our target surface, as shown in Figure \ref{fig:geometryAlignment}.
+This procedure reconciles both errors in camera poses as well as in geometry, and results in sharp, continuous borders across images, which is crucial when performing occlusion checks.
 
@@
 \label{sec:imageOcclusion}
-Now that images have been aligned to geometry where possible, we
-perform a simple recursive occlusion procedure on each image. This is
-done by performing the intersection tests in Section
-\ref{sec:simpleTextureMapping} in a regularly spaced grid. Where four
+In order to properly texture surfaces such as the one shown in Figure
+\ref{fig:occlusion}, it is important to detect when parts of image
+projections contain texture belonging to other surfaces and should
+therefore not be used. This can be tested by recursively performing
+ray-polygon intersection tests between camera locations and other
+surfaces in a regularly spaced grid \cite{rayintersection}. Where four
 corners of a rectangular region are occluded, texture is
@@
 \label{sec:robustSIFTFeatureMatching}
-Our next step is to align images by searching for corresponding points
-between all pairs of overlapping images. We use feature alignment
-rather than pixel or intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lowe1999object,
-  mikolajczyk2005performance, szeliski2006image}.  We use SiftGPU
-\cite{siftgpu} for its high performance on both feature detection as
-well as pairwise matching. These matches determine $dx$ and $dy$
-distances between each pair of features for two image projections,
-though these distances may not always be the same for different
-features. Since indoor environments often contain repetitive features
-such as floor tiles or doors, we need to ensure that SIFT-based
-distances are reliable. First, we only perform alignment on parts of
-images that overlap given the original noisy poses. Second, we discard
-feature matches that correspond to an image distance greater than 200
-mm from what the noisy poses estimate. In order to utilize the
-remaining feature matches robustly, RANSAC \cite{fischler1981random}
-is again used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$
-distances between two images $i$ and $j$. We use a 5 mm threshold for
-RANSAC, so that SIFT matches are labeled as outliers if their distance
-is not within 5 mm of the sampled average distance.
+Our next step is to align images to each other by searching for
+corresponding feature points between all pairs of overlapping
+images. We use feature alignment rather than pixel or intensity-based
+alignment due to the differences in lighting as well as possible
+occlusion among our images, both of which feature alignment is less
+sensitive to \cite{lowe1999object, mikolajczyk2005performance,
+  szeliski2006image}.  We use SiftGPU \cite{siftgpu} for its high
+performance on both feature detection as well as pairwise
+matching. These matches determine $dx$ and $dy$ distances between each
+pair of features for two image projections, though these distances may
+not always be the same for different features. Since indoor
+environments often contain repetitive features such as floor tiles or
+doors, we need to ensure that SIFT-based distances are
+reliable. First, we only perform alignment on parts of images that
+overlap given the original noisy poses. Second, we discard feature
+matches that correspond to an image distance greater than 200 mm from
+what the noisy poses estimate. In order to utilize the remaining
+feature matches robustly, RANSAC \cite{fischler1981random} is again
+used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances
+between two images $i$ and $j$. We use a 5 mm threshold for RANSAC, so
+that SIFT matches are labeled as outliers if their distance is not
+within 5 mm of the sampled average distance.
 
-We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
-of images, as well as our previous geometry alignment results to refine their positions using weighted linear least
-squares. The variables we wish to solve for are the $x_i$ and $y_i$
-positions of our images, while our equations are the SIFT-based
-distances between pairs of images, images fixed to geometry with 0 or
-1 degrees of freedom, and the original camera poses. An example setup for
-solving our weighted linear least squares problem $\textrm{min}_{\vec{\beta}} ||W^\frac{1}{2}(A \vec{\beta} -
-\vec{\gamma})||_2^2 $ with 3 images is shown below.
+We now use the feature-based distances between each pair of images as
+well as our previous geometry alignment results to refine all image
+positions using a weighted linear least squares solution. The
+variables we wish to solve for are the $x_i$ and $y_i$ positions of
+images, while equations are the feature-based distances between pairs
+of images, images fixed to geometry with 0 or 1 degrees of freedom,
+and the original noisy camera poses. The original camera poses are
+needed because we sometimes are not able to detect feature matches in
+all of our images, or we lack enough geometry alignment results to
+generate a single solution. Because we want to minimally use our
+original poses, we give them a weighting factor of $0.01$, while all
+other equations are weighted at $1$. An example setup for a weighted
+linear least squares problem $\textrm{min}_{\vec{\beta}}
+||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
+shown below.
 
@@
 
-In this scenario, a SIFT-based distance of $dx_{1,2}$, $dy_{1,2}$ was
-calculated between images 1 and 2. This corresponds to the first and
-second row of $A$, while the third and fourth row of $A$ represent the
-same for images 2 and 3. Row 5 corresponds to a constraint of image 2's location to a line of slope $m_2$, passing through point $gx_2$, $gy_2$. 
-Row 6 and 7 do stuff and 8 and 9 ensure that we are not rank deficient in case of whatever.
-
- Rows 5 and 6 of $A$ correspond to a fixed
-location of $tx_1$, $ty_1$ for image 1, while Row 7 corresponds to a
-constraint to a line of slope $m$, with current location $tx_2$,
-$ty_2$, both possible results of the geometry alignment procedure in
-Section \ref{sec:geometryAlignment}. If we do not have enough SIFT
-matches, or lack images matched to geometry, our matrix becomes
-rank-deficient and our problem cannot be solved. As a result, we add
-rows for each image corresponding to the original noisy image
-locations, and downweight them heavily, e.g. with a weight of 0.01
-versus 1.
+In this scenario, a feature-based distance of $dx_{1,2}$, $dy_{1,2}$
+was calculated between images 1 and 2. This corresponds to the first
+and second row of $A$, while the third and fourth row of $A$ represent
+the same for images 2 and 3. Rows 5 through 7 correspond to results of
+the geometry alignment procedure in Section
+\ref{sec:geometryAlignment}. Specifically, row 5 corresponds to a
+geometry-based constraint of image 2's location to a line of slope
+$m_2$, passing through point $gx_2$, $gy_2$, while rows 6 and 7
+correspond to a fixed location for image 1 without any degrees of
+freedom. Rows 8 and 9 correspond to the original camera pose for image
+1, and original poses for images 2 and 3 are omitted for brevity.
 
@@
 mechanism to reduce image boundaries. This method works well given all
-manner of camera poses and surfaces, but for optimal cases where we
-have large sections of usable texture from images, we propose a
-superior method that further reduces image boundaries.
+manner of camera poses and surfaces, but for optimal cases where
+images have consistently perpendicular viewing angles, we propose a
+superior method that selectively reduces image boundaries.
 
@@
 texturing method, though over 75\% of that time is spent calculating
-SIFT matches within the SiftGPU framework. While not real-time, the
+SIFT matches within the SiftGPU framework, which could feasibly be
+split into a separate preprocessing step. While not real-time, the
 process is capable of generating quick updates after changes in
@@
 
-\subsection{Future Work}
-While our method works well on our datasets, it is heavily reliant on
-having a large number of input images, and minimal non-2D error. A
-technique for resolving camera error in 3D that would mesh well with
-our approach is to perform matching between image lines and geometry
-in 3D, which can be done reasonably efficiently \cite{linebased,
+While our method works well on our datasets, it is likely to fail in
+areas where 3D error is much higher. A technique for resolving camera
+error in 3D that would be a logical progression of our approach is to
+perform 3D matching between image lines and geometry in 3D, which can
+be done reasonably efficiently \cite{linebased,
   rectangularstructures}. Using linear features on top of our SIFT
@@
 scenes often have long, unbroken lines spanning multiple images
-\cite{linearposeestimation}. Finally, our blending approach is quite
+\cite{linearposeestimation}. Finally, our blending procedure is very
 basic, and applying more sophisticated methods of blending as well as

### 2013-02-04 spie/_region_.tex
few more changes remaining

--- 2013-01-20 spie/_region_.tex
@@
 
-\message{ !name(paper.tex) !offset(371) }
-\subsection{2D Feature Alignment}
-\label{sec:robustSIFTFeatureMatching}
-Our next step is to align images by searching for corresponding points
-between all pairs of overlapping images. We use feature alignment
-rather than pixel or intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lowe1999object,
-  mikolajczyk2005performance, szeliski2006image}.  We use SiftGPU
-\cite{siftgpu} for its high performance on both feature detection as
-well as pairwise matching. These matches determine $dx$ and $dy$
-distances between each pair of features for two image projections,
-though these distances may not always be the same for different
-features. Since indoor environments often contain repetitive features
-such as floor tiles or doors, we need to ensure that SIFT-based
-distances are reliable. First, we only perform alignment on parts of
-images that overlap given the original noisy poses. Second, we discard
-feature matches that correspond to an image distance greater than 200
-mm from what the noisy poses estimate. In order to utilize the
-remaining feature matches robustly, RANSAC \cite{fischler1981random}
-is again used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$
-distances between two images $i$ and $j$. We use a 5 mm threshold for
-RANSAC, so that SIFT matches are labeled as outliers if their distance
-is not within 5 mm of the sampled average distance.
+\message{ !name(paper.tex) !offset(395) }
+\subsection{Image Occlusion}
+\label{sec:imageOcclusion}
 
-We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
-of images to refine their positions using weighted linear least
-squares. The variables we wish to solve for are the $_ix$ and $y_i$
-positions of our images, while our equations are the SIFT-based
-distances between pairs of images, images fixed to geometry with 0 or
-1 degrees of freedom, and the original camera poses. Ignoring
-weighting and the original camera poses for now, an example setup for
-solving $\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
-\vec{\gamma}||_2^2 $ with 3 images is shown below.
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.jpg}}
+  \hspace{0.4cm} \subfloat[][]{\includegraphics[width=3in, height=1.8in]{occlusionimages.png}}
+  \caption{(a) The green image contains texture that belongs to the red surface, which should not be projected onto the blue target surface.
+(b) Above, without geometry alignment, texture to the left of the red line would be removed, which would leave some erroneous texture projected onto our target surface.
+Below, after geometry alignment, the correct amount of texture is removed.}
+  \label{fig:occlusion}
+\end{figure}
 
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & -1 & 1 & 0\\
-  0 & -1 & 1 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & -1 & 1\\
-  1 & 0 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 1 & 0 & 0\\
-  0 & -m & 0 & 0 & 1 & 0\\
-\end{pmatrix}\quad
-\vec{\beta} =
-\begin{pmatrix}
-  x_1, \\ x_2, \\ x_3, \\ y_1, \\ y_2, \\ y_3
-\end{pmatrix}
-\vec{\gamma} =
-\begin{pmatrix}
-  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ t1_x, \\ t1_y, \\ -mx_2 +
-  ty_2
-\end{pmatrix}
-\]
+In order to properly texture surfaces such as the one shown in Figure
+\ref{fig:occlusion}, it is important to detect when parts of image
+projections contain texture belonging to other surfaces and should
+therefore not be used. This can be tested by recursively performing
+ray-polygon intersection tests between camera locations and other
+surfaces in a regularly spaced grid \cite{rayintersection}. Where four
+corners of a rectangular region are occluded, texture is
+removed. Where no corners are occluded, the recursion stops. Where
+there is a mixture of both, the rectangular region is subdivided into
+four, and the same process is performed on each. By performing Section
+\ref{sec:geometryAlignment}'s alignment procedure before occlusion,
+texture belonging to other surfaces is accurately removed, which is
+necessary for the next section.
 
-In this scenario, a SIFT-based distance of $dx_{1,2}$, $dy_{1,2}$ was
-calculated between images 1 and 2. This corresponds to the first and
-second row of $A$, while the third and fourth row of $A$ represent the
-same for images 2 and 3. Rows 5 and 6 of $A$ correspond to a fixed
-location of $tx_1$, $ty_1$ for image 1, while Row 7 corresponds to a
-constraint to a line of slope $m$, with current location $tx_2$,
-$ty_2$, both possible results of the geometry alignment procedure in
-Section \ref{sec:geometryAlignment}. If we do not have enough SIFT
-matches, or lack images matched to geometry, our matrix becomes
-rank-deficient and our problem cannot be solved. As a result, we add
-rows for each image corresponding to the original noisy image
-locations, and downweight them heavily, e.g. with a weight of 0.01
-versus 1.
-
-Because our problem is linear, it is easily and quickly solved, and
-after applying the resulting shifts, our images overlap and match each
-other with far greater accuracy. Applying the simple mapping scheme in
-Section \ref{sec:tileBasedMapping} to the same wall used in that
-section results in Figure \ref{fig:compareAll}(b), which has far fewer
-discontinuities, though errors due to lighting differences and
-parallax effects are still visible.
-
-\message{ !name(paper.tex) !offset(668) }
+\message{ !name(paper.tex) !offset(791) }
 

### 2013-02-04 spie/paper.tex
few more changes remaining

@@
   \centering
-  \caption{}
+  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
+
+  \caption{Images projected onto a ceiling surface, where geometry-based lines corresponding to the ceiling's boundary are shown in red.
+Image-based lines detected by Hough transform in the image projections are shown in blue.
+(a) shows images projected with their original noisy camera poses, while (b) is after images have been aligned to maximize line matches between images and geometry.}
   \label{fig:geometryAlignment}
@@
 \label{sec:imageOcclusion}
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.jpg}}
+  \hspace{0.4cm} \subfloat[][]{\includegraphics[width=3in, height=1.8in]{occlusionimages.png}}
+  \caption{(a) The green image contains texture that belongs to the red surface, which should not be projected onto the blue target surface.
+(b) Above, without geometry alignment, texture to the left of the red line would be removed, which would leave some erroneous texture projected onto our target surface.
+Below, after geometry alignment, the correct amount of texture is removed.}
+  \label{fig:occlusion}
+\end{figure}
+
 In order to properly texture surfaces such as the one shown in Figure

### 2013-03-03 spie/_region_.tex
first revision of revisions

@@
 
-\author{Peter Cheng, Michael Anderson, Stewart He, Avideh Zakhor
+\author{Peter Cheng, Michael Anderson, Stewart He, and Avideh Zakhor
 \skiplinehalf
@@
 
-\message{ !name(paper.tex) !offset(395) }
-\subsection{Image Occlusion}
-\label{sec:imageOcclusion}
+\message{ !name(paper.tex) !offset(467) }
+\subsection{2D Feature Alignment}
+\label{sec:robustSIFTFeatureMatching}
+The next step is to align the selected images from Section
+\ref{sec:simpleTextureMapping} for each surface to each other by
+searching for corresponding feature points between all pairs of
+overlapping images. We use feature alignment rather than pixel or
+intensity-based alignment due to the differences in lighting as well
+as possible occlusion among images, both of which feature alignment is
+less sensitive to \cite{lowe1999object, mikolajczyk2005performance,
+  szeliski2006image}. We use SiftGPU \cite{siftgpu} for its high
+performance on both feature detection as well as pairwise
+matching. These matches determine $dx$ and $dy$ distances between each
+pair of features for two image projections, though these distances may
+not always be the same for different features. Since indoor
+environments often contain repetitive features such as floor tiles or
+doors, we need to ensure that SIFT-based distances are
+reliable. First, we only align parts of images that overlap given the
+original noisy poses. Second, we discard feature matches that
+correspond to an image distance greater than 200 mm from what the
+noisy poses estimate. In order to utilize the remaining feature
+matches robustly, RANSAC \cite{fischler1981random} is again used to
+estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
+images $i$ and $j$. We use a 5 mm threshold for RANSAC, so that SIFT
+matches are labeled as outliers if their distance is not within 5 mm
+of the sampled average distance.
 
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.jpg}}
-  \hspace{0.4cm} \subfloat[][]{\includegraphics[width=3in, height=1.8in]{occlusionimages.png}}
-  \caption{(a) The green image contains texture that belongs to the red surface, which should not be projected onto the blue target surface.
-(b) Above, without geometry alignment, texture to the left of the red line would be removed, which would leave some erroneous texture projected onto our target surface.
-Below, after geometry alignment, the correct amount of texture is removed.}
-  \label{fig:occlusion}
-\end{figure}
+We now use the feature-based distances between each pair of images as
+well as geometry alignment results from Section
+\ref{sec:geometryAlignment} to refine all image positions using a
+weighted linear least squares approach. An example setup for a
+weighted linear least squares problem $\textrm{min}_{\vec{\beta}}
+||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
+as follows.
 
-In order to properly texture surfaces such as the one shown in Figure
-\ref{fig:occlusion}, it is important to detect when parts of image
-projections contain texture belonging to other surfaces and should
-therefore not be used. This can be tested by recursively performing
-ray-polygon intersection tests between camera locations and other
-surfaces in a regularly spaced grid \cite{rayintersection}. Where four
-corners of a rectangular region are occluded, texture is
-removed. Where no corners are occluded, the recursion stops. Where
-there is a mixture of both, the rectangular region is subdivided into
-four, and the same process is performed on each. By performing Section
-\ref{sec:geometryAlignment}'s alignment procedure before occlusion,
-texture belonging to other surfaces is accurately removed, which is
-necessary for the next section.
+\[
+A =
+\begin{pmatrix}
+  -1 & 1 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & -1 & 1 & 0\\
+  0 & -1 & 1 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & -1 & 1\\
+  0 & -m_2 & 0 & 0 & 1 & 0\\
+  1 & 0 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 1 & 0 & 0\\
+  1 & 0 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 1 & 0 & 0\\
+  0 & 1 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & 1 & 0\\
+  0 & 0 & 1 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & 0 & 1\\
 
-\message{ !name(paper.tex) !offset(791) }
+\end{pmatrix}\quad
+\vec{\beta} =
+\begin{pmatrix}
+  x_1, \\ x_2, \\ x_3, \\ y_1, \\ y_2, \\ y_3
+\end{pmatrix}
+\vec{\gamma} =
+\begin{pmatrix}
+  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ -m_2gx_2 + gy_2,
+  \\ gx_1, \\ gy_1, \\ tx_1, \\ ty_1, \\ tx_2, \\ ty_2, \\ tx_3, \\
+  ty_3
+
+\end{pmatrix}
+\vec{W} =
+\begin{pmatrix}
+  1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 0.01, \\ 0.01, \\ 0.01, \\
+  0.01, \\ 0.01, \\ 0.01
+\end{pmatrix}
+\]
+
+The variables we wish to solve for are the $x_i$ and $y_i$ positions
+of images, while equations are the feature-based distances between
+pairs of images, images fixed to geometry with 0 or 1 degrees of
+freedom, and the original noisy camera poses. In this scenario, a
+feature-based distance of $dx_{1,2}$, $dy_{1,2}$ was calculated
+between images 1 and 2. This corresponds to the first and second row
+of $A$, while the third and fourth row of $A$ represent the same for
+images 2 and 3. Rows 5 through 7 correspond to results of the geometry
+alignment procedure in Section
+\ref{sec:geometryAlignment}. Specifically, row 5 corresponds to a
+geometry-based constraint of image 2's location to a line of slope
+$m_2$, passing through point $gx_2$, $gy_2$, while rows 6 and 7
+correspond to a fixed location for image 1 without any degrees of
+freedom. Rows 8 through 13 correspond to the original camera poses for
+each image ($tx_i,ty_i$).
+
+The original camera poses are needed because we sometimes are not able
+to detect feature matches in all of our images, or we lack enough
+geometry alignment results to generate a single solution. Since we
+want to minimally use our original poses, we give them a weighting
+factor of $0.01$, while all other equations are weighted at $1$.
+
+Since this problem is linear, it can be solved efficiently; after
+applying the resulting shifts, images overlap and match each other
+with far greater accuracy. Using the simple tile-based texturing
+scheme from Section \ref{sec:simpleTextureMapping} on these adjusted
+images results in Figure \ref{fig:compareAll}(b), which has far fewer
+discontinuities than in \ref{fig:compareAll}(a), though some 3d error
+as well as lighting differences and parallax effects are still
+visible.
+
+\message{ !name(paper.tex) !offset(767) }
 

### 2013-03-03 spie/paper.tex
first revision of revisions

--- 2013-02-04 spie/paper.tex
@@
   resulting in visible discontinuities when successive images are
-  projected onto a surface for texturing. Existing methods to stitch
-  images together are often computationally expensive and work
-  independently of pose estimates and geometry data. We present a
-  method for texture mapping that reduces complexity by selecting
-  images whose camera poses can be align in 2D. We perform alignment
-  of images to geometry as well as images to each other, which
-  produces visually consistent textures even in the presence of
-  inaccurate surface geometry. We also present two different methods
-  for selecting and compositing images into a single texture,
-  depending on the geometry of the surface being textured. The
-  effectiveness of these methods is demonstrated on a number of different
-  indoor environments.
+  projected onto a surface for texturing. We present a method for
+  texture mapping that starts by selecting images whose camera poses
+  are well-aligned in two dimensions. We then align images to geometry
+  as well as to each other, producing visually consistent textures
+  even in the presence of inaccurate surface geometry and noisy camera
+  poses. The final step is to select and composite images into a
+  texture mosaic. The effectiveness of the proposed method is
+  demonstrated on a number of different indoor environments.
 \end{abstract}
@@
 the environment's geometry. An indoor modeling system must be able to
-recover camera poses within an environment while simultaneously
+recover its pose within an environment while simultaneously
 reconstructing the 3D structure of the environment itself
@@
 cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment.
+within the environment. Mounting such devices on a platform carried by
+an ambulatory human provides unique advantages over vehicular-based
+systems on wheels in terms of agility and portability, but can also
+result in larger localization error \cite{liu2010indoor}. As a result,
+common methods for texture mapping generally produce poor results.
 
-Mounting such devices on a platform carried by an ambulatory human
-provides unique advantages over vehicular-based systems on wheels in
-terms of agility and portability, but can also result in larger
-localization error \cite{liu2010indoor}. As a result, common methods
-for texture mapping generally produce poor results.
-
-In this paper, we present a number of approaches to texture mapping 3D
-models of indoor environments made of planar surfaces in the presence
-of uncertainty and noise in camera poses. In particular, we consider
-data obtained from a human-operated backpack system with a number of
-laser range scanners as well as 2 cameras facing left and right, each
+In this paper, we present an approach to texture mapping 3D models of
+indoor environments made of planar surfaces in the presence of
+uncertainty and noise in camera poses. In particular, we consider data
+obtained from a human-operated backpack system with a number of laser
+range scanners as well as 2 cameras facing left and right, each
 equipped with fisheye lenses reaching an approximately 180$^{\circ}$
@@
 its data collection period. This requires recovering the 6 degrees of
-freedom for the backpack as well as the cameras rigidly mounted on
-it. Once this is complete, the data from the laser range scanners is
-used to generate a 3D point cloud of the surrounding environment, from
-which a 3D planar model is created \cite{sanchez2012point}. This
+freedom for the backpack itself as well as the cameras rigidly mounted
+on it. Once this is complete, the data from the laser range scanners
+is used to generate a 3D point cloud of the surrounding environment,
+from which a 3D planar model is created \cite{sanchez2012point}. This
 model, consisting of 2D polygonal planes in 3D space, along with the
@@
 
-We perform texture mapping on each planar surface independently and in
-parallel. For each surface, we begin by obtaining a set of images that
-spans the entire surface with high resolution imagery. We then use our
-noisy camera poses to project these selected images onto the
-surface. These projections are then refined in 2D, in order to
-maximally align them with the surface's geometry, as well as to each
-other, allowing us to handle both errors in geometry as well as camera
-poses. For surfaces and camera poses at any location or orientation,
-we demonstrate a simple tile-based approach for sampling
-high-resolution portions of images and compositing them into a
-texture. In cases where cameras have consistently perpendicular
-viewing angles, we demonstrate a superior approach that leads to more
-seamless textures.
+\begin{figure}
+  \centering
+  \includegraphics[trim=0cm 3cm 0cm 0cm, clip=true,
+  width=6in]{flowchart.jpg}
+  \caption{The proposed texture mapping procedure\\}
+  \label{fig:flowchart}
+\end{figure}
+
+The overall block diagram for the proposed texture mapping procedure
+is shown in Figure \ref{fig:flowchart}. We texture map each planar
+surface independently and in parallel. For each surface, we begin by
+obtaining a set of images that spans the entire surface with high
+resolution imagery. We then use our noisy camera poses to project
+these selected images onto the surface. These projections are then
+refined in 2D, in order to maximally align them with the surface's
+geometry, as well as to each other, allowing us to handle both errors
+in geometry as well as camera poses. For surfaces and camera poses at
+arbitrary locations or orientations, generally ceilings and floors, we
+propose a tile-based approach for sampling high-resolution portions of
+images and compositing them into a texture. In cases where cameras
+have consistently perpendicular viewing angles to the surfaces under
+consideration, generally walls, we demonstrate a superior approach
+that leads to more seamless textures.
 
 The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} explains how images are projected onto
-geometry and shows a simple texture mapping procedure. Section
 \ref{sec:existingApproaches} covers existing approaches to image
 stitching, and their performance on our datasets. Section
-\ref{sec:2dAlignment} contains our approach towards efficient 2D image
+\ref{sec:simpleTextureMapping} explains how to downsample the set of
+available images by selecting those with the best orientation and
+distance from surfaces under consideration. Section
+\ref{sec:2dAlignment} contains our approach towards 2D image
 alignment, followed by Section \ref{sec:imageCompositing}, which
 describes two methods of selecting and compositing images to create
-the final texture. Section \ref{sec:resultsAndConclusions} contains
-results and conclusions.
+the final texture. Sections \ref{sec:results} and \ref{sec:conclusion}
+contain results and conclusions.
 
@@
 
-\section{Simple Texture Mapping}
+\section{Existing Approaches to Image Alignment}
+\label{sec:existingApproaches}
+There are many existing approaches to stitching together multiple
+images to produce a larger, seamless image \cite{szeliski2006image,
+  agarwalapanoramas, wangmultipleviews, coorg1997matching,
+  debevechybrid, bernardinimultiplescans}. Generally, parts of images
+are matched to each other, either through direct comparisons or
+feature detection and matching. Images are then transformed to
+maximize matches, often by computing homographies between pairs of
+images, or by iteratively adjusting camera poses in 1 to 6 degrees of
+freedom.
+
+Feature matching has a number of advantages over direct matching that
+make it more suitable for our often non-planar environments, and
+rotational differences between camera poses
+\cite{szeliski2006image}. Feature matching however, works best when
+multiple unique visual references exist in the environment that can be
+detected in multiple images. In contrast, indoor environments have a
+high prevalence of bare surfaces, as well as repeating textures, such
+as similar windows, doors, and wall-mounted decorations, that are
+difficulte to disambiguate. This lack of reliable reference points
+often results in errors when matching images together.
+
+Additionally, our datasets often contain long chains of images,
+corresponding to long hallways and corridors as shown in Figure
+\ref{fig:mosaic3D}, which leads to error accumulation when image
+correspondences are not accurate. For example, when matching a long
+chain of images through homography, a pixel in the $nth$ image must be
+translated into the first image's coordinates by multiplying by the
+$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these
+homography matrices is propagated to all further images, resulting in
+drift.
+
+\begin{figure}
+  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 20cm 0cm,
+    clip=true, width=6in, height=0.7in]{graphApproach.jpg}}
+
+  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 15cm 0cm,
+    clip=true, width=6in, height=0.7in]{autostitchResult.jpg}}
+
+  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 75cm 0cm,
+    clip=true, width=6in, height=0.7in]{finalLong.jpg}}
+
+  \caption{Texture alignment via (a) the graph-based localization
+    refinement algorithm, (b) the AutoStitch software package, and (c)
+    the proposed method.}
+  \label{fig:mosaic3D}
+\end{figure}
+
+In prior work, we have experimented with integrating image stitching
+with the iterative global localization algorithm used to recover the 6
+degrees of freedom of the backpack acquisition system
+\cite{liu2010indoor}. When run on long chains of images, especially
+where features are sparse, this approach produces distorted textures,
+as seen in Figure \ref{fig:mosaic3D}(a). Furthermore, this approach is
+not closed-form, and its iterative camera adjustment process over
+large datasets led to prohibitively long computation time.
+
+The AutoStitch software package performs homography-based alignment as
+well, with additional provisions that attempt to reduce drift and
+increase efficiency \cite{panorama2d, autostitch}. Though AutoStitch
+performs well in areas with dense features, it can not handle areas
+without features, and has trouble aligning wall sections with even
+short segments of bare texture. The example in Figure
+\ref{fig:mosaic3D}(b) has been generated after many rounds of manual
+tuning; we have empirically found that areas with fewer visual
+features or repeating texture patterns simply failed outright with
+AutoStitch.
+
+\section{Image Selection}
 \label{sec:simpleTextureMapping}
 
-Before describing our texture mapping procedure, we use this section
-to explain basic texture mapping and a method for selecting images for
-texturing. The geometry of the texture mapping process for a planar
-surface is shown in Figure \ref{fig:projection}.  Given a set of $M$
-images to texture a target plane, camera matrix $P_i$ for the $ith$
-image, translates a 3D point in the world coordinate system to a 2D
-point or pixel in image $i$'s coordinates. A camera matrix $P_i$ is
-composed of the camera's intrinsic parameters, containing focal length
-and image center, as well as extrinsic parameters which specify the
-rotation and translation of the camera's position in 3D world
-coordinates at the time that image $i$ is taken. These extrinsic
-parameters are determined by the backpack hardware and localization
+The geometry of the texture mapping process for a planar surface is
+shown in Figure \ref{fig:projection}. Given a set of $M$ images to
+texture a target plane, camera matrix $P_i$ for the $ith$ image
+transforms a 3D point in the world coordinate system to a 2D point or
+pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
+the camera's intrinsic parameters, containing focal length and image
+center, as well as extrinsic parameters which specify the rotation and
+translation of the camera's position in 3D world coordinates at the
+time that image $i$ is taken. These extrinsic parameters are
+determined by the backpack hardware and the corresponding localization
 algorithms \cite{chen2010indoor, liu2010indoor, kua2012loopclosure}
-and are substantially noisy.
+and are noisy.
 
-Because the backpack system takes pictures at a rate of 5 Hz, hundreds
-of images are available for texturing each surface in the model. Our
-objective in designing a texture mapping process is to determine which
-of these images should be used, and where their contents should map
-onto the final texture, in order to minimize any visual
-discontinuities or seams that would suggest that the plane's texture
-is not composed of a single continuous image. In the remainder of this
-section, we provide an overview of a simple tile-based texture mapping
-procedure.
+Since the backpack system takes pictures at a rate of 5 Hz, hundreds
+of images are available for texturing each surface in the 3D
+model. Our objective in designing a texture mapping process is to
+determine which of these images should be used, and where their
+contents should map onto the final texture, in order to minimize any
+visual discontinuities or seams that would suggest that the plane's
+texture is not composed of a single continuous image. In the remainder
+of this section, we propose an image selection criteria and use it to
+derive a simple tile-based texture mapping procedure.
 
@@
 Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-the most straightforward approach is to discretize the target plane
-into small square tiles, and choose an image to texture each tile
-directly. We choose to work with rectangular units to ensure that
+a straightforward approach for texturing is to discretize the target
+plane into small square tiles, and choose an image to texture each
+tile directly. We choose to work with rectangular units to ensure that
 borders between any two distinct images in the final texture are
-either horizontal or vertical. Since most strong environmental
-features inside buildings are horizontal or vertical, any visible
-seams in the texture intersect them minimally and are less noticeable.
+either horizontal or vertical. Since most environmental features
+inside buildings are horizontal or vertical, any visible seams in the
+texture intersect them minimally and are therefore less noticeable.
 
 In order to select an image for texturing a tile $t$, we first gather
-a list of candidate images that contain all four of its corners, which
-we can rapidly check by projecting $t$ into each image using the $P_i$
-camera matrices. Furthermore, each candidate image must have been
-taken at a time when its camera had a clear line-of-sight to $t$,
+a list of candidate images that contain all four of its corners; we
+can rapidly check this by projecting $t$ into each image using the
+$P_i$ camera matrices. Furthermore, each candidate image must have
+been taken at a time when its camera had a clear line-of-sight to $t$,
 which can be determined using standard ray-polygon intersection tests
@@
 effects due to real-world geometry not accurately represented by the
-digital model. In other words, we wish to minimize the angle between
-the tile's normal vector and the camera axis for images selected for
-texturing that tile. These two criteria can be met by maximizing the
-function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ as shown in
-Figure \ref{fig:scoringFunction}, where $d$ is the distance between
-the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-the directions of the plane's normal and the camera axis respectively.
+digital 3D model. In other words, we wish to minimize the angle
+between the tile's normal vector and the camera axis for images
+selected for texturing that tile. These two criteria can be met by
+maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
+as shown in Figure \ref{fig:scoringFunction}, where $d$ is the
+distance between the centers of a camera and a tile, and $\vec{n}$ and
+$\vec{c}$ are the directions of the plane's normal and the camera axis
+respectively. As Figure \ref{fig:compareAll}(a) demonstrates, this
+approach, when used directly for texturing, results in image
+boundaries with abrupt discontinuities between tiles, due to
+misalignment between images, though most of it appears to be
+reconcilable using 2D transforms.
 
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach results
-in image boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images, though most of it appears to
-be reconcilable using 2D transforms. Given the large number of input
-images, it is possible to develop a more sophisticated image selection
-procedure, as described in Section \ref{sec:imageCompositing},
-however, a more significant and reliable improvement can be found
-through first improving the alignment of the images as shown in the
-next 2 sections.
+While this procedure can be used to generate a texture, it is also
+useful for obtaining a collection of images that can be used as a
+starting point for our proposed texturing procedure, as explained in
+Section \ref{sec:2dAlignment}. For our datasets, this process
+generally selects around 10\% of all the images that could be used for
+texturing the surface. This roughly 10:1 subsampling not only reduces
+computational complexity of the remaining steps, but also selects the
+most preomising images for the remaining steps.
 
-\begin{figure}[H]
+Given the large number of input images, it is possible to develop a
+more sophisticated image selection procedure, as described in Section
+\ref{sec:imageCompositing}, however, a more significant and reliable
+improvement can be found through first improving the alignment of the
+images as shown in the next section.
+
+\begin{figure}
   \centering \subfloat[][]{\includegraphics[width=3.4in,
@@
 
-  \caption{(a): Tile-based texturing. (b): Tile-based texturing after
-    image alignment. (c): Tile-based texturing after image alignment
-    with caching. (d): Shortest path texturing after image
-    alignment). (e,f): Blending applied to (c) and (d). (g,h): Zoomed
+  \caption{(a) Tile-based texturing; (b) Tile-based texturing after
+    image alignment; (c) Tile-based texturing after image alignment
+    with caching; (d) Shortest path texturing after image
+    alignment; (e,f) Blending applied to (c) and (d); (g,h) Zoomed
     in views of discontinuities in (e) vs. in (f).}
@@
 
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-Stitching together multiple images to produce a larger, seamless image
-is a commonly performed task, with many successful approaches over the
-past years. Generally, parts of images are matched to each other,
-usually through direct comparisons or feature detection and
-matching. Images are then transformed to maximize matches, often by
-calculating homographies between pairs of images, or by iteratively
-adjusting camera poses in 1 to 6 degrees of freedom.
-
-Feature matching has a number of advantages over direct matching that
-make it more suitable for our often non-planar data, and rotational
-differences \cite{szeliski2006image}. Feature matching however, works
-best when multiple unique visual references exist in the environment
-that can be detected in multiple images. In contrast, indoor
-environments have a high prevalence of bare surfaces, as well as
-repeating textures, such as similar windows, doors, and wall-mounted
-decorations, that cause difficulty in disambiguating features. This
-lack of reliable reference points often results in errors when
-matching images together.
-
-Additionally, our datasets often contain long chains of images,
-corresponding to long hallways and corridors as shown in Figure
-\ref{fig:mosaic3D}, which leads to error accumulation when image
-correspondences are not accurate. For example, when matching a long
-chain of images through homography, a pixel in the $nth$ image must be
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these
-homography matrices is propagated to all further images, resulting in
-drift.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{graphApproach.jpg}}
-
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{autostitchResult.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=6in]{finalLong.jpg}}
-
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm, (b) the AutoStitch software package, and (c)
-    the proposed method.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-In prior work, we experimented with integrating image stitching with
-an iterative localization algorithm \cite{liu2010indoor}. When run on
-long chains of images, especially where features are sparse, this
-approach produces distorted textures, as seen in Figure
-\ref{fig:mosaic3D}(a). Furthermore, this approach is not closed-form,
-and its iterative camera adjustment process over large datasets led to
-prohibitively long computation time.
-
-The AutoStitch software package performs homography-based alignment as
-well, with additional provisions that attempt to reduce drift and
-increase efficiency \cite{panorama2d, autostitch}. Though AutoStitch
-also performs well in areas with dense features, it can not handle
-areas without features, and has trouble aligning wall sections with
-even short segments of bare texture. The example in Figure
-\ref{fig:mosaic3D}(b) was generated after many rounds of manual
-tuning, and areas with fewer visual features or repeating texture
-patterns simply failed outright with AutoStitch.
-
 \section{2D Image Alignment}
@@
 In this section, we describe our method for efficient and robust image
-alignment. Rather than attempt to register all of our images in 3D, as
-many state-of-the-art techniques for image stitching do, we instead
-select a subset of images that can be aligned in 2D. The subset of
-images we select for alignment and subsequent texturing corresponds to
-the images selected by the tile-based texturing procedure described in
-Section \ref{sec:simpleTextureMapping}.
+alignment. Rather than register all of our images in 3D, as many
+state-of-the-art techniques for image stitching do, we instead select
+a subset of images to be aligned in 2D. This subset corresponds to the
+images selected by the image selection procedure described in Section
+\ref{sec:simpleTextureMapping}.
 
-We have found that applying 2D alignments to this set of images works
-well for a few reasons. First, the nature of our input data and the
-selected images is such that localization error chiefly occurs in two
+Applying 2D alignments to this set of images works well for a number
+of reasons. First, the nature of our input data and the selected
+images is such that localization error chiefly occurs in two
 dimensions, which correspond to the plane of the surface being
-projected onto. This is because our backpack operator, during data
+projected onto. This is because the backpack operator, during data
 acquisition, makes efforts to walk within a few meters of, and
@@
 error of camera poses is quite minimal in the dimension perpendicular
-to the surface being textured. Furthermore, because our set of images
-was selected to have minimal distance from our surface, rotational
-errors have a lesser effect, except for rotation around the axis
-perpendicular to the surface being textured. Therefore, the majority
-of both our translation and rotational errors occur in the 2
-dimensions of the surface's plane. This of course does not apply for
-ceilings and floors; however, the lack of features on most ceilings
-and floors means that 3D misalignment does not often have a visible
-effect, beyond what can be fixed in 2D.
+to the wall surface being textured. Furthermore, because our set of
+images has minimal distance from its corresponding wall surface,
+rotational errors are less pronounced, except for rotation around the
+axis perpendicular to the surface being textured. Therefore, most
+translation and rotational errors occur in the 2 dimensions of the
+wall surface's plane. This of course does not apply for ceilings and
+floors; however, the lack of features on most ceilings and floors
+means that 3D misalignment is not likely to visually make a
+difference, beyond what can be done in 2D.
 
-Our proposed 2D alignment procedure consists of three parts. First, images
-are projected onto the surface and lines within these projections are
-detected.
-These lines are then used to transform images such that they match geometry-based lines composing the boundaries of the surface being textured.
-Second, occlusion checks are performed to remove invalid parts of each image for the target surface.
-Third, SIFT feature matches are detected between pairs of images, and a weighted linear least squares problem is solved in order to maximize all image and geometry-based alignments.
-Each step will now be explained in detail.
+Our proposed 2D alignment procedure consists of three parts. First,
+images are projected onto the surface and lines within these projected
+images are detected. Images are then transformed such that these lines
+match geometric lines composing the boundaries of the surface being
+textured. Second, occlusion checks are performed to remove invalid
+parts of each image for the target surface. Third, SIFT feature
+matches are detected between pairs of images, and a weighted linear
+least squares problem is solved in order to maximize all image and
+geometry-based alignments. Each step will now be explained in detail.
 
@@
   \centering
-  \caption{}
+  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
+
+  \centering
+  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
+
+  \centering \subfloat[][]{\includegraphics[trim=0cm 3cm 0cm 0cm,
+    clip=true, width=5in]{matchlines.jpg}}
+
+  \caption{Images projected onto a ceiling surface, where
+    geometry-based lines corresponding to the ceiling's boundary are
+    shown in red. Image-based lines detected by Hough transform in the
+    image projections are shown in blue; (a) images projected with
+    their original noisy camera poses; (b) after image alignment to
+    maximize line matches between images and geometry; (c) examples of
+    matching lines in cases with $\geq$ 2 line pairs, 1 line pair, and
+    zero line pairs, from top to bottom.}
   \label{fig:geometryAlignment}
@@
 border, as well as lines formed where other surfaces intersect the
-target surface. An example of these lines is shown for a ceiling
-surface in Figure \ref{fig:geometryAlignment}. Given perfect camera
-poses and surface geometry, the lines in images corresponding to
-corners between surfaces should match up exactly with borders and
-intersections of surfaces. By inducing such lines to match, we fit our
-camera poses more accurately to our surface, and therefore to
-eachother.
+target surface. An example of these lines is shown in red for a
+ceiling surface in Figure \ref{fig:geometryAlignment}(a). Ideally, for
+perfect camera poses and surface geometry, the lines in images
+corresponding to corners between surfaces should match up exactly with
+corners in the 3D model. By inducing such lines to match, we fit
+camera poses more accurately to the surface, and to each other as
+well.
 
-To perform geometry-based alignment, we collect pairs of image-based
-and geometry-based lines, which are within a distance and orientation
-difference threshold of each other. We have found a distance threshold
-of 250 mm and an orientation difference threshold of $10^\circ$ to
-work well for our datasets. In practice, we rarely have more than 2
-such pairs, but if so, we select the 2 noncollinear pairs with the
-most similar orientation difference and continue. With 2 noncollinear
-pairs, we select the pair with the longer image-based line, and
-perform a rotation of the image such that the lines in that pair
-become parallel. We then perform a translation such that the lines in
-that same pair overlap. This translation has ambiguity in the
-dimension along that line, which is resolved by matching the midpoint
-of the image-based line in the second pair to its corresponding
-geometry-based line. Thus, with 2 or more pairs, we can obtain a fixed
-rotation and translation, which we save for usage in Section
-\ref{sec:robustSIFTFeatureMatching}. If we only have 1 pair, we
-perform a rotation and a minimal translation to match its lines. This
-translation's ambiguity however, can not be resolved, but is saved
-also to be used in Section
-\ref{sec:robustSIFTFeatureMatching}. Finally, in the case where we
-have no matches, we can still perform rotations in order to exploit
-patterns in indoor environments. For instance, doors, windows,
-furniture, etc. all tend to have linear edges that are parallel to the
+To align images to surface geometry, we collect pairs of image-based
+and geometry-based line segments, which are within a distance and
+angular difference threshold of each other. We have found a distance
+threshold of 250 mm and an orientation difference threshold of
+$10^\circ$ to work well for our datasets. For each pair of lines, we
+compute the angular difference between the pair's image and geometry
+lines. If there are 2 or more pairs with angular differences within
+$1^\circ$, we select the two pairs with the longest noncollinear
+image-based lines, and rotate the image such that the lines in the
+pair with the longest image-based line become parallel. We then find a
+translation such that the lines in that same pair overlap. This
+translation has ambiguity in the dimension along the matched lines,
+which is resolved by matching the midpoint of the image-based line in
+the second pair to its corresponding geometry-based line. Thus, with 2
+or more pairs, it is possible to obtain a fixed rotation and
+translation, which are saved for usage in Section
+\ref{sec:robustSIFTFeatureMatching}.
+
+If there are not 2 or more pairs with similar angular differences, we
+select the pair with the longest image-based line and apply a rotation
+and the minimal translation to match its lines. This translation's
+ambiguity however, can not be resolved, but is also saved to be used
+in Section \ref{sec:robustSIFTFeatureMatching}. Finally, in the case
+where there are no line pairs, we can still rotate images in order to
+exploit patterns in indoor environments. For instance, doors, windows,
+furniture, etc. tend to have linear edges that are parallel to the
 edges of the surfaces they are on. Similarly, lights, visible interior
-walls, etc. which are visible in floor and ceiling images, all tend to
-be parallel to exterior walls corresponding to the edges of ceiling
-and floor surfaces. Thus, we choose to minimize the angle between
-image-based lines and any geometry-based line. We do this using the
-RANSAC framework, which successfully ignores outliers
-\cite{fischler1981random}.
+walls, etc. which are visible in floor and ceiling images, tend to be
+parallel to exterior walls corresponding to the edges of ceiling and
+floor surfaces. Thus, we choose to minimize the angle between
+image-based lines and geometry-based lines. We use the RANSAC
+framework, with an inlier difference of $0.5^\circ$ in order to
+successfully ignore outliers \cite{fischler1981random}.
 
-After these steps are performed, our image projections line up well with our target surface, as shown in Figure \ref{fig:geometryAlignment}.
-This procedure reconciles both errors in camera poses as well as in geometry, and results in sharp, continuous borders across images, which is crucial when performing occlusion checks.
+After these steps, image projections line up well with
+target surfaces, as shown in Figure \ref{fig:geometryAlignment}(b),
+which is considerably more aligned than Figure
+\ref{fig:geometryAlignment}(a) is. This procedure reconciles both
+errors in camera poses as well as in geometry, and results in sharp,
+continuous borders across images, which is crucial when checking for
+occlusion.
 
@@
 \label{sec:imageOcclusion}
-In order to properly texture surfaces such as the one shown in Figure
-\ref{fig:occlusion}, it is important to detect when parts of image
-projections contain texture belonging to other surfaces and should
-therefore not be used. This can be tested by recursively performing
-ray-polygon intersection tests between camera locations and other
-surfaces in a regularly spaced grid \cite{rayintersection}. Where four
-corners of a rectangular region are occluded, texture is
-removed. Where no corners are occluded, the recursion stops. Where
-there is a mixture of both, the rectangular region is subdivided into
-four, and the same process is performed on each. By performing Section
-\ref{sec:geometryAlignment}'s alignment procedure before occlusion,
-texture belonging to other surfaces is accurately removed, which is
-necessary for the next section.
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.png}}
+  \hspace{0.4cm} \subfloat[][]{\includegraphics[width=3in,
+    height=1.8in]{occlusionimages.png}}
+  \caption{(a) The image from the camera in this diagram contains
+    texture that belongs to the grey occluding surface, which should
+    not be projected onto the orange target surface; (b) without
+    geometry alignment, texture to the left of the red line would be
+    removed, which would leave some erroneous texture projected onto
+    our target surface; (c) after geometry alignment, the image is
+    shifted, resulting in the correct amount of texture being
+    removed.}
+  \label{fig:occlusion}
+\end{figure}
+
+In order to correctly texture surfaces, it is important to detect and
+remove parts of image projections containing texture for occluding
+surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
+used to texture the orange target surface also contains part of a grey
+occluding surface. We remove this incorrect texture by recursively
+performing ray-polygon intersection tests between the camera location
+and other surfaces \cite{rayintersection}. These intersection tests
+are performed at the corners of a grid overlaid upon the target
+surface. Where all four corners of a grid section are occluded,
+texture is removed. Where one or more corners are occluded, the grid
+is subdivided into four, and the process repeats. Occlusion checking
+works entirely with geometry, so by ensuring that images match
+geometry using \ref{sec:geometryAlignment}'s alignment procedure,
+texture belonging to other surfaces is accurately removed, as seen in
+Figure \ref{fig:occlusion}(b).
 
@@
 \label{sec:robustSIFTFeatureMatching}
-Our next step is to align images to each other by searching for
-corresponding feature points between all pairs of overlapping
-images. We use feature alignment rather than pixel or intensity-based
-alignment due to the differences in lighting as well as possible
-occlusion among our images, both of which feature alignment is less
-sensitive to \cite{lowe1999object, mikolajczyk2005performance,
+The next step is to align the selected images from Section
+\ref{sec:simpleTextureMapping} for each surface to each other by
+searching for corresponding feature points between all pairs of
+overlapping images. We use feature alignment rather than pixel or
+intensity-based alignment due to the differences in lighting as well
+as possible occlusion among images, both of which feature alignment is
+less sensitive to \cite{lowe1999object, mikolajczyk2005performance,
   szeliski2006image}. We use SiftGPU \cite{siftgpu} for its high
@@
 doors, we need to ensure that SIFT-based distances are
-reliable. First, we only perform alignment on parts of images that
-overlap given the original noisy poses. Second, we discard feature
-matches that correspond to an image distance greater than 200 mm from
-what the noisy poses estimate. In order to utilize the remaining
-feature matches robustly, RANSAC \cite{fischler1981random} is again
-used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances
-between two images $i$ and $j$. We use a 5 mm threshold for RANSAC, so
-that SIFT matches are labeled as outliers if their distance is not
-within 5 mm of the sampled average distance.
+reliable. First, we only align parts of images that overlap given the
+original noisy poses. Second, we discard feature matches that
+correspond to an image distance greater than 200 mm from what the
+noisy poses estimate. In order to utilize the remaining feature
+matches robustly, RANSAC \cite{fischler1981random} is again used to
+estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
+images $i$ and $j$. We use a 5 mm threshold for RANSAC, so that SIFT
+matches are labeled as outliers if their distance is not within 5 mm
+of the sampled average distance.
 
 We now use the feature-based distances between each pair of images as
-well as our previous geometry alignment results to refine all image
-positions using a weighted linear least squares solution. The
-variables we wish to solve for are the $x_i$ and $y_i$ positions of
-images, while equations are the feature-based distances between pairs
-of images, images fixed to geometry with 0 or 1 degrees of freedom,
-and the original noisy camera poses. The original camera poses are
-needed because we sometimes are not able to detect feature matches in
-all of our images, or we lack enough geometry alignment results to
-generate a single solution. Because we want to minimally use our
-original poses, we give them a weighting factor of $0.01$, while all
-other equations are weighted at $1$. An example setup for a weighted
-linear least squares problem $\textrm{min}_{\vec{\beta}}
+well as geometry alignment results from Section
+\ref{sec:geometryAlignment} to refine all image positions using a
+weighted linear least squares approach. An example setup for a
+weighted linear least squares problem $\textrm{min}_{\vec{\beta}}
 ||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
-shown below.
+as follows.
 
@@
   0 & 0 & 0 & 1 & 0 & 0\\
+  0 & 1 & 0 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & 1 & 0\\
+  0 & 0 & 1 & 0 & 0 & 0\\
+  0 & 0 & 0 & 0 & 0 & 1\\
 
@@
   dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ -m_2gx_2 + gy_2,
-  \\ gx_1, \\ gy_1, \\ tx_1, \\ ty_1
+  \\ gx_1, \\ gy_1, \\ tx_1, \\ ty_1, \\ tx_2, \\ ty_2, \\ tx_3, \\
+  ty_3
 
@@
 \begin{pmatrix}
-  1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 0.01, \\ 0.01
+  1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 0.01, \\ 0.01, \\ 0.01, \\
+  0.01, \\ 0.01, \\ 0.01
 \end{pmatrix}
@@
 
-In this scenario, a feature-based distance of $dx_{1,2}$, $dy_{1,2}$
-was calculated between images 1 and 2. This corresponds to the first
-and second row of $A$, while the third and fourth row of $A$ represent
-the same for images 2 and 3. Rows 5 through 7 correspond to results of
-the geometry alignment procedure in Section
+The variables we wish to solve for are the $x_i$ and $y_i$ positions
+of images, while equations are the feature-based distances between
+pairs of images, images fixed to geometry with 0 or 1 degrees of
+freedom, and the original noisy camera poses. In this scenario, a
+feature-based distance of $dx_{1,2}$, $dy_{1,2}$ was calculated
+between images 1 and 2. This corresponds to the first and second row
+of $A$, while the third and fourth row of $A$ represent the same for
+images 2 and 3. Rows 5 through 7 correspond to results of the geometry
+alignment procedure in Section
 \ref{sec:geometryAlignment}. Specifically, row 5 corresponds to a
@@
 correspond to a fixed location for image 1 without any degrees of
-freedom. Rows 8 and 9 correspond to the original camera pose for image
-1, and original poses for images 2 and 3 are omitted for brevity.
+freedom. Rows 8 through 13 correspond to the original camera locations
+for each image ($tx_i,ty_i$).
 
-Because our problem is linear, it is easily and quickly solved, and
-after applying the resulting shifts, our images overlap and match each
-other with far greater accuracy. Applying the simple mapping scheme in
-Section \ref{sec:tileBasedMapping} to the same wall used in that
-section results in Figure \ref{fig:compareAll}(b), which has far fewer
-discontinuities, though errors due to lighting differences and
-parallax effects are still visible.
+The original camera poses are needed due to lack of feature matches in
+all images, or lack of enough geometry alignment results to generate a
+single solution. Since it is desirable to minimally use the original
+noisy poses, we assign to them a weighting factor of $0.01$, while all
+other equations are weighted at $1$.
+
+Since this problem is linear, it can be solved efficiently; after
+applying the resulting shifts, images overlap and match each other
+with far greater accuracy. Using the simple tile-based texturing
+scheme from Section \ref{sec:simpleTextureMapping} on these adjusted
+images results in Figure \ref{fig:compareAll}(b), which has far fewer
+discontinuities than in \ref{fig:compareAll}(a), though some 3D error
+as well as lighting differences and parallax effects are still
+visible.
 
@@
 \label{sec:imageCompositing}
-In this section, we revisit the tile-based texturing approach from
-Section \ref{sec:simpleTextureMapping}, with an added caching
-mechanism to reduce image boundaries. This method works well given all
-manner of camera poses and surfaces, but for optimal cases where
-images have consistently perpendicular viewing angles, we propose a
-superior method that selectively reduces image boundaries.
+In Section \ref{sec:mappingWithCaching}, we refine the tile-based
+texturing approach from Section \ref{sec:simpleTextureMapping}, with
+an added caching mechanism to reduce image boundaries. This method is
+general and works well given arbitrary camera poses and surfaces such
+as walls, floors, and ceilings. For special cases where images have
+consistently perpendicular viewing angles to the surfaces under
+consideration, such as walls, it is possible to develop an alternative
+method in Section \ref{sec:shortestPath} to further reduce visual
+artifacts.
 
@@
 \label{sec:mappingWithCaching}
-From Section \ref{sec:tileBasedMapping}, we saw that discontinuities
-occur where adjacent tiles are textured by different images. Though
-Section \ref{sec:2dAlignment}'s image alignment removes many such
+For the simple texture mapping method described in Section
+\ref{sec:simpleTextureMapping}, discontinuities occur where adjacent
+tiles are textured by different images. Though Section
+\ref{sec:2dAlignment}'s image alignment removes many such
 discontinuities, there are still cases where seams are visible due to
-imprecise matching or other factors such as model-based errors. To
-reduce the cases where this happens, it makes sense to take into
+imprecise matching or other factors such as model-based errors as
+shown in Figure \ref{fig:compareAll}(b). To reduce this, it is
+desirable to develop a spatiotemporal caching mechanism to take into
 account image selections made by neighboring tiles while texture
 mapping a given tile. By using the same image across tile boundaries,
-we can eliminate a discontinuity altogether. If this is not possible
-because a tile is not visible in images used by neighboring tiles,
-using similar images across tile boundaries also leads to less
-noticeable discontinuities.
+it is possible to eliminate a discontinuity altogether. If a tile is
+not visible in images used by neighboring tiles, using similar images
+across tile boundaries also leads to less noticeable discontinuities.
 
-Essentially a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set of valid images. The first
-subset of images is the images selected by adjacent tiles that have
-already been textured. We must first check which of these images can
-map to $t$, and then of those, we make a choice according to the
-scoring function in Figure \ref{fig:scoringFunction}. Before reusing
-this image, we ensure it meets the criteria $\alpha < 45^\circ$, in
-order to ensure a high resolution projection, with $\alpha$ as the
-camera angle as shown in Figure \ref{fig:scoringFunction}.
+The best image for a tile $t$ is selected by searching through two
+subsets of images for a viable candidate, before searching through the
+entire set of valid images obtained in Section
+\ref{sec:simpleTextureMapping}. The first subset of images is those
+selected by adjacent tiles that have already been textured. We must
+first check which of these images contain texture for $t$, and then of
+those, we make a choice according to the scoring function in Figure
+\ref{fig:scoringFunction}. Before reusing this image, we check the
+criteria $\alpha < 45^\circ$, in order to ensure a high resolution
+projection, with $\alpha$ as the camera angle as shown in Figure
+\ref{fig:scoringFunction}.
 
@@
 second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar, and thus likely matched more cleanly. If
-no viable image is found according to the same criteria as before, we
-search the entire set of candidate images, selecting based on the same
-scoring function from Figure \ref{fig:scoringFunction}.
+the first subset, both spatially and temporally. We use the noisy
+camera poses to determine priority. These images are not the same as
+the ones used for neighboring tiles, but are taken at a similar
+location and time, suggesting that their localization and projection
+are quite similar, and thus likely match more seamlessly. If no viable
+image is found according to the $\alpha < 45^\circ$ criteria, we
+search the entire set of candidate images from Section
+\ref{sec:simpleTextureMapping}, selecting based on the same scoring
+function from Figure \ref{fig:scoringFunction}.
 
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(c), where seams are now reduced as compared to
-Figure \ref{fig:compareAll}(b). However, some discontinuities are
-still present, as visible in the posters on the wall with breaks in
-their borders.
+The result of applying this caching approach to the images for the
+surface in Figure \ref{fig:compareAll}(a) is shown in Figure
+\ref{fig:compareAll}(c), where seams are considerably reduced as
+compared to Figure \ref{fig:compareAll}(b). However, some
+discontinuities are still present, as visible in the posters on the
+wall with breaks in their borders.
 
@@
   \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \centering
+  \hspace{1in} \centering
   \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering
+  \centering \hspace{1in}
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
@@
 
-As mentioned earlier, our data comes from a mobile backpack
-system. Human operators can not carry the backpack in a perfectly
-upright position and are bent forwards at 15 to 20 degrees with
-respect to the vertical direction. As a result, cameras facing
-sideways are head on with respect to vertical walls, while cameras
-oriented towards the top or bottom of the backpack are at an angle
-with respect to horizontal floors and ceilings. This is depicted in
-Figures \ref{fig:projectionAngles}(a) and
+\subsection{Shortest Path Texturing}
+\label{sec:shortestPath}
+
+As mentioned earlier, our data comes from a mobile backpack system
+carried by am ambulatory human operator, typically bent forwards at 15
+to 20 degrees with respect to the vertical direction. As a result,
+cameras facing sideways are head on with respect to vertical walls, as
+shown in Figure \ref{fig:projectionAngles}(a), while cameras oriented
+towards the top or bottom of the backpack are at an angle with respect
+to horizontal floors and ceilings, as shown in Figure
 \ref{fig:projectionAngles}(b). These oblique camera angles for
@@
 depending on the location of a tile on the plane. Thus, the tiling
-approach in this section is a good choice for texturing floors and
-ceilings, as it uses the parts of image projections that maximize
-resolution and accuracy for their respective plane locations,
-e.g. areas near point A and not near point B, in Figure
+approach in Section \ref{sec:mappingWithCaching} is an appropriate
+choice for texturing floors and ceilings, as it uses the parts of
+image projections that maximize resolution for their respective plane
+locations, e.g. areas near point A and not near point B, in Figure
 \ref{fig:projectionAngles}(b).
 
-\subsection{Shortest Path Texturing}
-\label{sec:shortestPath}
-For vertical walls, most images are taken from close distances and
-head-on angles, resulting in high resolution fronto-parallel
+For vertical walls however, most images are taken from close distances
+and head-on angles, resulting in high resolution fronto-parallel
 projections. As a result, for each tile on a wall plane, the scoring
@@
 respect to candidate images, as they are all more or less head
-on. Thus, the scoring function is less significant for walls, and it
-is conceivable to use a different texturing strategy to directly
+on. Since the scoring function is less discriminative for walls, it is
+conceivable to devise a different texturing strategy to directly
 minimize visible seams when texturing them. This is done by choosing
-the smallest possible set of images that (a) covers the entire plane
-and (b) minimizes the visibility of borders between them. A
-straightforward cost function that accomplishes the latter is the sum
-of squared differences (SSD) of pixels in overlapping regions between
-all pairs of images. Minimizing this cost function encourages image
-boundaries to occur either in featureless areas, such as bare walls,
-or in areas where images match extremely well.
+the smallest possible subset of images from the set selected in
+Section \ref{sec:simpleTextureMapping} and aligned in Section
+\ref{sec:robustSIFTFeatureMatching} such that it (a) covers the entire
+plane and (b) minimizes the visibility of borders between the
+images. A straightforward cost function that accomplishes the latter
+is the sum of squared differences (SSD) of pixels in overlapping
+regions between all pairs of images. Minimizing this cost function
+encourages image boundaries to occur either in featureless areas, such
+as bare walls, or in areas where images match extremely well.
 
-The first step in this procedure is to obtain a list of images useful
-for texturing the wall. A simple way to do this is to use the images
-selected by the tiling process in Section
-\ref{sec:tileBasedMapping}. Such a list of images is guaranteed to
-cover the entire wall, and consists of desired camera poses overall.
-
-In the general case, our problem can be defined as minimally covering
-a polygon i.e. the planar surface, using other polygons of arbitrary
-geometry i.e. image projections, with the added constraint of
-minimizing the cost function between chosen images. Given that
+In its most general form, our problem can be defined as minimally
+covering a polygon i.e. the planar surface, using other polygons of
+arbitrary geometry i.e. image projections, with the added constraint
+of minimizing the cost function between chosen images. Given that
 wall-texture candidate images are taken from more or less head-on
@@
 \ref{sec:2dAlignment}, we can crop our image projections to be
-rectangular with minimal texture loss. Furthermore, because our
-fisheye camera lenses have full floor-to-ceiling coverage of nearly
-all walls, and our backpack operator logically only moves
-horizontally, we only need to ensure lateral coverage of our wall
-planes. We can thus construct a Directed Acyclic Graph (DAG) from the
-images, with edge costs defined by the SSD cost function, and solve a
-simple shortest path problem to find an optimal subset of images with
-regard to the SSD cost function \cite{dijkstra}.
+rectangular with minimal texture loss as shown in Figure
+\ref{fig:projectionAngles}(c). Furthermore, because the fisheye camera
+lenses have full floor-to-ceiling coverage of nearly all walls, and
+the backpack operator logically only moves horizontally, we only need
+to ensure lateral coverage of our wall planes. We can thus construct a
+Directed Acyclic Graph (DAG) from the images, with edge costs defined
+by the SSD cost function, and solve a simple shortest path problem to
+find an optimal subset of images with regard to the SSD cost function
+\cite{dijkstra}.
 
@@
 
-In very rare cases where the vertical dimension of the plane is not
+In rare cases where the vertical dimension of the plane is not
 entirely covered by one or more chosen images, we are left with holes
@@
 blending region around the hole, as discussed in Section
-\ref{sec:blending}. This method is not as optimal as a true
-2D-coverage solution would be, but it is a fast approximation, and
-adequately handles the few holes we encounter.
+\ref{sec:blending}. This method is not optimal as a true 2D-coverage
+solution would be, but it is a fast approximation, and adequately
+handles the few holes encountered.
 
-With this completed, we have now mapped every location on the plane to
-at least one image, and have minimized the number of images, as well
-as the discontinuities at their borders. As seen in Figure
+We have now mapped every location on the plane to at least one image,
+and have decreased the number of images, generally retaining around 20\% of the image subset obtained in Section \ref{sec:simpleTextureMapping}, as
+well as the discontinuities at each image border. As seen in Figure
 \ref{fig:compareAll}(d), this shortest path method has fewer visible
@@
 When texturing an entire 3D planar model, we apply the shortest path
-method on walls, due to its superior output when provided with head-on
-images. Floors and ceilings however, given their many images taken at
-oblique angles, are textured using the tile caching method.
+method on walls, due to its superior results when provided with
+head-on images. Floors and ceilings however, given their many images
+taken at oblique angles, are textured using the tile caching method of Section \ref{sec:mappingWithCaching}.
 
@@
 \label{sec:blending}
-We now apply a blending procedure to both texturing methods. Although
-the image alignment steps and image selection in both methods attempt
-to minimize all mismatches between images, there are occasional
+We now apply a blending procedure to the texturing methods in Sections
+\ref{sec:mappingWithCaching} and \ref{sec:shortestPath}. Although the
+image alignment steps and image selection in both methods attempt to
+minimize all mismatches between images, there are occasional
 unavoidable discontinuities in the final texture due to different
@@
 however be treated and smoothed over by applying alpha blending over
-image seams.  Whether the units we are blending are
+image seams.  Whether the units to be blended are
 rectangularly-cropped images or rectangular tiles, we can apply the
-same blending procedure, as long as we have a guaranteed overlap
+same blending procedure, as long as there is a guaranteed overlap
 between units to blend over.
 
-For the tile caching method, we can ensure overlap by texturing a
+For the tile caching method of Section \ref{sec:mappingWithCaching}, we can ensure overlap by texturing a
 larger tile than needed for display. For example, for a rendered tile
@@
 images. To enforce consistent blending however, we add a minimum
-required overlap distance of 200 mm while solving the shortest path
+required overlap of images of 200 mm while solving the shortest path
 problem in Section \ref{sec:shortestPath}. Additionally, if images
@@
 
-After performing linear alpha blending across overlapping regions, our
-texture mapping process is complete. Figures \ref{fig:compareAll}(e)
+After linear alpha blending across overlapping regions, the texture mapping process is complete. Figures \ref{fig:compareAll}(e)
 and \ref{fig:compareAll}(f) show the blended versions of Figures
@@
 
-\section{Results and Conclusions}
-\label{sec:resultsAndConclusions}
+\section{Results}
+\label{sec:results}
 Examples of ceilings and floors textured with the tile caching
 approach, and walls textured with the shortest path approach, are
-displayed in Figure \ref{fig:results}. These results are as accurate
-and clean as the best results we obtained using the two algorithms
-mentioned in Section \ref{sec:existingApproaches}. High resolution
-colored texture comparisons, as well as video and interactive
-walkthroughs of full models are available at
-\footnote{\url{http://www.eecs.berkeley.edu/~pcheng/indoormapping}}.
+displayed in Figure \ref{fig:results}. High resolution colored texture
+comparisons, as well as video and interactive walkthroughs of full
+models are available at
+\footnote{\url{http://www-video.eecs.berkeley.edu/research/indoor/}}.
 
@@
 the entire dataset, a 2.8GHz dual-core consumer-grade laptop takes
-approximately a minute to pick 36 candidate images, followed by under
-a minute to perform both image alignment and the shortest path
+approximately a minute to choose 36 candidate images, followed by
+under a minute to perform both image alignment and the shortest path
 texturing method, though over 75\% of that time is spent calculating
@@
 split into a separate preprocessing step. While not real-time, the
-process is capable of generating quick updates after changes in
-various parameters or modifications to input data, and if integrated
-directly into a modeling system, could provide live visualization as
-data is collected. Our full models consist of our input model file,
-textures that we generate, and a mapping of image points to model
-vertices. The models shown in Figure \ref{fig:results} are roughly 20
-MB in size, and are visualized using the OpenSceneGraph toolkit
-\cite{openscenegraph}, which allows for export to many common model
-formats, as well as efficient visualization, even in web browsers or
-mobile devices.
+process is capable of generating fast updates after changes in various
+parameters or modifications to input data, and if integrated directly
+into a 3D modeling system, could provide live visualization as data is
+collected. Our full models consist of an input model file, textures,
+and a mapping of image points to 3D model vertices. The models shown
+in Figure \ref{fig:results} are roughly 20 MB in size, and are
+visualized using the OpenSceneGraph toolkit \cite{openscenegraph},
+which allows for export to many common model formats, as well as
+efficient visualization, even in web browsers or mobile devices.
+
+\section{Conclusion}
+\label{sec:conclusion}
 
@@
 
-While our method works well on our datasets, it is likely to fail in
-areas where 3D error is much higher. A technique for resolving camera
-error in 3D that would be a logical progression of our approach is to
-perform 3D matching between image lines and geometry in 3D, which can
+Our method is likely to fail in scenarios where 3D error is large. A
+logical progression of our approach to resolve camera error in 3D is
+to perform matching between image lines and geometry in 3D, which can
 be done reasonably efficiently \cite{linebased,
-  rectangularstructures}. Using linear features on top of our SIFT
+  rectangularstructures}. Using linear features in addition to SIFT
 features is also likely to result in improved matches, as indoor
 scenes often have long, unbroken lines spanning multiple images
-\cite{linearposeestimation}. Finally, our blending procedure is very
+\cite{linearposeestimation}. Finally, the blending procedure is quite
 basic, and applying more sophisticated methods of blending as well as
-normalization would benefit our final visual quality, and more
+normalization would benefit the final visual quality, and more
 robustly handle motion-based or parallax errors.
@@
   \centering{
-    \includegraphics[width=1.9in]{fullmodel.png}
-    \includegraphics[width=1.9in]{threestoryfull2.png}
-    \includegraphics[width=1.9in]{pier15.png} \\
-    \includegraphics[width=6in]{threestoryfull.png}
+    \includegraphics[width=3in]{fullmodel.png}
+    \includegraphics[width=3in]{pier15.png} \\
+    \includegraphics[width=3in]{threestoryfull2.png}
+    \includegraphics[width=3in]{threestoryfull.png}
   }

### 2013-03-03 spie/_region_.tex
yet another draft

--- 2013-02-04 spie/_region_.tex
@@
 
-\message{ !name(paper.tex) !offset(395) }
+\message{ !name(paper.tex) !offset(435) }
 \subsection{Image Occlusion}
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.jpg}}
-  \hspace{0.4cm} \subfloat[][]{\includegraphics[width=3in, height=1.8in]{occlusionimages.png}}
-  \caption{(a) The green image contains texture that belongs to the red surface, which should not be projected onto the blue target surface.
-(b) Above, without geometry alignment, texture to the left of the red line would be removed, which would leave some erroneous texture projected onto our target surface.
-Below, after geometry alignment, the correct amount of texture is removed.}
+  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.png}}
+   \subfloat[][]{\includegraphics[width=3in,
+    height=1.8in]{occlusionimagebad.png}}\\
+  \hspace{3in} 
+  \subfloat[][]{\includegraphics[width=3in,
+    height=1.8in]{occlusionimagegood.png}}
+
+  \caption{(a) The image from the camera in this diagram contains
+    texture that belongs to the grey occluding surface, which should
+    not be projected onto the orange target surface; (b) without
+    geometry alignment, texture to the left of the red line would be
+    removed, which would leave some erroneous texture projected onto
+    our target surface; (c) after geometry alignment, the image is
+    shifted, resulting in the correct amount of texture being
+    removed.}
   \label{fig:occlusion}
@@
 
-In order to properly texture surfaces such as the one shown in Figure
-\ref{fig:occlusion}, it is important to detect when parts of image
-projections contain texture belonging to other surfaces and should
-therefore not be used. This can be tested by recursively performing
-ray-polygon intersection tests between camera locations and other
-surfaces in a regularly spaced grid \cite{rayintersection}. Where four
-corners of a rectangular region are occluded, texture is
-removed. Where no corners are occluded, the recursion stops. Where
-there is a mixture of both, the rectangular region is subdivided into
-four, and the same process is performed on each. By performing Section
-\ref{sec:geometryAlignment}'s alignment procedure before occlusion,
-texture belonging to other surfaces is accurately removed, which is
-necessary for the next section.
+In order to correctly texture surfaces, it is important to detect and
+remove parts of image projections containing texture for occluding
+surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
+used to texture the orange target surface also contains part of a grey
+occluding surface. We remove this incorrect texture by recursively
+performing ray-polygon intersection tests between the camera location
+and other surfaces \cite{rayintersection}. These intersection tests
+are performed at the corners of a grid overlaid upon the target
+surface. Where all four corners of a grid section are occluded,
+texture is removed. Where one or more corners are occluded, the grid
+is subdivided into four, and the process repeats. Occlusion checking
+works entirely with geometry, so by ensuring that images match
+geometry using \ref{sec:geometryAlignment}'s alignment procedure,
+texture belonging to other surfaces is accurately removed, as seen in
+Figure \ref{fig:occlusion}(b).
 
-\message{ !name(paper.tex) !offset(791) }
+\message{ !name(paper.tex) !offset(852) }
 

### 2013-03-03 spie/paper.tex
yet another draft

@@
 \usepackage{float}
+\usepackage{multirow}
 \title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
@@
   \centering
-  \includegraphics[trim=0cm 3cm 0cm 0cm, clip=true,
-  width=6in]{flowchart.jpg}
+  \includegraphics[width=6in]{flowchart.jpg}
   \caption{The proposed texture mapping procedure\\}
@@
 as similar windows, doors, and wall-mounted decorations, that are
-difficulte to disambiguate. This lack of reliable reference points
+difficult to disambiguate. This lack of reliable reference points
 often results in errors when matching images together.
@@
 computational complexity of the remaining steps, but also selects the
-most preomising images for the remaining steps.
+most promising images for the remaining steps.
 
@@
 
-Our proposed 2D alignment procedure consists of three parts. First,
-images are projected onto the surface and lines within these projected
-images are detected. Images are then transformed such that these lines
-match geometric lines composing the boundaries of the surface being
+Our proposed 2D alignment procedure consists of three parts, as shown
+in the diagram in Figure \ref{fig:flowchart}. First, images are
+projected onto the surface and lines within these projected images are
+detected. Images are then transformed such that these lines match
+geometric lines composing the boundaries of the surface being
 textured. Second, occlusion checks are performed to remove invalid
@@
 
-  \centering \subfloat[][]{\includegraphics[trim=0cm 3cm 0cm 0cm,
-    clip=true, width=5in]{matchlines.jpg}}
+  \centering \subfloat[][]{\includegraphics[trim=0cm 2cm 0cm 0cm,
+    clip=true, width=5in]{matchLines.jpg}}
 
@@
 which is resolved by matching the midpoint of the image-based line in
-the second pair to its corresponding geometry-based line. Thus, with 2
-or more pairs, it is possible to obtain a fixed rotation and
-translation, which are saved for usage in Section
-\ref{sec:robustSIFTFeatureMatching}.
+the second pair to its corresponding geometry-based line. This
+corresponds to case (1) of Figure
+\ref{fig:geometryAlignment}(c). Thus, with 2 or more pairs, it is
+possible to obtain a fixed rotation and translation, which are saved
+for usage in Section \ref{sec:robustSIFTFeatureMatching}.
 
@@
 ambiguity however, can not be resolved, but is also saved to be used
-in Section \ref{sec:robustSIFTFeatureMatching}. Finally, in the case
-where there are no line pairs, we can still rotate images in order to
-exploit patterns in indoor environments. For instance, doors, windows,
+in Section \ref{sec:robustSIFTFeatureMatching}. This corresponds to
+case (2) of Figure \ref{fig:geometryAlignment}(c). Finally, in the
+case where there are no line pairs, we can still rotate images in
+order to exploit patterns in indoor environments (case (3) of Figure
+\ref{fig:geometryAlignment}(c)). For instance, doors, windows,
 furniture, etc. tend to have linear edges that are parallel to the
@@
 
-After these steps, image projections line up well with
-target surfaces, as shown in Figure \ref{fig:geometryAlignment}(b),
-which is considerably more aligned than Figure
-\ref{fig:geometryAlignment}(a) is. This procedure reconciles both
-errors in camera poses as well as in geometry, and results in sharp,
-continuous borders across images, which is crucial when checking for
-occlusion.
+After these steps, image projections line up well with target
+surfaces, as shown in Figure \ref{fig:geometryAlignment}(b), which is
+considerably more aligned than Figure \ref{fig:geometryAlignment}(a)
+is. This procedure reconciles both errors in camera poses as well as
+in geometry, and results in sharp, continuous borders across images,
+which is crucial when checking for occlusion.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{occlusiondiagram.png}}
-  \hspace{0.4cm} \subfloat[][]{\includegraphics[width=3in,
-    height=1.8in]{occlusionimages.png}}
+  \begin{tabular}{cc}
+    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{occlusiondiagram.png}}} &
+
+  \begin{tabular}{c}
+    \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
+    clip=true, width=3in,
+      height=0.9in]{occlusionimagebad.png}} \\
+    \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
+    clip=true, width=3in,
+      height=0.9in]{occlusionimagegood.png}}
+  \end{tabular}
+\end{tabular}
 \caption{(a) The image from the camera in this diagram contains
-    texture that belongs to the grey occluding surface, which should
-    not be projected onto the orange target surface; (b) without
-    geometry alignment, texture to the left of the red line would be
-    removed, which would leave some erroneous texture projected onto
-    our target surface; (c) after geometry alignment, the image is
-    shifted, resulting in the correct amount of texture being
-    removed.}
+  texture that belongs to the gray occluding surface, which should not
+  be projected onto the orange target surface; (b) without geometry
+  alignment, texture to the left of the red line would be removed,
+  which would leave some erroneous texture projected onto our target
+  surface; (c) after geometry alignment, the image is shifted,
+  resulting in the correct amount of texture being removed.}
 \label{fig:occlusion}
@@
 surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
-used to texture the orange target surface also contains part of a grey
+used to texture the orange target surface also contains part of a gray
 occluding surface. We remove this incorrect texture by recursively
@@
 method in Section \ref{sec:shortestPath} to further reduce visual
-artifacts.
+artifacts. Both of these approaches are followed by a blending step in
+order to produce final textures for each surface, as shown in Figure
+\ref{fig:flowchart}.
 
@@
 We have now mapped every location on the plane to at least one image,
-and have decreased the number of images, generally retaining around 20\% of the image subset obtained in Section \ref{sec:simpleTextureMapping}, as
-well as the discontinuities at each image border. As seen in Figure
-\ref{fig:compareAll}(d), this shortest path method has fewer visible
-discontinuities than Figure \ref{fig:compareAll}(c) corresponding to
-the tile caching approach\footnote{In Figure \ref{fig:compareAll}(d),
-  we arbitrarily chose one image for texturing where images overlap,
-  as blending will be discussed in section \ref{sec:blending}.}. This
-is especially evident when comparing the posters in the images. This
-shortest path approach approach directly reduces the cost of each
-image boundary, while the tile caching method uses a scoring function
-that only approximates this effect. Furthermore, this approach
-guarantees the best selection of images to minimize seams, while the
-sequential tile caching method may select images early on that turn
-out to be poor choices once subsequent tiles have been processed. This
-shortest path approach is also far less intensive in terms of memory
-usage and runtime, both during texture generation and rendering, as it
-does not require discretizing planes or images.
+and have decreased the number of images, generally retaining around
+20\% of the image subset obtained in Section
+\ref{sec:simpleTextureMapping}, as well as the discontinuities at each
+image border. As seen in Figure \ref{fig:compareAll}(d), this shortest
+path method has fewer visible discontinuities than Figure
+\ref{fig:compareAll}(c) corresponding to the tile caching
+approach\footnote{In Figure \ref{fig:compareAll}(d), we arbitrarily
+  chose one image for texturing where images overlap, as blending will
+  be discussed in section \ref{sec:blending}.}. This is especially
+evident when comparing the posters in the images. This shortest path
+approach approach directly reduces the cost of each image boundary,
+while the tile caching method uses a scoring function that only
+approximates this effect. Furthermore, this approach guarantees the
+best selection of images to minimize seams, while the sequential tile
+caching method may select images early on that turn out to be poor
+choices once subsequent tiles have been processed. This shortest path
+approach is also far less intensive in terms of memory usage and
+runtime, both during texture generation and rendering, as it does not
+require discretizing planes or images.
 
@@
 head-on images. Floors and ceilings however, given their many images
-taken at oblique angles, are textured using the tile caching method of Section \ref{sec:mappingWithCaching}.
+taken at oblique angles, are textured using the tile caching method of
+Section \ref{sec:mappingWithCaching}.
 
@@
 
-For the tile caching method of Section \ref{sec:mappingWithCaching}, we can ensure overlap by texturing a
-larger tile than needed for display. For example, for a rendered tile
-$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size.  We have found $l_2 = \frac{l_1}{2}$ to
-provide a balance between blending and keeping features unblurred. For
-the shortest path method, we have already ensured overlap between
-images. To enforce consistent blending however, we add a minimum
-required overlap of images of 200 mm while solving the shortest path
-problem in Section \ref{sec:shortestPath}. Additionally, if images
-overlap in a region greater than the overlap distance, we only apply
-blending over an area equal to the overlap distance.
+For the tile caching method of Section \ref{sec:mappingWithCaching},
+we can ensure overlap by texturing a larger tile than needed for
+display. For example, for a rendered tile $l_1 \times l_1$, we can
+associate it with a texture $(l_1 + l_2) \times (l_1 + l_2)$ in size.
+We have found $l_2 = \frac{l_1}{2}$ to provide a balance between
+blending and keeping features unblurred. For the shortest path method,
+we have already ensured overlap between images. To enforce consistent
+blending however, we add a minimum required overlap of images of 200
+mm while solving the shortest path problem in Section
+\ref{sec:shortestPath}. Additionally, if images overlap in a region
+greater than the overlap distance, we only apply blending over an area
+equal to the overlap distance.
 
-After linear alpha blending across overlapping regions, the texture mapping process is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
+After linear alpha blending across overlapping regions, the texture
+mapping process is complete. Figures \ref{fig:compareAll}(e) and
+\ref{fig:compareAll}(f) show the blended versions of Figures
 \ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. The

### 2013-05-02 masters/body/_region_.tex
masters

\message{ !name(masters.tex)}\documentclass[]{spie}  %>>> use for US letter paper

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{float}
\usepackage{multirow}

\title{Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses}

\author{Peter Cheng
\skiplinehalf
University of California, Berkeley\\
}

\begin{document}

\message{ !name(masters.tex) !offset(135) }
\subsection{Geometry Partitioning}
\label{sec:geometryPartioning}
In order to effectively texture a 3D model, we first divide the model
into a set of regions, each to be textured independently. The purpose
of this is to ensure texture continuity along large uniform areas,
while allowing texture boundaries to fall along natural environmental
boundaries. Because textures may not match at such boundaries where
two regions meet, it is important to minimize the visibility of
boundaries. This is done by encouraging region boundaries to occur at
large sharp corners, where texture continuity is less important.

When working with low-resolution models, where surfaces generally
correspond to large planar features such as walls, ceilings, or
floors, and often meet at right angles, each planar surface in the
model is directly treated as a distinct region and textured
separately.

When working with a high-resolution model however, geometry often
represents large features as well as small details found in furniture,
plants, and other miscellaneous objects. For instance, in Figure
\ref{fig:deskGeom}, the geometry modeling the desk and binders
consists of many small triangles at various orientations. Texturing
each of these triangles independently makes little sense, as the
textures applied to each should match up well with the textures of its
neighbors in order to avoid any breaks in the overall image of the
desk and binders. On the other hand, the textures for the triangles
belonging to the wall behind need not match up with the textures on
the desk and binders, and so each group of triangles should be
designated to separate regions. This region grouping is performed by designating all contiguous coplanar groups of triangles as different regions. Any region that is less than $1 m^2$ in size is joined to its largest neighboring region, such that the angle between them is under $90^{\circ}$.

Because a texture is 2D, and the region to be textured may not be
flat, a mapping needs to be defined. We first fit a plane to each
region for the purposes of texturing. This can be accomplished via a
least squares plane-fitting through each triangle vertex, though in
practice we simply use the plane equation of the largest contiguous
section of coplanar triangles, as most regions are characterized by
small outcroppings from a largely planar surface, such as objects on a
table or features protruding from a wall. The 3d vertices within a
region are then projected onto its calculated plane, and the
rectangular bounding box for these projected vertices is
calculated. This bounding box corresponds to the 2D image that will be
created to texture the region.

Of course, the area encompassed by the bounding box is larger than the
corresponding 2d area of the projected geometry, which itself is not
as accurate as the original 3d geometry. Thus, we also create a k-d
tree consisting of the triangle primitives from the original
mesh. Though we generate texture for the 2d bounding box surface, we
will reference the original 3D geometry to ensure accuracy when
texturing.

\message{ !name(masters.tex) !offset(944) }

\end{document}

### 2013-05-02 masters/body/assets/3dimpvt/_region_.tex
masters

--- 2012-12-23 spie/assets/_region_.tex
@@
-\message{ !name(oldpaper.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}
+\message{ !name(paper.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}
 
@@
 
- \cvprfinalcopy % *** Uncomment this line for the final submission
+% \cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
-\message{ !name(oldpaper.tex) !offset(-3) }
-
-%%%%%%%%% TITLE
-\title{Texture Mapping 3D Planar Models of Indoor Environments with Noisy
-  Camera Poses}
-
-\author{Peter Cheng \hspace*{2em} Michael Anderson \hspace*{2em} Stewart He \hspace*{2em} Avideh Zakhor\\
-  UC Berkeley\\
-}
-\maketitle
-% \thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  Automated 3D modeling of building interiors is useful in
-  applications such as virtual reality and environment
-  mapping. Applying textures to these models is an important step in
-  generating photorealistic visualizations of data collected by
-  modeling systems. Camera pose recovery in such systems often suffers
-  from inaccuracies, resulting in visible discontinuities when
-  successive images are projected adjacently onto a plane for
-  texturing. We propose two approaches to reduce discontinuities in
-  texture mapping 3D models made of planar surfaces. The first one is
-  tile based and can be used for images and planes at arbitrary angles
-  relative to each other. The second one results in a more seamless
-  texture, but is only applicable where camera axes for images are
-  closely aligned with plane normals of the surfaces to be
-  textured. The effectiveness of our approaches are demonstrated on
-  two indoor datasets.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:introduction}
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and as
-such, automated 3D site modeling has garnered much interest in recent
-years.
-
-The first step in automated 3D modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-recover camera poses within an environment while simultaneously
-reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
-known as the simultaneous localization and mapping (SLAM) problem, and
-is generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment.
-
-Mounting such devices on a platform carried by an ambulatory human
-provides unique advantages over vehicular-based systems on wheels in
-terms of agility and portability, but can also result in larger
-localization error \cite{liu2010indoor}. As a result, common methods
-for texture mapping generally produce poor results.
-
-In this paper, we present a number of approaches to texture mapping 3D
-models of indoor environments made of planar surfaces in the presence
-of uncertainty and noise in camera poses. In particular, we consider
-data obtained from a human-operated backpack system with a number of
-laser range scanners as well as 2 cameras facing left and right, each
-equipped with fisheye lenses reaching an approximately 180$^{\circ}$
-field of view and taking photos at a rate of 5 Hz. Applying multiple
-localization and loop-closure algorithms on the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, the backpack is localized\footnote{In this paper, we
-  use the terms localization and pose recovery interchangeably, in
-  that they both refer to recovering position and orientation.}  over
-its data collection period. This requires recovering the 6 degrees of
-freedom for the backpack as well as the cameras rigidly mounted on
-it. Once this is complete, the data from the laser range scanners is
-used to generate a 3D point cloud of the surrounding environment, from which a
-3D planar model is created \cite{sanchez2012point}. This model, consisting of 2D
-polygonal planes in 3D space, along with the set of images captured by
-the backpack's cameras and their noisy 3D poses, can be considered the
-input to our texture mapping problem.
-
-This problem straddles the fields of image-based localization
-refinement as well as image alignment and mosaicing, and thus our
-proposed solution shares many similarities with past research in those
-areas, which will be examined in Section
-\ref{sec:existingApproaches}. However, we can exploit known
-approximate camera poses as well as the 3D geometry of the environment
-to more accurately and efficiently texture the planes.
-
-The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} describes two variants of a tile-based
-mapping approach and their shortcomings.  Section
-\ref{sec:existingApproaches} discusses past research in related
-fields, demonstrates two previous attempts at improving texture
-alignment, and exhibits their inadequacies for our datasets. Section
-\ref{sec:proposedApproach} presents our proposed seam minimization
-approach to texture mapping. Section \ref{sec:resultsAndConclusions}
-contains results and conclusions.
-
-In all subsequent sections, we discuss the process of texture mapping
-a single plane, as the texturing of each plane is independent and can
-be completed in parallel.
-
-\section{Tile-Based Texture Mapping}
-\label{sec:simpleTextureMapping}
-\begin{figure}
-  \centering
-  \includegraphics[height=2in]{Projection.pdf}
-  \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera
-    matrices $P_{1..M}$. }
-  \label{fig:projection}
-\end{figure}
-
-The geometry of the texture mapping process for a plane is shown in
-Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images to texture the target plane. Each image has a
-camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
-world coordinate system to a 2D point or pixel in image $i$'s
-coordinates. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, such as focal length and image center, as well
-as extrinsic parameters which specify the rotation and translation of
-the camera's position in 3D world coordinates at the time that image
-$i$ is taken. These extrinsic parameters are determined by the
-backpack hardware and localization algorithms \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure} and are quite noisy.
-
-Because the backpack system takes photos at a rate of 5 Hz, thousands
-of images are available for texturing each plane. Our goal in creating
-a texture mapping process is to decide which of these images should be
-used, and where their contents should map onto the texture, in order
-to eliminate any visual discontinuities or seams that would suggest
-that the plane's final texture is not composed of a single continuous
-image.
-
-\subsection{Direct Mapping}
-\label{sec:directMapping}
-
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square tiles,
-generally about 5 pixels across, and choosing an image to texture each
-tile.
-
-We choose to work with rectangular units to ensure that borders
-between any two distinct images in the final texture are either
-horizontal or vertical. Since most environmental features inside
-buildings are horizontal or vertical, any seams in our texture
-intersect them minimally and are likely to be less noticeable.
-
-In order to select an image for texturing a tile $t$, we must first
-gather a list of candidate images that contain all four of its
-corners, which we can quickly check by projecting $t$ into each image
-using the $P_i$ camera matrices. Furthermore, each candidate image
-must have been taken at a time when its camera had a clear
-line-of-sight to $t$, which can be calculated using standard
-ray-polygon intersection tests between the camera location, the center
-of $t$, and every other plane \cite{rayintersection}.
-
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image. Since camera
-pose errors compound over distance, we wish to minimize the distance
-between cameras and the plane they texture. Additionally, we desire
-images that are projected perpendicularly onto the plane, maximizing
-the resolution and amount of useful texture available in their
-projections, as well as minimizing any parallax effects. In other
-words, we wish to minimize the angle between the plane normal and the
-camera axis for images selected for texture mapping. These two
-criteria can be met by maximizing the function $\frac{1}{d} (-1 \cdot
-\vec{c}) \cdot \vec{n}$ as shown in Figure
-\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
-the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-the directions of the plane's normal and the camera axis respectively.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=1.5in]{scoringFunction.jpg}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by
-    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-    \cdot \vec{n}$}
-  \label{fig:scoringFunction}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_naive.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog_noblend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog.pdf}}
-  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
-    with caching after image alignment. (d) Seam minimization after
-    image alignment). (e) same as (c) with blending. (f) same as (d)
-    with blending.}
-  \label{fig:compareAll}
-\end{figure}
-
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but overall results in
-many image boundaries with abrupt discontinuities, due to significant
-misalignment between images, as a result of camera pose inaccuracies.
-
-\subsection{Mapping with Caching}
-\label{sec:mappingWithCaching}
-Since discontinuities occur where adjacent tiles select non-aligned
-images, it makes sense to take into account image selections made by
-neighboring tiles while texture mapping a given tile. By using the
-same image across tile boundaries, we can eliminate a discontinuity
-altogether. If this is not possible because a tile is not visible in
-images chosen by its neighbors, using similar images across tile
-boundaries also leads to less noticeable discontinuities.
-
-Similar to a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set. The first subset of images is
-those selected by adjacent tiles that have already been textured. We
-must first check which of these images can map to $t$, and then of
-those, we make a choice according to the scoring function in Figure
-\ref{fig:scoringFunction}. Before reusing this image, we ensure it
-meets the criteria $\alpha < 45^\circ$, in order to be considered a
-viable image, with $\alpha$ as the camera angle as shown in Figure
-\ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check the
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar. Again, if no viable image is found
-according to the same criteria, we search the entire set of candidate
-images, selecting based on the same scoring function from Figure
-\ref{fig:scoringFunction}.
-
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(b). As compared to Figure
-\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
-amount of remaining seams suggests that image selection alone cannot
-produce seamless textures. Camera matrices, or the image projections
-themselves have to be adjusted in order to reliably generate clean
-textures.
-
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-In order to produce seamless texture mapping, either camera matrices
-need to be refined such that their localization is pixel accurate, or
-image stitching techniques need to be applied to provide this
-illusion.
-
-Image projections can be aligned by refining their noisy camera poses,
-using image correspondences to adjust each image's camera matrix over
-6 degrees of freedom (DOF) \cite{coorg1997matching, liu2010indoor,
-  shum2000systems, szeliski1997creating}. Applying such approaches to
-our datasets however results in error accumulation and drift as shown
-in Figure \ref{fig:mosaic3D}(a), as well as high complexity and
-runtime \cite{liu2010indoor}.
-
-Another common approach to image alignment is to
-iteratively match images on intensity differences in selected patches,
-often in a spatial hierarchy \cite{hager1998efficient,
-  lucas1981iterative, shum2000systems, szeliski2006image}. Another
-widely-used approach is to perform feature matching, which requires
-the detection of visual features and their existence in multiple
-images \cite{brown2007automatic, cho2003automatic,
-  mikolajczyk2005performance, szeliski2006image,
-  yun2003comprehensive}. Notably, both approaches rely on the presence
-of multiple visual references, as when texturing detailed objects at
-high resolutions \cite{bernardinimultiplescans, wangmultipleviews}, or
-when creating large scene panoramas \cite{agarwalapanoramas,
-  bernardinimultiplescans, debevecviewdependent,
-  snavelyphototourism}. In contrast, our indoor datasets have a high
-prevalence of bare walls and ceilings, resulting in few reference
-points that can be used to judge alignment.
-
-Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not
-accurate. For example, when matching a long chain of images through
-homography, a pixel in the $nth$ image must be translated into the
-first image's coordinates by multiplying by the $3\times3$ matrix $H_1
-H_2 H_3 ... H_n$. Any error in one of these homography matrices is
-propagated to all further images, resulting in drift. Figure
-\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
-package, which performs homography-based image mosaicing
-\cite{autostitch}. Even with many features spread across this plane,
-the mosaicing produces errors that causes straight lines to appear as
-waves on the plane, despite the fact that it is generated after
-careful hand tuning. Many planes with fewer features simply failed
-outright using this approach.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm from \cite{chen2010indoor} and (b) image
-    mosaicing.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-\section{Seamless Texture Mapping}
-\label{sec:proposedApproach}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{pipeline.pdf}
-  \caption{Our proposed method for seamless texture mapping.}
-  \label{fig:pipeline}
-\end{figure}
-
-In this section, we describe our proposed method for seamless texture
-mapping. Our approach consists of 4 steps, as seen in Figure
-\ref{fig:pipeline}.  First, we project all images onto the plane and
-rotate them for verticality. Next,we perform 2D shifting in order to
-maximize SIFT feature matches in overlapping areas between these
-projections. We then select which textures to be used either with the
-tile caching method from Section \ref{sec:mappingWithCaching}, or with
-the more specialized method to be described in Section
-\ref{sec:seamMinimization}. This choice depends on the availability of
-head-on images for a given plane. We then finish by applying linear
-alpha blending to smooth out any remaining seams.
-
-\subsection{Image Rotation}
-\label{sec:projectionAndRotation}
-We begin with the projection of all images onto the plane. This is
-done in the same way as in Section
-\ref{sec:simpleTextureMapping}. Rather than work with all 6 DOF, which
-is computationally intensive, we choose to work only in two
-dimensions, performing 2D rotations and translations on the image
-projections, as errors in either lead to the greatest discontinuities.
-
-We perform rotations using Hough transforms, which detect the presence
-and orientation of linear features in our images. Rather than match
-the orientation of such features in each image, we simply apply
-rotations such that the strongest near-vertical features are made
-completely vertical. This is effective for vertical planes in indoor
-models, since they usually consist of parallel vertical lines
-corresponding to doors, wall panels, rectangular frames, etc. If
-features in the area are not vertical, e.g. for floors and ceilings,
-this step is skipped.
-
-\subsection{Image Shifting}
-\label{sec:robustSIFTFeatureMatching}
-Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images. We use
-SIFT features for their high detection rate, and choose to use feature
-alignment rather than intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lai1999robust,
-  lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-
-SIFT matches determine $d^x$ and $d^y$ distances between each pair of
-features for two images on the plane, though these distances may not
-always be the same for different features. Since indoor environments
-often contain repetitive features such as floor tiles or doors, we
-need to ensure that SIFT-based distances are reliable. In order to
-mitigate the effect of incorrect matches and outliers, the RANSAC
-framework \cite{fischler1981random} is used for a robust estimate of
-the optimal $d^x_{i,j}$ and $d^y_{i,j}$ distances between two images
-$i$ and $j$. The RANSAC framework handles the consensus-building
-machinery, and requires a fitting function and a distance
-function. For this application, the fitting function simply finds the
-average distance between matches in a pair of images. The distance
-function for a pair of points is chosen to be the difference between
-those points' SIFT match distance and the average distance computed by
-the fitting function. We use a 10 pixel outlier threshold, so that
-SIFT matches are labeled as outliers if their horizontal or vertical
-distances are not within 10 pixels of the average distance computed by
-the fitting function.
-
-We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
-of images to refine their positions using least squares. Recall that
-there are a total of $M^{2}$ possible pairs of images, though we only
-generate distances between images that overlap at SIFT feature
-points. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
-
-\[\vec{\beta} =
-\begin{pmatrix}
-  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
-\end{pmatrix}
-\]
-
-The $N \times (M+1)$ dimensional matrix $A$ is constructed with one
-row for each pair of images with measured distances produced by the
-SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the
-columns corresponding to the two images in the pair. For example, the
-matrix below indicates a SIFT-based distance between images 1 and 2,
-images 1 and 3, images 2 and 3, etc.
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & \cdots & 0 & 0\\
-  -1 & 0 & 1 & \cdots & 0 & 0\\
-  0 & -1 & 1 & \cdots & 0 & 0\\
-  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
-  0 & 0 & 0 & \cdots & 1 & 0 \\
-  0 & 0 & 0 & \cdots & -1 & 1 \\
-  1 & 0 & 0 & \cdots & 0 & 0 \\
-\end{pmatrix}
-\]
-If only relative distances between images are included then there is
-no way to determine the absolute location of any of the images and the
-matrix becomes rank deficient. To fix this we choose the first image
-to serve as the anchor for the rest, meaning all the absolute
-distances are based on its original location. This is done by adding a
-row with a $1$ in the first column and the rest zeros.
-
-Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
-constructed using the SIFT-based distances generated earlier in the
-RANSAC matching stage. The last element in the observation vector is
-the location of the first image determined by its original noisy
-localization, from \cite{chen2010indoor, liu2010indoor}. Thus
-$\vec{\gamma}$ can be written as:
-
-\[
-\vec{\gamma}^T =
-\begin{pmatrix}
-  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
-\end{pmatrix}
-\]
-
-The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
-\vec{\gamma}||_2^2$ results in a set of image locations on the plane
-that best honors all the SIFT-based distance measurements between
-images. In practice there is often a break in the chain of images,
-meaning that no SIFT matches are found between one segment of the
-plane and another. In this case we add rows to the $A$ matrix and
-observations to the $\vec{\gamma}$ vector that contain the original
-noisy $x$ and $y$ distance estimates from the original camera
-poses. Another way to do this is to add rows for all neighboring pairs
-of images and solve a weighted least squares problem where the SIFT
-distances are given a higher weight i.e. 1, and the noisy distances
-generated by the original camera poses \cite{chen2010indoor,
-  liu2010indoor} are given a smaller weight e.g. 0.01.
-
-After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and match each other
-with far greater accuracy. Applying the tile caching method from
-Section \ref{sec:mappingWithCaching} on these rotated and shifted
-images results in the significant improvements shown in Figure
-\ref{fig:compareAll}(c), as compared to Figure
-\ref{fig:compareAll}(b).
-
-\subsection{Seam Minimization}
-\label{sec:seamMinimization}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a) Undistorted fisheye images for vertical planes are
-    tilted, but their effective camera axis is more or less normal to
-    the plane. (b) The effective camera axis for ceilings is at an
-    angle with respect to the plane normal. (c) Wall images are
-    cropped to be rectangular.}
-  \label{fig:projectionAngles}
-\end{figure}
-
-As mentioned earlier, the mobile backpack system used to capture data
-in this paper contains 2 cameras with $180^\circ$ fisheye lenses
-facing to the right and left. Since most human operators do not carry
-the backpack in a perfectly upright position and are bent forwards at
-15 to 20 degrees with respect to the vertical direction, the
-undistorted fisheye images are head on with respect to vertical walls,
-but at an angle with respect to horizontal floors and ceilings. This
-is depicted for wall and ceiling planes in Figures
-\ref{fig:projectionAngles}(a) and \ref{fig:projectionAngles}(b)
-respectively. These oblique camera angles for ceilings translate into
-textures that span extremely large areas once projected, as shown in
-Figure \ref{fig:projectionAngles}(b). Using the tile-based texture
-mapping criteria from Figure \ref{fig:scoringFunction}, such
-projections have highly varying scores depending on the location on
-the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
-tiling approach in Section \ref{sec:simpleTextureMapping} is a
-reasonable choice for texturing floors and ceilings, as it uses the
-parts of image projections that are viable choices for their
-respective plane locations, e.g. areas near point A in Figure
-\ref{fig:projectionAngles}(b), but not near point B.
-
-For wall planes however, most images are taken from close distances
-and more or less head-on angles, resulting in higher resolution
-fronto-parallel projections. As a result, for each tile on a wall
-plane, the scoring function of Figure \ref{fig:scoringFunction} is
-relatively flat with respect to a large number of captured images, as
-they are all more or less head on. Thus, the scoring function is less
-significant for walls, and it is conceivable to use a different
-texturing strategy for them so as to minimize visible seams in texture
-mapped planes. This can be done by choosing the smallest possible set
-of images that (a) covers the entire plane and (b) minimizes the
-amount of visible seams between them. A straightforward cost function
-that accomplishes the latter is the Sum of Squared Differences (SSD)
-of pixels in overlapping regions between all pairs of images, after
-they have been rotated as described in Section
-\ref{sec:projectionAndRotation}. Minimizing this cost function
-encourages image boundaries to occur either in featureless areas, such
-as bare walls, or in areas where images match extremely well.
-
-To cover the entirety of a plane, our problem can be defined as
-minimally covering a polygon i.e. the plane, using other polygons of
-arbitrary geometry i.e. image projections, with the added constraint
-of minimizing the cost function between chosen images.  This is a
-complex problem, though we can take a number of steps to simplify it.
-
-Given that wall-texture candidate images are taken from more or less
-head-on angles, and assuming only minor rotations are made in Section
-\ref{sec:projectionAndRotation}, we can reason that their projections
-onto the plane are approximately rectangular. By cropping them all to
-be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
-problem becomes the conceptually simpler one of filling a polygon with
-rectangles, such that the sum of all costs between each pair of
-rectangles is minimal. We thus also retain the advantages of working
-with rectangular units, as explained in Section
-\ref{sec:simpleTextureMapping}.
-
-The location and orientation of the cameras and the fisheye lenses on
-the acquisition backpack is such that images nearly always contain the
-entirety of the floor to ceiling range of wall planes. Images are
-therefore rarely projected with one above another when texturing wall
-planes. In essence, we need only to ensure lateral coverage of wall
-planes, e.g. from left to right, as our images provide full vertical
-coverage themselves. We can thus construct a Directed Acyclic Graph
-(DAG) from the images, with edge costs defined by the SSD cost
-function, and solve a simple shortest path problem to find an optimal
-subset of images with regard to the cost function \cite{dijkstra}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process. \\}
-  \label{fig:dagCreation}
-\end{figure}
-
-Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a long hallway. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
-between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal cost $C_0$ to(from) all images that
-meet the left(right) border of the plane.
-
-We now solve the shortest path problem from the start node to the end
-node. This results in a set of images completely covering the plane
-horizontally, while minimizing the cost of seams between images.
-
-In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. To address this, we solve for
-a new shortest path after modifying the edges chosen by the original
-shortest path solution such that they have higher cost than all other
-edges in the DAG, and solve for a new shortest path. This ensures that
-these edges are not chosen again unless they are the only available
-option. Our second shortest path solution results in a new set of
-chosen images, of which we only retain those that cover areas not
-covered by the first set. This process can be repeated as many times
-as needed, until holes are no longer present. This method is not as
-optimal as a 2D-coverage solution would be, but it is a fast
-approximation, and adequately handles the few holes we encounter.
-
-With this completed, we have now mapped every location on the plane to
-at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. As seen in Figure
-\ref{fig:compareAll}(d), this seam minimization method has fewer
-visible discontinuities than Figure \ref{fig:compareAll}(c)
-corresponding to the tile caching approach\footnote{In Figure
-  \ref{fig:compareAll}(d), we arbitrarily chose one image for
-  texturing where images overlap, as blending will be discussed in the
-  next section.}. This is especially evident when comparing the
-posters in the images, which have clear misalignment over seams in
-Figure \ref{fig:compareAll}(c), but are much more aligned in Figure
-\ref{fig:compareAll}(d). This is because the seam minimization
-approach directly reduces the cost of each image boundary, while the
-tile caching method uses a scoring function that only approximates
-this effect. Furthermore, seam minimization guarantees the best
-selection of images, while the sequential tile caching method may
-select images early on that turn out to be poor choices once
-subsequent tiles have been processed. The seam minimization approach
-is also far less intensive in terms of memory usage and runtime, both
-during texture generation and rendering, as it does not require
-discretizing planes or images\footnote {For the seam minimization
-  approach, occlusion checks are performed over the entirety of each
-  image to determine available areas for texture mapping. Since indoor
-  environments mostly consist of vertical or horizontal surfaces with
-  high amounts of right angles, image projections remain largely
-  rectangular after masking out occluded areas. Therefore, as a
-  preprocessing step, we can recursively split each image into
-  rectangular pieces and check for occlusions in a similar manner as
-  in the tiling process.  }.
-
-In the context of texturing an entire 3D planar model, we choose to
-apply the seam minimization approach on walls, due to its superior
-output when provided with head-on images. Floors and ceilings however,
-given their many images taken at oblique angles, are textured using
-the tile caching method.
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=6in]{pipelineimages.pdf}
-%   \caption{Textures corresponding to each step in our texture
-%   mapping pipeline.}
-%   \label{fig:pipelineimages}
-% \end{figure*}
-
-\subsection{Blending}
-\label{sec:blending}
-We now apply the same blending process to the two texturing methods:
-image alignment followed by either tile caching or seam minimization.
-
-Although the preprocessing steps and image selection in both methods
-attempt to minimize all mismatches between images, there are
-occasional unavoidable discontinuities in the final texture due to
-different lighting conditions or inaccuracies in planar geometry or
-projection. These can however be treated and smoothed over by applying
-alpha blending over image seams.  Whether the units we are blending
-are rectangularly-cropped images or rectangular tiles, we can apply
-the same blending procedure, as long as we have a guaranteed overlap
-between units to blend over.
-
-For the tile caching method, we can ensure overlap by texturing a
-larger tile than needed for display. For example, for a rendered tile
-$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size. For the seam minimization method, we have
-already ensured overlap between images. To enforce consistent blending
-however, we add a minimum required overlap distance while solving the
-shortest path problem in Section
-\ref{sec:seamMinimization}. Additionally, if images overlap in a
-region greater than the overlap distance, we only apply blending over
-an area equal to the overlap distance.
-
-After blending pixels linearly across overlapping regions using alpha
-blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the seam minimization approach still exhibits better
-alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
-
-\section{Results and Conclusions}
-\label{sec:resultsAndConclusions}
-Examples of ceilings and floors textured with the tile caching
-approach, and walls textured with the seam minimization approach, are
-displayed in Figure \ref{fig:results}. High resolution texture
-comparisons, as well as a walkthrough of a fully textured 3D model are
-available in the accompanying video to this paper.
-
-In this paper, we have developed an approach to texture map models
-with noisy camera localization data. We are able to refine image
-locations based on feature matching, and robustly handle outliers. The
-tile-based mapping approach can be used to texture both simple
-rectangular walls as well as complex floor and ceiling geometry. We
-also presented a seam minimization texturing method that produces
-seamless textures on planes where multiple head-on images are
-available. Each of these approaches is highly modular, and easily
-tunable for different environments and acquisition hardware.
-
+\message{ !name(paper.tex) !offset(705) }
 \begin{figure*}
@@
   \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
-  ~~~~~~
+  ~~~
   \centering
@@
   \subfloat[][]{\includegraphics[height=2in, width=3in]{floorcropped.jpg}}
-  ~~~~~~~~
+  ~~~
   \centering \subfloat[][]{\includegraphics[width=3in]{fullmodel.png}}
@@
 \end{figure*}
-
-{\small \bibliographystyle{ieee} \bibliography{egbib} }
+\message{ !name(paper.tex) !offset(708) }
 
 \end{document}
-
-\message{ !name(oldpaper.tex) !offset(-739) }

### 2013-05-02 masters/body/assets/3dimpvt/template/egpaper_for_review.tex
masters

--- 2012-06-15 3dimpvt/template/egpaper_final.tex
@@
 % run, let it finish, and you should be clear).
-%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
 
-\cvprfinalcopy % *** Uncomment this line for the final submission
+% \cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\ifcvprfinal\pagestyle{empty}\fi
 \begin{document}
@@
   {\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
+  % For a paper whose authors are all at the same institution, omit
+  % the following lines up until the closing ``}''.  Additional
+  % authors and addresses can be added with ``\and'', just like the
+  % second author.  To save space, use either the email address or
+  % home page, not both
   \and
@@
   First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
+  {\small\url{http://www.author.org/~second}} }
 
 \maketitle
-%\thispagestyle{empty}
+% \thispagestyle{empty}
 
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
+  abcd The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
@@
   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous 3DIMPVT/3DIM/3DPVT abstracts to get a feel for style and length.
+  Look at previous 3DIMPVT/3DIM/3DPVT abstracts to get a feel for
+  style and length.
 \end{abstract}
@@
 
-Please follow the steps outlined below when submitting your manuscript to
-the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against the
-use of sticky tape to attach your artwork to the paper), so all authors
-should read this new version.
+Please follow the steps outlined below when submitting your manuscript
+to the IEEE Computer Society Press.  This style guide now has several
+important modifications (for example, you are no longer warned against
+the use of sticky tape to attach your artwork to the paper), so all
+authors should read this new version.
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{Language}
@@
 
-By submitting a manuscript to 3DIMPVT, the authors assert that it has not been
-previously published in substantially similar form. Furthermore, no paper
-which contains significant overlap with the contributions of this paper
-either has been or will be submitted during the 3DIMPVT 2012 review period to
-{\bf either a journal} or any conference or any
-workshop.
- {\bf Papers violating this condition will be rejected and a list of violating authors may be included in the proceedings.}
+By submitting a manuscript to 3DIMPVT, the authors assert that it has
+not been previously published in substantially similar
+form. Furthermore, no paper which contains significant overlap with
+the contributions of this paper either has been or will be submitted
+during the 3DIMPVT 2012 review period to {\bf either a journal} or any
+conference or any workshop.  {\bf Papers violating this condition will
+  be rejected}.
 
-If there are papers that may appear to the reviewers
-to violate this condition, then it is your responsibility to: (1)~cite
-these papers (preserving anonymity as described in Section 1.6 below),
-(2)~argue in the body of your paper why your 3DIMPVT paper is non-trivially
-different from these concurrent submissions, and (3)~include anonymized
-versions of those papers in the supplemental material.
+If there are papers that may appear to the reviewers to violate this
+condition, then it is your responsibility to: (1)~cite these papers
+(preserving anonymity as described in Section 1.6 below), (2)~argue in
+the body of your paper why your 3DIMPVT paper is non-trivially
+different from these concurrent submissions, and (3)~include
+anonymized versions of those papers in the supplemental material.
 
 \subsection{Paper length}
-3DIMPVT papers may be between 6 pages and 8 pages. Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
+3DIMPVT papers may be between 6 pages and 8 pages.  Overlength papers
+will simply not be reviewed.  This includes papers where the margins
+and formatting are deemed to have been significantly altered from
+those laid down by this style guide.  Note that this \LaTeX\ guide
+already sets figure captions and references in a smaller font.  The
+reason such papers will not be reviewed is that there is no provision
+for supervised revisions of manuscripts.  The reviewing process cannot
+determine the suitability of the paper for presentation in eight pages
+if it is reviewed in eleven.
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
+The \LaTeX\ style defines a printed ruler which should be present in
+the version submitted for review.  The ruler is provided in order that
 reviewers may comment on particular lines in the paper without
@@
 document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
+appear on the final output pages.  The presence or absence of the
+ruler should not change the appearance of any other content on the
+page.  The camera ready copy should not contain a ruler. (\LaTeX\
+users may uncomment the \verb'\cvprfinalcopy' command in the document
+preamble.)  Reviewers: note that the ruler measurements do not align
+well with lines in the paper --- this turns out to be very difficult
+to do well when the paper contains many figures and equations, and,
+when done, looks ugly.  Just use fractional references (e.g.\ this
+line is $097.15$), although in most cases one would expect that the
+approximate location will be adequate.
 
@@
 Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics.%: \url{http://www.cvpr.org/doc/mermin.pdf}.
+important for readers to be able to refer to any particular equation.
+Just because you didn't refer to it in the text doesn't mean some
+future reader might not need to refer to it.  It is cumbersome to have
+to use circumlocutions like ``the equation second from the top of page
+3 column 1''.  (Note that the ruler will not be present in the final
+copy, so is not an alternative to equation numbers).  All authors will
+benefit from reading Mermin's description of how to write mathematics:
+\url{http://www.cvpr.org/doc/mermin.pdf}.
 
@@
 Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
+review.  Blind review does not mean that one must remove citations to
+one's own work---in fact it is often impossible to review a paper
+unless the previous citations are known and available.
 
@@
 
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith, it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
+Saying ``this builds on the work of Lucy Smith [1]'' does not say that
+you are Lucy Smith, it says that you are building on her work.  If you
+are Smith and Jones, do not say ``as we show in [7]'', say ``as Smith
+and Jones show in [7]'' and at the end of the paper, include reference
+7 as you would any other cited work.
 
@@
 
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
+  In this paper we present a performance analysis of our previous
+  paper [1], and show it to be inferior to all previously known
+  methods.  Why the previous paper was accepted without this analysis
+  is beyond me.
 
@@
 
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
+  In this paper we present a performance analysis of the paper of
+  Smith \etal [1], and show it to be inferior to all previously known
+  methods.  Why the previous paper was accepted without this analysis
+  is beyond me.
 
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
+  [1] Smith, L and Jones, C. ``The frobnicatable foo filter, a
+  fundamental contribution to human knowledge''.  Nature 381(12),
+  1-213.
 \end{quote}
@@
 If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors12} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2012 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
+which covers similar or overlapping material, you may need to refer to
+that submission in order to explain the differences, just as you would
+if you had previously published related work.  In such cases, include
+the anonymized parallel submission~\cite{Authors12} as additional
+material and cite it as
+\begin{quote} [1] Authors. ``The frobnicatable foo filter'', F\&G 2012
+  Submission ID 324, Supplied as additional material {\tt fg324.pdf}.
 \end{quote}
 
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors12b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
+Finally, you may feel you need to tell the reader that more details
+can be found elsewhere, and refer them to a technical report.  For
+conference submissions, the paper must stand on its own, and not {\em
+  require} the reviewer to go to a techreport for further details.
+Thus, you may say in the body of the paper ``further details may be
+found in~\cite{Authors12b}''.  Then submit the techreport as
+additional material.  Again, you may not assume the reviewers will
+read this material.
 
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the 3DIMPVT12 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
+Sometimes your paper is about a problem which you tested using a tool
+which is widely known to be restricted to a single institution.  For
+example, let's say it's 1969, you have solved a key problem on the
+Apollo lander, and you believe that the CVPR70 audience would like to
+hear about your solution.  The work is a development of your
+celebrated 1968 paper entitled ``Zero-g frobnication: How being the
+only people in the world with access to the Apollo lander source code
+makes us a wow at parties'', by Zeus \etal.
 
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
+You can handle this paper like any other.  Don't write ``We show how
+to improve our previous work [Anonymous, 1968].  This time we tested
+the algorithm on a lunar lander [name of lander removed for blind
+review]''.  That would be silly, and would immediately identify the
+authors. Instead write the following:
 \begin{quotation}
   \noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
+  We describe a system for zero-g frobnication.  This system is new
+  because it handles the following cases: A, B.  Previous systems
+  [Zeus et al. 1968] didn't handle case B properly.  Ours handles it
+  by including a foo term in the bar integral.
 
@@
 
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
+  The proposed system was integrated with the Apollo lunar lander, and
+  went all the way to the moon, don't you know.  It displayed the
+  following behaviours which show how well we solved cases A and B:
+  ...
 \end{quotation}
 As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
+reads better than the first version, and does not explicitly name you
+as the authors.  A reviewer might think it likely that the new paper
+was written by Zeus \etal, but cannot make any decision based on that
+guess.  He or she would have to be sure that no other authors could
+have been contracted to solve problem B.
 
@@
     \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
   \end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
+    (always set in Roman: $B \sin A = A \sin B$) may be included
+    without an ugly clash.}
   \label{fig:long}
@@
 The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
+sentence-ending space. So \eg is correct, {\em e.g.} is not.  The
+provided \verb'\eg' macro takes care of this.
 
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
+When citing a multi-author paper, you may save space by using ``et
+alia'', shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}''
+is a complete word.)  However, use it only when there are three or
+more authors.  Thus, the following is correct: `` Frobnication has
+been trendy lately.  It was introduced by Alpher~\cite{Alpher02}, and
+subsequently developed by Alpher and
+Fotheringham-Smythe~\cite{Alpher03}, and Alpher
+\etal~\cite{Alpher04}.''
 
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
+This is incorrect: ``... subsequently developed by Alpher
+\etal~\cite{Alpher03} ...''  because reference~\cite{Alpher03} has
+just two authors.  If you use the \verb'\etal' macro provided, then
+you need not worry about double periods when used at the end of a
+sentence as in Alpher \etal.
 
@@
 
-%------------------------------------------------------------------------
+% ------------------------------------------------------------------------
 \section{Formatting your paper}
 
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
+All text must be in a two-column format. The total allowable width of
+the text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches
+(22.54 cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide,
+with a $\frac{5}{16}$ inch (0.8 cm) space between them. The main title
+(on the first page) should begin 1.0 inch (2.54 cm) from the top edge
+of the page. The second and following pages should begin 1.0 inch
+(2.54 cm) from the top edge. On all pages, the bottom margin should be
+1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5
+\times 11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13
+cm) from the bottom edge of the page.
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{Margins and page numbering}
 
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.  Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)  
-\begin{verbatim}
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
+All printed material, including text, illustrations, and charts, must
+be kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8
+inches (22.54 cm) high.
 
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
-
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{Type-style and fonts}
 
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
+Wherever Times is specified, Times Roman may also be used. If neither
+is available on your word processor, please use the font closest in
 appearance to Times to which you have access.
 
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
+MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge
+of the first page. The title should be in Times 14-point, boldface
+type.  Capitalize the first letter of nouns, pronouns, verbs,
+adjectives, and adverbs; do not capitalize articles, coordinate
+conjunctions, or prepositions (unless the title begins with such a
+word). Leave two blank lines after the title.
 
 AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
+and printed in Times 12-point, non-boldface type. This information is
+to be followed by two blank lines.
 
@@
 Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
+Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should
+be centred.
 
@@
 should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before.
+with one blank line before, and one blank line after.
 
@@
 should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
+with one blank line before, and one after. If you require a
+third-order heading (we discourage it), use 10-point Times, boldface,
+initially capitalized, flush left, preceded by one blank line,
+followed by a period and your text on the same line.
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{Footnotes}
@@
 Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
+  often distracts the reader from the main flow of the argument.}
+sparingly.  Indeed, try to avoid footnotes altogether and include
+necessary peripheral observations in the text (within parentheses, if
+you prefer, as in this sentence).  If you wish to use a footnote,
+place it at the bottom of the column on the page on which it is
+referenced. Use Times 8-point type, single-spaced.
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{References}
@@
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{Illustrations, graphs, and photographs}
 
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
+All graphics should be centered.  Please ensure that any point you
+wish to make is resolvable in a printed copy of the paper.  Resize
+fonts in figures to match the font in the body text, and choose line
+widths which render effectively in print.  Many readers (and
+reviewers), even of an electronic copy, will choose to print your
+paper in order to read it.  You cannot insist that they do otherwise,
+and therefore must not assume that they can zoom in to see tiny
+details on a graphic.
 
 When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
+\verb+\includegraphics+, and to specify the figure width as a multiple
+of the line width as in the example below {\small\begin{verbatim}
     \usepackage[dvips]{graphicx} ...
@@
 
-%-------------------------------------------------------------------------
+% -------------------------------------------------------------------------
 \subsection{Color}
 
-Color is valuable, and will be visible to readers of the electronic copy.
-However ensure that, when printed on a monochrome printer, no important
-information is lost by the conversion to grayscale.
+Color is valuable, and will be visible to readers of the electronic
+copy.  However ensure that, when printed on a monochrome printer, no
+important information is lost by the conversion to grayscale.
 
-%------------------------------------------------------------------------
+% ------------------------------------------------------------------------
 \section{Final copy}
 
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
+You must include your signed IEEE copyright release form when you
+submit your finished paper. We MUST have this form before your paper
+can be published in the proceedings.
 
-{\small
-\bibliographystyle{ieee}
-\bibliography{egbib}
-}
+% Please direct any questions to the production editor in charge of
+% these proceedings at the IEEE Computer Society Press: Phone (714)
+% 821-8380, or Fax (714) 761-1784.
+
+{\small \bibliographystyle{ieee} \bibliography{egbib} }
 

### 2013-05-02 masters/body/assets/_region_.tex
masters

--- 2012-12-23 spie/assets/_region_.tex
@@
 
-\message{ !name(oldpaper.tex) !offset(-3) }
-
-%%%%%%%%% TITLE
-\title{Texture Mapping 3D Planar Models of Indoor Environments with Noisy
-  Camera Poses}
-
-\author{Peter Cheng \hspace*{2em} Michael Anderson \hspace*{2em} Stewart He \hspace*{2em} Avideh Zakhor\\
-  UC Berkeley\\
-}
-\maketitle
-% \thispagestyle{empty}
-
-%%%%%%%%% ABSTRACT
-\begin{abstract}
-  Automated 3D modeling of building interiors is useful in
-  applications such as virtual reality and environment
-  mapping. Applying textures to these models is an important step in
-  generating photorealistic visualizations of data collected by
-  modeling systems. Camera pose recovery in such systems often suffers
-  from inaccuracies, resulting in visible discontinuities when
-  successive images are projected adjacently onto a plane for
-  texturing. We propose two approaches to reduce discontinuities in
-  texture mapping 3D models made of planar surfaces. The first one is
-  tile based and can be used for images and planes at arbitrary angles
-  relative to each other. The second one results in a more seamless
-  texture, but is only applicable where camera axes for images are
-  closely aligned with plane normals of the surfaces to be
-  textured. The effectiveness of our approaches are demonstrated on
-  two indoor datasets.
-\end{abstract}
-
-%%%%%%%%% BODY TEXT
-\section{Introduction}
-\label{sec:introduction}
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and as
-such, automated 3D site modeling has garnered much interest in recent
-years.
-
-The first step in automated 3D modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-recover camera poses within an environment while simultaneously
-reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
-known as the simultaneous localization and mapping (SLAM) problem, and
-is generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment.
-
-Mounting such devices on a platform carried by an ambulatory human
-provides unique advantages over vehicular-based systems on wheels in
-terms of agility and portability, but can also result in larger
-localization error \cite{liu2010indoor}. As a result, common methods
-for texture mapping generally produce poor results.
-
-In this paper, we present a number of approaches to texture mapping 3D
-models of indoor environments made of planar surfaces in the presence
-of uncertainty and noise in camera poses. In particular, we consider
-data obtained from a human-operated backpack system with a number of
-laser range scanners as well as 2 cameras facing left and right, each
-equipped with fisheye lenses reaching an approximately 180$^{\circ}$
-field of view and taking photos at a rate of 5 Hz. Applying multiple
-localization and loop-closure algorithms on the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, the backpack is localized\footnote{In this paper, we
-  use the terms localization and pose recovery interchangeably, in
-  that they both refer to recovering position and orientation.}  over
-its data collection period. This requires recovering the 6 degrees of
-freedom for the backpack as well as the cameras rigidly mounted on
-it. Once this is complete, the data from the laser range scanners is
-used to generate a 3D point cloud of the surrounding environment, from which a
-3D planar model is created \cite{sanchez2012point}. This model, consisting of 2D
-polygonal planes in 3D space, along with the set of images captured by
-the backpack's cameras and their noisy 3D poses, can be considered the
-input to our texture mapping problem.
-
-This problem straddles the fields of image-based localization
-refinement as well as image alignment and mosaicing, and thus our
-proposed solution shares many similarities with past research in those
-areas, which will be examined in Section
-\ref{sec:existingApproaches}. However, we can exploit known
-approximate camera poses as well as the 3D geometry of the environment
-to more accurately and efficiently texture the planes.
-
-The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} describes two variants of a tile-based
-mapping approach and their shortcomings.  Section
-\ref{sec:existingApproaches} discusses past research in related
-fields, demonstrates two previous attempts at improving texture
-alignment, and exhibits their inadequacies for our datasets. Section
-\ref{sec:proposedApproach} presents our proposed seam minimization
-approach to texture mapping. Section \ref{sec:resultsAndConclusions}
-contains results and conclusions.
-
-In all subsequent sections, we discuss the process of texture mapping
-a single plane, as the texturing of each plane is independent and can
-be completed in parallel.
-
-\section{Tile-Based Texture Mapping}
-\label{sec:simpleTextureMapping}
-\begin{figure}
-  \centering
-  \includegraphics[height=2in]{Projection.pdf}
-  \caption{Planes are specified in 3D space by four corners $C_1$ to
-    $C_4$. Images are related to each plane through the camera
-    matrices $P_{1..M}$. }
-  \label{fig:projection}
-\end{figure}
-
-The geometry of the texture mapping process for a plane is shown in
-Figure \ref{fig:projection}.  As described earlier, we are provided
-with a set of $M$ images to texture the target plane. Each image has a
-camera matrix $P_i$ for $i=1..M$, which translates a 3D point in the
-world coordinate system to a 2D point or pixel in image $i$'s
-coordinates. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, such as focal length and image center, as well
-as extrinsic parameters which specify the rotation and translation of
-the camera's position in 3D world coordinates at the time that image
-$i$ is taken. These extrinsic parameters are determined by the
-backpack hardware and localization algorithms \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure} and are quite noisy.
-
-Because the backpack system takes photos at a rate of 5 Hz, thousands
-of images are available for texturing each plane. Our goal in creating
-a texture mapping process is to decide which of these images should be
-used, and where their contents should map onto the texture, in order
-to eliminate any visual discontinuities or seams that would suggest
-that the plane's final texture is not composed of a single continuous
-image.
-
-\subsection{Direct Mapping}
-\label{sec:directMapping}
-
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-we can texture the plane by discretizing it into small square tiles,
-generally about 5 pixels across, and choosing an image to texture each
-tile.
-
-We choose to work with rectangular units to ensure that borders
-between any two distinct images in the final texture are either
-horizontal or vertical. Since most environmental features inside
-buildings are horizontal or vertical, any seams in our texture
-intersect them minimally and are likely to be less noticeable.
-
-In order to select an image for texturing a tile $t$, we must first
-gather a list of candidate images that contain all four of its
-corners, which we can quickly check by projecting $t$ into each image
-using the $P_i$ camera matrices. Furthermore, each candidate image
-must have been taken at a time when its camera had a clear
-line-of-sight to $t$, which can be calculated using standard
-ray-polygon intersection tests between the camera location, the center
-of $t$, and every other plane \cite{rayintersection}.
-
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image. Since camera
-pose errors compound over distance, we wish to minimize the distance
-between cameras and the plane they texture. Additionally, we desire
-images that are projected perpendicularly onto the plane, maximizing
-the resolution and amount of useful texture available in their
-projections, as well as minimizing any parallax effects. In other
-words, we wish to minimize the angle between the plane normal and the
-camera axis for images selected for texture mapping. These two
-criteria can be met by maximizing the function $\frac{1}{d} (-1 \cdot
-\vec{c}) \cdot \vec{n}$ as shown in Figure
-\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
-the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
-the directions of the plane's normal and the camera axis respectively.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=1.5in]{scoringFunction.jpg}
-  \caption{We minimize camera angle $\alpha$ and distance $d$ by
-    maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-    \cdot \vec{n}$}
-  \label{fig:scoringFunction}
-\end{figure}
-
-\begin{figure}[h!]
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_naive.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog_noblend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_cache_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in,
-    height=0.97in]{wall2_dynprog.pdf}}
-  \caption{(a) Direct mapping. (b) Mapping with caching. (c) Mapping
-    with caching after image alignment. (d) Seam minimization after
-    image alignment). (e) same as (c) with blending. (f) same as (d)
-    with blending.}
-  \label{fig:compareAll}
-\end{figure}
-
-As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
-the best texture for each tile independently, but overall results in
-many image boundaries with abrupt discontinuities, due to significant
-misalignment between images, as a result of camera pose inaccuracies.
-
-\subsection{Mapping with Caching}
-\label{sec:mappingWithCaching}
-Since discontinuities occur where adjacent tiles select non-aligned
-images, it makes sense to take into account image selections made by
-neighboring tiles while texture mapping a given tile. By using the
-same image across tile boundaries, we can eliminate a discontinuity
-altogether. If this is not possible because a tile is not visible in
-images chosen by its neighbors, using similar images across tile
-boundaries also leads to less noticeable discontinuities.
-
-Similar to a caching mechanism, we select the best image for a tile
-$t$ by searching through two subsets of images for a viable candidate,
-before searching through the entire set. The first subset of images is
-those selected by adjacent tiles that have already been textured. We
-must first check which of these images can map to $t$, and then of
-those, we make a choice according to the scoring function in Figure
-\ref{fig:scoringFunction}. Before reusing this image, we ensure it
-meets the criteria $\alpha < 45^\circ$, in order to be considered a
-viable image, with $\alpha$ as the camera angle as shown in Figure
-\ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check the
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. These images are not
-the same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar. Again, if no viable image is found
-according to the same criteria, we search the entire set of candidate
-images, selecting based on the same scoring function from Figure
-\ref{fig:scoringFunction}.
-
-The result of this caching approach is shown in Figure
-\ref{fig:compareAll}(b). As compared to Figure
-\ref{fig:compareAll}(a), discontinuities are reduced overall, but the
-amount of remaining seams suggests that image selection alone cannot
-produce seamless textures. Camera matrices, or the image projections
-themselves have to be adjusted in order to reliably generate clean
-textures.
-
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-In order to produce seamless texture mapping, either camera matrices
-need to be refined such that their localization is pixel accurate, or
-image stitching techniques need to be applied to provide this
-illusion.
-
-Image projections can be aligned by refining their noisy camera poses,
-using image correspondences to adjust each image's camera matrix over
-6 degrees of freedom (DOF) \cite{coorg1997matching, liu2010indoor,
-  shum2000systems, szeliski1997creating}. Applying such approaches to
-our datasets however results in error accumulation and drift as shown
-in Figure \ref{fig:mosaic3D}(a), as well as high complexity and
-runtime \cite{liu2010indoor}.
-
-Another common approach to image alignment is to
-iteratively match images on intensity differences in selected patches,
-often in a spatial hierarchy \cite{hager1998efficient,
-  lucas1981iterative, shum2000systems, szeliski2006image}. Another
-widely-used approach is to perform feature matching, which requires
-the detection of visual features and their existence in multiple
-images \cite{brown2007automatic, cho2003automatic,
-  mikolajczyk2005performance, szeliski2006image,
-  yun2003comprehensive}. Notably, both approaches rely on the presence
-of multiple visual references, as when texturing detailed objects at
-high resolutions \cite{bernardinimultiplescans, wangmultipleviews}, or
-when creating large scene panoramas \cite{agarwalapanoramas,
-  bernardinimultiplescans, debevecviewdependent,
-  snavelyphototourism}. In contrast, our indoor datasets have a high
-prevalence of bare walls and ceilings, resulting in few reference
-points that can be used to judge alignment.
-
-Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not
-accurate. For example, when matching a long chain of images through
-homography, a pixel in the $nth$ image must be translated into the
-first image's coordinates by multiplying by the $3\times3$ matrix $H_1
-H_2 H_3 ... H_n$. Any error in one of these homography matrices is
-propagated to all further images, resulting in drift. Figure
-\ref{fig:mosaic3D}(b) shows the output of the AutoStitch software
-package, which performs homography-based image mosaicing
-\cite{autostitch}. Even with many features spread across this plane,
-the mosaicing produces errors that causes straight lines to appear as
-waves on the plane, despite the fact that it is generated after
-careful hand tuning. Many planes with fewer features simply failed
-outright using this approach.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{Graph_crop.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3in]{panoMy.jpg}}
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm from \cite{chen2010indoor} and (b) image
-    mosaicing.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-\section{Seamless Texture Mapping}
-\label{sec:proposedApproach}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{pipeline.pdf}
-  \caption{Our proposed method for seamless texture mapping.}
-  \label{fig:pipeline}
-\end{figure}
-
-In this section, we describe our proposed method for seamless texture
-mapping. Our approach consists of 4 steps, as seen in Figure
-\ref{fig:pipeline}.  First, we project all images onto the plane and
-rotate them for verticality. Next,we perform 2D shifting in order to
-maximize SIFT feature matches in overlapping areas between these
-projections. We then select which textures to be used either with the
-tile caching method from Section \ref{sec:mappingWithCaching}, or with
-the more specialized method to be described in Section
-\ref{sec:seamMinimization}. This choice depends on the availability of
-head-on images for a given plane. We then finish by applying linear
-alpha blending to smooth out any remaining seams.
-
-\subsection{Image Rotation}
-\label{sec:projectionAndRotation}
-We begin with the projection of all images onto the plane. This is
-done in the same way as in Section
-\ref{sec:simpleTextureMapping}. Rather than work with all 6 DOF, which
-is computationally intensive, we choose to work only in two
-dimensions, performing 2D rotations and translations on the image
-projections, as errors in either lead to the greatest discontinuities.
-
-We perform rotations using Hough transforms, which detect the presence
-and orientation of linear features in our images. Rather than match
-the orientation of such features in each image, we simply apply
-rotations such that the strongest near-vertical features are made
-completely vertical. This is effective for vertical planes in indoor
-models, since they usually consist of parallel vertical lines
-corresponding to doors, wall panels, rectangular frames, etc. If
-features in the area are not vertical, e.g. for floors and ceilings,
-this step is skipped.
-
-\subsection{Image Shifting}
-\label{sec:robustSIFTFeatureMatching}
-Our next step is to align overlapping images by searching for
-corresponding points between all pairs of overlapping images. We use
-SIFT features for their high detection rate, and choose to use feature
-alignment rather than intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lai1999robust,
-  lowe1999object, mikolajczyk2005performance, szeliski2006image}.
-
-SIFT matches determine $d^x$ and $d^y$ distances between each pair of
-features for two images on the plane, though these distances may not
-always be the same for different features. Since indoor environments
-often contain repetitive features such as floor tiles or doors, we
-need to ensure that SIFT-based distances are reliable. In order to
-mitigate the effect of incorrect matches and outliers, the RANSAC
-framework \cite{fischler1981random} is used for a robust estimate of
-the optimal $d^x_{i,j}$ and $d^y_{i,j}$ distances between two images
-$i$ and $j$. The RANSAC framework handles the consensus-building
-machinery, and requires a fitting function and a distance
-function. For this application, the fitting function simply finds the
-average distance between matches in a pair of images. The distance
-function for a pair of points is chosen to be the difference between
-those points' SIFT match distance and the average distance computed by
-the fitting function. We use a 10 pixel outlier threshold, so that
-SIFT matches are labeled as outliers if their horizontal or vertical
-distances are not within 10 pixels of the average distance computed by
-the fitting function.
-
-We now use the $d^x_{i,j}$ and $d^y_{i,j}$ distances between each pair
-of images to refine their positions using least squares. Recall that
-there are a total of $M^{2}$ possible pairs of images, though we only
-generate distances between images that overlap at SIFT feature
-points. Given these distances and the original image location
-estimates, we can solve a least squares problem
-($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
-to estimate the location of the images on the plane. The
-$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
-location of each image on the plane for $1 \dots M$. The optimal $x$
-and $y$ locations are obtained in the same way, so we only consider
-the $x$ locations here:
-
-\[\vec{\beta} =
-\begin{pmatrix}
-  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
-\end{pmatrix}
-\]
-
-The $N \times (M+1)$ dimensional matrix $A$ is constructed with one
-row for each pair of images with measured distances produced by the
-SIFT matching stage. A row in the matrix has a $-1$ and $1$ in the
-columns corresponding to the two images in the pair. For example, the
-matrix below indicates a SIFT-based distance between images 1 and 2,
-images 1 and 3, images 2 and 3, etc.
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & \cdots & 0 & 0\\
-  -1 & 0 & 1 & \cdots & 0 & 0\\
-  0 & -1 & 1 & \cdots & 0 & 0\\
-  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
-  0 & 0 & 0 & \cdots & 1 & 0 \\
-  0 & 0 & 0 & \cdots & -1 & 1 \\
-  1 & 0 & 0 & \cdots & 0 & 0 \\
-\end{pmatrix}
-\]
-If only relative distances between images are included then there is
-no way to determine the absolute location of any of the images and the
-matrix becomes rank deficient. To fix this we choose the first image
-to serve as the anchor for the rest, meaning all the absolute
-distances are based on its original location. This is done by adding a
-row with a $1$ in the first column and the rest zeros.
-
-Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is
-constructed using the SIFT-based distances generated earlier in the
-RANSAC matching stage. The last element in the observation vector is
-the location of the first image determined by its original noisy
-localization, from \cite{chen2010indoor, liu2010indoor}. Thus
-$\vec{\gamma}$ can be written as:
-
-\[
-\vec{\gamma}^T =
-\begin{pmatrix}
-  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
-\end{pmatrix}
-\]
-
-The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
-\vec{\gamma}||_2^2$ results in a set of image locations on the plane
-that best honors all the SIFT-based distance measurements between
-images. In practice there is often a break in the chain of images,
-meaning that no SIFT matches are found between one segment of the
-plane and another. In this case we add rows to the $A$ matrix and
-observations to the $\vec{\gamma}$ vector that contain the original
-noisy $x$ and $y$ distance estimates from the original camera
-poses. Another way to do this is to add rows for all neighboring pairs
-of images and solve a weighted least squares problem where the SIFT
-distances are given a higher weight i.e. 1, and the noisy distances
-generated by the original camera poses \cite{chen2010indoor,
-  liu2010indoor} are given a smaller weight e.g. 0.01.
-
-After completing this same process for the $y$ dimension as well, and
-making the resultant shifts, our images overlap and match each other
-with far greater accuracy. Applying the tile caching method from
-Section \ref{sec:mappingWithCaching} on these rotated and shifted
-images results in the significant improvements shown in Figure
-\ref{fig:compareAll}(c), as compared to Figure
-\ref{fig:compareAll}(b).
-
-\subsection{Seam Minimization}
-\label{sec:seamMinimization}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering
-  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
-  \caption{(a) Undistorted fisheye images for vertical planes are
-    tilted, but their effective camera axis is more or less normal to
-    the plane. (b) The effective camera axis for ceilings is at an
-    angle with respect to the plane normal. (c) Wall images are
-    cropped to be rectangular.}
-  \label{fig:projectionAngles}
-\end{figure}
-
-As mentioned earlier, the mobile backpack system used to capture data
-in this paper contains 2 cameras with $180^\circ$ fisheye lenses
-facing to the right and left. Since most human operators do not carry
-the backpack in a perfectly upright position and are bent forwards at
-15 to 20 degrees with respect to the vertical direction, the
-undistorted fisheye images are head on with respect to vertical walls,
-but at an angle with respect to horizontal floors and ceilings. This
-is depicted for wall and ceiling planes in Figures
-\ref{fig:projectionAngles}(a) and \ref{fig:projectionAngles}(b)
-respectively. These oblique camera angles for ceilings translate into
-textures that span extremely large areas once projected, as shown in
-Figure \ref{fig:projectionAngles}(b). Using the tile-based texture
-mapping criteria from Figure \ref{fig:scoringFunction}, such
-projections have highly varying scores depending on the location on
-the plane, as shown in Figure \ref{fig:projectionAngles}(b). Thus, the
-tiling approach in Section \ref{sec:simpleTextureMapping} is a
-reasonable choice for texturing floors and ceilings, as it uses the
-parts of image projections that are viable choices for their
-respective plane locations, e.g. areas near point A in Figure
-\ref{fig:projectionAngles}(b), but not near point B.
-
-For wall planes however, most images are taken from close distances
-and more or less head-on angles, resulting in higher resolution
-fronto-parallel projections. As a result, for each tile on a wall
-plane, the scoring function of Figure \ref{fig:scoringFunction} is
-relatively flat with respect to a large number of captured images, as
-they are all more or less head on. Thus, the scoring function is less
-significant for walls, and it is conceivable to use a different
-texturing strategy for them so as to minimize visible seams in texture
-mapped planes. This can be done by choosing the smallest possible set
-of images that (a) covers the entire plane and (b) minimizes the
-amount of visible seams between them. A straightforward cost function
-that accomplishes the latter is the Sum of Squared Differences (SSD)
-of pixels in overlapping regions between all pairs of images, after
-they have been rotated as described in Section
-\ref{sec:projectionAndRotation}. Minimizing this cost function
-encourages image boundaries to occur either in featureless areas, such
-as bare walls, or in areas where images match extremely well.
-
-To cover the entirety of a plane, our problem can be defined as
-minimally covering a polygon i.e. the plane, using other polygons of
-arbitrary geometry i.e. image projections, with the added constraint
-of minimizing the cost function between chosen images.  This is a
-complex problem, though we can take a number of steps to simplify it.
-
-Given that wall-texture candidate images are taken from more or less
-head-on angles, and assuming only minor rotations are made in Section
-\ref{sec:projectionAndRotation}, we can reason that their projections
-onto the plane are approximately rectangular. By cropping them all to
-be rectangular, as shown in Figure \ref{fig:projectionAngles}(c), our
-problem becomes the conceptually simpler one of filling a polygon with
-rectangles, such that the sum of all costs between each pair of
-rectangles is minimal. We thus also retain the advantages of working
-with rectangular units, as explained in Section
-\ref{sec:simpleTextureMapping}.
-
-The location and orientation of the cameras and the fisheye lenses on
-the acquisition backpack is such that images nearly always contain the
-entirety of the floor to ceiling range of wall planes. Images are
-therefore rarely projected with one above another when texturing wall
-planes. In essence, we need only to ensure lateral coverage of wall
-planes, e.g. from left to right, as our images provide full vertical
-coverage themselves. We can thus construct a Directed Acyclic Graph
-(DAG) from the images, with edge costs defined by the SSD cost
-function, and solve a simple shortest path problem to find an optimal
-subset of images with regard to the cost function \cite{dijkstra}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process. \\}
-  \label{fig:dagCreation}
-\end{figure}
-
-Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a long hallway. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
-between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal cost $C_0$ to(from) all images that
-meet the left(right) border of the plane.
-
-We now solve the shortest path problem from the start node to the end
-node. This results in a set of images completely covering the plane
-horizontally, while minimizing the cost of seams between images.
-
-In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. To address this, we solve for
-a new shortest path after modifying the edges chosen by the original
-shortest path solution such that they have higher cost than all other
-edges in the DAG, and solve for a new shortest path. This ensures that
-these edges are not chosen again unless they are the only available
-option. Our second shortest path solution results in a new set of
-chosen images, of which we only retain those that cover areas not
-covered by the first set. This process can be repeated as many times
-as needed, until holes are no longer present. This method is not as
-optimal as a 2D-coverage solution would be, but it is a fast
-approximation, and adequately handles the few holes we encounter.
-
-With this completed, we have now mapped every location on the plane to
-at least one image, and have minimized the number of images, as well
-as the discontinuities between their borders. As seen in Figure
-\ref{fig:compareAll}(d), this seam minimization method has fewer
-visible discontinuities than Figure \ref{fig:compareAll}(c)
-corresponding to the tile caching approach\footnote{In Figure
-  \ref{fig:compareAll}(d), we arbitrarily chose one image for
-  texturing where images overlap, as blending will be discussed in the
-  next section.}. This is especially evident when comparing the
-posters in the images, which have clear misalignment over seams in
-Figure \ref{fig:compareAll}(c), but are much more aligned in Figure
-\ref{fig:compareAll}(d). This is because the seam minimization
-approach directly reduces the cost of each image boundary, while the
-tile caching method uses a scoring function that only approximates
-this effect. Furthermore, seam minimization guarantees the best
-selection of images, while the sequential tile caching method may
-select images early on that turn out to be poor choices once
-subsequent tiles have been processed. The seam minimization approach
-is also far less intensive in terms of memory usage and runtime, both
-during texture generation and rendering, as it does not require
-discretizing planes or images\footnote {For the seam minimization
-  approach, occlusion checks are performed over the entirety of each
-  image to determine available areas for texture mapping. Since indoor
-  environments mostly consist of vertical or horizontal surfaces with
-  high amounts of right angles, image projections remain largely
-  rectangular after masking out occluded areas. Therefore, as a
-  preprocessing step, we can recursively split each image into
-  rectangular pieces and check for occlusions in a similar manner as
-  in the tiling process.  }.
-
-In the context of texturing an entire 3D planar model, we choose to
-apply the seam minimization approach on walls, due to its superior
-output when provided with head-on images. Floors and ceilings however,
-given their many images taken at oblique angles, are textured using
-the tile caching method.
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=6in]{pipelineimages.pdf}
-%   \caption{Textures corresponding to each step in our texture
-%   mapping pipeline.}
-%   \label{fig:pipelineimages}
-% \end{figure*}
-
-\subsection{Blending}
-\label{sec:blending}
-We now apply the same blending process to the two texturing methods:
-image alignment followed by either tile caching or seam minimization.
-
-Although the preprocessing steps and image selection in both methods
-attempt to minimize all mismatches between images, there are
-occasional unavoidable discontinuities in the final texture due to
-different lighting conditions or inaccuracies in planar geometry or
-projection. These can however be treated and smoothed over by applying
-alpha blending over image seams.  Whether the units we are blending
-are rectangularly-cropped images or rectangular tiles, we can apply
-the same blending procedure, as long as we have a guaranteed overlap
-between units to blend over.
-
-For the tile caching method, we can ensure overlap by texturing a
-larger tile than needed for display. For example, for a rendered tile
-$l_1 \times l_1$, we can associate it with a texture $(l_1 + l_2)
-\times (l_1 + l_2)$ in size. For the seam minimization method, we have
-already ensured overlap between images. To enforce consistent blending
-however, we add a minimum required overlap distance while solving the
-shortest path problem in Section
-\ref{sec:seamMinimization}. Additionally, if images overlap in a
-region greater than the overlap distance, we only apply blending over
-an area equal to the overlap distance.
-
-After blending pixels linearly across overlapping regions using alpha
-blending, texture mapping is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
-is clear that the seam minimization approach still exhibits better
-alignment and fewer seams than the tile-caching method, as Figure
-\ref{fig:compareAll}(f) has the best visual quality among the textures
-in Figure \ref{fig:compareAll}.
-
+\message{ !name(oldpaper.tex) !offset(667) }
 \section{Results and Conclusions}
@@
 
+\message{ !name(oldpaper.tex) !offset(665) }
+
 \end{document}
-
-\message{ !name(oldpaper.tex) !offset(-739) }

### 2013-05-02 masters/body/masters.tex
masters

--- 2013-03-03 spie/paper.tex
@@
-%  article.tex (Version 3.3, released 19 January 2008)
-%  Article to demonstrate format for SPIE Proceedings
-%  Special instructions are included in this file after the
-%  symbol %>>>>
-%  Numerous commands are commented out, but included to show how
-%  to effect various options, e.g., to print page numbers, etc.
-%  This LaTeX source file is composed for LaTeX2e.
+\documentclass[]{spie}  %>>> use for US letter paper
 
-%  The following commands have been added in the SPIE class 
-%  file (spie.cls) and will not be understood in other classes:
-%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
-%  The bibliography style file is called spiebib.bst, 
-%  which replaces the standard style unstr.bst.
-
-\documentclass[]{spie}  %>>> use for US letter paper
-%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
-%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
-%% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
-%  The following command loads a graphics package to include images 
-%  in the document. It may be necessary to specify a DVI driver option,
-%  e.g., [dvips], but that may be inappropriate for some LaTeX 
-%  installations. 
 \usepackage{graphicx}
@@
 \usepackage{multirow}
-\title{Texture mapping 3D planar models of indoor environments with noisy camera poses}
 
-%>>>> The author is responsible for formatting the 
-%  author list and their institutions.  Use  \skiplinehalf 
-%  to separate author list from addresses and between each address.
-%  The correspondence between each author and his/her address
-%  can be indicated with a superscript in italics, 
-%  which is easily obtained with \supit{}.
+\title{Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses}
 
-\author{Peter Cheng, Michael Anderson, Stewart He, and Avideh Zakhor
+\author{Peter Cheng
 \skiplinehalf
@@
 }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%>>>> uncomment following for page numbers
-% \pagestyle{plain}    
-%>>>> uncomment following to start page numbering at 301 
-%\setcounter{page}{301}
 
@@
   projected onto a surface for texturing. We present a method for
-  texture mapping that starts by selecting images whose camera poses
-  are well-aligned in two dimensions. We then align images to geometry
-  as well as to each other, producing visually consistent textures
-  even in the presence of inaccurate surface geometry and noisy camera
-  poses. The final step is to select and composite images into a
-  texture mosaic. The effectiveness of the proposed method is
-  demonstrated on a number of different indoor environments.
+  texture mapping models of indoor environments that starts by
+  selecting images whose camera poses are well-aligned in two
+  dimensions. We then align images to geometry as well as to each
+  other, producing visually consistent textures even in the presence
+  of inaccurate surface geometry and noisy camera poses. Images are
+  then composited into a final texture mosaic and projected onto
+  surface geometry for visualization. The effectiveness of the
+  proposed method is demonstrated on a number of different indoor
+  environments.
 \end{abstract}
@@
 virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and as
-such, automated 3D site modeling has garnered much interest in recent
-years.
+construction of these digital models can be time consuming, and
+consequently automated 3D site modeling has garnered much interest in
+recent years.
 
@@
 within the environment. Mounting such devices on a platform carried by
-an ambulatory human provides unique advantages over vehicular-based
-systems on wheels in terms of agility and portability, but can also
-result in larger localization error \cite{liu2010indoor}. As a result,
-common methods for texture mapping generally produce poor results.
-
-In this paper, we present an approach to texture mapping 3D models of
-indoor environments made of planar surfaces in the presence of
+an ambulatory human provides unique advantages over static or
+vehicular-based systems on wheels in terms of agility and portability,
+but can also result in larger localization error
+\cite{liu2010indoor}. As a result, common methods for texture mapping
+generally produce poor results. In this paper, we present an approach
+to texture mapping 3D models of indoor environments in the presence of
 uncertainty and noise in camera poses. In particular, we consider data
-obtained from a human-operated backpack system with a number of laser
-range scanners as well as 2 cameras facing left and right, each
-equipped with fisheye lenses reaching an approximately 180$^{\circ}$
-field of view and taking photos at a rate of 5 Hz. Applying multiple
-localization and loop-closure algorithms on the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, the backpack is localized\footnote{In this paper, we
-  use the terms localization and pose recovery interchangeably, in
-  that they both refer to recovering position and orientation.}  over
-its data collection period. This requires recovering the 6 degrees of
-freedom for the backpack itself as well as the cameras rigidly mounted
-on it. Once this is complete, the data from the laser range scanners
-is used to generate a 3D point cloud of the surrounding environment,
-from which a 3D planar model is created \cite{sanchez2012point}. This
-model, consisting of 2D polygonal planes in 3D space, along with the
-set of images captured by the backpack's cameras and their noisy 3D
-poses, can be considered the input to our texture mapping problem.
+obtained from a human-operated backpack system, detailed in Section
+\ref{sec:dataAcquisitionSystem}.
 
@@
   \includegraphics[width=6in]{flowchart.jpg}
-  \caption{The proposed texture mapping procedure\\}
+  \caption{The proposed texture mapping procedure ***this will
+    change\\}
   \label{fig:flowchart}
@@
 The overall block diagram for the proposed texture mapping procedure
-is shown in Figure \ref{fig:flowchart}. We texture map each planar
-surface independently and in parallel. For each surface, we begin by
-obtaining a set of images that spans the entire surface with high
-resolution imagery. We then use our noisy camera poses to project
-these selected images onto the surface. These projections are then
-refined in 2D, in order to maximally align them with the surface's
-geometry, as well as to each other, allowing us to handle both errors
-in geometry as well as camera poses. For surfaces and camera poses at
-arbitrary locations or orientations, generally ceilings and floors, we
-propose a tile-based approach for sampling high-resolution portions of
-images and compositing them into a texture. In cases where cameras
-have consistently perpendicular viewing angles to the surfaces under
-consideration, generally walls, we demonstrate a superior approach
-that leads to more seamless textures.
+is shown in Figure \ref{fig:flowchart}, where the number attached
+attached to each box indicates the section in which the concept in the
+box is explained in this paper ***will change. First, the geometry of
+an environment is split into regions. For each region, we begin by
+selecting a set of images that spans the entire region's surface with
+high resolution imagery. We then use recovered noisy camera poses to project
+these selected images onto the surface. These projections are rotated
+and translated in 2D, in order to maximally align them with the
+surface's geometry, as well as to each other, allowing us to handle
+both errors in geometry as well as camera poses. For surfaces and
+camera poses at arbitrary locations or orientations, generally
+ceilings and floors, we propose a tile-based approach for sampling
+high-resolution portions of images and compositing them into a
+texture. In cases where cameras have consistently perpendicular
+viewing angles to the surfaces under consideration, generally walls,
+we demonstrate a superior approach based on a shortest-path
+computation that leads to more seamless textures.
 
 The remainder of the paper is organized as follows. Section
+\ref{sec:dataAcquisitionSystem} describes our data acquisition system
+as well as our region segmentation procedure. Section
 \ref{sec:existingApproaches} covers existing approaches to image
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Data Acquisition}
+\label{sec:dataAcquisition}
 
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
+\begin{figure}
+  \centering
+  \includegraphics[width=3in]{backpackCAD.png}
+  \caption{CAD model of the backpack system.}
+  \label{fig:backpack}
+\end{figure}
+
+A CAD model of the backpack-mounted system is shown in Figure
+\ref{fig:backpack}. This backpack system has a number of laser range
+scanners as well as 2 cameras facing left and right, each equipped
+with fisheye lenses reaching an approximately 180$^{\circ}$ field of
+view each and taking photos at a rate of 5 Hz \cite{liu2010indoor}. In
+order to collect data, an operator wears the
+backpack system and traverses the environment to be scanned, walking
+in straight lines at a standard pace and making an effort to walk
+parallel to all walls in the area. Multiple localization and
+loop-closure algorithms are then applied to the raw data collected by
+the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
+  liu2010indoor}, and the backpack is localized\footnote{In this
+  paper, we use the terms localization and pose recovery
+  interchangeably, in that they both refer to recovering position and
+  orientation.}  over its data collection period. This involves
+recovering the 6 degrees of freedom for the backpack itself as well as
+the cameras rigidly mounted on it. Once this is complete, the data
+from the laser range scanners is used to generate a 3D point cloud of
+the surrounding environment. This point cloud is used to construct
+either a low-resolution planar model, such as for usage in basic
+navigation or energy analysis \cite{sanchez2012point,
+  turnerfloorplane}, or a high-resolution, detailed triangular mesh,
+for applications such as accurate remodeling or virtual walkthroughs
+\cite{turnerwatertight}.  Regardless of resolution, size, or detail,
+the model, consisting of geometric surfaces in 3D space, along with
+the set of images captured by the backpack's cameras and their noisy
+3D poses, are the input to our texture mapping problem.
+
+\subsection{Geometry Partitioning}
+\label{sec:geometryPartioning}
+In order to effectively texture a 3D model, we first divide the model
+into a set of regions, each to be textured independently. The purpose
+of this is to ensure texture continuity along large uniform areas,
+while allowing texture boundaries to fall along natural environmental
+boundaries. Because textures may not match at such boundaries where
+two regions meet, it is important to minimize the visibility of
+boundaries. This is done by encouraging region boundaries to occur at
+large sharp corners, where texture continuity is less important.
+
+When working with low-resolution models, where surfaces generally
+correspond to large planar features such as walls, ceilings, or
+floors, and often meet at right angles, each planar surface in the
+model is directly treated as a distinct region and textured
+separately.
+
+When working with a high-resolution model however, geometry often
+represents large features as well as small details found in furniture,
+plants, and other miscellaneous objects. For instance, in Figure
+\ref{fig:deskGeom}(a), the geometry modeling the desk and binders
+consists of many small triangles at various orientations. Texturing
+each of these triangles independently makes little sense, as the
+textures applied to each should match up well with the textures of its
+neighbors in order to avoid any breaks in the overall image of the
+desk and binders. On the other hand, the textures for the triangles
+belonging to the wall behind need not match up with the textures on
+the desk and binders, and so each group of triangles should be
+designated to separate regions. This region grouping is performed by
+designating all contiguous coplanar groups of triangles as different
+regions. Any region that is less than $1 m^2$ in size is joined to its
+largest neighboring region, such that the angle between them is under
+$90^{\circ}$. An example of such a grouping is shown in
+\ref{fig:deskGeom}(b).
+
+Though most regions are not completely flat, we fit a plane to each
+region for the purposes of texturing. This plane corresponds to the
+largest contiguous section of coplanar triangles, as most regions are
+characterized by small outcroppings from a largely planar surface,
+such as objects on a table or features protruding from a wall. The 3d
+vertices within a region are then projected onto its calculated plane,
+and the 2D contour for these projected vertices is calculated.
+
+Of course, the 2D contour of a region is not as accurate as its
+original 3D geometry. Thus, we also create a k-d tree consisting of
+the triangle primitives from the original mesh. Though textures are
+generated upon the 2D planar surface, the original 3D geometry in the
+k-d tree is referenced to ensure accuracy at various stages when
+texturing.
+
+At this point, we either have a series of planar regions, or planar
+approximations for regions and an associated k-d tree. The task now is
+to generate a texture for each region, though first some related work
+will be discussed.
+
+\section{Related Work}
+\label{sec:relatedWork}
 There are many existing approaches to stitching together multiple
@@
   debevechybrid, bernardinimultiplescans}. Generally, parts of images
-are matched to each other, either through direct comparisons or
-feature detection and matching. Images are then transformed to
-maximize matches, often by computing homographies between pairs of
-images, or by iteratively adjusting camera poses in 1 to 6 degrees of
-freedom.
+are matched to each other, either through direct comparisons at pixel
+level, or through feature detection and matching. Images are then
+transformed to maximize matches, often by computing homographies
+between pairs of images, or by iteratively adjusting camera poses in 1
+to 6 degrees of freedom.
 
@@
 with the iterative global localization algorithm used to recover the 6
-degrees of freedom of the backpack acquisition system
-\cite{liu2010indoor}. When run on long chains of images, especially
-where features are sparse, this approach produces distorted textures,
-as seen in Figure \ref{fig:mosaic3D}(a). Furthermore, this approach is
-not closed-form, and its iterative camera adjustment process over
-large datasets led to prohibitively long computation time.
+degrees of freedom of the backpack acquisition system detailed in
+Section \ref{sec:dataAcquisitionSystem} \cite{liu2010indoor}. When run
+on long chains of images however, especially where features are
+sparse, this approach produces distorted textures, as seen in Figure
+\ref{fig:mosaic3D}(a). Furthermore, this approach is not closed-form,
+and its iterative camera adjustment process over large datasets leads
+to prohibitively long computation time.
 
-The AutoStitch software package performs homography-based alignment as
-well, with additional provisions that attempt to reduce drift and
-increase efficiency \cite{panorama2d, autostitch}. Though AutoStitch
-performs well in areas with dense features, it can not handle areas
-without features, and has trouble aligning wall sections with even
+The AutoStitch software package, based on research in the area of
+panorama genoration, performs homography-based alignment as well, with
+additional provisions that attempt to reduce drift and increase
+overall efficiency \cite{panorama2d, autostitch}. Though AutoStitch
+performs well in small areas, it often stiff induces drift in images,
+such that global alignment to the environment geometry is
+lost. Furthermore, its performance relies on the presence of a dense
+set of features, and it has trouble aligning wall sections with even
 short segments of bare texture. The example in Figure
-\ref{fig:mosaic3D}(b) has been generated after many rounds of manual
+\ref{fig:mosaic3D}(b) was generated after many rounds of manual
 tuning; we have empirically found that areas with fewer visual
@@
 \section{Image Selection}
-\label{sec:simpleTextureMapping}
+\label{sec:imageSelection}
 
-The geometry of the texture mapping process for a planar surface is
-shown in Figure \ref{fig:projection}. Given a set of $M$ images to
-texture a target plane, camera matrix $P_i$ for the $ith$ image
-transforms a 3D point in the world coordinate system to a 2D point or
-pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
-the camera's intrinsic parameters, containing focal length and image
-center, as well as extrinsic parameters which specify the rotation and
+The geometry of the texture mapping process for a region, as described
+in Section \ref{sec:geometryPartitioning}, is shown in Figure
+\ref{fig:projection}. Given a set of $M$ images to texture a target
+plane, camera matrix $P_i$ for the $ith$ image transforms a 3D point
+in the world coordinate system to a 2D point or pixel in image $i$'s
+coordinates. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, containing focal length and image center, as
+well as extrinsic parameters which specify the rotation and
 translation of the camera's position in 3D world coordinates at the
@@
 
-Since the backpack system takes pictures at a rate of 5 Hz, hundreds
+Since the backpack system takes pictures at a rate of 5 Hz, thousands
 of images are available for texturing each surface in the 3D
@@
 texture is not composed of a single continuous image. In the remainder
-of this section, we propose an image selection criteria and use it to
-derive a simple tile-based texture mapping procedure.
+of this section, we propose an image subsampling procedure and use it
+to derive a simple tile-based texture mapping procedure.
 
@@
 
-Given the large number of input images, it is possible to develop a
-more sophisticated image selection procedure, as described in Section
-\ref{sec:imageCompositing}, however, a more significant and reliable
-improvement can be found through first improving the alignment of the
-images as shown in the next section.
-
 \begin{figure}
@@
     image alignment; (c) Tile-based texturing after image alignment
-    with caching; (d) Shortest path texturing after image
-    alignment; (e,f) Blending applied to (c) and (d); (g,h) Zoomed
-    in views of discontinuities in (e) vs. in (f).}
+    with caching; (d) Shortest path texturing after image alignment;
+    (e,f) Blending applied to (c) and (d); (g,h) Zoomed in views of
+    discontinuities in (e) vs. in (f).}
   \label{fig:compareAll}
@@
 of image-based line segments by using Hough transforms to detect lines
-in the image projections. We then gather a set of geometry-based
-lines, which correspond to the lines comprising the target surface's
-border, as well as lines formed where other surfaces intersect the
-target surface. An example of these lines is shown in red for a
-ceiling surface in Figure \ref{fig:geometryAlignment}(a). Ideally, for
-perfect camera poses and surface geometry, the lines in images
-corresponding to corners between surfaces should match up exactly with
-corners in the 3D model. By inducing such lines to match, we fit
-camera poses more accurately to the surface, and to each other as
-well.
+in the image projections. These lines are detected in the image
+projections rather than the original images, as the varying
+orientation and distances of camera poses relative to surfaces results
+in high variance of line lengths and strengths for real-world linear
+features across the original images. We also gather a set of
+geometry-based lines, which correspond to the lines comprising the
+target surface's border, as well as lines formed where other surfaces
+intersect the target surface. An example of these lines is shown in
+red for a ceiling surface in Figure
+\ref{fig:geometryAlignment}(a). Ideally, for perfect camera poses and
+surface geometry, the lines in images corresponding to corners between
+surfaces should match up exactly with corners in the 3D model. By
+inducing such lines to match, we fit camera poses more accurately to
+the surface, and to each other as well.
 
@@
 which is resolved by matching the midpoint of the image-based line in
-the second pair to its corresponding geometry-based line. This
-corresponds to case (1) of Figure
-\ref{fig:geometryAlignment}(c). Thus, with 2 or more pairs, it is
-possible to obtain a fixed rotation and translation, which are saved
-for usage in Section \ref{sec:robustSIFTFeatureMatching}.
+the second pair to its corresponding geometry-based line. This is
+shown in case (1) of Figure \ref{fig:geometryAlignment}(c). Thus, with
+2 or more pairs, it is possible to obtain a fixed rotation and
+translation, which are saved for usage in Section
+\ref{sec:robustSIFTFeatureMatching}.
 
@@
 ambiguity however, can not be resolved, but is also saved to be used
-in Section \ref{sec:robustSIFTFeatureMatching}. This corresponds to
-case (2) of Figure \ref{fig:geometryAlignment}(c). Finally, in the
-case where there are no line pairs, we can still rotate images in
-order to exploit patterns in indoor environments (case (3) of Figure
-\ref{fig:geometryAlignment}(c)). For instance, doors, windows,
+in Section \ref{sec:robustSIFTFeatureMatching}. This is shown in case
+(2) of Figure \ref{fig:geometryAlignment}(c). Finally, in the case
+where there are no line pairs, we can still rotate images in order to
+exploit patterns in indoor environments, as shown in case (3) of
+Figure \ref{fig:geometryAlignment}(c). For instance, doors, windows,
 furniture, etc. tend to have linear edges that are parallel to the
@@
 surfaces, as shown in Figure \ref{fig:geometryAlignment}(b), which is
-considerably more aligned than Figure \ref{fig:geometryAlignment}(a)
-is. This procedure reconciles both errors in camera poses as well as
-in geometry, and results in sharp, continuous borders across images,
-which is crucial when checking for occlusion.
+considerably more aligned than Figure
+\ref{fig:geometryAlignment}(a). This procedure reconciles both errors
+in camera poses as well as in geometry, and results in sharp,
+continuous borders across images, which is crucial when checking for
+occlusion.
 
@@
 performing ray-polygon intersection tests between the camera location
-and other surfaces \cite{rayintersection}. These intersection tests
-are performed at the corners of a grid overlaid upon the target
-surface. Where all four corners of a grid section are occluded,
-texture is removed. Where one or more corners are occluded, the grid
-is subdivided into four, and the process repeats. Occlusion checking
-works entirely with geometry, so by ensuring that images match
-geometry using \ref{sec:geometryAlignment}'s alignment procedure,
-texture belonging to other surfaces is accurately removed, as seen in
-Figure \ref{fig:occlusion}(b).
+and every surface in our model except the target surface
+\cite{rayintersection}. These intersection tests are performed at the
+corners of a grid overlaid upon the target surface. Where all four
+corners of a grid section are occluded, texture is removed. Where one
+or more corners are occluded, the grid is subdivided into four, and
+the process repeats. Occlusion checking works entirely with geometry,
+so by ensuring that images match geometry using
+\ref{sec:geometryAlignment}'s alignment procedure, texture belonging
+to other surfaces is accurately removed, as seen in Figure
+\ref{fig:occlusion}(b).
 
@@
 \label{sec:imageCompositing}
-In Section \ref{sec:mappingWithCaching}, we refine the tile-based
-texturing approach from Section \ref{sec:simpleTextureMapping}, with
-an added caching mechanism to reduce image boundaries. This method is
-general and works well given arbitrary camera poses and surfaces such
-as walls, floors, and ceilings. For special cases where images have
-consistently perpendicular viewing angles to the surfaces under
-consideration, such as walls, it is possible to develop an alternative
-method in Section \ref{sec:shortestPath} to further reduce visual
-artifacts. Both of these approaches are followed by a blending step in
-order to produce final textures for each surface, as shown in Figure
+In Section \ref{sec:simpleTextureMapping} we described an image
+selection method that reduces the list of candidate images for
+texturing by a factor of 10. In this section we go one step further to
+choose a subset of the above candidates in order to further reduce
+visual artifacts and discontinuities across textured
+surfaces. Specifically, in Section \ref{sec:mappingWithCaching}, we
+refine the tile-based texturing approach from Section
+\ref{sec:simpleTextureMapping}, with an added caching mechanism to
+reduce image boundaries. This method is general and works well given
+arbitrary camera poses and surfaces such as walls, floors, and
+ceilings. For special cases where images have consistently
+perpendicular viewing angles to the surfaces under consideration, such
+as walls, it is possible to develop an alternative method in Section
+\ref{sec:shortestPath} to further reduce visual artifacts. Both of
+these approaches are followed by a blending step in order to produce
+final textures for each surface, as shown in Figure
 \ref{fig:flowchart}.
@@
 the first subset, both spatially and temporally. We use the noisy
-camera poses to determine priority. These images are not the same as
-the ones used for neighboring tiles, but are taken at a similar
-location and time, suggesting that their localization and projection
-are quite similar, and thus likely match more seamlessly. If no viable
-image is found according to the $\alpha < 45^\circ$ criteria, we
-search the entire set of candidate images from Section
-\ref{sec:simpleTextureMapping}, selecting based on the same scoring
-function from Figure \ref{fig:scoringFunction}.
+camera poses to determine spatial proximity. These images are not the
+same as the ones used for neighboring tiles, but are taken at a
+similar location and time, suggesting that their localization and
+projection are quite similar, and thus likely match more
+seamlessly. If no viable image is found according to the $\alpha <
+45^\circ$ criteria, we search the entire set of candidate images from
+Section \ref{sec:simpleTextureMapping}, selecting based on the same
+scoring function from Figure \ref{fig:scoringFunction}.
 
@@
 Section \ref{sec:simpleTextureMapping} and aligned in Section
-\ref{sec:robustSIFTFeatureMatching} such that it (a) covers the entire
-plane and (b) minimizes the visibility of borders between the
-images. A straightforward cost function that accomplishes the latter
-is the sum of squared differences (SSD) of pixels in overlapping
-regions between all pairs of images. Minimizing this cost function
-encourages image boundaries to occur either in featureless areas, such
-as bare walls, or in areas where images match extremely well.
+\ref{sec:2dAlignment} such that it (a) covers the entire plane and (b)
+minimizes the visibility of borders between the images. A
+straightforward cost function that accomplishes the latter is the sum
+of squared differences (SSD) of pixels in overlapping regions between
+all pairs of images. Minimizing this cost function encourages image
+boundaries to occur either in featureless areas, such as bare walls,
+or in areas where images match extremely well.
 
@@
 
-We have now mapped every location on the plane to at least one image,
-and have decreased the number of images, generally retaining around
-20\% of the image subset obtained in Section
-\ref{sec:simpleTextureMapping}, as well as the discontinuities at each
-image border. As seen in Figure \ref{fig:compareAll}(d), this shortest
-path method has fewer visible discontinuities than Figure
+We have now (a) mapped every location on the plane to at least one
+image, (b) decreased the number of texturing images, generally
+retaining around 20\% of the image subset obtained in Section
+\ref{sec:simpleTextureMapping}, and (c) decreased the discontinuities
+at each image border. As seen in Figure \ref{fig:compareAll}(d), this
+shortest path method has fewer visible discontinuities than Figure
 \ref{fig:compareAll}(c) corresponding to the tile caching
@@
 textures in Figure \ref{fig:compareAll}.
+
+\section{Visualization}
+\label{sec:visualization}
 

### 2013-05-02 masters/body/newpaper.tex
masters

--- 2013-01-18 spie/newpaper.tex
@@
 Three-dimensional modeling of indoor environments has a variety of
-applications in fields such as architecture and simulation. Adding
-accurate textures to these models is important in adding context to
-digital visualizations, and allows for image-based analysis of
-environments.  In this paper, we work with a backpack-mounted system,
-carried by an ambulatory human. This backpack system contains a series
-of laser scanners and inertial measurement units, allowing it to solve
-the simultaneous localization and mapping (SLAM) problem, which
-produces backpack poses over time, and a point cloud representing its
-environment. For our environment geometry, we work with models
-obtained by fitting low-resolution planar surfaces to these point
-clouds.  While a human-carried system provides advantages over more
-common wheel-mounted systems in terms of agility and portability, it
-often leads to relatively high localization error even after applying
+applications in fields such as architecture, conservation, and
+simulation. Applying accurate textures to these models is important in
+adding context to digital visualizations, and allows for image-based
+analysis of environments. In this paper, we perform data acquisition
+with a backpack-mounted system carried by an ambulatory human. This
+backpack system contains a series of laser scanners and inertial
+measurement units, allowing it to solve the simultaneous localization
+and mapping (SLAM) problem, which produces backpack poses over time as
+well as a point cloud representing the surrounding environment. For
+environment geometry, we work with models obtained by fitting
+low-resolution planar surfaces to these point clouds.  While a
+human-carried system provides advantages over more common
+wheel-mounted systems in terms of agility and portability, it often
+leads to relatively high localization error even after applying
 sophisticated localization techniques. Furthermore, our model geometry
-often contains some error as well, and is often adjusted to ignore
-low-resolution features, such as small walls, furniture, and various
-small features commonly found in indoor environments. As a result,
-methods for texture mapping that rely on accurate camera poses
-generally produce poor results.
+usually contains some error as well, and is often tuned to ignore
+low-resolution features, such as small walls, furniture, and other
+small non-planar features commonly found in indoor environments. As a
+result, methods for texture mapping that rely on accurate camera poses
+and projection surfaces generally produce poor results.
 
@@
 stitching, panorama generation, and image-based localization
-algorithims. We will examine the results of existing approaches in
-Section X, and compare them with our approach, which utilizes several
-aspects of our modeling system and input data.
+algorithims. We will examine the results of two existing approaches
+from these fields of study in Section X, and compare them with our
+approach, which utilizes several unique aspects of our modeling system
+and input data.
 
-The remainder of the paper is organized as follows.
-Section X demonstrates 2 existing algorithms on our datasets and discusses unique aspects of our modeling system.
-Section X describes the basics of image projection, and a tile-based mapping approach and its shortcomings.
-Section X presents our approach towards image alignment, followed by Section X, which describes our two methods of compositing images.
-Section X contains results and conclusions.
+The remainder of the paper is organized as follows. Section X
+demonstrates 2 existing image stitching algorithms on our
+datasets. Section X explains how images are projected onto our
+geometry, and a simple approach towards texturing. Section X contains
+our approach towards image alignment, followed by Section X, which
+describes our two methods of compositing images. Section X contains
+results and conclusions.
+
+\section{Existing Approaches}
+Stitching together multiple images to produce a larger image is a
+commonly performed task, with many successful approaches over the past
+years. Generally, parts of images are first matched to eachother,
+usually through direct comparisons or feature detection and
+matching. Images are then transformed to maximize matches, often by
+calculating homographies between pairs of images, or by modifying
+camera poses in 1 to 6 degrees of freedom.
+
+Feature matching has a number of advantages over direct matching that
+make it more suitable for our data, which is X. Feature matching
+however, works best when multiple unique visual references exist in the
+environment that can be detected in multiple images. In contrast, our
+indoor environments have a high prevalence of bare surfaces, as well
+as repeating textures that cause difficulty in disambiguating
+features. This lack of reliable reference points often results in
+errors when matching images together.
+
+Additionally, our datasets often contain long chains of images, which
+leads to error accumulation when image correspondences are not
+exact. For example, when matching a long chain of images through
+homographies, a pixel in the $nth$ image is translated into the first
+image's coordinates by multiplying by the $3\times3$ matrices $H_1 H_2
+H_3 ... H_n$. Errors in any of these homography matrices are
+propagated to all further images, resulting in drift.
+
+Past work with our data acquisition backpack integrated image
+stitching with localization algorithms, and performed homography-based
+alignment. As described above, this often resulted in drift, as shown in Figure X. This approach is also tied into a localization
+algorithm, and its iterative camera adjustment process over our large
+datasets leads to prohibitively long runtime.
+
+Drift during image stitching can be combated using X. The AutoStitch software package
+contains X. Though AutoStitch performs well in areas with dense
+features, it can not handle even short segments of bare walls. The example in Figure X was generated after manual tuning, and areas with fewer visual
+features or repeating texture patterns simply failed outright with AutoStitch.
 

### 2013-05-02 masters/body/template.tex
masters

%  article.tex (Version 3.3, released 19 January 2008)
%  Article to demonstrate format for SPIE Proceedings
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, e.g., to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class 
%  file (spie.cls) and will not be understood in other classes:
%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
%  The bibliography style file is called spiebib.bst, 
%  which replaces the standard style unstr.bst.

\documentclass[]{spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
%  The following command loads a graphics package to include images 
%  in the document. It may be necessary to specify a DVI driver option,
%  e.g., [dvips], but that may be inappropriate for some LaTeX 
%  installations. 
\usepackage[]{graphicx}

\title{Style template and guidelines for SPIE Proceedings}

%>>>> The author is responsible for formatting the 
%  author list and their institutions.  Use  \skiplinehalf 
%  to separate author list from addresses and between each address.
%  The correspondence between each author and his/her address
%  can be indicated with a superscript in italics, 
%  which is easily obtained with \supit{}.

\author{Anna A. Author1\supit{a} and Barry B. Author2\supit{b}
\skiplinehalf
\supit{a}Affiliation1, Address, City, Country; \\
\supit{b}Affiliation2, Address, City, Country
}

%>>>> Further information about the authors, other than their 
%  institution and addresses, should be included as a footnote, 
%  which is facilitated by the \authorinfo{} command.

\authorinfo{Further author information: (Send correspondence to A.A.A.)\\A.A.A.: E-mail: aaa@tbk2.edu, Telephone: 1 505 123 1234\\  B.B.A.: E-mail: bba@cmp.com, Telephone: +33 (0)1 98 76 54 32}
%%>>>> when using amstex, you need to use @@ instead of @

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%>>>> uncomment following for page numbers
% \pagestyle{plain}    
%>>>> uncomment following to start page numbering at 301 
%\setcounter{page}{301}

  \begin{document} 
  \maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.  It contains general formatting instructions and hints about how to use LaTeX.  The LaTeX source file that produced this document, {\tt article.tex} (Version 3.3), provides a template, used in conjunction with {\tt spie.cls} (Version 3.3).  
\end{abstract}

%>>>> Include a list of keywords after the abstract

\keywords{Manuscript format, template, SPIE Proceedings, LaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
\label{sec:intro}  % \label{} allows reference to this section

This document shows the desired format and appearance of a manuscript prepared for the Proceedings of the SPIE.\footnote{The basic format was developed in 1995 by Rick Herman (SPIE) and Ken Hanson (Los Alamos National Lab.).} It is prepared using LaTeX2e\cite{Lamport94} with the class file {\tt spie.cls}.  The LaTeX source file used to create this document is {\tt article.tex}, which contains important formatting information embedded in it.  These files are available on the Internet at {\tt http://home.lanl.gov/kmh/spie/}.  The font used throughout is the LaTeX default font, Computer Modern Roman, which is equivalent to the Times Roman font available on many systems.  If this font is not available, use a similar serif font.  Normal text has a font size of 10 points\footnote{Font sizes are specified in points, abbreviated pt., which is a unit of length.  One inch = 72.27 pt.; one cm = 28.4 pt.} for which the actual height of a capital E is about 2.4 mm (7 pt.) and the line-to-line spacing is about 4.2 mm (12 pt.).  The font attributes for other parts of the manuscript, summarized in Table~\ref{tab:fonts}, are described in the following sections.  Normal text should be justified to both the left and right margins.  Appendix~\ref{sec:latex} has information about PostScript fonts.

To be properly reproduced in the Proceedings, all text and figures must fit inside a rectangle 6.75-in.\ wide by 8.75-in.\ high or 17.15 cm by 22.23 cm.  The text width and height are set in {\tt spie.cls} to match this requirement.
%% This table is carefully placed in the source file to make 
%% it appear at bottom of page, but above the footnotes.  
%% Use of [h] in following command forces table to appear "here".
\begin{table}[h]
\caption{Fonts sizes to be used for various parts of the manuscript.  All fonts are Computer Modern Roman or an equivalent.  Table captions should be centered above the table.  When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.} 
\label{tab:fonts}
\begin{center}       
\begin{tabular}{|l|l|} %% this creates two columns
%% |l|l| to left justify each column entry
%% |c|c| to center each column entry
%% use of \rule[]{}{} below opens up each row
\hline
\rule[-1ex]{0pt}{3.5ex}  Article title & 16 pt., bold, centered  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Author names and affiliations & 12 pt., normal, centered   \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Section heading & 11 pt., bold, centered (all caps)  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Subsection heading & 11 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Sub-subsection heading & 10 pt., bold, left justified  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Normal text & 10 pt., normal  \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Figure and table captions & \, 9 pt., normal \\
\hline
\rule[-1ex]{0pt}{3.5ex}  Footnote & \, 9 pt., normal \\
\hline 
\end{tabular}
\end{center}
\end{table} 
The text should begin 1.00 in.\ or 2.54 cm from the top of the page.  The right and left margins should be 0.875~in.\ or 2.22 cm for US letter-size paper (8.5 in.\ by 11 in.) or 1.925 cm for A4 paper (210 mm by 297 mm) to horizontally center the text on the page.  See Appendix~\ref{sec:latex} for guidance regarding paper-size specification.

Authors are encouraged to follow the principles of sound technical writing, as described in Refs.~\citenum{Alred03} and \citenum{Perelman97}, for example.  Many aspects of technical writing are addressed in the {\em AIP Style Manual}, published by the American Institute of Physics.  It is available on line at {\tt http://www.aip.org/pubservs/style/4thed/toc.html} or {\tt http://public.lanl.gov/kmh/AIP\verb+_+Style\verb+_+4thed.pdf}. A spelling checker is helpful for finding misspelled words.

An author may use this LaTeX source file as a template by substituting his/her own text in each field.  This document is not meant to be a complete guide on how to use LaTeX.  For that, refer to books on LaTeX usage, such as the definitive work by Lamport\cite{Lamport94} or the very useful compendium by Mittelbach et al.\cite{Mittelbach04}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{PARTS OF MANUSCRIPT}

This section describes the normal structure of a manuscript and how each part should be handled.  The appropriate vertical spacing between various parts of this document is achieved in LaTeX through the proper use of defined constructs, such as \verb|\section{}|.  In LaTeX, paragraphs are separated by blank lines in the source file.

At times it may be desired, for formatting reasons, to break a line without starting a new paragraph.  This situation may occur, for example, when formatting the article title, author information, or section headings.  Line breaks are inserted in LaTeX by entering \verb|\\| or \verb|\linebreak| in the LaTeX source file at the desired location.

%%%%%Sometimes it is necessary to precede the double slash 
%%%%%by \verb|\protect| to get the desired result, 
%%%%%for example, in article titles.

%%-----------------------------------------------------------
\subsection{Title and Author Information} 
\label{sec:title}

The article title appears centered at the top of the first page.  The title font is 16 point, bold.  The rules for capitalizing the title are the same as for sentences; only the first word, proper nouns, and acronyms should be capitalized.  Avoid using acronyms in the title.  Keep in mind that people outside your area of expertise might read your article.  Appendix~\ref{sec:misc} contains more about acronyms.

The list of authors immediately follows the title after a blank vertical space of about 7 mm.  The font is 12 point, normal with each line centered.  The authors' affiliations and addresses follow the author list after another blank space of about 4 mm, also in 12-point, normal font and centered.  Do not use acronyms in affiliations and addresses. For multiple affiliations, each affiliation should appear on a new line, separated from the following address by a semicolon.  Italicized superscripts may be used to identify the correspondence between the authors and their respective affiliations.  Further author information, such as e-mail address, complete postal address, and web-site location, may be provided in a footnote by using \verb|\authorinfo{}|, as demonstrated above.

When the abbreviated title or author information is too long to fit on one line, multiple lines may be used; insert line breaks appropriately to achieve a visually pleasing format.  The proper spacing of one and one-half lines between the title, author list, and their affiliations is achieved with the command \verb|\skiplinehalf| defined in {\tt spie.cls}.

%%-----------------------------------------------------------
\subsection{Abstract and Keywords} 
The title and author information is immediately followed by the Abstract. The Abstract should concisely summarize the key findings of the paper.  It should consist of a single paragraph containing no more than 200 words.  The Abstract does not have a section number.  A list of up to ten keywords should immediately follow the Abstract after a blank line.  These keywords will be included in a searchable database at SPIE.

%%-----------------------------------------------------------
\subsection{Body of Paper} 
The body of the paper consists of numbered sections that present the main findings.  These sections should be organized to best present the material.  See Sec.~\ref{sec:sections} for formatting instructions.

%%-----------------------------------------------------------
\subsection{Appendices} 
Auxiliary material that is best left out of the main body of the paper, for example, derivations of equations, proofs of theorems, and details of algorithms, may be included in appendices.  Appendices are enumerated with uppercase Latin letters in alphabetic order, and appear just before the Acknowledgments and References.

%%-----------------------------------------------------------
\subsection{Acknowledgments} 
In the Acknowledgments section, appearing just before the References, the authors may credit others for their guidance or help.  Also, funding sources may be stated.  The Acknowledgments section does not have a section number.

%%-----------------------------------------------------------
\subsection{References} 
The References section lists books, articles, and reports that are cited in the paper.  It does not have a section number.  The references are numbered in the order in which they are cited.  Examples of the format to be followed are given at the end of this document.

The reference list at the end of this document is created using BibTeX, which looks through the file {\tt report.bib} for the entries cited in the LaTeX source file.  The format of the reference list is determined by the bibliography style file {\tt spiebib.bst}, as specified in the \verb|\bibliographystyle{spiebib}| command.  Alternatively, the references may be directly formatted in the LaTeX source file.

For books\cite{Lamport94,Alred03,Goossens97} the listing includes the list of authors, book title (in italics), page or chapter numbers, publisher, city, and year of publication.  A reference to a journal article\cite{Metropolis53} includes the author list, title of the article (in quotes), journal name (in italics, properly abbreviated), volume number (in bold), inclusive page numbers, and year.  By convention\cite{Lamport94}, article titles are capitalized as described in Sec.~\ref{sec:title}.  A reference to a proceedings paper or a chapter in an edited book\cite{Gull89a} includes the author list, title of the article (in quotes), conference name (in italics), if appropriate, editors, volume or series title (in italics), volume number (in bold), if applicable, inclusive page numbers, publisher, city, and year.  References to an article in the SPIE Proceedings may include the conference name, as shown in Ref.~\citenum{Hanson93c}.

Citations to the references are made using superscript numerals, as demonstrated in the preceding paragraph.  One may also directly refer to a reference within the text, e.g., ``as shown in Ref.~\citenum{Metropolis53} ..."

%%-----------------------------------------------------------
\subsection{Footnotes} 
Footnotes\footnote{Footnotes are indicated as superscript symbols to avoid confusion with citations.} may be used to provide auxiliary information that doesn't need to appear in the text, e.g., to explain measurement units.  They should be used sparingly, however.

Only nine footnote symbols are available in LaTeX. If you have more than nine footnotes, you will need to restart the sequence using the command  \verb|\footnote[1]{Your footnote text goes here.}|. If you don't, LaTeX will provide the error message {\tt Counter too large.}, followed by the offending footnote command.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SECTION FORMATTING} \label{sec:sections}

Section headings are centered and formatted completely in uppercase 11-point bold font.  Sections should be numbered sequentially, starting with the first section after the Abstract.  The heading starts with the section number, followed by a period.  In LaTeX, a new section is created with the \verb|\section{}| command, which automatically numbers the sections.

Paragraphs that immediately follow a section heading are leading paragraphs and should not be indented, according to standard publishing style\cite{Lamport94}.  The same goes for leading paragraphs of subsections and sub-subsections.  Subsequent paragraphs are standard paragraphs, with 14-pt.\ (5 mm) indentation.  An extra half-line space should be inserted between paragraphs.  In LaTeX, this spacing is specified by the parameter \verb|\parskip|, which is set in {\tt spie.cls}.  Indentation of the first line of a paragraph may be avoided by starting it with \verb|\noindent|.

%%-----------------------------------------------------------
\subsection{Subsection Attributes}

The subsection heading is left justified and set in 11-point, bold font.  Capitalization rules are the same as those for book titles.  The first word of a subsection heading is capitalized.  The remaining words are also capitalized, except for minor words with fewer than four letters, such as articles (a, an, and the), short prepositions (of, at, by, for, in, etc.), and short conjunctions (and, or, as, but, etc.).  Subsection numbers consist of the section number, followed by a period, and the subsection number within that section.

%%-----------
\subsubsection{Sub-subsection attributes} 
The sub-subsection heading is left justified and its font is 10 point, bold.  Capitalize as for sentences.  The first word of a sub-subsection heading is capitalized.  The rest of the heading is not capitalized, except for acronyms and proper names.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FIGURES AND TABLES}

Figures are numbered in the order of their first citation.  They should appear in numerical order and on or after the same page as their first reference in the text.  Alternatively, all figures may be placed at the end of the manuscript, that is, after the Reference section.  It is preferable to have figures appear at the top or bottom of the page.  Figures, along with their captions, should be separated from the main text by at least 0.2 in.\ or 5 mm.

Figure captions are centered below the figure or graph.  Figure captions start with the figure number in 9-point bold font, followed by a period; the text is in 9-point normal font; for example, ``{\footnotesize{Figure 3.}  Original image...}".  See Fig.~\ref{fig:example} for an example of a figure caption.  When the caption is too long to fit on one line, it should be justified to the right and left margins of the body of the text.

Tables are handled identically to figures, except that their captions appear above the table. 
%%  Use following command to specify that graphics file is in 
%%  a directory other than this LaTeX source file.
%%  Note use of / to separate subdirectories, for UNIX and Windows OS.
%%\graphicspath{{H:/HANSON/SPIESTY/}}
%% tabular environment useful for creating an array of images  
%-------------
   \begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=7cm]{Projection.pdf}
   \end{tabular}
   \end{center}
   \caption[example] 
%>>>> use \label inside caption to get Fig. number with \ref{}
   { \label{fig:example} 
Figure captions are used to describe the figure and help the reader understand it's significance.  The caption should be centered underneath the figure and set in 9-point font.  It is preferable for figures and tables to be placed at the top or bottom of the page. LaTeX tends to adhere to this standard.}
   \end{figure} 
%-------------

For further details concerning the inclusion of grayscale and color images, consult SPIE's {\it Author Guide for Publication and Presentation}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix    %>>>> this command starts appendixes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{MISCELLANEOUS FORMATTING DETAILS} \label{sec:misc}

It is often useful to refer back (or forward) to other sections in the article.  Such references are made by section number.  When a section reference starts a sentence, Section is spelled out; otherwise use its abbreviation, for example, ``In Sec.~2 we showed..." or ``Section~2.1 contained a description...".  References to figures, tables, and theorems are handled the same way.

At the first occurrence of an acronym, spell it out, followed by the acronym in parentheses, e.g., noise power spectrum (NPS).

%%-----------------------------------------------
\subsection{Formatting Equations} 
Equations may appear in line with the text, if they are simple, short, and not of major importance; e.g., $\beta = b/r$.  Important equations appear on their own line.  Such equations are centered.  For example, ``The expression for the minus-log-posterior is
	\begin{equation}
	\label{eq:alpha}
\phi = |{\rm\bf y} - {\rm\bf A}{\rm\bf x}|^2 + \alpha \log p({\rm\bf x}) \, ,
	\end{equation}
where $\alpha$ determines the strength of ..."  Principal equations are numbered, with the equation number placed within parentheses and right justified.

Equations are considered to be part of a sentence and should be punctuated accordingly. In the above example, a comma follows the equation because the next line is a subordinate clause.  If the equation ends the sentence, a period should follow the equation.  The line following an equation should not be indented unless it is meant to start a new paragraph.  Indentation after an equation is avoided in LaTeX by not leaving a blank line between the equation and the subsequent text.

References to equations include the equation number in parentheses, for example, ``Equation~(\ref{eq:alpha}) shows ..." or ``Combining Eqs.~(2) and (3), we obtain..."  Using a tilde in the LaTeX source file between two characters avoids unwanted line breaks.

%%-----------------------------------------------------------
\subsection{Formatting Theorems}

To include theorems in a formal way, the theorem identification should appear in a 10-point, bold font, left justified and followed by a period.  The text of the theorem continues on the same line in normal, 10-point font.  For example,

\noindent{\bf Theorem 1.} For any unbiased estimator...

Formal statements of lemmas and algorithms receive a similar treatment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SOME LATEX GUIDANCE} \label{sec:latex}

%%-----------------------------------------------------------
\subsection{Margins and PostScript Fonts}

Manuscripts submitted electronically to as PostScript (PS) files must have the correct margins. LaTeX margins are related to the document's paper size. The paper size is set at two separate places in the process of creating a PS file. The first place is in {\tt latex}. The default in {\tt article.tex}, on which {\tt spie.cls} is based, is USA letter paper. To format a document for A4 paper, the first line of the LaTeX source file should be \verb|\documentclass[a4paper]{spie}|.

The output of the LaTeX utility is a file with the extension DVI (for Device Independent), which encodes the formatted document.  The application DVIPS is typically used to convert the DVI file to a PS file.  DVIPS has its own default paper size, which can be overridden with the option ``{\tt -t letter}" or ``{\tt -t a4}".  
If the foregoing steps do not produce the correct top margin, you can move the text lower on the page (by 9 mm) with the command \verb|\addtolength{\voffset}{9mm}|, placed right after the \verb|\documentclass| command, for example.

Another DVIPS option specifies the incorporation of (scalable) PostScript Type 1 fonts in its output PS file. This feature is important for obtaining a subsequent PDF file that will be clearly displayed on a computer monitor by Adobe Acrobat Reader.  The option ``{\tt -P pdf}" makes DVIPS include these fonts in its output PS file.

%%-----------------------------------------------------------
\subsection{Bold Math Symbols}

The math package from the American Mathematical Society allows one to easily produce bold math symbols, well beyond what is available in LaTeX. It also provides many useful capabilities for creating elaborate mathematical expressions. You need to load the AMS math package near the top of the LaTeX source file, right after the \verb+\documentclass+ command:\\[1ex]
\verb+\usepackage[]{amsmath}+ \\[1ex]
Then for bold math symbols use \verb+\boldsymbol+ in equations, e.g., 
\verb+$\boldsymbol{\pi}$+ 
yields a bold pi.  You can make it easier to use by defining a command:\\[1ex]
\verb+\newcommand{\bm}[1]{\boldsymbol{#1}}+ \\[1ex]
and then using it like so \verb+$\bm{\pi}$+.

Not all math symbols are available in bold.  In a pinch, you can use \verb+\pmb+ ("poor man's bold"), which is defined in \verb+amsmath+. This command approximates a bold character with a superposition of several, slightly displaced unbold characters.

If you want a Greek symbol in the article title, it should be both larger and bold. The easiest thing is to load the AMS math package as described above. 
Then, in the title, use something like:\\[1ex]
\verb+\title{Estimation of {\LARGE$\boldsymbol\alpha$} by a Monte Carlo technique}+ \\[1ex]
Note that the command to create the alpha character is enclosed within braces to form a self-contained environment. The use of \verb+\LARGE+ in this example may not be needed when using nondefault font packages, such as the {\tt times} package, because of how the article title is handled in {\tt spie.cls}.

%%-----------------------------------------------------------
\subsection{Uppercase letters and special symbols in BibTex}

BibTeX tries to enforce standard publishing rules regarding article titles and authors' names; it sometimes changes uppercase letters to lower case. BibTeX also has trouble with umlauts, generally created in LaTeX with \verb+\"{o}+, because it is looking for the \verb+"+ to end the input line.

The general rule for overriding LaTeX's and BibTex's reinterpretation of your input text is to put the items you wish to be unchanged in braces. Thus, to obtain an umlaut in an author's name or in an article title, or to force an uppercase letter, do something like the following: \\[1ex]
\verb+ @article{Kaczmarz37,+ \\ 
\verb+ author = "S. Kaczmarz",+ \\ 
\verb+ title  = "Angen{\"{a}}hrte {A}ufl{\"{o}}sung von {S}ystemen linearer {G}leichungen",+ \\ 
\verb+ journal= "Bull. Acad. Polon. Sci. Lett.",+ \\ 
\verb+ volume = "A35",+ \\ 
\verb+ pages  = "355-357",+ \\	
\verb+ year   = "1937"	} + \\[1ex]
This example shows the use of both umlauts and uppercase letters.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}

This unnumbered section is used to identify those who have aided the authors in understanding or accomplishing the work presented and to acknowledge sources of funding.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%

\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document}

### 2013-05-31 masters/body/_region_.tex
so much

@@
 
-\message{ !name(masters.tex) !offset(135) }
-\subsection{Geometry Partitioning}
-\label{sec:geometryPartioning}
-In order to effectively texture a 3D model, we first divide the model
-into a set of regions, each to be textured independently. The purpose
-of this is to ensure texture continuity along large uniform areas,
-while allowing texture boundaries to fall along natural environmental
-boundaries. Because textures may not match at such boundaries where
-two regions meet, it is important to minimize the visibility of
-boundaries. This is done by encouraging region boundaries to occur at
-large sharp corners, where texture continuity is less important.
+\message{ !name(masters.tex) !offset(938) }
+\subsection{Examples}
+\label{sec:examples}
+As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
+procedure in this thesis can be applied both to low-resolution and
+high-resolution models. Low resolution models have an advantage in
+their simplicity, and in that only important environmental features
+are represented. As a result, images are generated for large sections
+of buildings, and boundaries between each texture are minimally
+visible. High resolution models have an obvious advantage in terms of
+the amount of detail that can be reconstructed, but with poor region
+partitioning, as described in Section \ref{sec:geometryPartitioning},
+or with high camera pose or geometry reconstruction error, 3D elements
+in the environment geometry may not match up well with their imaged
+counterparts.
 
-When working with low-resolution models, where surfaces generally
-correspond to large planar features such as walls, ceilings, or
-floors, and often meet at right angles, each planar surface in the
-model is directly treated as a distinct region and textured
-separately.
+\begin{figure}
+  \centering
+  \subfloat[][]{
+    \includegraphics[width=2in]{results_swarm_3_v.jpg}
+    \includegraphics[width=2in]{results_swarm_3_2d.jpg}
+    \includegraphics[width=2in]{results_swarm_3_3d.jpg}
+  }
+  \subfloat[][]{
+    \includegraphics[width=2in]{results_swarm_2_v.jpg}
+    \includegraphics[width=2in]{results_swarm_2_2d.jpg}
+    \includegraphics[width=2in]{results_swarm_2_3d.jpg}
+  }
+  \subfloat[][]{
+    \includegraphics[width=2in]{results_swarm_5_v.jpg}
+    \includegraphics[width=2in]{results_swarm_5_2d.jpg}
+    \includegraphics[width=2in]{results_swarm_5_3d.jpg}
+  }
 
-When working with a high-resolution model however, geometry often
-represents large features as well as small details found in furniture,
-plants, and other miscellaneous objects. For instance, in Figure
-\ref{fig:deskGeom}, the geometry modeling the desk and binders
-consists of many small triangles at various orientations. Texturing
-each of these triangles independently makes little sense, as the
-textures applied to each should match up well with the textures of its
-neighbors in order to avoid any breaks in the overall image of the
-desk and binders. On the other hand, the textures for the triangles
-belonging to the wall behind need not match up with the textures on
-the desk and binders, and so each group of triangles should be
-designated to separate regions.
-This region grouping is performed by designating all contiguous coplanar groups of triangles as different regions.
-Any region that is less than $1 m^2$ in size is joined to its largest neighboring region, such that the angle between them is under $90^{\circ}$.
+  \caption{The same indoor environment, as generated using (a) PCA
+    plane-fitting, (b) Floor plan extrusion, (c) Watertight mesh
+    generation. The first two are low-resolution models, while the
+    third is high-resolution}
+  \label{fig:modelcomparisons}
+\end{figure}
 
-Because a texture is 2D, and the region to be textured may not be
-flat, a mapping needs to be defined. We first fit a plane to each
-region for the purposes of texturing. This can be accomplished via a
-least squares plane-fitting through each triangle vertex, though in
-practice we simply use the plane equation of the largest contiguous
-section of coplanar triangles, as most regions are characterized by
-small outcroppings from a largely planar surface, such as objects on a
-table or features protruding from a wall. The 3d vertices within a
-region are then projected onto its calculated plane, and the
-rectangular bounding box for these projected vertices is
-calculated. This bounding box corresponds to the 2D image that will be
-created to texture the region.
+Our approach was tested with three different geometry-reconstruction
+methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
+floor plan extrusion method \cite{turnerfloorplan}, and a
+voxel-carving mesh generation method \cite{turnerwatertight}. The
+first two methods generate lower-resolution models, containing only
+major walls, ceilings and floors. The third method generates
+high-resolution models, and attempts to reconstruct all scanned
+objects in the environment. A comparison of all three methods as
+applied to the same dataset is shown in Figure
+\ref{fig:modelcomparisons}
 
-Of course, the area encompassed by the bounding box is larger than the
-corresponding 2d area of the projected geometry, which itself is not
-as accurate as the original 3d geometry. Thus, we also create a k-d
-tree consisting of the triangle primitives from the original
-mesh. Though we generate texture for the 2d bounding box surface, we
-will reference the original 3D geometry to ensure accuracy when
-texturing.
+\begin{figure}
+  \centering
+  \caption{low resolution stuff. (a) is not watertight}
+  \label{fig:lowresmodels}
+\end{figure}
 
-\message{ !name(masters.tex) !offset(944) }
+The PCA and floor plan methods produce models at a similar level of
+detail. As visible in Figure \ref{fig:lowresmodels}(a), the PCA method
+is not watertight, while the floor plan method is. As a result, the
+PCA-generated model contains holes where surfaces were not adequately
+scanned. On the other hand, the watertight floor plan model sometimes
+must make assumptions about the location of surfaces that were not
+adequately scanned, in order to maintain watertightness. Because
+buildings generally follow straight lines and right angle corners
+however, such assumptions tend to be correct. Additionally, the
+floor-plan method is generally superior at reconstructing smaller
+surfaces, such as small walls, or to approximate curved surfaces,
+while the PCA method only fits large planes, and fails in both
+cases. As a result, the floor-plan method usually produces more
+visually pleasing low-resolution models, and is the method of choice
+for generating textured low-resolution models.
+
+\begin{figure}
+  \caption{2d vs 3d}
+  \label{fig:2dvs3d}
+\end{figure}
+
+High-resolution models, as generated by the voxel-carving method, can
+produce more accurate reconstructions of environment geometry. With
+such models, region partitioning, as described in Section
+\ref{sec:geometryPartitioning}, plays an important factor in the
+quality of generated textures. If regions are small, boundaries
+between adjacent textures become visible, and since each region is
+processed independently, image alignment procedures are performed
+across smaller areas. If regions are large, then the difference
+between the 3D surface geometry and the approximated 2D texturing
+surface become large as well, introducing greater texture projection
+error. Additionally, in areas where pose error or surface
+reconstruction error is high, 3D objects in images do not get
+accurately projected onto their modeled counterparts. While large
+objects can be aligned to geometry via the methods in Section
+\ref{sec:geometryAlignment}, smaller objects such as plants or
+computers are difficult to line up to geometry references. While the
+compositing techniques is Section \ref{sec:imageCompositing} can
+ensure that textures for small objects appear seamless, such textures
+may not map accurately upon their corresponding geometry, leading to
+visually obvious discrepancies in the textured model. Figure
+\ref{fig:2dvs3d} demonstrates this by showcasing the low-resolution
+floor plan approach alongside the high-resolution voxel-carving
+approach.
+
+As visible in Figure \ref{fig:2dvs3d} and other images in this
+section, 2D models using the floor plan approach are generally
+preferred, as they provide enough detail in geometry to reconstruct
+the basic layout of an environment, while textures can be used to
+visualize smaller details. On the other hand, for applications where
+furniture and smaller interior details are important, applying
+textures to the 3D voxel-carved models provides useful image-based
+context for visualizing indoor areas. Figures 1-3 demonstrate further
+interior and exterior views of a number of 2D models, while Figures
+4-6 demonstrate interior and exterior views of 3D models.
+
+\message{ !name(masters.tex) !offset(1065) }
 

### 2013-05-31 masters/body/masters.tex
so much

@@
 \cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results. In this paper, we present an approach
+generally produce poor results. In this thesis, we present an approach
 to texture mapping 3D models of indoor environments in the presence of
@@
 obtained from a human-operated backpack system, detailed in Section
-\ref{sec:dataAcquisitionSystem}.
+\ref{sec:dataAcquisition}.
 
@@
   \includegraphics[width=6in]{flowchart.jpg}
-  \caption{The proposed texture mapping procedure ***this will
-    change\\}
+  \caption{The proposed texture mapping procedure\\}
   \label{fig:flowchart}
@@
 The overall block diagram for the proposed texture mapping procedure
-is shown in Figure \ref{fig:flowchart}, where the number attached
-attached to each box indicates the section in which the concept in the
-box is explained in this paper ***will change. First, the geometry of
-an environment is split into regions. For each region, we begin by
-selecting a set of images that spans the entire region's surface with
-high resolution imagery. We then use recovered noisy camera poses to project
-these selected images onto the surface. These projections are rotated
-and translated in 2D, in order to maximally align them with the
-surface's geometry, as well as to each other, allowing us to handle
-both errors in geometry as well as camera poses. For surfaces and
-camera poses at arbitrary locations or orientations, generally
-ceilings and floors, we propose a tile-based approach for sampling
-high-resolution portions of images and compositing them into a
-texture. In cases where cameras have consistently perpendicular
-viewing angles to the surfaces under consideration, generally walls,
-we demonstrate a superior approach based on a shortest-path
-computation that leads to more seamless textures.
-
-The remainder of the paper is organized as follows. Section
-\ref{sec:dataAcquisitionSystem} describes our data acquisition system
-as well as our region segmentation procedure. Section
-\ref{sec:existingApproaches} covers existing approaches to image
-stitching, and their performance on our datasets. Section
-\ref{sec:simpleTextureMapping} explains how to downsample the set of
+is shown in Figure \ref{fig:flowchart}, where the number attached to
+each box indicates the section in which the concept in the box is
+explained in this thesis. First, the geometry of an environment is
+split into regions, each of which will be textured independently and
+in parallel. For each region, we begin by selecting a set of images
+that spans the entire region's surface with high resolution
+imagery. We then use recovered noisy camera poses to project these
+selected images onto the surface. These projections are rotated and
+translated in 2D, in order to maximally align them with the surface's
+geometry, as well as to each other, allowing us to handle both errors
+in geometry as well as camera poses. For surfaces and camera poses at
+arbitrary locations or orientations, generally horizontal surfaces, we
+propose a tile-based approach for sampling high-resolution portions of
+images and compositing them into a texture. In cases where cameras
+have consistently perpendicular viewing angles to the surfaces under
+consideration, generally vertical surfaces, we demonstrate a superior
+approach based on a shortest-path computation that leads to more
+seamless textures.
+
+The remainder of the thesis is organized as follows. Section
+\ref{sec:dataAcquisition} provides background on the data acquisition
+system and describes a region segmentation procedure. Section
+\ref{sec:relatedWork} covers existing approaches to image stitching,
+and their performance on our datasets. Section
+\ref{sec:imageSelection} explains how to downsample the set of
 available images by selecting those with the best orientation and
 distance from surfaces under consideration. Section
-\ref{sec:2dAlignment} contains our approach towards 2D image
+\ref{sec:2dAlignment} contains the proposed approach towards 2D image
 alignment, followed by Section \ref{sec:imageCompositing}, which
@@
 \end{figure}
+
+This section contains background information describing the
+backpack-mounted system and its operation. The hardware and operation
+of the backpack system, as well as the postprocessing of acquired
+data, play an important role in motivating the approaches described in
+this thesis. The following two sections will focus on image and raw
+data acquisition, and a method of partitioning recovered environment
+geometry, respectively.
+
+\subsection{Acquisition Hardware}
 
@@
 view each and taking photos at a rate of 5 Hz \cite{liu2010indoor}. In
-order to collect data, an operator wears the
-backpack system and traverses the environment to be scanned, walking
-in straight lines at a standard pace and making an effort to walk
-parallel to all walls in the area. Multiple localization and
-loop-closure algorithms are then applied to the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, and the backpack is localized\footnote{In this
-  paper, we use the terms localization and pose recovery
-  interchangeably, in that they both refer to recovering position and
-  orientation.}  over its data collection period. This involves
-recovering the 6 degrees of freedom for the backpack itself as well as
-the cameras rigidly mounted on it. Once this is complete, the data
-from the laser range scanners is used to generate a 3D point cloud of
-the surrounding environment. This point cloud is used to construct
-either a low-resolution planar model, such as for usage in basic
-navigation or energy analysis \cite{sanchez2012point,
-  turnerfloorplane}, or a high-resolution, detailed triangular mesh,
-for applications such as accurate remodeling or virtual walkthroughs
-\cite{turnerwatertight}.  Regardless of resolution, size, or detail,
-the model, consisting of geometric surfaces in 3D space, along with
-the set of images captured by the backpack's cameras and their noisy
-3D poses, are the input to our texture mapping problem.
+order to collect data, an operator wears the backpack system and
+traverses the environment to be scanned, walking in straight lines at
+a standard pace and making an effort to walk parallel to all walls in
+the area. Multiple localization and loop-closure algorithms are then
+applied to the raw data collected by the onboard sensors
+\cite{chen2010indoor, kua2012loopclosure, liu2010indoor}, and the
+backpack is localized\footnote{In this thesis, we use the terms
+  localization and pose recovery interchangeably, in that they both
+  refer to recovering position and orientation.}  over its data
+collection period. This involves recovering the 6 degrees of freedom
+for the backpack itself as well as the cameras rigidly mounted on it.
+These results are noisy, which motivates the approaches in this
+thesis. Once this is complete, the data from the laser range scanners
+is used to generate a 3D point cloud of the surrounding
+environment. This point cloud is used to construct either a
+low-resolution planar model, such as for usage in basic navigation or
+energy analysis \cite{sanchez2012point, turnerfloorplan}, or a
+high-resolution, detailed mesh, for applications such as accurate
+remodeling or virtual walkthroughs \cite{turnerwatertight}.
+Regardless of resolution, size, or detail, the model, consisting of
+geometric surfaces in 3D space, along with the set of images captured
+by the backpack's cameras and their noisy 3D poses, are the input to
+the texture mapping problem.
 
 \subsection{Geometry Partitioning}
-\label{sec:geometryPartioning}
+\label{sec:geometryPartitioning}
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=2.2in]{geomdeskwire_crop.png}}
+  \subfloat[][]{\includegraphics[width=2.2in]{geomdeskregions_crop.png}}
+  \subfloat[][]{\includegraphics[width=2.2in]{geomdesktexturetris_crop.png}}
+  \caption{(a) Part of a model representing a desk and miscellaneous
+    objects on top of the desk. (b) Triangles grouped into regions for
+    texturing. (c) Final textured output.}
+  \label{fig:deskGeom}
+\end{figure}
+
 In order to effectively texture a 3D model, we first divide the model
@@
 boundaries. This is done by encouraging region boundaries to occur at
-large sharp corners, where texture continuity is less important.
-
-When working with low-resolution models, where surfaces generally
+large sharp corners, where texture continuity is not important. When
+working with lower-resolution models, where surfaces generally
 correspond to large planar features such as walls, ceilings, or
 floors, and often meet at right angles, each planar surface in the
-model is directly treated as a distinct region and textured
+model can simply be treated as a distinct region and textured
 separately.
 
-When working with a high-resolution model however, geometry often
-represents large features as well as small details found in furniture,
-plants, and other miscellaneous objects. For instance, in Figure
-\ref{fig:deskGeom}(a), the geometry modeling the desk and binders
-consists of many small triangles at various orientations. Texturing
-each of these triangles independently makes little sense, as the
-textures applied to each should match up well with the textures of its
-neighbors in order to avoid any breaks in the overall image of the
-desk and binders. On the other hand, the textures for the triangles
-belonging to the wall behind need not match up with the textures on
-the desk and binders, and so each group of triangles should be
-designated to separate regions. This region grouping is performed by
-designating all contiguous coplanar groups of triangles as different
-regions. Any region that is less than $1 m^2$ in size is joined to its
-largest neighboring region, such that the angle between them is under
-$90^{\circ}$. An example of such a grouping is shown in
-\ref{fig:deskGeom}(b).
-
-Though most regions are not completely flat, we fit a plane to each
-region for the purposes of texturing. This plane corresponds to the
-largest contiguous section of coplanar triangles, as most regions are
-characterized by small outcroppings from a largely planar surface,
-such as objects on a table or features protruding from a wall. The 3d
-vertices within a region are then projected onto its calculated plane,
-and the 2D contour for these projected vertices is calculated.
-
-Of course, the 2D contour of a region is not as accurate as its
-original 3D geometry. Thus, we also create a k-d tree consisting of
-the triangle primitives from the original mesh. Though textures are
-generated upon the 2D planar surface, the original 3D geometry in the
-k-d tree is referenced to ensure accuracy at various stages when
-texturing.
-
-At this point, we either have a series of planar regions, or planar
-approximations for regions and an associated k-d tree. The task now is
-to generate a texture for each region, though first some related work
-will be discussed.
+With high-resolution models however, geometry often represents large
+features as well as small details found in furniture, plants, and
+other miscellaneous objects. For instance, in Figure
+\ref{fig:deskGeom}(a), the geometry modeling each side of a desk as
+well as objects on top of it consists of many small triangles at
+various orientations. It is important that triangles belonging to the
+same object or surface are textured together, as texturing them
+independently might lead to visible misalignment between the textures
+of each triangle, resulting in poor visualizations. On the other hand,
+triangles belonging to different objects, such as the wall vs. objects
+on the desk need not be textured together, as texture alignment
+between the two is not important in terms of overall visual quality of
+the scene. Thus, in this example, the triangles comprising each side
+of the desk, objects on top of the desk, and the wall behind, should
+all be grouped into separate regions. This region grouping is done by
+first designating all contiguous coplanar groups of triangles as
+different regions. Any regions that are less than $1 m^2$ in size are
+then joined to their largest neighboring regions, as long as the angle
+between them is under $90^{\circ}$. An example of such a grouping is
+shown in Figure \ref{fig:deskGeom}(b). The same area with textures
+successfully applied to each region is shown in Figure
+\ref{fig:deskGeom}(c).
+
+Though some of these regions from high-resolution models are not
+completely flat, a plane is fitted to each region for the purposes of
+texturing. This plane corresponds to the largest contiguous section of
+coplanar triangles, as most regions are characterized by small
+outcroppings from a largely planar surface, such as objects on a table
+or features protruding from a wall. The 3D surface composing a region
+is then projected onto its calculated plane, and the resulting 2D
+planar polygon is used as the texturing surface. This 2D planar
+approximation provides a simple, yet approximately accurate surface
+onto which images can be projected in order to generate
+textures. However, 3D surfaces are still retained in order to achieve
+more accurate results when performing occlusion checks during the
+texturing process. To improve runtime during such occlusion checks,
+the triangles within all 3D surfaces are also loaded into a k-d tree
+for quick lookup. Thus, for high-resolution models, each region has
+both 3D geometry stored in a k-d tree for occlusion purposes, and an
+approximate 2D representation stored as the texturing surface.
+
+At this point, we either have a series of planar regions from a low
+resolution model, or a set of planar approximations for regions as
+well as an associated k-d tree from a high resolution model. The task
+now is to generate a texture for each region.
 
@@
   debevechybrid, bernardinimultiplescans}. Generally, parts of images
-are matched to each other, either through direct comparisons at pixel
-level, or through feature detection and matching. Images are then
-transformed to maximize matches, often by computing homographies
+are matched to each other, either through direct comparisons at a
+pixel level, or through feature detection and matching. Images are
+then transformed to maximize matches, often by computing homographies
 between pairs of images, or by iteratively adjusting camera poses in 1
@@
 degrees of freedom of the backpack acquisition system detailed in
-Section \ref{sec:dataAcquisitionSystem} \cite{liu2010indoor}. When run
-on long chains of images however, especially where features are
-sparse, this approach produces distorted textures, as seen in Figure
+Section \ref{sec:dataAcquisition} \cite{liu2010indoor}. When run on
+long chains of images however, especially where features are sparse,
+this approach produces distorted textures, as seen in Figure
 \ref{fig:mosaic3D}(a). Furthermore, this approach is not closed-form,
@@
 
-The AutoStitch software package, based on research in the area of
-panorama genoration, performs homography-based alignment as well, with
+The AutoStitch software package, based on research in the related area
+of panorama genoration, also performs homography-based alignment, with
 additional provisions that attempt to reduce drift and increase
 overall efficiency \cite{panorama2d, autostitch}. Though AutoStitch
-performs well in small areas, it often stiff induces drift in images,
+performs well in small areas, it often induces drift in images,
 such that global alignment to the environment geometry is
@@
 in Section \ref{sec:geometryPartitioning}, is shown in Figure
-\ref{fig:projection}. Given a set of $M$ images to texture a target
-plane, camera matrix $P_i$ for the $ith$ image transforms a 3D point
+\ref{fig:projection}. Given a set of images to texture a target
+surface, camera matrix $P_i$ for the $i$th image transforms a 3D point
 in the world coordinate system to a 2D point or pixel in image $i$'s
@@
 translation of the camera's position in 3D world coordinates at the
-time that image $i$ is taken. These extrinsic parameters are
+time that image $i$ was taken. These extrinsic parameters are
 determined by the backpack hardware and the corresponding localization
@@
 texture is not composed of a single continuous image. In the remainder
-of this section, we propose an image subsampling procedure and use it
-to derive a simple tile-based texture mapping procedure.
+of this section, we propose an image subsampling procedure to obtain a
+set of images for all further steps, and use it to derive a simple
+tile-based texture mapping procedure.
 
@@
     \includegraphics[height=1.8in]{Projection.pdf}
-    \caption{Surfaces to be textured are specified in 3D space by
-      corners $C_i$. Images are related to each surface through the
-      camera matrices $P_{1..m}$. }
+    \caption{Images are related to each surface through the camera
+      matrices $P_{1..m}$. }
     \label{fig:projection}
@@
     \includegraphics[height=1.8in]{scoringFunction.jpg}
-    \caption{We minimize camera angle $\alpha$ and distance $d$ by
+    \caption{Camera angle $\alpha$ and distance $d$ are minimized by
       maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
@@
 
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-a straightforward approach for texturing is to discretize the target
-plane into small square tiles, and choose an image to texture each
-tile directly. We choose to work with rectangular units to ensure that
-borders between any two distinct images in the final texture are
-either horizontal or vertical. Since most environmental features
-inside buildings are horizontal or vertical, any visible seams in the
-texture intersect them minimally and are therefore less noticeable.
-
-In order to select an image for texturing a tile $t$, we first gather
-a list of candidate images that contain all four of its corners; we
-can rapidly check this by projecting $t$ into each image using the
-$P_i$ camera matrices. Furthermore, each candidate image must have
-been taken at a time when its camera had a clear line-of-sight to $t$,
-which can be determined using standard ray-polygon intersection tests
-between the camera location, $t$, and every other surface
+Our criteria for image subsampling has the following
+stipulations. First, we want a set of images such that their
+projections together cover up the entirety of our target surface, so
+as to avoid holes in the final texture. Second, we desire our final
+texture to have high resolution throughout; thus every location on the
+target surface should have at least one image that contains high
+resolution imagery for it. A straightforward way to accomplish these
+goals is to discretize the target surface into small square tiles, and
+for each tile, select the image that has the best viewing angle and
+resolution for texturing that tile. In order to select the image that
+can best texture a tile $t$, we first gather a list of candidate
+images that contain all four of its corners; we can rapidly check this
+by projecting $t$ into each image using the $P_i$ camera
+matrices. Furthermore, each candidate image must have been taken at a
+time when its camera had a clear line-of-sight to $t$, which can be
+determined using standard ray-polygon intersection tests between the
+camera location, $t$, and every other surface, or via the k-d tree
+from Section \ref{sec:geometryPartitioning} if present
 \cite{rayintersection}.
@@
 $\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively. As Figure \ref{fig:compareAll}(a) demonstrates, this
-approach, when used directly for texturing, results in image
-boundaries with abrupt discontinuities between tiles, due to
-misalignment between images, though most of it appears to be
-reconcilable using 2D transforms.
-
-While this procedure can be used to generate a texture, it is also
-useful for obtaining a collection of images that can be used as a
-starting point for our proposed texturing procedure, as explained in
-Section \ref{sec:2dAlignment}. For our datasets, this process
-generally selects around 10\% of all the images that could be used for
-texturing the surface. This roughly 10:1 subsampling not only reduces
-computational complexity of the remaining steps, but also selects the
-most promising images for the remaining steps.
+respectively.
+
+When the images selected for each tile are used directly to texture
+their respective tiles, image boundaries with abrupt discontinuities
+between tiles are visible, as shown in Figure
+\ref{fig:compareAll}(a). While it is clear that camera pose
+inaccuracies are too severe for such a simple approach to work, the
+selected images all appear to contain optimal camera angles with high
+resolution, and much of their misalignment appears reconcilable using
+2D transforms. This procedure generally selects around 10\% of the
+possible images that could be used for texturing a surface, and not
+only reduces the computational complexity of the remaining steps, but
+also selects the most promising images for the remaining steps.
 
@@
 alignment. Rather than register all of our images in 3D, as many
-state-of-the-art techniques for image stitching do, we instead select
-a subset of images to be aligned in 2D. This subset corresponds to the
-images selected by the image selection procedure described in Section
-\ref{sec:simpleTextureMapping}.
+state-of-the-art techniques for image stitching do, we instead align a
+subset of images in 2D; this subset corresponds to the images selected
+by the image selection procedure described in Section
+\ref{sec:imageSelection}.
 
@@
 images is such that localization error chiefly occurs in two
-dimensions, which correspond to the plane of the surface being
+dimensions, which correspond to the plane of most surfaces being
 projected onto. This is because the backpack operator, during data
 acquisition, makes efforts to walk within a few meters of, and
-parallel to all walls being scanned. As a result, the translational
-error of camera poses is quite minimal in the dimension perpendicular
-to the wall surface being textured. Furthermore, because our set of
-images has minimal distance from its corresponding wall surface,
-rotational errors are less pronounced, except for rotation around the
-axis perpendicular to the surface being textured. Therefore, most
-translation and rotational errors occur in the 2 dimensions of the
-wall surface's plane. This of course does not apply for ceilings and
-floors; however, the lack of features on most ceilings and floors
-means that 3D misalignment is not likely to visually make a
-difference, beyond what can be done in 2D.
+parallel to all walls being scanned. Furthermore, the backpack system
+maintains a fairly consistent distance from floors and ceilings during
+data collection. As a result, the translational error of camera poses
+is quite minimal in dimensions perpendicular to most surfaces being
+textured, corresponding to, or parallel to walls, ceilings and
+floors.
 
@@
 After computing each image's projection onto the target surface, as
-described in Section \ref{sec:simpleTextureMapping}, we obtain a set
-of image-based line segments by using Hough transforms to detect lines
-in the image projections. These lines are detected in the image
+described in Section \ref{sec:imageSelection}, we can obtain a set of
+image-based line segments by using Hough transforms to detect lines in
+the image projections. These lines are detected in the image
 projections rather than the original images, as the varying
@@
 2 or more pairs, it is possible to obtain a fixed rotation and
-translation, which are saved for usage in Section
-\ref{sec:robustSIFTFeatureMatching}.
+translation for geometry alignment, which are saved for usage in
+Section \ref{sec:robustSIFTFeatureMatching}.
 
 If there are not 2 or more pairs with similar angular differences, we
-select the pair with the longest image-based line and apply a rotation
-and the minimal translation to match its lines. This translation's
+select the pair with the longest image-based line, which corresponds
+to a strong linear visual feature, and apply a rotation and the
+minimal translation to match the pair's lines. This translation's
 ambiguity however, can not be resolved, but is also saved to be used
@@
 walls, etc. which are visible in floor and ceiling images, tend to be
-parallel to exterior walls corresponding to the edges of ceiling and
-floor surfaces. Thus, we choose to minimize the angle between
-image-based lines and geometry-based lines. We use the RANSAC
-framework, with an inlier difference of $0.5^\circ$ in order to
-successfully ignore outliers \cite{fischler1981random}.
+parallel to interior and exterior walls, corresponding to the
+intersection lines and edges of ceiling and floor surfaces
+respectively. Thus, we choose to minimize the angle between
+image-based lines and geometry-based lines regardless of distance. We
+use the RANSAC framework to compute a rotation angle that best
+accomplishes this while ignoring outliers. \cite{fischler1981random}.
 
@@
 and every surface in our model except the target surface
-\cite{rayintersection}. These intersection tests are performed at the
-corners of a grid overlaid upon the target surface. Where all four
-corners of a grid section are occluded, texture is removed. Where one
-or more corners are occluded, the grid is subdivided into four, and
-the process repeats. Occlusion checking works entirely with geometry,
-so by ensuring that images match geometry using
+\cite{rayintersection}. If using planar approximations for regions, as
+explained in Section \ref{sec:geometryPartitioning}, the k-d tree is
+used instead. These intersection tests are performed at the corners of
+a grid overlaid upon the target surface. Where all four corners of a
+grid section are occluded, texture is removed. Where one or more
+corners are occluded, the grid is subdivided into four, and the
+process repeats. Occlusion checking works entirely with geometry, so
+by ensuring that images match geometry using
 \ref{sec:geometryAlignment}'s alignment procedure, texture belonging
 to other surfaces is accurately removed, as seen in Figure
-\ref{fig:occlusion}(b).
+\ref{fig:occlusion}(b) vs. \ref{fig:occlusion}(c).
 
@@
 The next step is to align the selected images from Section
-\ref{sec:simpleTextureMapping} for each surface to each other by
-searching for corresponding feature points between all pairs of
-overlapping images. We use feature alignment rather than pixel or
-intensity-based alignment due to the differences in lighting as well
-as possible occlusion among images, both of which feature alignment is
-less sensitive to \cite{lowe1999object, mikolajczyk2005performance,
+\ref{sec:imageSelection} for each surface to each other by searching
+for corresponding feature points between all pairs of overlapping
+images. We use feature alignment rather than pixel or intensity-based
+alignment due to the differences in lighting as well as possible
+occlusion among images, both of which feature alignment is less
+sensitive to \cite{lowe1999object, mikolajczyk2005performance,
   szeliski2006image}. We use SiftGPU \cite{siftgpu} for its high
@@
 with far greater accuracy. Using the simple tile-based texturing
-scheme from Section \ref{sec:simpleTextureMapping} on these adjusted
-images results in Figure \ref{fig:compareAll}(b), which has far fewer
+scheme from Section \ref{sec:imageSelection} on these adjusted images
+results in Figure \ref{fig:compareAll}(b), which has far fewer
 discontinuities than in \ref{fig:compareAll}(a), though some 3D error
@@
 \label{sec:imageCompositing}
-In Section \ref{sec:simpleTextureMapping} we described an image
-selection method that reduces the list of candidate images for
-texturing by a factor of 10. In this section we go one step further to
-choose a subset of the above candidates in order to further reduce
-visual artifacts and discontinuities across textured
-surfaces. Specifically, in Section \ref{sec:mappingWithCaching}, we
-refine the tile-based texturing approach from Section
-\ref{sec:simpleTextureMapping}, with an added caching mechanism to
-reduce image boundaries. This method is general and works well given
-arbitrary camera poses and surfaces such as walls, floors, and
-ceilings. For special cases where images have consistently
+In Section \ref{sec:imageSelection} we described an image selection
+method that reduces the list of candidate images for texturing by a
+factor of 10. In this section we go one step further to choose a
+subset of the above candidates in order to further reduce visual
+artifacts and discontinuities across textured surfaces. Specifically,
+in Section \ref{sec:mappingWithCaching}, we refine the tile-based
+texturing approach from Section \ref{sec:imageSelection}, with an
+added caching mechanism to reduce image boundaries. This method is
+general and works well given arbitrary camera poses and surfaces,
+whether large planar surfaces or small geometric interior
+features. For special cases where images have consistently
 perpendicular viewing angles to the surfaces under consideration, such
@@
 For the simple texture mapping method described in Section
-\ref{sec:simpleTextureMapping}, discontinuities occur where adjacent
-tiles are textured by different images. Though Section
+\ref{sec:imageSelection}, discontinuities occur where adjacent tiles
+are textured by different images. Though Section
 \ref{sec:2dAlignment}'s image alignment removes many such
@@
 entire set of valid images obtained in Section
-\ref{sec:simpleTextureMapping}. The first subset of images is those
-selected by adjacent tiles that have already been textured. We must
-first check which of these images contain texture for $t$, and then of
-those, we make a choice according to the scoring function in Figure
+\ref{sec:imageSelection}. The first subset of images is those selected
+by adjacent tiles that have already been textured. We must first check
+which of these images contain texture for $t$, and then of those, we
+make a choice according to the scoring function in Figure
 \ref{fig:scoringFunction}. Before reusing this image, we check the
@@
 45^\circ$ criteria, we search the entire set of candidate images from
-Section \ref{sec:simpleTextureMapping}, selecting based on the same
-scoring function from Figure \ref{fig:scoringFunction}.
+Section \ref{sec:imageSelection}, selecting based on the same scoring
+function from Figure \ref{fig:scoringFunction}.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \hspace{1in} \centering
-  \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering \hspace{1in}
-  \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
+  \subfloat[][]{\includegraphics[width=1.5in]{projectionWall.pdf}}
+  \hspace{0.51in} \centering
+  \subfloat[][]{\includegraphics[width=1.5in]{projectionCeiling.pdf}}
+  \centering \hspace{0.5in}
+  \subfloat[][]{\includegraphics[width=1.5in]{projectionWallCrop.pdf}}
   \caption{(a) Images for vertical planes are tilted, but their camera
@@
 to 20 degrees with respect to the vertical direction. As a result,
-cameras facing sideways are head on with respect to vertical walls, as
-shown in Figure \ref{fig:projectionAngles}(a), while cameras oriented
-towards the top or bottom of the backpack are at an angle with respect
-to horizontal floors and ceilings, as shown in Figure
-\ref{fig:projectionAngles}(b). These oblique camera angles for
-horizontal surfaces translate into textures that span large areas once
-projected, as shown in Figure \ref{fig:projectionAngles}(b). Using the
-tile-based texture mapping criteria from Figure
-\ref{fig:scoringFunction}, such projections have highly varying scores
-depending on the location of a tile on the plane. Thus, the tiling
-approach in Section \ref{sec:mappingWithCaching} is an appropriate
-choice for texturing floors and ceilings, as it uses the parts of
-image projections that maximize resolution for their respective plane
-locations, e.g. areas near point A and not near point B, in Figure
+cameras facing sideways are head on with respect to vertical surfaces,
+as shown in Figure \ref{fig:projectionAngles}(a), while cameras
+oriented towards the top or bottom of the backpack are at an angle
+with respect to floors, ceilings and other horizontal surfaces, as
+shown in Figure \ref{fig:projectionAngles}(b). These oblique camera
+angles for horizontal surfaces translate into textures that span large
+areas once projected, as shown in Figure
+\ref{fig:projectionAngles}(b). Using the tile-based texture mapping
+criteria from Figure \ref{fig:scoringFunction}, such projections have
+highly varying scores depending on the location of a tile on the
+plane. Thus, the tiling approach in Section
+\ref{sec:mappingWithCaching} is an appropriate choice for texturing
+horizontal surfaces, as it uses the parts of image projections that
+maximize resolution for their respective plane locations, e.g. areas
+near point A and not near point B, in Figure
 \ref{fig:projectionAngles}(b).
 
-For vertical walls however, most images are taken from close distances
-and head-on angles, resulting in high resolution fronto-parallel
-projections. As a result, for each tile on a wall plane, the scoring
-function of Figure \ref{fig:scoringFunction} is relatively flat with
-respect to candidate images, as they are all more or less head
-on. Since the scoring function is less discriminative for walls, it is
-conceivable to devise a different texturing strategy to directly
-minimize visible seams when texturing them. This is done by choosing
-the smallest possible subset of images from the set selected in
-Section \ref{sec:simpleTextureMapping} and aligned in Section
-\ref{sec:2dAlignment} such that it (a) covers the entire plane and (b)
-minimizes the visibility of borders between the images. A
-straightforward cost function that accomplishes the latter is the sum
-of squared differences (SSD) of pixels in overlapping regions between
-all pairs of images. Minimizing this cost function encourages image
-boundaries to occur either in featureless areas, such as bare walls,
-or in areas where images match extremely well.
+For vertical surfaces however, which make up a large portion of most
+models, images are usually taken from close distances and head-on
+angles, resulting in high resolution fronto-parallel projections. As a
+result, for each tile on a wall plane, the scoring function of Figure
+\ref{fig:scoringFunction} is relatively flat with respect to candidate
+images, as they are all more or less head on. Since the scoring
+function is less discriminative for walls, it is conceivable to devise
+a different texturing strategy to directly minimize visible seams when
+texturing them. This is done by choosing the smallest possible subset
+of images from the set selected in Section \ref{sec:imageSelection}
+and aligned in Section \ref{sec:2dAlignment} such that it (a) covers
+the entire plane and (b) minimizes the visibility of borders between
+the images. A straightforward cost function that accomplishes the
+latter is the sum of squared differences (SSD) of pixels in
+overlapping regions between all pairs of images. Minimizing this cost
+function encourages image boundaries to occur either in featureless
+areas, such as bare walls, or in areas where images match extremely
+well.
 
@@
   \centering
-  \includegraphics[width=5in]{dagCreation.pdf}
+  \includegraphics[width=4in]{dagCreation.pdf}
   \caption{DAG construction for the image selection process. \\}
@@
 
-In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. Since these holes are rare,
-and generally fairly small, we use a greedy approach, repeatedly
-filling the hole with images that result in the lowest SSD costs in a
-blending region around the hole, as discussed in Section
-\ref{sec:blending}. This method is not optimal as a true 2D-coverage
-solution would be, but it is a fast approximation, and adequately
-handles the few holes encountered.
-
 We have now (a) mapped every location on the plane to at least one
@@
 retaining around 20\% of the image subset obtained in Section
-\ref{sec:simpleTextureMapping}, and (c) decreased the discontinuities
-at each image border. As seen in Figure \ref{fig:compareAll}(d), this
+\ref{sec:imageSelection}, and (c) decreased the discontinuities at
+each image border. As seen in Figure \ref{fig:compareAll}(d), this
 shortest path method has fewer visible discontinuities than Figure
@@
 
-When texturing an entire 3D planar model, we apply the shortest path
-method on walls, due to its superior results when provided with
-head-on images. Floors and ceilings however, given their many images
-taken at oblique angles, are textured using the tile caching method of
-Section \ref{sec:mappingWithCaching}.
+When texturing a model, we apply the shortest path method on vertical
+surfaces, due to its superior results when provided with head-on
+images. Floors, ceilings, and smaller complex objects such as
+furniture, given their many images taken at oblique angles, are
+textured using the tile caching method of Section
+\ref{sec:mappingWithCaching}.
 
@@
 we can ensure overlap by texturing a larger tile than needed for
-display. For example, for a rendered tile $l_1 \times l_1$, we can
-associate it with a texture $(l_1 + l_2) \times (l_1 + l_2)$ in size.
-We have found $l_2 = \frac{l_1}{2}$ to provide a balance between
-blending and keeping features unblurred. For the shortest path method,
-we have already ensured overlap between images. To enforce consistent
-blending however, we add a minimum required overlap of images of 200
-mm while solving the shortest path problem in Section
-\ref{sec:shortestPath}. Additionally, if images overlap in a region
-greater than the overlap distance, we only apply blending over an area
-equal to the overlap distance.
+display. For example, for a rendered tile of size $l_1 \times l_1$, we
+can associate it with a texture $(l_1 + l_2) \times (l_1 + l_2)$ in
+size.  We have found $l_2 = \frac{l_1}{2}$ to provide a good balance
+between blending and keeping features unblurred at image
+boundaries. For the shortest path method, we already have ensured
+overlap between images. To enforce consistent blending however, we add
+a minimum required overlap of images of 200 mm while solving the
+shortest path problem in Section \ref{sec:shortestPath}. Additionally,
+if images overlap in a region greater than the overlap distance, we
+only apply blending over an area equal to the overlap distance.
 
@@
 
-\section{Visualization}
-\label{sec:visualization}
-
 \section{Results}
 \label{sec:results}
-Examples of ceilings and floors textured with the tile caching
-approach, and walls textured with the shortest path approach, are
-displayed in Figure \ref{fig:results}. High resolution colored texture
-comparisons, as well as video and interactive walkthroughs of full
-models are available at
+This section contains results of the proposed texture mapping process
+on a number of different environments, with geometry generated from
+three different models. Further images of individual textured
+surfaces and entire textured models, as well as videos and interactive
+walkthroughs can also be found at
 \footnote{\url{http://www-video.eecs.berkeley.edu/research/indoor/}}.
 
+\subsection{Examples}
+\label{sec:examples}
+As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
+procedure in this thesis can be applied both to low-resolution and
+high-resolution models. Low resolution models have an advantage in
+their simplicity, and in that only important environmental features
+are represented. As a result, images are generated for large sections
+of buildings, and boundaries between each texture are minimally
+visible. High resolution models have an obvious advantage in terms of
+the amount of detail that can be reconstructed, but with poor region
+partitioning, as described in Section \ref{sec:geometryPartitioning},
+or with high camera pose or geometry reconstruction error, 3D elements
+in the environment geometry may not match up well with their imaged
+counterparts.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
+  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
+  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
+  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_v.png}
+  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_2d.png}
+  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_3d.png}\\
+  \subfloat[][]{
+    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
+  } \subfloat[][]{
+    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
+  } \subfloat[][]{
+    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
+  }
+  \caption{The same indoor environments, as generated using (a) PCA
+    plane-fitting, (b) Floor plan extrusion, (c) Watertight mesh
+    generation. The first two are low-resolution models, while the
+    third is high-resolution}
+  \label{fig:modelcomparisons}
+\end{figure}
+
+Our approach was tested with three different geometry-reconstruction
+methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
+floor plan extrusion method \cite{turnerfloorplan}, and a
+voxel-carving mesh generation method \cite{turnerwatertight}. The
+first two methods generate lower-resolution models, containing only
+major walls, ceilings and floors. The third method generates
+high-resolution models, and attempts to reconstruct all scanned
+objects in the environment. A comparison of all three methods as
+applied to the same dataset is shown in Figure
+\ref{fig:modelcomparisons}
+
+\begin{figure}
+  \centering \subfloat[][]{
+    \includegraphics[width=3in]{results_p15_v.png}
+  } \subfloat[][]{
+    \includegraphics[width=3in]{results_p15_2d.png}
+  }
+  \caption{(a) A model generated by the PCA method with many missing
+    surfaces. (b) A watertight model generated by the floor plan
+    extrusion method.}
+  \label{fig:lowresmodels}
+\end{figure}
+
+The PCA and floor plan methods produce models at a similar level of
+detail. As visible in Figure \ref{fig:lowresmodels}, the PCA method is
+not watertight, while the floor plan method is. As a result, the
+PCA-generated model contains holes where surfaces were not adequately
+scanned. On the other hand, the watertight floor plan model sometimes
+must make assumptions about the location of surfaces that were not
+adequately scanned, in order to maintain watertightness. Because
+buildings generally follow straight lines and right angle corners
+however, such assumptions tend to be correct. Additionally, the
+floor-plan method is generally superior at reconstructing smaller
+surfaces, such as small walls, or to approximate curved surfaces,
+while the PCA method only fits large planes, and fails in both
+cases. As a result, the floor-plan method usually produces more
+visually pleasing low-resolution models, and is the method of choice
+for generating textured low-resolution models.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=3.1in]{results_houston_1_2d.png}
+  \includegraphics[width=3.1in]{results_houston_1_3d.png}\\
+  \includegraphics[width=3.1in]{results_houston_2_2d.png}
+  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
+  \subfloat[][]{
+    \includegraphics[width=3.1in]{results_houston_3_2d.png}
+  } \subfloat[][]{
+    \includegraphics[width=3.1in]{results_houston_3_3d.png}
+  }
+  \caption{(a) A model generated by the low-resolution floor plan
+    method. (b) A model generated by the high-resolution voxel-carving
+    method.}
+  \label{fig:2dvs3d}
+\end{figure}
+
+High-resolution models, as generated by the voxel-carving method, can
+produce more accurate reconstructions of environment geometry. With
+such models, region partitioning, as described in Section
+\ref{sec:geometryPartitioning}, plays an important factor in the
+quality of generated textures. If regions are small, boundaries
+between adjacent textures become visible, and since each region is
+processed independently, image alignment procedures are performed
+across smaller areas. If regions are large, then the difference
+between the 3D surface geometry and the approximated 2D texturing
+surface become large as well, introducing greater texture projection
+error. Additionally, in areas where pose error or surface
+reconstruction error is high, 3D objects in images do not get
+accurately projected onto their modeled counterparts. While large
+objects can be aligned to geometry via the methods in Section
+\ref{sec:geometryAlignment}, smaller objects such as plants or
+computers are difficult to line up to geometry references. While the
+compositing techniques is Section \ref{sec:imageCompositing} can
+ensure that textures for small objects appear seamless, such textures
+may not map accurately upon their corresponding geometry, leading to
+visually obvious discrepancies in the textured model. Figure
+\ref{fig:2dvs3d} contains textured examples from the low-resolution
+floor plan approach alongside examples from the high-resolution
+voxel-carving approach. As evident in the image comparisons, the 3D
+models may be more accurate, but the 2D models often allow for a
+cleaner visualization, with larger regions over which images are
+successfully composited together.
+
+As visible in Figure \ref{fig:2dvs3d} and other images in this
+section, 2D models using the floor plan approach are generally
+preferred, as they provide enough detail in geometry to reconstruct
+the basic layout of an environment, while textures can be used to
+visualize smaller details. On the other hand, for applications where
+furniture and smaller interior details are important, applying
+textures to the 3D voxel-carved models provides useful image-based
+context for visualizing indoor areas. Further examples of
+texture-mapped models are contained at the end of this
+document. Figure \ref{fig:indivPlanes} contains textured surfaces
+alone. Figures \ref{fig:victor1}-\ref{fig:e2d4} contain interior and
+exterior views of low-resolution models. Figures
+\ref{fig:e3d1}-\ref{fig:e3d4} contain interior and exterior views of
+high-resolution models.
+
+\subsection{Runtime}
 As mentioned earlier, our approach is quite efficient. The top wall in
-Figure \ref{fig:results}(a) was generated with 7543 $\times$ 776
-pixels, and spans a 40-meter long wall. Given 41000 input images of
+Figure \ref{fig:indivPlanes}(a) was generated with 7543 $\times$ 776
+pixels, and spans a 40-meter long wall. Given 41000 input images in
 the entire dataset, a 2.8GHz dual-core consumer-grade laptop takes
-approximately a minute to choose 36 candidate images, followed by
-under a minute to perform both image alignment and the shortest path
-texturing method, though over 75\% of that time is spent calculating
-SIFT matches within the SiftGPU framework, which could feasibly be
-split into a separate preprocessing step. While not real-time, the
-process is capable of generating fast updates after changes in various
-parameters or modifications to input data, and if integrated directly
-into a 3D modeling system, could provide live visualization as data is
-collected. Our full models consist of an input model file, textures,
-and a mapping of image points to 3D model vertices. The models shown
-in Figure \ref{fig:results} are roughly 20 MB in size, and are
-visualized using the OpenSceneGraph toolkit \cite{openscenegraph},
-which allows for export to many common model formats, as well as
-efficient visualization, even in web browsers or mobile devices.
+under a second to choose 36 candidate images, followed by a minute to
+perform image projections, image alignment, and the shortest path
+texturing method. The tile-caching approach takes roughly comparable
+time, and over 75\% of the time for either method is spent on
+calculating image projections, which are cached over multiple runs,
+and also could be performed as a preprocessing step instead. While not
+real-time, the process is capable of generating fast updates after
+changes in various parameters or modifications to input data, and if
+integrated directly into a 3D modeling system, could provide quick
+visual feedback as data is collected.
+
+\subsection{Visualization}
+Our full models consist of an input model file, generated textures,
+and a mapping of image points to 3D model vertices. The textured
+models shown throughout this thesis range from 20 MB in size to over
+400 MB in a compressed format, with textures of sizes over 500
+megapixels. These models are visualized using the OpenSceneGraph
+toolkit \cite{openscenegraph}, which allows for export to many common
+model formats, as well as interactive visualization, even in web
+browsers or mobile devices.
 
@@
 
-In this paper, we have developed an approach to texture mapping models
-with noisy camera localization data. We are able to refine image
-locations based on geometry references and feature matching, and
-robustly handle outliers. Using the tile-based mapping approach, we
-can texture both simple rectangular walls as well as complex floor and
-ceiling geometry. We also implemented a shortest path texturing method
-that produces seamless textures on planes where multiple head-on
-images are available. Both of these approaches are highly modular, and
-easily tunable for similar systems across multiple environments.
-
-Our method is likely to fail in scenarios where 3D error is large. A
-logical progression of our approach to resolve camera error in 3D is
-to perform matching between image lines and geometry in 3D, which can
-be done reasonably efficiently \cite{linebased,
+In this thesis, we have developed an approach to texture mapping
+models of indoor environments with noisy camera localization data. We
+are able to refine image locations based on geometry references and
+feature matching, and robustly handle outliers. Using the tile-based
+mapping approach, we can texture both large planar features as well as
+smaller, more complex surfaces. We also implemented a shortest path
+texturing method that produces seamless textures on planes where
+multiple head-on images are available. Both of these approaches are
+highly modular, and easily tunable for similar systems across multiple
+environments.
+
+Our method is likely to fail however in scenarios where 3D error is
+large. A logical progression of our approach to resolve camera error
+in 3D is to perform matching between image lines and geometry in 3D,
+which can be done reasonably efficiently \cite{linebased,
   rectangularstructures}. Using linear features in addition to SIFT
@@
 \cite{linearposeestimation}. Finally, the blending procedure is quite
-basic, and applying more sophisticated methods of blending as well as
-normalization would benefit the final visual quality, and more
-robustly handle motion-based or parallax errors.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
-  \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
+basic, and applying more sophisticated methods of blending,
+normalization, as well as image boundary selection would benefit the
+final visual quality, and more robustly handle motion-based or
+parallax errors.
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=6in]{finalfloors.jpg}} ~~~~~~~~
+  \\
+  \centering
+  \subfloat[][]{\includegraphics[width=6in]{finalceilings.jpg}}
 
@@
   }
-
+  \caption{Examples of our final texture mapping output for (a) walls,
+    (b) ceilings, (c) floors}
+  \label{fig:indivPlanes}
+\end{figure}
+
+\begin{figure}
   \centering{
-    \includegraphics[width=3in]{fullmodel.png}
-    \includegraphics[width=3in]{pier15.png} \\
-    \includegraphics[width=3in]{threestoryfull2.png}
-    \includegraphics[width=3in]{threestoryfull.png}
-  }
-
-  \centering \subfloat[][]{ }
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) floors, (d) full models.}
-  \label{fig:results}
+    \includegraphics[width=6.2in]{threestoryfull2.png} \\
+    \includegraphics[width=6.2in]{threestoryfull.png}
+  }
+  \caption{Textured low-resolution models from the PCA-based approach.}
+  \label{fig:victor1}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in]{fullmodel.png} \\
+    \includegraphics[width=6.2in]{pier15.png} \\
+  }
+  \caption{Textured low-resolution models from the PCA-based approach.}
+  \label{fig:victor2}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston3.png}
+  }
+  \caption{A textured low-resolution model from the floor plan extrusion approach.}
+  \label{fig:e2d1}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{coryf2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{coryf2_2d_1.png} \\
+    \includegraphics[width=6.2in,height=3in]{coryf2_2d_2.png}
+  }
+  \caption{A textured low-resolution model from the floor plan extrusion approach.}
+  \label{fig:e2d2}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{office.png} \\
+    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston3.png}
+  }
+  \caption{A textured low-resolution model from the floor plan extrusion approach.}
+  \label{fig:e2d3}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=6in,height=1.7in]{coryf2.jpg}\\
+    \includegraphics[width=6in,height=1.7in]{houston1.jpg}
+  }
+  \caption{Further exterior views of textured models.}
+  \label{fig:e2d4}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston3.png}
+  }
+  \caption{A textured high-resolution model from the voxel-carving approach.}
+  \label{fig:e3d1}
+\end{figure}
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{coryf2_3d_1.png} \\
+    \includegraphics[width=6.2in,height=3in]{coryf2_3d_2.png} \\
+    \includegraphics[width=6.2in,height=3in]{coryf2_3d_3.png}
+  }
+  \caption{A textured high-resolution model from the voxel-carving approach.}
+  \label{fig:e3d2}
+\end{figure}
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston3.png}
+  }
+  \caption{A textured high-resolution model from the voxel-carving approach.}
+  \label{fig:e3d3}
+\end{figure}
+\begin{figure}
+  \centering{
+    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston3.png}
+  }
+  \caption{A textured high-resolution model from the voxel-carving approach.}
+  \label{fig:e3d4}
 \end{figure}

### 2013-11-08 masters/body/masters.tex
dunno

@@
 This section contains results of the proposed texture mapping process
-on a number of different environments, with geometry generated from
-three different models. Further images of individual textured
+on a number of different environments, with geometry generated using
+three different methods. Further images of individual textured
 surfaces and entire textured models, as well as videos and interactive
@@
 are represented. As a result, images are generated for large sections
-of buildings, and boundaries between each texture are minimally
-visible. High resolution models have an obvious advantage in terms of
+of buildings, and texture continuity is maintained over large
+areas. High resolution models have an obvious advantage in terms of
 the amount of detail that can be reconstructed, but with poor region
@@
   \caption{The same indoor environments, as generated using (a) PCA
-    plane-fitting, (b) Floor plan extrusion, (c) Watertight mesh
-    generation. The first two are low-resolution models, while the
-    third is high-resolution}
+    plane-fitting, (b) Floor plan extrusion, (c) Voxel carving. The
+    first two are low-resolution models, while the third is
+    high-resolution. The PCA method is not watertight, and contains
+    some holes (white). It also has the lowest level of detail in its
+    geometry. The floor plan method is slightly more detailed, and is
+    watertight as well. The voxel carving method also produces
+    watertight meshes, and reconstructs smaller features, such as the
+    bench and the ladder in the lower two images.}
   \label{fig:modelcomparisons}
@@
 high-resolution models, and attempts to reconstruct all scanned
-objects in the environment. A comparison of all three methods as
-applied to the same dataset is shown in Figure
-\ref{fig:modelcomparisons}
+objects in the environment. Images illustrating the differences
+between the three methods are in Figure \ref{fig:modelcomparisons}
 
@@
     method. (b) A model generated by the high-resolution voxel-carving
-    method.}
+    method. The high-resolution model contains far more surface
+    detail, such as in the ceiling indentations or the benches on the
+    ground. In terms of producing a realistic visualization however,
+    the low-resolution model performs very similarly to the
+    high-resolution model.}
   \label{fig:2dvs3d}
@@
 exterior views of low-resolution models. Figures
-\ref{fig:e3d1}-\ref{fig:e3d4} contain interior and exterior views of
+\ref{fig:e3d1}-\ref{fig:e3d3} contain interior and exterior views of
 high-resolution models.
@@
   \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
+    \includegraphics[width=6.2in,height=3in]{houston2d1.png} \\
+    \includegraphics[width=6.2in,height=3in]{houston2d2.png} \\
     \includegraphics[width=6.2in,height=3in]{houston3.png}
@@
     \includegraphics[width=6.2in,height=3in]{office.png} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
+    \includegraphics[width=6.2in,height=3in]{office1.png} \\
+    \includegraphics[width=6.2in,height=3in]{office2.png}
   }
@@
   \centering{
-    \includegraphics[width=6in,height=1.7in]{coryf2.jpg}\\
-    \includegraphics[width=6in,height=1.7in]{houston1.jpg}
-  }
-  \caption{Further exterior views of textured models.}
+    \includegraphics[width=6.2in,height=3in]{bhh1.png} \\
+    \includegraphics[width=6.2in,height=3in]{bhh2.png} \\
+    \includegraphics[width=6.2in,height=3in]{bhh3.png}
+  }
+  \caption{A textured low-resolution model from the floor plan extrusion approach.}
   \label{fig:e2d4}
@@
     \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
+    \includegraphics[width=6.2in,height=3in]{houston3d2.png}
   }
@@
   \centering{
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_1.png} \\
+    \includegraphics[width=6.2in,height=3in]{coryf2_3d_4.png} \\
     \includegraphics[width=6.2in,height=3in]{coryf2_3d_2.png} \\
@@
   \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
+    \includegraphics[width=6.2in,height=3in]{bhh3d1.png} \\
+    \includegraphics[width=6.2in,height=3in]{bhh3d2.png} \\
+    \includegraphics[width=6.2in,height=3in]{bhh3d3.png}
   }
@@
 \end{figure}
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d4}
-\end{figure}
 

### 2013-11-28 masters/body/_region_.tex
gain comp

--- 2013-05-02 masters/body/_region_.tex
@@
 
-\message{ !name(masters.tex) !offset(135) }
-\subsection{Geometry Partitioning}
-\label{sec:geometryPartioning}
-In order to effectively texture a 3D model, we first divide the model
-into a set of regions, each to be textured independently. The purpose
-of this is to ensure texture continuity along large uniform areas,
-while allowing texture boundaries to fall along natural environmental
-boundaries. Because textures may not match at such boundaries where
-two regions meet, it is important to minimize the visibility of
-boundaries. This is done by encouraging region boundaries to occur at
-large sharp corners, where texture continuity is less important.
+\message{ !name(masters.tex) !offset(890) }
+\subsection{Exposure Compensation}
+\label{sec:exposureCompensation}
 
-When working with low-resolution models, where surfaces generally
-correspond to large planar features such as walls, ceilings, or
-floors, and often meet at right angles, each planar surface in the
-model is directly treated as a distinct region and textured
-separately.
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3.3in]{exposureDiff1.png}}
+  \subfloat[][]{\includegraphics[width=3.3in]{exposureDiff2.png}}
+  \caption{(a) A ceiling texture composed of images taken with varying
+    exposures, with significant brightness differences. (b) Exposure
+    compensation applied to the same set of images from (a) by
+    applying computed gains to each image}
+  \label{fig:exposureDiff}
+\end{figure}
 
-When working with a high-resolution model however, geometry often
-represents large features as well as small details found in furniture,
-plants, and other miscellaneous objects. For instance, in Figure
-\ref{fig:deskGeom}, the geometry modeling the desk and binders
-consists of many small triangles at various orientations. Texturing
-each of these triangles independently makes little sense, as the
-textures applied to each should match up well with the textures of its
-neighbors in order to avoid any breaks in the overall image of the
-desk and binders. On the other hand, the textures for the triangles
-belonging to the wall behind need not match up with the textures on
-the desk and binders, and so each group of triangles should be
-designated to separate regions.
-This region grouping is performed by designating all contiguous coplanar groups of triangles as different regions.
-Any region that is less than $1 m^2$ in size is joined to its largest neighboring region, such that the angle between them is under $90^{\circ}$.
+Before blending images together, exposure compensation is applied to
+equalize brightness among neighboring images. For the images in this
+report, cameras are set to have automatic exposure, which means that
+images of the same object may have different brightness levels. While
+successful image alignment and blending can reduce sharp seams between
+adjacent images, there may still be noticeable brightness gradients
+between images, particularly in areas near light sources. This can be
+seen in Figure \ref{fig:exposureDiff}(a), where the ceiling texture
+has patches of clearly differing brightness, most noticeably around
+light sources. To diminish this effect, a gain can be computed and
+applied to each image, with the effect of linearly scaling the
+brightness of an image. The goal is to compute a gain for each image,
+such that the brightness of an area is consistent across image
+boundaries.
 
-Because a texture is 2D, and the region to be textured may not be
-flat, a mapping needs to be defined. We first fit a plane to each
-region for the purposes of texturing. This can be accomplished via a
-least squares plane-fitting through each triangle vertex, though in
-practice we simply use the plane equation of the largest contiguous
-section of coplanar triangles, as most regions are characterized by
-small outcroppings from a largely planar surface, such as objects on a
-table or features protruding from a wall. The 3d vertices within a
-region are then projected onto its calculated plane, and the
-rectangular bounding box for these projected vertices is
-calculated. This bounding box corresponds to the 2D image that will be
-created to texture the region.
+Similar to the image location adjustment procedure in Section
+\ref{sec:robustSIFTFeatureMatching}, exposure compensation can be
+neatly formed as a least-squares optimization problem with pair-wise
+observations. In this case, observations do not need to be weighted,
+and so the formulation is $\textrm{min}_{\vec{\beta}} ||(A \vec{\beta}
+- \vec{\gamma})||_2^2 $. An example setup for 3 images, each with 2
+overlapping pixels is shown below.
+\[
+A =
+\begin{pmatrix}
+  P_{11} & -P_{12} & 0\\
+  P_{21} & -P_{12} & 0\\
+  0 & P_{32} & -P_{33}\\
+  0 & P_{42} & -P_{43}\\
+  1 & 1 & 1\\
 
-Of course, the area encompassed by the bounding box is larger than the
-corresponding 2d area of the projected geometry, which itself is not
-as accurate as the original 3d geometry. Thus, we also create a k-d
-tree consisting of the triangle primitives from the original
-mesh. Though we generate texture for the 2d bounding box surface, we
-will reference the original 3D geometry to ensure accuracy when
-texturing.
+\end{pmatrix}\quad
+\vec{\beta} =
+\begin{pmatrix}
+  G_1, \\ G_2, \\ G_3
+\end{pmatrix}
+\vec{\gamma} =
+\begin{pmatrix}
+  0, \\ 0, \\ 0, \\ 0, \\ 3
+\end{pmatrix}
+\]
 
-\message{ !name(masters.tex) !offset(944) }
+In this problem, $\beta$ is the vector of gains $G_i$ to be solved
+for.  The observations, represented by $A$ and $\gamma$, correspond to
+equalizing the brightness for each pixel present in two images. For
+instance, for pixel $P_x$ which is present in two overlapping images
+$I_i$ and $I_j$, the goal is to find gains $G_i$ and $G_j$ such that
+$G_iP_{xi} - G_jP_{xj} = 0$, where $P_{xy}$ is the value of pixel
+$P_x$ in image $I_y$. Thus, $\gamma$ contains all zeros, while each
+row of $A$ contains a $P_i$ value in the $ith$ column and a $-P_j$
+value in the $jth$ column, and zeros elsewhere. The number of
+observations is thus equal to the number of pixels that occur in two
+distinct images.  This problem is not constrained, as it allows all
+computed gains to be scaled by any amount. To keep gains at reasonable
+values, a final observation is added: $\Sigma G_i = N$, where $N$ is
+the number of images. This has the effect of averaging all gains to 1.
+
+The result of computing gains and equalizing exposure can be seen for
+the same ceiling location in Figure \ref{fig:exposureDiff}(b). The
+effect is clear, as dark/bright patches are no longer present, and the
+overall brightness of the image has not changed significantly.
+
+\message{ !name(masters.tex) !offset(1248) }
 

### 2013-11-28 masters/body/masters.tex
gain comp

@@
 
+\subsection{Exposure Compensation}
+\label{sec:exposureCompensation}
+
+\begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3.3in]{exposureDiff1.png}}
+  \subfloat[][]{\includegraphics[width=3.3in]{exposureDiff2.png}}
+  \caption{(a) A ceiling texture composed of images taken with varying
+    exposures, with significant brightness differences. (b) Exposure
+    compensation applied to the same set of images from (a) by
+    applying computed gains to each image}
+  \label{fig:exposureDiff}
+\end{figure}
+
+Before blending images together, exposure compensation is applied to
+equalize brightness among neighboring images. For the images in this
+report, cameras are set to have automatic exposure, which means that
+images of the same object may have different brightness levels. While
+successful image alignment and blending can reduce sharp seams between
+adjacent images, there may still be noticeable brightness gradients
+between images, particularly in areas near light sources. This can be
+seen in Figure \ref{fig:exposureDiff}(a), where the ceiling texture
+has patches of clearly differing brightness. To diminish this effect,
+a gain can be computed and applied to each image, with the effect of
+linearly scaling the brightness of each image. The goal is to compute
+a gain for each image, such that the brightness of an area is
+consistent across image boundaries.
+
+Similar to the image position refinement procedure in Section
+\ref{sec:robustSIFTFeatureMatching}, exposure compensation is
+performed simulatenously across all images present in a single
+region. As before, this is solved as a least-squares optimization
+problem with pair-wise observations. In this case, observations do not
+need to be weighted, and so the formulation is
+$\textrm{min}_{\vec{\beta}} ||(A \vec{\beta} - \vec{\gamma})||_2^2
+$. An example setup for 3 images, each with 2 overlapping pixels, is
+shown below.
+\[
+A =
+\begin{pmatrix}
+  P_{11} & -P_{12} & 0\\
+  P_{21} & -P_{12} & 0\\
+  0 & P_{32} & -P_{33}\\
+  0 & P_{42} & -P_{43}\\
+  1 & 1 & 1\\
+
+\end{pmatrix}\quad
+\vec{\beta} =
+\begin{pmatrix}
+  G_1, \\ G_2, \\ G_3
+\end{pmatrix}
+\vec{\gamma} =
+\begin{pmatrix}
+  0, \\ 0, \\ 0, \\ 0, \\ 3
+\end{pmatrix}
+\]
+
+In this problem, $\beta$ is the vector of gains $G_i$ to be solved
+for.  The observations, represented by $A$ and $\gamma$, correspond to
+equalizing the brightness for each pixel present in two images. For
+instance, for pixel $P_x$ which is present in two overlapping images
+$I_i$ and $I_j$, the goal is to find gains $G_i$ and $G_j$ such that
+$G_iP_{xi} - G_jP_{xj} = 0$, where $P_{xy}$ is the value of pixel
+$P_x$ in image $I_y$. Thus, $\gamma$ contains all zeros, while each
+row of $A$ contains a $P_{xi}$ value in the $ith$ column and a
+$-P_{xj}$ value in the $jth$ column, and zeros elsewhere. This problem
+is not constrained, as it allows all computed gains to be scaled by
+any amount. To keep gains at reasonable values, a final observation is
+added: $\Sigma G_i = N$, where $N$ is the number of images. This has
+the effect of setting the average of all gains to 1, and is
+represented by adding a row of ones to $A$, and a corresponding $N$
+value to $\gamma$.
+
+The result of computing and applying gains for each image can be seen
+for the same ceiling location in Figure \ref{fig:exposureDiff}(b). As
+compared to Figure \ref{fig:exposureDiff}(a), the effect is clear, as
+dark/bright patches are no longer present, and the overall brightness
+of the image has not changed significantly.
+
 \subsection{Blending}
@@
 \ref{sec:mappingWithCaching} and \ref{sec:shortestPath}. Although the
-image alignment steps and image selection in both methods attempt to
-minimize all mismatches between images, there are occasional
-unavoidable discontinuities in the final texture due to different
-lighting conditions or inaccuracies in model geometry. These can
-however be treated and smoothed over by applying alpha blending over
-image seams.  Whether the units to be blended are
-rectangularly-cropped images or rectangular tiles, we can apply the
-same blending procedure, as long as there is a guaranteed overlap
-between units to blend over.
+image alignment and selection steps in both methods attempt to
+minimize all mismatches between images, and exposure compensation
+minimizes brightness differences, there are occasional unavoidable
+discontinuities in the final texture due to parallax effects or
+inaccuracies in model geometry. These can however be treated and
+smoothed over by applying alpha blending over image seams.  Whether
+the units to be blended are rectangularly-cropped images or
+rectangular tiles, we can apply the same blending procedure, as long
+as there is a guaranteed overlap between units to blend over.
 

### 2013-11-28 masters/body/compressPdf.sh

@@ -1,0 +1,3 @@
+#!/bin/sh
+
+gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dNOPAUSE -dQUIET -dBATCH -sOutputFile=$2 $1

### 2013-12-29 acivs/acivs.tex
cleanup

--- 2013-03-03 spie/paper.tex
@@
-%  article.tex (Version 3.3, released 19 January 2008)
-%  Article to demonstrate format for SPIE Proceedings
-%  Special instructions are included in this file after the
-%  symbol %>>>>
-%  Numerous commands are commented out, but included to show how
-%  to effect various options, e.g., to print page numbers, etc.
-%  This LaTeX source file is composed for LaTeX2e.
-
-%  The following commands have been added in the SPIE class 
-%  file (spie.cls) and will not be understood in other classes:
-%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
-%  The bibliography style file is called spiebib.bst, 
-%  which replaces the standard style unstr.bst.
-
-\documentclass[]{spie}  %>>> use for US letter paper
-%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
-%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
-%% \addtolength{\voffset}{9mm}   %>>> moves text field down
-%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
-%  The following command loads a graphics package to include images 
-%  in the document. It may be necessary to specify a DVI driver option,
-%  e.g., [dvips], but that may be inappropriate for some LaTeX 
-%  installations. 
+% This is LLNCS.DEM the demonstration file of
+% the LaTeX macro package from Springer-Verlag
+% for Lecture Notes in Computer Science,
+% version 2.4 for LaTeX2e as of 16. April 2010
+%
+\documentclass{llncs}
+\usepackage{cite}
 \usepackage{graphicx}
@@
 
-\author{Peter Cheng, Michael Anderson, Stewart He, and Avideh Zakhor
-\skiplinehalf
-University of California, Berkeley\\
-}
+\author{Peter Cheng \and Michael Anderson \and Stewart He \and Avideh Zakhor}
+\institute{University of California, Berkeley\\ Berkeley CA 94720, USA}
 
@@
   even in the presence of inaccurate surface geometry and noisy camera
-  poses. The final step is to select and composite images into a
-  texture mosaic. The effectiveness of the proposed method is
-  demonstrated on a number of different indoor environments.
+  poses. Images are then composited into a final texture mosaic. The
+  effectiveness of the proposed method is demonstrated on a number of
+  different indoor environments.
+
+  \keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}
 \end{abstract}
@@
 % >>>> Include a list of keywords after the abstract
-
-\keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}
 
@@
 reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
-known as the simultaneous localization and mapping (SLAM) problem, and
-is generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment. Mounting such devices on a platform carried by
-an ambulatory human provides unique advantages over vehicular-based
-systems on wheels in terms of agility and portability, but can also
-result in larger localization error \cite{liu2010indoor}. As a result,
-common methods for texture mapping generally produce poor results.
+\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is known as the simultaneous localization and
+mapping (SLAM) problem, and is generally solved by taking readings
+from laser range scanners, cameras, and inertial measurement units
+(IMUs) at multiple locations within the environment. Mounting such
+devices on a platform carried by an ambulatory human provides unique
+advantages over vehicular-based systems on wheels in terms of agility
+and portability, but can also result in larger localization error
+\cite{liu2010indoor}. As a result, common methods for texture mapping
+generally produce poor results.
 
@@
 equipped with fisheye lenses reaching an approximately 180$^{\circ}$
-field of view and taking photos at a rate of 5 Hz. Applying multiple
-localization and loop-closure algorithms on the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, the backpack is localized\footnote{In this paper, we
-  use the terms localization and pose recovery interchangeably, in
-  that they both refer to recovering position and orientation.}  over
-its data collection period. This requires recovering the 6 degrees of
-freedom for the backpack itself as well as the cameras rigidly mounted
-on it. Once this is complete, the data from the laser range scanners
-is used to generate a 3D point cloud of the surrounding environment,
-from which a 3D planar model is created \cite{sanchez2012point}. This
-model, consisting of 2D polygonal planes in 3D space, along with the
-set of images captured by the backpack's cameras and their noisy 3D
-poses, can be considered the input to our texture mapping problem.
+field of view and taking photos at a rate of 5 Hz
+\cite{liu2010indoor}. Applying multiple localization and loop-closure
+algorithms on the raw data collected by the onboard sensors
+\cite{chen2010indoor, kua2012loopclosure, liu2010indoor}, the backpack
+is localized\footnote{In this paper, we use the terms localization and
+  pose recovery interchangeably, in that they both refer to recovering
+  position and orientation.}  over its data collection period. This
+involves recovering the 6 degrees of freedom for the backpack itself
+as well as the cameras rigidly mounted on it. Once this is complete,
+the data from the laser range scanners is used to generate a 3D point
+cloud of the surrounding environment, from which a 3D planar model is
+created \cite{sanchez2012point}. This model, consisting of 2D
+polygonal planes in 3D space, along with the set of images captured by
+the backpack's cameras and their noisy 3D poses, can be considered the
+input to our texture mapping problem.
 
@@
   \centering
-  \includegraphics[width=6in]{flowchart.jpg}
+  \includegraphics[width=4.5in]{flowchart.jpg}
   \caption{The proposed texture mapping procedure\\}
@@
 The overall block diagram for the proposed texture mapping procedure
-is shown in Figure \ref{fig:flowchart}. We texture map each planar
-surface independently and in parallel. For each surface, we begin by
-obtaining a set of images that spans the entire surface with high
-resolution imagery. We then use our noisy camera poses to project
-these selected images onto the surface. These projections are then
-refined in 2D, in order to maximally align them with the surface's
-geometry, as well as to each other, allowing us to handle both errors
-in geometry as well as camera poses. For surfaces and camera poses at
-arbitrary locations or orientations, generally ceilings and floors, we
-propose a tile-based approach for sampling high-resolution portions of
-images and compositing them into a texture. In cases where cameras
-have consistently perpendicular viewing angles to the surfaces under
+is shown in Figure \ref{fig:flowchart}, where the number attached
+attached to each box indicates the section in which the concept in the
+box is explained in this paper. We texture map each planar surface
+independently and in parallel. For each surface, we begin by selecting
+a set of images that spans the entire surface with high resolution
+imagery. We then use our noisy camera poses to project these selected
+images onto the surface. These projections are then refined in 2D, in
+order to maximally align them with the surface's geometry, as well as
+to each other, allowing us to handle both errors in geometry as well
+as camera poses. For surfaces and camera poses at arbitrary locations
+or orientations, generally ceilings and floors, we propose a
+tile-based approach for sampling high-resolution portions of images
+and compositing them into a texture. In cases where cameras have
+consistently perpendicular viewing angles to the surfaces under
 consideration, generally walls, we demonstrate a superior approach
@@
 
-\section{Existing Approaches to Image Alignment}
-\label{sec:existingApproaches}
-There are many existing approaches to stitching together multiple
-images to produce a larger, seamless image \cite{szeliski2006image,
-  agarwalapanoramas, wangmultipleviews, coorg1997matching,
-  debevechybrid, bernardinimultiplescans}. Generally, parts of images
-are matched to each other, either through direct comparisons or
-feature detection and matching. Images are then transformed to
-maximize matches, often by computing homographies between pairs of
-images, or by iteratively adjusting camera poses in 1 to 6 degrees of
-freedom.
-
-Feature matching has a number of advantages over direct matching that
-make it more suitable for our often non-planar environments, and
-rotational differences between camera poses
-\cite{szeliski2006image}. Feature matching however, works best when
-multiple unique visual references exist in the environment that can be
-detected in multiple images. In contrast, indoor environments have a
-high prevalence of bare surfaces, as well as repeating textures, such
-as similar windows, doors, and wall-mounted decorations, that are
-difficult to disambiguate. This lack of reliable reference points
-often results in errors when matching images together.
-
-Additionally, our datasets often contain long chains of images,
-corresponding to long hallways and corridors as shown in Figure
-\ref{fig:mosaic3D}, which leads to error accumulation when image
-correspondences are not accurate. For example, when matching a long
-chain of images through homography, a pixel in the $nth$ image must be
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these
-homography matrices is propagated to all further images, resulting in
-drift.
-
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 20cm 0cm,
-    clip=true, width=6in, height=0.7in]{graphApproach.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 15cm 0cm,
-    clip=true, width=6in, height=0.7in]{autostitchResult.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 75cm 0cm,
-    clip=true, width=6in, height=0.7in]{finalLong.jpg}}
-
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm, (b) the AutoStitch software package, and (c)
-    the proposed method.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-In prior work, we have experimented with integrating image stitching
-with the iterative global localization algorithm used to recover the 6
-degrees of freedom of the backpack acquisition system
-\cite{liu2010indoor}. When run on long chains of images, especially
-where features are sparse, this approach produces distorted textures,
-as seen in Figure \ref{fig:mosaic3D}(a). Furthermore, this approach is
-not closed-form, and its iterative camera adjustment process over
-large datasets led to prohibitively long computation time.
-
-The AutoStitch software package performs homography-based alignment as
-well, with additional provisions that attempt to reduce drift and
-increase efficiency \cite{panorama2d, autostitch}. Though AutoStitch
-performs well in areas with dense features, it can not handle areas
-without features, and has trouble aligning wall sections with even
-short segments of bare texture. The example in Figure
-\ref{fig:mosaic3D}(b) has been generated after many rounds of manual
-tuning; we have empirically found that areas with fewer visual
-features or repeating texture patterns simply failed outright with
-AutoStitch.
-
 \section{Image Selection}
@@
 
-The geometry of the texture mapping process for a planar surface is
-shown in Figure \ref{fig:projection}. Given a set of $M$ images to
-texture a target plane, camera matrix $P_i$ for the $ith$ image
-transforms a 3D point in the world coordinate system to a 2D point or
-pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
-the camera's intrinsic parameters, containing focal length and image
-center, as well as extrinsic parameters which specify the rotation and
-translation of the camera's position in 3D world coordinates at the
-time that image $i$ is taken. These extrinsic parameters are
-determined by the backpack hardware and the corresponding localization
-algorithms \cite{chen2010indoor, liu2010indoor, kua2012loopclosure}
-and are noisy.
+% The geometry of the texture mapping process for a planar surface is
+% shown in Figure \ref{fig:projection}. Given a set of $M$ images to
+% texture a target plane, camera matrix $P_i$ for the $ith$ image
+% transforms a 3D point in the world coordinate system to a 2D point or
+% pixel in image $i$'s coordinates. A camera matrix $P_i$ is composed of
+% the camera's intrinsic parameters, containing focal length and image
+% center, as well as extrinsic parameters which specify the rotation and
+% translation of the camera's position in 3D world coordinates at the
+% time that image $i$ is taken. These extrinsic parameters are
+% determined by the backpack hardware and the corresponding localization
+% algorithms \cite{chen2010indoor, liu2010indoor, kua2012loopclosure}
+% and are noisy.
 
 Since the backpack system takes pictures at a rate of 5 Hz, hundreds
-of images are available for texturing each surface in the 3D
-model. Our objective in designing a texture mapping process is to
-determine which of these images should be used, and where their
-contents should map onto the final texture, in order to minimize any
-visual discontinuities or seams that would suggest that the plane's
-texture is not composed of a single continuous image. In the remainder
-of this section, we propose an image selection criteria and use it to
-derive a simple tile-based texture mapping procedure.
+of images are available for texturing each surface in the 3D model. To
+obtain a selection of images to work with, we discretize each surface
+into small square tiles, and for each tile, gather the images with a
+clear line of sight to it. We then find the image that maximizes the
+scoring function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ for
+each tile, as shown in Figure \ref{fig:scoringFunction}, where $d$ is
+the distance between the centers of a camera and a tile, and $\vec{n}$
+and $\vec{c}$ are the directions of the plane's normal and the camera
+axis respectively. In Figure \ref{fig:compareAll}(a), an image has
+been textured using the images selected for each tile. While images
+with good viewing angles and high resolution have been used, there are
+a significant amount of discontinuities, though many appear
+reconcilable with 2D transformations.
+
+By aggregating the images selected for tiles on each surface, we
+obtain a collection of images that can be used as a starting point for
+the proposed texturing procedure, as explained in Section
+\ref{sec:2dAlignment}. For our datasets, this process generally
+selects around 10\% of all the images that could be used for texturing
+the surface. This roughly 10:1 subsampling removes images with poor
+viewing angles, ensuring that the most promising images are considered
+in the following steps.
 
@@
     \centering
-    \includegraphics[height=1.8in]{Projection.pdf}
+    \includegraphics[height=1.2in,width=2in]{Projection.pdf}
     \caption{Surfaces to be textured are specified in 3D space by
@@
     \centering
-    \includegraphics[height=1.8in]{scoringFunction.jpg}
+    \includegraphics[height=1.2in, width=2in]{scoringFunction.jpg}
     \caption{We minimize camera angle $\alpha$ and distance $d$ by
@@
 
-Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
-a straightforward approach for texturing is to discretize the target
-plane into small square tiles, and choose an image to texture each
-tile directly. We choose to work with rectangular units to ensure that
-borders between any two distinct images in the final texture are
-either horizontal or vertical. Since most environmental features
-inside buildings are horizontal or vertical, any visible seams in the
-texture intersect them minimally and are therefore less noticeable.
+\begin{figure}
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_naive.jpg}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_naive_shift.jpg}}
 
-In order to select an image for texturing a tile $t$, we first gather
-a list of candidate images that contain all four of its corners; we
-can rapidly check this by projecting $t$ into each image using the
-$P_i$ camera matrices. Furthermore, each candidate image must have
-been taken at a time when its camera had a clear line-of-sight to $t$,
-which can be determined using standard ray-polygon intersection tests
-between the camera location, $t$, and every other surface
-\cite{rayintersection}.
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_cache_shift.jpg}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_shortest_shift.pdf}}
 
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image for texturing
-$t$. Since resolution decreases and camera pose errors become more
-pronounced with distance, we wish to minimize the distance between
-cameras and the surfaces they texture. Additionally, we desire images
-that are projected perpendicularly, rather than obliquely, onto the
-plane, maximizing the resolution and amount of useful texture
-available in their projections, as well as minimizing any parallax
-effects due to real-world geometry not accurately represented by the
-digital 3D model. In other words, we wish to minimize the angle
-between the tile's normal vector and the camera axis for images
-selected for texturing that tile. These two criteria can be met by
-maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
-as shown in Figure \ref{fig:scoringFunction}, where $d$ is the
-distance between the centers of a camera and a tile, and $\vec{n}$ and
-$\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively. As Figure \ref{fig:compareAll}(a) demonstrates, this
-approach, when used directly for texturing, results in image
-boundaries with abrupt discontinuities between tiles, due to
-misalignment between images, though most of it appears to be
-reconcilable using 2D transforms.
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_shortest_shift_blend.pdf}}
 
-While this procedure can be used to generate a texture, it is also
-useful for obtaining a collection of images that can be used as a
-starting point for our proposed texturing procedure, as explained in
-Section \ref{sec:2dAlignment}. For our datasets, this process
-generally selects around 10\% of all the images that could be used for
-texturing the surface. This roughly 10:1 subsampling not only reduces
-computational complexity of the remaining steps, but also selects the
-most promising images for the remaining steps.
-
-Given the large number of input images, it is possible to develop a
-more sophisticated image selection procedure, as described in Section
-\ref{sec:imageCompositing}, however, a more significant and reliable
-improvement can be found through first improving the alignment of the
-images as shown in the next section.
-
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive_shift.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_cache_comparison.png}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_shortest_comparison.png}}
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=2.2in]{wall2_cache_comparison.png}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=2.2in]{wall2_shortest_comparison.png}}
 
@@
 \label{sec:2dAlignment}
-In this section, we describe our method for efficient and robust image
-alignment. Rather than register all of our images in 3D, as many
-state-of-the-art techniques for image stitching do, we instead select
-a subset of images to be aligned in 2D. This subset corresponds to the
-images selected by the image selection procedure described in Section
-\ref{sec:simpleTextureMapping}.
+% In this section, we describe our method for efficient and robust image
+% alignment. Rather than register all of our images in 3D, as many
+% state-of-the-art techniques for image stitching do, we instead select
+% a subset of images to be aligned in 2D. This subset corresponds to the
+% images selected by the image selection procedure described in Section
+% \ref{sec:simpleTextureMapping}.
 
-Applying 2D alignments to this set of images works well for a number
-of reasons. First, the nature of our input data and the selected
-images is such that localization error chiefly occurs in two
-dimensions, which correspond to the plane of the surface being
-projected onto. This is because the backpack operator, during data
-acquisition, makes efforts to walk within a few meters of, and
-parallel to all walls being scanned. As a result, the translational
-error of camera poses is quite minimal in the dimension perpendicular
-to the wall surface being textured. Furthermore, because our set of
-images has minimal distance from its corresponding wall surface,
-rotational errors are less pronounced, except for rotation around the
-axis perpendicular to the surface being textured. Therefore, most
-translation and rotational errors occur in the 2 dimensions of the
-wall surface's plane. This of course does not apply for ceilings and
-floors; however, the lack of features on most ceilings and floors
-means that 3D misalignment is not likely to visually make a
-difference, beyond what can be done in 2D.
+% Applying 2D alignments to this set of images works well for a number
+% of reasons. First, the nature of our input data and the selected
+% images is such that localization error chiefly occurs in two
+% dimensions, which correspond to the plane of the surface being
+% projected onto. This is because the backpack operator, during data
+% acquisition, makes efforts to walk within a few meters of, and
+% parallel to all walls being scanned. As a result, the translational
+% error of camera poses is quite minimal in the dimension perpendicular
+% to the wall surface being textured. Furthermore, because our set of
+% images has minimal distance from its corresponding wall surface,
+% rotational errors are less pronounced, except for rotation around the
+% axis perpendicular to the surface being textured. Therefore, most
+% translation and rotational errors occur in the 2 dimensions of the
+% wall surface's plane. This of course does not apply for ceilings and
+% floors; however, the lack of features on most ceilings and floors
+% means that 3D misalignment is not likely to visually make a
+% difference, beyond what can be done in 2D.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
-
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 2cm 0cm 0cm,
-    clip=true, width=5in]{matchLines.jpg}}
-
+  \begin{tabular}{cc}
+    \subfloat[][]{\raisebox{-0.8in}{\includegraphics[trim=0cm 2cm 0cm 0cm,
+        clip=true, width=2.4in]{matchLines.jpg}}} &
+    \begin{tabular}{c}
+      \subfloat[][]{\includegraphics[width=2.4in]{allunshifted.jpg}} \\
+      \subfloat[][]{\includegraphics[width=2.4in]{allshifted.jpg}}
+    \end{tabular}
+  \end{tabular}
   \caption{Images projected onto a ceiling surface, where
@@
     shown in red. Image-based lines detected by Hough transform in the
-    image projections are shown in blue; (a) images projected with
-    their original noisy camera poses; (b) after image alignment to
-    maximize line matches between images and geometry; (c) examples of
-    matching lines in cases with $\geq$ 2 line pairs, 1 line pair, and
-    zero line pairs, from top to bottom.}
+    image projections are shown in blue; (a) examples of matching
+    lines in cases with $\geq$ 2 line pairs, 1 line pair, and zero
+    line pairs, from top to bottom; (b) images projected with their
+    original noisy camera poses; (c) after image alignment to maximize
+    line matches between images and geometry; }
   \label{fig:geometryAlignment}
@@
 
-After computing each image's projection onto the target surface, as
-described in Section \ref{sec:simpleTextureMapping}, we obtain a set
-of image-based line segments by using Hough transforms to detect lines
-in the image projections. We then gather a set of geometry-based
-lines, which correspond to the lines comprising the target surface's
-border, as well as lines formed where other surfaces intersect the
-target surface. An example of these lines is shown in red for a
-ceiling surface in Figure \ref{fig:geometryAlignment}(a). Ideally, for
-perfect camera poses and surface geometry, the lines in images
-corresponding to corners between surfaces should match up exactly with
-corners in the 3D model. By inducing such lines to match, we fit
-camera poses more accurately to the surface, and to each other as
-well.
+To align images to geometry, line segments are detected in images via
+Hough transforms. We also gather a set of geometry-based lines, which
+correspond to lines comprising the target surface's border, as well as
+lines formed where other surfaces intersect the target surface. An
+example of these lines is shown in red for a ceiling surface in Figure
+\ref{fig:geometryAlignment}(a). Ideally, for perfect camera poses and
+surface geometry, the lines in images corresponding to corners between
+surfaces should match up exactly with corners in the 3D model. By
+inducing such lines to match, we fit camera poses more accurately to
+the surface, and therefore to each other as well.
 
-To align images to surface geometry, we collect pairs of image-based
-and geometry-based line segments, which are within a distance and
-angular difference threshold of each other. We have found a distance
-threshold of 250 mm and an orientation difference threshold of
-$10^\circ$ to work well for our datasets. For each pair of lines, we
-compute the angular difference between the pair's image and geometry
-lines. If there are 2 or more pairs with angular differences within
-$1^\circ$, we select the two pairs with the longest noncollinear
-image-based lines, and rotate the image such that the lines in the
-pair with the longest image-based line become parallel. We then find a
-translation such that the lines in that same pair overlap. This
-translation has ambiguity in the dimension along the matched lines,
-which is resolved by matching the midpoint of the image-based line in
-the second pair to its corresponding geometry-based line. This
-corresponds to case (1) of Figure
-\ref{fig:geometryAlignment}(c). Thus, with 2 or more pairs, it is
-possible to obtain a fixed rotation and translation, which are saved
-for usage in Section \ref{sec:robustSIFTFeatureMatching}.
+First, pairs of image-based and geometry-based line segments within a
+distance and angular difference threshold of each other are
+collected. We have found a distance threshold of 250 mm and an
+orientation difference threshold of $10^\circ$ to work well for our
+datasets. Each such pair signifies a rotation and translation with one
+degree of freedom that matches an image line to a geometry line. Pairs
+are then binned by rotation in $1^\circ$ increments, which reveals the
+rotation that maximizes line matches. From the pairs with that
+corresponding rotation, the two longest noncollinear image-based lines
+are used to compute a fixed translation. An example of this is case
+(1) of Figure \ref{fig:geometryAlignment}(c). If a rotation is
+calculated, but a fixed translation cannot be obtained, the pair with
+the longest image-based line is selected, and the rotation and the
+minimal translation to match its lines are applied. This corresponds
+to case (2) of Figure \ref{fig:geometryAlignment}(c). Finally, if no
+line pairs were detected, images are rotated using a RANSAC
+\cite{fischler1981random} approach to maximize parallel image and
+geometry lines, without regard for translational distance. This
+corresponds to case (3) of Figure \ref{geometryAlignment}(c). The
+results of this procedure are recorded, as the translational degrees
+of freedom for each image are used in Section
+\ref{sec:robustSIFTFeatureMatching}.
 
-If there are not 2 or more pairs with similar angular differences, we
-select the pair with the longest image-based line and apply a rotation
-and the minimal translation to match its lines. This translation's
-ambiguity however, can not be resolved, but is also saved to be used
-in Section \ref{sec:robustSIFTFeatureMatching}. This corresponds to
-case (2) of Figure \ref{fig:geometryAlignment}(c). Finally, in the
-case where there are no line pairs, we can still rotate images in
-order to exploit patterns in indoor environments (case (3) of Figure
-\ref{fig:geometryAlignment}(c)). For instance, doors, windows,
-furniture, etc. tend to have linear edges that are parallel to the
-edges of the surfaces they are on. Similarly, lights, visible interior
-walls, etc. which are visible in floor and ceiling images, tend to be
-parallel to exterior walls corresponding to the edges of ceiling and
-floor surfaces. Thus, we choose to minimize the angle between
-image-based lines and geometry-based lines. We use the RANSAC
-framework, with an inlier difference of $0.5^\circ$ in order to
-successfully ignore outliers \cite{fischler1981random}.
-
-After these steps, image projections line up well with target
-surfaces, as shown in Figure \ref{fig:geometryAlignment}(b), which is
-considerably more aligned than Figure \ref{fig:geometryAlignment}(a)
-is. This procedure reconciles both errors in camera poses as well as
-in geometry, and results in sharp, continuous borders across images,
-which is crucial when checking for occlusion.
+After this step, image projections line up well with target surfaces,
+as shown in Figure \ref{fig:geometryAlignment}(b), which is
+considerably more aligned than Figure
+\ref{fig:geometryAlignment}(a). This procedure reconciles both errors
+in camera poses as well as in geometry, and results in sharp,
+continuous borders across images, which is crucial when checking for
+occlusion.
 
@@
   \begin{tabular}{cc}
-    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{occlusiondiagram.png}}} &
+    \subfloat[][]{\raisebox{-0.8in}{\includegraphics[width=2.4in]{occlusiondiagram.png}}} &
 
@@
       \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
-    clip=true, width=3in,
-      height=0.9in]{occlusionimagebad.png}} \\
+        clip=true, width=2.4in,
+        height=0.6in]{occlusionimagebad.png}} \\
       \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
-    clip=true, width=3in,
-      height=0.9in]{occlusionimagegood.png}}
+        clip=true, width=2.4in,
+        height=0.6in]{occlusionimagegood.png}}
     \end{tabular}
@@
 occluding surface. We remove this incorrect texture by recursively
-performing ray-polygon intersection tests between the camera location
-and other surfaces \cite{rayintersection}. These intersection tests
-are performed at the corners of a grid overlaid upon the target
-surface. Where all four corners of a grid section are occluded,
-texture is removed. Where one or more corners are occluded, the grid
-is subdivided into four, and the process repeats. Occlusion checking
-works entirely with geometry, so by ensuring that images match
-geometry using \ref{sec:geometryAlignment}'s alignment procedure,
-texture belonging to other surfaces is accurately removed, as seen in
-Figure \ref{fig:occlusion}(b).
+performing ray-polygon intersection tests between the ray from the
+camera location to locations on the target surface
+\cite{rayintersection}. These intersection tests are performed at the
+corners of a grid overlaid upon the target surface. Where all four
+corners of a grid section are occluded, texture is removed. Where one
+or more corners are occluded, the grid is subdivided into four, and
+the process repeats. Occlusion checking works entirely with geometry,
+so by ensuring that images match geometry using
+\ref{sec:geometryAlignment}'s alignment procedure, texture belonging
+to other surfaces is accurately removed, as seen in Figure
+\ref{fig:occlusion}(b).
 
@@
 \label{sec:robustSIFTFeatureMatching}
-The next step is to align the selected images from Section
-\ref{sec:simpleTextureMapping} for each surface to each other by
-searching for corresponding feature points between all pairs of
-overlapping images. We use feature alignment rather than pixel or
-intensity-based alignment due to the differences in lighting as well
-as possible occlusion among images, both of which feature alignment is
-less sensitive to \cite{lowe1999object, mikolajczyk2005performance,
+The next step is to align images to each other by detecting feature
+point matches between all pairs of overlapping images. We use feature
+alignment rather than pixel or intensity-based alignment due to the
+differences in lighting as well as possible occlusion among images,
+both of which feature alignment is less sensitive to
+\cite{lowe1999object, mikolajczyk2005performance,
   szeliski2006image}. We use SiftGPU \cite{siftgpu} for its high
 performance on both feature detection as well as pairwise
-matching. These matches determine $dx$ and $dy$ distances between each
-pair of features for two image projections, though these distances may
-not always be the same for different features. Since indoor
+matching. Detected matches determine $dx$ and $dy$ distances between
+each pair of features for two image projections, though distances
+often are not the same for different features. Since indoor
 environments often contain repetitive features such as floor tiles or
 doors, we need to ensure that SIFT-based distances are
-reliable. First, we only align parts of images that overlap given the
-original noisy poses. Second, we discard feature matches that
-correspond to an image distance greater than 200 mm from what the
-noisy poses estimate. In order to utilize the remaining feature
-matches robustly, RANSAC \cite{fischler1981random} is again used to
+reliable. First, we only detect feature matches in the parts of images
+that overlap given the original noisy poses. Second, feature matches
+that correspond to an image distance greater than 200 mm from what the
+noisy poses estimate are discarded. In order to utilize the remaining
+feature matches robustly, RANSAC \cite{fischler1981random} is used to
 estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
-images $i$ and $j$. We use a 5 mm threshold for RANSAC, so that SIFT
-matches are labeled as outliers if their distance is not within 5 mm
-of the sampled average distance.
+images $i$ and $j$.
 
-We now use the feature-based distances between each pair of images as
-well as geometry alignment results from Section
-\ref{sec:geometryAlignment} to refine all image positions using a
-weighted linear least squares approach. An example setup for a
-weighted linear least squares problem $\textrm{min}_{\vec{\beta}}
-||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
-as follows.
+We now use the feature-based distances between pairs of images as well
+as geometry alignment results from Section \ref{sec:geometryAlignment}
+to refine all image positions using a weighted linear least squares
+approach. An example setup for a weighted linear least squares problem
+$\textrm{min}_{\vec{\beta}} ||W^\frac{1}{2}(A \vec{\beta} -
+\vec{\gamma})||_2^2 $ with 3 images is as follows.
 
@@
 
-The variables we wish to solve for are the $x_i$ and $y_i$ positions
-of images, while equations are the feature-based distances between
-pairs of images, images fixed to geometry with 0 or 1 degrees of
-freedom, and the original noisy camera poses. In this scenario, a
-feature-based distance of $dx_{1,2}$, $dy_{1,2}$ was calculated
-between images 1 and 2. This corresponds to the first and second row
-of $A$, while the third and fourth row of $A$ represent the same for
-images 2 and 3. Rows 5 through 7 correspond to results of the geometry
-alignment procedure in Section
-\ref{sec:geometryAlignment}. Specifically, row 5 corresponds to a
-geometry-based constraint of image 2's location to a line of slope
-$m_2$, passing through point $gx_2$, $gy_2$, while rows 6 and 7
-correspond to a fixed location for image 1 without any degrees of
-freedom. Rows 8 through 13 correspond to the original camera locations
-for each image ($tx_i,ty_i$).
+The variables to solve for are the $x_i$ and $y_i$ positions of
+images, while equations are the feature-based distances between pairs
+of images, images fixed to geometry with 0 or 1 degrees of freedom,
+and the original noisy camera poses. In this scenario, a feature-based
+distance of $dx_{1,2}$, $dy_{1,2}$ was calculated between images 1 and
+2. This corresponds to the first and second row of $A$, while the
+third and fourth row of $A$ represent the same for images 2 and
+3. Rows 5 through 7 correspond to results of the geometry alignment
+procedure in Section \ref{sec:geometryAlignment}. Specifically, row 5
+corresponds to a geometry-based constraint of image 2's location to a
+line of slope $m_2$, passing through point $gx_2$, $gy_2$, while rows
+6 and 7 correspond to a fixed location for image 1 without any degrees
+of freedom. Rows 8 through 13 correspond to the original camera
+locations for each image ($tx_i,ty_i$).
 
@@
 
-Since this problem is linear, it can be solved efficiently; after
-applying the resulting shifts, images overlap and match each other
-with far greater accuracy. Using the simple tile-based texturing
-scheme from Section \ref{sec:simpleTextureMapping} on these adjusted
-images results in Figure \ref{fig:compareAll}(b), which has far fewer
-discontinuities than in \ref{fig:compareAll}(a), though some 3D error
-as well as lighting differences and parallax effects are still
+This problem is linear, and it is solved quickly. After applying the
+resulting shifts, images overlap and match each other with far greater
+accuracy. Using the simple tile texturing scheme from Section
+\ref{sec:simpleTextureMapping} on these adjusted images results in
+Figure \ref{fig:compareAll}(b), which has far fewer discontinuities
+than in \ref{fig:compareAll}(a), though some discontinuities remain
 visible.
@@
 \label{sec:imageCompositing}
-In Section \ref{sec:mappingWithCaching}, we refine the tile-based
-texturing approach from Section \ref{sec:simpleTextureMapping}, with
-an added caching mechanism to reduce image boundaries. This method is
-general and works well given arbitrary camera poses and surfaces such
-as walls, floors, and ceilings. For special cases where images have
-consistently perpendicular viewing angles to the surfaces under
-consideration, such as walls, it is possible to develop an alternative
-method in Section \ref{sec:shortestPath} to further reduce visual
-artifacts. Both of these approaches are followed by a blending step in
-order to produce final textures for each surface, as shown in Figure
+In Section \ref{sec:simpleTextureMapping}, a simple tile-based image
+selection and texturing method was described. After performing image
+alignment, the image in Figure \ref{fig:compareAll}(b) was
+obtained. It is clear that discontinuities in the image occur at tile
+boundaries, and Section \ref{sec:mappingWithCaching} adds a caching
+mechanism to reduce such boundaries. On the other hand, for special
+cases where images have consistently perpendicular viewing
+angles, Section \ref{sec:shortestPath} develops another image
+compositing method that tends to produce cleaner textures. Both
+methods are followed by a blending step, as shown in Figure
 \ref{fig:flowchart}.
@@
 \label{sec:mappingWithCaching}
-For the simple texture mapping method described in Section
-\ref{sec:simpleTextureMapping}, discontinuities occur where adjacent
-tiles are textured by different images. Though Section
-\ref{sec:2dAlignment}'s image alignment removes many such
-discontinuities, there are still cases where seams are visible due to
-imprecise matching or other factors such as model-based errors as
-shown in Figure \ref{fig:compareAll}(b). To reduce this, it is
-desirable to develop a spatiotemporal caching mechanism to take into
-account image selections made by neighboring tiles while texture
-mapping a given tile. By using the same image across tile boundaries,
-it is possible to eliminate a discontinuity altogether. If a tile is
-not visible in images used by neighboring tiles, using similar images
-across tile boundaries also leads to less noticeable discontinuities.
+To reduce discontinuities between tiles, this method reuses images for
+adjacent tiles where possible, and otherwise selects images with
+similar poses. This is accomplished via the use of a spatiotemporal
+cache for selected images.
 
@@
 \ref{sec:simpleTextureMapping}. The first subset of images is those
-selected by adjacent tiles that have already been textured. We must
-first check which of these images contain texture for $t$, and then of
-those, we make a choice according to the scoring function in Figure
+selected by adjacent tiles that have already been textured, and that
+also contain texture for $t$. Of these images, one is selected
+according to the scoring function in Figure
 \ref{fig:scoringFunction}. Before reusing this image, we check the
@@
 
-If no satisfactory image is found in the first subset, we check a
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. We use the noisy
-camera poses to determine priority. These images are not the same as
-the ones used for neighboring tiles, but are taken at a similar
-location and time, suggesting that their localization and projection
-are quite similar, and thus likely match more seamlessly. If no viable
-image is found according to the $\alpha < 45^\circ$ criteria, we
-search the entire set of candidate images from Section
-\ref{sec:simpleTextureMapping}, selecting based on the same scoring
-function from Figure \ref{fig:scoringFunction}.
+If no satisfactory image is found in the first subset, a second subset
+of images is used, consisting of those taken near the ones in the
+first subset, both spatially and temporally. These images have quite
+similar localization and projection, and are likely to match
+well. If no viable image is found according to the $\alpha < 45^\circ$
+criteria, we use the image selected from Section
+\ref{sec:simpleTextureMapping}.
 
@@
   \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \hspace{1in} \centering
+  \hspace{0.4in} \centering
   \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering \hspace{1in}
+  \centering \hspace{0.4in}
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
@@
 wall-texture candidate images are taken from more or less head-on
-angles, and knowing that only minor rotations are made in Section
+angles, and knowing that generally minor rotations are made in Section
 \ref{sec:2dAlignment}, we can crop our image projections to be
-rectangular with minimal texture loss as shown in Figure
+rectangular with minimal texture loss, as shown in Figure
 \ref{fig:projectionAngles}(c). Furthermore, because the fisheye camera
 lenses have full floor-to-ceiling coverage of nearly all walls, and
-the backpack operator logically only moves horizontally, we only need
-to ensure lateral coverage of our wall planes. We can thus construct a
-Directed Acyclic Graph (DAG) from the images, with edge costs defined
-by the SSD cost function, and solve a simple shortest path problem to
-find an optimal subset of images with regard to the SSD cost function
-\cite{dijkstra}.
+the backpack operator nearly always only moves horizontally, we only
+need to ensure lateral coverage of our wall planes. We can thus
+construct a Directed Acyclic Graph (DAG) from the images, with edge
+costs defined by the SSD cost function, and solve a simple shortest
+path problem to find an optimal subset of images with regard to the
+SSD cost function \cite{dijkstra}.
 
@@
   \centering
-  \includegraphics[width=5in]{dagCreation.pdf}
+  \includegraphics[width=4.8in]{dagCreation.pdf}
   \caption{DAG construction for the image selection process. \\}
@@
 Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a hallway wall. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
+from overlapping images of a hallway wall. Images are nodes in a
+graph, and directed edges are placed in the graph from left to right
 between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal and arbitrary cost $C_0$ to(from)
-all images that meet the left(right) border of the plane. We now solve
-the shortest path problem from the start node to the end node. This
-results in a set of images completely covering the plane horizontally,
-while minimizing the cost of seams between images.
+by the SSD cost function. Next, two artificial nodes representing the
+ends of the plane are added, with equal-cost $C_0$ edges to the images
+crossing them. We now solve the shortest path problem from one end to
+the other. This results in a set of images completely covering the
+plane horizontally, while minimizing the cost of seams between images.
 
-In rare cases where the vertical dimension of the plane is not
-entirely covered by one or more chosen images, we are left with holes
-where no images are selected to texture. Since these holes are rare,
-and generally fairly small, we use a greedy approach, repeatedly
-filling the hole with images that result in the lowest SSD costs in a
-blending region around the hole, as discussed in Section
-\ref{sec:blending}. This method is not optimal as a true 2D-coverage
-solution would be, but it is a fast approximation, and adequately
-handles the few holes encountered.
-
-We have now mapped every location on the plane to at least one image,
-and have decreased the number of images, generally retaining around
-20\% of the image subset obtained in Section
-\ref{sec:simpleTextureMapping}, as well as the discontinuities at each
-image border. As seen in Figure \ref{fig:compareAll}(d), this shortest
-path method has fewer visible discontinuities than Figure
-\ref{fig:compareAll}(c) corresponding to the tile caching
-approach\footnote{In Figure \ref{fig:compareAll}(d), we arbitrarily
-  chose one image for texturing where images overlap, as blending will
-  be discussed in section \ref{sec:blending}.}. This is especially
-evident when comparing the posters in the images. This shortest path
-approach approach directly reduces the cost of each image boundary,
-while the tile caching method uses a scoring function that only
-approximates this effect. Furthermore, this approach guarantees the
-best selection of images to minimize seams, while the sequential tile
-caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. This shortest path
-approach is also far less intensive in terms of memory usage and
-runtime, both during texture generation and rendering, as it does not
-require discretizing planes or images.
+As seen in Figure \ref{fig:compareAll}(d), this shortest path method
+has fewer visible discontinuities than Figure \ref{fig:compareAll}(c)
+corresponding to the tile caching approach\footnote{In Figure
+  \ref{fig:compareAll}(d), we arbitrarily chose one image for
+  texturing where images overlap, as blending will be discussed in
+  section \ref{sec:blending}.}. This is especially evident when
+comparing the posters in the images. This shortest path approach
+directly reduces the cost of each image boundary, while the tile
+caching method uses a scoring function that only approximates this
+effect. Furthermore, this approach guarantees the best selection of
+images to minimize seams, while the sequential tile caching method may
+select images early on that turn out to be poor choices once
+subsequent tiles have been processed.
 
@@
 method on walls, due to its superior results when provided with
-head-on images. Floors and ceilings however, given their many images
-taken at oblique angles, are textured using the tile caching method of
-Section \ref{sec:mappingWithCaching}.
+head-on images with lateral coverage. Floors and ceilings however,
+given their many images taken at oblique angles, are textured using
+the tile caching method of Section \ref{sec:mappingWithCaching}.
 
@@
 lighting conditions or inaccuracies in model geometry. These can
-however be treated and smoothed over by applying alpha blending over
-image seams.  Whether the units to be blended are
-rectangularly-cropped images or rectangular tiles, we can apply the
-same blending procedure, as long as there is a guaranteed overlap
-between units to blend over.
+however be treated and smoothed over by blending over image seams.
+Whether the units to be blended are rectangularly-cropped images or
+rectangular tiles, we can apply the same blending procedure, as long
+as there is a guaranteed overlap between images.
 
 For the tile caching method of Section \ref{sec:mappingWithCaching},
-we can ensure overlap by texturing a larger tile than needed for
+overlap can be ensured by texturing a larger tile than needed for
 display. For example, for a rendered tile $l_1 \times l_1$, we can
 associate it with a texture $(l_1 + l_2) \times (l_1 + l_2)$ in size.
-We have found $l_2 = \frac{l_1}{2}$ to provide a balance between
-blending and keeping features unblurred. For the shortest path method,
-we have already ensured overlap between images. To enforce consistent
-blending however, we add a minimum required overlap of images of 200
-mm while solving the shortest path problem in Section
-\ref{sec:shortestPath}. Additionally, if images overlap in a region
-greater than the overlap distance, we only apply blending over an area
-equal to the overlap distance.
+For the shortest path method, overlap between images is inherently
+ensured. To enforce consistent blending however, a minimum required
+overlap between images of 200 mm for the graph is added.
 
@@
 between the two methods, showing that Figure \ref{fig:compareAll}(f)
-has the best visual quality and the best texturing approach among the
-textures in Figure \ref{fig:compareAll}.
+has the cleanest texture and contains the best visual quality among
+the textures in Figure \ref{fig:compareAll}.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
+  \subfloat[][]{\includegraphics[width=2.4in]{finalfloors.jpg}} ~~~~~~~~
   \centering
-  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
+  \subfloat[][]{\includegraphics[width=2.4in]{finalceilings.jpg}}
 
   \centering \subfloat[][]{
-    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
-    \includegraphics[width=3in]{pier15floor.jpg}
+    \includegraphics[height=2in, width=2.3in]{floorcropped.jpg} ~~~~~~~~
+    \includegraphics[width=2.3in]{pier15floor.jpg}
   }
@@
   \centering{
-    \includegraphics[width=3in]{fullmodel.png}
-    \includegraphics[width=3in]{pier15.png} \\
-    \includegraphics[width=3in]{threestoryfull2.png}
-    \includegraphics[width=3in]{threestoryfull.png}
+    \includegraphics[width=2.3in]{fullmodel.png}
+    \includegraphics[width=2.3in]{pier15.png} \\
+    \includegraphics[width=2.3in]{threestoryfull2.png}
+    \includegraphics[width=2.3in]{threestoryfull.png}
   }

### 2013-12-29 acivs/fullacivs.tex
cleanup

--- 2013-03-03 spie/paper.tex
@@
   \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 20cm 0cm,
-    clip=true, width=6in, height=0.7in]{graphApproach.jpg}}
+    clip=true, width=4.8in, height=0.7in]{graphApproach.jpg}}
 
   \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 15cm 0cm,
-    clip=true, width=6in, height=0.7in]{autostitchResult.jpg}}
+    clip=true, width=4.8in, height=0.7in]{autostitchResult.jpg}}
 
   \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 75cm 0cm,
-    clip=true, width=6in, height=0.7in]{finalLong.jpg}}
+    clip=true, width=4.8in, height=0.7in]{finalLong.jpg}}
 
@@
 not closed-form, and its iterative camera adjustment process over
-large datasets led to prohibitively long computation time.
+large datasets leads to prohibitively long computation time.
 
@@
 
-Given the large number of input images, it is possible to develop a
-more sophisticated image selection procedure, as described in Section
-\ref{sec:imageCompositing}, however, a more significant and reliable
-improvement can be found through first improving the alignment of the
-images as shown in the next section.
+\begin{figure}
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_naive.jpg}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_naive_shift.jpg}}
 
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive_shift.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_cache_shift.jpg}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_shortest_shift.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=0.8in]{wall2_shortest_shift_blend.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_cache_comparison.png}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_shortest_comparison.png}}
+  \centering \subfloat[][]{\includegraphics[width=2.4in,
+    height=2.2in]{wall2_cache_comparison.png}}
+  \subfloat[][]{\includegraphics[width=2.4in,
+    height=2.2in]{wall2_shortest_comparison.png}}
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
+  \subfloat[][]{\includegraphics[width=4.8in]{allunshifted.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
+  \subfloat[][]{\includegraphics[width=4.8in]{allshifted.jpg}}
 
   \centering \subfloat[][]{\includegraphics[trim=0cm 2cm 0cm 0cm,
-    clip=true, width=5in]{matchLines.jpg}}
+    clip=true, width=4.8in]{matchLines.jpg}}
 
@@
     \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
-    clip=true, width=3in,
+      clip=true, width=2.4in,
       height=0.9in]{occlusionimagebad.png}} \\
     \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
-    clip=true, width=3in,
+      clip=true, width=2.4in,
       height=0.9in]{occlusionimagegood.png}}

### 2013-12-29 masters/body/_region_.tex
cleanup

--- 2013-05-02 masters/body/_region_.tex
@@
 
-\message{ !name(masters.tex) !offset(135) }
-\subsection{Geometry Partitioning}
-\label{sec:geometryPartioning}
-In order to effectively texture a 3D model, we first divide the model
-into a set of regions, each to be textured independently. The purpose
-of this is to ensure texture continuity along large uniform areas,
-while allowing texture boundaries to fall along natural environmental
-boundaries. Because textures may not match at such boundaries where
-two regions meet, it is important to minimize the visibility of
-boundaries. This is done by encouraging region boundaries to occur at
-large sharp corners, where texture continuity is less important.
+\message{ !name(masters.tex) !offset(1175) }
+\subsection{Runtime}
+As mentioned earlier, our approach is quite efficient. The top wall in
+Figure \ref{fig:indivPlanes}(a) was generated with 7543 $\times$ 776
+pixels, and spans a 40-meter long wall. Given 41000 input images in
+the entire dataset, a 2.8 GHz dual-core consumer-grade laptop takes
+under a second to choose 36 candidate images, followed by a minute to
+perform image projections, image alignment, and the shortest path
+texturing method. The tile-caching approach takes roughly comparable
+time, and over 75\% of the time for either method is spent on
+calculating image projections, which are cached over multiple runs,
+and also could be performed as a preprocessing step instead. While not
+real-time, the process is capable of generating fast updates after
+changes in various parameters or modifications to input data, and if
+integrated directly into a 3D modeling system, could provide quick
+visual feedback as data is collected.
 
-When working with low-resolution models, where surfaces generally
-correspond to large planar features such as walls, ceilings, or
-floors, and often meet at right angles, each planar surface in the
-model is directly treated as a distinct region and textured
-separately.
-
-When working with a high-resolution model however, geometry often
-represents large features as well as small details found in furniture,
-plants, and other miscellaneous objects. For instance, in Figure
-\ref{fig:deskGeom}, the geometry modeling the desk and binders
-consists of many small triangles at various orientations. Texturing
-each of these triangles independently makes little sense, as the
-textures applied to each should match up well with the textures of its
-neighbors in order to avoid any breaks in the overall image of the
-desk and binders. On the other hand, the textures for the triangles
-belonging to the wall behind need not match up with the textures on
-the desk and binders, and so each group of triangles should be
-designated to separate regions.
-This region grouping is performed by designating all contiguous coplanar groups of triangles as different regions.
-Any region that is less than $1 m^2$ in size is joined to its largest neighboring region, such that the angle between them is under $90^{\circ}$.
-
-Because a texture is 2D, and the region to be textured may not be
-flat, a mapping needs to be defined. We first fit a plane to each
-region for the purposes of texturing. This can be accomplished via a
-least squares plane-fitting through each triangle vertex, though in
-practice we simply use the plane equation of the largest contiguous
-section of coplanar triangles, as most regions are characterized by
-small outcroppings from a largely planar surface, such as objects on a
-table or features protruding from a wall. The 3d vertices within a
-region are then projected onto its calculated plane, and the
-rectangular bounding box for these projected vertices is
-calculated. This bounding box corresponds to the 2D image that will be
-created to texture the region.
-
-Of course, the area encompassed by the bounding box is larger than the
-corresponding 2d area of the projected geometry, which itself is not
-as accurate as the original 3d geometry. Thus, we also create a k-d
-tree consisting of the triangle primitives from the original
-mesh. Though we generate texture for the 2d bounding box surface, we
-will reference the original 3D geometry to ensure accuracy when
-texturing.
-
-\message{ !name(masters.tex) !offset(944) }
+\message{ !name(masters.tex) !offset(1325) }
 

### 2013-12-30 spie2014/spie2014.tex
thesis->paper

--- 2013-11-28 masters/body/masters.tex
@@
 
-\author{Peter Cheng
+\author{Peter Cheng\supit{a}, Michael Anderson\supit{a}, Stewart He\supit{b}, and Avideh Zakhor\supit{a}
 \skiplinehalf
-University of California, Berkeley\\
+\supit{a}University of California, Berkeley; \\
+\supit{b}University of California, Davis
 }
@@
 \cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results. In this thesis, we present an approach
+generally produce poor results. In this paper, we present an approach
 to texture mapping 3D models of indoor environments in the presence of
@@
 each box indicates the section in which the concept in the box is
-explained in this thesis. First, the geometry of an environment is
+explained in this paper. First, the geometry of an environment is
 split into regions, each of which will be textured independently and
@@
 
-The remainder of the thesis is organized as follows. Section
+The remainder of the paper is organized as follows. Section
 \ref{sec:dataAcquisition} provides background on the data acquisition
@@
 data, play an important role in motivating the approaches described in
-this thesis. The following two sections will focus on image and raw
+this paper. The following two sections will focus on image and raw
 data acquisition, and a method of partitioning recovered environment
@@
 \cite{chen2010indoor, kua2012loopclosure, liu2010indoor}, and the
-backpack is localized\footnote{In this thesis, we use the terms
+backpack is localized\footnote{In this paper, we use the terms
   localization and pose recovery interchangeably, in that they both
@@
 These results are noisy, which motivates the approaches in this
-thesis. Once this is complete, the data from the laser range scanners
+paper. Once this is complete, the data from the laser range scanners
 is used to generate a 3D point cloud of the surrounding
@@
 performed simulatenously across all images present in a single
-region. As before, this is solved as a least-squares optimization
-problem with pair-wise observations. In this case, observations do not
-need to be weighted, and so the formulation is
-$\textrm{min}_{\vec{\beta}} ||(A \vec{\beta} - \vec{\gamma})||_2^2
-$. An example setup for 3 images, each with 2 overlapping pixels, is
-shown below.
+region. To begin, a relative gain $R_{ij}$ is computed for each pair
+of overlapping images $I_i$ and $I_j$, which have a set of pixels
+common to both images, labeled as $P_{ij}$. The relative gain $R_{ij}$
+is then obtained by calculating the scaling factor between the average
+intensity of $P_{ij}$ in $I_i$ and the average intensity of $P_{ij}$
+in $I_j$.
+
+As before, these pair-wise observations can be combined and solved as
+a least-squares optimization problem. In this case, observations do
+not need to be weighted, and so the formulation is
+$\textrm{min}_{\vec{b}} ||(X \vec{b} - \vec{a})||_2^2 $. An example
+setup for 3 images, where each image overlaps with both of the other
+images, is shown below.
 \[
-A =
+X =
 \begin{pmatrix}
-  P_{11} & -P_{12} & 0\\
-  P_{21} & -P_{12} & 0\\
-  0 & P_{32} & -P_{33}\\
-  0 & P_{42} & -P_{43}\\
+  R_{12} & -1 & 0\\
+  R_{13} & 0 & -1\\
+  0 & R_{23} & -1\\
   1 & 1 & 1\\
@@
 \end{pmatrix}\quad
-\vec{\beta} =
+\vec{b} =
 \begin{pmatrix}
@@
 \end{pmatrix}
-\vec{\gamma} =
+\vec{a} =
 \begin{pmatrix}
-  0, \\ 0, \\ 0, \\ 0, \\ 3
+  0, \\ 0, \\ 0, \\ 3
 \end{pmatrix}
@@
 
-In this problem, $\beta$ is the vector of gains $G_i$ to be solved
-for.  The observations, represented by $A$ and $\gamma$, correspond to
-equalizing the brightness for each pixel present in two images. For
-instance, for pixel $P_x$ which is present in two overlapping images
-$I_i$ and $I_j$, the goal is to find gains $G_i$ and $G_j$ such that
-$G_iP_{xi} - G_jP_{xj} = 0$, where $P_{xy}$ is the value of pixel
-$P_x$ in image $I_y$. Thus, $\gamma$ contains all zeros, while each
-row of $A$ contains a $P_{xi}$ value in the $ith$ column and a
-$-P_{xj}$ value in the $jth$ column, and zeros elsewhere. This problem
-is not constrained, as it allows all computed gains to be scaled by
-any amount. To keep gains at reasonable values, a final observation is
-added: $\Sigma G_i = N$, where $N$ is the number of images. This has
-the effect of setting the average of all gains to 1, and is
-represented by adding a row of ones to $A$, and a corresponding $N$
-value to $\gamma$.
-
-The result of computing and applying gains for each image can be seen
-for the same ceiling location in Figure \ref{fig:exposureDiff}(b). As
-compared to Figure \ref{fig:exposureDiff}(a), the effect is clear, as
-dark/bright patches are no longer present, and the overall brightness
-of the image has not changed significantly.
+In this problem, $\vec{b}$ is the $N\times1$ vector of gains $G_i$ to
+be solved for, where $N$ is the number of images.  Matrix $X$ is an
+observation matrix corresponding to the relative intensities of
+overlapping images. In particular, the number of rows of $X$ is one
+plus the number of unique pairs of overlapping images, and the number
+of columns of $X$ is equal to $N$. Each row of $X$, except the last
+one, contains an $R_{ij}$ value which is placed in column $i$, as well
+as a $-1$ value in column $j$, with zeroes elsewhere. As explained
+above, $R_{ij}$ is the relative gain between images $i$ and $j$, and
+therefore $G_iR_{ij} - G_j = 0$.  Thus, all values of $\vec{a}$, which
+is a vector with size equal to the number of rows of $X$, are set to
+$0$, except for the last one.
+
+The last row of $X$ and corresponding last entry of $\vec{a}$ are used
+to constrain the problem, as without them, all computed gains would be
+allowed to scale by any amount. To keep gains at reasonable values,
+the final observation is used: $\Sigma G_i = N$, where $N$ is the
+number of images. This has the effect of setting the average of all
+gains to 1, and is represented by the final row of ones in $X$, and
+the corresponding $N$ value in $\vec{a}$.
+
+For the 81 source images that compose the ceiling location in Figure
+\ref{fig:exposureDiff}, the corresponding $X$ matrix has 1343 rows,
+and the optimization problem takes under a second to solve, on a 2.8
+GHz dual core machine.  The result of computing and applying gains can
+be seen in Figure \ref{fig:exposureDiff}(b). As compared to Figure
+\ref{fig:exposureDiff}(a), the effect is clear, as dark/bright patches
+are no longer present, and the overall brightness of the image has not
+changed significantly.
 
@@
 As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
-procedure in this thesis can be applied both to low-resolution and
+procedure in this paper can be applied both to low-resolution and
 high-resolution models. Low resolution models have an advantage in
@@
 pixels, and spans a 40-meter long wall. Given 41000 input images in
-the entire dataset, a 2.8GHz dual-core consumer-grade laptop takes
+the entire dataset, a 2.8 GHz dual-core consumer-grade laptop takes
 under a second to choose 36 candidate images, followed by a minute to
@@
 and a mapping of image points to 3D model vertices. The textured
-models shown throughout this thesis range from 20 MB in size to over
+models shown throughout this paper range from 20 MB in size to over
 400 MB in a compressed format, with textures of sizes over 500
@@
 
-In this thesis, we have developed an approach to texture mapping
+In this paper, we have developed an approach to texture mapping
 models of indoor environments with noisy camera localization data. We
@@
     \includegraphics[width=6.2in,height=3in]{houston2d1.png} \\
-    \includegraphics[width=6.2in,height=3in]{houston2d2.png} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
+    \includegraphics[width=6.2in,height=3in]{houston2d2_2.png} \\
+    \includegraphics[width=6.2in,height=3in]{houston3_2.png}
   }

### 2014-01-03 spie2014/spie2014.tex
almost down to 15

@@
   \centering
-  \includegraphics[width=6in]{flowchart.jpg}
+  \includegraphics[width=4in]{flowchart.jpg}
   \caption{The proposed texture mapping procedure\\}
@@
 geometry, as well as to each other, allowing us to handle both errors
-in geometry as well as camera poses. For surfaces and camera poses at
-arbitrary locations or orientations, generally horizontal surfaces, we
-propose a tile-based approach for sampling high-resolution portions of
-images and compositing them into a texture. In cases where cameras
-have consistently perpendicular viewing angles to the surfaces under
-consideration, generally vertical surfaces, we demonstrate a superior
-approach based on a shortest-path computation that leads to more
-seamless textures.
+in geometry as well as camera poses. Finally, we demonstrate a
+tile-based as well as a shortest-path-based approach for compositing
+images, where the latter produces superior textures, but is only
+applicable for surfaces with optimal camera poses and lateral image
+coverage.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{backpackCAD.png}
-  \caption{CAD model of the backpack system.}
-  \label{fig:backpack}
-\end{figure}
-
 This section contains background information describing the
@@
 
-A CAD model of the backpack-mounted system is shown in Figure
-\ref{fig:backpack}. This backpack system has a number of laser range
-scanners as well as 2 cameras facing left and right, each equipped
-with fisheye lenses reaching an approximately 180$^{\circ}$ field of
-view each and taking photos at a rate of 5 Hz \cite{liu2010indoor}. In
-order to collect data, an operator wears the backpack system and
-traverses the environment to be scanned, walking in straight lines at
-a standard pace and making an effort to walk parallel to all walls in
-the area. Multiple localization and loop-closure algorithms are then
-applied to the raw data collected by the onboard sensors
-\cite{chen2010indoor, kua2012loopclosure, liu2010indoor}, and the
-backpack is localized\footnote{In this paper, we use the terms
-  localization and pose recovery interchangeably, in that they both
-  refer to recovering position and orientation.}  over its data
-collection period. This involves recovering the 6 degrees of freedom
-for the backpack itself as well as the cameras rigidly mounted on it.
-These results are noisy, which motivates the approaches in this
-paper. Once this is complete, the data from the laser range scanners
-is used to generate a 3D point cloud of the surrounding
-environment. This point cloud is used to construct either a
-low-resolution planar model, such as for usage in basic navigation or
-energy analysis \cite{sanchez2012point, turnerfloorplan}, or a
-high-resolution, detailed mesh, for applications such as accurate
-remodeling or virtual walkthroughs \cite{turnerwatertight}.
-Regardless of resolution, size, or detail, the model, consisting of
-geometric surfaces in 3D space, along with the set of images captured
-by the backpack's cameras and their noisy 3D poses, are the input to
-the texture mapping problem.
+The backpack system used in this paper has a number of laser range
+scanners as well as side-facing cameras taking photos at a rate of 5
+Hz \cite{liu2010indoor}. In order to collect data, an operator wears
+the backpack system and traverses the environment to be scanned,
+walking in straight lines at a standard pace and making an effort to
+walk parallel to all walls in the area. Multiple localization and
+loop-closure algorithms are then applied to the raw data collected by
+the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
+  liu2010indoor}, and the backpack is localized\footnote{In this
+  paper, we use the terms localization and pose recovery
+  interchangeably, in that they both refer to recovering position and
+  orientation.}  over its data collection period. This involves
+recovering the 6 degrees of freedom for the backpack itself as well as
+the cameras rigidly mounted on it. These results are noisy, which
+motivates the approaches in this paper. Once this is complete, the
+data from the laser range scanners is used to generate a 3D point
+cloud of the surrounding environment. This point cloud is used to
+construct simple, coarse models \cite{sanchez2012point,
+  turnerfloorplan}, as well as highly detailed models
+\cite{turnerwatertight}.  Regardless of resolution, size, or detail,
+the model, consisting of geometric surfaces in 3D space, along with
+the set of images captured by the backpack's cameras and their noisy
+3D poses, are the input to the texture mapping problem.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=2.2in]{geomdeskwire_crop.png}}
-  \subfloat[][]{\includegraphics[width=2.2in]{geomdeskregions_crop.png}}
-  \subfloat[][]{\includegraphics[width=2.2in]{geomdesktexturetris_crop.png}}
+  \subfloat[][]{\includegraphics[width=1.5in]{geomdeskwire_crop.png}}
+  \hspace{0.5in}
+  \subfloat[][]{\includegraphics[width=1.5in]{geomdeskregions_crop.png}}
+  \hspace{0.5in}
+  \subfloat[][]{\includegraphics[width=1.5in]{geomdesktexturetris_crop.png}}
   \caption{(a) Part of a model representing a desk and miscellaneous
@@
 boundaries. This is done by encouraging region boundaries to occur at
-large sharp corners, where texture continuity is not important. When
-working with lower-resolution models, where surfaces generally
-correspond to large planar features such as walls, ceilings, or
-floors, and often meet at right angles, each planar surface in the
-model can simply be treated as a distinct region and textured
-separately.
-
-With high-resolution models however, geometry often represents large
-features as well as small details found in furniture, plants, and
-other miscellaneous objects. For instance, in Figure
-\ref{fig:deskGeom}(a), the geometry modeling each side of a desk as
-well as objects on top of it consists of many small triangles at
-various orientations. It is important that triangles belonging to the
-same object or surface are textured together, as texturing them
-independently might lead to visible misalignment between the textures
-of each triangle, resulting in poor visualizations. On the other hand,
-triangles belonging to different objects, such as the wall vs. objects
-on the desk need not be textured together, as texture alignment
-between the two is not important in terms of overall visual quality of
-the scene. Thus, in this example, the triangles comprising each side
-of the desk, objects on top of the desk, and the wall behind, should
-all be grouped into separate regions. This region grouping is done by
+sharp corners in the model geometry, where texture continuity is not
+important. For instance, in Figure \ref{fig:deskGeom}(a), each side of
+the desk, objects on top of the desk, and the wall behind, should be
+textured separately. This is done by grouping the triangles comprising
+each such area into separate regions. Region grouping is performed by
 first designating all contiguous coplanar groups of triangles as
 different regions. Any regions that are less than $1 m^2$ in size are
-then joined to their largest neighboring regions, as long as the angle
-between them is under $90^{\circ}$. An example of such a grouping is
-shown in Figure \ref{fig:deskGeom}(b). The same area with textures
-successfully applied to each region is shown in Figure
+then repeatedly joined to their largest neighboring regions, as long
+as the angle between them is under $90^{\circ}$. An example of such a
+grouping is shown in Figure \ref{fig:deskGeom}(b). The same area with
+textures successfully applied to each region is shown in Figure
 \ref{fig:deskGeom}(c).
@@
 of this section, we propose an image subsampling procedure to obtain a
-set of images for all further steps, and use it to derive a simple
-tile-based texture mapping procedure.
+set of images for use in all further steps.
 
@@
     \centering
-    \includegraphics[height=1.8in]{Projection.pdf}
+    \includegraphics[height=1.5in]{Projection.pdf}
     \caption{Images are related to each surface through the camera
@@
     \centering
-    \includegraphics[height=1.8in]{scoringFunction.jpg}
+    \includegraphics[height=1.5in]{scoringFunction.jpg}
     \caption{Camera angle $\alpha$ and distance $d$ are minimized by
@@
 
-Applying 2D alignments to this set of images works well for a number
-of reasons. First, the nature of our input data and the selected
-images is such that localization error chiefly occurs in two
+Applying 2D alignments to this set of images works well for the
+following reasons. First, the nature of our input data and the
+selected images is such that localization error chiefly occurs in two
 dimensions, which correspond to the plane of most surfaces being
-projected onto. This is because the backpack operator, during data
-acquisition, makes efforts to walk within a few meters of, and
-parallel to all walls being scanned. Furthermore, the backpack system
-maintains a fairly consistent distance from floors and ceilings during
-data collection. As a result, the translational error of camera poses
-is quite minimal in dimensions perpendicular to most surfaces being
-textured, corresponding to, or parallel to walls, ceilings and
-floors.
+projected onto. This is because the backpack operator, while scanning
+an environment, generally walks parallel to walls. Furthermore, the
+backpack system maintains a consistent distance from floors and
+ceilings during data collection. As a result, the translational error
+of camera poses is quite minimal in dimensions perpendicular to walls,
+ceilings and floors, which comprise the majority of surfaces being
+textured.
 
@@
 least squares problem is solved in order to maximize all image and
-geometry-based alignments. Each step will now be explained in detail.
+geometry-based alignments.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
-
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 2cm 0cm 0cm,
-    clip=true, width=5in]{matchLines.jpg}}
-
+  \begin{tabular}{cc}
+    \begin{tabular}{c}
+      \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
+        clip=true, width=3in,
+        height=0.9in]{allunshifted.jpg}} \\
+      \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
+        clip=true, width=3in,
+        height=0.9in]{allshifted.jpg}}
+    \end{tabular} &
+    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{matchLines.jpg}}} 
+  \end{tabular}
   \caption{Images projected onto a ceiling surface, where
@@
 image-based line segments by using Hough transforms to detect lines in
-the image projections. These lines are detected in the image
-projections rather than the original images, as the varying
-orientation and distances of camera poses relative to surfaces results
-in high variance of line lengths and strengths for real-world linear
-features across the original images. We also gather a set of
-geometry-based lines, which correspond to the lines comprising the
-target surface's border, as well as lines formed where other surfaces
-intersect the target surface. An example of these lines is shown in
-red for a ceiling surface in Figure
-\ref{fig:geometryAlignment}(a). Ideally, for perfect camera poses and
-surface geometry, the lines in images corresponding to corners between
-surfaces should match up exactly with corners in the 3D model. By
-inducing such lines to match, we fit camera poses more accurately to
-the surface, and to each other as well.
+the image projections. We also gather a set of geometry-based lines,
+which correspond to the lines comprising the target surface's border,
+as well as lines formed where other surfaces intersect the target
+surface. An example of these lines is shown in red for a ceiling
+surface in Figure \ref{fig:geometryAlignment}(a). Given perfect camera
+poses and surface geometry, the lines in images corresponding to
+corners between surfaces should match up exactly with corners in the
+3D model. By inducing such lines to match, we can fit camera poses
+more accurately to the surface, and therefore to each other as well.
 
 To align images to surface geometry, we collect pairs of image-based
-and geometry-based line segments, which are within a distance and
-angular difference threshold of each other. We have found a distance
-threshold of 250 mm and an orientation difference threshold of
-$10^\circ$ to work well for our datasets. For each pair of lines, we
-compute the angular difference between the pair's image and geometry
-lines. If there are 2 or more pairs with angular differences within
-$1^\circ$, we select the two pairs with the longest noncollinear
-image-based lines, and rotate the image such that the lines in the
-pair with the longest image-based line become parallel. We then find a
-translation such that the lines in that same pair overlap. This
-translation has ambiguity in the dimension along the matched lines,
-which is resolved by matching the midpoint of the image-based line in
-the second pair to its corresponding geometry-based line. This is
-shown in case (1) of Figure \ref{fig:geometryAlignment}(c). Thus, with
-2 or more pairs, it is possible to obtain a fixed rotation and
-translation for geometry alignment, which are saved for usage in
-Section \ref{sec:robustSIFTFeatureMatching}.
+and geometry-based line segments, which are within distance and
+angular thresholds of each other. We have found a distance threshold
+of 250 mm and an angular difference threshold of $10^\circ$ to work
+well for our datasets. For each pair of lines, we compute the angular
+difference between the pair's image and geometry lines. If there are 2
+or more pairs with angular differences within $1^\circ$, we select the
+two pairs with the longest noncollinear image-based lines, and rotate
+the image such that the lines in the pair with the longest image-based
+line become parallel. We then find a translation such that the lines
+in that same pair overlap. This translation has ambiguity in the
+dimension along the matched lines, which is resolved by matching the
+midpoint of the image-based line in the second pair to its
+corresponding geometry-based line. This is shown in case (1) of Figure
+\ref{fig:geometryAlignment}(c). Thus, with 2 or more pairs, it is
+possible to obtain a fixed rotation and translation for geometry
+alignment, which are saved for usage in Section
+\ref{sec:robustSIFTFeatureMatching}.
 
@@
 Figure \ref{fig:geometryAlignment}(c). For instance, doors, windows,
-furniture, etc. tend to have linear edges that are parallel to the
-edges of the surfaces they are on. Similarly, lights, visible interior
-walls, etc. which are visible in floor and ceiling images, tend to be
-parallel to interior and exterior walls, corresponding to the
-intersection lines and edges of ceiling and floor surfaces
-respectively. Thus, we choose to minimize the angle between
-image-based lines and geometry-based lines regardless of distance. We
-use the RANSAC framework to compute a rotation angle that best
-accomplishes this while ignoring outliers. \cite{fischler1981random}.
+furniture, ceiling lights, etc. tend to have linear edges that are
+parallel to the edges of the surfaces they are on. Thus, we choose to
+minimize the angle between image-based lines and geometry-based lines
+regardless of distance. We use the RANSAC framework to compute a
+rotation angle that best accomplishes this while ignoring
+outliers. \cite{fischler1981random}.
 
@@
 used to texture the orange target surface also contains part of a gray
-occluding surface. We remove this incorrect texture by recursively
-performing ray-polygon intersection tests between the camera location
-and every surface in our model except the target surface
+occluding surface. We remove this incorrect texture by performing
+ray-polygon intersection tests between the camera location and every
+surface in our model except the target surface
 \cite{rayintersection}. If using planar approximations for regions, as
 explained in Section \ref{sec:geometryPartitioning}, the k-d tree is
-used instead. These intersection tests are performed at the corners of
-a grid overlaid upon the target surface. Where all four corners of a
-grid section are occluded, texture is removed. Where one or more
-corners are occluded, the grid is subdivided into four, and the
-process repeats. Occlusion checking works entirely with geometry, so
-by ensuring that images match geometry using
+used instead. These intersection tests are performed repeatedly in a
+recursive grid, until all occlusions are detected and corresponding
+occluded texture is removed. Occlusion checking works entirely with
+geometry, so by ensuring that images match geometry using
 \ref{sec:geometryAlignment}'s alignment procedure, texture belonging
@@
 correspond to an image distance greater than 200 mm from what the
-noisy poses estimate. In order to utilize the remaining feature
-matches robustly, RANSAC \cite{fischler1981random} is again used to
-estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
-images $i$ and $j$. We use a 5 mm threshold for RANSAC, so that SIFT
-matches are labeled as outliers if their distance is not within 5 mm
-of the sampled average distance.
+noisy poses estimate. RANSAC \cite{fischler1981random} is then used to
+obtain a consensus from the the remaining feature matches.
 
@@
 \ref{sec:geometryAlignment} to refine all image positions using a
-weighted linear least squares approach. An example setup for a
-weighted linear least squares problem $\textrm{min}_{\vec{\beta}}
+weighted linear least squares approach. An example setup for such a problem $\textrm{min}_{\vec{\beta}}
 ||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
@@
 
-The variables we wish to solve for are the $x_i$ and $y_i$ positions
+The variables to solve for are the $x_i$ and $y_i$ positions
 of images, while equations are the feature-based distances between
@@
 In Section \ref{sec:imageSelection} we described an image selection
-method that reduces the list of candidate images for texturing by a
-factor of 10. In this section we go one step further to choose a
-subset of the above candidates in order to further reduce visual
-artifacts and discontinuities across textured surfaces. Specifically,
-in Section \ref{sec:mappingWithCaching}, we refine the tile-based
-texturing approach from Section \ref{sec:imageSelection}, with an
-added caching mechanism to reduce image boundaries. This method is
-general and works well given arbitrary camera poses and surfaces,
-whether large planar surfaces or small geometric interior
-features. For special cases where images have consistently
-perpendicular viewing angles to the surfaces under consideration, such
-as walls, it is possible to develop an alternative method in Section
-\ref{sec:shortestPath} to further reduce visual artifacts. Both of
-these approaches are followed by a blending step in order to produce
-final textures for each surface, as shown in Figure
-\ref{fig:flowchart}.
+method, that when used to create a texture, resulted in many visible
+discontinuities. In Section \ref{sec:mappingWithCaching}, we will
+refine that approach with an added caching mechanism to improve
+texture continuity. This method works well for all arbitrary camera
+poses and surfaces. However, for cases where images have consistently
+perpendicular viewing angles to surfaces under consideration, such as
+walls, we develop an alternative method in Section
+\ref{sec:shortestPath} which further reduces visual artifacts. Both of
+these approaches are then combined with an exposure compensation and
+blending scheme in order to produce final textures for each surface.
 
@@
 \label{sec:mappingWithCaching}
-For the simple texture mapping method described in Section
+For the simple texturing method described in Section
 \ref{sec:imageSelection}, discontinuities occur where adjacent tiles
@@
 discontinuities, there are still cases where seams are visible due to
-imprecise matching or other factors such as model-based errors as
-shown in Figure \ref{fig:compareAll}(b). To reduce this, it is
-desirable to develop a spatiotemporal caching mechanism to take into
-account image selections made by neighboring tiles while texture
+imprecise matching or other factors such as model-based errors. To
+reduce this, we implement a spatiotemporal caching mechanism to take
+into account image selections made by neighboring tiles while texture
 mapping a given tile. By using the same image across tile boundaries,
@@
 not visible in images used by neighboring tiles, using similar images
-across tile boundaries also leads to less noticeable discontinuities.
+across tile boundaries still leads to less noticeable discontinuities.
 
@@
 
+\subsection{Shortest Path Texturing}
+\label{sec:shortestPath}
+
 \begin{figure}
   \centering
-  \subfloat[][]{\includegraphics[width=1.5in]{projectionWall.pdf}}
-  \hspace{0.51in} \centering
-  \subfloat[][]{\includegraphics[width=1.5in]{projectionCeiling.pdf}}
-  \centering \hspace{0.5in}
-  \subfloat[][]{\includegraphics[width=1.5in]{projectionWallCrop.pdf}}
-  \caption{(a) Images for vertical planes are tilted, but their camera
-    axes are more or less normal to their respective planes. (b)
-    Camera axes for ceiling images are at large angles with respect to
-    plane normals. (c) Wall images are cropped to be rectangular.}
-  \label{fig:projectionAngles}
+  \begin{minipage}{3in}
+    \centering
+    \includegraphics[width=1.5in]{projectionCeiling.pdf}
+    \captionof{figure}{Camera axes for horizontal surfaces are at
+      large angles with respect to plane normals.}
+    \label{fig:projectionCeiling}
+  \end{minipage}%
+  \hspace{0.5in}
+  \begin{minipage}{3in}
+    \centering
+    \includegraphics[width=3in]{dagCreation.pdf}
+    \captionof{figure}{DAG construction for the image selection
+      process.}
+    \label{fig:dagCreation}
+  \end{minipage}
 \end{figure}
 
-\subsection{Shortest Path Texturing}
-\label{sec:shortestPath}
-
 As mentioned earlier, our data comes from a mobile backpack system
-carried by am ambulatory human operator, typically bent forwards at 15
-to 20 degrees with respect to the vertical direction. As a result,
-cameras facing sideways are head on with respect to vertical surfaces,
-as shown in Figure \ref{fig:projectionAngles}(a), while cameras
-oriented towards the top or bottom of the backpack are at an angle
-with respect to floors, ceilings and other horizontal surfaces, as
-shown in Figure \ref{fig:projectionAngles}(b). These oblique camera
-angles for horizontal surfaces translate into textures that span large
-areas once projected, as shown in Figure
-\ref{fig:projectionAngles}(b). Using the tile-based texture mapping
+with side-facing cameras. While these cameras have a wide-angle field
+of view,they are often pointed directly at vertical surfaces during
+data acquisition. This means that image projections on vertical
+surfaces tend to have higher, and more consistent resolution, while
+the more oblique projections onto horizontal surfaces result in
+textures spanning large areas, such as in Figure
+\ref{fig:projectionCeiling}. Using the tile-based texture mapping
 criteria from Figure \ref{fig:scoringFunction}, such projections have
@@
 near point A and not near point B, in Figure
-\ref{fig:projectionAngles}(b).
+\ref{fig:projectionCeiling}.
 
@@
 models, images are usually taken from close distances and head-on
-angles, resulting in high resolution fronto-parallel projections. As a
+angles, resulting in high resolution rectangular projections. As a
 result, for each tile on a wall plane, the scoring function of Figure
@@
 images, as they are all more or less head on. Since the scoring
-function is less discriminative for walls, it is conceivable to devise
-a different texturing strategy to directly minimize visible seams when
-texturing them. This is done by choosing the smallest possible subset
-of images from the set selected in Section \ref{sec:imageSelection}
-and aligned in Section \ref{sec:2dAlignment} such that it (a) covers
-the entire plane and (b) minimizes the visibility of borders between
-the images. A straightforward cost function that accomplishes the
-latter is the sum of squared differences (SSD) of pixels in
-overlapping regions between all pairs of images. Minimizing this cost
-function encourages image boundaries to occur either in featureless
-areas, such as bare walls, or in areas where images match extremely
-well.
-
-In its most general form, our problem can be defined as minimally
-covering a polygon i.e. the planar surface, using other polygons of
-arbitrary geometry i.e. image projections, with the added constraint
-of minimizing the cost function between chosen images. Given that
-wall-texture candidate images are taken from more or less head-on
-angles, and knowing that only minor rotations are made in Section
-\ref{sec:2dAlignment}, we can crop our image projections to be
-rectangular with minimal texture loss as shown in Figure
-\ref{fig:projectionAngles}(c). Furthermore, because the fisheye camera
-lenses have full floor-to-ceiling coverage of nearly all walls, and
-the backpack operator logically only moves horizontally, we only need
-to ensure lateral coverage of our wall planes. We can thus construct a
-Directed Acyclic Graph (DAG) from the images, with edge costs defined
-by the SSD cost function, and solve a simple shortest path problem to
-find an optimal subset of images with regard to the SSD cost function
-\cite{dijkstra}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=4in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process. \\}
-  \label{fig:dagCreation}
-\end{figure}
+function is less discriminative for walls, we devise a different
+texturing strategy to directly minimize visible seams when texturing
+them. This is done by choosing a subset of images such that their
+projections (a) cover the entire plane and (b) have minimal
+differences in overlapping regions. A straightforward cost function
+that accomplishes the latter is the sum of squared differences (SSD)
+of pixels in overlapping regions between all pairs of
+images. Minimizing this cost function encourages image boundaries to
+occur either in featureless areas, such as bare walls, or in areas
+where images match extremely well.
+
+To find the subset of images that covers the plane with minimal cost,
+we form a shortest path problem. This can be done because the
+wide-angle cameras have full floor-to-ceiling coverage of walls, and
+the backpack operator logically only moves horizontally. We thus are
+only concerned with lateral coverage when working with wall
+surfaces. We can therefore construct a horizontal Directed Acyclic
+Graph (DAG) from the images, with edge costs defined by the SSD cost
+function, and solve a simple shortest path problem to find an optimal
+subset of images with regard to the SSD cost function \cite{dijkstra}.
 
@@
 
-When texturing a model, we apply the shortest path method on vertical
-surfaces, due to its superior results when provided with head-on
-images. Floors, ceilings, and smaller complex objects such as
-furniture, given their many images taken at oblique angles, are
-textured using the tile caching method of Section
+When texturing our models, we apply the shortest path method on
+surfaces where images are taken at optimal angles and provide full
+coverage along one dimension. Floors, ceilings, and smaller complex
+objects such as furniture, given their many images taken at oblique
+angles, are textured using the tile caching method of Section
 \ref{sec:mappingWithCaching}.
@@
 \label{sec:examples}
-As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
-procedure in this paper can be applied both to low-resolution and
-high-resolution models. Low resolution models have an advantage in
-their simplicity, and in that only important environmental features
-are represented. As a result, images are generated for large sections
-of buildings, and texture continuity is maintained over large
-areas. High resolution models have an obvious advantage in terms of
-the amount of detail that can be reconstructed, but with poor region
-partitioning, as described in Section \ref{sec:geometryPartitioning},
-or with high camera pose or geometry reconstruction error, 3D elements
-in the environment geometry may not match up well with their imaged
-counterparts.
 
@@
   \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
-  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_v.png}
-  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_2d.png}
-  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_3d.png}\\
   \subfloat[][]{
@@
     plane-fitting, (b) Floor plan extrusion, (c) Voxel carving. The
-    first two are low-resolution models, while the third is
-    high-resolution. The PCA method is not watertight, and contains
-    some holes (white). It also has the lowest level of detail in its
-    geometry. The floor plan method is slightly more detailed, and is
-    watertight as well. The voxel carving method also produces
-    watertight meshes, and reconstructs smaller features, such as the
-    bench and the ladder in the lower two images.}
+    first two are lower-resolution models, while the third is
+    higher-resolution, and reconstructs significantly more features,
+    such as the ladder in the lower image.}
   \label{fig:modelcomparisons}
 \end{figure}
-
-Our approach was tested with three different geometry-reconstruction
-methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
-floor plan extrusion method \cite{turnerfloorplan}, and a
-voxel-carving mesh generation method \cite{turnerwatertight}. The
-first two methods generate lower-resolution models, containing only
-major walls, ceilings and floors. The third method generates
-high-resolution models, and attempts to reconstruct all scanned
-objects in the environment. Images illustrating the differences
-between the three methods are in Figure \ref{fig:modelcomparisons}
-
 \begin{figure}
-  \centering \subfloat[][]{
-    \includegraphics[width=3in]{results_p15_v.png}
-  } \subfloat[][]{
-    \includegraphics[width=3in]{results_p15_2d.png}
-  }
-  \caption{(a) A model generated by the PCA method with many missing
-    surfaces. (b) A watertight model generated by the floor plan
-    extrusion method.}
-  \label{fig:lowresmodels}
-\end{figure}
-
-The PCA and floor plan methods produce models at a similar level of
-detail. As visible in Figure \ref{fig:lowresmodels}, the PCA method is
-not watertight, while the floor plan method is. As a result, the
-PCA-generated model contains holes where surfaces were not adequately
-scanned. On the other hand, the watertight floor plan model sometimes
-must make assumptions about the location of surfaces that were not
-adequately scanned, in order to maintain watertightness. Because
-buildings generally follow straight lines and right angle corners
-however, such assumptions tend to be correct. Additionally, the
-floor-plan method is generally superior at reconstructing smaller
-surfaces, such as small walls, or to approximate curved surfaces,
-while the PCA method only fits large planes, and fails in both
-cases. As a result, the floor-plan method usually produces more
-visually pleasing low-resolution models, and is the method of choice
-for generating textured low-resolution models.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3.1in]{results_houston_1_2d.png}
-  \includegraphics[width=3.1in]{results_houston_1_3d.png}\\
   \includegraphics[width=3.1in]{results_houston_2_2d.png}
@@
 
-High-resolution models, as generated by the voxel-carving method, can
-produce more accurate reconstructions of environment geometry. With
-such models, region partitioning, as described in Section
-\ref{sec:geometryPartitioning}, plays an important factor in the
-quality of generated textures. If regions are small, boundaries
-between adjacent textures become visible, and since each region is
-processed independently, image alignment procedures are performed
-across smaller areas. If regions are large, then the difference
-between the 3D surface geometry and the approximated 2D texturing
-surface become large as well, introducing greater texture projection
-error. Additionally, in areas where pose error or surface
-reconstruction error is high, 3D objects in images do not get
-accurately projected onto their modeled counterparts. While large
-objects can be aligned to geometry via the methods in Section
-\ref{sec:geometryAlignment}, smaller objects such as plants or
-computers are difficult to line up to geometry references. While the
-compositing techniques is Section \ref{sec:imageCompositing} can
-ensure that textures for small objects appear seamless, such textures
-may not map accurately upon their corresponding geometry, leading to
-visually obvious discrepancies in the textured model. Figure
-\ref{fig:2dvs3d} contains textured examples from the low-resolution
-floor plan approach alongside examples from the high-resolution
-voxel-carving approach. As evident in the image comparisons, the 3D
-models may be more accurate, but the 2D models often allow for a
-cleaner visualization, with larger regions over which images are
-successfully composited together.
-
-As visible in Figure \ref{fig:2dvs3d} and other images in this
-section, 2D models using the floor plan approach are generally
-preferred, as they provide enough detail in geometry to reconstruct
-the basic layout of an environment, while textures can be used to
-visualize smaller details. On the other hand, for applications where
-furniture and smaller interior details are important, applying
-textures to the 3D voxel-carved models provides useful image-based
-context for visualizing indoor areas. Further examples of
-texture-mapped models are contained at the end of this
-document. Figure \ref{fig:indivPlanes} contains textured surfaces
-alone. Figures \ref{fig:victor1}-\ref{fig:e2d4} contain interior and
-exterior views of low-resolution models. Figures
-\ref{fig:e3d1}-\ref{fig:e3d3} contain interior and exterior views of
-high-resolution models.
+The texture mapping procedure in this paper was tested with three
+different geometry-reconstruction methods, a PCA-based plane-fitting
+method \cite{sanchez2012point}, a floor plan extrusion method
+\cite{turnerfloorplan}, and a voxel-carving mesh generation method
+\cite{turnerwatertight}. The first two methods generate very similar
+low-resolution models, containing only major walls, ceilings and
+floors. The third method generates high-resolution models, and
+attempts to reconstruct all scanned objects in the environment. A
+comparison of the three model types is in Figure
+\ref{fig:modelcomparisons}, while Figure \ref{fig:2dvs3d} compares the
+latter 2 types for a closer comparison of a low-resolution model vs a
+high-resolution model.
 
@@
 
-In this paper, we have developed an approach to texture mapping
-models of indoor environments with noisy camera localization data. We
-are able to refine image locations based on geometry references and
+In this paper, we have developed an approach to texture mapping models
+of indoor environments with noisy camera localization data. We are
+able to refine image locations based on geometry references and
 feature matching, and robustly handle outliers. Using the tile-based
@@
 \cite{linearposeestimation}. Finally, the blending procedure is quite
-basic, and applying more sophisticated methods of blending,
-normalization, as well as image boundary selection would benefit the
-final visual quality, and more robustly handle motion-based or
-parallax errors.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{finalfloors.jpg}} ~~~~~~~~
-  \\
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{finalceilings.jpg}}
-
-  \centering \subfloat[][]{
-    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
-    \includegraphics[width=3in]{pier15floor.jpg}
-  }
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) floors}
-  \label{fig:indivPlanes}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in]{threestoryfull2.png} \\
-    \includegraphics[width=6.2in]{threestoryfull.png}
-  }
-  \caption{Textured low-resolution models from the PCA-based approach.}
-  \label{fig:victor1}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in]{fullmodel.png} \\
-    \includegraphics[width=6.2in]{pier15.png} \\
-  }
-  \caption{Textured low-resolution models from the PCA-based approach.}
-  \label{fig:victor2}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston2d1.png} \\
-    \includegraphics[width=6.2in,height=3in]{houston2d2_2.png} \\
-    \includegraphics[width=6.2in,height=3in]{houston3_2.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d1}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{coryf2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_2d_1.png} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_2d_2.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d2}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{office.png} \\
-    \includegraphics[width=6.2in,height=3in]{office1.png} \\
-    \includegraphics[width=6.2in,height=3in]{office2.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d3}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{bhh1.png} \\
-    \includegraphics[width=6.2in,height=3in]{bhh2.png} \\
-    \includegraphics[width=6.2in,height=3in]{bhh3.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d4}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3d2.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d1}
-\end{figure}
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_4.png} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_2.png} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d2}
-\end{figure}
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{bhh3d1.png} \\
-    \includegraphics[width=6.2in,height=3in]{bhh3d2.png} \\
-    \includegraphics[width=6.2in,height=3in]{bhh3d3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d3}
-\end{figure}
+basic, and applying more sophisticated methods of blending as well as
+image boundary selection would benefit the final visual quality, and
+more robustly handle motion-based or parallax errors.
 

### 2014-01-04 spie2014/spie2014.tex
down to 15, but no graphics
down to 14

@@
   \centering
-  \includegraphics[width=4in]{flowchart.jpg}
+  \includegraphics[width=6.2in]{flowchart2.jpg}
   \caption{The proposed texture mapping procedure\\}
@@
   turnerfloorplan}, as well as highly detailed models
-\cite{turnerwatertight}.  Regardless of resolution, size, or detail,
+\cite{turnerwatertight}.  Regardless of resolution or size,
 the model, consisting of geometric surfaces in 3D space, along with
@@
 
-Though some of these regions from high-resolution models are not
-completely flat, a plane is fitted to each region for the purposes of
-texturing. This plane corresponds to the largest contiguous section of
-coplanar triangles, as most regions are characterized by small
-outcroppings from a largely planar surface, such as objects on a table
-or features protruding from a wall. The 3D surface composing a region
-is then projected onto its calculated plane, and the resulting 2D
-planar polygon is used as the texturing surface. This 2D planar
-approximation provides a simple, yet approximately accurate surface
-onto which images can be projected in order to generate
-textures. However, 3D surfaces are still retained in order to achieve
-more accurate results when performing occlusion checks during the
-texturing process. To improve runtime during such occlusion checks,
-the triangles within all 3D surfaces are also loaded into a k-d tree
-for quick lookup. Thus, for high-resolution models, each region has
-both 3D geometry stored in a k-d tree for occlusion purposes, and an
-approximate 2D representation stored as the texturing surface.
-
-At this point, we either have a series of planar regions from a low
-resolution model, or a set of planar approximations for regions as
-well as an associated k-d tree from a high resolution model. The task
-now is to generate a texture for each region.
+For the purposes of texturing, it is convenient to treat each region
+as planar. To accomplish this, a plane is fitted to each region. This
+plane corresponds to the largest contiguous section of coplanar
+triangles, as most regions are characterized by small outcroppings
+from a largely planar surface, such as objects on a table or features
+protruding from a wall. The 3D surface composing a region is then
+projected onto its calculated plane, and the resulting 2D planar
+polygon is used as the texturing surface. This 2D planar approximation
+provides a simple, yet approximately accurate surface onto which
+images can be projected in order to generate textures. However, 3D
+surfaces are still retained in order to achieve accurate results when
+performing occlusion checks, and of course are used to generate the
+final textured model. Each region now has a set of triangles
+representing the original model geometry, as well as a planar
+approximation. The task now is to generate a texture for each region.
 
@@
 \label{sec:relatedWork}
-There are many existing approaches to stitching together multiple
-images to produce a larger, seamless image \cite{szeliski2006image,
-  agarwalapanoramas, wangmultipleviews, coorg1997matching,
-  debevechybrid, bernardinimultiplescans}. Generally, parts of images
-are matched to each other, either through direct comparisons at a
-pixel level, or through feature detection and matching. Images are
-then transformed to maximize matches, often by computing homographies
-between pairs of images, or by iteratively adjusting camera poses in 1
-to 6 degrees of freedom.
-
-Feature matching has a number of advantages over direct matching that
-make it more suitable for our often non-planar environments, and
-rotational differences between camera poses
-\cite{szeliski2006image}. Feature matching however, works best when
-multiple unique visual references exist in the environment that can be
-detected in multiple images. In contrast, indoor environments have a
-high prevalence of bare surfaces, as well as repeating textures, such
-as similar windows, doors, and wall-mounted decorations, that are
-difficult to disambiguate. This lack of reliable reference points
-often results in errors when matching images together.
-
-Additionally, our datasets often contain long chains of images,
-corresponding to long hallways and corridors as shown in Figure
-\ref{fig:mosaic3D}, which leads to error accumulation when image
-correspondences are not accurate. For example, when matching a long
-chain of images through homography, a pixel in the $nth$ image must be
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these
-homography matrices is propagated to all further images, resulting in
-drift.
 
@@
 
-In prior work, we have experimented with integrating image stitching
-with the iterative global localization algorithm used to recover the 6
-degrees of freedom of the backpack acquisition system detailed in
-Section \ref{sec:dataAcquisition} \cite{liu2010indoor}. When run on
-long chains of images however, especially where features are sparse,
-this approach produces distorted textures, as seen in Figure
-\ref{fig:mosaic3D}(a). Furthermore, this approach is not closed-form,
-and its iterative camera adjustment process over large datasets leads
-to prohibitively long computation time.
-
-The AutoStitch software package, based on research in the related area
-of panorama genoration, also performs homography-based alignment, with
-additional provisions that attempt to reduce drift and increase
-overall efficiency \cite{panorama2d, autostitch}. Though AutoStitch
-performs well in small areas, it often induces drift in images,
-such that global alignment to the environment geometry is
-lost. Furthermore, its performance relies on the presence of a dense
-set of features, and it has trouble aligning wall sections with even
-short segments of bare texture. The example in Figure
-\ref{fig:mosaic3D}(b) was generated after many rounds of manual
-tuning; we have empirically found that areas with fewer visual
-features or repeating texture patterns simply failed outright with
-AutoStitch.
+There are many existing approaches to stitching together multiple
+images to produce a larger, seamless image \cite{szeliski2006image,
+  agarwalapanoramas, wangmultipleviews, coorg1997matching,
+  debevechybrid, bernardinimultiplescans}. Generally, parts of images
+are matched to each other, by detecting feature points and identifying
+matches. Images are then transformed to maximizally align matches,
+often by computing homographies between pairs of images, or by
+iteratively adjusting camera poses in 1 to 6 degrees of freedom.
+
+Feature matching works best when unique visual references exist in the
+environment that can be detected in multiple images. Unfortunately,
+many indoor environments have a high prevalence of bare surfaces as
+well as repeating textures, such as with windows and
+doors. Additionally, our datasets often contain long 1-dimensional
+chains of images, such as in Figure \ref{fig:mosaic3D}, which often
+leads to error accumulation. For example, when matching a long chain
+of images via homography matrices, a pixel in the $nth$ image must be
+translated into the first image's coordinates by multiplying by the
+$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Errors in each of these
+homography matrices is propagated to all further images, resulting in
+drift.
+
+Two methods based on feature matching and homography calculation are
+shown in Figure \ref{fig:mosaic3D}. Figure \ref{fig:mosaic3D}(a)
+depicts an attempt at integrating image stitching with the iterative
+global localization algorithm used to localize the backpack system
+detailed in Section \ref{sec:dataAcquisition}
+\cite{liu2010indoor}. Figure \ref{fig:mosaic3D}(b) depicts an output
+image from AutoStitch, which is software based on research in the
+related area of panorama generation \cite{panorama2d,
+  autostitch}. Both methods were thoroughly tuned for the shown
+example, but due to the factors mentioned in the previous paragraph,
+they still show significant amounts of drift and distortion, as well
+as loss of alignment to the environment geometry.
 
@@
 \begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive_shift.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_cache_comparison.png}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_shortest_comparison.png}}
+  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
+    height=0.8in]{wall2_naive.jpg}}
+  \subfloat[][]{\includegraphics[width=0.33\textwidth,
+    height=0.8in]{wall2_naive_shift.jpg}}
+  \subfloat[][]{\includegraphics[trim=1.2cm 0cm 0cm 0cm,
+        clip=true,width=0.33\textwidth,
+    height=0.8in]{wall2_cache_shift.jpg}}
+
+  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
+    height=0.8in]{wall2_shortest_shift.pdf}}
+  \subfloat[][]{\includegraphics[width=0.33\textwidth,
+    height=0.8in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=0.33\textwidth,
+    height=0.8in]{wall2_shortest_shift_blend.pdf}}
 
@@
     with caching; (d) Shortest path texturing after image alignment;
-    (e,f) Blending applied to (c) and (d); (g,h) Zoomed in views of
-    discontinuities in (e) vs. in (f).}
+    (e,f) Blending applied to (c) and (d).}
   \label{fig:compareAll}
@@
   \centering
-  \subfloat[][]{\includegraphics[width=3.3in]{exposureDiff1.png}}
-  \subfloat[][]{\includegraphics[width=3.3in]{exposureDiff2.png}}
+  \subfloat[][]{\includegraphics[width=2.5in, height=0.9in]{exposureDiff1.png}}
+  \hspace{0.5in}
+  \subfloat[][]{\includegraphics[width=2.5in, height=0.9in]{exposureDiff2.png}}
   \caption{(a) A ceiling texture composed of images taken with varying
@@
 \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. The
-remaining images in Figure \ref{fig:compareAll} highlight differences
-between the two methods, showing that Figure \ref{fig:compareAll}(f)
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. By
+comparing all images, it is clear that Figure \ref{fig:compareAll}(f)
 has the best visual quality and the best texturing approach among the

### 2014-01-04 spie2013/assets/3dimpvt/paperv1.tex
organize stuff

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr} \usepackage{times} \usepackage{epsfig}
\usepackage{graphicx} \usepackage{amsmath} \usepackage{amssymb}
\usepackage{subfig}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first
% latex run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the 3DIMPVT Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in
% camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{Texture Mapping 3D Models of Indoor Environments with Noisy
  Camera Poses}

\author{First Author\\
  Institution1\\
  Institution1 address\\
  {\tt\small firstauthor@i1.org}
  % For a paper whose authors are all at the same institution, omit
  % the following lines up until the closing ``}''.  Additional
  % authors and addresses can be added with ``\and'', just like the
  % second author.  To save space, use either the email address or
  % home page, not both
  \and
  Second Author\\
  Institution2\\
  First line of institution2 address\\
  {\small\url{http://www.author.org/~second}} }

\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is useful in
  applications such as virtual reality and environment
  mapping. Applying textures to these models is an important step in
  generating photorealistic visualizations of data gathered by
  modeling systems.  The localization of cameras in such systems often
  suffer from inaccuracies, resulting in visible discontinuties when
  different images are projected adjacently onto a plane for
  texturing. We propose two approaches for reducing discontinuities
  during texture mapping, one to robustly accomodate images of all
  orientations, and one to take advantage of optimal situations where
  images have uniform orientation. The effectiveness of our approaches
  will be demonstrated on two indoor datasets.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:introduction}
Three-dimensional modeling of indoor environments has a variety of
applications such as training and simulation for disaster management,
virtual heritage conservation, and mapping of hazardous sites. Manual
construction of these digital models can be time consuming, and as
such, automated 3D site modeling has garnered much interest in recent
years.

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with high camera pose
errors and great variance in camera locations.

The first step in automated 3D modeling is the physical scanning of
the environment's geometry. An indoor modeling system must be able to
recover camera poses within an environment while simulatenously
reconstructing the 3D structure of the environment itself. This is
known as the simultaneous localization and mapping (SLAM) problem, and
is generally solved by taking readings from laser range scanners,
cameras, and inertial measurement units (IMUs) at multiple locations
within the environment.

Mounting such devices on a human-carried platform provides unique
advantages over vehicular-based systems in terms of agility and
portability. Unfortunately, human-operated systems also result in much
larger localization error. As a result, common methods for texture
mapping generally produce poor results, as later shown in Sections
\ref{sec:simpleTextureMapping} and
\ref{sec:existingApproaches}. Before discussing how to overcome these
challenges, we first provide an overview of the backpack modeling
system from which our test data has been obtained.

Our backpack-mounted modeling system contains five 2D laser range
scanners, two cameras, and an orientation sensor. The laser scanners
are mounted orthogonally and have a 30-meter range and a 270$^{\circ}$
field of view. The two cameras are equipped with fisheye lenses,
reaching an approximately 180$^{\circ}$ field of view, and are mounted
with one facing left and the other facing right. These cameras take
images at the rate of 5 Hz. The orientation sensor provides
orientation parameters at a rate of 180 Hz.

With the laser scanners active, the human operator wearing the
backpack takes great care to walk a path such that every wall in the
desired indoor environment is traversed and scanned lengthwise at
least once.

Using data gathered by the onboard sensors and multiple localization
and loop-closure algorithms, the backpack is first localized over its
data collection period, and a 3D point cloud of the surrounding
environment is constructed based on the laser scanner readings
relative to the backpack \cite{chen2010indoor, kua2012loopclosure, liu2010indoor}. Approximate normal vectors for each point in
the point cloud are then calculated by gathering neighboring points
within a small radius and processing them through principal component
analysis. These normal vectors allow for the classification and
grouping of adjacent points into structures such as walls, ceilings,
floors, and staircases. A RANSAC algorithm is then employed to fit
polygonal planes to these structured groupings of points, resulting in
a fully planar model \cite{sanchez2012point}. This model, consisting
of multiple 2D polygonal planes in 3D space, along with the set of
images captured by the backpack's camera, can be considered the input
to our texture mapping problem.

The remainder of the paper is organized as follows. Section
\ref{sec:simpleTextureMapping} describes the general problem of
texture mapping and examines two simple mapping approaches and their
shortcomings.  Section \ref{sec:existingApproaches} demonstrates two
previous attempts at localization refinement, and demonstrates their
inadequacies for our datasets.  Section \ref{sec:proposedApproach}
presents our proposed approach to texture mapping, combining an
improved localization refinement process with two image selection
approaches. Section \ref{sec:resultsAndConclusions} contains results
and conclusions.

\section{Simple Texture Mapping}
\label{sec:simpleTextureMapping}
\begin{figure}
  \centering
  \includegraphics[height=2in]{Projection.pdf}
  \caption{Planes are specified in 3D space by four corners $C_1$ to
    $C_4$. Images are related to each plane through the camera
    matrices $P_{1..M}$. }
  \label{fig:projection}
\end{figure}

In all subsequent sections, we discuss the process of texture
mapping a single plane, as the texturing of each of our planes is
independent and can be completed in parallel.

The geometry of the texture mapping process for a plane is shown in
Figure \ref{fig:projection}.  As described earlier, we
are provided with a set of $M$ images with which we must texture our
target plane. Each image has a camera matrix $P_i$ for $i=1..M$, which
translates a 3D point in the world coordinate system to a 2D point or
pixel in image $i$'s coordinates. If the 3D world point is not
contained in the image, the 2D point will simply be outside of the
image boundaries. A camera matrix $P_i$ is composed of the camera's
intrinsic parameters, such as focal length and image center, as well
as extrinsic parameters which specify the rotation and translation of
the camera's position in 3D world coordinates at the time that image
$i$ is taken. These extrinsic parameters are determined by the
backpack hardware and localization algorithms mentioned earlier. A point $X$ on the plane in 3D space
can be related to its corresponding pixel $x$ in image $i$ through the
following equation:

\[
x=project(P_iX)
\]

where
\[X = \begin{pmatrix} x \\ y \\ z \end{pmatrix} \textrm{ and }
project(X) = \begin{pmatrix} x/z \\ y/z \end{pmatrix}
\]

For the sake of simplicity, we treat all planes as rectangles by
generating minimum bounding boxes for them. Since our final textures
are stored as standard rectangular images anyway, we can simply
leave the area between plane boundary and bounding box untextured, or
crop it out as needed. A plane to be textured is thus defined by a
bounding box with corners $C_i$ in world coordinates and a normal
vector indicating the front facing side of the plane. Our goal is to
texture this plane using images captured by the backpack, while
eliminating any visual discontinuities or seams that would suggest
that the plane's texture is not composed of a single continuous
image.

\subsection{Direct Mapping}
\label{sec:directMapping}

Ignoring the fact that the camera matrices $P_{1..M}$ are inaccurate,
we can texture the plane by discretizing it into small square tiles,
generally about 5 pixels across, and choosing an image to texture each
tile with. We choose to work with rectangular units to ensure that
borders between any two distinct images in our final texture are
either horizontal or vertical. Since most environmental features
inside buildings are horizontal or vertical, any seams in our texture
intersect them miniimally and are likely to be less noticeable.

In order to select an image for texturing tile $t$, we must first
gather a list of candidate images that contain all four of its
corners, which we can quickly check by projecting $t$ into each image
using the projection method above. Furthermore, each candidate image
must have been taken at a time when its camera had a clear
line-of-sight to $t$, which can be calculated using standard
ray-polygon intersection tests between the camera location, the center
of $t$, and other planes, all in world coordinates.

Once we have a list of candidate images for $t$, we must define a
scoring function in order to compare images and objectively select the
best one. Since camera localization errors compound over distance, we
wish to minimize the distance between cameras used for texturing and
our plane. Additionally, we desire images that are projected
perpendicularly onto the plane, maximizing the resolution and amount
of useful texture available in their projections.

These two criteria can be met by maximizing the function

\[
\frac{1}{d} \cdot (-1 \cdot C) \cdot N
\]

which minimizes camera angle $\alpha$ and distance $d$ as shown in Figure \ref{fig:scoringFunction}.

\begin{figure}
  \centering
  \includegraphics[height=1.5in]{scoringFunction.pdf}
  \caption{Images are selected by minimizing camera angle $\alpha$ and distance $d$.}
  \label{fig:scoringFunction}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=3in]{wall1_naive.jpg}
  \caption{The result of direct texture mapping based on locally
    optimized textures.}
  \label{fig:directMapping}
\end{figure}

As Figure \ref{fig:directMapping} demonstrates, this approach leads to
the best texture for each tile independently, but overall results in
many image boundaries with abrupt discontinuities, due to significant
misalignment between images.

\subsection{Mapping with Caching}
\label{sec:mappingWithCaching}
Since discontinuities occur where adjacent tiles select different
images that do not align, it makes sense to take into account image
selections made by neighboring tiles while selecting the best image
for a given tile. By using the same image across tile boundaries, we
eliminate the discontinuity altogether. If a tile is not visible in
images chosen by its neighbors, using similar images is likely to
result in less noticeable discontinuities.

Similar to a caching mechanism, we select the best image for a tile
$t$ by searching through two subsets of images for a good candidate,
before searching through the entire set. The first subset of images is
those selected by adjacent tiles that have already been textured. We
must first check which images can map to $t$, and then of those, we
make a choice according to the same scoring function in Figure
\ref{fig:scoringFunction}. Rather than blindly reusing this image, we
ensure it meets a threshold, which we set to $\alpha < 45^\circ$, to
be considered a good image.

If no good image is found, we then check our second subset of images,
which consists of images that were taken near the images in the first
subset, both spatially and temporally. These images are not the same
as the ones used for neighboring tiles, but they were taken at a
similar location and time, suggesting that their localization and
projection are very similar. Again, if no good image is found
according to the same threshold, we then must search the entire set of
candidate images.

\begin{figure}
  \centering
  \includegraphics[width=3in]{wall1_cache_full.jpg}
  \caption{The result of adding a caching system to locally optimized
    textures.}
  \label{fig:caching}
\end{figure}

The result of this caching approach is shown in figure
\ref{fig:caching}. As compared to \ref{fig:directMapping},
discontinuities have been reduced overall, but the amount of remaining
seams suggests that image selection alone cannot produce seamless
textures. Camera matrices, or the image projections themselves have to
be adjusted in order to reliably generate clean textures.

\section{Existing Approaches to Image-Aligned Texture Mapping}
\label{sec:existingApproaches}
In order to produce seamless texture mapping, either camera matrices
need to be refined such that their localization is pixel accurate,
resulting in a perfect mapping, or image stitching techniques need to
be applied to provide this illusion. Before examining these
approaches, we first obtain a set of images to work with.

Rather than perform camera or image adjustments across the many
thousands of images acquired in a typical data collection, we opt to
work with the more limited set of images corresponding to those chosen
by the direct mapping approach, without caching. This set of images
constitutes a good candidate set for generating a final seamless
texture since it meets three important criteria. First, it contains at least one image that covers each tile on our
plane; this ensures no holes in our final texture. Second, since
images are all selected according to the same scoring function in
Figure \ref{fig:scoringFunction}, they are taken at as much of a head-on angle as possible and should project
onto the plane in similar ways. Third, as a side result of the scoring
function, selected images are only good candidates for the tiles near
their center of projection. Thus, there should be plenty of overlap
between selected images, allowing for some degree of shifting without
resulting in holes, as well as area for blending between them. With
this set of images, we now review two existing approaches towards refining and
combining their projections.

\subsection{Image Mosaicing}
\label{sec:imageMosaicing}
\begin{figure}
  \centering
  \includegraphics[width=3in]{panoMy.jpg}
  \caption{Image mosaicing. }
  \label{fig:mosaic}
\end{figure}

When images of a plane are taken from arbitrary overlapping positions,
they are related by homography \cite{hz}. Thus, existing
homography-based image mosaicing algorithms are applicable
\cite{brown2007automatic}. However, errors can compound when long
chains of images are mosaiced together using these approaches. For
example, a pixel in the $n$th image in the chain must be translated
into the first image's coordinates by multiplying by the $3\times3$
matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these homography
matrices is propagated to all further images until the chain is
broken. For some chains of images this can happen almost immediately
due to erroneous correspondence matches and the resulting image mosaic
is grossly misshapen.

Figure \ref{fig:mosaic} shows the output of the AutoStitch software
package which does homography-based image mosaicing. This plane is
nearly a best-case scenerio with many features spread uniformly across
it. Even so, the mosaicing produces errors that causes straight lines
to appear as waves on the plane. This image was generated after
careful hand tuning as well. Many planes that had fewer features
simply failed outright. Thus, image mosaicing is not a robust enough
solution for reliably texture mapping our dataset.

\subsection{Image-Based 3D Localization Refinement}
\label{sec:imageBased3DRefinement}
\begin{figure}
  \centering
  \includegraphics[width=3in]{Graph_crop.pdf}
  \caption{The graph-based localization refinement algorithm from [11]
    suffers from the problem of compounding errors. }
  \label{fig:graph}
\end{figure}

Another approach is to refine the camera matrices using image
correspondences to guide the process. Each image's camera matrix has 6
degrees of freedom that can be adjusted. Previous work on this problem
attempted to refine camera matrices by solving a non-linear
optimization problem \cite{liu2010indoor}. This process is specific to
the backpack system which generated our dataset, as it must be run
during backpack
localization\cite{liu2010indoor,chen2010indoor}. Unfortunately, this
approach suffers from a similar error propagation problem shown in
Figure \ref{fig:graph}.

\section{Proposed Method for Seamless Texture Mapping}
\label{sec:proposedApproach}
Our proposed approach towards texture mapping is a two-step
process. First, with the same input set of images as described in
Section \ref{sec:existingApproaches}, we perform image rotation and
shifting in order to maximize SIFT feature matches between images. We
then project these images onto our plane, applying textures either
with the tile caching method from Section
\ref{sec:mappingWithCaching}, or with the more specialized method
described in Section \ref{sec:seamMinimization}.

\subsection{Image Projection and Rotation}
\label{sec:projectionAndRotation}
Our localization approach begins with the projection of all our images
onto separate copies of our plane, such that no projected data is
covered up and lost. This is done in the same way as the approaches in
Section \ref{sec:simpleTextureMapping}. We then perform rotations on
these projections, as adjacent images with different orientations will
result in strong discontinuities.

These rotations are accomplished by using Hough transforms, which
detect the presence and orientation of linear features in our
images. Rather than match the orientation of such features in each
image, we simply apply rotations such that the strongest near-vertical
features are made completely vertical. This is effective for indoor
models, since strong features in indoor scenes usually consist of
parallel vertical lines corresponding to doors, wall panels,
rectangular frames, etc. If features in the environment are not
vertical, or are not parallel to eachother, this step is skipped.

\begin{figure}
  \centering
  \includegraphics[width=3in]{matches.jpg}
  \caption{SIFT feature matches between overlapping images.}
  \label{fig:matches}
\end{figure}

\subsection{Robust SIFT Feature Matching using RANSAC}
\label{sec:robustSIFTFeatureMatching}
Our next step is to fix misalignment between overlapping images. We do
this by first searching for corresponding points between all pairs of
overlapping images using SIFT feature matching
\cite{lowe1999object}. An illustration of this is given in Figure
\ref{fig:matches}. The SIFT matches allow us to determine $dx$ and
$dy$ distances between each pair of features for two images on the
plane, determining where they should be projected relative to
eachother.

Since indoor environments often contain repetitive features such as
floor tiles or doors, we need to ensure that our SIFT-based distances
are reliable. In order to mitigate the effect of incorrect matches and
outliers, the RANSAC framework \cite{fischler1981random} is used for a
robust estimate of the optimal $dx$ and $dy$ distances between two
images. The RANSAC framework handles the consensus-building machinery,
and requires a fitting function and a distance function. For this
application, the fitting function simply finds the average distance
between matches in a pair of images. Our distance function for a pair
of points is the difference between those points' SIFT match distance
and the average distance computed by the fitting function; we use a 10
pixel outlier threshold. This means that a SIFT match is labeled as an
outlier if its horizontal or vertical distance is not within 10 pixels
of the average distance computed by the fitting function.

\subsubsection{Refining Image Positions using Least Squares}
\label{sec:refiningImagePositions}
There are a total of $M^{2}$ possible pairs of images, though we only
generate distances between images that overlap at SIFT feature
points. Given these distances and the original image location
estimates, we can solve a least squares problem ($\textrm{min}_{\vec{\beta}}
||X \vec{\beta} - \vec{\gamma}||_2^2 $) to estimate the correct location of the images
on the plane. The $M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
and $y$ locations of each image on the plane from $1 \dots M$. The
optimal $x$ and $y$ locations are obtained in the same way, so we
only consider the $x$ locations here:

% Draw least squares problem here.

\[\vec{\beta} =
\begin{pmatrix}
  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
\end{pmatrix}
\]

The $N$ by $(M+1)$ dimensional matrix $X$ is constructed with one row for each pair of images
with measured distances produced by the SIFT matching stage. A row in
the matrix has a $-1$ and $1$ in the columns corresponding to the two
images in the pair. For example, the matrix below indicates that we
generated a SIFT-based distance between images 1 and 2, images 1 and
3, images 2 and 3, etc.

\[
X =
\begin{pmatrix}
  -1 & 1 & 0 & \cdots & 0 & 0\\
  -1 & 0 & 1 & \cdots & 0 & 0\\
  0 & -1 & 1 & \cdots & 0 & 0\\
  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
  0 & 0 & 0 & \cdots & 1 & 0 \\
  0 & 0 & 0 & \cdots & -1 & 1 \\
  1 & 0 & 0 & \cdots & 0 & 0 \\
\end{pmatrix}
\]

If only relative distances between images are included then there is
no way to determine the absolute location of any of the images and the
matrix becomes rank deficient. To fix this we choose the first image
to serve as the anchor for the rest, meaning all the absolute
distances are based on its original location. This is done by adding a
row with a $1$ in the first column and the rest zeros.

Finally, the $N$-dimensional observation vector $\vec{\gamma}$ is constructed using the
SIFT-based distances generated earlier in the matching stage. The
distances are denoted as $d_1 \dots d_N$ for $N$ SIFT-based
distances. The last element in the observation vector is the location
of the first image determined by its original noisy localization, from \cite{chen2010indoor, liu2010indoor}:

\[
\vec{y}^T =
\begin{pmatrix}
  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
\end{pmatrix}
\]

The $\vec{\beta}$ that minimizes $||X \vec{\beta} - \vec{\gamma}||_2^2$ results in a set of
image locations on the plane that best honors all the SIFT-based
distance measurements between images. In practice there are often
cases where there is a break in the chain of images, meaning that no
SIFT matches were found between one segment of the plane and
another. In this case we add rows to the $X$ matrix and observations
to the $\vec{\gamma}$ vector that contain the original noisy $x$ and $y$ distance
estimates generated by the localization algorithm \cite{chen2010indoor, liu2010indoor}. Another way to do
this is to add rows for all neighboring pairs of images and solve a
weighted least squares problem where the SIFT distances are given a
higher weight i.e. 1, and the noisy distances generated by the localization
algorithm \cite{chen2010indoor, liu2010indoor} are given a smaller weight i.e. 0.01.

After completing this same process for the $y$ dimension as well, and
making the resultant shifts, our image projections should overlap and
match eachother with far greater accuracy.

\subsection{Relocalized Mapping with Caching}
\label{sec:mappingCachingLocalized}
Now that our images have been relocalized for much greater accuracy
relative to eachother, we can revisit the cached mapping approach from
section \ref{sec:mappingWithCaching}.  In figure \ref{fig:shifted}, we
see the wall from section \ref{sec:mappingWithCaching}, texture mapped
using the same caching method after our localization refinement
process.

\begin{figure}
  \centering
  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
  \caption{Localization refinement results in signifcantly fewer
    discontinuities in the final texture.}
  \label{fig:shifted}
\end{figure}

It should be evident that our localization adjustments resulted in a
major improvement. A great strength of our tiling approach for image
selection is that it extracts the areas with good camera angles from
each image, and thus can handle images of all types. As demonstrated
on the floor plane in figure \ref{fig:floor_suboptimal}, we can run
this process even with extremely poor image projections, where the
amount of quality texture for each image is limited. Additionally,
since our plane is discretized, we can handle arbitrarily complex
plane geometry as well.

\begin{figure}
  \centering
  \includegraphics[width=3in]{floor_suboptimal.jpg}
  \caption{The tiling method ensures that only the most optimal
    portions of each image are used. This allows it to successfully
    handle all manner of plane and image geometry, as shown in this
    floor texture.}
  \label{fig:floor_suboptimal}
\end{figure}

Given that the backpack system's hardware and the data collection
process strive for optimal wall texturing however, we can aim for a
less conservative approach when texturing walls, and simply fall back
to this more robust approach as needed.

\subsection{Texture Mapping with Seam Minimization}
\label{sec:seamMinimization}
Since we now have higher confidence in the quality of image
boundaries, we explore an alternate method for texture mapping that
greatly reduces seams in cases where we have an abundance of optimal
images.  The cached tile approach used previously selected images
based on individual and neighboring quality of image selections, in an
effort to reduce seams between tiles. In a more optimal case, as the
backpack system provides for walls, images are all taken from close
distances and have near-rectangular projections and thus less
deviation between scores according to the scoring function in figure
\ref{fig:scoringFunction}. Thus, we can reason that rather than
selecting the set of best images, since all images are near in
quality, we should instead select the best set of images, such that
the selection together results in the cleanest final texture. We will
accomplish this by using entire images where possible, defining a cost
function between images, and seeking to minimize total cost.

\subsection{Occlusion Masking}
\label{sec:occlusionMasking}
Before we proceed with this approach, we need to ensure that our
images contain only content that should be mapped onto the target
plane in question. The tiling approach used previously checked
occlusion for each tile as it was being textured, but we plan on using
entire images, so we need to perform occlusion checks over the
entirety of each image, so we know which areas are available for
texture mapping.

Fortunately, by virtue of our indoor environments, the vast majority
of surface geometry is either horizontal or vertical, with high
amounts of right angles. This means that after masking out occluded
areas, our image projections will remain largely rectangular. We can
thus be efficient by recursively splitting each image into rectangular
pieces, and performing the same occlusion checks used in the tiling
process where needed. To actually occlude out rectangles, we simply
remove their texture, as we will ensure that untextured areas are
never chosen for texture mapping.

\subsection{Inter-Image Cost Functions}
\label{sec:interImageCosts}
In order to objectively decide which set of images results in the
cleanest texture, we need a cost function such that we can evaluate
the visibiilty of seams between images in our set. A straightforward
cost function that accomplishes this is the sum of squared pixel
differences in overlapping regions between all pairs of
images. Minimizing this cost function encourages image boundaries to
occur in featureless areas, such as bare walls, as well as in areas
where images match extremely well.

Another possible cost function is overall edge energy, i.e. the sum of
the smoothed gradient over seams. Minimizing this encourages image
boundaries to be placed in featureless areas even more than the first
cost function. For the results shown throughout this paper, the first
cost function was used, as the regular occurrence of featureless areas
was not guaranteed in our datasets.

\subsection{Image Selection}
\label{sec:imageSelection}
Now that we have a cost function defined, we mechanically select the
set of images for which the overall cost function is minimized. Since
we aim to cover the entirety of our plane, our problem is to minimally
cover a polygon(our plane), using other polygons of arbitrary geometry
(our image projections), with the added constraint of minimizing our
cost function between chosen images. This is a complex problem, though
we can take a number of steps to simplify it. Returning again to the
optimality of our situation when texturing walls, we can make a quick
simplification for the sake of efficiency. Given that our wall-texture
candidate images were all taken from a head-on angle, and assuming
only minor rotations were made during localization refinement, we can
reason that their projections onto the plane are approximately
rectangular. By discarding the minor excess texture and cropping them
all to be rectangular, our problem becomes the conceptually simpler
problem of filling a polygon with rectangles, such that the sum of all
edge costs between each pair of rectangles is minimal. We thus also
retain axis-aligned image boundaries, along with their advantages
explained in section \ref{sec:simpleTextureMapping}.

By taking two more shortcut we can simplify our problem down even
further. Since this approach is already assuming optimal images, we
know it will be applied on walls, which are the focus of the backpack
modeling system. For wall planes, which are nearly always rectangular,
care is taken so that images contain the entirety of their
floor-to-ceiling range, and thus we do not have wall images such that
one should be projected vertically above the other. In essence, we
need only to ensure horizontal coverage of our planes, as our images
provide full vertical coverage themselves. We can thus construct a
Directed Acyclic Graph (DAG) from the images, with edge costs defined
by our cost function above, and solve a simple shortest path problem
to find an optimal subset of images with regard to the cost functions.

\begin{figure}
  \centering
  \includegraphics[width=3in]{dagCreation.pdf}
  \caption{DAG construction for the image selection process.}
  \label{fig:dagCreation}
\end{figure}

Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
from overlapping images of a long hallway. Images are sorted by
horizontal location left to right, and become nodes in a
graph. Directed edges are placed in the graph from left to right
between images that overlap. The weights of these edges are determined
by the cost functions discussed previously. Next, we add two
artificial nodes, one start node representing the left border of the
plane, and one end node representing the right border of the
plane. The left artificial node has directed edges with equal cost
$C_0$ to all images that meet the left border of the plane, and the
right artificial node has directed edges from all images with that
meet the right border of the plane, with equal cost $C_0$ as well.

We now solve the standard shortest path problem from the start node to
the end node. This provides a set of images that completely covers the
plane horizontally, while minimizing the cost of the seams between
images.

In rare cases where the vertical dimension of the plane is not
entirely covered by a chosen image, we are left with a hole where no
image was chosen to texture. Rather than reverting to a 2D-coverage
problem, we can elect to simply fill the hole by selecting images to
fill it in a greedy fashion with respect to edge costs of the same
cost function.

With this completed, we have now mapped every location on our plane to
at least one image, and have minimized the amount of images, as well
as the discontinuity between their borders. In the next section, we
will apply blending between images where they overlap, but for the
sake of comparison with the unblended tile caching method in section
\ref{sec:mappingWithCaching}, we arbitrarily pick one image for
texturing where images overlap. Figure \ref{fig:compare_unblended}
compares the tile caching method against this seam minimization
method.

\begin{figure}
  \centering
  \includegraphics[width=3in]{wall1_cache_full_shifted.jpg}
  \includegraphics[width=3in]{wall1_dynprog_noblend.jpg}
  \caption{The tile caching approach is presented above the seam
    minimization approach.}
  \label{fig:compare_unblended}
\end{figure}

Though both methods provide quite accurate texturing thanks to the
localization refinement process, the seam minimization approach
results in fewer visible discontinuities, since it directly reduces
the cost of each image boundary, while the tile caching method uses a
scoring function that only approximates this effect. Furthermore, seam
minimization guarantees the best selection of images, while the tile
caching method may select images early on that turn out to be poor
choices once subsequent tiles have been processed.

In the context of the backpack modeling system, we apply the seam
minimization approach on walls, due to its superior output when
provided with optimal images. Floors and ceilings however, given their
suboptimal images, as shown in figure \ref{fig:floor_suboptimal}, can
only be textured using the tile caching method.

\subsection{Blending}
\label{sec:blending}
Until now, blending of images has not been used, for the sake of clear
comparisons between texturing methods. We will now apply the same
blending process on our two final texturing methods: localization
refinement followed by either tile caching or seam minimization.

Although our preprocessing steps and image selections in either method
attempt to minimize all mismatches between images, there are cases,
where due to different lighting conditions or inaccuracies in geometry
or projection, where we simply have unavoidable discontinuities. These
can however be treated and smoothed over by applying alpha blending
over image seams.  Whether the units we are blending are
rectangularly-cropped images or rectangular tiles, we can apply the
same blending procedure, as long as we have a guaranteed overlap
between units to blend over.

For the tile caching method, we can ensure overlap by texturing a
larger tile than we really have. For example, for a tile $l_1 x l_1$
in size, we can make sure to associate it with a texture $(l_1 + l_2)
x (l_1 + l_2)$ in size. For the seam minimization method, we have
already ensured overlap between images. To enforce consistent blending
however, it is beneficial to add a required overlap distance while
solving the shortest path problem in section
\ref{sec:imageSelection}. If images do not overlap in a region at
least the length of this overlap distance, we do not consider them to
overlap at all. If images overlap in a region greater than the overlap
distance, we will only apply blending over an area equal to the
overlap distance.

Our alpha blending technique is widely used, and blends pixels
linearly across overlapping regions. For each pixel within such a
region, we simply scale its intensity (by a factor from 0 to 1), based
on its distance from the image's border, with a cap set at a fixed
distance from the border. In this way, we interpolate between two
overlapping images, providing a gradual transition between them. Our
texture mapping process is now complete, and in figure
\ref{fig:pipeline}, we review our entire pipeline and demonstrate the
final blended output of both approaches.

\begin{figure}
  \centering
  \includegraphics[width=3in]{pipeline.pdf}
  \caption{Our final texture processing pipeline, with the final
    output of both approaches.}
  \label{fig:pipeline}
\end{figure}

\section{Results and Conclusions}
\label{sec:resultsAndConclusions}
In this paper, we have shown how to accurately texture map models,
even when provided with imprecise camera localization data. We were
able to refine image locations based on feature mapping, and robustly
handle outliers.  We generalized one approach to texture mapping to
any manner of planes and images, and successfully textured both simple
rectangular walls as well as complex floor and ceiling geometry. We
also presented an optimized texturing method that takes advantage of
our localization refinement process and produces cleaner textures on
planes where multiple head-on images are available. Each of these
approaches is highly modular, and easily tunable for different
environments and acquisition hardware.

Ceilings and floors textured with the robust approach, and walls
textured with the optimized approach, are displayed in figure
\ref{fig:results}. A more detailed walkthrough demonstrating fully
textured 3D models using the approaches in this paper is available in
the accompanying video to this paper.

\begin{figure}
  \centering
  \includegraphics[width=3in]{4thfloor21.jpg}
  \includegraphics[width=3in]{4thfloor61.jpg}
  \includegraphics[width=2in]{4thfloor8.jpg}
  \includegraphics[width=3in]{fullmodel.png}
  \caption{Examples of our final texture mapping output for walls,
    floors, and ceilings}
  \label{fig:results}
\end{figure}

{\small \bibliographystyle{ieee} \bibliography{egbib} }

\end{document}

### 2014-01-04 spie2013/assets/template/_region_.tex
organize stuff

--- 2013-05-02 masters/body/assets/3dimpvt/template/egpaper_for_review.tex
@@
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\message{ !name(egpaper_for_review.tex)}\documentclass[10pt,twocolumn,letterpaper]{article}
 
@@
 
+\message{ !name(egpaper_for_review.tex) !offset(-3) }
+
 %%%%%%%%% TITLE
@@
 \begin{abstract}
-  abcd The ABSTRACT is to be in fully-justified italicized text, at the top
+  The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
@@
 
+\message{ !name(egpaper_for_review.tex) !offset(-5) }
+
 \end{document}

### 2014-01-04 spie2013/paper.tex
organize stuff

--- 2013-12-29 acivs/fullacivs.tex
@@
-% This is LLNCS.DEM the demonstration file of
-% the LaTeX macro package from Springer-Verlag
-% for Lecture Notes in Computer Science,
-% version 2.4 for LaTeX2e as of 16. April 2010
-%
-\documentclass{llncs}
-\usepackage{cite}
+%  article.tex (Version 3.3, released 19 January 2008)
+%  Article to demonstrate format for SPIE Proceedings
+%  Special instructions are included in this file after the
+%  symbol %>>>>
+%  Numerous commands are commented out, but included to show how
+%  to effect various options, e.g., to print page numbers, etc.
+%  This LaTeX source file is composed for LaTeX2e.
+
+%  The following commands have been added in the SPIE class 
+%  file (spie.cls) and will not be understood in other classes:
+%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
+%  The bibliography style file is called spiebib.bst, 
+%  which replaces the standard style unstr.bst.
+
+\documentclass[]{spie}  %>>> use for US letter paper
+%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
+%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
+%% \addtolength{\voffset}{9mm}   %>>> moves text field down
+%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing 
+%  The following command loads a graphics package to include images 
+%  in the document. It may be necessary to specify a DVI driver option,
+%  e.g., [dvips], but that may be inappropriate for some LaTeX 
+%  installations. 
 \usepackage{graphicx}
@@
 
-\author{Peter Cheng \and Michael Anderson \and Stewart He \and Avideh Zakhor}
-\institute{University of California, Berkeley\\ Berkeley CA 94720, USA}
+\author{Peter Cheng, Michael Anderson, Stewart He, and Avideh Zakhor
+\skiplinehalf
+University of California, Berkeley\\
+}
 
@@
   even in the presence of inaccurate surface geometry and noisy camera
-  poses. Images are then composited into a final texture mosaic. The
-  effectiveness of the proposed method is demonstrated on a number of
-  different indoor environments.
-
-  \keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}
+  poses. The final step is to select and composite images into a
+  texture mosaic. The effectiveness of the proposed method is
+  demonstrated on a number of different indoor environments.
 \end{abstract}
@@
 % >>>> Include a list of keywords after the abstract
+
+\keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}
 
@@
 reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is known as the simultaneous localization and
-mapping (SLAM) problem, and is generally solved by taking readings
-from laser range scanners, cameras, and inertial measurement units
-(IMUs) at multiple locations within the environment. Mounting such
-devices on a platform carried by an ambulatory human provides unique
-advantages over vehicular-based systems on wheels in terms of agility
-and portability, but can also result in larger localization error
-\cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results.
+\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
+known as the simultaneous localization and mapping (SLAM) problem, and
+is generally solved by taking readings from laser range scanners,
+cameras, and inertial measurement units (IMUs) at multiple locations
+within the environment. Mounting such devices on a platform carried by
+an ambulatory human provides unique advantages over vehicular-based
+systems on wheels in terms of agility and portability, but can also
+result in larger localization error \cite{liu2010indoor}. As a result,
+common methods for texture mapping generally produce poor results.
 
@@
   \centering
-  \includegraphics[width=4.5in]{flowchart.jpg}
+  \includegraphics[width=6in]{flowchart.jpg}
   \caption{The proposed texture mapping procedure\\}
@@
   \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 20cm 0cm,
-    clip=true, width=4.8in, height=0.7in]{graphApproach.jpg}}
+    clip=true, width=6in, height=0.7in]{graphApproach.jpg}}
 
   \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 15cm 0cm,
-    clip=true, width=4.8in, height=0.7in]{autostitchResult.jpg}}
+    clip=true, width=6in, height=0.7in]{autostitchResult.jpg}}
 
   \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 75cm 0cm,
-    clip=true, width=4.8in, height=0.7in]{finalLong.jpg}}
+    clip=true, width=6in, height=0.7in]{finalLong.jpg}}
 
@@
     \centering
-    \includegraphics[height=1.2in,width=2in]{Projection.pdf}
+    \includegraphics[height=1.8in]{Projection.pdf}
     \caption{Surfaces to be textured are specified in 3D space by
@@
     \centering
-    \includegraphics[height=1.2in, width=2in]{scoringFunction.jpg}
+    \includegraphics[height=1.8in]{scoringFunction.jpg}
     \caption{We minimize camera angle $\alpha$ and distance $d$ by
@@
 \begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=2.4in,
-    height=0.8in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=2.4in,
-    height=0.8in]{wall2_naive_shift.jpg}}
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_naive.jpg}}
+  \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_naive_shift.jpg}}
 
-  \centering \subfloat[][]{\includegraphics[width=2.4in,
-    height=0.8in]{wall2_cache_shift.jpg}}
-  \subfloat[][]{\includegraphics[width=2.4in,
-    height=0.8in]{wall2_shortest_shift.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_cache_shift.jpg}}
+  \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_shortest_shift.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=2.4in,
-    height=0.8in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=2.4in,
-    height=0.8in]{wall2_shortest_shift_blend.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_cache_shift_blend.pdf}}
+  \subfloat[][]{\includegraphics[width=3.4in,
+    height=1.2in]{wall2_shortest_shift_blend.pdf}}
 
-  \centering \subfloat[][]{\includegraphics[width=2.4in,
-    height=2.2in]{wall2_cache_comparison.png}}
-  \subfloat[][]{\includegraphics[width=2.4in,
-    height=2.2in]{wall2_shortest_comparison.png}}
+  \centering \subfloat[][]{\includegraphics[width=3.4in,
+    height=3.4in]{wall2_cache_comparison.png}}
+  \subfloat[][]{\includegraphics[width=3.4in,
+    height=3.4in]{wall2_shortest_comparison.png}}
 
@@
     image alignment; (c) Tile-based texturing after image alignment
-    with caching; (d) Shortest path texturing after image alignment;
-    (e,f) Blending applied to (c) and (d); (g,h) Zoomed in views of
-    discontinuities in (e) vs. in (f).}
+    with caching; (d) Shortest path texturing after image
+    alignment; (e,f) Blending applied to (c) and (d); (g,h) Zoomed
+    in views of discontinuities in (e) vs. in (f).}
   \label{fig:compareAll}
@@
   \centering
-  \subfloat[][]{\includegraphics[width=4.8in]{allunshifted.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=4.8in]{allshifted.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
 
   \centering \subfloat[][]{\includegraphics[trim=0cm 2cm 0cm 0cm,
-    clip=true, width=4.8in]{matchLines.jpg}}
+    clip=true, width=5in]{matchLines.jpg}}
 
@@
   \begin{tabular}{cc}
-    \subfloat[][]{\raisebox{-0.8in}{\includegraphics[width=2.4in]{occlusiondiagram.png}}} &
+    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{occlusiondiagram.png}}} &
 
@@
     \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
-      clip=true, width=2.4in,
+      clip=true, width=3in,
       height=0.9in]{occlusionimagebad.png}} \\
     \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
-      clip=true, width=2.4in,
+      clip=true, width=3in,
       height=0.9in]{occlusionimagegood.png}}
@@
   \subfloat[][]{\includegraphics[width=1in]{projectionWall.pdf}}
-  \hspace{0.4in} \centering
+  \hspace{1in} \centering
   \subfloat[][]{\includegraphics[width=1.1in]{projectionCeiling.pdf}}
-  \centering \hspace{0.4in}
+  \centering \hspace{1in}
   \subfloat[][]{\includegraphics[width=0.9in]{projectionWallCrop.pdf}}
@@
   \centering
-  \includegraphics[width=4.8in]{dagCreation.pdf}
+  \includegraphics[width=5in]{dagCreation.pdf}
   \caption{DAG construction for the image selection process. \\}
@@
 evident when comparing the posters in the images. This shortest path
-approach approach directly reduces the cost of each image boundary,
+approach directly reduces the cost of each image boundary,
 while the tile caching method uses a scoring function that only
@@
   \centering
-  \subfloat[][]{\includegraphics[width=2.4in]{finalfloors.jpg}} ~~~~~~~~
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}} ~~~~~~~~
   \centering
-  \subfloat[][]{\includegraphics[width=2.4in]{finalceilings.jpg}}
+  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}}
 
   \centering \subfloat[][]{
-    \includegraphics[height=2in, width=2.3in]{floorcropped.jpg} ~~~~~~~~
-    \includegraphics[width=2.3in]{pier15floor.jpg}
+    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
+    \includegraphics[width=3in]{pier15floor.jpg}
   }
@@
   \centering{
-    \includegraphics[width=2.3in]{fullmodel.png}
-    \includegraphics[width=2.3in]{pier15.png} \\
-    \includegraphics[width=2.3in]{threestoryfull2.png}
-    \includegraphics[width=2.3in]{threestoryfull.png}
+    \includegraphics[width=3in]{fullmodel.png}
+    \includegraphics[width=3in]{pier15.png} \\
+    \includegraphics[width=3in]{threestoryfull2.png}
+    \includegraphics[width=3in]{threestoryfull.png}
   }

### 2014-01-04 spie2014/_region_.tex
organize stuff

--- 2014-01-04 spie2014/spie2014.tex
@@
+\message{ !name(spie2014.tex)}\documentclass[]{spie}  %>>> use for US letter paper
+
+\usepackage{graphicx}
+\usepackage{subfig}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{hyperref}
+\usepackage{float}
+\usepackage{multirow}
+
+\title{Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses}
+
+\author{Peter Cheng\supit{a}, Michael Anderson\supit{a}, Stewart He\supit{b}, and Avideh Zakhor\supit{a}
+\skiplinehalf
+\supit{a}University of California, Berkeley; \\
+\supit{b}University of California, Davis
+}
+
+\begin{document}
+
+\message{ !name(spie2014.tex) !offset(-21) }
 \documentclass[]{spie}  %>>> use for US letter paper
@@
 
-\begin{document}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\begin{abstract}
-  Automated 3D modeling of building interiors is used in applications
-  such as virtual reality and environment mapping. Texturing these
-  models allows for photo-realistic visualizations of the data
-  collected by such modeling systems. While data acquisition times for
-  mobile mapping systems are considerably shorter than for static
-  ones, their recovered camera poses often suffer from inaccuracies,
-  resulting in visible discontinuities when successive images are
-  projected onto a surface for texturing. We present a method for
-  texture mapping models of indoor environments that starts by
-  selecting images whose camera poses are well-aligned in two
-  dimensions. We then align images to geometry as well as to each
-  other, producing visually consistent textures even in the presence
-  of inaccurate surface geometry and noisy camera poses. Images are
-  then composited into a final texture mosaic and projected onto
-  surface geometry for visualization. The effectiveness of the
-  proposed method is demonstrated on a number of different indoor
-  environments.
-\end{abstract}
-
-% >>>> Include a list of keywords after the abstract
-
-\keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:introduction} % \label{} allows reference to this section
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and
-consequently automated 3D site modeling has garnered much interest in
-recent years.
-
-The first step in automated 3D modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-recover its pose within an environment while simultaneously
-reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
-known as the simultaneous localization and mapping (SLAM) problem, and
-is generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment. Mounting such devices on a platform carried by
-an ambulatory human provides unique advantages over static or
-vehicular-based systems on wheels in terms of agility and portability,
-but can also result in larger localization error
-\cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results. In this paper, we present an approach
-to texture mapping 3D models of indoor environments in the presence of
-uncertainty and noise in camera poses. In particular, we consider data
-obtained from a human-operated backpack system, detailed in Section
-\ref{sec:dataAcquisition}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=6.2in]{flowchart2.jpg}
-  \caption{The proposed texture mapping procedure\\}
-  \label{fig:flowchart}
-\end{figure}
-
-The overall block diagram for the proposed texture mapping procedure
-is shown in Figure \ref{fig:flowchart}, where the number attached to
-each box indicates the section in which the concept in the box is
-explained in this paper. First, the geometry of an environment is
-split into regions, each of which will be textured independently and
-in parallel. For each region, we begin by selecting a set of images
-that spans the entire region's surface with high resolution
-imagery. We then use recovered noisy camera poses to project these
-selected images onto the surface. These projections are rotated and
-translated in 2D, in order to maximally align them with the surface's
-geometry, as well as to each other, allowing us to handle both errors
-in geometry as well as camera poses. Finally, we demonstrate a
-tile-based as well as a shortest-path-based approach for compositing
-images, where the latter produces superior textures, but is only
-applicable for surfaces with optimal camera poses and lateral image
-coverage.
-
-The remainder of the paper is organized as follows. Section
-\ref{sec:dataAcquisition} provides background on the data acquisition
-system and describes a region segmentation procedure. Section
-\ref{sec:relatedWork} covers existing approaches to image stitching,
-and their performance on our datasets. Section
-\ref{sec:imageSelection} explains how to downsample the set of
-available images by selecting those with the best orientation and
-distance from surfaces under consideration. Section
-\ref{sec:2dAlignment} contains the proposed approach towards 2D image
-alignment, followed by Section \ref{sec:imageCompositing}, which
-describes two methods of selecting and compositing images to create
-the final texture. Sections \ref{sec:results} and \ref{sec:conclusion}
-contain results and conclusions.
-
-\section{Data Acquisition}
-\label{sec:dataAcquisition}
-
-This section contains background information describing the
-backpack-mounted system and its operation. The hardware and operation
-of the backpack system, as well as the postprocessing of acquired
-data, play an important role in motivating the approaches described in
-this paper. The following two sections will focus on image and raw
-data acquisition, and a method of partitioning recovered environment
-geometry, respectively.
-
-\subsection{Acquisition Hardware}
-
-The backpack system used in this paper has a number of laser range
-scanners as well as side-facing cameras taking photos at a rate of 5
-Hz \cite{liu2010indoor}. In order to collect data, an operator wears
-the backpack system and traverses the environment to be scanned,
-walking in straight lines at a standard pace and making an effort to
-walk parallel to all walls in the area. Multiple localization and
-loop-closure algorithms are then applied to the raw data collected by
-the onboard sensors \cite{chen2010indoor, kua2012loopclosure,
-  liu2010indoor}, and the backpack is localized\footnote{In this
-  paper, we use the terms localization and pose recovery
-  interchangeably, in that they both refer to recovering position and
-  orientation.}  over its data collection period. This involves
-recovering the 6 degrees of freedom for the backpack itself as well as
-the cameras rigidly mounted on it. These results are noisy, which
-motivates the approaches in this paper. Once this is complete, the
-data from the laser range scanners is used to generate a 3D point
-cloud of the surrounding environment. This point cloud is used to
-construct simple, coarse models \cite{sanchez2012point,
-  turnerfloorplan}, as well as highly detailed models
-\cite{turnerwatertight}.  Regardless of resolution or size,
-the model, consisting of geometric surfaces in 3D space, along with
-the set of images captured by the backpack's cameras and their noisy
-3D poses, are the input to the texture mapping problem.
-
-\subsection{Geometry Partitioning}
-\label{sec:geometryPartitioning}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=1.5in]{geomdeskwire_crop.png}}
-  \hspace{0.5in}
-  \subfloat[][]{\includegraphics[width=1.5in]{geomdeskregions_crop.png}}
-  \hspace{0.5in}
-  \subfloat[][]{\includegraphics[width=1.5in]{geomdesktexturetris_crop.png}}
-  \caption{(a) Part of a model representing a desk and miscellaneous
-    objects on top of the desk. (b) Triangles grouped into regions for
-    texturing. (c) Final textured output.}
-  \label{fig:deskGeom}
-\end{figure}
-
-In order to effectively texture a 3D model, we first divide the model
-into a set of regions, each to be textured independently. The purpose
-of this is to ensure texture continuity along large uniform areas,
-while allowing texture boundaries to fall along natural environmental
-boundaries. Because textures may not match at such boundaries where
-two regions meet, it is important to minimize the visibility of
-boundaries. This is done by encouraging region boundaries to occur at
-sharp corners in the model geometry, where texture continuity is not
-important. For instance, in Figure \ref{fig:deskGeom}(a), each side of
-the desk, objects on top of the desk, and the wall behind, should be
-textured separately. This is done by grouping the triangles comprising
-each such area into separate regions. Region grouping is performed by
-first designating all contiguous coplanar groups of triangles as
-different regions. Any regions that are less than $1 m^2$ in size are
-then repeatedly joined to their largest neighboring regions, as long
-as the angle between them is under $90^{\circ}$. An example of such a
-grouping is shown in Figure \ref{fig:deskGeom}(b). The same area with
-textures successfully applied to each region is shown in Figure
-\ref{fig:deskGeom}(c).
-
-For the purposes of texturing, it is convenient to treat each region
-as planar. To accomplish this, a plane is fitted to each region. This
-plane corresponds to the largest contiguous section of coplanar
-triangles, as most regions are characterized by small outcroppings
-from a largely planar surface, such as objects on a table or features
-protruding from a wall. The 3D surface composing a region is then
-projected onto its calculated plane, and the resulting 2D planar
-polygon is used as the texturing surface. This 2D planar approximation
-provides a simple, yet approximately accurate surface onto which
-images can be projected in order to generate textures. However, 3D
-surfaces are still retained in order to achieve accurate results when
-performing occlusion checks, and of course are used to generate the
-final textured model. Each region now has a set of triangles
-representing the original model geometry, as well as a planar
-approximation. The task now is to generate a texture for each region.
-
-\section{Related Work}
-\label{sec:relatedWork}
-
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 20cm 0cm,
-    clip=true, width=6in, height=0.7in]{graphApproach.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 15cm 0cm,
-    clip=true, width=6in, height=0.7in]{autostitchResult.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 75cm 0cm,
-    clip=true, width=6in, height=0.7in]{finalLong.jpg}}
-
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm, (b) the AutoStitch software package, and (c)
-    the proposed method.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-There are many existing approaches to stitching together multiple
-images to produce a larger, seamless image \cite{szeliski2006image,
-  agarwalapanoramas, wangmultipleviews, coorg1997matching,
-  debevechybrid, bernardinimultiplescans}. Generally, parts of images
-are matched to each other, by detecting feature points and identifying
-matches. Images are then transformed to maximizally align matches,
-often by computing homographies between pairs of images, or by
-iteratively adjusting camera poses in 1 to 6 degrees of freedom.
-
-Feature matching works best when unique visual references exist in the
-environment that can be detected in multiple images. Unfortunately,
-many indoor environments have a high prevalence of bare surfaces as
-well as repeating textures, such as with windows and
-doors. Additionally, our datasets often contain long 1-dimensional
-chains of images, such as in Figure \ref{fig:mosaic3D}, which often
-leads to error accumulation. For example, when matching a long chain
-of images via homography matrices, a pixel in the $nth$ image must be
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Errors in each of these
-homography matrices is propagated to all further images, resulting in
-drift.
-
-Two methods based on feature matching and homography calculation are
-shown in Figure \ref{fig:mosaic3D}. Figure \ref{fig:mosaic3D}(a)
-depicts an attempt at integrating image stitching with the iterative
-global localization algorithm used to localize the backpack system
-detailed in Section \ref{sec:dataAcquisition}
-\cite{liu2010indoor}. Figure \ref{fig:mosaic3D}(b) depicts an output
-image from AutoStitch, which is software based on research in the
-related area of panorama generation \cite{panorama2d,
-  autostitch}. Both methods were thoroughly tuned for the shown
-example, but due to the factors mentioned in the previous paragraph,
-they still show significant amounts of drift and distortion, as well
-as loss of alignment to the environment geometry.
-
-\section{Image Selection}
-\label{sec:imageSelection}
-
-The geometry of the texture mapping process for a region, as described
-in Section \ref{sec:geometryPartitioning}, is shown in Figure
-\ref{fig:projection}. Given a set of images to texture a target
-surface, camera matrix $P_i$ for the $i$th image transforms a 3D point
-in the world coordinate system to a 2D point or pixel in image $i$'s
-coordinates. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, containing focal length and image center, as
-well as extrinsic parameters which specify the rotation and
-translation of the camera's position in 3D world coordinates at the
-time that image $i$ was taken. These extrinsic parameters are
-determined by the backpack hardware and the corresponding localization
-algorithms \cite{chen2010indoor, liu2010indoor, kua2012loopclosure}
-and are noisy.
-
-Since the backpack system takes pictures at a rate of 5 Hz, thousands
-of images are available for texturing each surface in the 3D
-model. Our objective in designing a texture mapping process is to
-determine which of these images should be used, and where their
-contents should map onto the final texture, in order to minimize any
-visual discontinuities or seams that would suggest that the plane's
-texture is not composed of a single continuous image. In the remainder
-of this section, we propose an image subsampling procedure to obtain a
-set of images for use in all further steps.
-
-\begin{figure}
-  \begin{minipage}[b]{0.45\linewidth}
-    \centering
-    \includegraphics[height=1.5in]{Projection.pdf}
-    \caption{Images are related to each surface through the camera
-      matrices $P_{1..m}$. }
-    \label{fig:projection}
-  \end{minipage}
-  \hspace{0.5cm}
-  \begin{minipage}[b]{0.45\linewidth}
-    \centering
-    \includegraphics[height=1.5in]{scoringFunction.jpg}
-    \caption{Camera angle $\alpha$ and distance $d$ are minimized by
-      maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-      \cdot \vec{n}$}
-    \label{fig:scoringFunction}
-  \end{minipage}
-\end{figure}
-
-Our criteria for image subsampling has the following
-stipulations. First, we want a set of images such that their
-projections together cover up the entirety of our target surface, so
-as to avoid holes in the final texture. Second, we desire our final
-texture to have high resolution throughout; thus every location on the
-target surface should have at least one image that contains high
-resolution imagery for it. A straightforward way to accomplish these
-goals is to discretize the target surface into small square tiles, and
-for each tile, select the image that has the best viewing angle and
-resolution for texturing that tile. In order to select the image that
-can best texture a tile $t$, we first gather a list of candidate
-images that contain all four of its corners; we can rapidly check this
-by projecting $t$ into each image using the $P_i$ camera
-matrices. Furthermore, each candidate image must have been taken at a
-time when its camera had a clear line-of-sight to $t$, which can be
-determined using standard ray-polygon intersection tests between the
-camera location, $t$, and every other surface, or via the k-d tree
-from Section \ref{sec:geometryPartitioning} if present
-\cite{rayintersection}.
-
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image for texturing
-$t$. Since resolution decreases and camera pose errors become more
-pronounced with distance, we wish to minimize the distance between
-cameras and the surfaces they texture. Additionally, we desire images
-that are projected perpendicularly, rather than obliquely, onto the
-plane, maximizing the resolution and amount of useful texture
-available in their projections, as well as minimizing any parallax
-effects due to real-world geometry not accurately represented by the
-digital 3D model. In other words, we wish to minimize the angle
-between the tile's normal vector and the camera axis for images
-selected for texturing that tile. These two criteria can be met by
-maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
-as shown in Figure \ref{fig:scoringFunction}, where $d$ is the
-distance between the centers of a camera and a tile, and $\vec{n}$ and
-$\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively.
-
-When the images selected for each tile are used directly to texture
-their respective tiles, image boundaries with abrupt discontinuities
-between tiles are visible, as shown in Figure
-\ref{fig:compareAll}(a). While it is clear that camera pose
-inaccuracies are too severe for such a simple approach to work, the
-selected images all appear to contain optimal camera angles with high
-resolution, and much of their misalignment appears reconcilable using
-2D transforms. This procedure generally selects around 10\% of the
-possible images that could be used for texturing a surface, and not
-only reduces the computational complexity of the remaining steps, but
-also selects the most promising images for the remaining steps.
-
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_naive_shift.jpg}}
-  \subfloat[][]{\includegraphics[trim=1.2cm 0cm 0cm 0cm,
-        clip=true,width=0.33\textwidth,
-    height=0.8in]{wall2_cache_shift.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_shortest_shift.pdf}}
-  \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_shortest_shift_blend.pdf}}
-
-  \caption{(a) Tile-based texturing; (b) Tile-based texturing after
-    image alignment; (c) Tile-based texturing after image alignment
-    with caching; (d) Shortest path texturing after image alignment;
-    (e,f) Blending applied to (c) and (d).}
-  \label{fig:compareAll}
-\end{figure}
-
-\section{2D Image Alignment}
-\label{sec:2dAlignment}
-In this section, we describe our method for efficient and robust image
-alignment. Rather than register all of our images in 3D, as many
-state-of-the-art techniques for image stitching do, we instead align a
-subset of images in 2D; this subset corresponds to the images selected
-by the image selection procedure described in Section
-\ref{sec:imageSelection}.
-
-Applying 2D alignments to this set of images works well for the
-following reasons. First, the nature of our input data and the
-selected images is such that localization error chiefly occurs in two
-dimensions, which correspond to the plane of most surfaces being
-projected onto. This is because the backpack operator, while scanning
-an environment, generally walks parallel to walls. Furthermore, the
-backpack system maintains a consistent distance from floors and
-ceilings during data collection. As a result, the translational error
-of camera poses is quite minimal in dimensions perpendicular to walls,
-ceilings and floors, which comprise the majority of surfaces being
-textured.
-
-Our proposed 2D alignment procedure consists of three parts, as shown
-in the diagram in Figure \ref{fig:flowchart}. First, images are
-projected onto the surface and lines within these projected images are
-detected. Images are then transformed such that these lines match
-geometric lines composing the boundaries of the surface being
-textured. Second, occlusion checks are performed to remove invalid
-parts of each image for the target surface. Third, SIFT feature
-matches are detected between pairs of images, and a weighted linear
-least squares problem is solved in order to maximize all image and
-geometry-based alignments.
-
-\subsection{Geometry-based Alignment}
-\label{sec:geometryAlignment}
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-    \begin{tabular}{c}
-      \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
-        clip=true, width=3in,
-        height=0.9in]{allunshifted.jpg}} \\
-      \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
-        clip=true, width=3in,
-        height=0.9in]{allshifted.jpg}}
-    \end{tabular} &
-    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{matchLines.jpg}}} 
-  \end{tabular}
-  \caption{Images projected onto a ceiling surface, where
-    geometry-based lines corresponding to the ceiling's boundary are
-    shown in red. Image-based lines detected by Hough transform in the
-    image projections are shown in blue; (a) images projected with
-    their original noisy camera poses; (b) after image alignment to
-    maximize line matches between images and geometry; (c) examples of
-    matching lines in cases with $\geq$ 2 line pairs, 1 line pair, and
-    zero line pairs, from top to bottom.}
-  \label{fig:geometryAlignment}
-\end{figure}
-
-After computing each image's projection onto the target surface, as
-described in Section \ref{sec:imageSelection}, we can obtain a set of
-image-based line segments by using Hough transforms to detect lines in
-the image projections. We also gather a set of geometry-based lines,
-which correspond to the lines comprising the target surface's border,
-as well as lines formed where other surfaces intersect the target
-surface. An example of these lines is shown in red for a ceiling
-surface in Figure \ref{fig:geometryAlignment}(a). Given perfect camera
-poses and surface geometry, the lines in images corresponding to
-corners between surfaces should match up exactly with corners in the
-3D model. By inducing such lines to match, we can fit camera poses
-more accurately to the surface, and therefore to each other as well.
-
-To align images to surface geometry, we collect pairs of image-based
-and geometry-based line segments, which are within distance and
-angular thresholds of each other. We have found a distance threshold
-of 250 mm and an angular difference threshold of $10^\circ$ to work
-well for our datasets. For each pair of lines, we compute the angular
-difference between the pair's image and geometry lines. If there are 2
-or more pairs with angular differences within $1^\circ$, we select the
-two pairs with the longest noncollinear image-based lines, and rotate
-the image such that the lines in the pair with the longest image-based
-line become parallel. We then find a translation such that the lines
-in that same pair overlap. This translation has ambiguity in the
-dimension along the matched lines, which is resolved by matching the
-midpoint of the image-based line in the second pair to its
-corresponding geometry-based line. This is shown in case (1) of Figure
-\ref{fig:geometryAlignment}(c). Thus, with 2 or more pairs, it is
-possible to obtain a fixed rotation and translation for geometry
-alignment, which are saved for usage in Section
-\ref{sec:robustSIFTFeatureMatching}.
-
-If there are not 2 or more pairs with similar angular differences, we
-select the pair with the longest image-based line, which corresponds
-to a strong linear visual feature, and apply a rotation and the
-minimal translation to match the pair's lines. This translation's
-ambiguity however, can not be resolved, but is also saved to be used
-in Section \ref{sec:robustSIFTFeatureMatching}. This is shown in case
-(2) of Figure \ref{fig:geometryAlignment}(c). Finally, in the case
-where there are no line pairs, we can still rotate images in order to
-exploit patterns in indoor environments, as shown in case (3) of
-Figure \ref{fig:geometryAlignment}(c). For instance, doors, windows,
-furniture, ceiling lights, etc. tend to have linear edges that are
-parallel to the edges of the surfaces they are on. Thus, we choose to
-minimize the angle between image-based lines and geometry-based lines
-regardless of distance. We use the RANSAC framework to compute a
-rotation angle that best accomplishes this while ignoring
-outliers. \cite{fischler1981random}.
-
-After these steps, image projections line up well with target
-surfaces, as shown in Figure \ref{fig:geometryAlignment}(b), which is
-considerably more aligned than Figure
-\ref{fig:geometryAlignment}(a). This procedure reconciles both errors
-in camera poses as well as in geometry, and results in sharp,
-continuous borders across images, which is crucial when checking for
-occlusion.
-
-\subsection{Image Occlusion}
-\label{sec:imageOcclusion}
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{occlusiondiagram.png}}} &
-
-  \begin{tabular}{c}
-    \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
-      clip=true, width=3in,
-      height=0.9in]{occlusionimagebad.png}} \\
-    \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
-      clip=true, width=3in,
-      height=0.9in]{occlusionimagegood.png}}
-  \end{tabular}
-\end{tabular}
-\caption{(a) The image from the camera in this diagram contains
-  texture that belongs to the gray occluding surface, which should not
-  be projected onto the orange target surface; (b) without geometry
-  alignment, texture to the left of the red line would be removed,
-  which would leave some erroneous texture projected onto our target
-  surface; (c) after geometry alignment, the image is shifted,
-  resulting in the correct amount of texture being removed.}
-\label{fig:occlusion}
-\end{figure}
-
-In order to correctly texture surfaces, it is important to detect and
-remove parts of image projections containing texture for occluding
-surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
-used to texture the orange target surface also contains part of a gray
-occluding surface. We remove this incorrect texture by performing
-ray-polygon intersection tests between the camera location and every
-surface in our model except the target surface
-\cite{rayintersection}. If using planar approximations for regions, as
-explained in Section \ref{sec:geometryPartitioning}, the k-d tree is
-used instead. These intersection tests are performed repeatedly in a
-recursive grid, until all occlusions are detected and corresponding
-occluded texture is removed. Occlusion checking works entirely with
-geometry, so by ensuring that images match geometry using
-\ref{sec:geometryAlignment}'s alignment procedure, texture belonging
-to other surfaces is accurately removed, as seen in Figure
-\ref{fig:occlusion}(b) vs. \ref{fig:occlusion}(c).
-
-\subsection{2D Feature Alignment}
-\label{sec:robustSIFTFeatureMatching}
-The next step is to align the selected images from Section
-\ref{sec:imageSelection} for each surface to each other by searching
-for corresponding feature points between all pairs of overlapping
-images. We use feature alignment rather than pixel or intensity-based
-alignment due to the differences in lighting as well as possible
-occlusion among images, both of which feature alignment is less
-sensitive to \cite{lowe1999object, mikolajczyk2005performance,
-  szeliski2006image}. We use SiftGPU \cite{siftgpu} for its high
-performance on both feature detection as well as pairwise
-matching. These matches determine $dx$ and $dy$ distances between each
-pair of features for two image projections, though these distances may
-not always be the same for different features. Since indoor
-environments often contain repetitive features such as floor tiles or
-doors, we need to ensure that SIFT-based distances are
-reliable. First, we only align parts of images that overlap given the
-original noisy poses. Second, we discard feature matches that
-correspond to an image distance greater than 200 mm from what the
-noisy poses estimate. RANSAC \cite{fischler1981random} is then used to
-obtain a consensus from the the remaining feature matches.
-
-We now use the feature-based distances between each pair of images as
-well as geometry alignment results from Section
-\ref{sec:geometryAlignment} to refine all image positions using a
-weighted linear least squares approach. An example setup for such a problem $\textrm{min}_{\vec{\beta}}
-||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
-as follows.
-
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & -1 & 1 & 0\\
-  0 & -1 & 1 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & -1 & 1\\
-  0 & -m_2 & 0 & 0 & 1 & 0\\
-  1 & 0 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 1 & 0 & 0\\
-  1 & 0 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 1 & 0 & 0\\
-  0 & 1 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & 1 & 0\\
-  0 & 0 & 1 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & 0 & 1\\
-
-\end{pmatrix}\quad
-\vec{\beta} =
-\begin{pmatrix}
-  x_1, \\ x_2, \\ x_3, \\ y_1, \\ y_2, \\ y_3
-\end{pmatrix}
-\vec{\gamma} =
-\begin{pmatrix}
-  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ -m_2gx_2 + gy_2,
-  \\ gx_1, \\ gy_1, \\ tx_1, \\ ty_1, \\ tx_2, \\ ty_2, \\ tx_3, \\
-  ty_3
-
-\end{pmatrix}
-\vec{W} =
-\begin{pmatrix}
-  1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 0.01, \\ 0.01, \\ 0.01, \\
-  0.01, \\ 0.01, \\ 0.01
-\end{pmatrix}
-\]
-
-The variables to solve for are the $x_i$ and $y_i$ positions
-of images, while equations are the feature-based distances between
-pairs of images, images fixed to geometry with 0 or 1 degrees of
-freedom, and the original noisy camera poses. In this scenario, a
-feature-based distance of $dx_{1,2}$, $dy_{1,2}$ was calculated
-between images 1 and 2. This corresponds to the first and second row
-of $A$, while the third and fourth row of $A$ represent the same for
-images 2 and 3. Rows 5 through 7 correspond to results of the geometry
-alignment procedure in Section
-\ref{sec:geometryAlignment}. Specifically, row 5 corresponds to a
-geometry-based constraint of image 2's location to a line of slope
-$m_2$, passing through point $gx_2$, $gy_2$, while rows 6 and 7
-correspond to a fixed location for image 1 without any degrees of
-freedom. Rows 8 through 13 correspond to the original camera locations
-for each image ($tx_i,ty_i$).
-
-The original camera poses are needed due to lack of feature matches in
-all images, or lack of enough geometry alignment results to generate a
-single solution. Since it is desirable to minimally use the original
-noisy poses, we assign to them a weighting factor of $0.01$, while all
-other equations are weighted at $1$.
-
-Since this problem is linear, it can be solved efficiently; after
-applying the resulting shifts, images overlap and match each other
-with far greater accuracy. Using the simple tile-based texturing
-scheme from Section \ref{sec:imageSelection} on these adjusted images
-results in Figure \ref{fig:compareAll}(b), which has far fewer
-discontinuities than in \ref{fig:compareAll}(a), though some 3D error
-as well as lighting differences and parallax effects are still
-visible.
-
-\section{Image Compositing}
-\label{sec:imageCompositing}
-In Section \ref{sec:imageSelection} we described an image selection
-method, that when used to create a texture, resulted in many visible
-discontinuities. In Section \ref{sec:mappingWithCaching}, we will
-refine that approach with an added caching mechanism to improve
-texture continuity. This method works well for all arbitrary camera
-poses and surfaces. However, for cases where images have consistently
-perpendicular viewing angles to surfaces under consideration, such as
-walls, we develop an alternative method in Section
-\ref{sec:shortestPath} which further reduces visual artifacts. Both of
-these approaches are then combined with an exposure compensation and
-blending scheme in order to produce final textures for each surface.
-
-\subsection{Tile-Mapping with Caching}
-\label{sec:mappingWithCaching}
-For the simple texturing method described in Section
-\ref{sec:imageSelection}, discontinuities occur where adjacent tiles
-are textured by different images. Though Section
-\ref{sec:2dAlignment}'s image alignment removes many such
-discontinuities, there are still cases where seams are visible due to
-imprecise matching or other factors such as model-based errors. To
-reduce this, we implement a spatiotemporal caching mechanism to take
-into account image selections made by neighboring tiles while texture
-mapping a given tile. By using the same image across tile boundaries,
-it is possible to eliminate a discontinuity altogether. If a tile is
-not visible in images used by neighboring tiles, using similar images
-across tile boundaries still leads to less noticeable discontinuities.
-
-The best image for a tile $t$ is selected by searching through two
-subsets of images for a viable candidate, before searching through the
-entire set of valid images obtained in Section
-\ref{sec:imageSelection}. The first subset of images is those selected
-by adjacent tiles that have already been textured. We must first check
-which of these images contain texture for $t$, and then of those, we
-make a choice according to the scoring function in Figure
-\ref{fig:scoringFunction}. Before reusing this image, we check the
-criteria $\alpha < 45^\circ$, in order to ensure a high resolution
-projection, with $\alpha$ as the camera angle as shown in Figure
-\ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check a
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. We use the noisy
-camera poses to determine spatial proximity. These images are not the
-same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar, and thus likely match more
-seamlessly. If no viable image is found according to the $\alpha <
-45^\circ$ criteria, we search the entire set of candidate images from
-Section \ref{sec:imageSelection}, selecting based on the same scoring
-function from Figure \ref{fig:scoringFunction}.
-
-The result of applying this caching approach to the images for the
-surface in Figure \ref{fig:compareAll}(a) is shown in Figure
-\ref{fig:compareAll}(c), where seams are considerably reduced as
-compared to Figure \ref{fig:compareAll}(b). However, some
-discontinuities are still present, as visible in the posters on the
-wall with breaks in their borders.
-
-\subsection{Shortest Path Texturing}
-\label{sec:shortestPath}
-
-\begin{figure}
-  \centering
-  \begin{minipage}{3in}
-    \centering
-    \includegraphics[width=1.5in]{projectionCeiling.pdf}
-    \captionof{figure}{Camera axes for horizontal surfaces are at
-      large angles with respect to plane normals.}
-    \label{fig:projectionCeiling}
-  \end{minipage}%
-  \hspace{0.5in}
-  \begin{minipage}{3in}
-    \centering
-    \includegraphics[width=3in]{dagCreation.pdf}
-    \captionof{figure}{DAG construction for the image selection
-      process.}
-    \label{fig:dagCreation}
-  \end{minipage}
-\end{figure}
-
-As mentioned earlier, our data comes from a mobile backpack system
-with side-facing cameras. While these cameras have a wide-angle field
-of view,they are often pointed directly at vertical surfaces during
-data acquisition. This means that image projections on vertical
-surfaces tend to have higher, and more consistent resolution, while
-the more oblique projections onto horizontal surfaces result in
-textures spanning large areas, such as in Figure
-\ref{fig:projectionCeiling}. Using the tile-based texture mapping
-criteria from Figure \ref{fig:scoringFunction}, such projections have
-highly varying scores depending on the location of a tile on the
-plane. Thus, the tiling approach in Section
-\ref{sec:mappingWithCaching} is an appropriate choice for texturing
-horizontal surfaces, as it uses the parts of image projections that
-maximize resolution for their respective plane locations, e.g. areas
-near point A and not near point B, in Figure
-\ref{fig:projectionCeiling}.
-
-For vertical surfaces however, which make up a large portion of most
-models, images are usually taken from close distances and head-on
-angles, resulting in high resolution rectangular projections. As a
-result, for each tile on a wall plane, the scoring function of Figure
-\ref{fig:scoringFunction} is relatively flat with respect to candidate
-images, as they are all more or less head on. Since the scoring
-function is less discriminative for walls, we devise a different
-texturing strategy to directly minimize visible seams when texturing
-them. This is done by choosing a subset of images such that their
-projections (a) cover the entire plane and (b) have minimal
-differences in overlapping regions. A straightforward cost function
-that accomplishes the latter is the sum of squared differences (SSD)
-of pixels in overlapping regions between all pairs of
-images. Minimizing this cost function encourages image boundaries to
-occur either in featureless areas, such as bare walls, or in areas
-where images match extremely well.
-
-To find the subset of images that covers the plane with minimal cost,
-we form a shortest path problem. This can be done because the
-wide-angle cameras have full floor-to-ceiling coverage of walls, and
-the backpack operator logically only moves horizontally. We thus are
-only concerned with lateral coverage when working with wall
-surfaces. We can therefore construct a horizontal Directed Acyclic
-Graph (DAG) from the images, with edge costs defined by the SSD cost
-function, and solve a simple shortest path problem to find an optimal
-subset of images with regard to the SSD cost function \cite{dijkstra}.
-
-Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a hallway wall. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
-between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal and arbitrary cost $C_0$ to(from)
-all images that meet the left(right) border of the plane. We now solve
-the shortest path problem from the start node to the end node. This
-results in a set of images completely covering the plane horizontally,
-while minimizing the cost of seams between images.
-
-We have now (a) mapped every location on the plane to at least one
-image, (b) decreased the number of texturing images, generally
-retaining around 20\% of the image subset obtained in Section
-\ref{sec:imageSelection}, and (c) decreased the discontinuities at
-each image border. As seen in Figure \ref{fig:compareAll}(d), this
-shortest path method has fewer visible discontinuities than Figure
-\ref{fig:compareAll}(c) corresponding to the tile caching
-approach\footnote{In Figure \ref{fig:compareAll}(d), we arbitrarily
-  chose one image for texturing where images overlap, as blending will
-  be discussed in section \ref{sec:blending}.}. This is especially
-evident when comparing the posters in the images. This shortest path
-approach approach directly reduces the cost of each image boundary,
-while the tile caching method uses a scoring function that only
-approximates this effect. Furthermore, this approach guarantees the
-best selection of images to minimize seams, while the sequential tile
-caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. This shortest path
-approach is also far less intensive in terms of memory usage and
-runtime, both during texture generation and rendering, as it does not
-require discretizing planes or images.
-
-When texturing our models, we apply the shortest path method on
-surfaces where images are taken at optimal angles and provide full
-coverage along one dimension. Floors, ceilings, and smaller complex
-objects such as furniture, given their many images taken at oblique
-angles, are textured using the tile caching method of Section
-\ref{sec:mappingWithCaching}.
-
-\subsection{Exposure Compensation}
-\label{sec:exposureCompensation}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=2.5in, height=0.9in]{exposureDiff1.png}}
-  \hspace{0.5in}
-  \subfloat[][]{\includegraphics[width=2.5in, height=0.9in]{exposureDiff2.png}}
-  \caption{(a) A ceiling texture composed of images taken with varying
-    exposures, with significant brightness differences. (b) Exposure
-    compensation applied to the same set of images from (a) by
-    applying computed gains to each image}
-  \label{fig:exposureDiff}
-\end{figure}
-
-Before blending images together, exposure compensation is applied to
-equalize brightness among neighboring images. For the images in this
-report, cameras are set to have automatic exposure, which means that
-images of the same object may have different brightness levels. While
-successful image alignment and blending can reduce sharp seams between
-adjacent images, there may still be noticeable brightness gradients
-between images, particularly in areas near light sources. This can be
-seen in Figure \ref{fig:exposureDiff}(a), where the ceiling texture
-has patches of clearly differing brightness. To diminish this effect,
-a gain can be computed and applied to each image, with the effect of
-linearly scaling the brightness of each image. The goal is to compute
-a gain for each image, such that the brightness of an area is
-consistent across image boundaries.
-
-Similar to the image position refinement procedure in Section
-\ref{sec:robustSIFTFeatureMatching}, exposure compensation is
-performed simulatenously across all images present in a single
-region. To begin, a relative gain $R_{ij}$ is computed for each pair
-of overlapping images $I_i$ and $I_j$, which have a set of pixels
-common to both images, labeled as $P_{ij}$. The relative gain $R_{ij}$
-is then obtained by calculating the scaling factor between the average
-intensity of $P_{ij}$ in $I_i$ and the average intensity of $P_{ij}$
-in $I_j$.
-
-As before, these pair-wise observations can be combined and solved as
-a least-squares optimization problem. In this case, observations do
-not need to be weighted, and so the formulation is
-$\textrm{min}_{\vec{b}} ||(X \vec{b} - \vec{a})||_2^2 $. An example
-setup for 3 images, where each image overlaps with both of the other
-images, is shown below.
-\[
-X =
-\begin{pmatrix}
-  R_{12} & -1 & 0\\
-  R_{13} & 0 & -1\\
-  0 & R_{23} & -1\\
-  1 & 1 & 1\\
-
-\end{pmatrix}\quad
-\vec{b} =
-\begin{pmatrix}
-  G_1, \\ G_2, \\ G_3
-\end{pmatrix}
-\vec{a} =
-\begin{pmatrix}
-  0, \\ 0, \\ 0, \\ 3
-\end{pmatrix}
-\]
-
-In this problem, $\vec{b}$ is the $N\times1$ vector of gains $G_i$ to
-be solved for, where $N$ is the number of images.  Matrix $X$ is an
-observation matrix corresponding to the relative intensities of
-overlapping images. In particular, the number of rows of $X$ is one
-plus the number of unique pairs of overlapping images, and the number
-of columns of $X$ is equal to $N$. Each row of $X$, except the last
-one, contains an $R_{ij}$ value which is placed in column $i$, as well
-as a $-1$ value in column $j$, with zeroes elsewhere. As explained
-above, $R_{ij}$ is the relative gain between images $i$ and $j$, and
-therefore $G_iR_{ij} - G_j = 0$.  Thus, all values of $\vec{a}$, which
-is a vector with size equal to the number of rows of $X$, are set to
-$0$, except for the last one.
-
-The last row of $X$ and corresponding last entry of $\vec{a}$ are used
-to constrain the problem, as without them, all computed gains would be
-allowed to scale by any amount. To keep gains at reasonable values,
-the final observation is used: $\Sigma G_i = N$, where $N$ is the
-number of images. This has the effect of setting the average of all
-gains to 1, and is represented by the final row of ones in $X$, and
-the corresponding $N$ value in $\vec{a}$.
-
-For the 81 source images that compose the ceiling location in Figure
-\ref{fig:exposureDiff}, the corresponding $X$ matrix has 1343 rows,
-and the optimization problem takes under a second to solve, on a 2.8
-GHz dual core machine.  The result of computing and applying gains can
-be seen in Figure \ref{fig:exposureDiff}(b). As compared to Figure
-\ref{fig:exposureDiff}(a), the effect is clear, as dark/bright patches
-are no longer present, and the overall brightness of the image has not
-changed significantly.
-
-\subsection{Blending}
-\label{sec:blending}
-We now apply a blending procedure to the texturing methods in Sections
-\ref{sec:mappingWithCaching} and \ref{sec:shortestPath}. Although the
-image alignment and selection steps in both methods attempt to
-minimize all mismatches between images, and exposure compensation
-minimizes brightness differences, there are occasional unavoidable
-discontinuities in the final texture due to parallax effects or
-inaccuracies in model geometry. These can however be treated and
-smoothed over by applying alpha blending over image seams.  Whether
-the units to be blended are rectangularly-cropped images or
-rectangular tiles, we can apply the same blending procedure, as long
-as there is a guaranteed overlap between units to blend over.
-
-For the tile caching method of Section \ref{sec:mappingWithCaching},
-we can ensure overlap by texturing a larger tile than needed for
-display. For example, for a rendered tile of size $l_1 \times l_1$, we
-can associate it with a texture $(l_1 + l_2) \times (l_1 + l_2)$ in
-size.  We have found $l_2 = \frac{l_1}{2}$ to provide a good balance
-between blending and keeping features unblurred at image
-boundaries. For the shortest path method, we already have ensured
-overlap between images. To enforce consistent blending however, we add
-a minimum required overlap of images of 200 mm while solving the
-shortest path problem in Section \ref{sec:shortestPath}. Additionally,
-if images overlap in a region greater than the overlap distance, we
-only apply blending over an area equal to the overlap distance.
-
-After linear alpha blending across overlapping regions, the texture
-mapping process is complete. Figures \ref{fig:compareAll}(e) and
-\ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. By
-comparing all images, it is clear that Figure \ref{fig:compareAll}(f)
-has the best visual quality and the best texturing approach among the
-textures in Figure \ref{fig:compareAll}.
-
-\section{Results}
-\label{sec:results}
-This section contains results of the proposed texture mapping process
-on a number of different environments, with geometry generated using
-three different methods. Further images of individual textured
-surfaces and entire textured models, as well as videos and interactive
-walkthroughs can also be found at
-\footnote{\url{http://www-video.eecs.berkeley.edu/research/indoor/}}.
-
-\subsection{Examples}
-\label{sec:examples}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
-  \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
-  } \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
-  } \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
-  }
-  \caption{The same indoor environments, as generated using (a) PCA
-    plane-fitting, (b) Floor plan extrusion, (c) Voxel carving. The
-    first two are lower-resolution models, while the third is
-    higher-resolution, and reconstructs significantly more features,
-    such as the ladder in the lower image.}
-  \label{fig:modelcomparisons}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=3.1in]{results_houston_2_2d.png}
-  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
-  \subfloat[][]{
-    \includegraphics[width=3.1in]{results_houston_3_2d.png}
-  } \subfloat[][]{
-    \includegraphics[width=3.1in]{results_houston_3_3d.png}
-  }
-  \caption{(a) A model generated by the low-resolution floor plan
-    method. (b) A model generated by the high-resolution voxel-carving
-    method. The high-resolution model contains far more surface
-    detail, such as in the ceiling indentations or the benches on the
-    ground. In terms of producing a realistic visualization however,
-    the low-resolution model performs very similarly to the
-    high-resolution model.}
-  \label{fig:2dvs3d}
-\end{figure}
-
-The texture mapping procedure in this paper was tested with three
-different geometry-reconstruction methods, a PCA-based plane-fitting
-method \cite{sanchez2012point}, a floor plan extrusion method
-\cite{turnerfloorplan}, and a voxel-carving mesh generation method
-\cite{turnerwatertight}. The first two methods generate very similar
-low-resolution models, containing only major walls, ceilings and
-floors. The third method generates high-resolution models, and
-attempts to reconstruct all scanned objects in the environment. A
-comparison of the three model types is in Figure
-\ref{fig:modelcomparisons}, while Figure \ref{fig:2dvs3d} compares the
-latter 2 types for a closer comparison of a low-resolution model vs a
-high-resolution model.
-
-\subsection{Runtime}
-As mentioned earlier, our approach is quite efficient. The top wall in
-Figure \ref{fig:indivPlanes}(a) was generated with 7543 $\times$ 776
-pixels, and spans a 40-meter long wall. Given 41000 input images in
-the entire dataset, a 2.8 GHz dual-core consumer-grade laptop takes
-under a second to choose 36 candidate images, followed by a minute to
-perform image projections, image alignment, and the shortest path
-texturing method. The tile-caching approach takes roughly comparable
-time, and over 75\% of the time for either method is spent on
-calculating image projections, which are cached over multiple runs,
-and also could be performed as a preprocessing step instead. While not
-real-time, the process is capable of generating fast updates after
-changes in various parameters or modifications to input data, and if
-integrated directly into a 3D modeling system, could provide quick
-visual feedback as data is collected.
-
-\subsection{Visualization}
-Our full models consist of an input model file, generated textures,
-and a mapping of image points to 3D model vertices. The textured
-models shown throughout this paper range from 20 MB in size to over
-400 MB in a compressed format, with textures of sizes over 500
-megapixels. These models are visualized using the OpenSceneGraph
-toolkit \cite{openscenegraph}, which allows for export to many common
-model formats, as well as interactive visualization, even in web
-browsers or mobile devices.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this paper, we have developed an approach to texture mapping models
-of indoor environments with noisy camera localization data. We are
-able to refine image locations based on geometry references and
-feature matching, and robustly handle outliers. Using the tile-based
-mapping approach, we can texture both large planar features as well as
-smaller, more complex surfaces. We also implemented a shortest path
-texturing method that produces seamless textures on planes where
-multiple head-on images are available. Both of these approaches are
-highly modular, and easily tunable for similar systems across multiple
-environments.
-
-Our method is likely to fail however in scenarios where 3D error is
-large. A logical progression of our approach to resolve camera error
-in 3D is to perform matching between image lines and geometry in 3D,
-which can be done reasonably efficiently \cite{linebased,
-  rectangularstructures}. Using linear features in addition to SIFT
-features is also likely to result in improved matches, as indoor
-scenes often have long, unbroken lines spanning multiple images
-\cite{linearposeestimation}. Finally, the blending procedure is quite
-basic, and applying more sophisticated methods of blending as well as
-image boundary selection would benefit the final visual quality, and
-more robustly handle motion-based or parallax errors.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% References %%%%%
-
-\bibliography{report} %>>>> bibliography data in report.bib
-\bibliographystyle{spiebib} %>>>> makes bibtex use spiebib.bst
+\message{ !name(spie2014.tex) !offset(1324) }
 

### 2014-01-04 spie2014/abstract.tex
organize stuff

--- 2013-05-31 masters/body/masters.tex
@@
 \keywords{Texture Mapping, Reconstruction, Image Stitching, Mosaicing}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-\label{sec:introduction} % \label{} allows reference to this section
-Three-dimensional modeling of indoor environments has a variety of
-applications such as training and simulation for disaster management,
-virtual heritage conservation, and mapping of hazardous sites. Manual
-construction of these digital models can be time consuming, and
-consequently automated 3D site modeling has garnered much interest in
-recent years.
-
-The first step in automated 3D modeling is the physical scanning of
-the environment's geometry. An indoor modeling system must be able to
-recover its pose within an environment while simultaneously
-reconstructing the 3D structure of the environment itself
-\cite{chen2010indoor, hz, kua2012loopclosure, liu2010indoor}. This is
-known as the simultaneous localization and mapping (SLAM) problem, and
-is generally solved by taking readings from laser range scanners,
-cameras, and inertial measurement units (IMUs) at multiple locations
-within the environment. Mounting such devices on a platform carried by
-an ambulatory human provides unique advantages over static or
-vehicular-based systems on wheels in terms of agility and portability,
-but can also result in larger localization error
-\cite{liu2010indoor}. As a result, common methods for texture mapping
-generally produce poor results. In this thesis, we present an approach
-to texture mapping 3D models of indoor environments in the presence of
-uncertainty and noise in camera poses. In particular, we consider data
-obtained from a human-operated backpack system, detailed in Section
-\ref{sec:dataAcquisition}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=6in]{flowchart.jpg}
-  \caption{The proposed texture mapping procedure\\}
-  \label{fig:flowchart}
-\end{figure}
-
-The overall block diagram for the proposed texture mapping procedure
-is shown in Figure \ref{fig:flowchart}, where the number attached to
-each box indicates the section in which the concept in the box is
-explained in this thesis. First, the geometry of an environment is
-split into regions, each of which will be textured independently and
-in parallel. For each region, we begin by selecting a set of images
-that spans the entire region's surface with high resolution
-imagery. We then use recovered noisy camera poses to project these
-selected images onto the surface. These projections are rotated and
-translated in 2D, in order to maximally align them with the surface's
-geometry, as well as to each other, allowing us to handle both errors
-in geometry as well as camera poses. For surfaces and camera poses at
-arbitrary locations or orientations, generally horizontal surfaces, we
-propose a tile-based approach for sampling high-resolution portions of
-images and compositing them into a texture. In cases where cameras
-have consistently perpendicular viewing angles to the surfaces under
-consideration, generally vertical surfaces, we demonstrate a superior
-approach based on a shortest-path computation that leads to more
-seamless textures.
-
-The remainder of the thesis is organized as follows. Section
-\ref{sec:dataAcquisition} provides background on the data acquisition
-system and describes a region segmentation procedure. Section
-\ref{sec:relatedWork} covers existing approaches to image stitching,
-and their performance on our datasets. Section
-\ref{sec:imageSelection} explains how to downsample the set of
-available images by selecting those with the best orientation and
-distance from surfaces under consideration. Section
-\ref{sec:2dAlignment} contains the proposed approach towards 2D image
-alignment, followed by Section \ref{sec:imageCompositing}, which
-describes two methods of selecting and compositing images to create
-the final texture. Sections \ref{sec:results} and \ref{sec:conclusion}
-contain results and conclusions.
-
-\section{Data Acquisition}
-\label{sec:dataAcquisition}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3in]{backpackCAD.png}
-  \caption{CAD model of the backpack system.}
-  \label{fig:backpack}
-\end{figure}
-
-This section contains background information describing the
-backpack-mounted system and its operation. The hardware and operation
-of the backpack system, as well as the postprocessing of acquired
-data, play an important role in motivating the approaches described in
-this thesis. The following two sections will focus on image and raw
-data acquisition, and a method of partitioning recovered environment
-geometry, respectively.
-
-\subsection{Acquisition Hardware}
-
-A CAD model of the backpack-mounted system is shown in Figure
-\ref{fig:backpack}. This backpack system has a number of laser range
-scanners as well as 2 cameras facing left and right, each equipped
-with fisheye lenses reaching an approximately 180$^{\circ}$ field of
-view each and taking photos at a rate of 5 Hz \cite{liu2010indoor}. In
-order to collect data, an operator wears the backpack system and
-traverses the environment to be scanned, walking in straight lines at
-a standard pace and making an effort to walk parallel to all walls in
-the area. Multiple localization and loop-closure algorithms are then
-applied to the raw data collected by the onboard sensors
-\cite{chen2010indoor, kua2012loopclosure, liu2010indoor}, and the
-backpack is localized\footnote{In this thesis, we use the terms
-  localization and pose recovery interchangeably, in that they both
-  refer to recovering position and orientation.}  over its data
-collection period. This involves recovering the 6 degrees of freedom
-for the backpack itself as well as the cameras rigidly mounted on it.
-These results are noisy, which motivates the approaches in this
-thesis. Once this is complete, the data from the laser range scanners
-is used to generate a 3D point cloud of the surrounding
-environment. This point cloud is used to construct either a
-low-resolution planar model, such as for usage in basic navigation or
-energy analysis \cite{sanchez2012point, turnerfloorplan}, or a
-high-resolution, detailed mesh, for applications such as accurate
-remodeling or virtual walkthroughs \cite{turnerwatertight}.
-Regardless of resolution, size, or detail, the model, consisting of
-geometric surfaces in 3D space, along with the set of images captured
-by the backpack's cameras and their noisy 3D poses, are the input to
-the texture mapping problem.
-
-\subsection{Geometry Partitioning}
-\label{sec:geometryPartitioning}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=2.2in]{geomdeskwire_crop.png}}
-  \subfloat[][]{\includegraphics[width=2.2in]{geomdeskregions_crop.png}}
-  \subfloat[][]{\includegraphics[width=2.2in]{geomdesktexturetris_crop.png}}
-  \caption{(a) Part of a model representing a desk and miscellaneous
-    objects on top of the desk. (b) Triangles grouped into regions for
-    texturing. (c) Final textured output.}
-  \label{fig:deskGeom}
-\end{figure}
-
-In order to effectively texture a 3D model, we first divide the model
-into a set of regions, each to be textured independently. The purpose
-of this is to ensure texture continuity along large uniform areas,
-while allowing texture boundaries to fall along natural environmental
-boundaries. Because textures may not match at such boundaries where
-two regions meet, it is important to minimize the visibility of
-boundaries. This is done by encouraging region boundaries to occur at
-large sharp corners, where texture continuity is not important. When
-working with lower-resolution models, where surfaces generally
-correspond to large planar features such as walls, ceilings, or
-floors, and often meet at right angles, each planar surface in the
-model can simply be treated as a distinct region and textured
-separately.
-
-With high-resolution models however, geometry often represents large
-features as well as small details found in furniture, plants, and
-other miscellaneous objects. For instance, in Figure
-\ref{fig:deskGeom}(a), the geometry modeling each side of a desk as
-well as objects on top of it consists of many small triangles at
-various orientations. It is important that triangles belonging to the
-same object or surface are textured together, as texturing them
-independently might lead to visible misalignment between the textures
-of each triangle, resulting in poor visualizations. On the other hand,
-triangles belonging to different objects, such as the wall vs. objects
-on the desk need not be textured together, as texture alignment
-between the two is not important in terms of overall visual quality of
-the scene. Thus, in this example, the triangles comprising each side
-of the desk, objects on top of the desk, and the wall behind, should
-all be grouped into separate regions. This region grouping is done by
-first designating all contiguous coplanar groups of triangles as
-different regions. Any regions that are less than $1 m^2$ in size are
-then joined to their largest neighboring regions, as long as the angle
-between them is under $90^{\circ}$. An example of such a grouping is
-shown in Figure \ref{fig:deskGeom}(b). The same area with textures
-successfully applied to each region is shown in Figure
-\ref{fig:deskGeom}(c).
-
-Though some of these regions from high-resolution models are not
-completely flat, a plane is fitted to each region for the purposes of
-texturing. This plane corresponds to the largest contiguous section of
-coplanar triangles, as most regions are characterized by small
-outcroppings from a largely planar surface, such as objects on a table
-or features protruding from a wall. The 3D surface composing a region
-is then projected onto its calculated plane, and the resulting 2D
-planar polygon is used as the texturing surface. This 2D planar
-approximation provides a simple, yet approximately accurate surface
-onto which images can be projected in order to generate
-textures. However, 3D surfaces are still retained in order to achieve
-more accurate results when performing occlusion checks during the
-texturing process. To improve runtime during such occlusion checks,
-the triangles within all 3D surfaces are also loaded into a k-d tree
-for quick lookup. Thus, for high-resolution models, each region has
-both 3D geometry stored in a k-d tree for occlusion purposes, and an
-approximate 2D representation stored as the texturing surface.
-
-At this point, we either have a series of planar regions from a low
-resolution model, or a set of planar approximations for regions as
-well as an associated k-d tree from a high resolution model. The task
-now is to generate a texture for each region.
-
-\section{Related Work}
-\label{sec:relatedWork}
-There are many existing approaches to stitching together multiple
-images to produce a larger, seamless image \cite{szeliski2006image,
-  agarwalapanoramas, wangmultipleviews, coorg1997matching,
-  debevechybrid, bernardinimultiplescans}. Generally, parts of images
-are matched to each other, either through direct comparisons at a
-pixel level, or through feature detection and matching. Images are
-then transformed to maximize matches, often by computing homographies
-between pairs of images, or by iteratively adjusting camera poses in 1
-to 6 degrees of freedom.
-
-Feature matching has a number of advantages over direct matching that
-make it more suitable for our often non-planar environments, and
-rotational differences between camera poses
-\cite{szeliski2006image}. Feature matching however, works best when
-multiple unique visual references exist in the environment that can be
-detected in multiple images. In contrast, indoor environments have a
-high prevalence of bare surfaces, as well as repeating textures, such
-as similar windows, doors, and wall-mounted decorations, that are
-difficult to disambiguate. This lack of reliable reference points
-often results in errors when matching images together.
-
-Additionally, our datasets often contain long chains of images,
-corresponding to long hallways and corridors as shown in Figure
-\ref{fig:mosaic3D}, which leads to error accumulation when image
-correspondences are not accurate. For example, when matching a long
-chain of images through homography, a pixel in the $nth$ image must be
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrix $H_1 H_2 H_3 ... H_n$. Any error in one of these
-homography matrices is propagated to all further images, resulting in
-drift.
-
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 20cm 0cm,
-    clip=true, width=6in, height=0.7in]{graphApproach.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 15cm 0cm,
-    clip=true, width=6in, height=0.7in]{autostitchResult.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 0cm 75cm 0cm,
-    clip=true, width=6in, height=0.7in]{finalLong.jpg}}
-
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm, (b) the AutoStitch software package, and (c)
-    the proposed method.}
-  \label{fig:mosaic3D}
-\end{figure}
-
-In prior work, we have experimented with integrating image stitching
-with the iterative global localization algorithm used to recover the 6
-degrees of freedom of the backpack acquisition system detailed in
-Section \ref{sec:dataAcquisition} \cite{liu2010indoor}. When run on
-long chains of images however, especially where features are sparse,
-this approach produces distorted textures, as seen in Figure
-\ref{fig:mosaic3D}(a). Furthermore, this approach is not closed-form,
-and its iterative camera adjustment process over large datasets leads
-to prohibitively long computation time.
-
-The AutoStitch software package, based on research in the related area
-of panorama genoration, also performs homography-based alignment, with
-additional provisions that attempt to reduce drift and increase
-overall efficiency \cite{panorama2d, autostitch}. Though AutoStitch
-performs well in small areas, it often induces drift in images,
-such that global alignment to the environment geometry is
-lost. Furthermore, its performance relies on the presence of a dense
-set of features, and it has trouble aligning wall sections with even
-short segments of bare texture. The example in Figure
-\ref{fig:mosaic3D}(b) was generated after many rounds of manual
-tuning; we have empirically found that areas with fewer visual
-features or repeating texture patterns simply failed outright with
-AutoStitch.
-
-\section{Image Selection}
-\label{sec:imageSelection}
-
-The geometry of the texture mapping process for a region, as described
-in Section \ref{sec:geometryPartitioning}, is shown in Figure
-\ref{fig:projection}. Given a set of images to texture a target
-surface, camera matrix $P_i$ for the $i$th image transforms a 3D point
-in the world coordinate system to a 2D point or pixel in image $i$'s
-coordinates. A camera matrix $P_i$ is composed of the camera's
-intrinsic parameters, containing focal length and image center, as
-well as extrinsic parameters which specify the rotation and
-translation of the camera's position in 3D world coordinates at the
-time that image $i$ was taken. These extrinsic parameters are
-determined by the backpack hardware and the corresponding localization
-algorithms \cite{chen2010indoor, liu2010indoor, kua2012loopclosure}
-and are noisy.
-
-Since the backpack system takes pictures at a rate of 5 Hz, thousands
-of images are available for texturing each surface in the 3D
-model. Our objective in designing a texture mapping process is to
-determine which of these images should be used, and where their
-contents should map onto the final texture, in order to minimize any
-visual discontinuities or seams that would suggest that the plane's
-texture is not composed of a single continuous image. In the remainder
-of this section, we propose an image subsampling procedure to obtain a
-set of images for all further steps, and use it to derive a simple
-tile-based texture mapping procedure.
-
-\begin{figure}
-  \begin{minipage}[b]{0.45\linewidth}
-    \centering
-    \includegraphics[height=1.8in]{Projection.pdf}
-    \caption{Images are related to each surface through the camera
-      matrices $P_{1..m}$. }
-    \label{fig:projection}
-  \end{minipage}
-  \hspace{0.5cm}
-  \begin{minipage}[b]{0.45\linewidth}
-    \centering
-    \includegraphics[height=1.8in]{scoringFunction.jpg}
-    \caption{Camera angle $\alpha$ and distance $d$ are minimized by
-      maximizing the scoring function $\frac{1}{d} (-1 \cdot \vec{c})
-      \cdot \vec{n}$}
-    \label{fig:scoringFunction}
-  \end{minipage}
-\end{figure}
-
-Our criteria for image subsampling has the following
-stipulations. First, we want a set of images such that their
-projections together cover up the entirety of our target surface, so
-as to avoid holes in the final texture. Second, we desire our final
-texture to have high resolution throughout; thus every location on the
-target surface should have at least one image that contains high
-resolution imagery for it. A straightforward way to accomplish these
-goals is to discretize the target surface into small square tiles, and
-for each tile, select the image that has the best viewing angle and
-resolution for texturing that tile. In order to select the image that
-can best texture a tile $t$, we first gather a list of candidate
-images that contain all four of its corners; we can rapidly check this
-by projecting $t$ into each image using the $P_i$ camera
-matrices. Furthermore, each candidate image must have been taken at a
-time when its camera had a clear line-of-sight to $t$, which can be
-determined using standard ray-polygon intersection tests between the
-camera location, $t$, and every other surface, or via the k-d tree
-from Section \ref{sec:geometryPartitioning} if present
-\cite{rayintersection}.
-
-Once we have a list of candidate images for $t$, we define a scoring
-function in order to objectively select the best image for texturing
-$t$. Since resolution decreases and camera pose errors become more
-pronounced with distance, we wish to minimize the distance between
-cameras and the surfaces they texture. Additionally, we desire images
-that are projected perpendicularly, rather than obliquely, onto the
-plane, maximizing the resolution and amount of useful texture
-available in their projections, as well as minimizing any parallax
-effects due to real-world geometry not accurately represented by the
-digital 3D model. In other words, we wish to minimize the angle
-between the tile's normal vector and the camera axis for images
-selected for texturing that tile. These two criteria can be met by
-maximizing the function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$
-as shown in Figure \ref{fig:scoringFunction}, where $d$ is the
-distance between the centers of a camera and a tile, and $\vec{n}$ and
-$\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively.
-
-When the images selected for each tile are used directly to texture
-their respective tiles, image boundaries with abrupt discontinuities
-between tiles are visible, as shown in Figure
-\ref{fig:compareAll}(a). While it is clear that camera pose
-inaccuracies are too severe for such a simple approach to work, the
-selected images all appear to contain optimal camera angles with high
-resolution, and much of their misalignment appears reconcilable using
-2D transforms. This procedure generally selects around 10\% of the
-possible images that could be used for texturing a surface, and not
-only reduces the computational complexity of the remaining steps, but
-also selects the most promising images for the remaining steps.
-
-\begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_naive_shift.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift.jpg}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=1.2in]{wall2_shortest_shift_blend.pdf}}
-
-  \centering \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_cache_comparison.png}}
-  \subfloat[][]{\includegraphics[width=3.4in,
-    height=3.4in]{wall2_shortest_comparison.png}}
-
-  \caption{(a) Tile-based texturing; (b) Tile-based texturing after
-    image alignment; (c) Tile-based texturing after image alignment
-    with caching; (d) Shortest path texturing after image alignment;
-    (e,f) Blending applied to (c) and (d); (g,h) Zoomed in views of
-    discontinuities in (e) vs. in (f).}
-  \label{fig:compareAll}
-\end{figure}
-
-\section{2D Image Alignment}
-\label{sec:2dAlignment}
-In this section, we describe our method for efficient and robust image
-alignment. Rather than register all of our images in 3D, as many
-state-of-the-art techniques for image stitching do, we instead align a
-subset of images in 2D; this subset corresponds to the images selected
-by the image selection procedure described in Section
-\ref{sec:imageSelection}.
-
-Applying 2D alignments to this set of images works well for a number
-of reasons. First, the nature of our input data and the selected
-images is such that localization error chiefly occurs in two
-dimensions, which correspond to the plane of most surfaces being
-projected onto. This is because the backpack operator, during data
-acquisition, makes efforts to walk within a few meters of, and
-parallel to all walls being scanned. Furthermore, the backpack system
-maintains a fairly consistent distance from floors and ceilings during
-data collection. As a result, the translational error of camera poses
-is quite minimal in dimensions perpendicular to most surfaces being
-textured, corresponding to, or parallel to walls, ceilings and
-floors.
-
-Our proposed 2D alignment procedure consists of three parts, as shown
-in the diagram in Figure \ref{fig:flowchart}. First, images are
-projected onto the surface and lines within these projected images are
-detected. Images are then transformed such that these lines match
-geometric lines composing the boundaries of the surface being
-textured. Second, occlusion checks are performed to remove invalid
-parts of each image for the target surface. Third, SIFT feature
-matches are detected between pairs of images, and a weighted linear
-least squares problem is solved in order to maximize all image and
-geometry-based alignments. Each step will now be explained in detail.
-
-\subsection{Geometry-based Alignment}
-\label{sec:geometryAlignment}
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{allunshifted.jpg}}
-
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{allshifted.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[trim=0cm 2cm 0cm 0cm,
-    clip=true, width=5in]{matchLines.jpg}}
-
-  \caption{Images projected onto a ceiling surface, where
-    geometry-based lines corresponding to the ceiling's boundary are
-    shown in red. Image-based lines detected by Hough transform in the
-    image projections are shown in blue; (a) images projected with
-    their original noisy camera poses; (b) after image alignment to
-    maximize line matches between images and geometry; (c) examples of
-    matching lines in cases with $\geq$ 2 line pairs, 1 line pair, and
-    zero line pairs, from top to bottom.}
-  \label{fig:geometryAlignment}
-\end{figure}
-
-After computing each image's projection onto the target surface, as
-described in Section \ref{sec:imageSelection}, we can obtain a set of
-image-based line segments by using Hough transforms to detect lines in
-the image projections. These lines are detected in the image
-projections rather than the original images, as the varying
-orientation and distances of camera poses relative to surfaces results
-in high variance of line lengths and strengths for real-world linear
-features across the original images. We also gather a set of
-geometry-based lines, which correspond to the lines comprising the
-target surface's border, as well as lines formed where other surfaces
-intersect the target surface. An example of these lines is shown in
-red for a ceiling surface in Figure
-\ref{fig:geometryAlignment}(a). Ideally, for perfect camera poses and
-surface geometry, the lines in images corresponding to corners between
-surfaces should match up exactly with corners in the 3D model. By
-inducing such lines to match, we fit camera poses more accurately to
-the surface, and to each other as well.
-
-To align images to surface geometry, we collect pairs of image-based
-and geometry-based line segments, which are within a distance and
-angular difference threshold of each other. We have found a distance
-threshold of 250 mm and an orientation difference threshold of
-$10^\circ$ to work well for our datasets. For each pair of lines, we
-compute the angular difference between the pair's image and geometry
-lines. If there are 2 or more pairs with angular differences within
-$1^\circ$, we select the two pairs with the longest noncollinear
-image-based lines, and rotate the image such that the lines in the
-pair with the longest image-based line become parallel. We then find a
-translation such that the lines in that same pair overlap. This
-translation has ambiguity in the dimension along the matched lines,
-which is resolved by matching the midpoint of the image-based line in
-the second pair to its corresponding geometry-based line. This is
-shown in case (1) of Figure \ref{fig:geometryAlignment}(c). Thus, with
-2 or more pairs, it is possible to obtain a fixed rotation and
-translation for geometry alignment, which are saved for usage in
-Section \ref{sec:robustSIFTFeatureMatching}.
-
-If there are not 2 or more pairs with similar angular differences, we
-select the pair with the longest image-based line, which corresponds
-to a strong linear visual feature, and apply a rotation and the
-minimal translation to match the pair's lines. This translation's
-ambiguity however, can not be resolved, but is also saved to be used
-in Section \ref{sec:robustSIFTFeatureMatching}. This is shown in case
-(2) of Figure \ref{fig:geometryAlignment}(c). Finally, in the case
-where there are no line pairs, we can still rotate images in order to
-exploit patterns in indoor environments, as shown in case (3) of
-Figure \ref{fig:geometryAlignment}(c). For instance, doors, windows,
-furniture, etc. tend to have linear edges that are parallel to the
-edges of the surfaces they are on. Similarly, lights, visible interior
-walls, etc. which are visible in floor and ceiling images, tend to be
-parallel to interior and exterior walls, corresponding to the
-intersection lines and edges of ceiling and floor surfaces
-respectively. Thus, we choose to minimize the angle between
-image-based lines and geometry-based lines regardless of distance. We
-use the RANSAC framework to compute a rotation angle that best
-accomplishes this while ignoring outliers. \cite{fischler1981random}.
-
-After these steps, image projections line up well with target
-surfaces, as shown in Figure \ref{fig:geometryAlignment}(b), which is
-considerably more aligned than Figure
-\ref{fig:geometryAlignment}(a). This procedure reconciles both errors
-in camera poses as well as in geometry, and results in sharp,
-continuous borders across images, which is crucial when checking for
-occlusion.
-
-\subsection{Image Occlusion}
-\label{sec:imageOcclusion}
-
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-    \subfloat[][]{\raisebox{-1in}{\includegraphics[width=3in]{occlusiondiagram.png}}} &
-
-  \begin{tabular}{c}
-    \subfloat[][]{\includegraphics[trim=0cm 0cm 1.3cm 0cm,
-      clip=true, width=3in,
-      height=0.9in]{occlusionimagebad.png}} \\
-    \subfloat[][]{\includegraphics[trim=1.3cm 0cm 0cm 0cm,
-      clip=true, width=3in,
-      height=0.9in]{occlusionimagegood.png}}
-  \end{tabular}
-\end{tabular}
-\caption{(a) The image from the camera in this diagram contains
-  texture that belongs to the gray occluding surface, which should not
-  be projected onto the orange target surface; (b) without geometry
-  alignment, texture to the left of the red line would be removed,
-  which would leave some erroneous texture projected onto our target
-  surface; (c) after geometry alignment, the image is shifted,
-  resulting in the correct amount of texture being removed.}
-\label{fig:occlusion}
-\end{figure}
-
-In order to correctly texture surfaces, it is important to detect and
-remove parts of image projections containing texture for occluding
-surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
-used to texture the orange target surface also contains part of a gray
-occluding surface. We remove this incorrect texture by recursively
-performing ray-polygon intersection tests between the camera location
-and every surface in our model except the target surface
-\cite{rayintersection}. If using planar approximations for regions, as
-explained in Section \ref{sec:geometryPartitioning}, the k-d tree is
-used instead. These intersection tests are performed at the corners of
-a grid overlaid upon the target surface. Where all four corners of a
-grid section are occluded, texture is removed. Where one or more
-corners are occluded, the grid is subdivided into four, and the
-process repeats. Occlusion checking works entirely with geometry, so
-by ensuring that images match geometry using
-\ref{sec:geometryAlignment}'s alignment procedure, texture belonging
-to other surfaces is accurately removed, as seen in Figure
-\ref{fig:occlusion}(b) vs. \ref{fig:occlusion}(c).
-
-\subsection{2D Feature Alignment}
-\label{sec:robustSIFTFeatureMatching}
-The next step is to align the selected images from Section
-\ref{sec:imageSelection} for each surface to each other by searching
-for corresponding feature points between all pairs of overlapping
-images. We use feature alignment rather than pixel or intensity-based
-alignment due to the differences in lighting as well as possible
-occlusion among images, both of which feature alignment is less
-sensitive to \cite{lowe1999object, mikolajczyk2005performance,
-  szeliski2006image}. We use SiftGPU \cite{siftgpu} for its high
-performance on both feature detection as well as pairwise
-matching. These matches determine $dx$ and $dy$ distances between each
-pair of features for two image projections, though these distances may
-not always be the same for different features. Since indoor
-environments often contain repetitive features such as floor tiles or
-doors, we need to ensure that SIFT-based distances are
-reliable. First, we only align parts of images that overlap given the
-original noisy poses. Second, we discard feature matches that
-correspond to an image distance greater than 200 mm from what the
-noisy poses estimate. In order to utilize the remaining feature
-matches robustly, RANSAC \cite{fischler1981random} is again used to
-estimate the optimal $dx_{i,j}$ and $dy_{i,j}$ distances between two
-images $i$ and $j$. We use a 5 mm threshold for RANSAC, so that SIFT
-matches are labeled as outliers if their distance is not within 5 mm
-of the sampled average distance.
-
-We now use the feature-based distances between each pair of images as
-well as geometry alignment results from Section
-\ref{sec:geometryAlignment} to refine all image positions using a
-weighted linear least squares approach. An example setup for a
-weighted linear least squares problem $\textrm{min}_{\vec{\beta}}
-||W^\frac{1}{2}(A \vec{\beta} - \vec{\gamma})||_2^2 $ with 3 images is
-as follows.
-
-\[
-A =
-\begin{pmatrix}
-  -1 & 1 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & -1 & 1 & 0\\
-  0 & -1 & 1 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & -1 & 1\\
-  0 & -m_2 & 0 & 0 & 1 & 0\\
-  1 & 0 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 1 & 0 & 0\\
-  1 & 0 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 1 & 0 & 0\\
-  0 & 1 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & 1 & 0\\
-  0 & 0 & 1 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & 0 & 1\\
-
-\end{pmatrix}\quad
-\vec{\beta} =
-\begin{pmatrix}
-  x_1, \\ x_2, \\ x_3, \\ y_1, \\ y_2, \\ y_3
-\end{pmatrix}
-\vec{\gamma} =
-\begin{pmatrix}
-  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ -m_2gx_2 + gy_2,
-  \\ gx_1, \\ gy_1, \\ tx_1, \\ ty_1, \\ tx_2, \\ ty_2, \\ tx_3, \\
-  ty_3
-
-\end{pmatrix}
-\vec{W} =
-\begin{pmatrix}
-  1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 1, \\ 0.01, \\ 0.01, \\ 0.01, \\
-  0.01, \\ 0.01, \\ 0.01
-\end{pmatrix}
-\]
-
-The variables we wish to solve for are the $x_i$ and $y_i$ positions
-of images, while equations are the feature-based distances between
-pairs of images, images fixed to geometry with 0 or 1 degrees of
-freedom, and the original noisy camera poses. In this scenario, a
-feature-based distance of $dx_{1,2}$, $dy_{1,2}$ was calculated
-between images 1 and 2. This corresponds to the first and second row
-of $A$, while the third and fourth row of $A$ represent the same for
-images 2 and 3. Rows 5 through 7 correspond to results of the geometry
-alignment procedure in Section
-\ref{sec:geometryAlignment}. Specifically, row 5 corresponds to a
-geometry-based constraint of image 2's location to a line of slope
-$m_2$, passing through point $gx_2$, $gy_2$, while rows 6 and 7
-correspond to a fixed location for image 1 without any degrees of
-freedom. Rows 8 through 13 correspond to the original camera locations
-for each image ($tx_i,ty_i$).
-
-The original camera poses are needed due to lack of feature matches in
-all images, or lack of enough geometry alignment results to generate a
-single solution. Since it is desirable to minimally use the original
-noisy poses, we assign to them a weighting factor of $0.01$, while all
-other equations are weighted at $1$.
-
-Since this problem is linear, it can be solved efficiently; after
-applying the resulting shifts, images overlap and match each other
-with far greater accuracy. Using the simple tile-based texturing
-scheme from Section \ref{sec:imageSelection} on these adjusted images
-results in Figure \ref{fig:compareAll}(b), which has far fewer
-discontinuities than in \ref{fig:compareAll}(a), though some 3D error
-as well as lighting differences and parallax effects are still
-visible.
-
-\section{Image Compositing}
-\label{sec:imageCompositing}
-In Section \ref{sec:imageSelection} we described an image selection
-method that reduces the list of candidate images for texturing by a
-factor of 10. In this section we go one step further to choose a
-subset of the above candidates in order to further reduce visual
-artifacts and discontinuities across textured surfaces. Specifically,
-in Section \ref{sec:mappingWithCaching}, we refine the tile-based
-texturing approach from Section \ref{sec:imageSelection}, with an
-added caching mechanism to reduce image boundaries. This method is
-general and works well given arbitrary camera poses and surfaces,
-whether large planar surfaces or small geometric interior
-features. For special cases where images have consistently
-perpendicular viewing angles to the surfaces under consideration, such
-as walls, it is possible to develop an alternative method in Section
-\ref{sec:shortestPath} to further reduce visual artifacts. Both of
-these approaches are followed by a blending step in order to produce
-final textures for each surface, as shown in Figure
-\ref{fig:flowchart}.
-
-\subsection{Tile-Mapping with Caching}
-\label{sec:mappingWithCaching}
-For the simple texture mapping method described in Section
-\ref{sec:imageSelection}, discontinuities occur where adjacent tiles
-are textured by different images. Though Section
-\ref{sec:2dAlignment}'s image alignment removes many such
-discontinuities, there are still cases where seams are visible due to
-imprecise matching or other factors such as model-based errors as
-shown in Figure \ref{fig:compareAll}(b). To reduce this, it is
-desirable to develop a spatiotemporal caching mechanism to take into
-account image selections made by neighboring tiles while texture
-mapping a given tile. By using the same image across tile boundaries,
-it is possible to eliminate a discontinuity altogether. If a tile is
-not visible in images used by neighboring tiles, using similar images
-across tile boundaries also leads to less noticeable discontinuities.
-
-The best image for a tile $t$ is selected by searching through two
-subsets of images for a viable candidate, before searching through the
-entire set of valid images obtained in Section
-\ref{sec:imageSelection}. The first subset of images is those selected
-by adjacent tiles that have already been textured. We must first check
-which of these images contain texture for $t$, and then of those, we
-make a choice according to the scoring function in Figure
-\ref{fig:scoringFunction}. Before reusing this image, we check the
-criteria $\alpha < 45^\circ$, in order to ensure a high resolution
-projection, with $\alpha$ as the camera angle as shown in Figure
-\ref{fig:scoringFunction}.
-
-If no satisfactory image is found in the first subset, we check a
-second subset of images, consisting of those taken near the ones in
-the first subset, both spatially and temporally. We use the noisy
-camera poses to determine spatial proximity. These images are not the
-same as the ones used for neighboring tiles, but are taken at a
-similar location and time, suggesting that their localization and
-projection are quite similar, and thus likely match more
-seamlessly. If no viable image is found according to the $\alpha <
-45^\circ$ criteria, we search the entire set of candidate images from
-Section \ref{sec:imageSelection}, selecting based on the same scoring
-function from Figure \ref{fig:scoringFunction}.
-
-The result of applying this caching approach to the images for the
-surface in Figure \ref{fig:compareAll}(a) is shown in Figure
-\ref{fig:compareAll}(c), where seams are considerably reduced as
-compared to Figure \ref{fig:compareAll}(b). However, some
-discontinuities are still present, as visible in the posters on the
-wall with breaks in their borders.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=1.5in]{projectionWall.pdf}}
-  \hspace{0.51in} \centering
-  \subfloat[][]{\includegraphics[width=1.5in]{projectionCeiling.pdf}}
-  \centering \hspace{0.5in}
-  \subfloat[][]{\includegraphics[width=1.5in]{projectionWallCrop.pdf}}
-  \caption{(a) Images for vertical planes are tilted, but their camera
-    axes are more or less normal to their respective planes. (b)
-    Camera axes for ceiling images are at large angles with respect to
-    plane normals. (c) Wall images are cropped to be rectangular.}
-  \label{fig:projectionAngles}
-\end{figure}
-
-\subsection{Shortest Path Texturing}
-\label{sec:shortestPath}
-
-As mentioned earlier, our data comes from a mobile backpack system
-carried by am ambulatory human operator, typically bent forwards at 15
-to 20 degrees with respect to the vertical direction. As a result,
-cameras facing sideways are head on with respect to vertical surfaces,
-as shown in Figure \ref{fig:projectionAngles}(a), while cameras
-oriented towards the top or bottom of the backpack are at an angle
-with respect to floors, ceilings and other horizontal surfaces, as
-shown in Figure \ref{fig:projectionAngles}(b). These oblique camera
-angles for horizontal surfaces translate into textures that span large
-areas once projected, as shown in Figure
-\ref{fig:projectionAngles}(b). Using the tile-based texture mapping
-criteria from Figure \ref{fig:scoringFunction}, such projections have
-highly varying scores depending on the location of a tile on the
-plane. Thus, the tiling approach in Section
-\ref{sec:mappingWithCaching} is an appropriate choice for texturing
-horizontal surfaces, as it uses the parts of image projections that
-maximize resolution for their respective plane locations, e.g. areas
-near point A and not near point B, in Figure
-\ref{fig:projectionAngles}(b).
-
-For vertical surfaces however, which make up a large portion of most
-models, images are usually taken from close distances and head-on
-angles, resulting in high resolution fronto-parallel projections. As a
-result, for each tile on a wall plane, the scoring function of Figure
-\ref{fig:scoringFunction} is relatively flat with respect to candidate
-images, as they are all more or less head on. Since the scoring
-function is less discriminative for walls, it is conceivable to devise
-a different texturing strategy to directly minimize visible seams when
-texturing them. This is done by choosing the smallest possible subset
-of images from the set selected in Section \ref{sec:imageSelection}
-and aligned in Section \ref{sec:2dAlignment} such that it (a) covers
-the entire plane and (b) minimizes the visibility of borders between
-the images. A straightforward cost function that accomplishes the
-latter is the sum of squared differences (SSD) of pixels in
-overlapping regions between all pairs of images. Minimizing this cost
-function encourages image boundaries to occur either in featureless
-areas, such as bare walls, or in areas where images match extremely
-well.
-
-In its most general form, our problem can be defined as minimally
-covering a polygon i.e. the planar surface, using other polygons of
-arbitrary geometry i.e. image projections, with the added constraint
-of minimizing the cost function between chosen images. Given that
-wall-texture candidate images are taken from more or less head-on
-angles, and knowing that only minor rotations are made in Section
-\ref{sec:2dAlignment}, we can crop our image projections to be
-rectangular with minimal texture loss as shown in Figure
-\ref{fig:projectionAngles}(c). Furthermore, because the fisheye camera
-lenses have full floor-to-ceiling coverage of nearly all walls, and
-the backpack operator logically only moves horizontally, we only need
-to ensure lateral coverage of our wall planes. We can thus construct a
-Directed Acyclic Graph (DAG) from the images, with edge costs defined
-by the SSD cost function, and solve a simple shortest path problem to
-find an optimal subset of images with regard to the SSD cost function
-\cite{dijkstra}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=4in]{dagCreation.pdf}
-  \caption{DAG construction for the image selection process. \\}
-  \label{fig:dagCreation}
-\end{figure}
-
-Figure \ref{fig:dagCreation} demonstrates the construction of a DAG
-from overlapping images of a hallway wall. Images are sorted by
-horizontal location left to right, and become nodes in a
-graph. Directed edges are placed in the graph from left to right
-between overlapping images. The weights of these edges are determined
-by the SSD cost function. Next, we add two artificial nodes, one start
-node representing the left border of the plane, and one end node
-representing the right border of the plane. The left(right) artificial
-node has directed edges with equal and arbitrary cost $C_0$ to(from)
-all images that meet the left(right) border of the plane. We now solve
-the shortest path problem from the start node to the end node. This
-results in a set of images completely covering the plane horizontally,
-while minimizing the cost of seams between images.
-
-We have now (a) mapped every location on the plane to at least one
-image, (b) decreased the number of texturing images, generally
-retaining around 20\% of the image subset obtained in Section
-\ref{sec:imageSelection}, and (c) decreased the discontinuities at
-each image border. As seen in Figure \ref{fig:compareAll}(d), this
-shortest path method has fewer visible discontinuities than Figure
-\ref{fig:compareAll}(c) corresponding to the tile caching
-approach\footnote{In Figure \ref{fig:compareAll}(d), we arbitrarily
-  chose one image for texturing where images overlap, as blending will
-  be discussed in section \ref{sec:blending}.}. This is especially
-evident when comparing the posters in the images. This shortest path
-approach approach directly reduces the cost of each image boundary,
-while the tile caching method uses a scoring function that only
-approximates this effect. Furthermore, this approach guarantees the
-best selection of images to minimize seams, while the sequential tile
-caching method may select images early on that turn out to be poor
-choices once subsequent tiles have been processed. This shortest path
-approach is also far less intensive in terms of memory usage and
-runtime, both during texture generation and rendering, as it does not
-require discretizing planes or images.
-
-When texturing a model, we apply the shortest path method on vertical
-surfaces, due to its superior results when provided with head-on
-images. Floors, ceilings, and smaller complex objects such as
-furniture, given their many images taken at oblique angles, are
-textured using the tile caching method of Section
-\ref{sec:mappingWithCaching}.
-
-\subsection{Blending}
-\label{sec:blending}
-We now apply a blending procedure to the texturing methods in Sections
-\ref{sec:mappingWithCaching} and \ref{sec:shortestPath}. Although the
-image alignment steps and image selection in both methods attempt to
-minimize all mismatches between images, there are occasional
-unavoidable discontinuities in the final texture due to different
-lighting conditions or inaccuracies in model geometry. These can
-however be treated and smoothed over by applying alpha blending over
-image seams.  Whether the units to be blended are
-rectangularly-cropped images or rectangular tiles, we can apply the
-same blending procedure, as long as there is a guaranteed overlap
-between units to blend over.
-
-For the tile caching method of Section \ref{sec:mappingWithCaching},
-we can ensure overlap by texturing a larger tile than needed for
-display. For example, for a rendered tile of size $l_1 \times l_1$, we
-can associate it with a texture $(l_1 + l_2) \times (l_1 + l_2)$ in
-size.  We have found $l_2 = \frac{l_1}{2}$ to provide a good balance
-between blending and keeping features unblurred at image
-boundaries. For the shortest path method, we already have ensured
-overlap between images. To enforce consistent blending however, we add
-a minimum required overlap of images of 200 mm while solving the
-shortest path problem in Section \ref{sec:shortestPath}. Additionally,
-if images overlap in a region greater than the overlap distance, we
-only apply blending over an area equal to the overlap distance.
-
-After linear alpha blending across overlapping regions, the texture
-mapping process is complete. Figures \ref{fig:compareAll}(e) and
-\ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. The
-remaining images in Figure \ref{fig:compareAll} highlight differences
-between the two methods, showing that Figure \ref{fig:compareAll}(f)
-has the best visual quality and the best texturing approach among the
-textures in Figure \ref{fig:compareAll}.
-
-\section{Results}
-\label{sec:results}
-This section contains results of the proposed texture mapping process
-on a number of different environments, with geometry generated from
-three different models. Further images of individual textured
-surfaces and entire textured models, as well as videos and interactive
-walkthroughs can also be found at
-\footnote{\url{http://www-video.eecs.berkeley.edu/research/indoor/}}.
-
-\subsection{Examples}
-\label{sec:examples}
-As mentioned in Section \ref{sec:dataAcquisition}, the texture mapping
-procedure in this thesis can be applied both to low-resolution and
-high-resolution models. Low resolution models have an advantage in
-their simplicity, and in that only important environmental features
-are represented. As a result, images are generated for large sections
-of buildings, and boundaries between each texture are minimally
-visible. High resolution models have an obvious advantage in terms of
-the amount of detail that can be reconstructed, but with poor region
-partitioning, as described in Section \ref{sec:geometryPartitioning},
-or with high camera pose or geometry reconstruction error, 3D elements
-in the environment geometry may not match up well with their imaged
-counterparts.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
-  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_v.png}
-  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_2d.png}
-  \includegraphics[width=2.1in,height=1.5in]{results_swarm_2_3d.png}\\
-  \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
-  } \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
-  } \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
-  }
-  \caption{The same indoor environments, as generated using (a) PCA
-    plane-fitting, (b) Floor plan extrusion, (c) Watertight mesh
-    generation. The first two are low-resolution models, while the
-    third is high-resolution}
-  \label{fig:modelcomparisons}
-\end{figure}
-
-Our approach was tested with three different geometry-reconstruction
-methods, a PCA-based plane-fitting method \cite{sanchez2012point}, a
-floor plan extrusion method \cite{turnerfloorplan}, and a
-voxel-carving mesh generation method \cite{turnerwatertight}. The
-first two methods generate lower-resolution models, containing only
-major walls, ceilings and floors. The third method generates
-high-resolution models, and attempts to reconstruct all scanned
-objects in the environment. A comparison of all three methods as
-applied to the same dataset is shown in Figure
-\ref{fig:modelcomparisons}
-
-\begin{figure}
-  \centering \subfloat[][]{
-    \includegraphics[width=3in]{results_p15_v.png}
-  } \subfloat[][]{
-    \includegraphics[width=3in]{results_p15_2d.png}
-  }
-  \caption{(a) A model generated by the PCA method with many missing
-    surfaces. (b) A watertight model generated by the floor plan
-    extrusion method.}
-  \label{fig:lowresmodels}
-\end{figure}
-
-The PCA and floor plan methods produce models at a similar level of
-detail. As visible in Figure \ref{fig:lowresmodels}, the PCA method is
-not watertight, while the floor plan method is. As a result, the
-PCA-generated model contains holes where surfaces were not adequately
-scanned. On the other hand, the watertight floor plan model sometimes
-must make assumptions about the location of surfaces that were not
-adequately scanned, in order to maintain watertightness. Because
-buildings generally follow straight lines and right angle corners
-however, such assumptions tend to be correct. Additionally, the
-floor-plan method is generally superior at reconstructing smaller
-surfaces, such as small walls, or to approximate curved surfaces,
-while the PCA method only fits large planes, and fails in both
-cases. As a result, the floor-plan method usually produces more
-visually pleasing low-resolution models, and is the method of choice
-for generating textured low-resolution models.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=3.1in]{results_houston_1_2d.png}
-  \includegraphics[width=3.1in]{results_houston_1_3d.png}\\
-  \includegraphics[width=3.1in]{results_houston_2_2d.png}
-  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
-  \subfloat[][]{
-    \includegraphics[width=3.1in]{results_houston_3_2d.png}
-  } \subfloat[][]{
-    \includegraphics[width=3.1in]{results_houston_3_3d.png}
-  }
-  \caption{(a) A model generated by the low-resolution floor plan
-    method. (b) A model generated by the high-resolution voxel-carving
-    method.}
-  \label{fig:2dvs3d}
-\end{figure}
-
-High-resolution models, as generated by the voxel-carving method, can
-produce more accurate reconstructions of environment geometry. With
-such models, region partitioning, as described in Section
-\ref{sec:geometryPartitioning}, plays an important factor in the
-quality of generated textures. If regions are small, boundaries
-between adjacent textures become visible, and since each region is
-processed independently, image alignment procedures are performed
-across smaller areas. If regions are large, then the difference
-between the 3D surface geometry and the approximated 2D texturing
-surface become large as well, introducing greater texture projection
-error. Additionally, in areas where pose error or surface
-reconstruction error is high, 3D objects in images do not get
-accurately projected onto their modeled counterparts. While large
-objects can be aligned to geometry via the methods in Section
-\ref{sec:geometryAlignment}, smaller objects such as plants or
-computers are difficult to line up to geometry references. While the
-compositing techniques is Section \ref{sec:imageCompositing} can
-ensure that textures for small objects appear seamless, such textures
-may not map accurately upon their corresponding geometry, leading to
-visually obvious discrepancies in the textured model. Figure
-\ref{fig:2dvs3d} contains textured examples from the low-resolution
-floor plan approach alongside examples from the high-resolution
-voxel-carving approach. As evident in the image comparisons, the 3D
-models may be more accurate, but the 2D models often allow for a
-cleaner visualization, with larger regions over which images are
-successfully composited together.
-
-As visible in Figure \ref{fig:2dvs3d} and other images in this
-section, 2D models using the floor plan approach are generally
-preferred, as they provide enough detail in geometry to reconstruct
-the basic layout of an environment, while textures can be used to
-visualize smaller details. On the other hand, for applications where
-furniture and smaller interior details are important, applying
-textures to the 3D voxel-carved models provides useful image-based
-context for visualizing indoor areas. Further examples of
-texture-mapped models are contained at the end of this
-document. Figure \ref{fig:indivPlanes} contains textured surfaces
-alone. Figures \ref{fig:victor1}-\ref{fig:e2d4} contain interior and
-exterior views of low-resolution models. Figures
-\ref{fig:e3d1}-\ref{fig:e3d4} contain interior and exterior views of
-high-resolution models.
-
-\subsection{Runtime}
-As mentioned earlier, our approach is quite efficient. The top wall in
-Figure \ref{fig:indivPlanes}(a) was generated with 7543 $\times$ 776
-pixels, and spans a 40-meter long wall. Given 41000 input images in
-the entire dataset, a 2.8GHz dual-core consumer-grade laptop takes
-under a second to choose 36 candidate images, followed by a minute to
-perform image projections, image alignment, and the shortest path
-texturing method. The tile-caching approach takes roughly comparable
-time, and over 75\% of the time for either method is spent on
-calculating image projections, which are cached over multiple runs,
-and also could be performed as a preprocessing step instead. While not
-real-time, the process is capable of generating fast updates after
-changes in various parameters or modifications to input data, and if
-integrated directly into a 3D modeling system, could provide quick
-visual feedback as data is collected.
-
-\subsection{Visualization}
-Our full models consist of an input model file, generated textures,
-and a mapping of image points to 3D model vertices. The textured
-models shown throughout this thesis range from 20 MB in size to over
-400 MB in a compressed format, with textures of sizes over 500
-megapixels. These models are visualized using the OpenSceneGraph
-toolkit \cite{openscenegraph}, which allows for export to many common
-model formats, as well as interactive visualization, even in web
-browsers or mobile devices.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this thesis, we have developed an approach to texture mapping
-models of indoor environments with noisy camera localization data. We
-are able to refine image locations based on geometry references and
-feature matching, and robustly handle outliers. Using the tile-based
-mapping approach, we can texture both large planar features as well as
-smaller, more complex surfaces. We also implemented a shortest path
-texturing method that produces seamless textures on planes where
-multiple head-on images are available. Both of these approaches are
-highly modular, and easily tunable for similar systems across multiple
-environments.
-
-Our method is likely to fail however in scenarios where 3D error is
-large. A logical progression of our approach to resolve camera error
-in 3D is to perform matching between image lines and geometry in 3D,
-which can be done reasonably efficiently \cite{linebased,
-  rectangularstructures}. Using linear features in addition to SIFT
-features is also likely to result in improved matches, as indoor
-scenes often have long, unbroken lines spanning multiple images
-\cite{linearposeestimation}. Finally, the blending procedure is quite
-basic, and applying more sophisticated methods of blending,
-normalization, as well as image boundary selection would benefit the
-final visual quality, and more robustly handle motion-based or
-parallax errors.
-
-\begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{finalfloors.jpg}} ~~~~~~~~
-  \\
-  \centering
-  \subfloat[][]{\includegraphics[width=6in]{finalceilings.jpg}}
-
-  \centering \subfloat[][]{
-    \includegraphics[height=2in, width=3in]{floorcropped.jpg} ~~~~~~~~
-    \includegraphics[width=3in]{pier15floor.jpg}
-  }
-  \caption{Examples of our final texture mapping output for (a) walls,
-    (b) ceilings, (c) floors}
-  \label{fig:indivPlanes}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in]{threestoryfull2.png} \\
-    \includegraphics[width=6.2in]{threestoryfull.png}
-  }
-  \caption{Textured low-resolution models from the PCA-based approach.}
-  \label{fig:victor1}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in]{fullmodel.png} \\
-    \includegraphics[width=6.2in]{pier15.png} \\
-  }
-  \caption{Textured low-resolution models from the PCA-based approach.}
-  \label{fig:victor2}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d1}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{coryf2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_2d_1.png} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_2d_2.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d2}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{office.png} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
-  }
-  \caption{A textured low-resolution model from the floor plan extrusion approach.}
-  \label{fig:e2d3}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6in,height=1.7in]{coryf2.jpg}\\
-    \includegraphics[width=6in,height=1.7in]{houston1.jpg}
-  }
-  \caption{Further exterior views of textured models.}
-  \label{fig:e2d4}
-\end{figure}
-
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d1}
-\end{figure}
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_1.png} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_2.png} \\
-    \includegraphics[width=6.2in,height=3in]{coryf2_3d_3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d2}
-\end{figure}
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d3}
-\end{figure}
-\begin{figure}
-  \centering{
-    \includegraphics[width=6.2in,height=3in]{houston1.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston2.jpg} \\
-    \includegraphics[width=6.2in,height=3in]{houston3.png}
-  }
-  \caption{A textured high-resolution model from the voxel-carving approach.}
-  \label{fig:e3d4}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%% References %%%%%
-
-\bibliography{report} %>>>> bibliography data in report.bib
-\bibliographystyle{spiebib} %>>>> makes bibtex use spiebib.bst
-
 \end{document}

### 2014-01-04 spie2014/paperv2.tex
organize stuff

--- 2013-01-20 spie/paper.tex
@@
 \begin{abstract}
+
   Automated 3D modeling of building interiors is used in applications
   such as virtual reality and environment mapping. Texturing these
-  models allows for photo-realistic visualizations of the data
-  collected by such modeling systems. We perform these tasks using a
-  backpack-mounted data acquisition system. Camera poses obtained by
-  this system and used for texturing often suffer from inaccuracies
+  models allows for photorealistic visualizations of the data
+  collected by such modeling systems. Camera poses obtained by these
+  systems and used for texturing often suffer from inaccuracies
   however, resulting in visible discontinuities when successive images
@@
   stitch images together are often computationally expensive and work
-  independently of pose estimates and geometry information. By
-  intelligently selecting images for texturing, we develop
-  an efficient method to adjust camera poses in 2D, followed by two
-  different methods to composite images together, based on the
-  geometry of surfaces being textured. The effectiveness of our
-  method is demonstrated on a number of different indoor
-  environments.
+  independently of pose estimates and geometry information. We propose
+  an efficient method to refine camera poses in 2D using both existing
+  estimates and geometry information, followed by two different
+  methods to composite images together, based on the uniformity of
+  available images. The effectiveness of our methods is demonstrated
+  on a number of different indoor environments.
 \end{abstract}
@@
 \label{sec:introduction} % \label{} allows reference to this section
+
 Three-dimensional modeling of indoor environments has a variety of
-applications in fields such as architecture, conservation, and
-simulation. Applying accurate textures to these models is important to
-add context to digital visualizations, and allows for image-based
-analysis of environments. In this paper, we perform data acquisition
-with a backpack-mounted system carried by an ambulatory human
-\cite{liu2010indoor}. This backpack system contains a series of
-cameras, laser scanners, and inertial measurement units, used to solve
-the simultaneous localization and mapping (SLAM) problem, which
-produces backpack (and therefore camera) poses over time as well as a
-point cloud representing the surrounding environment
-\cite{chen2010indoor, liu2010indoor, kua2012loopclosure}. For
-environment geometry, we work with models obtained by fitting
-low-resolution planar surfaces to these point clouds
-\cite{sanchez2012point}.
+applications such as training and simulation for disaster management,
+virtual heritage conservation, and mapping of hazardous sites. Manual
+construction of these digital models can be time-consuming, and as a
+result, automated 3D site modeling has garnered much interest in
+recent years.
 
-While a human-carried system provides advantages over more common
-wheeled systems in terms of agility and portability, it often leads to
-relatively high localization error even after applying sophisticated
-localization techniques \cite{liu2010indoor}. Furthermore, our model
-geometry usually contains some error as well, and is often tuned to
-ignore low-resolution features, such as small walls, furniture, and
-other minor non-planar features commonly found in indoor
-environments. As a result, methods for texture mapping that rely on
-accurate camera poses and projection surfaces generally produce poor
-results, while more sophisticated methods to accurately align images
-in 3D lead to high runtime on our typically very large datasets. In
-contrast, we present a method, which given a high number of images,
-searches for a subset of them that can be successfully aligned with 2D
-adjustments alone.
+The first step in automated 3D modeling is the physical scanning of an
+environment's geometry. An indoor modeling system must recover its own
+poses within an environment while simultaneously reconstructing the 3D
+structure of the environment itself \cite{chen2010indoor,
+  liu2010indoor, kua2012loopclosure}. This is known as the
+simultaneous localization and mapping (SLAM) problem, and is generally
+solved by taking readings from laser range scanners, cameras, and
+inertial measurement units (IMUs) at multiple locations within the
+environment.
+
+In this paper, we work with data obtained from a backpack-mounted
+system, carried by an ambulatory human. Such a system provides
+advantages over more common wheel-mounted systems in terms of agility
+and portability, but results in higher difficulty and error when
+performing localization \cite{liu2010indoor}. As a result, common
+approaches to texture mapping that rely on accurate camera poses
+produce poor results, leading to the development of the approaches
+contained in this paper. Besides localization information and images,
+environment geometry is required as well for texture mapping. In this
+paper we work with models obtained by fitting planar surfaces to point
+clouds generated by the backpack system \cite{sanchez2012point}.
+
+Though our texture mapping procedure was designed with the
+aforementioned system in mind, it is applicable to other systems,
+provided the required inputs of planar geometry, images with rough
+extrinsic pose estimates, and either known or estimated intrinsic
+camera calibration matrices. An important benefit of our method is its
+relatively low complexity and runtime, and independence of many steps,
+allowing for efficient tuning of parameters and easy accomodation of
+new input data given updates in localization or model-generation
+algorithms.
 
 The remainder of the paper is organized as follows. Section
-\ref{sec:simpleTextureMapping} explains how images are projected onto
-our geometry and explains a simple approach towards selecting images
-for texturing. Section \ref{sec:existingApproaches} covers existing
-approaches to image stitching, and their performance on our
-datasets. Section \ref{sec:2dAlignment} contains our approach towards
-efficient 2D image alignment, followed by Section
+\ref{sec:simpleTextureMapping} explains how input images are projected
+onto our geometry and a simple approach towards texturing. Section
+\ref{sec:existingApproaches} covers more sophisticated existing
+approaches, using image matching and stitching, and their performance
+on our datasets. Section \ref{sec:2dAlignment} contains our approach
+towards image alignment, followed by Section
 \ref{sec:imageCompositing}, which describes our two methods of
@@
 results and conclusions.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The geometry of the texture mapping process for a planar surface is
-shown in Figure \ref{fig:projection}.  We are provided with a set of
-$M$ images to texture a target plane, where each image has a camera
-matrix $P_i$ for $i=1..M$, which translates a 3D point in the world
-coordinate system to a 2D point or pixel in image $i$'s coordinates. A
-camera matrix $P_i$ is composed of the camera's intrinsic parameters,
-containing focal length and image center, as well as extrinsic
-parameters which specify the rotation and translation of the camera's
-position in 3D world coordinates at the time that image $i$ is
-taken. These extrinsic parameters are determined by the backpack
-hardware and localization algorithms \cite{chen2010indoor,
-  liu2010indoor, kua2012loopclosure} and are substantially noisy.
+shown in Figure \ref{fig:projection}.  As described earlier, we are
+provided with a set of $M$ images to texture a target plane. Each
+image has a camera matrix $P_i$ for $i=1..M$, which translates a 3D
+point in the world coordinate system to a 2D point or pixel in image
+$i$'s coordinates. A camera matrix $P_i$ is composed of the camera's
+intrinsic parameters, containing focal length and image center, as
+well as extrinsic parameters which specify the rotation and
+translation of the camera's position in 3D world coordinates at the
+time that image $i$ is taken. These extrinsic parameters are
+determined by the backpack hardware and localization algorithms
+\cite{chen2010indoor, liu2010indoor, kua2012loopclosure} and are quite
+noisy.
 
-Because our backpack system takes photos at a rate of 5 Hz, hundreds
+Because our backpack system takes photos at a rate of 5 Hz, thousands
 of images are available for texturing each surface in our model. Our
@@
     \includegraphics[height=1.5in]{Projection.pdf}
-    \caption{Surfaces to be textured are specified in 3D space by
-      corners $C_i$. Images are related to each surface through the
-      camera matrics $P_{1..m}$. }
+    \caption{Planes are specified in 3D space by four corners $C_1$ to
+      $C_4$. Images are related to each plane through the camera
+      matrics $P_{1..m}$. }
     \label{fig:projection}
@@
 a simple texturing approach can be performed by discretizing the
-target plane into small square tiles, and choosing an image to texture
-each tile directly.
+target plane into small square tiles, in our case 5 pixels across, and
+choosing an image to texture each tile.
 
@@
 inside buildings are horizontal or vertical, any visible seams in our
-texture will intersect them minimally and be less noticeable.
+texture thus intersect them minimally and are less noticeable.
 
-In order to select an image for texturing a tile $t$, we first gather
-a list of candidate images that contain all four of its corners, which
-we can quickly check by projecting $t$ into each image using the $P_i$
-camera matrices. Furthermore, each candidate image must have been
-taken at a time when its camera had a clear line-of-sight to $t$,
-which can be calculated using standard ray-polygon intersection tests
-between the camera location, $t$, and every other plane
-\cite{rayintersection}.
+In order to select an image for texturing a tile $t$, we must first
+gather a list of candidate images that contain all four of its
+corners, which we can quickly check by projecting $t$ into each image
+using the $P_i$ camera matrices. Furthermore, each candidate image
+must have been taken at a time when its camera had a clear
+line-of-sight to $t$, which can be calculated using standard
+ray-polygon intersection tests between the camera location, $t$, and
+every other plane \cite{rayintersection}.
 
@@
 function in order to objectively select the best image for texturing
-$t$. Since resolution decreases and camera pose errors become more
-extreme over distance, we wish to minimize the distance between
-cameras and the surfaces they texture. Additionally, we desire images
-that are projected perpendicularly onto the plane, maximizing the
-resolution and amount of useful texture available in their
-projections, as well as minimizing any parallax effects due to
-real-world geometry not accurately represented by our digital
-model. In other words, we wish to minimize the angle between the
-tile's normal vector and the camera axis for images selected for
-texturing that tile. These two criteria can be met by maximizing the
-function $\frac{1}{d} (-1 \cdot \vec{c}) \cdot \vec{n}$ as shown in
-Figure \ref{fig:scoringFunction}. Specifically, $d$ is the distance
-between the centers of a camera and a tile, and $\vec{n}$ and
-$\vec{c}$ are the directions of the plane's normal and the camera axis
-respectively.
+$t$. Since resolution decreases and camera pose errors compound over
+distance, we wish to minimize the distance between cameras and the
+surfaces they texture. Additionally, we desire images that are
+projected perpendicularly onto the plane, maximizing the resolution
+and amount of useful texture available in their projections, as well
+as minimizing any parallax effects due to real-world geometry not
+accurately represented by our digital model. In other words, we wish
+to minimize the angle between the tile's normal vector and the camera
+axis for images selected for texture mapping. These two criteria can
+be met by maximizing the function $\frac{1}{d} (-1 \cdot \vec{c})
+\cdot \vec{n}$ as shown in Figure
+\ref{fig:scoringFunction}. Specifically, $d$ is the distance between
+the centers of a camera and a tile, and $\vec{n}$ and $\vec{c}$ are
+the directions of the plane's normal and the camera axis respectively.
 
@@
 
-As Figure \ref{fig:compareAll}(a) demonstrates, there are many image
-boundaries with abrupt discontinuities between tiles, due to
-significant misalignment between images, though most of it appears to
-be reconcilable using 2D transforms. Given our high number of input
-images, a better image selection procedure will further improve
-results, as described in Section \ref{sec:imageCompositing}, but a
-more significant and reliable improvement can be found through first
-improving the alignment of our images.
+As Figure \ref{fig:compareAll}(a) demonstrates, this approach leads to
+the best texture for each tile independently, but results in many
+image boundaries with abrupt discontinuities between tiles, due to
+significant misalignment between images. Given our high number of
+input images, a better image selection procedure could be used, as
+described in Section \ref{sec:imageCompositing}, but a more
+significant and reliable improvement can be found through the
+alignment of our images.
 
@@
 \label{sec:existingApproaches}
-Stitching together multiple images to produce a larger, seamless image
-is a commonly performed task, with many successful approaches over the
-past years. Generally, parts of images are matched to each other,
-usually through direct comparisons or feature detection and
-matching. Images are then transformed to maximize matches, often by
-calculating homographies between pairs of images, or by iteratively
-adjusting camera poses in 1 to 6 degrees of freedom.
+Stitching together multiple images to produce a larger image is a
+commonly performed task, with many successful approaches over the past
+few decades. Parts of images are first matched to eachother, through
+direct pixel comparisons, or more commonly through feature detection
+and matching. Images are then adjusted to maximize matches, either by
+calculating homographies between pairs of images, or by modifying
+camera poses in 1 to 6 degrees of freedom.
 
-Feature matching has a number of advantages over direct matching that
-make it more suitable for our often non-planar data, and rotational
-differences \cite{szeliski2006image}. Feature matching however, works
-best when multiple unique visual references exist in the environment
-that can be detected in multiple images. In contrast, our indoor
-environments have a high prevalence of bare surfaces, as well as
-repeating textures, such as similar windows, doors, and wall-mounted
-decorations, that cause difficulty in disambiguating features. This
-lack of reliable reference points often results in errors when
-matching images together.
+Feature detection and matching works best when multiple unique visual
+references exist in the environment and are present within multiple
+images. In contrast, our indoor environments have a high prevalence of
+bare surfaces, as well as repeating textures that cause difficulty in
+disambiguating features. This lack of reliable reference points often
+results in errors when matching images together.
 
 Additionally, our datasets often contain long chains of images, which
-leads to error accumulation when image correspondences are not exact
-and are compounded together. For example, when matching a long chain
-of images through homographies, a pixel in the $nth$ image is
-translated into the first image's coordinates by multiplying by the
-$3\times3$ matrices $H_1 H_2 H_3 ... H_n$. Errors in any of these
-homography matrices are propagated to all further images, resulting in
-drift.
+leads to error accumulation when image correspondences are not
+accurate. For example, when matching a long chain of images through
+homographies, a pixel in the $nth$ image is translated into the first
+image's coordinates by multiplying by the $3\times3$ matrices $H_1 H_2
+H_3 ... H_n$. Errors in any of these homography matrices are
+propagated to all further images, resulting in drift. Figure
+\ref{fig:mosaic3D}(a) shows the output of the AutoStitch software
+package, which performs homography-based image mosaicing
+\cite{autostitch}. Though AutoStitch performs well in areas with dense
+features, it has difficulty with even short segments of bare walls,
+and produces errors that cause straight lines to appear
+distorted. Many areas with fewer visual features or repeating texture
+patterns failed outright using AutoStitch.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{graphApproach.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{autostitchResult.jpg}}
 
   \centering
-  \subfloat[][]{\includegraphics[width=6in]{autostitchResult.jpg}}
+  \subfloat[][]{\includegraphics[width=6in]{graphApproach.jpg}}
 
@@
 
-  \caption{Texture alignment via (a) the graph-based localization
-    refinement algorithm, (b) the AutoStitch software package, and (c)
-    our method.}
+  \caption{Texture alignment via (a) image mosaicing, (b) the
+    graph-based localization refinement algorithm from
+    \cite{chen2010indoor}, and (c) the method proposed in this paper.}
   \label{fig:mosaic3D}
@@
 
-Past work with our data acquisition backpack integrated image
-stitching with an iterative localization algorithm, and performed
-homography-based camera pose refinement \cite{liu2010indoor}. When run
-on long chains of images, especially where features are sparse, it
-produces distorted textures, as seen in Figure \ref{fig:mosaic3D}(a),
-due to the problems described above. This approach is also not
-closed-form, and its iterative camera adjustment process over our
-large datasets leads to prohibitively long computation time.
+Image projections can also be aligned by iteratively adjusting camera
+poses to maximize matches. This is generally done over 6 degrees of
+freedom \cite{liu2010indoor}. The approach in [2] works well locally,
+but over larger areas results again in error accumulation and drift,
+as shown in Figure \ref{fig:mosaic3D}(b). Furthermore, it adjusts
+image locations using a long iterative process, which results in high
+runtime.
 
-The AutoStitch software package performs homography-based alignment as
-well, with additional provisions that attempt to reduce drift
-\cite{panorama2d, autostitch}. Though AutoStitch also performs well in
-areas with dense features, it can not handle areas without features,
-and has trouble aligning wall sections with even short segments of
-bare texture. The example in Figure \ref{fig:mosaic3D}(b) was
-generated after manual tuning, and areas with fewer visual features or
-repeating texture patterns simply failed outright with AutoStitch.
-
-\section{2D Image Alignment}
+\section{2D Image Alignment with Geometry Information}
 \label{sec:2dAlignment}
-
 In this section, we describe our method of efficient and robust image
-alignment. Though state-of-the-art techniques towards image stitching
-work in 3D, we elect to perform image alignments entirely in
-2D. Besides the benifits of reduced complexity, we have found 2D
-alignment to work well for two main reasons. First, because we have
-such a large number of images to choose from, the compositing
-approaches in Section \ref{sec:imageCompositing} are able to select a
-subset of images that align well, given only 2D alignments. Second,
-the nature of our input data is such that localization error chiefly
-occurs in two dimensions, in the same plane as the surface being
-projected onto. Our data acquisition system contains cameras facing to
-the sides of the operator. The operator makes efforts to walk parallel
-to walls, and the localization and model-generation algorithms that
-provide our input conform the operator's path to be straight and
-parallel to detected surfaces \cite{kua2012loopclosure,
-  sanchez2012point}. Since the operator also walks in a manner to keep
-the backpack balanced, errors in roll and yaw are minimal. Thus, our
-highest errors stem from uncertainty in the operator's pitch,
-equivalent to rotation around the camera axes, as well as location
-along surfaces. These equate to 2D rotation and translation in a
-surface's plane.
-
-Our 2D alignment procedure consists of three parts. First, all images
-are projected onto the surface and lines within these projections are
-detected. These lines are then rotated and shifted to match
+alignment. Our approach consists of three main parts. First, all
+images are projected onto the surface and lines within these
+projections are detected. These lines are then matched up with
 geometry-based lines comprising the surface's boundary and
@@
 parallel. Third, we detect SIFT feature matches between pairs of
-images and solve a weighted linear least squares problem in 2D to
-maximize matches.
+images and solve a linear least squares problem in 2D to maximize
+matches.
+
+All of our following calculations and alignments are performed in 2D,
+partly for efficiency, partly because we have a large number of images
+to choose from, and partly because the nature of our input data is
+such that localization error chiefly occurs in two dimensions, in the
+same plane as the surface being projected onto. Recall that our data
+acquisition system is backpack-mounted, with cameras facing to the
+sides of the operator. The operator makes efforts to walk parallel to
+walls, and the localization and model-generation algorithms that
+provide our input conform the operator's path to be straight and
+parallel to detected surfaces \cite{kua2012loopclosure,
+  sanchez2012point}. Since the operator walks in as upright a position
+as possible, errors in roll, yaw, and the operator's distance from
+parallel surfaces are minimal. Thus, our highest errors stem from
+uncertainty in the operator's pitch, equivalent to rotation around the
+camera axes, as well as location along surfaces. These equate to 2D
+rotation and translation in a surface's plane.
 
@@
 described in Section \ref{sec:simpleTextureMapping}, we detect line
-segments in the image projections using Hough transforms, as shown in
-Figure \ref{fig:geometryAlignment}(a). Experience and intuition show
-that walls in indoor environments often contain linear features that
-are either horizontal or vertical, corresponding to doors, windows,
-posters, etc. Thus, when texturing walls, we rotate images in 2D such
-that dominant lines are made to be horizontal or vertical. This can be
-further generalized by instead orienting lines to be parallel with a
-surface's boundaries, which makes it applicable to non-rectangular
-surfaces, such as ceilings, floors, or slanted walls.
+segments in the image projections using Hough transforms. Experience
+and intuition show that walls in indoor environments often contain
+linear features that are either horizontal or vertical, corresponding
+to doors, windows, posters, etc. Thus, when texturing walls, we rotate
+images in 2D such that dominant lines are made to be horizontal or
+vertical. This can be further extrapolated by orienting lines with a
+wall's boundaries, for example in areas with a slanted roof.
 
@@
   \centering
-  \subfloat[][]{\includegraphics[height=3in]{detectedLines.png}}
-  \hspace{0.4 cm}
-  \subfloat[][]{\includegraphics[height=3in, width=4in]{bothunalignedaligned.png}}
-  \caption{(a) Lines detected in image projections via Hough transform
-    (b) In this example, we project two images at once for the sake of
-    demonstration, where the red lines are geometry-based lines where
-    surfaces intersect, and the green ines are lines detected in the
-    image. Above are the original projections using input camera
-    poses, and below are the projections after rotation and
-    translation for alignment.}
+  \subfloat[][]{\includegraphics[height=1.5in]{geometryAlign_planes.png}}
+  \subfloat[][]{\includegraphics[height=1.5in]{geomAlign}}
+  \caption{(a) When texturing the red surface, it makes sense to align
+    images to surface boundaries and intersections with other
+    surfaces. (b) The darker lines are geometry-based lines, while
+    lighter lines are lines detected in the image via Hough
+    transform. Above is the original projection using the input camera
+    poses, and below is the projection after rotation and translation
+    for alignment.}
   \label{fig:geometryAlignment}
@@
 
-Furthermore, at this point in time, image occlusions have not been
-accounted for. As a result, some image projections contain texture
-that should project to an adjacent surface, sometimes with a visible
-linear boundary where the two surfaces meet. If this linear boundary
-can be detected by Hough transform, the image is rotated and shifted
-in 2D such that the visual boundary between two surfaces in an image
-projection matches the physical boundary in our digital model. An
-example of such an adjustment is in Figure
-\ref{fig:geometryAlignment}(b) and \ref{fig:geometryAlignment}(c).
+At this point in time, image occlusions have not been accounted
+for. As a result, some image projections contain texture that should
+project to an adjacent surface, generally with a linear boundary where
+the two surfaces meet. If this linear boundary is detected by Hough
+transform, the image is rotated and shifted in 2D such that the visual
+boundary between two surfaces in an image projection matches the
+physical boundary in our digital model. An example of such an
+adjustment is in Figure \ref{fig:geometryAlignment}
 
-To perform rotation, we use a RANSAC \cite{fischler1981random}
-framework to determine an optimal rotation angle between lines in our
-image and lines in our geometry. RANSAC allows us to ignore erroneous
-lines in our image, such as the slanted lines corresponding to the
-ladder in Figure \ref{fig:geometryAlignment}(a). Once this rotation is
-discovered and applied, we gather all pairs of image line segments and
-geometry line segments with less than $0.1^\circ$ difference in
-orientation and less than 250 mm distance at their furthest points. If
-2 or more pairs exist, we select the 2 that contain the longest
-noncollinear image-based line segments, and perform the corresponding
-fixed translation to match them. If we only have 1 pair, we perform
-the minimal shift to match the lines of that pair, and make note of
-their orientation, for usage in Section
-\ref{sec:robustSIFTFeatureMatching}.
+To perform the rotation and alignment, we use the RANSAC
+\cite{fischler1981random} framework. RANSAC allows us to determine an
+optimal rotation and translation to match up two groups of line
+segments, while accounting for outliers. First, a rotation angle is
+computed by gathering all pairs of image line segments and geometry
+line segments with less than 20 degrees between them. We then run the
+RANSAC algorithm by sampling 4 of these angles at a time, and using
+their average as the fitting function. Angles over 2 degrees from this
+average are considered outliers. Once this 2d rotation angle is
+determined, it is applied to the image, and projections are
+re-calculated and image-based lines are re-detected. Now, all pairs of
+image line segments and geometry line segments with less than 0.2
+degree difference and less than 250 mm distance at their furthest
+points are gathered. RANSAC is then similarly employed to calculate
+optimal horizontal and vertical translations independently, by
+sampling 4 pairs at a time and considering an outlier threshold of 10
+mm. If a translation is applied, we indicate that the image was
+aligned to geometry in one or both dimensions, which will reduce
+further shifting in Section \ref{sec:robustSIFTFeatureMatching}.
 
@@
 perform a simple recursive occlusion procedure on each image. This is
-done by performing the intersection tests in Section
+done by performing the intersection tests in section
 \ref{sec:simpleTextureMapping} in a regularly spaced grid. Where four
 corners of a rectangular region are occluded, texture is
-removed. Where no corners are occluded, the recursion stops. Where
-there is a mixture of both, the rectangular region is subdivided into
-four, and the same process is performed on each. By performing Section
+removed. Where no corners are occluded, nothing occurs. Where there is
+a mixture of both, the rectangular region is subdivided into four, and
+the same process is performed on each. By performing Section
 \ref{sec:geometryAlignment}'s alignment procedure before occlusion,
@@
 \label{sec:robustSIFTFeatureMatching}
-Our next step is to align images by searching for corresponding points
-between all pairs of overlapping images. We use feature alignment
-rather than pixel or intensity-based alignment due to the differences
-in lighting as well as possible occlusion among our images, both of
-which feature alignment is less sensitive to \cite{lowe1999object,
-  mikolajczyk2005performance, szeliski2006image}.  We use SiftGPU
-\cite{siftgpu} for its high performance on both feature detection as
-well as pairwise matching. These matches determine $dx$ and $dy$
-distances between each pair of features for two image projections,
-though these distances may not always be the same for different
-features. Since indoor environments often contain repetitive features
-such as floor tiles or doors, we need to ensure that SIFT-based
-distances are reliable. First, we only perform alignment on parts of
-images that overlap given the original noisy poses. Second, we discard
-feature matches that correspond to an image distance greater than 200
-mm from what the noisy poses estimate. In order to utilize the
-remaining feature matches robustly, RANSAC \cite{fischler1981random}
-is again used to estimate the optimal $dx_{i,j}$ and $dy_{i,j}$
-distances between two images $i$ and $j$. We use a 5 mm threshold for
-RANSAC, so that SIFT matches are labeled as outliers if their distance
-is not within 5 mm of the sampled average distance.
+Our next step is to align overlapping images by searching for
+corresponding points between all pairs of overlapping images. We use
+SIFT features for their high detection rate, and choose to use feature
+alignment rather than pixel or intensity-based alignment due to the
+differences in lighting as well as possible occlusion among our
+images, both of which feature alignment is less sensitive to
+\cite{lowe1999object, mikolajczyk2005performance, szeliski2006image}.
+We use SiftGPU \cite{siftgpu} for its high performance on both feature
+detection as well as pairwise matching. These matches determine $d^x$
+and $d^y$ distances between each pair of features for two image
+projections, though these distances may not always be the same for
+different features. Since indoor environments often contain repetitive
+features such as floor tiles or doors, we need to ensure that
+SIFT-based distances are reliable. First, we only perform alignment on
+parts of images that overlap given the original noisy poses. Second,
+we discard feature matches that correspond to an image distance
+greater than 40 pixels from what the noisy poses estimate. In order to
+utilize the remaining feature matches robustly, RANSAC
+\cite{fischler1981random} is again used to estimate the optimal
+$d^x_{i,j}$ and $d^y_{i,j}$ distances between two images $i$ and
+$j$. For this application, the RANSAC fitting function finds the
+average distance between selected matches in a pair of images, and the
+distance function for a pair of points is chosen to be the difference
+between those points' SIFT match distance and the average distance
+computed by the fitting function. We use a 10 pixel threshold, so that
+SIFT matches are labeled as outliers if their horizontal or vertical
+distances are not within 10 pixels of the average distance computed by
+the fitting function.
 
-We now use the $dx_{i,j}$ and $dy_{i,j}$ distances between each pair
-of images to refine their positions using weighted linear least
-squares. The variables we wish to solve for are the $_ix$ and $y_i$
-positions of our images, while our equations are the SIFT-based
-distances between pairs of images, images fixed to geometry with 0 or
-1 degrees of freedom, and the original camera poses. Ignoring
-weighting and the original camera poses for now, an example setup for
-solving $\textrm{min}_{\vec{\beta}} ||A \vec{\beta} -
-\vec{\gamma}||_2^2 $ with 3 images is shown below.
+We now use the RANSAC-calculated $d^x_{i,j}$ and $d^y_{i,j}$ distances
+between each pair of images to refine their positions using weighted
+linear least squares. There are a total of $M^{2}$ possible pairs of
+images, though we only generate distances between images with SIFT
+matches. Given these distances and the original image location
+estimates, we can solve a least squares problem
+($\textrm{min}_{\vec{\beta}} ||A \vec{\beta} - \vec{\gamma}||_2^2 $)
+to estimate the location of the images on the plane. The
+$M$-dimensional vector $\vec{\beta}$ represents the unknown $x$
+location of each image on the plane for $1 \dots M$. The optimal $x$
+and $y$ locations are obtained in the same way, so we only consider
+the $x$ locations here:
 
+\[\vec{\beta} =
+\begin{pmatrix}
+  x_1, & x_2, & x_3, & \cdots & x_{M-1}, & x_M
+\end{pmatrix}
+\]
+
+The $N \times M$ matrix $A$ is constructed with one row for each pair
+of images with measured distances produced by the SIFT matching
+stage. A row in the matrix has a $-1$ and $1$ in the columns
+corresponding to the two images in the pair. For example, the matrix
+below indicates a SIFT-based distance between images 1 and 2, images 1
+and 3, images 2 and 3, etc.
 \[
@@
 \begin{pmatrix}
-  -1 & 1 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & -1 & 1 & 0\\
-  0 & -1 & 1 & 0 & 0 & 0\\
-  0 & 0 & 0 & 0 & -1 & 1\\
-  1 & 0 & 0 & 0 & 0 & 0\\
-  0 & 0 & 0 & 1 & 0 & 0\\
-  0 & -m & 0 & 0 & 1 & 0\\
-\end{pmatrix}\quad
-\vec{\beta} =
+  -1 & 1 & 0 & \cdots & 0 & 0\\
+  -1 & 0 & 1 & \cdots & 0 & 0\\
+  0 & -1 & 1 & \cdots & 0 & 0\\
+  \vdots  & \vdots & \vdots & \ddots & \vdots  & \vdots\\
+  0 & 0 & 0 & \cdots & 1 & 0 \\
+  0 & 0 & 0 & \cdots & -1 & 1 \\
+  1 & 0 & 0 & \cdots & 0 & 0\\
+\end{pmatrix}
+\]
+If only relative distances between images are included, the absolute
+location of the images can not be calculated, and the matrix is rank
+deficient. From Section \ref{sec:geometryAlignment}, a number of
+images are anchored to geometry points, in one or both dimensions, and
+thus their locations can be used to fix the rest in place. In case no
+anchor images exist, we simply arbitrarily pick an image, as we have
+no other reference points to work with. In the above matrix, the first
+image is set to be such an anchor, simply by placing a $1$ in its
+column.
+
+The $N$-dimensional observation vector $\vec{\gamma}$ is constructed
+using the SIFT-based distances generated in the RANSAC matching
+stage. Elements in the observation vector corresponding to anchor
+images are simply their locations as determined by the original noisy
+localization. Thus a $\vec{\gamma}$ corresponding to the above matrix
+can be written as:
+
+\[
+\vec{\gamma}^T =
 \begin{pmatrix}
-  x_1, \\ x_2, \\ x_3, \\ y_1, \\ y_2, \\ y_3
-\end{pmatrix}
-\vec{\gamma} =
-\begin{pmatrix}
-  dx_{1,2}, \\ dy_{1,2}, \\ dx_{2,3}, \\ dy_{2,3}, \\ t1_x, \\ t1_y, \\ -mx_2 +
-  ty_2
+  d_{1,2}, &d_{1,3}, &d_{2,3}, &\hdots &d_{N-2,N-1}, &d_{N-1,N}, &x_1
 \end{pmatrix}
@@
 
-In this scenario, a SIFT-based distance of $dx_{1,2}$, $dy_{1,2}$ was
-calculated between images 1 and 2. This corresponds to the first and
-second row of $A$, while the third and fourth row of $A$ represent the
-same for images 2 and 3. Rows 5 and 6 of $A$ correspond to a fixed
-location of $tx_1$, $ty_1$ for image 1, while Row 7 corresponds to a
-constraint to a line of slope $m$, with current location $tx_2$,
-$ty_2$, both possible results of the geometry alignment procedure in
-Section \ref{sec:geometryAlignment}. If we do not have enough SIFT
-matches, or lack images matched to geometry, our matrix becomes
-rank-deficient and our problem cannot be solved. As a result, we add
-rows for each image corresponding to the original noisy image
-locations, and downweight them heavily, e.g. with a weight of 0.01
-versus 1.
+The $\vec{\beta}$ that minimizes $||A \vec{\beta} -
+\vec{\gamma}||_2^2$ results in a set of image locations on the plane
+that best honors all the SIFT-based distance measurements between
+images. This solution however does not make use of our noisy camera
+poses, and will fail when no SIFT matches are found between one
+segment of the plane and another. To account for this, we add rows to
+the $A$ matrix and observations to the $\vec{\gamma}$ vector
+corresponding to the original noisy distances. We then add weighting
+to our least squares problem where the SIFT distances and anchor
+values are given a high weight e.g. 1, while the noisy distances are
+given a smaller weight e.g. 0.01.
 
-Because our problem is linear, it is easily and quickly solved, and
-after applying the resulting shifts, our images overlap and match each
-other with far greater accuracy. Applying the simple mapping scheme in
+After completing this same process for the $y$ dimension as well, and
+making the resultant shifts, our images overlap and match each other
+with far greater accuracy. Applying the simple mapping scheme in
 Section \ref{sec:tileBasedMapping} to the same wall used in that
@@
 discontinuities, though errors due to lighting differences and
-parallax effects are still visible.
+repeating features are still visible.
 
@@
 Figure \ref{fig:compareAll}(b). However, some discontinuities are
-still present, as visible in the posters on the wall with breaks
+still present, as visible in the many posters on the wall with breaks
 in their borders.
@@
   \centering
-  \includegraphics[width=5in]{dagCreation.pdf}
+  \includegraphics[width=3in]{dagCreation.pdf}
   \caption{DAG construction for the image selection process. \\}
@@
   as blending will be discussed in section \ref{sec:blending}.}. This
-is especially evident when comparing the posters in the images. This
-shortest path approach approach directly reduces the cost of each
-image boundary, while the tile caching method uses a scoring function
-that only approximates this effect. Furthermore, this approach
-guarantees the best selection of images to minimize seams, while the
-sequential tile caching method may select images early on that turn
-out to be poor choices once subsequent tiles have been processed. This
-shortest path approach is also far less intensive in terms of memory
-usage and runtime, both during texture generation and rendering, as it
-does not require discretizing planes or images.
+is especially evident when comparing the posters in the images, as
+seen in Figures \ref{fig:compareAll}(e) and
+\ref{fig:compareAll}(f). This shortest path approach approach directly
+reduces the cost of each image boundary, while the tile caching method
+uses a scoring function that only approximates this
+effect. Furthermore, this approach guarantees the best selection of
+images to minimize seams, while the sequential tile caching method may
+select images early on that turn out to be poor choices once
+subsequent tiles have been processed. This shortest path approach is
+also far less intensive in terms of memory usage and runtime, both
+during texture generation and rendering, as it does not require
+discretizing planes or images.
 
@@
 After performing linear alpha blending across overlapping regions, our
-texture mapping process is complete. Figures \ref{fig:compareAll}(e)
-and \ref{fig:compareAll}(f) show the blended versions of Figures
-\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. The
-remaining images in Figure \ref{fig:compareAll} highlight differences
-between the two methods, showing that Figure \ref{fig:compareAll}(f)
-clearly has the best visual quality and the best texturing approach
-among the textures in Figure \ref{fig:compareAll}.
+texture mapping process is complete. Figures \ref{fig:compareAll}(g)
+and \ref{fig:compareAll}(h) show the blended versions of Figures
+\ref{fig:compareAll}(c) and \ref{fig:compareAll}(d) respectively. It
+is clear that the shortest path approach exhibits much better
+alignment and fewer seams than the tile-caching method, as Figure
+\ref{fig:compareAll}(h) clearly has the best visual quality among the
+textures in Figure \ref{fig:compareAll}.
 
@@
 pixels, and spans a 40-meter long wall. Given 41000 input images, a
-2.8GHz dual-core consumer-grade laptop takes approximately a minute to
-pick 36 candidate images, followed by another minute to perform both
-image alignment and the shortest path texturing method, though over
-75\% of that time is spent calculating SIFT matches within the SiftGPU
+2.8GHz consumer-grade laptop takes approximately a minute to pick 36
+candidate images, followed by another minute to perform both image
+alignment and the shortest path texturing method, though over 75\% of
+that time is spent calculating SIFT matches within the SiftGPU
 framework. While not real-time, the process is capable of generating
@@
 input data, and if integrated directly into a modeling system, could
-provide live visualization as data is collected. Our full models
-consist of our input model file, textures that we generate, and a
-mapping of image points to model vertices. The models shown in Figure
-\ref{fig:results} are roughly 20 MB in size, and are visualized using
-the OpenSceneGraph toolkit \cite{openscenegraph}, which allows for
-export to many common model formats, as well as efficient
-visualization, even in web browsers or mobile devices.
+provide live visualization as data is collected.
 
@@
 images are available. Both of these approaches are highly modular, and
-easily tunable for similar systems across multiple environments.
+easily tunable for different environments and acquisition systems.
 

### 2014-01-04 spie2014/spiepaper.tex
organize stuff

--- 2014-01-04 spie2013/paper.tex
@@
 evident when comparing the posters in the images. This shortest path
-approach directly reduces the cost of each image boundary,
+approach approach directly reduces the cost of each image boundary,
 while the tile caching method uses a scoring function that only

### 2014-01-04 spie2014/spie2014.tex
minimal, just runtime now

@@
     refinement algorithm, (b) the AutoStitch software package, and (c)
-    the proposed method.}
+    the method proposed in this paper.}
   \label{fig:mosaic3D}
@@
 \begin{figure}
-  \centering
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
-  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
-  \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
-  } \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
-  } \subfloat[][]{
-    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
+  \centering{
+    \includegraphics[width=3in]{threestoryfull2.png}
+    \includegraphics[width=3in]{threestoryfull.png} \\
+    \includegraphics[width=3in]{fullmodel.png}
+    \includegraphics[width=3in]{pier15.png}
   }
-  \caption{The same indoor environments, as generated using (a) PCA
-    plane-fitting, (b) Floor plan extrusion, (c) Voxel carving. The
-    first two are lower-resolution models, while the third is
-    higher-resolution, and reconstructs significantly more features,
-    such as the ladder in the lower image.}
-  \label{fig:modelcomparisons}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=3.1in]{results_houston_2_2d.png}
-  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
-  \subfloat[][]{
-    \includegraphics[width=3.1in]{results_houston_3_2d.png}
-  } \subfloat[][]{
-    \includegraphics[width=3.1in]{results_houston_3_3d.png}
+  \caption{Textured models from the PCA-based approach.}
+  \label{fig:pcaModels}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=3in]{houston2d1.png}
+    \includegraphics[width=3in]{coryf2.jpg} \\
+    \includegraphics[width=3in]{houston3_2.png}
+    \includegraphics[width=3in]{office.png}
   }
-  \caption{(a) A model generated by the low-resolution floor plan
-    method. (b) A model generated by the high-resolution voxel-carving
-    method. The high-resolution model contains far more surface
-    detail, such as in the ceiling indentations or the benches on the
-    ground. In terms of producing a realistic visualization however,
-    the low-resolution model performs very similarly to the
-    high-resolution model.}
-  \label{fig:2dvs3d}
+  \caption{Textured models from the floor plan extrusion approach.}
+  \label{fig:fpModels}
+\end{figure}
+
+\begin{figure}
+  \centering{
+    \includegraphics[width=3in]{houston2.jpg}
+    \includegraphics[width=3in]{results_houston_1_3d.png} \\
+    \includegraphics[width=3in]{bhh3d2.png}
+    \includegraphics[width=3in]{bhh3d3.png}
+  }
+  \caption{Textured models from the voxel-carving approach.}
+  \label{fig:voxelModels}
 \end{figure}
@@
 floors. The third method generates high-resolution models, and
-attempts to reconstruct all scanned objects in the environment. A
-comparison of the three model types is in Figure
-\ref{fig:modelcomparisons}, while Figure \ref{fig:2dvs3d} compares the
-latter 2 types for a closer comparison of a low-resolution model vs a
-high-resolution model.
+attempts to reconstruct all scanned objects in the
+environment. Texture mapped models generated by the PCA-based, floor
+plan extrusion, and voxel-carving approaches, can be seen in Figures
+\ref{fig:pcaModels}, \ref{fig:fpModels}, and \ref{fig:voxelModels}
+respectively.
 

### 2014-01-04 spie2014/spie2014.tex
done?'

@@
 \begin{figure}
+  \centering
+  \subfloat[][]{\includegraphics[width=3in]{finalfloors.jpg}}
+  \subfloat[][]{\includegraphics[width=3in]{finalceilings.jpg}} \\
+
+  \centering \subfloat[][]{
+    \includegraphics[height=2in, width=3in]{floorcropped.jpg} 
+    \includegraphics[width=3in]{pier15floor.jpg}
+  }
+  \caption{Examples of our final texture mapping output for (a) walls,
+    (b) ceilings, (c) floors}
+  \label{fig:indivPlanes}
+\end{figure}
+
+\begin{figure}
   \centering{
@@
 attempts to reconstruct all scanned objects in the
-environment. Texture mapped models generated by the PCA-based, floor
-plan extrusion, and voxel-carving approaches, can be seen in Figures
-\ref{fig:pcaModels}, \ref{fig:fpModels}, and \ref{fig:voxelModels}
-respectively.
+environment. Examples of individually textured regions are shown in
+Figure \ref{fig:indivPlanes}, while fully texture mapped models
+generated by the PCA-based, floor plan extrusion, and voxel-carving
+approaches, can be seen in Figures \ref{fig:pcaModels},
+\ref{fig:fpModels}, and \ref{fig:voxelModels} respectively.
 
@@
 As mentioned earlier, our approach is quite efficient. The top wall in
-Figure \ref{fig:indivPlanes}(a) was generated with 7543 $\times$ 776
-pixels, and spans a 40-meter long wall. Given 41000 input images in
-the entire dataset, a 2.8 GHz dual-core consumer-grade laptop takes
-under a second to choose 36 candidate images, followed by a minute to
-perform image projections, image alignment, and the shortest path
-texturing method. The tile-caching approach takes roughly comparable
-time, and over 75\% of the time for either method is spent on
-calculating image projections, which are cached over multiple runs,
-and also could be performed as a preprocessing step instead. While not
-real-time, the process is capable of generating fast updates after
-changes in various parameters or modifications to input data, and if
-integrated directly into a 3D modeling system, could provide quick
-visual feedback as data is collected.
+Figure \ref{fig:indivPlanes}(a) is a single region, and its texture
+was generated with 7543 $\times$ 776 pixels, spanning a 40 meter long
+wall. Given 41000 input images in the dataset, a 2.8 GHz dual-core
+machine takes under 10 seconds to choose 36 candidate images and
+perform the full texturing process. The tile-caching approach takes a
+similar amount of time as well, with the much larger floor textures in
+Figure \ref{fig:indivPlanes}(c) taking 5-10 minutes to generate.
+While not real-time, our process is capable of generating fast updates
+after changes in various parameters or modifications to input data,
+and if integrated directly into a 3D modeling system, could provide
+quick visual feedback as data is collected.
 

### 2014-01-04 spie2014/spie2014.tex
final perhaps

@@
 For the purposes of texturing, it is convenient to treat each region
-as planar. To accomplish this, a plane is fitted to each region. This
-plane corresponds to the largest contiguous section of coplanar
-triangles, as most regions are characterized by small outcroppings
-from a largely planar surface, such as objects on a table or features
-protruding from a wall. The 3D surface composing a region is then
-projected onto its calculated plane, and the resulting 2D planar
-polygon is used as the texturing surface. This 2D planar approximation
-provides a simple, yet approximately accurate surface onto which
-images can be projected in order to generate textures. However, 3D
-surfaces are still retained in order to achieve accurate results when
-performing occlusion checks, and of course are used to generate the
-final textured model. Each region now has a set of triangles
-representing the original model geometry, as well as a planar
-approximation. The task now is to generate a texture for each region.
+as planar, and fit a plane to each region. This plane corresponds to
+the largest contiguous section of coplanar triangles in the region, as
+most regions are characterized by small outcroppings from a largely
+planar surface, such as objects on a table or features protruding from
+a wall. The 3D surface composing a region is then projected onto its
+calculated plane, and the resulting 2D planar polygon is used as the
+texturing surface. This 2D planar approximation provides a simple, yet
+approximately accurate surface onto which images can be projected in
+order to generate textures. However, 3D surfaces are still retained in
+order to achieve accurate results when performing occlusion checks,
+and of course are used to project the final textures upon. Each region
+now has a set of triangles representing the original model geometry,
+as well as a planar approximation. The task now is to generate a
+texture for each region.
 
@@
 are matched to each other, by detecting feature points and identifying
-matches. Images are then transformed to maximizally align matches,
+matches. Images are then transformed to maximally align matches,
 often by computing homographies between pairs of images, or by
@@
 determined using standard ray-polygon intersection tests between the
-camera location, $t$, and every other surface, or via the k-d tree
-from Section \ref{sec:geometryPartitioning} if present
+camera location, $t$, and the rest of the model's geometry.
 \cite{rayintersection}.
@@
 surface in our model except the target surface
-\cite{rayintersection}. If using planar approximations for regions, as
-explained in Section \ref{sec:geometryPartitioning}, the k-d tree is
-used instead. These intersection tests are performed repeatedly in a
+\cite{rayintersection}. These intersection tests are performed repeatedly in a
 recursive grid, until all occlusions are detected and corresponding
@@
 function, and solve a simple shortest path problem to find an optimal
-subset of images with regard to the SSD cost function \cite{dijkstra}.
+subset of images with which to texture the surface \cite{dijkstra}.
 
@@
 surfaces where images are taken at optimal angles and provide full
-coverage along one dimension. Floors, ceilings, and smaller complex
+coverage along one dimension. This generally includes all walls and
+most other vertical surfaces. Floors, ceilings, and smaller complex
 objects such as furniture, given their many images taken at oblique
@@
 \ref{sec:robustSIFTFeatureMatching}, exposure compensation is
-performed simulatenously across all images present in a single
+performed simultaneously across all images present in a single
 region. To begin, a relative gain $R_{ij}$ is computed for each pair
@@
 \cite{turnerfloorplan}, and a voxel-carving mesh generation method
-\cite{turnerwatertight}. The first two methods generate very similar
-low-resolution models, containing only major walls, ceilings and
-floors. The third method generates high-resolution models, and
-attempts to reconstruct all scanned objects in the
-environment. Examples of individually textured regions are shown in
-Figure \ref{fig:indivPlanes}, while fully texture mapped models
-generated by the PCA-based, floor plan extrusion, and voxel-carving
-approaches, can be seen in Figures \ref{fig:pcaModels},
-\ref{fig:fpModels}, and \ref{fig:voxelModels} respectively.
+\cite{turnerwatertight}. The first two methods generate low-resolution
+models containing only major walls, ceilings and floors. The third
+method generates high-resolution models, and attempts to reconstruct
+all scanned objects in the environment. Examples of individually
+textured regions are shown in Figure \ref{fig:indivPlanes}, while
+fully texture mapped models generated by the PCA-based, floor plan
+extrusion, and voxel-carving approaches, can be seen in Figures
+\ref{fig:pcaModels}, \ref{fig:fpModels}, and \ref{fig:voxelModels}
+respectively.
 
@@
 wall. Given 41000 input images in the dataset, a 2.8 GHz dual-core
-machine takes under 10 seconds to choose 36 candidate images and
+machine takes under 30 seconds to choose 36 candidate images and
 perform the full texturing process. The tile-caching approach takes a
-similar amount of time as well, with the much larger floor textures in
+similar amount of time as well, with the larger floor textures in
 Figure \ref{fig:indivPlanes}(c) taking 5-10 minutes to generate.
@@
 
-In this paper, we have developed an approach to texture mapping models
+In this paper, we have developed a method for texture mapping models
 of indoor environments with noisy camera localization data. We are
-able to refine image locations based on geometry references and
-feature matching, and robustly handle outliers. Using the tile-based
-mapping approach, we can texture both large planar features as well as
-smaller, more complex surfaces. We also implemented a shortest path
-texturing method that produces seamless textures on planes where
-multiple head-on images are available. Both of these approaches are
-highly modular, and easily tunable for similar systems across multiple
-environments.
+able to refine image locations based on geometry references as well as
+feature matching, while robustly handling environments with repeating
+or sparse details. Using the tile-based mapping approach, we can
+texture both large planar features as well as smaller, more complex
+surfaces. We also implemented a shortest path texturing method that
+produces seamless textures on planes where multiple head-on images are
+available. Both of these approaches are highly modular, and easily
+tunable for similar systems across multiple environments.
 
@@
 basic, and applying more sophisticated methods of blending as well as
-image boundary selection would benefit the final visual quality, and
+image boundary selection would benefit texture visual quality, and
 more robustly handle motion-based or parallax errors.

### 2014-03-31 spie2014/spie2014.tex
old cleanup

@@
 approximately accurate surface onto which images can be projected in
-order to generate textures. However, 3D surfaces are still retained in
-order to achieve accurate results when performing occlusion checks,
-and of course are used to project the final textures upon. Each region
-now has a set of triangles representing the original model geometry,
-as well as a planar approximation. The task now is to generate a
-texture for each region.
+order to generate textures. However, the original 3D surfaces are
+still retained in order to achieve accurate results when performing
+occlusion checks, and are used to project the final generated textures
+upon for 3D visualization. Each region now has a set of triangles
+representing the original model geometry, as well as a planar
+approximation. The task now is to generate a texture for each region.
 
@@
 \begin{figure}
-  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_naive.jpg}}
-  \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_naive_shift.jpg}}
-  \subfloat[][]{\includegraphics[trim=1.2cm 0cm 0cm 0cm,
-    clip=true,width=0.33\textwidth,
-    height=0.8in]{wall2_cache_shift.jpg}}
-
-  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_shortest_shift.pdf}}
-  \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_cache_shift_blend.pdf}}
-  \subfloat[][]{\includegraphics[width=0.33\textwidth,
-    height=0.8in]{wall2_shortest_shift_blend.pdf}}
+  \centering \subfloat[][]{\includegraphics[width=0.4\textwidth,
+    height=0.81in]{wall2_naive.jpg}} \hspace{0.4in}
+  \subfloat[][]{\includegraphics[width=0.4\textwidth,
+    height=0.81in]{wall2_naive_shift.jpg}}
+
+  \centering \subfloat[][]{\includegraphics[trim=1.2cm 0cm 0cm 0cm,
+    clip=true,width=0.4\textwidth,
+    height=0.81in]{wall2_cache_shift.jpg}} \hspace{0.4in}
+  \subfloat[][]{\includegraphics[width=0.4\textwidth,
+    height=0.81in]{wall2_shortest_shift.pdf}}
+
+  \centering \subfloat[][]{\includegraphics[width=0.4\textwidth,
+    height=0.81in]{wall2_cache_shift_blend.pdf}} \hspace{0.4in}
+  \subfloat[][]{\includegraphics[width=0.4\textwidth,
+    height=0.81in]{wall2_shortest_shift_blend.pdf}}
 
@@
 ray-polygon intersection tests between the camera location and every
-surface in our model except the target surface
-\cite{rayintersection}. These intersection tests are performed repeatedly in a
-recursive grid, until all occlusions are detected and corresponding
-occluded texture is removed. Occlusion checking works entirely with
-geometry, so by ensuring that images match geometry using
+other surface in our model \cite{rayintersection}. These intersection
+tests are performed repeatedly in a recursive grid, until all
+occlusions are detected and corresponding occluded texture is
+removed. Occlusion checking works entirely with geometry, so by
+ensuring that images match geometry using
 \ref{sec:geometryAlignment}'s alignment procedure, texture belonging
@@
 only concerned with lateral coverage when working with wall
-surfaces. We can therefore construct a horizontal Directed Acyclic
-Graph (DAG) from the images, with edge costs defined by the SSD cost
-function, and solve a simple shortest path problem to find an optimal
-subset of images with which to texture the surface \cite{dijkstra}.
+surfaces. We first crop each image projection to be rectangular, while
+maintaining full vertical coverage. This makes it easy to determine
+which images overlap, and has the benefit of enforcing image
+boundaries to be vertical and thus less noticeable, as vertical
+boundaries will minimally intersect the typically rectangular features
+in indoor environments. We then construct a horizontal Directed
+Acyclic Graph (DAG) from the images, with edge costs defined by the
+SSD cost function, and solve a simple shortest path problem to find an
+optimal subset of images with which to texture the surface
+\cite{dijkstra}.
 
@@
 \begin{figure}
-  \centering
-  \subfloat[][]{\includegraphics[width=2.5in, height=0.9in]{exposureDiff1.png}}
-  \hspace{0.5in}
-  \subfloat[][]{\includegraphics[width=2.5in, height=0.9in]{exposureDiff2.png}}
+  \centering \subfloat[][]{\includegraphics[width=2.5in,
+    height=0.9in]{exposureDiff1.png}} \hspace{0.5in}
+  \subfloat[][]{\includegraphics[width=2.5in,
+    height=0.9in]{exposureDiff2.png}}
   \caption{(a) A ceiling texture composed of images taken with varying
@@
 allowed to scale by any amount. To keep gains at reasonable values,
-the final observation is used: $\Sigma G_i = N$, where $N$ is the
-number of images. This has the effect of setting the average of all
-gains to 1, and is represented by the final row of ones in $X$, and
-the corresponding $N$ value in $\vec{a}$.
+the final observation is used: $\Sigma G_i = N$. This has the effect
+of setting the average of all gains to 1, and is represented by the
+final row of ones in $X$, and the corresponding $N$ value in
+$\vec{a}$.
 
@@
 perform the full texturing process. The tile-caching approach takes a
-similar amount of time as well, with the larger floor textures in
+similar amount of time as well, with the large floor textures in
 Figure \ref{fig:indivPlanes}(c) taking 5-10 minutes to generate.
@@
 surfaces. We also implemented a shortest path texturing method that
-produces seamless textures on planes where multiple head-on images are
+produces seamless textures on surfaces where multiple head-on images are
 available. Both of these approaches are highly modular, and easily
